### 2018-10-26 RICAM2018NovTalk.tex
changes

%Talk given at Computational Math Stat Seminar
\documentclass[11pt,compress,xcolor={usenames,dvipsnames},aspectratio=169]{beamer}
%\documentclass[xcolor={usenames,dvipsnames},aspectratio=169]{beamer} %slides and 
%notes
\usepackage{amsmath,datetime,
	mathtools,
	bbm,
	%mathabx,
	array,
	booktabs,
	xspace,
	calc,
	colortbl,
 	graphicx}
\usepackage[usenames]{xcolor}
\usepackage[giveninits=false,backend=biber,style=nature, maxcitenames =10, mincitenames=9]{biblatex}
\addbibresource{FJHown23.bib}
\addbibresource{FJH23.bib}
\usepackage{newpxtext}
\usepackage[euler-digits,euler-hat-accent]{eulervm}
\usepackage{media9}
\usepackage[autolinebreaks]{mcode}

\usetheme{FJHSlimNoFoot169}
\setlength{\parskip}{2ex}
\setlength{\arraycolsep}{0.5ex}

\newcommand{\sol}{S}
\newcommand{\app}{A}
%\DeclareMathOperator{\sol}{sol}
%\DeclareMathOperator{\app}{app}

\providecommand{\HickernellFJ}{H.}

\iffalse
Adaptive Approximation to Multivariate Linear Problems for Inputs Lying in a Cone

Function recovery, differentiation, and integral equations are examples of multivariate problems which require approximate numerical solutions.  One would like to identify a good algorithm, analyze the computational cost to achieve the desired error tolerance, understand how this cost depends on the number of variables, and determine whether the proposed algorithm is nearly optimal relative to the best possible algorithm.  This talk focuses on the situation where the inputs can be represented as series, and where the algorithm is allowed go sample individual series coefficients.  Rather than focusing on inputs lying inside a ball of fixed radius, we focus on inputs lying inside a cone of nice inputs.  This allows us to construct an adaptive algorithm, that automatically determines the number of series coefficients required to achieve the desired error tolerance.  The computational cost of the algorithm is characterized in terms of the space of inputs, space of outputs, solution operator, and definition of the cone.  The information-based complexity of problem and its tractability are also characterized.  These depend on the relative importance of the variables. 
\fi

\renewcommand{\OffTitleLength}{-10ex}
\setlength{\FJHThankYouMessageOffset}{-8ex}
\title{Adaptive Approximation for Multivariate Linear Problems  \\ for Inputs Lying in a Cone}
\author[]{Fred J. Hickernell}
\institute{Department of Applied Mathematics \\
	Center for Interdisciplinary Scientific Computation \\  Illinois Institute of Technology \\
	\href{mailto:hickernell@iit.edu}{\url{hickernell@iit.edu}} \quad
	\href{http://mypages.iit.edu/~hickernell}{\url{mypages.iit.edu/~hickernell}}}

\thanksnote{{\large Joint work with Yuhan Ding, Peter Kritzer, and Simon Mak} \\
	This work partially supported by  NSF-DMS-1522687 and NSF-DMS-1638521 (SAMSI) \& ???
}
\event{RICAM Workshop on Multivariate Algorithms and Information-Based Complexity}
\date[]{\\ November 9, 2018}

\input FJHDef.tex

%Abstract:  When

\newlength{\figwidth}
\setlength{\figwidth}{0.25\textwidth}

\newlength{\figwidthSmall}
\setlength{\figwidthSmall}{0.2\textwidth}

\newcommand{\financePict}{\href{http://i2.cdn.turner.com/money/dam/assets/130611131918-chicago-board-options-exchange-1024x576.jpg}{\includegraphics[width
		= 3cm]{ProgramsImages/130611131918-chicago-board-options-exchange-1024x576.jpg}}}

	\newcommand{\smallscoop}{\parbox{1cm}{\includegraphics[width=1cm]{ProgramsImages/IceCreamScoop.eps}}\xspace}
	\newcommand{\medscoop}{\parbox{1.8cm}{\includegraphics[width=1.8cm]{ProgramsImages/IceCreamScoop.eps}}\xspace}
	\newcommand{\meddanger}{\parbox{0.8cm}{\vspace{-0.3cm}\includegraphics[width=0.75cm]{ProgramsImages/dangersign.eps}}\xspace}
	\newcommand{\medcone}{\parbox{1.2cm}{\includegraphics[width=0.55cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}
	\newcommand{\largercone}{\parbox{2.2cm}{\vspace*{-0.2cm}\includegraphics[width=1cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}
	\newcommand{\largecone}{\parbox{1.54cm}{\vspace*{-0.2cm}\includegraphics[width=0.7cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}
	\newcommand{\smallcone}{\parbox{0.65cm}{\includegraphics[width=0.3cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}

\begin{document}
\everymath{\displaystyle}
\frame{\titlepage}
\section{Introduction}

\begin{frame}{Multivariate Linear Problems}
\vspace{-3ex}
\begin{tabular}{p{0.47\textwidth}p{0.5\textwidth}}
Given $f \in \cf$ find $g \in \cg$, where $g = \sol(f)$, \\
$\sol: \cf \to \cg$ is linear, e.g., 
\begin{gather*}
    g = \int_{\reals^d} f(\vx) \, \varrho(\vx) \, \dif \vx\\
    g = f\\
    g = \frac{\partial f}{\partial x_1} \\
    - \nabla^2 g = f, \ \  g = 0 \text{ on boundary}
\end{gather*}
&
\vspace{-10ex}
\begin{multline*}
    \ca(\ch) : = \{\app: \ch \times (0,\infty) \to \reals \text{ such that } \\
\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \\ \forall f \in \ch \subseteq \cf, \ \varepsilon > 0 \}
\end{multline*}

\vspace{-2ex}
where $\app(f,\varepsilon)$ depends on \alert{function values}, \alert{Fourier coefficients}, or \alert{linear functionals}, e.g.,

\vspace{-4ex}
\begin{gather*}
    \app(f,\varepsilon) = \sum_{i=1}^n f(\vx_i) v_i, \quad v_i \in \cg \\
    \app(f,\varepsilon) = \sum_{i=1}^n \hf_i v_i, \quad v_i \in \cg \\
    \app(f,\varepsilon) = \sum_{i=1}^n L_i(f) v_i, \quad v_i \in \cg \\
\end{gather*}

\vspace{-4ex}
How big should $n$ be to satisfy error tolerance?

\end{tabular}

\end{frame}

\begin{frame}{Issues}

\vspace{-3ex}

\begin{tabular}{p{0.48\textwidth}p{0.49\textwidth}}
Given $f \in \cf$ find $g \in \cg$, where $g = \sol(f)$, \\
$\sol: \cf \to \cg$ is linear

\vspace{-2ex}

\begin{multline*}
    \ca(\ch) : = \{\app: \ch \times (0,\infty) \to \reals \text{ such that } \\
\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \\ \forall f \in \ch \subseteq \cf, \ \varepsilon > 0 \}
\end{multline*}

\vspace{-2ex}
where $\app(f,\varepsilon)$ depends on \alert{function values}, \alert{Fourier coefficients}, or \alert{linear functionals}
&

\vspace{-9ex}
\uncover<2->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\ch) \ne \emptyset$

\medskip

\alert{Construction}: Identify concrete $\app \in \ca(\ch)$}

\medskip

\uncover<3->{\alert{Cost}: $\cost(\app,f,\varepsilon) = $ \# of function data
\newline
 $\cost(\app,\ch,\varepsilon, \rho) = \max_{f \in \ch \cap \cb_{\rho}} \cost(\app,f,\varepsilon)$
 \newline
 $\cb_{\rho} = \{f \in \cf : \norm[\cf]{f} \le \rho \}$

 \medskip

\alert{Complexity}\footfullcite{TraWasWoz88}: $\comp(\ca(\ch),\varepsilon,\rho)$ 
\newline \phantom{a} \hfill \hfill $= \min_{\app \in \ca(\ch)} \cost(\app,\ch,\varepsilon, \rho)$

\medskip

\alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\ch,\varepsilon, \rho) \le \comp(\ca(\ch),\alert{\omega} \varepsilon,\rho)$}

\medskip

\uncover<4->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\ch,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}

\vspace{-6ex}

\phantom{a}

\end{tabular}

\end{frame}

\thankyouframe

\printbibliography

\end{document}

\begin{frame}
\frametitle{What Does It Mean to Solve a Mathematics or Statistics Problem?}
\vspace{-5ex}

\[
\begin{array}{r@{\qquad}l}
	\text{Problem} & \text{Solution} \\
	\toprule
	x^2 +2 x - 3 = 0 &  x = -3, 1  \qquad \text{\alert{numbers}}\\
	\uncover<2->{\frac{\dif}{\dif x} \sin(x) & \cos(x) \qquad \text{\alert{elementary function}}} \\[2ex]
	\uncover<3->{\frac{1}{\sqrt{2\pi}} \int_{-\infty}^{1} \me^{-x^2/2} \, \dif x &  \Phi(1) \qquad \text{\alert{special function}} \\
	& \Phi \text{ is the standard Gaussian cumulative distribution function} } \\
\midrule
\uncover<4->{
\int_0^1 f(x) \, \dif x  & \text{Need a \alert{numerical solution}, i.e., } A(f,\varepsilon) \\[2ex]
f \text{ known via an algorithm} & \text{depending on integrand values } f(x_1), \, f(x_2), \ldots  \\
\text{i.e., can get } f(x) \ \forall x \in [0,1] & \text{such that } \abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon }
	\end{array}
	\]
\end{frame}

\begin{frame}
\frametitle{What About the Trapezoidal Rule?}
\vspace{-5ex}
\[
\int_0^1 f(x) \, \dif x \approx T_n(f)=\frac{1}{n}\left[\frac{f(0)}{2} + f\left(\frac{1}{n}\right) + \cdots + f\left(\frac{n-1}{n}\right) +  \frac{f(1)}{2} \right]
\]
\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
\only<5->{\only<5-6>{Theory says
	\vspace{-3ex}
	\begin{equation*}
	\biggabs{\int_0^1 f(x) \, \dif x -T_n(f)} \le \frac{\overbrace{\int_0^1 \abs{f''(x)} \, \dif x}^{\text{curvature}}}{8 n^2} = \frac{\norm[1]{f''}}{8 n^2} \overset{\alert{?}}{\le} \varepsilon
	\end{equation*}

		\vspace{-1ex}
	\only<6>{Let $\cf = \{f :\norm[1]{f''} \le \rho \}$  \medscoop, and let}}\only<7->{Let}\uncover<6->{

	\vspace{-1ex}
	\[
	A(f,\varepsilon) = T_n(f) \quad \text{where }n = \left \lceil \sqrt{\frac{\rho}{8\varepsilon}} \, \right \rceil
	\]

	\vspace{-2ex}
	Then 
	\[
	 \abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf\only<7->{= \{f :\norm[1]{f''} \le \rho \}}, \, \varepsilon > 0
	 \]}}
	& 
	\only<1>{\includegraphics[width=5cm]{ProgramsImages/traprule-1.eps}\\$T_1(f)=0.5034$}
	\only<2>{\includegraphics[width=5cm]{ProgramsImages/traprule-2.eps}\\$T_2(f)=0.3949$}
	\only<3>{\includegraphics[width=5cm]{ProgramsImages/traprule-3.eps}\\$T_4(f)=0.3954$}
	\only<4->{\includegraphics[width=5cm]{ProgramsImages/traprule-4.eps}\\$T_{50}(f)=0.3957$}
\end{tabular}
\only<7->{We say that integration is \alert{solvable} for integrands in $\cf$  \medscoop}

\end{frame}

\section{Solvability}
\begin{frame}
\frametitle{Solvability\footfullcite{KunEtal19a}}
\vspace{-4ex}

A problem is called \alert{solvable} for a set of inputs $\cf$ \alert{if there exists} a numerical algorithm that provides a solution with error no greater than $\varepsilon$.  Specifically, integration is solvable for $\cf$ if there exists an $A$ for which 
	\[
\abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf, \, \varepsilon > 0
\]
\uncover<2->{We demonstrated that integration is solvable for 
\[
\cf = \{f :\norm[1]{f''} \le \rho \}  \quad \medscoop
\]
\uncover<3>{Is integration solvable for 
\[
\cf = \{f :\norm[1]{f''} < \alert{\infty} \} \quad \text{since } \biggabs{\int_0^1 f(x) \, \dif x -T_n(f)} \le  \frac{\norm[1]{f''}}{8 n^2} \alert{?}
\]
}}

\end{frame}

\begin{frame}
\frametitle{Integration Is \emph{Not} Solvable for $\cf = \{f :\norm[1]{f''} < \infty \}$}
\vspace{-3ex}
Suppose that there exists  $A$ such that 
\[
\abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf= \{f :\norm[1]{f''} < \infty \}, \, \varepsilon > 0
\]
\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
	\begin{itemize}
	\item<2->Observe where $A(0,\varepsilon)$ gets function values

\item<3->Construct $f_{\text{bump}} \in \cf$, as tall as you like; note that $A(0,\varepsilon) = A(f_{\text{bump}},\varepsilon)$

	\item<4->  Since $\int_0^1 0 \, \dif x$ and $\int_0^1 f_{\text{bump}}(x) \, \dif x$ are so different, $A$ cannot be successful

\end{itemize}

	&
	\only<2>{\includegraphics[width=5cm]{ProgramsImages/ZeroFun.eps}}
	\only<3->{\includegraphics[width=5cm]{ProgramsImages/QuadHump.eps}}
\end{tabular}

\vspace{-5ex}

\uncover<5->{Why doesn't this argument hold for $\cf = \{f :\norm[1]{f''} \le \rho \}  \medscoop$? \\  \uncover<6->{Because $f_{\text{bump}} \notin \medscoop$}}

\end{frame}

\section{Optimality}

\begin{frame}
\frametitle{Is Trapezoidal Rule the Best Algorithm?}
\vspace{-4ex}
Let $\cost(A,f,\varepsilon)$ denote the number of function values, $n$ required for $A(f,\varepsilon)$ and 
\[
\cost(A,\cf,\varepsilon) = \sup_{f \in \cf} \cost(A,f,\varepsilon)
\]
For our trapezoidal rule algorithm, $A$
\[
\cost(A,\cf,\varepsilon) =  \cost(A,f,\varepsilon) = \left \lceil \sqrt{\frac{\rho}{8\varepsilon}} \right \rceil = \Order\left(\sqrt{ \frac{\rho}{\varepsilon}} \right) \qquad \forall f \in \cf = \{f :\norm[1]{f''} \le \rho \}  \medscoop
\]
This is the \alert{(up to a constant)} the smallest possible cost \uncover<2->{for integrands in $\cf = \{f :\norm[1]{f''} \le \rho \}  \medscoop$, no worse than Simpson's rule, Gauss rules, etc.}
\end{frame}

\finalthanksnote{Slides available on SpeakerDeck at
	\href{https://speakerdeck.com/fjhickernell/matrix-week-two-2018-june}
	{\nolinkurl{speakerdeck.com/fjhickernell/matrix-week-two-2018-june}}
}

\begin{frame}
\frametitle{Why the Trapezoidal Rule Is Optimal for $\cf = \{f :\norm[1]{f''} < \rho \}$}
\vspace{-3ex}
Let $A$ be \alert{any} algorithm satisfying
\[
\abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf= \{f :\norm[1]{f''} < \rho \}, \, \varepsilon > 0
\]

\vspace{-5ex}
\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
	\begin{itemize}
		\item<2->Observe where $A(0,\varepsilon)$ gets function values

		\item<3->Construct $f_{\text{bump}} \in \cf$; note that $A(0,\varepsilon) = A(f_{\text{bump}},\varepsilon) = A(-f_{\text{bump}},\varepsilon)$

		\item<4->  For $A$ to succeed for $\pm f_{\text{bump}} $, which have different integrals, one must have 
		\[
		\cost(A,\cf,\varepsilon) =  \Order\left(\sqrt{ \frac{\rho}{\varepsilon}} \right)
		\]
		the same as the trapezoidal rule algorithm.

	\end{itemize}

	&
	\only<2>{\includegraphics[width=5cm]{ProgramsImages/ZeroFun.eps}}
	\only<3->{\includegraphics[width=5cm]{ProgramsImages/TwoQuadHump.eps}}
\end{tabular}

\vspace{-5ex}

\uncover<5->{Why do your instructors tell you that other algorithms are \alert{better than the trapezoidal rule}?  \\  \uncover<6->{They are only better when you assume that the integrand has \alert{more smoothness}}}

\end{frame}

\section{Adaptive Algorithms}

\begin{frame}
\frametitle{The Impracticality of Our Non-Adaptive Trapezoidal Rule Algorithm}
\vspace{-7ex}
\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
\begin{gather*}
T_n(f)=\frac{1}{n}\left[\frac{f(0)}{2} + f\left(\frac{1}{n}\right) + \cdots + f\left(\frac{n-1}{n}\right) +  \frac{f(1)}{2} \right] \\
A(f,\varepsilon) = T_n(f) \quad \text{where }n = \left \lceil \sqrt{\frac{\rho}{8\varepsilon}} \, \right \rceil
\end{gather*}

\vspace{-2ex}
\begin{itemize}
	\item \alert{Solves} the integration problem for  $\cf = \{f :\norm[1]{f''} \le \rho \}$  \medscoop

	\item \alert{Costs} $\Order(\sqrt{\rho/\varepsilon})$ function values

	\item Is \alert{optimal} for $\cf = \{f :\norm[1]{f''} \le \rho \}$  \medscoop
\end{itemize}
	& 
	\includegraphics[width=5cm]{ProgramsImages/traprule-4.eps}\\$T_{50}(f)=0.3957$
\end{tabular}
What more could we want?

\uncover<2>{An algorithm that costs  $\Order(\sqrt{\norm[1]{f''}/\varepsilon})$  without needing to know  $\norm[1]{f''}$; \alert{cost depends on difficulty}}
\end{frame}

\begin{frame}
\frametitle{Adaptive Algorithms Don't Work for Balls, But May Work for Cones}
\vspace{-3ex}

\alert{Adptive} algorithms expend effort comensurate with the difficulty of the problem

\vspace{-3ex}
\begin{itemize}

	\item If $\cf = \medscoop$, then non-adaptive algorithms are optimal because $\medscoop$ is 
	\begin{description}

		\item[Balanced:] $f \in \cf \implies -f \in \cf$, and

		\item[Convex:] $f, g \in \cf \implies \theta \cf + (1 - \theta) g \in \cf$ for $0 \le \theta \le 1$

\end{description}

\end{itemize}

\vspace{-3ex}

\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
	\begin{itemize}
		\item<2-> However, adaptive algorithms may be optimal for non-convex $\cf = \medcone$ ($f \in \cf \implies cf \in \cf$)

	\item<3-> We developed an adaptive trapezoidal rule that \alert{optimally solves} the integral for $\cf = \medcone$, a set of functions where the true curvature is not much more than its numerical approximation\footfullcite{HicEtal14b}

	\item<4-> Common adaptive algorithms in use \alert{have no theory}
	\end{itemize}
	& 
	\includegraphics[width=5cm]{ProgramsImages/traprule-4.eps}
\end{tabular}

\end{frame}

\begin{frame}
\frametitle{Adaptive Algorithms Don't Work for Balls, But May Work for Cones}
\vspace{-3ex}

We also developed adaptive algorithms for

\vspace{-3ex}
\begin{itemize}

	\item Univariate integration by Simpson's rule\footfullcite{Zha18a}

	\item Univariate function approximation and optimization\footfullcite{ChoEtal17a}

	\item Multivariate integration\footfullcite{HicEtal14a,HicJim16a,RatHic19a}

\end{itemize}

\vspace{-3ex}

made available in the Guaranteed Automatic Integration Library (GAIL)\footfullcite{ChoEtal17b}

\end{frame}

\section{Open Problems}

\begin{frame}
\frametitle{Work to Be Done}

\vspace{-5ex}
\begin{itemize}

	\item Find $\cf = \medcone$ for which MATLAB's\footfullcite{MAT9.5} \alert{\mcode{integral_g}} or \alert{Chebfun}\footfullcite{TrefEtal17a} are guaranteed to solve the integration problem

	\item \alert{Locally} adaptive univariate integration

	\item Higher order \alert{function approximation}

	\item Adaptive \alert{multi-level Monte Carlo} methods\footfullcite{Gil15a}

	\item Adaptive multivariate \alert{function approximation}\footfullcite{DinHic20a}

	\item Other error criteria, such as \alert{relative error} or a hybrid of absolute and relative error\footfullcite{HicEtal17a}

	\item Combining our software efforts with that of other research groups

\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Other Opportunities for You}

\begin{itemize}
	\item Join the Society for Industrial and Applied Mathematics (SIAM) for free \beamerbutton{\href{https://www.siam.org/Membership/Join-SIAM/Individual-Members/Student}{Click here}}

	\item Join the American Statististcal Association (ASA) for \$25 per year  \beamerbutton{\href{https://www.amstat.org/ASA/JoinRenew/JoinMemberType.aspx?membertype=IREG}{Click here}}
\end{itemize}
\end{frame}

\finalthanksnote{Slides available on SpeakerDeck at
	\href{https://speakerdeck.com/fjhickernell/can-we-solve-it-if-so-how-fast}
	{\nolinkurl{speakerdeck.com/fjhickernell/can-we-solve-it-if-so-how-fast}}
}

\thankyouframe

\printbibliography

\end{document}

### 2018-11-02 ProgramsImages/BasisPictures.m
adding basis figures

@@ -1,0 +1,64 @@
+%% Basis Pictures
+
+clearvars
+InitializeDisplay
+set(0,'defaultLineLineWidth',6) %thick lines
+
+n1plot = 1e4;
+n2plot = 500;
+s_max = 4;
+d = 2;
+twoD = [1 1; 1 2; 1 3; 1 4; 2 2; 2 3];
+nTwoD = size(twoD,1);
+
+basisHandles = {@WalshBasis,@legendreBasis,@chebyshevBasis,@CosSinBasis};
+basisNames = ["Walsh","Legendre","Chebyshev","CosineSine"];
+nBasis = length(basisNames);
+aa = [0 -1 -1 0];
+bb = [1 1 1 1];
+for nB = 1:1
+   % One dimensional basis plots
+   a = aa(nB);
+   b = bb(nB);
+   h1 = (b - a)/(n1plot-1);
+   h2 = (b - a)/(n2plot-1);
+   x1plot = [a:h1:b-h1 b - 100*eps];
+   x2plot = [a:h2:b-h2 b - 100*eps];
+   [xx, yy] = meshgrid(x2plot);
+   horizOff = a + 0.15*(b-a);
+   vertOff = 1.2;
+   for s = 0:s_max
+      y = basisHandles{nB}(s,x1plot);
+      figure
+      plot(x1plot,y,'-')
+      axis([a b -1.2 1.2])
+      set(gca,'Visible','off')
+      text(horizOff,vertOff,['\boldmath\(j\,\) \unboldmath \(= (' int2str(s) ', 0, \ldots, 0)\)'], ...
+         'interpreter','latex','fontsize',48)
+       eval(['print(''' char(basisNames(nB)) '_Degree_' int2str(s) '.png'',' ...
+          '''-dpng'')'])
+      eval(['print(''' char(basisNames(nB)) '_Degree_' int2str(s) '.eps'',' ...
+         '''-depsc'', ''-opengl'')'])
+   end
+   
+   %Two-dimensional basis plots
+   xOff = a;
+   yOff = a + 3*(b-a)/4;
+   zOff = 2.2;
+   for j = 1:nTwoD
+      z = basisHandles{nB}(twoD(j,1),xx).*basisHandles{nB}(twoD(j,2),yy);
+      figure
+      surf(xx,yy,z); shading interp
+      axis([a b a b -1.2 1.2])
+      set(gca,'Visible','off')
[…]

### 2018-11-02 ProgramsImages/CosSinBasis.m

@@ -1,0 +1,4 @@
+function [y,p] = CosSinBasis(s,x)
+y = cos((2*pi*ceil(s/2))*x - mod(s,2)*(pi/2));
+p = 1;
+return

### 2018-11-02 ProgramsImages/WalshBasis.m

@@ -1,0 +1,13 @@
+function [y,p] = WalshBasis(s,x)
+y = ones(size(x));
+numSdig = max(0,floor(log2(s)) + 1);
+twok = 1;
+for k = 1:numSdig
+   twokm1 = twok;
+   twok = 2*twok;
+   if mod(floor(s/twokm1),2)
+      y = y.*((-1).^floor(mod(x*twok,2)));
+   end
+end
+p = 1;
+return

### 2018-11-02 RICAM2018NovTalk.tex

@@
 \newcommand{\app}{A}
-%\DeclareMathOperator{\sol}{sol}
+\newcommand{\Sapp}{S_{\textup{app}}}
+\newcommand{\LambdaStd}{\Lambda^{\textup{std}}}
+\newcommand{\LambdaSer}{\Lambda^{\textup{ser}}}
+\newcommand{\LambdaAll}{\Lambda^{\textup{all}}}
+\DeclareMathOperator{\spann}{span}
 %\DeclareMathOperator{\app}{app}
@@
 \iffalse
-Adaptive Approximation to Multivariate Linear Problems for Inputs Lying in a Cone
+Adaptive Approximation to Multivariate Linear Problems with Inputs Lying in a Cone
 
@@
 \setlength{\FJHThankYouMessageOffset}{-8ex}
-\title{Adaptive Approximation for Multivariate Linear Problems  \\ for Inputs Lying in a Cone}
+\title{Adaptive Approximation for Multivariate Linear Problems  \\ with Inputs Lying in a Cone}
 \author[]{Fred J. Hickernell}
@@
 
-	\newcommand{\smallscoop}{\parbox{1cm}{\includegraphics[width=1cm]{ProgramsImages/IceCreamScoop.eps}}\xspace}
-	\newcommand{\medscoop}{\parbox{1.8cm}{\includegraphics[width=1.8cm]{ProgramsImages/IceCreamScoop.eps}}\xspace}
-	\newcommand{\meddanger}{\parbox{0.8cm}{\vspace{-0.3cm}\includegraphics[width=0.75cm]{ProgramsImages/dangersign.eps}}\xspace}
-	\newcommand{\medcone}{\parbox{1.2cm}{\includegraphics[width=0.55cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}
-	\newcommand{\largercone}{\parbox{2.2cm}{\vspace*{-0.2cm}\includegraphics[width=1cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}
-	\newcommand{\largecone}{\parbox{1.54cm}{\vspace*{-0.2cm}\includegraphics[width=0.7cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}
-	\newcommand{\smallcone}{\parbox{0.65cm}{\includegraphics[width=0.3cm,angle=270]{ProgramsImages/MediumWaffleCone.eps}}\xspace}
+	\newcommand{\scoop}[1]{\parbox{#1}{\includegraphics[width=#1]{IceCreamScoop.eps}}\xspace}
+	\newcommand{\smallscoop}{\scoop{1cm}}
+	\newcommand{\medscoop}{\parbox{1.8cm}{\includegraphics[width=1.8cm]{IceCreamScoop.eps}}\xspace}
+	\newcommand{\largescoop}{\scoop{3cm}}
+	\newcommand{\ICcone}[1]{\parbox{#1}{\includegraphics[width=#1,angle=270]{MediumWaffleCone.eps}}\xspace}
+	\newcommand{\medcone}{\ICcone{1.2cm}}
+	\newcommand{\largercone}{\parbox{2.2cm}{\vspace*{-0.2cm}\includegraphics[width=1cm,angle=270]{MediumWaffleCone.eps}}\xspace}
+	\newcommand{\largecone}{\ICcone{1.8cm}}
+	\newcommand{\smallcone}{\parbox{0.65cm}{\includegraphics[width=0.3cm,angle=270]{MediumWaffleCone.eps}}\xspace}
 
@@
 \begin{tabular}{p{0.47\textwidth}p{0.5\textwidth}}
-Given $f \in \cf$ find $g \in \cg$, where $g = \sol(f)$, \\
+Given $f \in \cf$ find $S(f) \in \cg$, where \\
 $\sol: \cf \to \cg$ is linear, e.g., 
 \begin{gather*}
-    g = \int_{\reals^d} f(\vx) \, \varrho(\vx) \, \dif \vx\\
-    g = f\\
-    g = \frac{\partial f}{\partial x_1} \\
-    - \nabla^2 g = f, \ \  g = 0 \text{ on boundary}
+    S(f) = \int_{\reals^d} f(\vx) \, \varrho(\vx) \, \dif \vx\\
+    S(f) = f\\
+    S(f) = \frac{\partial f}{\partial x_1} \\
+    - \nabla^2 S(f) = f, \ \  S(f) = 0 \text{ on boundary}
 \end{gather*}
 &
-\vspace{-10ex}
+\vspace{-5ex}
+\alert{Successful algorithms}
+\vspace{-3ex}
 \begin{multline*}
-    \ca(\ch) : = \{\app: \ch \times (0,\infty) \to \reals \text{ such that } \\
-\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \\ \forall f \in \ch \subseteq \cf, \ \varepsilon > 0 \}
+    \ca(\cc) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } \\
+\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \ \ \forall f \in \cc \subseteq \cf, \ \varepsilon > 0 \}
 \end{multline*}
 
-\vspace{-2ex}
-where $\app(f,\varepsilon)$ depends on \alert{function values}, \alert{Fourier coefficients}, or \alert{linear functionals}, e.g.,
+\vspace{-1ex}
+where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{linear functionals}, $\LambdaAll$, e.g.,
 
@@
 \begin{gather*}
-    \app(f,\varepsilon) = \sum_{i=1}^n f(\vx_i) v_i, \quad v_i \in \cg \\
-    \app(f,\varepsilon) = \sum_{i=1}^n \hf_i v_i, \quad v_i \in \cg \\
-    \app(f,\varepsilon) = \sum_{i=1}^n L_i(f) v_i, \quad v_i \in \cg \\
+    \app(f,\varepsilon) = \Sapp(f,n) = \sum_{i=1}^n f(\vx_i) g_i, \quad g_i \in \cg \\
+    \app(f,\varepsilon) = \Sapp(f,n) = \sum_{i=1}^n \hf_i g_i, \quad g_i \in \cg \\
+    \app(f,\varepsilon) = \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i, \quad g_i \in \cg \\
 \end{gather*}
 
-\vspace{-4ex}
-How big should $n$ be to satisfy error tolerance?
+\vspace{-5ex}
+\hfill \hfill \alert{$n = ?$, $\cc$ is not a ball}
 
@@
 \begin{tabular}{p{0.48\textwidth}p{0.49\textwidth}}
-Given $f \in \cf$ find $g \in \cg$, where $g = \sol(f)$, \\
+Given $f \in \cf$ find $S(f) \in \cg$, where \\
 $\sol: \cf \to \cg$ is linear
 
+\bigskip
+
+\alert{Successful algorithms}
 \vspace{-2ex}
-
 \begin{multline*}
-    \ca(\ch) : = \{\app: \ch \times (0,\infty) \to \reals \text{ such that } \\
-\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \\ \forall f \in \ch \subseteq \cf, \ \varepsilon > 0 \}
+    \ca(\cc) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } \\
+\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \ \ \forall f \in \cc \subseteq \cf, \ \varepsilon > 0 \}
 \end{multline*}
 
-\vspace{-2ex}
-where $\app(f,\varepsilon)$ depends on \alert{function values}, \alert{Fourier coefficients}, or \alert{linear functionals}
+\vspace{-1ex}
+where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{linear functionals}, $\LambdaAll$
 &
@@
 \vspace{-9ex}
-\uncover<2->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\ch) \ne \emptyset$
+\uncover<2->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc) \ne \emptyset$
 
@@
 
-\alert{Construction}: Identify concrete $\app \in \ca(\ch)$}
+\alert{Construction}: Identify $\app \in \ca(\cc)$}
 
@@
 \newline
- $\cost(\app,\ch,\varepsilon, \rho) = \max_{f \in \ch \cap \cb_{\rho}} \cost(\app,f,\varepsilon)$
+ $\cost(\app,\cc,\varepsilon, \rho) = \max_{f \in \cc \cap \cb_{\rho}} \cost(\app,f,\varepsilon)$
  \newline
- $\cb_{\rho} = \{f \in \cf : \norm[\cf]{f} \le \rho \}$
+ $\cb_{\rho} := \{f \in \cf : \norm[\cf]{f} \le \rho \}$
 
@@
 
-\alert{Complexity}\footfullcite{TraWasWoz88}: $\comp(\ca(\ch),\varepsilon,\rho)$ 
-\newline \phantom{a} \hfill \hfill $= \min_{\app \in \ca(\ch)} \cost(\app,\ch,\varepsilon, \rho)$
+\alert{Complexity}\footfullcite{TraWasWoz88}: $\comp(\ca(\cc),\varepsilon,\rho)$ 
+\newline \phantom{a} \hfill \hfill $= \min_{\app \in \ca(\cc)} \cost(\app,\cc,\varepsilon, \rho)$
 
@@
 
-\alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\ch,\varepsilon, \rho) \le \comp(\ca(\ch),\alert{\omega} \varepsilon,\rho)$}
+\alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\cc,\varepsilon, \rho) \le \comp(\ca(\cc),\alert{\omega} \varepsilon,\rho)$}
 
@@
 
-\uncover<4->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\ch,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}
+\uncover<4->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\cc,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}
 
@@
 
-\thankyouframe
+\begin{frame}{Cones}
+\vspace{-4ex}
+\begin{tabular}{>{\centering}m{0.4\textwidth}@{\qquad}>{\centering}m{0.4\textwidth}}
+     \largescoop \hspace{-3cm}\raisebox{-4ex}{\color{red}\fontsize{100}{120}\selectfont $\times$} & 
+      \largecone \tabularnewline
+      Ball $\cb_{\rho} := \{f \in \cf : \norm[\cf]{f} \le \rho \}$ &
+      \hspace{2cm} (Non-Convex) Cone $\cc$
+\end{tabular}
 
-\printbibliography
+\begin{itemize}
+    \item Assume set of inputs, $\cc \subseteq \cf$, is a \alert{cone}, not a ball
 
-\end{document}
+    \item \alert{Cone} means $f \in \cc \implies af \in \cc$
 
-\begin{frame}
-\frametitle{What Does It Mean to Solve a Mathematics or Statistics Problem?}
-\vspace{-5ex}
+    \item \alert{Cones} are unbounded
 
-\[
-\begin{array}{r@{\qquad}l}
-	\text{Problem} & \text{Solution} \\
-	\toprule
-	x^2 +2 x - 3 = 0 &  x = -3, 1  \qquad \text{\alert{numbers}}\\
-	\uncover<2->{\frac{\dif}{\dif x} \sin(x) & \cos(x) \qquad \text{\alert{elementary function}}} \\[2ex]
-	\uncover<3->{\frac{1}{\sqrt{2\pi}} \int_{-\infty}^{1} \me^{-x^2/2} \, \dif x &  \Phi(1) \qquad \text{\alert{special function}} \\
-	& \Phi \text{ is the standard Gaussian cumulative distribution function} } \\
-\midrule
-\uncover<4->{
-\int_0^1 f(x) \, \dif x  & \text{Need a \alert{numerical solution}, i.e., } A(f,\varepsilon) \\[2ex]
-f \text{ known via an algorithm} & \text{depending on integrand values } f(x_1), \, f(x_2), \ldots  \\
-\text{i.e., can get } f(x) \ \forall x \in [0,1] & \text{such that } \abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon }
-	\end{array}
-	\]
-\end{frame}
+    \item If we can bound the error for $f \in $ \alert{cone}, then we can typically also bound the error  for $af$
 
-\begin{frame}
-\frametitle{What About the Trapezoidal Rule?}
-\vspace{-5ex}
-\[
-\int_0^1 f(x) \, \dif x \approx T_n(f)=\frac{1}{n}\left[\frac{f(0)}{2} + f\left(\frac{1}{n}\right) + \cdots + f\left(\frac{n-1}{n}\right) +  \frac{f(1)}{2} \right]
-\]
-\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
-\only<5->{\only<5-6>{Theory says
-	\vspace{-3ex}
-	\begin{equation*}
-	\biggabs{\int_0^1 f(x) \, \dif x -T_n(f)} \le \frac{\overbrace{\int_0^1 \abs{f''(x)} \, \dif x}^{\text{curvature}}}{8 n^2} = \frac{\norm[1]{f''}}{8 n^2} \overset{\alert{?}}{\le} \varepsilon
-	\end{equation*}
-
-		\vspace{-1ex}
-	\only<6>{Let $\cf = \{f :\norm[1]{f''} \le \rho \}$  \medscoop, and let}}\only<7->{Let}\uncover<6->{
-
-	\vspace{-1ex}
-	\[
-	A(f,\varepsilon) = T_n(f) \quad \text{where }n = \left \lceil \sqrt{\frac{\rho}{8\varepsilon}} \, \right \rceil
-	\]
-
-	\vspace{-2ex}
-	Then 
-	\[
-	 \abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf\only<7->{= \{f :\norm[1]{f''} \le \rho \}}, \, \varepsilon > 0
-	 \]}}
-	& 
-	\only<1>{\includegraphics[width=5cm]{ProgramsImages/traprule-1.eps}\\$T_1(f)=0.5034$}
-	\only<2>{\includegraphics[width=5cm]{ProgramsImages/traprule-2.eps}\\$T_2(f)=0.3949$}
-	\only<3>{\includegraphics[width=5cm]{ProgramsImages/traprule-3.eps}\\$T_4(f)=0.3954$}
-	\only<4->{\includegraphics[width=5cm]{ProgramsImages/traprule-4.eps}\\$T_{50}(f)=0.3957$}
-\end{tabular}
-\only<7->{We say that integration is \alert{solvable} for integrands in $\cf$  \medscoop}
+    \item Union of \alert{cones} is a \alert{cone}
+\end{itemize}
 
@@
 \section{Solvability}
-\begin{frame}
-\frametitle{Solvability\footfullcite{KunEtal19a}}
-\vspace{-4ex}
+\begin{frame}{When Is $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \emph{Solvable}?}
 
-A problem is called \alert{solvable} for a set of inputs $\cf$ \alert{if there exists} a numerical algorithm that provides a solution with error no greater than $\varepsilon$.
-Specifically, integration is solvable for $\cf$ if there exists an $A$ for which
-	\[
-\abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf, \, \varepsilon > 0
-\]
-\uncover<2->{We demonstrated that integration is solvable for 
-\[
-\cf = \{f :\norm[1]{f''} \le \rho \}  \quad \medscoop
-\]
-\uncover<3>{Is integration solvable for 
-\[
-\cf = \{f :\norm[1]{f''} < \alert{\infty} \} \quad \text{since } \biggabs{\int_0^1 f(x) \, \dif x -T_n(f)} \le  \frac{\norm[1]{f''}}{8 n^2} \alert{?}
-\]
-}}
+\vspace{-7ex}
+\begin{multline*}
+     \ca(\cc) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } 
+\norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \ \forall f \in \cc \subseteq \cf, \ \varepsilon > 0 \}
+  \\
+  \text{where $A(f,\varepsilon)$ depends on } \{L_i(f)\}_{i=1}^n \in \Lambda^n \subseteq \cf^{*n}
+\end{multline*}
+
+\vspace{-3ex}
+
+\alert{Definition} \quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} $\iff \ca(\cc) \ne \emptyset$\\[1ex]
+\alert{Lemma}  \quad $f_1, f_2 \in \cc$  and $A(f_1, \varepsilon) = A(f_2,\varepsilon) \implies \norm[\cg]{S(f_1-f_2)} \le \varepsilon$\\[1ex]
+\alert{Corollary} \label{ZeroCorollary} \quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} and $\exists f \in \cc,\  \varepsilon > 0$ with $A(f,\varepsilon) = A(0,\varepsilon)$  \\ \hfill \hfill $\implies S(f) = 0$\\[1ex]
+\alert{Theorem} \label{VectorSpaceThm}\quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} and $\cc$ is a \alert{vector space} \\ \hfill \hfill 
+$\iff S(f) = \sum_{i=1}^n L_i(f) g_i$ for some $\vL \in \Lambda^n, \vg \in \cg^n$  \hyperlink{VectorSpaceThmProof}{\beamergotobutton{Proof}}\\[1ex]
+E.g. $\left(\int_{[0,1]^d} \cdot (\vx) \, \dif \vx: C^{1,\ldots,1}[0,1]^d\to\reals,\Lambda^{\textup{std/\alert{all}}}\right)$ is unsolvable/\alert{solvable}
+
+\end{frame}
+
+\section{Series Spaces}
+
+\begin{frame}{Spaces of Inputs and Outputs}
+
+\vspace{-3ex}
+
+We focus on Banach spaces that look like
+
+\vspace{-5ex}
+\begin{align*}
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \\
+    \cg &: = \left \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\right \}, \qquad S(u_{\vj}) = v_{\vj}, \\
+    \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
+    & \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj\\
+    \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
+    \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
+\end{align*}
 
@@
 \begin{frame}
-\frametitle{Integration Is \emph{Not} Solvable for $\cf = \{f :\norm[1]{f''} < \infty \}$}
+\frametitle{Example Bases}
 \vspace{-3ex}
-Suppose that there exists  $A$ such that 
-\[
-\abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf= \{f :\norm[1]{f''} < \infty \}, \, \varepsilon > 0
-\]
-\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
-	\begin{itemize}
-	\item<2->Observe where $A(0,\varepsilon)$ gets function values
+	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_0.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_3.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_4.png} 
+	\tabularnewline[-7ex]
+	Legendre
+	\tabularnewline
+	\tabularnewline
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_3.png} 
+\tabularnewline[0ex]
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_0.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_3.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_4.png} 
+\tabularnewline[-7ex]
+Chebyshev \tabularnewline
+\tabularnewline
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_3.png} 
+	\end{tabular}
+\end{frame}
 
-\item<3->Construct $f_{\text{bump}} \in \cf$, as tall as you like; note that $A(0,\varepsilon) = A(f_{\text{bump}},\varepsilon)$
+\begin{frame}
+\frametitle{Example Bases}
+\vspace{-3ex}
+	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_0.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_3.png}  &
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_4.png} 
+	\tabularnewline[-7ex]
+	Legendre
+	\tabularnewline
+	\tabularnewline
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_3.png} 
+\tabularnewline[0ex]
+		\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_0.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_3.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_4.png} 
+\tabularnewline[-7ex]
+Chebyshev \tabularnewline
+\tabularnewline
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_3.png} 
+	\end{tabular}
+\end{frame}
 
-	\item<4->  Since $\int_0^1 0 \, \dif x$ and $\int_0^1 f_{\text{bump}}(x) \, \dif x$ are so different, $A$ cannot be successful
-
-\end{itemize}
-
-	&
-	\only<2>{\includegraphics[width=5cm]{ProgramsImages/ZeroFun.eps}}
-	\only<3->{\includegraphics[width=5cm]{ProgramsImages/QuadHump.eps}}
-\end{tabular}
+\begin{frame}{Series Spaces}
 
@@
 
-\uncover<5->{Why doesn't this argument hold for $\cf = \{f :\norm[1]{f''} \le \rho \}  \medscoop$? \\  \uncover<6->{Because $f_{\text{bump}} \notin \medscoop$}}
+\begin{align*}
+    \cf &:= \left \{ f = \sum_{\vi \in \cn} \hf(\vi) u_{\vi} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vi)}}{\lambda_{\vi}} \right)_{\vi \in \cn}} \right \} \\
+    \cg &: = \left \{ g = \sum_{\vi \in \cn} \hg(\vi) v_{\vi} : \norm[\cg]{g} := \bignorm[t]{\hg}\right \}, \qquad S(u_{\vi}) = v_{\vi}, \\
+    \text{E.g., } & \text{ Function recovery: } S(u_{\vi}) = u_{\vi} = v_{\vi} \\
+    & \text{ Integration: } S(u_{\vi}) = \int_{[0,1]^d} u_\vi (\vx) \, \dif \vx  = v_\vi\\
+    \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vi \in \cn} \bigabs{\hf(\vi)} \norm[\cg]{v_\vi - \Sapp(u_{\vi},n)}
+\end{align*}
+If $\gamma_{\vi_1} \ge \gamma_{\vi_2} \ge \cdots$, then $S_{\textup{app},n}(f) = \sum_{j=1}^n \hf(\vi_j) v_{\vi_j}$ is an optimal building block, and 
+\begin{equation*}
+    \norm[t]{S(f) - S_{\textup{app},n}(f)} = \Bignorm[r']{\left(\hf(\vi_j)\right)_{j=n+1}^{\infty}} \le \bignorm[r,\vgamma]{\hf} \Bignorm[qq'/(q-q')]{\left(\gamma_{\vi_j}\right)_{j=n+1}^{\infty}}
+\end{equation*}
 
@@
 
-\section{Optimality}
-
-\begin{frame}
-\frametitle{Is Trapezoidal Rule the Best Algorithm?}
-\vspace{-4ex}
-Let $\cost(A,f,\varepsilon)$ denote the number of function values, $n$ required for $A(f,\varepsilon)$ and 
-\[
-\cost(A,\cf,\varepsilon) = \sup_{f \in \cf} \cost(A,f,\varepsilon)
-\]
-For our trapezoidal rule algorithm, $A$
-\[
-\cost(A,\cf,\varepsilon) =  \cost(A,f,\varepsilon) = \left \lceil \sqrt{\frac{\rho}{8\varepsilon}} \right \rceil = \Order\left(\sqrt{ \frac{\rho}{\varepsilon}} \right) \qquad \forall f \in \cf = \{f :\norm[1]{f''} \le \rho \}  \medscoop
-\]
-This is the \alert{(up to a constant)} the smallest possible cost \uncover<2->{for integrands in $\cf = \{f :\norm[1]{f''} \le \rho \}  \medscoop$, no worse than Simpson's rule, Gauss rules, etc.}
-\end{frame}
-
-\finalthanksnote{Slides available on SpeakerDeck at
-	\href{https://speakerdeck.com/fjhickernell/matrix-week-two-2018-june}
-	{\nolinkurl{speakerdeck.com/fjhickernell/matrix-week-two-2018-june}}
-}
-
-\begin{frame}
-\frametitle{Why the Trapezoidal Rule Is Optimal for $\cf = \{f :\norm[1]{f''} < \rho \}$}
-\vspace{-3ex}
-Let $A$ be \alert{any} algorithm satisfying
-\[
-\abs{\int_0^1 f(x) \, \dif x - A(f,\varepsilon)} \le \varepsilon \quad \forall f \in \cf= \{f :\norm[1]{f''} < \rho \}, \, \varepsilon > 0
-\]
-
-\vspace{-5ex}
-\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
-	\begin{itemize}
-		\item<2->Observe where $A(0,\varepsilon)$ gets function values
-
-		\item<3->Construct $f_{\text{bump}} \in \cf$; note that $A(0,\varepsilon) = A(f_{\text{bump}},\varepsilon) = A(-f_{\text{bump}},\varepsilon)$
-
-		\item<4->  For $A$ to succeed for $\pm f_{\text{bump}} $, which have different integrals, one must have 
-		\[
-		\cost(A,\cf,\varepsilon) =  \Order\left(\sqrt{ \frac{\rho}{\varepsilon}} \right)
-		\]
-		the same as the trapezoidal rule algorithm.
-
-	\end{itemize}
-
-	&
-	\only<2>{\includegraphics[width=5cm]{ProgramsImages/ZeroFun.eps}}
-	\only<3->{\includegraphics[width=5cm]{ProgramsImages/TwoQuadHump.eps}}
-\end{tabular}
-
-\vspace{-5ex}
-
-\uncover<5->{Why do your instructors tell you that other algorithms are \alert{better than the trapezoidal rule}?
-\\  \uncover<6->{They are only better when you assume that the integrand has \alert{more smoothness}}}
+\begin{frame}{Cones that Make Sense for Series Spaces}
+\begin{gather*}
+    \cf := \left \{ f = \sum_{\vi \in \cn} \hf(\vi) u_{\vi} : \norm[\cf]{f} := \bignorm[q,\vgamma]{\hf} : = \norm[q]{\left(\frac{\bigabs{\hf(\vi)}}{\gamma_{\vi}} \right)_{\vi \in \cn}} \right \} \\
+    \cg : = \left \{ g = \sum_{\vi \in \cn} \hg(\vi) v_{\vi} : \norm[\cg]{g} := \bignorm[q']{\hg}\right \}, \qquad S(u_{\vi}) = v_{\vi}, \\
+    \text{If } \gamma_{\vi_1} \ge \gamma_{\vi_2} \ge \cdots, \text{ then } \hS_n(f) = \sum_{j=1}^n \hf(\vi_j) v_{\vi_j} \text{ is a good buidling block} \\
+    \text{E.g., Function recovery: } S(u_{\vi}) = u_{\vi} = v_{\vi}
+\end{gather*}
 
 \end{frame}
-
-\section{Adaptive Algorithms}
-
-\begin{frame}
-\frametitle{The Impracticality of Our Non-Adaptive Trapezoidal Rule Algorithm}
-\vspace{-7ex}
-\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
-\begin{gather*}
-T_n(f)=\frac{1}{n}\left[\frac{f(0)}{2} + f\left(\frac{1}{n}\right) + \cdots + f\left(\frac{n-1}{n}\right) +  \frac{f(1)}{2} \right] \\
-A(f,\varepsilon) = T_n(f) \quad \text{where }n = \left \lceil \sqrt{\frac{\rho}{8\varepsilon}} \, \right \rceil
-\end{gather*}
-
-\vspace{-2ex}
-\begin{itemize}
-	\item \alert{Solves} the integration problem for  $\cf = \{f :\norm[1]{f''} \le \rho \}$  \medscoop
-
-	\item \alert{Costs} $\Order(\sqrt{\rho/\varepsilon})$ function values
-
-	\item Is \alert{optimal} for $\cf = \{f :\norm[1]{f''} \le \rho \}$  \medscoop
-\end{itemize}
-	& 
-	\includegraphics[width=5cm]{ProgramsImages/traprule-4.eps}\\$T_{50}(f)=0.3957$
-\end{tabular}
-What more could we want?
-
-\uncover<2>{An algorithm that costs  $\Order(\sqrt{\norm[1]{f''}/\varepsilon})$  without needing to know  $\norm[1]{f''}$; \alert{cost depends on difficulty}}
-\end{frame}
-
-\begin{frame}
-\frametitle{Adaptive Algorithms Don't Work for Balls, But May Work for Cones}
-\vspace{-3ex}
-
-\alert{Adptive} algorithms expend effort comensurate with the difficulty of the problem
-
-\vspace{-3ex}
-\begin{itemize}
-
-	\item If $\cf = \medscoop$, then non-adaptive algorithms are optimal because $\medscoop$ is 
-	\begin{description}
-
-		\item[Balanced:] $f \in \cf \implies -f \in \cf$, and
-
-		\item[Convex:] $f, g \in \cf \implies \theta \cf + (1 - \theta) g \in \cf$ for $0 \le \theta \le 1$
-
-\end{description}
-
-\end{itemize}
-
-\vspace{-3ex}
-
-\begin{tabular}{>{\raggedright}m{0.6\textwidth}@{\qquad}>{\centering}m{0.37\textwidth}}
-	\begin{itemize}
-		\item<2-> However, adaptive algorithms may be optimal for non-convex $\cf = \medcone$ ($f \in \cf \implies cf \in \cf$)
-
-	\item<3-> We developed an adaptive trapezoidal rule that \alert{optimally solves} the integral for $\cf = \medcone$, a set of functions where the true curvature is not much more than its numerical approximation\footfullcite{HicEtal14b}
-
-	\item<4-> Common adaptive algorithms in use \alert{have no theory}
-	\end{itemize}
-	& 
-	\includegraphics[width=5cm]{ProgramsImages/traprule-4.eps}
-\end{tabular}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Adaptive Algorithms Don't Work for Balls, But May Work for Cones}
-\vspace{-3ex}
-
-We also developed adaptive algorithms for
-
-\vspace{-3ex}
-\begin{itemize}
-
-	\item Univariate integration by Simpson's rule\footfullcite{Zha18a}
-
-	\item Univariate function approximation and optimization\footfullcite{ChoEtal17a}
-
-	\item Multivariate integration\footfullcite{HicEtal14a,HicJim16a,RatHic19a}
-
-\end{itemize}
-
-\vspace{-3ex}
-
-made available in the Guaranteed Automatic Integration Library (GAIL)\footfullcite{ChoEtal17b}
-
-\end{frame}
-
-\section{Open Problems}
-
-\begin{frame}
-\frametitle{Work to Be Done}
-
-\vspace{-5ex}
-\begin{itemize}
-
-	\item Find $\cf = \medcone$ for which MATLAB's\footfullcite{MAT9.5} \alert{\mcode{integral_g}} or \alert{Chebfun}\footfullcite{TrefEtal17a} are guaranteed to solve the integration problem
-
-	\item \alert{Locally} adaptive univariate integration
-
-	\item Higher order \alert{function approximation}
-
-	\item Adaptive \alert{multi-level Monte Carlo} methods\footfullcite{Gil15a}
-
-	\item Adaptive multivariate \alert{function approximation}\footfullcite{DinHic20a}
-
-	\item Other error criteria, such as \alert{relative error} or a hybrid of absolute and relative error\footfullcite{HicEtal17a}
-
-	\item Combining our software efforts with that of other research groups
-
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Other Opportunities for You}
-
-\begin{itemize}
-	\item Join the Society for Industrial and Applied Mathematics (SIAM) for free \beamerbutton{\href{https://www.siam.org/Membership/Join-SIAM/Individual-Members/Student}{Click here}}
-
-	\item Join the American Statististcal Association (ASA) for \$25 per year  \beamerbutton{\href{https://www.amstat.org/ASA/JoinRenew/JoinMemberType.aspx?membertype=IREG}{Click here}}
-\end{itemize}
-\end{frame}
-
-\finalthanksnote{Slides available on SpeakerDeck at
-	\href{https://speakerdeck.com/fjhickernell/can-we-solve-it-if-so-how-fast}
-	{\nolinkurl{speakerdeck.com/fjhickernell/can-we-solve-it-if-so-how-fast}}
-}
 
@@
 
+\section{Bonus}
+\begin{frame}[label = VectorSpaceThmProof]{Proof of Theorem for Solvability on a Vector Space}
+
+\vspace{-3ex}
+
+Let the cone $\cc$ be a \alert{vector space} and let
+
+\vspace{-3ex}
+\begin{itemize}
+    \item $A$ be a successful algorithm
+
+    \item $\varepsilon > 0$ be any positive tolerance
+
+    \item  $\{L_1, \ldots, L_{M}\} \subset \Lambda$ be the linear functionals used by $A(0,\varepsilon)$, and
+
+    \item  $\{L_1, \ldots, L_m\}$ be a basis for $\spann(\{L_1, \ldots, L_{M}\})$
+
+    \item $n  = \min(m,\dim(\cc))$
+
+        \item $\{f_1, \ldots, f_n\} \subset \cc$ satisfy $L_i(f_j) = \delta_{i,j}$, $i =1, \ldots, n$, $j=1, \ldots, m$
+\end{itemize}
+
+\vspace{-2ex}
+
+For any $f \in \cc$, let $\tf = f- \sum_{i=1}^n L_i(f) f_i$, and note that $L_j(\tf) = 0$ for $j =1, \ldots, M$.
+Thus, $A(\tf,\varepsilon) = A(0,\varepsilon)$, and so by the \hyperlink{ZeroCorollary}{\beamergotobutton{Corollary}},
+\[
+0 = S(\tf) = S(f) - \sum_{i=1}^n L_i(f) S(f_i), \qquad \text{which implies } S(f) = \sum_{i=1}^n L_i(f) S(f_i)
+\]
+
+\vspace{-3ex}
+    \hyperlink{VectorSpaceThm}{\beamerreturnbutton{Back}}
+\end{frame}
+
 \end{document}

### 2018-11-02 RICAM2018NovTalk.tex
Updating changes
adding

@@
 &
-\vspace{-5ex}
+\vspace{-7ex}
 \alert{Successful algorithms}
@@
 \begin{gather*}
-    \app(f,\varepsilon) = \Sapp(f,n) = \sum_{i=1}^n f(\vx_i) g_i, \quad g_i \in \cg \\
-    \app(f,\varepsilon) = \Sapp(f,n) = \sum_{i=1}^n \hf_i g_i, \quad g_i \in \cg \\
-    \app(f,\varepsilon) = \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i, \quad g_i \in \cg \\
+    \Sapp(f,n) = \sum_{i=1}^n f(\vx_i) g_i, \quad g_i \in \cg \\
+    \Sapp(f,n) = \sum_{i=1}^n \hf_i g_i, \quad g_i \in \cg \\
+    \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i, \quad g_i \in \cg \\
 \end{gather*}
@@
 \vspace{-5ex}
-\hfill \hfill \alert{$n = ?$, $\cc$ is not a ball}
+\hfill \hfill \alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}\newline
+\phantom{a} \hfill \hfill \alert{$\cc$ is not a ball}
 
@@
 \end{tabular}
+answer those who like balls
 
@@
 	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_0.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_3.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_4.png} 
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_0.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_3.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_4.png} 
 	\tabularnewline[-7ex]
-	Legendre
+	Cosine \& Sine
 	\tabularnewline
 	\tabularnewline
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_3.png} 
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_3.png} 
 \tabularnewline[0ex]
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_0.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_3.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_4.png} 
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_0.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_4.png} 
 \tabularnewline[-7ex]
-Chebyshev \tabularnewline
+Walsh \tabularnewline
 \tabularnewline
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_3.png} 
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_3.png} 
 	\end{tabular}
@@
 	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_0.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_3.png}  &
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_4.png} 
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_0.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_3.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_4.png} 
 	\tabularnewline[-7ex]
@@
 	\tabularnewline
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Legendre_Degree_2_3.png} 
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_3.png} 
 \tabularnewline[0ex]
-		\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_0.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_3.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_4.png} 
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_0.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_4.png} 
 \tabularnewline[-7ex]
@@
 \tabularnewline
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{FourierSampling/Chebyshev_Degree_2_3.png} 
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_3.png} 
 	\end{tabular}
@@
 
-\begin{frame}{Series Spaces}
+\begin{frame}{Integration Using Function Values \footfullcite{HicJim16a,JimHic16a}}
 
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vi \in \cn} \hf(\vi) u_{\vi} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vi)}}{\lambda_{\vi}} \right)_{\vi \in \cn}} \right \} \\
-    \cg &: = \left \{ g = \sum_{\vi \in \cn} \hg(\vi) v_{\vi} : \norm[\cg]{g} := \bignorm[t]{\hg}\right \}, \qquad S(u_{\vi}) = v_{\vi}, \\
-    \text{E.g., } & \text{ Function recovery: } S(u_{\vi}) = u_{\vi} = v_{\vi} \\
-    & \text{ Integration: } S(u_{\vi}) = \int_{[0,1]^d} u_\vi (\vx) \, \dif \vx  = v_\vi\\
-    \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vi \in \cn} \bigabs{\hf(\vi)} \norm[\cg]{v_\vi - \Sapp(u_{\vi},n)}
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \}\\
+    u_{\vj} &= \text{Walsh or Cosine/Sine} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
+    \Sapp(f,n) &= \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj), \qquad \{\vx_i\}_{i=1}^n = \text{net or lattice} \quad   \\
+    \abs{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \text{dual set}} \bigabs{\hf(\vj)}
 \end{align*}
-If $\gamma_{\vi_1} \ge \gamma_{\vi_2} \ge \cdots$, then $S_{\textup{app},n}(f) = \sum_{j=1}^n \hf(\vi_j) v_{\vi_j}$ is an optimal building block, and 
-\begin{equation*}
-    \norm[t]{S(f) - S_{\textup{app},n}(f)} = \Bignorm[r']{\left(\hf(\vi_j)\right)_{j=n+1}^{\infty}} \le \bignorm[r,\vgamma]{\hf} \Bignorm[qq'/(q-q')]{\left(\gamma_{\vi_j}\right)_{j=n+1}^{\infty}}
-\end{equation*}
 
@@
 
+\begin{frame}{But I Like Balls \smallscoop!}
+
+\vspace{-5ex}
+How might you construct an adaptive algorithm if you insist on using \alert{balls}?
+
+\vspace{-2ex}
+\begin{description}
+    \item[Step 1] Start with a default radius $\rho$, and assume input $f \in \cb_{\rho}$
+
+    \item[Step 2] Choose $n$ large enough so that 
+    \[
+    \norm[\cg]{S(f) - \Sapp(f,n)} \le \varepsilon \qquad \forall f \in \cb_{\rho}, \qquad \text{where } \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i
+    \]
+
+    \item[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$.
+
+    \item[Step 4]  If $C\bignorm[\cf]{\tf} \le \rho$ for some preset inflation factor, $C$, then return $A(f,\varepsilon) = \Sapp(f,n)$.
+Otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2.
+\end{description}
+
+\vspace{-2ex}
+
+This algorithm succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.
+
+\end{frame}
+
 \end{document}

### 2018-11-03 degruyter-proceedings/DingHickKritzMakRICAMChap.tex
Proceedings beginning

\documentclass[USenglish]{article}

\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}[2017/03/31]%(only for the luatex or the xetex engine)
\usepackage[small]{dgruyter}
\usepackage{microtype}

\begin{document}

  \articletype{...}

  \author*[1]{Yuhan Ding}
  \author[2]{Fred J. Hickernell}
  \author[3]{Peter Krtizer} 
  \author[4]{Simon Mak}
  \runningauthor{...}
  \affil[1]{...}
  \affil[2]{...}
  \title{...}
  \runningtitle{...}
  \subtitle{...}
  \abstract{...}
  \keywords{...}
  \classification[PACS]{...}
  \communicated{...}
  \dedication{...}
  \received{...}
  \accepted{...}
  \journalname{...}
  \journalyear{...}
  \journalvolume{..}
  \journalissue{..}
  \startpage{1}
  \aop
  \DOI{...}

\maketitle

\section{A section}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
  tincidunt.

  Cras dapibus. Vivamus elementum semper nisi. Aenean vulputate eleifend tellus. Aenean
  leo ligula, porttitor eu, consequat vitae, eleifend ac, enim. Aliquam lorem ante, dapibus in,
  viverra quis, feugiat a, tellus. Phasellus viverra nulla ut metus varius laoreet. Quisque
  rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies
  nisi. Nam eget dui. Etiam rhoncus. Maecenas tempus, tellus eget condimentum rhoncus, sem quam
  semper libero, sit amet adipiscing sem neque sed ipsum. Nam quam nunc, blandit vel, luctus
  pulvinar, hendrerit id, lorem. Maecenas nec odio et ante tincidunt tempus. Donec vitae sapien ut
  libero venenatis faucibus. Nullam quis ante. Etiam sit amet orci eget eros faucibus
  tincidunt. Duis leo. Sed fringilla mauris sit amet nibh. Donec sodales sagittis magna. Sed
  consequat, leo eget bibendum sodales, augue velit cursus nunc,

\section{Another section}

\subsection{A subsection}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
  tincidunt.

  Cras dapibus. Vivamus elementum semper nisi. Aenean vulputate eleifend tellus. Aenean
  leo ligula, porttitor eu, consequat vitae, eleifend ac, enim. Aliquam lorem ante, dapibus in,
  viverra quis, feugiat a, tellus. Phasellus viverra nulla ut metus varius laoreet. Quisque
  rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies
  nisi. Nam eget dui. Etiam rhoncus. Maecenas tempus, tellus eget condimentum rhoncus, sem quam
  semper libero, sit amet adipiscing sem neque sed ipsum. Nam quam nunc, blandit vel, luctus
  pulvinar, hendrerit id, lorem. Maecenas nec odio et ante tincidunt tempus. Donec vitae sapien ut
  libero venenatis faucibus. Nullam quis ante. Etiam sit amet orci eget eros faucibus
  tincidunt. Duis leo. Sed fringilla mauris sit amet nibh. Donec sodales sagittis magna. Sed
  consequat, leo eget bibendum sodales, augue velit cursus nunc,

\subsection{Another subsection}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
  tincidunt.

  Cras dapibus. Vivamus elementum semper nisi. Aenean vulputate eleifend tellus. Aenean
  leo ligula, porttitor eu, consequat vitae, eleifend ac, enim. Aliquam lorem ante, dapibus in,
  viverra quis, feugiat a, tellus. Phasellus viverra nulla ut metus varius laoreet. Quisque
  rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies
  nisi. Nam eget dui. Etiam rhoncus. Maecenas tempus, tellus eget condimentum rhoncus, sem quam
  semper libero, sit amet adipiscing sem neque sed ipsum. Nam quam nunc, blandit vel, luctus
  pulvinar, hendrerit id, lorem. Maecenas nec odio et ante tincidunt tempus. Donec vitae sapien ut
  libero venenatis faucibus. Nullam quis ante. Etiam sit amet orci eget eros faucibus
  tincidunt. Duis leo. Sed fringilla mauris sit amet nibh. Donec sodales sagittis magna. Sed
  consequat, leo eget bibendum sodales, augue velit cursus nunc,

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
  tincidunt.

\begin{acknowledgement}
  ...
\end{acknowledgement}

%\bibliographystyle{...}
%\bibliography{...}
\end{document}

### 2018-11-03 RICAM2018NovTalk.tex

@@
 
-\begin{frame}{Cones}
+\begin{frame}[label = ConeFrame]{Cones}
 \vspace{-4ex}
@@
 \end{tabular}
-answer those who like balls
 
@@
     \item Union of \alert{cones} is a \alert{cone}
+
+    \item \hyperlink{BallsWontHelp}{\beamergotobutton{But I really like balls!}}
 \end{itemize}
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \\
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
     \cg &: = \left \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\right \}, \qquad S(u_{\vj}) = v_{\vj}, \\
@@
     \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
-    \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
+    % \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
 \end{align*}
 
-\end{frame}
+\vspace{-7ex}
+\alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}
 
-\begin{frame}
-\frametitle{Example Bases}
-\vspace{-3ex}
-	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_0.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_3.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_4.png} 
-	\tabularnewline[-7ex]
-	Cosine \& Sine
-	\tabularnewline
-	\tabularnewline
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_3.png} 
-\tabularnewline[0ex]
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_0.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_3.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_4.png} 
-\tabularnewline[-7ex]
-Walsh \tabularnewline
-\tabularnewline
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_3.png} 
-	\end{tabular}
 \end{frame}
@@
 
+\section{Integration}
+
+\begin{frame}
+\frametitle{Complex Exponential and Walsh Bases}
+\vspace{-3ex}
+	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_0.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_3.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_4.png} 
+	\tabularnewline[-7ex]
+	Cosine \& Sine
+	\tabularnewline
+	\tabularnewline
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/CosineSine_Degree_2_3.png} 
+\tabularnewline[0ex]
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_0.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_4.png} 
+\tabularnewline[-7ex]
+Walsh \tabularnewline
+\tabularnewline
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Walsh_Degree_2_3.png} 
+	\end{tabular}
+\end{frame}
+
 \begin{frame}{Integration Using Function Values \footfullcite{HicJim16a,JimHic16a}}
 
-\vspace{-5ex}
+\vspace{-7ex}
 
@@
     \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \}\\
-    u_{\vj} &= \text{Walsh or Cosine/Sine} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
-    \Sapp(f,n) &= \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj), \qquad \{\vx_i\}_{i=1}^n = \text{net or lattice} \quad   \\
-    \abs{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \text{dual set}} \bigabs{\hf(\vj)}
+    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
+    \Sapp(f,n) &= \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj), \qquad \{\vx_i\}_{i=1}^n = \text{lattice or net} \quad   \\
+    &\abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
 \end{align*}
@@
 
-\begin{frame}{But I Like Balls \smallscoop!}
+\begin{frame}[label = BallsWontHelp]{But I Like Balls \smallscoop!}
 
@@
 This algorithm succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.
+\hyperlink{ConeFrame}{\beamerreturnbutton{Back}}
 

### 2018-11-03 RICAM2018NovTalk.tex
Updates from ShareLaTeX
edits

@@
     u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
-    \Sapp(f,n) &= \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj), \qquad \{\vx_i\}_{i=1}^n = \text{lattice or net} \quad   \\
-    &\abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
+    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
+    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
+    \end{array}
+    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/LatTwo12.eps} \qquad
+    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
+\end{align*}
+
+\end{frame}
+
+\begin{frame}{Integration Using Function Values (cont'd)}
+
+\vspace{-7ex}
+
+\begin{align*}
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \}\\
+    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
+    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
+    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
+    \end{array}
+    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
+    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
 \end{align*}

### 2018-11-03 RICAM2018NovTalk.tex
Editing and expanding

@@
 \newcommand{\LambdaAll}{\Lambda^{\textup{all}}}
-\DeclareMathOperator{\spann}{span}
+%\DeclareMathOperator{\spann}{span}
 %\DeclareMathOperator{\app}{app}
@@
 
-    \item \hyperlink{BallsWontHelp}{\beamergotobutton{But I really like balls!}}
+    \item \hyperlink{BallsWontHelp}{\beamergotobutton{``But I really like balls!''}}
 \end{itemize}
@@
 
+\begin{frame}{Integration Using Function Values\footfullcite{DicEtal14a}}
+
+\vspace{-7ex}
+
+\begin{align*}
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
+    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
+    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]
+    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
+    \end{array}
+    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
+    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
+\end{align*}
+
+\end{frame}
+
 \begin{frame}{Integration Using Function Values \footfullcite{HicJim16a,JimHic16a}}
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \}\\
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
     u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
@@
 \end{frame}
+
+\section{General Problems}
 
@@
 
-\begin{frame}[label = BallsWontHelp]{But I Like Balls \smallscoop!}
+\begin{frame}[label = BallsWontHelp]{``But I Like Balls \smallscoop!''}
 
@@
     \item[Step 2] Choose $n$ large enough so that
-    \[
-    \norm[\cg]{S(f) - \Sapp(f,n)} \le \varepsilon \qquad \forall f \in \cb_{\rho}, \qquad \text{where } \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i
-    \]
 
-    \item[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$.
+    \vspace{-4ex}
+    \begin{multline*}
+     \norm[\cg]{S(f) - \Sapp(f,n)} \le \norm[\cf\to \cg]{S - \Sapp(\cdot,n)} \rho \le \varepsilon \\
+         \text{where } \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i
+    \end{multline*}
 
-    \item[Step 4]  If $C\bignorm[\cf]{\tf} \le \rho$ for some preset inflation factor, $C$, then return $A(f,\varepsilon) = \Sapp(f,n)$.
-Otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2.
+    \vspace{-2ex}
+
+    \item<2>[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$
+
+    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{\tf} \le \rho$ for some preset \alert{inflation} factor, $C$, }then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2}
 \end{description}
@@
 
-This algorithm succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.
-\hyperlink{ConeFrame}{\beamerreturnbutton{Back}}
+\uncover<2>{This succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.
+\hyperlink{ConeFrame}{\beamerreturnbutton{Back}}}
 

### 2018-11-03 RICAM2018NovTalk.tex

@@
 \vspace{-5ex}
-How might you construct an adaptive algorithm if you insist on using \alert{balls}?
+How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \alert{balls}?
 
@@
 \begin{description}
-    \item[Step 1] Start with a default radius $\rho$, and assume input $f \in \cb_{\rho}$
+    \item[Step 1] Pick with a default radius $\rho$, and \alert{assume} input $f \in \cb_{\rho}$
 
-    \item[Step 2] Choose $n$ large enough so that
+    \item[Step 2] Choose $n$ \alert{large enough} so that
 

### 2018-11-04 RICAM2018NovTalk.tex
last revise for going to airport
editing

@@
 
-\begin{frame}{Integration Using Function Values \footfullcite{HicJim16a,JimHic16a}}
+\begin{frame}{Cones of Integrands \footfullcite{HicJim16a,JimHic16a}}
 
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \}\\
-    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
-    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
+n_0 & = 0, \quad n_k = 2^{k-1}, \ k \in \naturals, \qquad \vj \text{ ordered}\\
+	 \sigma_k(f) & = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \qquad  \hsigma_{\ell,k}(f)  = \sum_{i=n_{\ell-1}+1}^{n_\ell}  \sum_{m=1}^{\infty} \bigabs{\hf(\vj_{i+mn_{k}})},\\
+	 \cc &: = \left\{f \in \cf :  \sigma_k(f) \le a b^{k - \ell}\sigma_\ell(f), \   \hsigma_{\ell,k}(f) \le \sigma_k(f) \right\} \\
+      &\begin{array}{l}\Sapp(f,n_k) = \frac 1{n_k} \sum_{i=1}^{n_k} f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
     \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
     \end{array}
-    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/LatTwo12.eps} \qquad
-    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
 \end{align*}
@@
 
+\begin{frame}{Asian Option Pricing}
+\end{frame}
+
 \section{General Problems}
@@
 \end{frame}
+
+\finalthanksnote{These slides are  available at \\  \href{https://speakerdeck.com/fjhickernell/samsi-qmc-transition-2018-may}{\nolinkurl{speakerdeck.com/fjhickernell/samsi-qmc-transition-2018-may}}}
 

### 2018-11-04 RICAM2018NovTalk.tex

@@
 
-\begin{frame}
-\frametitle{Example Bases}
-\vspace{-3ex}
-	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_0.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_3.png}  &
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_4.png} 
-	\tabularnewline[-7ex]
-	Legendre
-	\tabularnewline
-	\tabularnewline
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_3.png} 
-\tabularnewline[0ex]
-		\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_0.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_3.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_4.png} 
-\tabularnewline[-7ex]
-Chebyshev \tabularnewline
-\tabularnewline
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_1.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_3.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_2.png}  &
-\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_3.png} 
-	\end{tabular}
-\end{frame}
-
 \section{Integration}
 
-\begin{frame}
-\frametitle{Complex Exponential and Walsh Bases}
+\begin{frame}{Complex Exponential and Walsh Bases}
 \vspace{-3ex}
@@
 
-\begin{frame}{Cones of Integrands \footfullcite{HicJim16a,JimHic16a}}
+\begin{frame}{Cones of Integrands Whose Fourier Coefficients Decay Steadily\footfullcite{HicJim16a,JimHic16a}}
 
@@
 \begin{align*}
-n_0 & = 0, \quad n_k = 2^{k-1}, \ k \in \naturals, \qquad \vj \text{ ordered}\\
-	 \sigma_k(f) & = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \qquad  \hsigma_{\ell,k}(f)  = \sum_{i=n_{\ell-1}+1}^{n_\ell}  \sum_{m=1}^{\infty} \bigabs{\hf(\vj_{i+mn_{k}})},\\
-	 \cc &: = \left\{f \in \cf :  \sigma_k(f) \le a b^{k - \ell}\sigma_\ell(f), \   \hsigma_{\ell,k}(f) \le \sigma_k(f) \right\} \\
+n_0 & = 0, \quad n_k = 2^{k-1}, \ k \in \naturals, \qquad \vj \text{ ordered}, \quad \text{true coef.} = \tf(\vj) \approx \tf_{\text{disc}}(\vj) = \text{discrete coef.}\\
+	 \sigma_k(f) & = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad  \hsigma_{k,\ell}(f)  = \sum_{i=n_{k-1}+1}^{n_k} \sum_{m=1}^{\infty} \bigabs{\hf(\vj_{i+mn_{\ell}})}, \quad \sigma_{\textup{disc},k}(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf_{\text{disc}}(\vj_i)} \\
+	 \cc &: = \left\{f \in \cf :  
+	 \sigma_\ell(f) \le a_1 b_1^{\ell - k}\sigma_k(f), \   \hsigma_{k,\ell}(f) \le a_2 b_2^{\ell - k} \sigma_\ell(f) \quad \forall k \le \ell \right\} \quad a_1, a_2 > 1 > b_1, b_2\\
       &\begin{array}{l}\Sapp(f,n_k) = \frac 1{n_k} \sum_{i=1}^{n_k} f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
-    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
+    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)} \le C(k) \sigma_{\textup{disc},k}(f)
     \end{array}
 \end{align*}
+
+\end{frame}
+
+\begin{frame}{ Option Pricing\footfullcite{ChoEtal17b}}
+\vspace{-12ex}
+\begin{tabular}{m{11cm}m{2.5cm}}
+	\[
+	\begin{aligned}
+	 \text{fair price} = 
+	\int_{\reals^d}\me^{-r T}\max\left(\frac{1}{d}\sum_{j=1}^d S_{j}-K, 0\right) 
+	\frac{\me^{-\vz^T\vz/2}}{(2\pi)^{d/2}}\,\dif \vz \approx \$13.12
+	\end{aligned}
+	\]
+	& 
+	\financePict
+\end{tabular}
+\vspace{-4ex}
+\begin{gather*}
+S_{j} =  S_0\me^{(r-\sigma^2/2)jT/d+\sigma x_j} = \text{stock price at time } 
+jT/d, \\
+\vx  = \mA \vz, \quad \mA \mA^T = \mSigma = \Bigl ( \min(i,j) T/d \Bigr) _{i,j = 1}^d,
+\quad T = 1/4, \ d=13 \text{ here}
+\end{gather*}
+\begin{equation*}
+\begin{array}{cccccccc}
+\text{Error}& && \text{Median}&& \text{Worst 10\%} & \text{Worst 10\%} \\
+\text{Tolerance} & \multicolumn{2}{c}{\text{Method}}  & \text{Error} & \text{Accuracy} 
+& n & \text{Time (s)} \\
+\toprule
+\input{ProgramsImages/AsianOutput.txt}
+\end{array}
+\end{equation*}
+\vspace{-8ex}
 
@@
 
-\begin{frame}{Asian Option Pricing}
-\end{frame}
-
 \section{General Problems}
@@
 
+\end{frame}
+
+\begin{frame}{Example Bases for Function Approximation}
+\vspace{-3ex}
+	\begin{tabular}{>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}>{\centering}m{0.18\textwidth}}
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_0.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_3.png}  &
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_4.png} 
+	\tabularnewline[-7ex]
+	Legendre
+	\tabularnewline
+	\tabularnewline
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Legendre_Degree_2_3.png} 
+\tabularnewline[0ex]
+		\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_0.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_4.png} 
+\tabularnewline[-7ex]
+Chebyshev \tabularnewline
+\tabularnewline
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_1.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_1_3.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_2.png}  &
+\includegraphics[width =0.18\textwidth]{ProgramsImages/Chebyshev_Degree_2_3.png} 
+	\end{tabular}
 \end{frame}

### 2018-11-04 ProgramsImages/AsianArithMeanOptionAutoOutput.m
data for asian option

@@ -1,0 +1,54 @@
+%% Produce tables of output for Asian Option Fixed Width Example
+function AsianArithMeanOptionAutoOutput
+gail.InitializeWorkspaceDisplay %clean up 
+format long
+
+load PierreAsianCallExampleAllDataA-2R-Inf
+outputMat(1:6,1) = absTol; %relative Tolerance
+outputMat(1:6,2) = ... %median error
+   [errmedAsianCallIIDDiffAuto 
+   errmedAsianCallSobDiffAuto 
+   errmedAsianCallSobPCAAuto 
+   errmedAsianCallSobPCACVAuto
+   errmedAsianCallLatPCAAuto 
+   errmedAsianCallBayesPCAAuto];
+outputMat(1:6,3) = ... %success rate
+   100*[successAsianCallIIDDiffAuto
+   successAsianCallSobDiffAuto
+   successAsianCallSobPCAAuto
+   successAsianCallSobPCACVAuto
+   successAsianCallLatPCAAuto
+   successAsianCallBayesPCAAuto];
+outputMat(1:6,4) = ... %worst n
+   [ntopAsianCallIIDDiffAuto
+   ntopAsianCallSobDiffAuto
+   ntopAsianCallSobPCAAuto
+   ntopAsianCallSobPCACVAuto
+   ntopAsianCallLatPCAAuto
+   ntopAsianCallBayesPCAAuto];
+outputMat(1:6,5) = ... %worst time
+   [timetopAsianCallIIDDiffAuto
+   timetopAsianCallSobDiffAuto
+   timetopAsianCallSobPCAAuto
+   timetopAsianCallSobPCACVAuto
+   timetopAsianCallLatPCAAuto
+   timetopAsianCallBayesPCAAuto];
+
+outputMat = round(outputMat,2,'significant');
+
+if exist('AsianOutput.txt','file')
+   delete AsianOutput.txt
+end
+diary AsianOutput.txt
+disp(gail.cleanString(sprintf('%2.0E & \\text{IID} & \\text{diff} & %3.0E & %3.0f\\%% & %3.1E & %3.3f \\\\',outputMat(1,:))))
[…]

### 2018-11-04 RICAM2018NovTalk.tex
push edits

@@
 
+    \item Philosophy of our algorithms:  \alert{What we cannot observe is not much worse than what we can observe}
+
     \item \hyperlink{BallsWontHelp}{\beamergotobutton{``But I really like balls!''}}
@@
     \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
-    \cg &: = \left \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\right \}, \qquad S(u_{\vj}) = v_{\vj}, \\
+    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
     \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
@@
 
-\begin{frame}{Complex Exponential and Walsh Bases}
+\begin{frame}{Complex Exponential and Walsh Bases for Cubature}
 \vspace{-3ex}
@@
 	 \sigma_\ell(f) \le a_1 b_1^{\ell - k}\sigma_k(f), \   \hsigma_{k,\ell}(f) \le a_2 b_2^{\ell - k} \sigma_\ell(f) \quad \forall k \le \ell \right\} \quad a_1, a_2 > 1 > b_1, b_2\\
-      &\begin{array}{l}\Sapp(f,n_k) = \frac 1{n_k} \sum_{i=1}^{n_k} f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
-    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)} \le C(k) \sigma_{\textup{disc},k}(f)
-    \end{array}
+      \MoveEqLeft{\Sapp(f,n_k) = \frac 1{n_k} \sum_{i=1}^{n_k} f(\vx_i)  \quad
+    \abs{S(f) - \Sapp(f,n_k)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)} \le C(k) \sigma_{\textup{disc},k}(f)} \\
+    \alert{A(f,\varepsilon)} & \alert{= S(f,n_k) \text{ for the smallest $k$ satisfying } C(k) \sigma_{\textup{disc},k}(f) \le \varepsilon}
 \end{align*}
@@
 
-\begin{frame}{Integration Using Function Values (cont'd)}
+\section{General Problems}
+
+\begin{frame}{Solving General Linear Problems Using Series Coefficients\footfullcite{DinHic20a}}
 
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
-    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
-    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i) = \sum_{\vj \in \text{dual set}} \hf(\vj)  \\[4ex]
-    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
-    \end{array}
-    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
-    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[2,\vlambda]{\hf} : = \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
+    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj} \\
+      \lambda_{\vj_1} & \ge \lambda_{\vj_2} \ge \cdots, \qquad
+      n_0 < n_1 < n_2 < \cdots,  \qquad
+ 	\sigma_k(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad k \in \naturals \\
+     \cc &: = \left\{f \in \cf :  
+ 	 \sigma_\ell(f) \le a b^{\ell - k}\sigma_k(f) \quad \forall k \le \ell \right\} \quad a > 1 > b \quad \text{\alert{series coef.\ decay steadily}}\\
+ 	 \Sapp(f,n) &= \sum_{i=1}^n \hf(\vj_i) v_{\vj_i} \text{ is a optimal for fixed }n, \qquad \norm[\cg]{S(f) - \Sapp(f,n)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}}
 \end{align*}
@@
 
-\section{General Problems}
-
-\begin{frame}{Cones that Make Sense for Series Spaces}
-\begin{gather*}
-    \cf := \left \{ f = \sum_{\vi \in \cn} \hf(\vi) u_{\vi} : \norm[\cf]{f} := \bignorm[q,\vgamma]{\hf} : = \norm[q]{\left(\frac{\bigabs{\hf(\vi)}}{\gamma_{\vi}} \right)_{\vi \in \cn}} \right \} \\
-    \cg : = \left \{ g = \sum_{\vi \in \cn} \hg(\vi) v_{\vi} : \norm[\cg]{g} := \bignorm[q']{\hg}\right \}, \qquad S(u_{\vi}) = v_{\vi}, \\
-    \text{If } \gamma_{\vi_1} \ge \gamma_{\vi_2} \ge \cdots, \text{ then } \hS_n(f) = \sum_{j=1}^n \hf(\vi_j) v_{\vi_j} \text{ is a good buidling block} \\
-    \text{E.g., Function recovery: } S(u_{\vi}) = u_{\vi} = v_{\vi}
-\end{gather*}
-
-\end{frame}
-
-\begin{frame}{Example Bases for Function Approximation}
+\begin{frame}{Legendre and Chebyshev Bases for Function Approximation}
 \vspace{-3ex}

### 2018-11-05 RICAM2018NovTalk.tex

@@
 \frame{\titlepage}
+
+\finalthanksnote{
+Thank you all for your participation \\
+\uncover<2>{Thanks to Peter Kritzer and Annette Weihs for doing all the work of organizing}}
+
+\thankyouframe
+
 \section{Introduction}
+
+\begin{frame}{Context for This Talk}
+
+\centerline{
+    \begin{tabular}{rp{0.4\textwidth}@{\qquad}p{0.4\textwidth}}
+    \alert{Henryk} & Many nice tractability results for \medscoop &
+    May we obtain analogous results for \medcone \hspace{7ex} ? \tabularnewline
+    \alert{Houman} & Let's learn the appropriate kernel from the function data & This will only work for nice functions in a \medcone
+    \end{tabular}}
+\end{frame}
 
@@
 \hfill \hfill \alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}\newline
-\phantom{a} \hfill \hfill \alert{$\cc$ is not a ball}
+\phantom{a} \hfill \hfill \alert{$\cc$ is a \smallcone}
 
@@
 
-    \item \alert{Cone} means $f \in \cc \implies af \in \cc$
+    \item \alert{Cone} means $f \in \cc \implies af \in \cc \ \forall a \in \reals$
 
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
     \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
@@
 
+\begin{frame}
+\frametitle{Integrands in $\cc$ Aren't Fuzzy}
+
+\setlength{\figwidth}{0.3\textwidth}
+
+\vspace{-8ex}
+
+\centerline{
+	\includegraphics[width = \figwidth] 
+	{ProgramsImages/FunctionWalshFourierCoeffDecay.eps} \qquad \qquad
+	\includegraphics[width = \figwidth] 
+	{ProgramsImages/FilteredFunctionWalshFourierCoeffDecay.eps} }
+
+\end{frame}
+
 \begin{frame}{ Option Pricing\footfullcite{ChoEtal17b}}
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[2,\vlambda]{\hf} : = \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
+    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[2,\vlambda]{\hf} : = \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
     \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj} \\

### 2018-11-06 RICAM2018NovTalk.tex
trimming

@@
 \vspace{-9ex}
-\uncover<2->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc) \ne \emptyset$
+\uncover<1->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc) \ne \emptyset$
 
@@
 
-\uncover<3->{\alert{Cost}: $\cost(\app,f,\varepsilon) = $ \# of function data
+\uncover<2->{\alert{Cost}: $\cost(\app,f,\varepsilon) = $ \# of function data
 \newline
@@
 
-\uncover<4->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\cc,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}
+\uncover<3->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\cc,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}
 
@@
 
-    \item Union of \alert{cones} is a \alert{cone}
+    %\item Union of \alert{cones} is a \alert{cone}
 
-    \item Philosophy of our algorithms:  \alert{What we cannot observe is not much worse than what we can observe}
+    \item Philosophy:  \alert{What we cannot observe is not much worse than what we can observe}
 
@@
 
-\begin{frame}{Spaces of Inputs and Outputs}
-
-\vspace{-3ex}
-
-We focus on Banach spaces that look like
+\begin{frame}{Inputs and Outputs}
 
 \vspace{-5ex}
-\begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
-    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
-    \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
-    & \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj\\
-    \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
-    % \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
-\end{align*}
-
-\vspace{-7ex}
-\alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}
+\begin{gather*}
+    \text{\alert{Input: }} f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} , \qquad 
+    \text{\alert{Output: }} g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj}, \qquad S(u_{\vj}) = v_{\vj}, \\
+    \text{E.g., Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj}, \qquad
+   \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj \\
+    \text{\alert{Fixed sample size algorithm: }} \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
+    \alert{\app(f,\varepsilon) = \Sapp(f,n) + \text{ stopping criterion}}
+\end{gather*}
 
 \end{frame}
+
+% \begin{frame}{Spaces of Inputs and Outputs}
+
+% \vspace{-3ex}
+
+% We focus on Banach spaces that look like
+
+% \vspace{-5ex}
+% \begin{align*}
+%     \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
+%     \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
+%     \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
+%     & \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj\\
+%     \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
+%     % \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
+% \end{align*}
+
+% \vspace{-7ex}
+% \alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}
+
+% \end{frame}
 
@@
 
-\begin{frame}{Integration Using Function Values\footfullcite{DicEtal14a}}
+\begin{frame}{Integration Using Function Values, $\LambdaStd$\footfullcite{DicEtal14a}}
 
@@
 
-\vspace{-7ex}
+\vspace{-8ex}
 
@@
 
+\vspace{-4ex}
+\alert{Have } $\cost(f,A,\varepsilon)$; \quad \alert{No } $\cost(A,\cc,\varepsilon,\rho)$,  $\comp(\ca(\cc),\varepsilon,\rho)$, or  tractability results \alert{yet}
+
 \end{frame}
@@
 
-\setlength{\figwidth}{0.3\textwidth}
+\setlength{\figwidth}{0.4\textwidth}
 
-\vspace{-8ex}
+\vspace{-6ex}
 
@@
 
-\begin{frame}{Solving General Linear Problems Using Series Coefficients\footfullcite{DinHic20a}}
+\begin{frame}{Solving General Linear Problems Using Series Coefficients, $\LambdaSer$\footfullcite{DinHic20a}}
 
@@
     \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[2,\vlambda]{\hf} : = \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
-    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj} \\
-      \lambda_{\vj_1} & \ge \lambda_{\vj_2} \ge \cdots, \qquad
+    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj} \\[-2ex]
+      & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
       n_0 < n_1 < n_2 < \cdots,  \qquad
@@
  	 \sigma_\ell(f) \le a b^{\ell - k}\sigma_k(f) \quad \forall k \le \ell \right\} \quad a > 1 > b \quad \text{\alert{series coef.\ decay steadily}}\\
- 	 \Sapp(f,n) &= \sum_{i=1}^n \hf(\vj_i) v_{\vj_i} \text{ is a optimal for fixed }n, \qquad \norm[\cg]{S(f) - \Sapp(f,n)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}}
+ 	 \Sapp(f,n) &= \sum_{i=1}^n \hf(\vj_i) v_{\vj_i} \text{ is a optimal for fixed }n, \qquad \norm[\cg]{S(f) - \Sapp(f,n)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}} \\[-1ex]
+ 	 \alert{A(f,\varepsilon)} & \alert{= S(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
 \end{align*}

### 2018-11-06 RICAM2018NovTalk.tex
revising

@@
 
-    \item \hyperlink{BallsWontHelp}{\beamergotobutton{``But I really like balls!''}}
 \end{itemize}
+
+\end{frame}
+
+\begin{frame}[label = BallsWontHelp]{``But I Like Balls \smallscoop!''}
+
+\vspace{-5ex}
+How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \alert{balls}?
+
+\vspace{-2ex}
+\begin{description}
+    \item[Step 1] Pick with a default radius $\rho$, and \alert{assume} input $f \in \cb_{\rho}$
+
+    \item[Step 2] Choose $n$ \alert{large enough} so that
+
+    \vspace{-4ex}
+    \begin{multline*}
+     \norm[\cg]{S(f) - \Sapp(f,n)} \le \norm[\cf\to \cg]{S - \Sapp(\cdot,n)} \rho \le \varepsilon \\
+         \text{where } \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i
+    \end{multline*}
+
+    \vspace{-2ex}
+
+    \item<2>[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$
+
+    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{\tf} \le \rho$ for some preset \alert{inflation} factor, $C$, }then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2}
+\end{description}
+
+\vspace{-2ex}
+
+\uncover<2>{This succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.
+\hyperlink{ConeFrame}{\beamerreturnbutton{Back}}}
 
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[1,\vlambda]{\hf} : = \norm[1]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractabililty}\end{minipage}\\
-    u_{\vj} &= \text{Cosine/Sine or Walsh} \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}, \qquad \cg : = \reals \\
+    f &= \sum_{\vj \in \cn} \hf(\vj) u_{\vj}, \qquad
+    u_{\vj} = \text{Cosine/Sine or Walsh}, \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}\\
     &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]
@@
 
-\begin{frame}{Cones of Integrands Whose Fourier Coefficients Decay Steadily\footfullcite{HicJim16a,JimHic16a}}
+\begin{frame}{Cones of Integrands Whose Fourier Series Coefficients Decay Steadily\footfullcite{HicJim16a,JimHic16a}}
 
@@
 \begin{align*}
-n_0 & = 0, \quad n_k = 2^{k-1}, \ k \in \naturals, \qquad \vj \text{ ordered}, \quad \text{true coef.} = \tf(\vj) \approx \tf_{\text{disc}}(\vj) = \text{discrete coef.}\\
+n_0 & = 0, \quad n_k = 2^{k-1}, \ k \in \naturals, \qquad \vj \text{ ordered}, \quad \text{true coef.} = \hf(\vj) \approx \tf_{\text{disc}}(\vj) = \text{discrete coef.}\\
 	 \sigma_k(f) & = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad  \hsigma_{k,\ell}(f)  = \sum_{i=n_{k-1}+1}^{n_k} \sum_{m=1}^{\infty} \bigabs{\hf(\vj_{i+mn_{\ell}})}, \quad \sigma_{\textup{disc},k}(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf_{\text{disc}}(\vj_i)} \\
@@
 \vspace{-4ex}
-\alert{Have } $\cost(f,A,\varepsilon)$; \quad \alert{No } $\cost(A,\cc,\varepsilon,\rho)$,  $\comp(\ca(\cc),\varepsilon,\rho)$, or  tractability results \alert{yet}
+\alert{Have} $\cost(f,A,\varepsilon)$; \quad \alert{No} $\cost(A,\cc,\varepsilon,\rho)$,  $\comp(\ca(\cc),\varepsilon,\rho)$, or  tractability results \alert{yet}
 
@@
 \begin{align*}
-    \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[2,\vlambda]{\hf} : = \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
-    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj} \\[-2ex]
+    \only<1>{\cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \norm[2]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
+    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[2]{\hg}\biggr \}, \qquad v_{\vj} = S(u_{\vj}) \\[-2ex]}
       & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
@@
  	 \sigma_\ell(f) \le a b^{\ell - k}\sigma_k(f) \quad \forall k \le \ell \right\} \quad a > 1 > b \quad \text{\alert{series coef.\ decay steadily}}\\
- 	 \Sapp(f,n) &= \sum_{i=1}^n \hf(\vj_i) v_{\vj_i} \text{ is a optimal for fixed }n, \qquad \norm[\cg]{S(f) - \Sapp(f,n)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}} \\[-1ex]
- 	 \alert{A(f,\varepsilon)} & \alert{= S(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
+ 	 \Sapp(f,n_k) &= \sum_{i=1}^{n_k} \hf(\vj_i) v_{\vj_i} \text{ is optimal for fixed }n_k, \qquad \norm[\cg]{S(f) - \Sapp(f,n_k)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}} \\[-1ex]
+ 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
+ 	 \only<2>{\\ 
+ 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) = n_{\ell^\dagger}, \quad 
+ 	 \ell^\dagger \le \min \left \{\ell \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{\ell-1} \frac{b^{2(k-\ell)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{\ell-1}+1}^2}\right]   \right\}}} \\
+ 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) \text{ essentially no worse than } \comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)}}}
+\end{align*}
+
+\end{frame}
+
+\begin{frame}{\emph{Function Approximation} when Function Values Are Expensive}
+
+\vspace{-7ex}
+
+    \begin{align*}
+    \only<1>{\cf &:= \left \{ f = \sum_{\vj \in \natzero^d} \hf(\vj) u_{\vj} : \norm[\cf]{f} :=  \norm[\infty]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
+    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[1]{\hg}\biggr \}, \qquad v_{\vj} = S(u_{\vj}) = u_{\vj} \\[-2ex]}
+    \lambda_{\vj} & = \Gamma_{\norm[0]{\vj}} \prod_{\substack{\ell = 1 \\ j_{\ell} > 0}}^d \gamma_\ell s_{j_\ell} \quad \text{\alert{product, order, and smoothness dependent weights}} \\
+      & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
+      \Sapp(f,n) = \sum_{i=1}^{n} \hf(\vj_i) u_{\vj_i} ,  \qquad
+ 	\sigma_k(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad k \in \naturals \\
+     \cc &: = \left\{f \in \cf :  
+ 	 \sigma_\ell(f) \le a b^{\ell - k}\sigma_k(f) \quad \forall k \le \ell \right\} \quad a > 1 > b \quad \text{\alert{series coef.\ decay steadily}}\\
+ 	 \Sapp(f,n_k) &= \sum_{i=1}^{n_k} \hf(\vj_i) v_{\vj_i} \text{ is optimal for fixed }n_k, \qquad \norm[\cg]{S(f) - \Sapp(f,n_k)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}} \\[-1ex]
+ 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
+ 	 \only<2>{\\ 
+ 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) = n_{\ell^\dagger}, \quad 
+ 	 \ell^\dagger \le \min \left \{\ell \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{\ell-1} \frac{b^{2(k-\ell)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{\ell-1}+1}^2}\right]   \right\}}} \\
+ 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) \text{ essentially no worse than } \comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)}}}
 \end{align*}

### 2018-11-07 RICAM2018NovTalk.tex
revising

@@
 	\newcommand{\smallscoop}{\scoop{1cm}}
-	\newcommand{\medscoop}{\parbox{1.8cm}{\includegraphics[width=1.8cm]{IceCreamScoop.eps}}\xspace}
+	\newcommand{\medscoop}{\scoop{1.8cm}}
 	\newcommand{\largescoop}{\scoop{3cm}}
@@
 
-\begin{frame}{Context for This Talk}
+\begin{frame}{Context}
+
+\vspace{-3ex}
 
 \centerline{
-    \begin{tabular}{rp{0.4\textwidth}@{\qquad}p{0.4\textwidth}}
-    \alert{Henryk} & Many nice tractability results for \medscoop &
-    May we obtain analogous results for \medcone \hspace{7ex} ? \tabularnewline
-    \alert{Houman} & Let's learn the appropriate kernel from the function data & This will only work for nice functions in a \medcone
+    \begin{tabular}{>{\vspace{-1.7ex}\raggedleft}p{0.2\textwidth}@{\qquad}p{0.3\textwidth}@{\qquad}p{0.3\textwidth}}
+    & \alert{Previous talks} & \alert{My reponse} \tabularnewline
+    \toprule
+    \alert{Henryk, Klaus, Greg, Stefan, \ldots} & Many results for $f \in \smallscoop$  &
+    May we obtain analogous results for $f \in \smallcone$? \tabularnewline[2ex]
+    \alert{Houman} & Let's \alert{learn} the appropriate kernel from the function data & Will only work for nice functions in a \smallcone \tabularnewline[2ex]
+    \alert{Paul} & Let's \alert{find} the Lipschitz matrix constant \ldots & Yes, lets learn from the function data \tabularnewline[2ex]
+    \alert{Klaus} & This adaptive algorithm has \alert{no theory}  & We want to construct adaptive algorithms \alert{with theory} \tabularnewline[2ex]
+    \alert{Henryk} & Tractability & Yes! \tabularnewline[2ex]
+    \alert{Greg} & POD weights & Yes!
     \end{tabular}}
@@
 
-    \item<2>[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$
+    \item<2>[Step 3] Let $f_{\textup{min}} \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$
 
-    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{\tf} \le \rho$ for some preset \alert{inflation} factor, $C$, }then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2}
+    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{f_{\textup{min}}} \le \rho$ for some preset \alert{inflation} factor, $C$, }then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; otherwise, choose $\rho = 2C\bignorm[\cf]{f_{\textup{min}}}$, and go to Step 2}
 \end{description}
@@
 
-\uncover<2>{This succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.
-\hyperlink{ConeFrame}{\beamerreturnbutton{Back}}}
+\uncover<2>{This succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.}
 
@@
  	 \Sapp(f,n_k) &= \sum_{i=1}^{n_k} \hf(\vj_i) v_{\vj_i} \text{ is optimal for fixed }n_k, \qquad \norm[\cg]{S(f) - \Sapp(f,n_k)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}} \\[-1ex]
- 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
+ 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k)} \text{ for the smallest $k$ satisfying } \alert{\sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
  	 \only<2>{\\ 
- 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) = n_{\ell^\dagger}, \quad 
- 	 \ell^\dagger \le \min \left \{\ell \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{\ell-1} \frac{b^{2(k-\ell)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{\ell-1}+1}^2}\right]   \right\}}} \\
- 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) \text{ essentially no worse than } \comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)}}}
+ 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) = n_{\ell^\dagger}}, \quad 
+ 	 \ell^\dagger \le \min \left \{\ell \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{\ell-1} \frac{b^{2(k-\ell)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{\ell-1}+1}^2}\right]   \right\}} \\
+ 	 \MoveEqLeft{\cost(A,\cc,\varepsilon,\rho) \text{ \alert{essentially no worse than} } \comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)}\\
+ 	 \MoveEqLeft{\text{\alert{No} tractability results}}}
 \end{align*}
@@
     \only<1>{\cf &:= \left \{ f = \sum_{\vj \in \natzero^d} \hf(\vj) u_{\vj} : \norm[\cf]{f} :=  \norm[\infty]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \qquad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
-    \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[1]{\hg}\biggr \}, \qquad v_{\vj} = S(u_{\vj}) = u_{\vj} \\[-2ex]}
-    \lambda_{\vj} & = \Gamma_{\norm[0]{\vj}} \prod_{\substack{\ell = 1 \\ j_{\ell} > 0}}^d \gamma_\ell s_{j_\ell} \quad \text{\alert{product, order, and smoothness dependent weights}} \\
+    \cg &: = \Biggl \{ g = \sum_{\vj \in \natzero^d} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[1]{\hg}\Biggr \}, \qquad v_{\vj} = S(u_{\vj}) = u_{\vj} \\[-2ex]}
+    \lambda_{\vj} & = \Gamma_{\norm[0]{\vj}} \prod_{\substack{\ell = 1 \\ j_{\ell} > 0}}^d \gamma_\ell s_{j_\ell} \quad
+    \begin{cases}
+\gamma_\ell = \text{coordinate importance} \\[-0.5ex]
+\Gamma_r = \text{order size} \\[-0.5ex]
+s_j =  \text{smoothness degree}
+\end{cases}
+\text{\alert{POSD weights\footfullcite{WuHam00,KuoEtal12a}}} \\
       & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
       \Sapp(f,n) = \sum_{i=1}^{n} \hf(\vj_i) u_{\vj_i} ,  \qquad
- 	\sigma_k(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad k \in \naturals \\
-     \cc &: = \left\{f \in \cf :  
- 	 \sigma_\ell(f) \le a b^{\ell - k}\sigma_k(f) \quad \forall k \le \ell \right\} \quad a > 1 > b \quad \text{\alert{series coef.\ decay steadily}}\\
- 	 \Sapp(f,n_k) &= \sum_{i=1}^{n_k} \hf(\vj_i) v_{\vj_i} \text{ is optimal for fixed }n_k, \qquad \norm[\cg]{S(f) - \Sapp(f,n_k)} \le \frac{ab \sigma_k(f)}{\sqrt{1 - b^2}} \\[-1ex]
- 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}}
+ 	\norm[\cg]{S(f) - \Sapp(f,n_k)} \le \norm[\cf]{f} \sum_{i = n+1} \lambda_{\vj_i} \\
+     \cc &: = \left\{f \in \cf :  \text those functions \right \}
  	 \only<2>{\\
+ 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}} \\ 
  	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) = n_{\ell^\dagger}, \quad 
@@
 	\end{tabular}
+\end{frame}
+
+\begin{frame}{Take Home Message}
+
+\begin{itemize}
+    \item Assuming that the input functions lie in \alert{cones} \smallcone allow us to construct \alert{adaptive} algorithms
+
+    \item Cone definitions reflect \alert{prior beliefs} or \alert{practical considerations}
+
+    \item Much to be done to 
+    \begin{itemize}
+        \item demonstrate \alert{solvability}
+
+        \item \alert{construct} algorithms
+
+        \item derive upper bounds on \alert{computational cost}
+
+        \item derive lower bounds on \alert{computational complexity}
+
+        \item determine conditions on \alert{tractability}
+
+        \item \alert{implement} algorithms in available software
+    \end{itemize}
+
+\end{itemize}
+
 \end{frame}
@@
 
-\begin{frame}[label = BallsWontHelp]{``But I Like Balls \smallscoop!''}
-
-\vspace{-5ex}
-How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \alert{balls}?
-
-\vspace{-2ex}
-\begin{description}
-    \item[Step 1] Pick with a default radius $\rho$, and \alert{assume} input $f \in \cb_{\rho}$
-
-    \item[Step 2] Choose $n$ \alert{large enough} so that
-
-    \vspace{-4ex}
-    \begin{multline*}
-     \norm[\cg]{S(f) - \Sapp(f,n)} \le \norm[\cf\to \cg]{S - \Sapp(\cdot,n)} \rho \le \varepsilon \\
-         \text{where } \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i
-    \end{multline*}
-
-    \vspace{-2ex}
-
-    \item<2>[Step 3] Let $\tf \in \cf$ be the \alert{minimum} norm interpolant of the data $L_1(f), \ldots, L_n(f)$
-
-    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{\tf} \le \rho$ for some preset \alert{inflation} factor, $C$, }then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; otherwise, choose $\rho = 2C\bignorm[\cf]{\tf}$, and go to Step 2}
-\end{description}
-
-\vspace{-2ex}
-
-\uncover<2>{This succeeds for the \alert{cone} \smallcone defined as those functions in $\cf$ whose norms are not much larger than their minimum norm interpolants.
-\hyperlink{ConeFrame}{\beamerreturnbutton{Back}}}
-
-\end{frame}
-
 \end{document}

### 2018-11-08 RICAM2018NovTalk.tex
Updates from ShareLaTeX
Nearly done

@@
 
-\begin{tabular}{p{0.48\textwidth}p{0.49\textwidth}}
+\begin{tabular}{p{0.47\textwidth}p{0.5\textwidth}}
 Given $f \in \cf$ find $S(f) \in \cg$, where \\
@@
 \begin{multline*}
-    \ca(\cc) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } \\
+    \ca(\cc,\Lambda) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } \\
 \norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \ \ \forall f \in \cc \subseteq \cf, \ \varepsilon > 0 \}
@@
 \vspace{-9ex}
-\uncover<1->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc) \ne \emptyset$
+\uncover<1->{\alert{Solvability}\footfullcite{KunEtal19a}: $\ca(\cc,\Lambda) \ne \emptyset$
 
@@
 
-\alert{Construction}: Identify $\app \in \ca(\cc)$}
+\alert{Construction}: Identify $\app \in \ca(\cc,\Lambda)$}
 
@@
 
-\alert{Complexity}\footfullcite{TraWasWoz88}: $\comp(\ca(\cc),\varepsilon,\rho)$ 
-\newline \phantom{a} \hfill \hfill $= \min_{\app \in \ca(\cc)} \cost(\app,\cc,\varepsilon, \rho)$
+\alert{Complexity}\footfullcite{TraWasWoz88}: $\comp(\ca(\cc,\Lambda),\varepsilon,\rho)$ 
+\newline \phantom{a} \hfill \hfill $= \min_{\app \in \ca(\cc,\Lambda)} \cost(\app,\cc,\varepsilon, \rho)$
 
@@
 
-\alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\cc,\varepsilon, \rho) \le \comp(\ca(\cc),\alert{\omega} \varepsilon,\rho)$}
+\alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\cc,\varepsilon, \rho) \le \comp(\ca(\cc,\Lambda),\alert{\omega} \varepsilon,\rho)$}
 
@@
 
-\uncover<3->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\app,\cc,\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}
+\uncover<3->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\ca(\cc,\Lambda),\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}
 
@@
 
-\section{Solvability}
+%\section{Solvability}
 \begin{frame}{When Is $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \emph{Solvable}?}
@@
 
-\section{Series Spaces}
+%\section{Series Spaces}
 
@@
 \end{frame}
-
-% \begin{frame}{Spaces of Inputs and Outputs}
-
-% \vspace{-3ex}
-
-% We focus on Banach spaces that look like
-
-% \vspace{-5ex}
-% \begin{align*}
-%     \cf &:= \left \{ f = \sum_{\vj \in \cn} \hf(\vj) u_{\vj} : \norm[\cf]{f} := \bignorm[r,\vlambda]{\hf} : = \norm[r]{\left(\frac{\bigabs{\hf(\vj)}}{\lambda_{\vj}} \right)_{\vj \in \cn}} \right \} \quad \begin{minipage}{3cm}\raggedright\alert{$\vlambda$ affects convergence rate \& tractability}\end{minipage}\\
-%     \cg &: = \biggl \{ g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj} : \norm[\cg]{g} := \bignorm[t]{\hg}\biggr \}, \qquad S(u_{\vj}) = v_{\vj}, \\
-%     \text{E.g., } & \text{ Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj} \\
-%     & \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj\\
-%     \Sapp(f,n) &= \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
-%     % \norm[\cg]{S(f) - A(f,\varepsilon)} & \le \sum_{\vj \in \cn} \bigabs{\hf(\vj)} \norm[\cg]{v_\vj - \Sapp(u_{\vj},n)}
-% \end{align*}
-
-% \vspace{-7ex}
-% \alert{$\app(f,\varepsilon) = \Sapp(f,n) + $ stopping criterion}
-
-% \end{frame}
 
@@
 
-\section{General Problems}
+\section{General Linear Problems}
 
@@
 
-\begin{frame}{\emph{Function Approximation} when Function Values Are Expensive}
+\section{Function Approximation}
+
+\begin{frame}{\emph{Function Approximation} when Function Values Are Expensive\footfullcite{WuHam00,KuoEtal12a}}
 
@@
 \end{cases}
-\text{\alert{POSD weights\footfullcite{WuHam00,KuoEtal12a}}} \\
+\text{\alert{POSD weights}} \\[-2ex]
       & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
@@
  	\norm[\cg]{S(f) - \Sapp(f,n_k)} \le \norm[\cf]{f} \sum_{i = n+1} \lambda_{\vj_i} \\
-     \cc &: = \left\{f \in \cf :  \text those functions \right \}
- 	 \only<2>{\\
- 	 \alert{A(f,\varepsilon)} & \alert{= \Sapp(f,n_k) \text{ for the smallest $k$ satisfying } \sigma_k(f) \le \frac{\varepsilon \sqrt{1 - b^2}}{ab}} \\ 
- 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) = n_{\ell^\dagger}, \quad 
- 	 \ell^\dagger \le \min \left \{\ell \in \naturals : \frac{\rho^2}{\varepsilon^2} \le \frac{(1 - b^2)}{a^2b^2} \left[ \sum_{k=1}^{\ell-1} \frac{b^{2(k-\ell)}}{a^2\lambda_{n_{k-1}+1}^2} + \frac{1}{\lambda_{n_{\ell-1}+1}^2}\right]   \right\}}} \\
- 	 \MoveEqLeft{\alert{\cost(A,\cc,\varepsilon,\rho) \text{ essentially no worse than } \comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)}}}
+     \cc &: = \left\{f \in \cf :  \text{ those functions for which } \norm[\cf]{f} \text{ can be inferred from a pilot sample} \right \}
 \end{align*}
@@
 
+\begin{frame}{Cheng and Sandu Function\footfullcite{VirLib17a}}
+    \vspace{-9ex}
+    \begin{gather*}
+        \text{Order weights }\Gamma_k = 1, \qquad \text{Coordinate weights } \gamma_\ell \text{ \alert{inferred}}, \\
+        \text{Smoothness weights } s_j \text{ \alert{inferred}}, \qquad \LambdaStd
+    \end{gather*}
+
+    \vspace{-3ex}
+
+    \includegraphics[height = 4.3cm]{ProgramsImages/sim_eval_results_chsan10_d6_sflg0ErrN.eps}
+    \qquad \includegraphics[height = 4.3cm]{ProgramsImages/sim_eval_results_chsan10_d6_sflg0fErr.eps}
+\end{frame}
+
+\section{Summary}
 \begin{frame}{Take Home Message}
+
+\vspace{-4ex}
 
@@
 
-    \item Much to be done to 
+    \item Demonstration of concept
     \begin{itemize}
-        \item demonstrate \alert{solvability}
+        \item Integration using $\LambdaStd$
+        \begin{itemize}
+            \item Constructed $A \in \ca(\cc,\LambdaStd)$
+            \item No cost, complexity, or tractability yet
+        \end{itemize}
+        \item General linear problems
+        \begin{itemize}
+            \item Constructed $A \in \ca(\cc,\LambdaSer)$, upper bound on $\cost(A,\cc,\varepsilon,\rho)$, lower bound on $\comp(\ca(\cc,\LambdaAll),\varepsilon,\rho)$, optimality
+            \item No tractability yet
+        \end{itemize}
+        \item Function approximation (recovery)
+        \begin{itemize}
+            \item Constructed $A \in \ca(\cc,\LambdaSer)$, algorithm learns weights, works in practice for $\LambdaStd$
+            \item Remaining theory in progress
+        \end{itemize}
+    \end{itemize}
 
-        \item \alert{construct} algorithms
-
-        \item derive upper bounds on \alert{computational cost}
-
-        \item derive lower bounds on \alert{computational complexity}
-
-        \item determine conditions on \alert{tractability}
-
-        \item \alert{implement} algorithms in available software
-    \end{itemize}
+    \item Much to be done
 
@@
 
-\finalthanksnote{These slides are  available at \\  \href{https://speakerdeck.com/fjhickernell/samsi-qmc-transition-2018-may}{\nolinkurl{speakerdeck.com/fjhickernell/samsi-qmc-transition-2018-may}}}
+\finalthanksnote{These slides are  available at \\  \href{https://speakerdeck.com/fjhickernell/ricam-2018-nov}{\nolinkurl{speakerdeck.com/fjhickernell/ricam-2018-nov}}}
 

### 2018-11-08 RICAM2018NovTalk.tex
clean up

@@
 \begin{gather*}
-    \Sapp(f,n) = \sum_{i=1}^n f(\vx_i) g_i, \quad g_i \in \cg \\
-    \Sapp(f,n) = \sum_{i=1}^n \hf_i g_i, \quad g_i \in \cg \\
-    \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i, \quad g_i \in \cg \\
+    \Sapp(f,n) = \sum_{i=1}^n f(\vx_i) \, g_i, \quad g_i \in \cg \\
+    \Sapp(f,n) = \sum_{i=1}^n \hf_i \, g_i, \quad g_i \in \cg \\
+    \Sapp(f,n) = \sum_{i=1}^n L_i(f) \, g_i, \quad g_i \in \cg \\
 \end{gather*}
@@
 
-    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{f_{\textup{min}}} \le \rho$ for some preset \alert{inflation} factor, $C$, }then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; otherwise, choose $\rho = 2C\bignorm[\cf]{f_{\textup{min}}}$, and go to Step 2}
+    \item[Step 4]  \uncover<2>{If $C\bignorm[\cf]{f_{\textup{min}}} \le \rho$ for some preset \alert{inflation} factor, $C$, \\}then return $A(f,\varepsilon) = \Sapp(f,n)$\uncover<2>{; \\otherwise, choose $\rho = 2C\bignorm[\cf]{f_{\textup{min}}}$, and go to Step 2}
 \end{description}
@@
 \begin{multline*}
-     \ca(\cc) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } 
+     \ca(\cc,\Lambda) : = \{\app: \cc \times (0,\infty) \to \cg \text{ such that } 
 \norm[\cg]{\sol(f) - \app(f,\varepsilon) } \le \varepsilon \ \forall f \in \cc \subseteq \cf, \ \varepsilon > 0 \}
@@
 \alert{Definition} \quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} $\iff \ca(\cc) \ne \emptyset$\\[1ex]
-\alert{Lemma}  \quad $f_1, f_2 \in \cc$  and $A(f_1, \varepsilon) = A(f_2,\varepsilon) \implies \norm[\cg]{S(f_1-f_2)} \le \varepsilon$\\[1ex]
+\alert{Lemma}  \quad $f_1, f_2 \in \cc$  and $A(f_1, \varepsilon) = A(f_2,\varepsilon) \implies \norm[\cg]{S(f_1-f_2)} \le 2\varepsilon$\\[1ex]
 \alert{Corollary} \label{ZeroCorollary} \quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} and $\exists f \in \cc,\  \varepsilon > 0$ with $A(f,\varepsilon) = A(0,\varepsilon)$  \\ \hfill \hfill $\implies S(f) = 0$\\[1ex]
 \alert{Theorem} \label{VectorSpaceThm}\quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} and $\cc$ is a \alert{vector space} \\ \hfill \hfill 
-$\iff S(f) = \sum_{i=1}^n L_i(f) g_i$ for some $\vL \in \Lambda^n, \vg \in \cg^n$  \hyperlink{VectorSpaceThmProof}{\beamergotobutton{Proof}}\\[1ex]
+$\iff S(f) = \sum_{i=1}^n L_i(f) g_i$ for some $\vL \in \Lambda^n, \ \vg \in \cg^n, \ n \in \naturals$  \hyperlink{VectorSpaceThmProof}{\beamergotobutton{Proof}}\\[1ex]
 E.g. $\left(\int_{[0,1]^d} \cdot (\vx) \, \dif \vx: C^{1,\ldots,1}[0,1]^d\to\reals,\Lambda^{\textup{std/\alert{all}}}\right)$ is unsolvable/\alert{solvable}
@@
 
-\vspace{-5ex}
+\vspace{-8ex}
 \begin{gather*}
@@
    \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj \\
-    \text{\alert{Fixed sample size algorithm: }} \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i = \sum_{\vj \in \cn} \hf(\vj) \Sapp(u_\vj,n)  \\
+    \text{\alert{Fixed sample size algorithm: }} \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i   \\
     \alert{\app(f,\varepsilon) = \Sapp(f,n) + \text{ stopping criterion}}
 \end{gather*}
+
+\vspace{-1ex}
+
+Three scenarios presented
+
+\vspace{-3ex}
+\begin{description}[\labelwidth = 2cm]
+\item[Integration] use $\LambdaStd$, but cost, complexity, etc. lacking
+\item[General Linear Problems] use $\LambdaSer$, have cost, complexity, and optimality
+\item[Function Approximation] use $\LambdaSer$, learn coordinate and smoothness weights
+\end{description}
 
@@
 \section{Integration}
+
+\begin{frame}{Integration Using Function Values, $\LambdaStd$\footfullcite{DicEtal14a}}
+
+\vspace{-7ex}
+
+\begin{align*}
+    f &= \sum_{\vj \in \cn} \hf(\vj) u_{\vj}, \qquad
+    u_{\vj} = \text{Cosine/Sine or Walsh}, \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}\\
+    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]
+    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
+    \end{array}
+    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
+    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
+\end{align*}
+
+\end{frame}
 
@@
 	\end{tabular}
-\end{frame}
-
-\begin{frame}{Integration Using Function Values, $\LambdaStd$\footfullcite{DicEtal14a}}
-
-\vspace{-7ex}
-
-\begin{align*}
-    f &= \sum_{\vj \in \cn} \hf(\vj) u_{\vj}, \qquad
-    u_{\vj} = \text{Cosine/Sine or Walsh}, \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}\\
-    &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]
-    \abs{S(f) - \Sapp(f,n)} \le \sum_{\vzero \ne \vj \in \text{dual set}} \bigabs{\hf(\vj)}
-    \end{array}
-    \quad \raisebox{-8ex}{\includegraphics[width=3cm]{ProgramsImages/ShiftedLatticePoints.eps} \qquad
-    \includegraphics[width=3cm]{ProgramsImages/SSobolPoints.eps}}
-\end{align*}
-
 \end{frame}

### 2018-11-08 RICAM2018NovTalk.tex
polishing

@@
 \centerline{
-    \begin{tabular}{>{\vspace{-1.7ex}\raggedleft}p{0.2\textwidth}@{\qquad}p{0.3\textwidth}@{\qquad}p{0.3\textwidth}}
-    & \alert{Previous talks} & \alert{My reponse} \tabularnewline
+    \begin{tabular}{>{\vspace{-1.7ex}\raggedleft}p{0.2\textwidth}@{\qquad}p{0.33\textwidth}@{\qquad}p{0.27\textwidth}}
+    & \alert{Tidbits from talks this week} & \alert{My reponse} \tabularnewline
     \toprule
-    \alert{Henryk, Klaus, Greg, Stefan, \ldots} & Many results for $f \in \smallscoop$  &
-    May we obtain analogous results for $f \in \smallcone$? \tabularnewline[2ex]
+    \alert{Henryk, Klaus, Greg, Stefan, Erich, \ldots} & Many results for $f \in \smallscoop$  &
+    Let's obtain analogous results for $f \in \smallcone$? \tabularnewline[2ex]
     \alert{Houman} & Let's \alert{learn} the appropriate kernel from the function data & Will only work for nice functions in a \smallcone \tabularnewline[2ex]
-    \alert{Paul} & Let's \alert{find} the Lipschitz matrix constant \ldots & Yes, lets learn from the function data \tabularnewline[2ex]
-    \alert{Klaus} & This adaptive algorithm has \alert{no theory}  & We want to construct adaptive algorithms \alert{with theory} \tabularnewline[2ex]
+    \alert{Klaus} & ``This adaptive algorithm has \alert{no theory}''  & We want to construct adaptive algorithms \alert{with theory} \tabularnewline[2ex]
     \alert{Henryk} & Tractability & Yes! \tabularnewline[2ex]
-    \alert{Greg} & POD weights & Yes!
+    \alert{Greg} & POD weights & Yes! \tabularnewline[2ex]
+    \alert{Mac} & Function values are expensive & Yes!
     \end{tabular}}
@@
 \vspace{-1ex}
-where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{linear functionals}, $\LambdaAll$, e.g.,
+where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{any linear functionals}, $\LambdaAll$, e.g.,
 
@@
 \vspace{-1ex}
-where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{linear functionals}, $\LambdaAll$
+where $\app(f,\varepsilon)$ depends on \alert{function values}, $\LambdaStd$, \alert{Fourier coefficients}, $\LambdaSer$, or \alert{any linear functionals}, $\LambdaAll$
 &
@@
 
-\medskip
+\smallskip
 
-\alert{Construction}: Identify $\app \in \ca(\cc,\Lambda)$}
+\alert{Construction}: Find $\app \in \ca(\cc,\Lambda)$}
 
-\medskip
+\smallskip
 
@@
 
- \medskip
+ \smallskip
 
@@
 
-\medskip
-
 \alert{Optimality}:  \newline \phantom{a} \hfill \hfill $\cost(\app,\cc,\varepsilon, \rho) \le \comp(\ca(\cc,\Lambda),\alert{\omega} \varepsilon,\rho)$}
 
-\medskip
+\smallskip
 
 \uncover<3->{\alert{Tractability}\footfullcite{NovWoz08a}: $\comp(\ca(\cc,\Lambda),\varepsilon, \rho) \le C \rho^p\varepsilon^{-p} d^{q} $}
+
+\smallskip
+\uncover<4->{\alert{Implementation} in open source software}
 
@@
 
-    \item Philosophy:  \alert{What we cannot observe is not much worse than what we can observe}
+    \item \alert{Philosophy:}  What we cannot observe about $f$ is not much worse than what we can observe about $f$
 
@@
 
-\begin{frame}[label = BallsWontHelp]{``But I Like Balls \smallscoop!''}
+\begin{frame}[label = BallsWontHelp]{``But I Like \smallscoop!''}
 
 \vspace{-5ex}
-How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \alert{balls}?
+How might you construct an \only<2>{\alert{adaptive}} algorithm if you insist on using \smallscoop?
 
@@
 
-Three scenarios presented
+Three scenarios presented here:
 
@@
 \begin{align*}
+    S(f) & = \int_{[0,1]^d} f(\vx) \, \dif \vx\\[2ex]
     f &= \sum_{\vj \in \cn} \hf(\vj) u_{\vj}, \qquad
-    u_{\vj} = \text{Cosine/Sine or Walsh}, \qquad S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx = \delta_{\vj,\vzero}\\
+    u_{\vj} = \text{Cosine/Sine or Walsh}, \qquad S(u_{\vj}) = \delta_{\vj,\vzero}\\
     &\begin{array}{l}\Sapp(f,n) = \frac 1n \sum_{i=1}^n f(\vx_i)  \\[4ex]

### 2018-11-09 RICAM2018NovTalk.tex
polish

@@
 \thanksnote{{\large Joint work with Yuhan Ding, Peter Kritzer, and Simon Mak} \\
-	This work partially supported by  NSF-DMS-1522687 and NSF-DMS-1638521 (SAMSI) \& ???
+	This work partially supported by  NSF-DMS-1522687 and NSF-DMS-1638521 (SAMSI)
 }
@@
     \alert{Henryk, Klaus, Greg, Stefan, Erich, \ldots} & Many results for $f \in \smallscoop$  &
-    Let's obtain analogous results for $f \in \smallcone$? \tabularnewline[2ex]
+    Let's obtain analogous results for $f \in \smallcone$? \tabularnewline[4ex]
     \alert{Houman} & Let's \alert{learn} the appropriate kernel from the function data & Will only work for nice functions in a \smallcone \tabularnewline[2ex]
@@
 
-    \item \alert{Cone} means $f \in \cc \implies af \in \cc \ \forall a \in \reals$
+    \item \alert{Cone} means $f \in \cc \implies af \in \cc \ \ \forall a \in \reals$
 
@@
 
-    \item If we can bound the error for $f \in $ \alert{cone}, then we can typically also bound the error  for $af$
+    \item If we can bound the $\norm[\cg]{S(f) - \Sapp(f,n)}$ for $f \in $ \alert{cone}, then we can typically also bound the error  for $af$
 
@@
 
-\alert{Definition} \quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} $\iff \ca(\cc) \ne \emptyset$\\[1ex]
+\alert{Definition} \quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} $\iff \ca(\cc,\Lambda) \ne \emptyset$\\[1ex]
 \alert{Lemma}  \quad $f_1, f_2 \in \cc$  and $A(f_1, \varepsilon) = A(f_2,\varepsilon) \implies \norm[\cg]{S(f_1-f_2)} \le 2\varepsilon$\\[1ex]
@@
 \alert{Theorem} \label{VectorSpaceThm}\quad $(S:\cc \subseteq \cf\to\cg,\Lambda)$ \alert{solvable} and $\cc$ is a \alert{vector space} \\ \hfill \hfill 
-$\iff S(f) = \sum_{i=1}^n L_i(f) g_i$ for some $\vL \in \Lambda^n, \ \vg \in \cg^n, \ n \in \naturals$  \hyperlink{VectorSpaceThmProof}{\beamergotobutton{Proof}}\\[1ex]
+$\iff \exists \ n \in \naturals, \ \vL \in \Lambda^n, \ \vg \in \cg^n$ such that $S(f) = \sum_{i=1}^n L_i(f) g_i \ \forall f \in \cc$ \alert{exactly}   \hyperlink{VectorSpaceThmProof}{\beamergotobutton{Proof}}\\[1ex]
 E.g. $\left(\int_{[0,1]^d} \cdot (\vx) \, \dif \vx: C^{1,\ldots,1}[0,1]^d\to\reals,\Lambda^{\textup{std/\alert{all}}}\right)$ is unsolvable/\alert{solvable}
@@
     \text{\alert{Output: }} g = \sum_{\vj \in \cn} \hg(\vj) v_{\vj}, \qquad S(u_{\vj}) = v_{\vj}, \\
-    \text{E.g., Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj}, \qquad
-   \text{ Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj \\
+    \text{E.g., Integration: } S(u_{\vj}) = \int_{[0,1]^d} u_\vj (\vx) \, \dif \vx  = v_\vj, \qquad  \text{Function recovery: } S(u_{\vj}) = u_{\vj} = v_{\vj}, \qquad\\
     \text{\alert{Fixed sample size algorithm: }} \Sapp(f,n) = \sum_{i=1}^n L_i(f) g_i   \\
@@
 \vspace{-4ex}
-\alert{Have} $\cost(f,A,\varepsilon)$; \quad \alert{No} $\cost(A,\cc,\varepsilon,\rho)$,  $\comp(\ca(\cc),\varepsilon,\rho)$, or  tractability results \alert{yet}
+\alert{Have} $\cost(f,A,\varepsilon)$; \quad \alert{No} $\cost(A,\cc,\varepsilon,\rho)$,  $\comp(\ca(\cc,\LambdaStd),\varepsilon,\rho)$, or  tractability results \alert{yet}
 
@@
       n_0 < n_1 < n_2 < \cdots,  \qquad
- 	\sigma_k(f) = \sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}, \quad k \in \naturals \\
+ 	\sigma_k(f) = \sqrt{\sum_{i=n_{k-1}+1}^{n_k}  \bigabs{\hf(\vj_i)}^2}, \quad k \in \naturals \\
      \cc &: = \left\{f \in \cf :  
@@
 s_j =  \text{smoothness degree}
-\end{cases}
-\text{\alert{POSD weights}} \\[-2ex]
+\end{cases} \quad\begin{minipage}{5.5cm}\raggedright\alert{POSD weights reflect effect sparsity, effect hierarchy, effect heredity, and effect smoothness}\end{minipage}
+ \\[-2ex]
       & \alert{\lambda_{\vj_1} \ge \lambda_{\vj_2} \ge \cdots}, \qquad
@@
  	\norm[\cg]{S(f) - \Sapp(f,n_k)} \le \norm[\cf]{f} \sum_{i = n+1} \lambda_{\vj_i} \\
-     \cc &: = \left\{f \in \cf :  \text{ those functions for which } \norm[\cf]{f} \text{ can be inferred from a pilot sample} \right \}
+     \cc &: = \left\{f \in \cf :  \text{ those functions for which } \norm[\cf]{f} \text{ can be \alert{inferred} from a pilot sample} \right \}
 \end{align*}
@@
     \begin{gather*}
-        \text{Order weights }\Gamma_k = 1, \qquad \text{Coordinate weights } \gamma_\ell \text{ \alert{inferred}}, \\
+        \text{Chebyshev polynomials}, \qquad \text{Order weights }\Gamma_k = 1, \qquad \text{Coordinate weights } \gamma_\ell \text{ \alert{inferred}}, \\
         \text{Smoothness weights } s_j \text{ \alert{inferred}}, \qquad \LambdaStd
@@
 \section{Summary}
-\begin{frame}{Take Home Message}
+\begin{frame}{Take Home Messages}
 
@@
 \begin{itemize}
-    \item Assuming that the input functions lie in \alert{cones} \smallcone allow us to construct \alert{adaptive} algorithms
+    \item Assuming that the input functions lie in convex \alert{cones} \smallcone allow us to construct \alert{adaptive} algorithms
 
-    \item Cone definitions reflect \alert{prior beliefs} or \alert{practical considerations}
+    \item Cone definitions reflect \alert{prior beliefs} and/or \alert{practical considerations}
 

### 2019-01-04 DingHickKritzMakRICAMChap.tex
moved proceedings to outer folder
revising
updating

--- 2018-11-03 degruyter-proceedings/DingHickKritzMakRICAMChap.tex
@@
 \usepackage{microtype}
+\usepackage{amsmath,amssymb}
+\input{macros}
+
+%% Beginning of author included packages and defined macros
+\usepackage{color,mathtools,bbm,xspace,natbib}
+\usepackage{algorithm, algorithmicx}
+\usepackage{algpseudocode}
+\algnewcommand\algorithmicparam{\textbf{Parameters:}}
+\algnewcommand\PARAM{\item[\algorithmicparam]}
+\algnewcommand\algorithmicinput{\textbf{Input:}}
+\algnewcommand\INPUT{\item[\algorithmicinput]}
+%\algnewcommand\STATE{\item}
+\algnewcommand\RETURN{\State \textbf{Return }}
+
+\DeclareMathOperator{\SOL}{SOL}
+\DeclareMathOperator{\APP}{APP}
+\DeclareMathOperator{\ALG}{ALG}
+\DeclareMathOperator{\ERR}{ERR}
+\newcommand{\dataN}{\bigl\{\hf(\bsk_i)\bigr\}_{i=1}^n}
+\newcommand{\ERRN}{\ERR\bigl(\dataN,n\bigr)}
+\DeclareMathOperator{\COST}{COST}
+\DeclareMathOperator{\COMP}{COMP}
+\newcommand{\hf}{\widehat{f}}
+\newcommand{\hg}{\widehat{g}}
+\newcommand{\tu}{\Tilde{u}}
+\newcommand{\tv}{\Tilde{v}}
+\newcommand{\tlambda}{\Tilde{\lambda}}
+\newcommand{\tbbK}{\widetilde{\bbK}}
+\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
+\newcommand{\normabs}[1]{\ensuremath{\lvert #1 \rvert}}
+\newcommand{\bigabs}[1]{\ensuremath{\bigl \lvert #1 \bigr \rvert}}
+\newcommand{\Bigabs}[1]{\ensuremath{\Bigl \lvert #1 \Bigr \rvert}}
+\newcommand{\biggabs}[1]{\ensuremath{\biggl \lvert #1 \biggr \rvert}}
+\newcommand{\Biggabs}[1]{\ensuremath{\Biggl \lvert #1 \Biggr \rvert}}
+\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
+\newcommand{\normnorm}[2][{}]{\ensuremath{\lVert #2 \rVert}_{#1}}
+\newcommand{\bignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
+\newcommand{\Bignorm}[2][{}]{\ensuremath{\Bigl \lVert #2 \Bigr \rVert}_{#1}}
+\newcommand{\biggnorm}[2][{}]{\ensuremath{\biggl \lVert #2 \biggr \rVert}_{#1}}
+\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
+\newcommand{\FredNote}[1]{{\color{blue}Fred: #1}}
+\newcommand{\YuhanNote}[1]{{\color{green}Yuhan: #1}}
+\newcommand{\PeterNote}[1]{{\color{orange}Peter: #1}}
+\newcommand{\SimonNote}[1]{{\color{purple}Simon: #1}}
+%\newcommand{\HickernellFJ}{Hickernell}
+
+%% End of author included packages and defined macros
 
@@
 
-  \articletype{...}
+  %\articletype{...}
 
-  \author*[1]{Yuhan Ding}
-  \author[2]{Fred J. Hickernell}
+  \author[1]{Yuhan Ding}
+  \author*[2]{Fred J. Hickernell}
   \author[3]{Peter Krtizer} 
   \author[4]{Simon Mak}
-  \runningauthor{...}
+  \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
   \affil[1]{...}
-  \affil[2]{...}
-  \title{...}
-  \runningtitle{...}
+  \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
+  \affil[3]{...}
+  \affil[4]{...}
+  \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
+  \runningtitle{Adaptive Approximation}
   \subtitle{...}
   \abstract{...}
-  \keywords{...}
-  \classification[PACS]{...}
-  \communicated{...}
-  \dedication{...}
-  \received{...}
-  \accepted{...}
-  \journalname{...}
-  \journalyear{...}
-  \journalvolume{..}
-  \journalissue{..}
+  %\keywords{...}
+  %\classification[PACS]{...}
+  %\communicated{...}
+  %\dedication{...}
+  %\received{...}
+  %\accepted{...}
+  %\journalname{...}
+  %\journalyear{...}
+  %\journalvolume{..}
+  %\journalissue{..}
   \startpage{1}
   \aop
-  \DOI{...}
+  %\DOI{...}
 
@@
 
-\section{A section}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Introduction} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
-  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
-  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
-  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
-  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
-  tincidunt.
+There are many situations in which adaptive algorithms cannot perform much better than non-adaptive algorithms.
+Yet, in practice adaptive algorithms are appreciated because they relieve the user from having to stipulate the computational effort required to achieve the desired accuracy.
+Adaptive algorithms infer the computational effort required based on the function data sampled.
 
-  Cras dapibus. Vivamus elementum semper nisi. Aenean vulputate eleifend tellus. Aenean
-  leo ligula, porttitor eu, consequat vitae, eleifend ac, enim. Aliquam lorem ante, dapibus in,
-  viverra quis, feugiat a, tellus. Phasellus viverra nulla ut metus varius laoreet. Quisque
-  rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies
-  nisi. Nam eget dui. Etiam rhoncus. Maecenas tempus, tellus eget condimentum rhoncus, sem quam
-  semper libero, sit amet adipiscing sem neque sed ipsum. Nam quam nunc, blandit vel, luctus
-  pulvinar, hendrerit id, lorem. Maecenas nec odio et ante tincidunt tempus. Donec vitae sapien ut
-  libero venenatis faucibus. Nullam quis ante. Etiam sit amet orci eget eros faucibus
-  tincidunt. Duis leo. Sed fringilla mauris sit amet nibh. Donec sodales sagittis magna. Sed
-  consequat, leo eget bibendum sodales, augue velit cursus nunc,
+Adaptive algorithms may perform better in the set of input functions is not convex, and that is the situation studied here.
+We propose adaptive algorithms for general multivariate linear problems where the input function lies in a non-convex cone.
+Our algorithms use series coefficients of the input function to construct an approximate solution that satisfies an absolute error tolerance.
+We show our algorithms to be essentially optimal.
+We derive conditions under which the problem is tractable.
+In the remainder of this section we define the problem and essential notation.
 
-\section{Another section}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{General Linear Problem}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Our general linear problem is defined by a solution operator that takes the input function to the solution, $\SOL:\calF \to \calG$.
+The spaces of inputs and outputs are defined in terms of series expansions:
+\begin{gather}
+    \calF = \left \{f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \\
+    \calG = \left \{g = \sum_{\bsk \in \mathbb{K}} \hg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \hg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} \right\}, \quad \tau \le \rho.
+\end{gather}
+Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$ and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$.
+These bases are defined to match the solution operator:
+\begin{equation}
+    \SOL(u_{\bsk}) = v_{\bsk} \qquad \forall \bsk \in \mathbb{K},
+\end{equation}
+where $\mathbb{K}$ is a general index set.
+
+To facilitate derivations below, we establish the following lemma:
+
+\begin{lemma}
+Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined the relation
+\begin{equation*}
+    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
+\end{equation*}
+\FredNote{I am trying to capture the case $\rho = \tau = 2, \ \rho' = \infty$ in \cite{DinHic20a} and the case $\rho = \infty, \ \rho' = \tau = 1$ in the work with Simon.}
+Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
+\begin{equation}
+\label{DHKM:SOL_ineq}
+    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
+    \end{equation}
+    \begin{multline}
+    \label{DHKM:SOL_tight_ineq}
+    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} \quad \forall \bsk \in \calK\\
+    \implies \norm[\calG]{\SOL(f)} = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \ \& \ \norm[\calF]{f} = R.
+    \end{multline}
+Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} tight.
+\end{lemma}
+\begin{proof}
+The proof proceeds by applying H\"older's inequality
+\begin{align}
+    \label{DHKM:SOL_A}
+    \norm[\calG]{\SOL(f)}  
+    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}} \\
+\nonumber
+    & = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
+    \nonumber
+    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau \\
+    \nonumber
+    & = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
+\end{align}
+which establishes inequality \eqref{DHKM:SOL_ineq}.
+Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
+\begin{equation*}
+       \norm[\calG]{\SOL(f)}  
+    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
+    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
+    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}.
+\end{equation*}
+Moreover,
+\begin{equation*}
+    \norm[\calF]{f}  
+    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
+    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
+    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
+    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R.
+\end{equation*}
+This completes the proof.
+\end{proof}
+
+Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
+\begin{equation}
+    \norm[\calF \to \calG]{\SOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\SOL(f)} = \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \mathbb{K}}}.
+\end{equation}
+
+The $\lambda_{\bsk}$ define the smoothness of the input space and have a known order:
+\begin{equation} \label{DHKM:lambda_order}
+    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots.
+\end{equation}
+An optimal approximation  based on $n$ series coefficients of the input function can be defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
+\begin{equation} \label{DHKM:APP_def}
+    \APP : \calF \times \N_0 \to \calG, \qquad  \APP(f,n) := \sum_{i=1}^n \hf(\bsk) v_{\bsk}, \quad \APP(f,0) = 0.
+\end{equation}
+
+\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
+The error of the approximation defined in \label{DHKM:APP_def} is bounded tightly above as
+\begin{equation} \label{DHKM:APP_errorBd}
+    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
+\end{equation}
+Moreover, the worst case error over $\calB_R$ of any approximation based on $n$ series coefficients of the input function, $\APP'(\cdot,n)$, can be no smaller.
+\end{theorem}
+
+To facilitate the proof of this theorem and theorems below, we first establish the following lemma:
+
+\begin{lemma}
+Let $\calK$ be some subset of $\bbK$.
+\end{lemma}
+
+\begin{proof}[Proof of Theorem \ref{DHKM:APP_optimality_thm}]
+The proof of \eqref{DHKM:APP_errorBd} follows from an argument similar to that used to derive 
+\eqref{DHKM:SOLNorm}.  The optimality of $\APP$ follows by bounding the error of an arbitrary approximation, $\APP'$ applied to functions that mimic the zero function.
+
+ Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.  Choose $f$ to satisfy the following conditions:
+\begin{gather*}
+    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ \Bignorm[\tau]{\bigl(\hf_{\bsk}\bigr)_{\bsk \notin \calJ}}
+    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
+    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}
+\end{gather*}
+Then $\APP'(\pm f,n) = \APP'(0,n)$, and
+\begin{align*}
+\MoveEqLeft{\max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)}} \\
+&=  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)} \\
+& \ge \frac 12 \left [ \norm[\calG]{\SOL(f) - \APP'(0,n)} 
++ \norm[\calG]{- \SOL(f) - \APP'(0,n)}\right] \\
+& \ge \norm[\calG]{\SOL(f)} 
+= \Bignorm[\tau]{\bigl(\hf_{\bsk}\bigr)_{\bsk \notin \calJ}}
+    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
+    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \\
+    & = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.
+\end{align*}
+The ordering of the $\lambda_{\bsk}$ implies that $\norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}$ for arbitrary $\calJ$ can be no smaller than the case $\calJ = \{\bsk_1, \ldots, \bsk_n\}$.
+This completes the proof.
+\end{proof}
+
+\hspace{\parindent} While approximation $\APP$ is a key component, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion
+\begin{equation} \label{DHKM:err_crit}
+    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \calC.
+\end{equation}
+The non-adaptive Algorithm \ref{DHKM:BallAlg} satisfies this error criterion for $\calC  = \calB_R$.
+However, in practice one cannot bound the norm of the input function a priori, so Algorithm \ref{DHKM:BallAlg} is impractical.
+
+In contrast to \eqref{DHKM:APP_errorBd}, we will construct data-based error bounds for $\APP(f,n)$, which will lead to \emph{adaptive} algorithms $\ALG$ satisfying \eqref{DHKM:err_crit}.
+For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}.
+
+\begin{algorithm}
+	\caption{Non-Adaptive $\ALG$ for a Ball of Input Functions} \label{DHKM:BallAlg}
+	\begin{algorithmic}
+	\PARAM the ball radius, $R$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
+	\INPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$
+
+    \Ensure Error criterion \eqref{DHKM:err_crit} for $\calC = \calB_{R}$
+
+    \State Choose $n^* =  \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}$
+
+    \RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
+\end{algorithmic}
+\end{algorithm}
+
+Note that algorithms satisfying \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$ if $\SOL(\calF)$ is infinite dimensional.
+No matter how large a sample size is required by an algorithm, it is finite.
+Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.
+Thus, algorithms satisfying the error criterion only exist for some strict subset of $\calF$, and choosing that subset well is both an art and a science.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Information Cost and Problem Complexity}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our case series coefficients---required by $\ALG(f,\varepsilon)$.
+For adaptive algorithms this cost varies with the input function $f$.
+We also define the information cost of the algorithm in general, recognizing that it will tend to depend on $\norm[\calF]{f}$
+\begin{equation*}
+    \COST(\ALG, \calC, \varepsilon,R) : = \max_{f \in \calC \cap \calB_{R}} \COST(\ALG,f,\varepsilon).
+\end{equation*}
+Note that while the cost depends on $\norm[\calF]{f}$, $\ALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
+It is common for $\COST(\ALG, \calC, \varepsilon,R)$ to be bounded by a power of $\varepsilon^{-1}$.
+
+Let $\calA(\calC)$ denote the set of all possible algorithms that may be constructed using series coefficients.
+We define the \emph{computational complexity} of a problem as the information cost of the best algorithm:
+\begin{equation*}
+    \COMP(\calA(\calC), \varepsilon,R) := \min_{\ALG \in \calA(\calC)} \COST(\ALG, \calC, \varepsilon,R) .
+\end{equation*}
+These definitions follow the information-based complexity literature \cite{TraWer98, TraWasWoz88}.
+We define an algorithm to be \emph{essentially optimal} if there exists some fixed positive $\omega$ for which
+\begin{equation*}
+    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calA(\calC), \omega \varepsilon,R) \qquad \forall \varepsilon,R > 0.
+\end{equation*}
+This means that the dependence of 
+We will show that our adaptive algorithms are essentially optimal.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tractability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Besides understanding the dependence of the computational complexity on $\varepsilon$, we also want to understand how the computational complexity depends on the dimension of the domain of the input function.
+Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
+Let the bases and $\lambda_{\bsk}$ be of product form:
+\begin{gather*}
+    u_{\bsk} = \tu_{1,k_1} \cdots \tu_{d,k_d}, \qquad  v_{\bsk} = \tv_{1,k_1} \cdots \tv_{d,k_d}, \\ 
+    \lambda_{\bsk} = \tlambda_{1,k_1} \cdots \tlambda_{d,k_d}, \quad \forall \bsk = (k_1, \ldots, k_d) \in \bbK = \tbbK^d.
+\end{gather*}
+The cone of functions for which our algorithms succeed, $\calC_d$ will also depend on the dimension.
+Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
+
+\FredNote{Peter please add here.}
+
+\section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
+\FredNote{I think that this is a simpler case than \cite{DinHic20a} or the work with Simon, so we should start with this}
+
+The idea behind an adaptive algorithm is that the finite information we observe about input function that tells us something about what is not observed about the input function.
+Let $n_1$ some positive integer and $\frakC$ be some constant greater than one.
+The cone of functions whose norm can be bounded well in terms of a pilot sample of the first $n_1$ series coefficients is given by
+\begin{equation} \label{DHKM:pilot_cone}
+    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\},
+\end{equation}
+where the $\bsk_i$ are given by the ordering of the $\lambda_{\bsk}$ in \eqref{DHKM:lambda_order}. Define the data-based error bound,
+\begin{equation} \label{DHKM:pilot_errbd}
+    \ERRN : =  
+    \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
+    \qquad n > n_1.
+\end{equation}
+Although the error bound does not actually depend on the series coefficients for $n> n_1$, we adopt this notation for the data-based error bound recognizing that other forms below do depend on all series coefficients observed.
+
+From the error bound on $\APP$ in \eqref{DHKM:APP_errorBd} and the definition of the cone in \eqref{DHKM:pilot_cone}, it follows that $ \norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN $ for all $f \in \calC$.
+For this cone of functions, Algorithm \ref{DHKM:PilotConeAlg} is successful:
+
+\begin{algorithm}
+	\caption{$\ALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
+	\begin{algorithmic}
+	\PARAM an initial sample size, $n_1$; an inflation factor, $\frakC$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
+		\INPUT a black-box function, $f$; an absolute error tolerance,
+		$\varepsilon>0$
+
+\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:pilot_cone}
+
+\State Choose $n^* =  \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \}$, where $\ERR$ is defined in \eqref{DHKM:pilot_errbd}
+
+\RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
+\end{algorithmic}
+\end{algorithm}
+
+\begin{theorem}
+Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}.  The computational cost of this algorithm is 
+\begin{equation} \label{DHKM:PilotConeAlg_cost}
+    \COST(\ALG,\calC,\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le \varepsilon/(\frakC R) \right \}.
+\end{equation}
+and the computational complexity has the lower bound
+\begin{equation}
+    a
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+The upper bound on the computational cost of this algorithm is obtained by noting that 
+\begin{align*}
+    \MoveEqLeft{\COST(\ALG,\calC,\varepsilon,R)} \\
+    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
+     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
+     \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
+     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
+    \le \varepsilon \right \} \\   
+     & \le \min \left \{n \ge n_1 : 
+     \frakC R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
+    \le \varepsilon \right \},  
+\end{align*}
+since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le R$ for all $f \in \calB_R$.
+Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
+This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.
+
+To prove the lower complexity 
+\end{proof}
+
+Since error bound
 
@@
 
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
-  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
-  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
-  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
-  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
-  tincidunt.
+\section{The \cite{DinHic20a} case with tractability, which needs a better title}
 
-  Cras dapibus. Vivamus elementum semper nisi. Aenean vulputate eleifend tellus. Aenean
-  leo ligula, porttitor eu, consequat vitae, eleifend ac, enim. Aliquam lorem ante, dapibus in,
-  viverra quis, feugiat a, tellus. Phasellus viverra nulla ut metus varius laoreet. Quisque
-  rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies
-  nisi. Nam eget dui. Etiam rhoncus. Maecenas tempus, tellus eget condimentum rhoncus, sem quam
-  semper libero, sit amet adipiscing sem neque sed ipsum. Nam quam nunc, blandit vel, luctus
-  pulvinar, hendrerit id, lorem. Maecenas nec odio et ante tincidunt tempus. Donec vitae sapien ut
-  libero venenatis faucibus. Nullam quis ante. Etiam sit amet orci eget eros faucibus
-  tincidunt. Duis leo. Sed fringilla mauris sit amet nibh. Donec sodales sagittis magna. Sed
-  consequat, leo eget bibendum sodales, augue velit cursus nunc,
-
-\subsection{Another subsection}
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
-  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
-  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
-  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
-  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
-  tincidunt.
-
-  Cras dapibus. Vivamus elementum semper nisi. Aenean vulputate eleifend tellus. Aenean
-  leo ligula, porttitor eu, consequat vitae, eleifend ac, enim. Aliquam lorem ante, dapibus in,
-  viverra quis, feugiat a, tellus. Phasellus viverra nulla ut metus varius laoreet. Quisque
-  rutrum. Aenean imperdiet. Etiam ultricies nisi vel augue. Curabitur ullamcorper ultricies
-  nisi. Nam eget dui. Etiam rhoncus. Maecenas tempus, tellus eget condimentum rhoncus, sem quam
-  semper libero, sit amet adipiscing sem neque sed ipsum. Nam quam nunc, blandit vel, luctus
-  pulvinar, hendrerit id, lorem. Maecenas nec odio et ante tincidunt tempus. Donec vitae sapien ut
-  libero venenatis faucibus. Nullam quis ante. Etiam sit amet orci eget eros faucibus
-  tincidunt. Duis leo. Sed fringilla mauris sit amet nibh. Donec sodales sagittis magna. Sed
-  consequat, leo eget bibendum sodales, augue velit cursus nunc,
-
-Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Aenean commodo ligula eget dolor. Aenean
-  massa. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Donec
-  quam felis, ultricies nec, pellentesque eu, pretium quis, sem. Nulla consequat massa quis
-  enim. Donec pede justo, fringilla vel, aliquet nec, vulputate eget, arcu. In enim justo, rhoncus
-  ut, imperdiet a, venenatis vitae, justo. Nullam dictum felis eu pede mollis pretium. Integer
-  tincidunt.
+\section{The work with Simon case, which needs a better title}
 
@@
 
-%\bibliographystyle{...}
-%\bibliography{...}
+\bibliographystyle{spbasic.bst}
+
+\bibliography{FJH23.bib,FJHown23.bib}
+
+\section*{Appendix}
+
 \end{document}

### 2019-01-07 DingHickKritzMakRICAMChap.tex
Finished first draft of Section 2.

@@
   \author*[2]{Fred J. Hickernell}
-  \author[3]{Peter Krtizer} 
+  \author[3]{Peter Kritzer} 
   \author[4]{Simon Mak}
@@
 
-\begin{lemma}
-Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined the relation
+\begin{lemma} \label{DHKM:Key_Lem}
+Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined by the relation
 \begin{equation*}
@@
        \norm[\calG]{\SOL(f)}  
-    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
-    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
+    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
+    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
     {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}.
@@
 Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
-\begin{equation}
+\begin{equation} \label{DHKM:SOLNorm}
     \norm[\calF \to \calG]{\SOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\SOL(f)} = \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \mathbb{K}}}.
@@
 \begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
-The error of the approximation defined in \label{DHKM:APP_def} is bounded tightly above as
+The error of the approximation defined in \eqref{DHKM:APP_def} is bounded tightly above as
 \begin{equation} \label{DHKM:APP_errorBd}
@@
 
-To facilitate the proof of this theorem and theorems below, we first establish the following lemma:
-
-\begin{lemma}
-Let $\calK$ be some subset of $\bbK$.
-\end{lemma}
-
-\begin{proof}[Proof of Theorem \ref{DHKM:APP_optimality_thm}]
+\begin{proof}
 The proof of \eqref{DHKM:APP_errorBd} follows from an argument similar to that used to derive 
@@
 
- Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.  Choose $f$ to satisfy the following conditions:
+ Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.  Use Lemma \ref{DHKM:Key_Lem} to choose $f$ to satisfy the following conditions:
 \begin{gather*}
-    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ \Bignorm[\tau]{\bigl(\hf_{\bsk}\bigr)_{\bsk \notin \calJ}}
+    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ \Bignorm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \notin \calJ}}
     = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
@@
 \begin{align*}
-\MoveEqLeft{\max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)}} \\
-&=  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)} \\
+\MoveEqLeft{\max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)} =  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)}} \\
 & \ge \frac 12 \left [ \norm[\calG]{\SOL(f) - \APP'(0,n)} 
@@
 & \ge \norm[\calG]{\SOL(f)} 
-= \Bignorm[\tau]{\bigl(\hf_{\bsk}\bigr)_{\bsk \notin \calJ}}
+= \Bignorm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \notin \calJ}}
     = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \FredNote{I think that this is a simpler case than \cite{DinHic20a} or the work with Simon, so we should start with this}
@@
 	\begin{algorithmic}
-	\PARAM an initial sample size, $n_1$; an inflation factor, $\frakC$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
+	\PARAM an initial sample size, $n_1 \in \N$; an inflation factor, $\frakC > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 \end{equation}
-and the computational complexity has the lower bound
-\begin{equation}
-    a
+The computational complexity has the lower bound
+\begin{equation} \label{DHKM:PilotConeAlg_comp}
+        \COMP(\calA(\calC),\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le 2\varepsilon/[(1 - 1/\frakC) R] \right \}.
 \end{equation}
@@
 
-\begin{proof}
+\begin{proof} \FredNote{Fred is working on this proof.}
 The upper bound on the computational cost of this algorithm is obtained by noting that 
@@
 \end{align*}
-since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le R$ for all $f \in \calB_R$.
+since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le \norm[\calF]{f} \le R$ for all $f \in \calB_R$.
 Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
@@
 
-To prove the lower complexity 
+To prove the lower complexity bound, let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.
+Fix $R$ and $\varepsilon$ arbitarily.
+Define $\calK_1 := \{\bsk_1, \ldots, \bsk_{n_1}\}$.
+Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.
+
+The input function $f_1$ is defined via its series coefficients as in Lemma \ref{DHKM:Key_Lem}, having nonzero coefficients only for $\bsk \in \calK_1$:
+\begin{equation*}
+    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/\frakC) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
+    0, & \bsk \notin \calK_1,
+    \end{cases}
+   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/\frakC)}{2}.
+\end{equation*}
+Suppose that $\ALG'(f_1,\varepsilon)$ samples the series coefficients $f_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
+
+Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$ and also as in Lemma \ref{DHKM:Key_Lem}:
+\begin{gather}
+\nonumber
+    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/\frakC) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
+    0, & \bsk \in \calJ, 
+    \end{cases}
+    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/\frakC)}{2}, \\
+    \label{DHKM:SOLf2bd}
+    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
+\end{gather}
+Let $f_{\pm} = f_1 \pm f_2$.  By the definitions above, it follows that
+\begin{align}
+    \norm[\calF]{f_{\pm}} &= \norm[\calF]{ f_1 \pm f_2 } \le \norm[\calF]{ f_1} + \norm[\calF]{ f_2 } =  R, \\
+    \nonumber
+    \norm[\rho]{\left( \frac{\hf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
+    & = \norm[\rho]{\left( \frac{\hf_1(\bsk_i) \pm \hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \nonumber
+    & \ge \norm[\rho]{\left( \frac{\hf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \nonumber
+    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{\frakC} \\
+    & \ge \frac{\norm[\calF]{f_{\pm}}}{\frakC}.
+\end{align}
+Therefore, $f_\pm \in \calC \cap \calB_R$.
+Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.
+Thus, $\SOL(f_{\pm})$ must be similar to each other.
+
+Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
+\begin{align*}
+\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
+=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
+& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
++ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
+& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
+=\frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
+& \ge \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
+\end{align*}
+by the ordering of the $\bsk_i$.  This inequality implies complexity bound \eqref{DHKM:PilotConeAlg_comp}.
 \end{proof}
 
-Since error bound
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Tracking the Decay Rate of the Fourier Coefficients} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\FredNote{The \cite{DinHic20a} case with tractability}
 
-\subsection{A subsection}
-
-\section{The \cite{DinHic20a} case with tractability, which needs a better title}
-
-\section{The work with Simon case, which needs a better title}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{
+.0
+.
+.} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\FredNote{The work with Simon}
 

### 2019-01-10 DingHickKritzMakRICAMChap.tex
update

@@
 
+\usepackage[notref,notcite]{showkeys}
+
 %% Beginning of author included packages and defined macros
@@
 \usepackage{algpseudocode}
+\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
 \algnewcommand\algorithmicparam{\textbf{Parameters:}}
@@
 
+\allowdisplaybreaks
+
 %% End of author included packages and defined macros
@@
   \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
-  \affil[3]{...}
+  \affil[3]{Johann Radon Institute for Computational and Applied Mathematics (RICAM), 
+  Austrian Academy of Sciences, Altenbergerstr. 69, 4040 Linz, Austria}
   \affil[4]{...}
@@
 
-Adaptive algorithms may perform better in the set of input functions is not convex, and that is the situation studied here.
+Adaptive algorithms may perform better if the set of input functions is not convex, and that is the situation studied here.
 We propose adaptive algorithms for general multivariate linear problems where the input function lies in a non-convex cone.
@@
 \FredNote{I am trying to capture the case $\rho = \tau = 2, \ \rho' = \infty$ in \cite{DinHic20a} and the case $\rho = \infty, \ \rho' = \tau = 1$ in the work with Simon.}
+\PeterNote{Should not $\rho'$ be 2 in the Ding et al. case?}
+
 Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
@@
 \begin{equation} \label{DHKM:APP_def}
-    \APP : \calF \times \N_0 \to \calG, \qquad  \APP(f,n) := \sum_{i=1}^n \hf(\bsk) v_{\bsk}, \quad \APP(f,0) = 0.
+    \APP : \calF \times \N_0 \to \calG, \qquad  \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i}, \quad \APP(f,0) = 0.
 \end{equation}
@@
 
-\FredNote{Peter please add here.}
+\PeterNote{Why do we need the product structure?}
+
+\FredNote{If we don't need it then, let's not introduce it.  But I think that at some point we may want it.}
+
+\PeterNote{I agree.}
+
+\PeterNote{started working on general tractability notions here.
+
+\bigskip
+
+We would like to study how $\COMP(\calA(\calC), \varepsilon,R)$ 
+depends on the dimension $d$ and the error threshold $\varepsilon$.
+This is described by defining various notions of tractability.
+Roughly speaking, the different tractability notions correspond to different
+ways of how the complexity $\COMP(\calA(\calC), \varepsilon,R)$ depends on $d$ and $\varepsilon$. Since 
+the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent 
+to the problem, not to a particular algorithm. 
+We define the following notions of tractability (for further information on tractability we refer to the trilogy 
+\cite{NovWoz08a}, \cite{NovWoz10a}, \cite{NovWoz12a}).
+
+\begin{itemize}   
+\item We say that the adaptive approximation problem is strongly polynomially tractable
+if and only if there are non-negative $C$ and $p$ such that   
+for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
+$$   
+\COMP(\calA(\calC), \varepsilon,R)\le C\,\varepsilon^{-p}.
+$$   
+The infimum of $p$ satisfying the bound above is denoted by $p^*$   
+and is called the exponent of strong polynomial tractability.    
+\newline \qquad
+
+\item    
+We say that the problem is polynomially tractable
+if and only if there are non-negative $C,p$, and $q$ such that   
+for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
+$$   
+\COMP(\calA(\calC), \varepsilon,R)\le C\,d^{\,q}\,   
+\varepsilon^{-p}.   
+$$   
+\vskip 0.5pc     
+\item   
+We say that the problem is quasi-polynomially tractable if and only if there are non-negative $C$ and $p$ such that   
+for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have    
+$$   
+\COMP(\calA(\calC), \varepsilon,R)\le   
+C\,\exp\left(p\,(1+\log\,d)(1+\log\,\varepsilon^{-1})\right).   
+$$    
+The infimum of $p$ satisfying the bound above is denoted by $p^*$   
+and is called the exponent of quasi-polynomial tractability.    
+\newline \qquad
+
+\item   
+We say that the problem is $(s,t)$-weakly tractable for positive $s$ and $t$ iff    
+$$   
+\lim_{d+\varepsilon^{-1}\to\infty}\   
+\frac{\log\, \COMP(\calA(\calC), \varepsilon,R)}   
+{d^{\,t}+\varepsilon^{-s}}\,=\,0.   
+$$    
+\newline \qquad
+
+\item    
+We say that the problem is uniformly weakly tractable if and only if it 
+is $(s,t)$-weakly tractable for all positive $s$ and $t$.    
+\end{itemize}
+
+}
 
@@
 \FredNote{I think that this is a simpler case than \cite{DinHic20a} or the work with Simon, so we should start with this}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The Cone and the Optimal Algorithm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{equation} \label{DHKM:PilotConeAlg_comp}
-        \COMP(\calA(\calC),\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+        \COMP(\calA(\calC),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
     \le 2\varepsilon/[(1 - 1/\frakC) R] \right \}.
@@
 
-\begin{proof} \FredNote{Fred is working on this proof.}
+\begin{proof} 
 The upper bound on the computational cost of this algorithm is obtained by noting that 
@@
 To prove the lower complexity bound, let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.
-Fix $R$ and $\varepsilon$ arbitarily.
+Fix $R$ and $\varepsilon$ arbitrarily.
 Define $\calK_1 := \{\bsk_1, \ldots, \bsk_{n_1}\}$.
@@
 \end{align*}
-by the ordering of the $\bsk_i$.  This inequality implies complexity bound \eqref{DHKM:PilotConeAlg_comp}.
+by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.  This inequality implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
 \end{proof}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tractability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\FredNote{Next should come tractability}
+
+\PeterNote{It seems to me that we can handle this case by an analogy to tractability for the 
+average case setting. There, the complexity also depends on the truncated trace of the eigenvalues.}
+\FredNote{Agreed.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Necessary Condition for the Input Function to Lie in the Cone}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\FredNote{Fred should add about the necessary conditions.}
+Although we may not be able to guarantee that the particular $f$ of interest lies in the cone, $\calC$, we may derive necessary conditions for $f \in \calC$.
+The following proposition follows from the definition of $\calC$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.
+
+\begin{proposition}
+If $f \in \calC$ and $n^*$ is defined as in Algorithm \ref{DHKM:PilotConeAlg}, then 
+\begin{equation} \label{DHKM:PilotConeNecessary}
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n^*}} \le \frakC 
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n_1}}.
+\end{equation}
+\end{proposition}
+
+If it is found in practice that condition \eqref{DHKM:PilotConeNecessary} is violated, then Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
+An alternative is to make the cone more inclusive by increasing $\frakC$ and/or $n_1$.
 
@@
 
+From the argument leading to \eqref{DHKM:SOL_A} it follows that 
+\begin{equation} \label{DHKM:APP_Err_Coef}
+    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
+\end{equation}
+Thus, the faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
+A disadvantage of Algorithm \ref{DHKM:PilotConeAlg} is that it cannot adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
+In this section, we develop an algorithm that can do so.
+
+Let $(n_j)_{j\ge 0}$ be a strictly increasing sequence of non-negative integers.
+This sequence may increase geometrically or algebraically.
+For any $f \in \calF$, define the partial sums of powers of series coefficients:
+\[
+\sigma_j (f):=\norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n_{j-1}-1}^{n_j}} \qquad \text{for}\ j \in \N,
+\]
+We now define the cone of input functions, $\calC$, by
+\begin{equation} \label{DHKM:TrackConeDef}
+  \calC : =\left\{f\in\calF \colon \sigma_{j+r} (f)\le ab^r \sigma_j (f)\ \forall j,r\in\NN\right\}.
+\end{equation}
+Here, $a$ and $b$ are positive reals with $b< 1 < a$.
+The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
+Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $S(f)$, to decay monotonically.
+However, we expect their partial sums to decay steadily.
+
+From the expression for the error in \label{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, one can now derive a data-driven error bound for $j \in \bbN$:
+\begin{align}
+\nonumber
+\norm[\calG]{\SOL(f)-\APP(f,n_j)} &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty} \\
+\nonumber 
+& = \left\{\sum_{r=1}^\infty \sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \abs{\hf(\bsk_i) }^{\tau}  \right\}^{1/\tau} = \norm[\tau]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
+&\le \norm[\tau]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}}
+ = \displaystyle a \left(\frac{b^\tau}{1 - b^\tau} \right)^{1/\tau} \sigma_{j}(f)
+ \label{DHKM:algoineq}
+\end{align}
+This upper bound depends only on the function data and the parameters defining $\calC$.
+The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.
+Moreover, the error of $\APP(f,n_j)$ is asymptotically no worse than $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
+
+\FredNote{Perhaps Yuhan can fill in here following our \cite{DinHic20a} paper.}
+
+\FredNote{Pity, I do not see our cost upper bounds reflecting different rates of decay of the series coefficients.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Adaptive Algorithm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{algorithm}
+	\caption{Adaptive ALG for a Cone of Input Functions} 
+	\begin{algorithmic}
+	\PARAM a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0},$ where $j \in \N$ starts from 1;  $\APP$ satisfying \eqref{DHKM:algoineq}
+		\INPUT a black-box function, $f$; an absolute error tolerance,
+		$\varepsilon>0$
+
+\Ensure  Choose $j^* =  \min \left \{j \in \N : 
+\sigma_{j}(f) < \frac{\varepsilon}{a}\left(\frac{1 - b^\tau}{b^\tau} \right)^{1/\tau} 
+\right \}$
+
+\RETURN $\ALG(f,\varepsilon) = \APP(f,j^*)$
+\end{algorithmic}
+\end{algorithm}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{
-.0
-.
-.} 
+\section{Inferring Coordinate Importance and Smoothness} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{acknowledgement}
-  ...
+ P.~Kritzer gratefully acknowledges support by the Austrian Science Fund (FWF) Project  F5506-N26, 
+which is part of the Special Research Program ``Quasi-Monte Carlo Methods: Theory and Applications''.
 \end{acknowledgement}

### 2019-01-26 DingHickKritzMakRICAMChap.tex
updates

@@
 \usepackage{amsmath,amssymb}
+\usepackage{subcaption}
 \input{macros}
@@
 
+\theoremstyle{dgthm}
+\newtheorem{theorem}{Theorem}
+\theoremstyle{dgthm}
+\newtheorem{lemma}{Lemma}
+\theoremstyle{dgthm}
+\newtheorem{corollary}{Corollary}
+\theoremstyle{dgthm}
+\newtheorem{proposition}{Proposition}
+\theoremstyle{dgdef}
+\newtheorem{remark}{Remark}
+
 \DeclareMathOperator{\SOL}{SOL}
@@
 \DeclareMathOperator{\ERR}{ERR}
-\newcommand{\dataN}{\bigl\{\hf(\bsk_i)\bigr\}_{i=1}^n}
+\newcommand{\dataN}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^n}
 \newcommand{\ERRN}{\ERR\bigl(\dataN,n\bigr)}
@@
 \newcommand{\tv}{\Tilde{v}}
+\newcommand{\tcalK}{\widetilde{\calK}}
 \newcommand{\tlambda}{\Tilde{\lambda}}
@@
 \newcommand{\FredNote}[1]{{\color{blue}Fred: #1}}
-\newcommand{\YuhanNote}[1]{{\color{green}Yuhan: #1}}
+\newcommand{\YuhanNote}[1]{{\color{magenta}Yuhan: #1}}
 \newcommand{\PeterNote}[1]{{\color{orange}Peter: #1}}
 \newcommand{\SimonNote}[1]{{\color{purple}Simon: #1}}
+\newcommand{\tLambda}{\widetilde{\Lambda}}
 %\newcommand{\HickernellFJ}{Hickernell}
@@
   \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
-  \affil[1]{...}
+  \affil[1]{Department of Mathematics, 
+  Misericorida University, 301 Lake Street, Dallas, PA 18704 USA}
   \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
@@
 Adaptive algorithms may perform better if the set of input functions is not convex, and that is the situation studied here.
-We propose adaptive algorithms for general multivariate linear problems where the input function lies in a non-convex cone.
+We propose adaptive algorithms for general multivariate linear problems where the input function lies in non-convex cones.
 Our algorithms use series coefficients of the input function to construct an approximate solution that satisfies an absolute error tolerance.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our general linear problem is defined by a solution operator that takes the input function to the solution, $\SOL:\calF \to \calG$.
-The spaces of inputs and outputs are defined in terms of series expansions:
+Our general linear problem is defined by a solution operator that mapping an input function to an output, $\SOL:\calF \to \calG$.
+The Banach spaces of inputs and outputs are defined by series expansions:
 \begin{gather}
-    \calF = \left \{f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \\
-    \calG = \left \{g = \sum_{\bsk \in \mathbb{K}} \hg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \hg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} \right\}, \quad \tau \le \rho.
+    \calF = \left \{f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad 1 \le \rho \le \infty, \\
+    \calG = \left \{g = \sum_{\bsk \in \mathbb{K}} \hg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \hg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad 1 \le \tau \le \rho.
 \end{gather}
-Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$ and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$.
+Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$.
 These bases are defined to match the solution operator:
-\begin{equation}
+\begin{equation} \label{DHKM:basis_relate}
     \SOL(u_{\bsk}) = v_{\bsk} \qquad \forall \bsk \in \mathbb{K},
 \end{equation}
-where $\mathbb{K}$ is a general index set.
+where $\mathbb{K}$ is a general index set. The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.
 
-To facilitate derivations below, we establish the following lemma:
+Although this problem formulation is quite general in some aspects, condition \eqref{DHKM:basis_relate} may be somewhat restrictive.
+In theory, the choice of basis can be made via the singular value decomposition, but in practice, if $\calF$ and $\calG$ have common norms, bases satisfying \eqref{DHKM:basis_relate} may be difficult to identify explicitly.
+
+To facilitate our derivations below, we establish the following lemma:
 
@@
 \begin{equation*}
-    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
+    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau, \qquad \text{i.e., } \rho' = \frac{\rho \tau}{\rho - \tau},
 \end{equation*}
-\FredNote{I am trying to capture the case $\rho = \tau = 2, \ \rho' = \infty$ in \cite{DinHic20a} and the case $\rho = \infty, \ \rho' = \tau = 1$ in the work with Simon.}
-\PeterNote{Should not $\rho'$ be 2 in the Ding et al. case?}
-
-Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
-\begin{equation}
+so $\tau \le \rho' < \infty$.  Let $\Lambda =  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$.  Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
+\begin{gather}
 \label{DHKM:SOL_ineq}
-    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
-    \end{equation}
-    \begin{multline}
+    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \Lambda,
+    \\
     \label{DHKM:SOL_tight_ineq}
-    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} \quad \forall \bsk \in \calK\\
-    \implies \norm[\calG]{\SOL(f)} = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \ \& \ \norm[\calF]{f} = R.
-    \end{multline}
-Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} tight.
+    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\Lambda^{\rho'/\rho}} \quad \forall \bsk \in \calK \ \ 
+    \implies  \ \ \norm[\calF]{f} = R \ \& \ \norm[\calG]{\SOL(f)} = R \Lambda.
+    \end{gather}
+Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} may be made tight.
 \end{lemma}
 \begin{proof}
-The proof proceeds by applying H\"older's inequality
+The proof of inequality \eqref{DHKM:SOL_ineq} proceeds by applying H\"older's inequality:
 \begin{align}
@@
     \nonumber
-    & = \norm[\calF]{f} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}},
+    & = \norm[\calF]{f} \, \Lambda.
 \end{align}
-which establishes inequality \eqref{DHKM:SOL_ineq}.
-Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
+Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into equation \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
 \begin{equation*}
        \norm[\calG]{\SOL(f)}  
-    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
+    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\Lambda^{\rho'/\rho}} 
     = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
-    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}.
+    {\Lambda^{\rho'/\rho}} = R \Lambda.
 \end{equation*}
@@
     = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
-    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} 
-    = \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
-    {\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}} = R.
+    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\Lambda^{\rho'/\rho}} 
+    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
+    {\Lambda^{\rho'/\rho}} = R.
 \end{equation*}
@@
 
-Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
+\hspace{\parindent} Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
 \begin{equation} \label{DHKM:SOLNorm}
@@
 \end{equation}
-
 The $\lambda_{\bsk}$ define the smoothness of the input space and have a known order:
 \begin{equation} \label{DHKM:lambda_order}
-    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots.
+    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots >0.
 \end{equation}
+We assume that all $\lambda_{\bsk_i}$ are positive to avoid the trivial case where the problem can be solved by knowing a finite number of series coefficients.
 An optimal approximation  based on $n$ series coefficients of the input function can be defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
@@
 
-\hspace{\parindent} While approximation $\APP$ is a key component, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion
+\hspace{\parindent} While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion
 \begin{equation} \label{DHKM:err_crit}
@@
 
-In contrast to \eqref{DHKM:APP_errorBd}, we will construct data-based error bounds for $\APP(f,n)$, which will lead to \emph{adaptive} algorithms $\ALG$ satisfying \eqref{DHKM:err_crit}.
+In contrast to error bound \eqref{DHKM:APP_errorBd}, we will construct data-based error bounds for $\APP(f,n)$, which will lead to \emph{adaptive} algorithms $\ALG$ satisfying \eqref{DHKM:err_crit}.
 For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}.
@@
 
-Note that algorithms satisfying \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$ if $\SOL(\calF)$ is infinite dimensional.
+Note that algorithms satisfying \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$.
 No matter how large a sample size is required by an algorithm, it is finite.
@@
 
-Let $\calA(\calC)$ denote the set of all possible algorithms that may be constructed using series coefficients.
+Let $\calA(\calC)$ denote the set of all possible algorithms that may be constructed using series coefficients and that \emph{satisfy error criterion \eqref{DHKM:err_crit}}.
 We define the \emph{computational complexity} of a problem as the information cost of the best algorithm:
@@
 We define an algorithm to be \emph{essentially optimal} if there exists some fixed positive $\omega$ for which
-\begin{equation*}
+\begin{equation} \label{DHKM:EssentialOpt}
     \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calA(\calC), \omega \varepsilon,R) \qquad \forall \varepsilon,R > 0.
-\end{equation*}
+\end{equation}
 This means that the dependence of 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tractability}
+\subsection{Tractability}\label{DHKM:secTractability}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Besides understanding the dependence of the computational complexity on $\varepsilon$, we also want to understand how the computational complexity depends on the dimension of the domain of the input function.
+
+Besides understanding the dependence of the computational complexity on $\varepsilon$, we also want to understand how this quantity depends on the dimension of the domain of the input function.
 Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
@@
 \end{gather*}
-The cone of functions for which our algorithms succeed, $\calC_d$ will also depend on the dimension.
+The cone of functions for which our algorithms succeed, $\calC_d$, will also depend on the dimension.
 Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
-
-\PeterNote{Why do we need the product structure?}
-
-\FredNote{If we don't need it then, let's not introduce it.  But I think that at some point we may want it.}
-
-\PeterNote{I agree.}
-
-\PeterNote{started working on general tractability notions here.
 
@@
 
-We would like to study how $\COMP(\calA(\calC), \varepsilon,R)$ 
+We would like to study how $\COMP(\calA(\calC_d), \varepsilon,R)$ 
 depends on the dimension $d$ and the error threshold $\varepsilon$.
@@
 Roughly speaking, the different tractability notions correspond to different
-ways of how the complexity $\COMP(\calA(\calC), \varepsilon,R)$ depends on $d$ and $\varepsilon$. Since 
-the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent 
-to the problem, not to a particular algorithm. 
+ways of how the complexity $\COMP(\calA(\calC_d), \varepsilon,R)$ depends on $d$ and $\varepsilon$. Since 
+the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
 We define the following notions of tractability (for further information on tractability we refer to the trilogy 
@@
 $$   
-\COMP(\calA(\calC), \varepsilon,R)\le C\,\varepsilon^{-p}.
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,\varepsilon^{-p}.
 $$   
@@
 $$   
-\COMP(\calA(\calC), \varepsilon,R)\le C\,d^{\,q}\,   
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,   
 \varepsilon^{-p}.   
@@
 \vskip 0.5pc
-\item   
-We say that the problem is quasi-polynomially tractable if and only if there are non-negative $C$ and $p$ such that   
-for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have    
-$$   
-\COMP(\calA(\calC), \varepsilon,R)\le   
-C\,\exp\left(p\,(1+\log\,d)(1+\log\,\varepsilon^{-1})\right).   
-$$    
-The infimum of $p$ satisfying the bound above is denoted by $p^*$   
-and is called the exponent of quasi-polynomial tractability.    
-\newline \qquad
 
 \item   
-We say that the problem is $(s,t)$-weakly tractable for positive $s$ and $t$ iff    
+We say that the problem is weakly tractable iff    
 $$   
 \lim_{d+\varepsilon^{-1}\to\infty}\   
-\frac{\log\, \COMP(\calA(\calC), \varepsilon,R)}   
-{d^{\,t}+\varepsilon^{-s}}\,=\,0.   
+\frac{\log\, \COMP(\calA(\calC_d), \varepsilon,R)}   
+{d+\varepsilon}\,=\,0.   
 $$    
-\newline \qquad
-
-\item    
-We say that the problem is uniformly weakly tractable if and only if it 
-is $(s,t)$-weakly tractable for all positive $s$ and $t$.    
 \end{itemize}
 
-}
+Necessary and sufficient conditions on these tractability notions will be studied 
+for different types of algorithms in Sections \ref{DHKM:SecPilotTract} and \ldots .
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\FredNote{I think that this is a simpler case than \cite{DinHic20a} or the work with Simon, so we should start with this}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The idea behind an adaptive algorithm is that the finite information we observe about input function that tells us something about what is not observed about the input function.
-Let $n_1$ some positive integer and $\frakC$ be some constant greater than one.
-The cone of functions whose norm can be bounded well in terms of a pilot sample of the first $n_1$ series coefficients is given by
+The premise of an adaptive algorithm is that the finite information we observe about the input function that tells us something about what is not observed about the input function.
+Let $n_1$ denote the number of pilot samples to be observed, based on the wave numbers
+\begin{equation} \label{DHKM:KOnedef}
+    \calK_1 := \{\bsk_1, \ldots, \bsk_{n_1} \},
+\end{equation}
+where the $\bsk_i$ are given by the ordering of the $\lambda_{\bsk}$ in \eqref{DHKM:lambda_order}.
+Let $a$ be some constant inflation factor greater than one.
+The cone of functions whose norm can be bounded well in terms of a pilot sample
+is given by
 \begin{equation} \label{DHKM:pilot_cone}
-    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\},
+    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le a \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\},
 \end{equation}
-where the $\bsk_i$ are given by the ordering of the $\lambda_{\bsk}$ in \eqref{DHKM:lambda_order}. Define the data-based error bound,
+Define the data-based error bound,
 \begin{equation} \label{DHKM:pilot_errbd}
     \ERRN : =  
-    \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
+    a \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
     \qquad n > n_1.
@@
 	\begin{algorithmic}
-	\PARAM an initial sample size, $n_1 \in \N$; an inflation factor, $\frakC > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
+	\PARAM an initial sample size, $n_1 \in \N$; an inflation factor, $a > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 
-\begin{theorem}
-Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}.  The computational cost of this algorithm is 
+\begin{theorem} \label{DHKM:PilotCostThm}
+Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC)$ for $\calC$ defined in \eqref{DHKM:pilot_cone}.
+The information cost is
 \begin{equation} \label{DHKM:PilotConeAlg_cost}
     \COST(\ALG,\calC,\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \varepsilon/(\frakC R) \right \}.
+    \le \varepsilon/(a R) \right \}.
 \end{equation}
@@
         \COMP(\calA(\calC),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le 2\varepsilon/[(1 - 1/\frakC) R] \right \}.
+    \le 2\varepsilon/[(1 - 1/a) R] \right \}.
 \end{equation}
+Therefore, Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.
 \end{theorem}
@@
      & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
-     \frakC \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
+     a \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
      \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
@@
      & \le \min \left \{n \ge n_1 : 
-     \frakC R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
+     a R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
     \le \varepsilon \right \},  
@@
 Fix $R$ and $\varepsilon$ arbitrarily.
-Define $\calK_1 := \{\bsk_1, \ldots, \bsk_{n_1}\}$.
 Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.
@@
 \begin{equation*}
-    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/\frakC) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
+    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/a) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
     0, & \bsk \notin \calK_1,
     \end{cases}
-   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/\frakC)}{2}.
+   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/a)}{2}.
 \end{equation*}
-Suppose that $\ALG'(f_1,\varepsilon)$ samples the series coefficients $f_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
+Suppose that $\ALG'(f_1,\varepsilon)$ samples the series coefficients $\hf_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
 
@@
 \nonumber
-    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/\frakC) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
+    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/a) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
     0, & \bsk \in \calJ, 
     \end{cases}
-    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/\frakC)}{2}, \\
+    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/a)}{2}, \\
     \label{DHKM:SOLf2bd}
-    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
+    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/a)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
 \end{gather}
@@
     \nonumber
-    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{\frakC} \\
-    & \ge \frac{\norm[\calF]{f_{\pm}}}{\frakC}.
+    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{a} \\
+    & \ge \frac{\norm[\calF]{f_{\pm}}}{a}.
 \end{align}
@@
 & \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
-=\frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
-& \ge \frac{R(1 - 1/\frakC)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
+=\frac{R(1 - 1/a)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
+& \ge \frac{R(1 - 1/a)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
 \end{align*}
-by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.  This inequality implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
+by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.  This inequality implies the lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
+
+The essential optimality of Algorithm \ref{DHKM:PilotConeAlg} follows by observing that 
+\[
+\COST(\ALG,\calC,\varepsilon,R) \le \COMP(\calA(\calC),\omega \varepsilon,R) \qquad \text{for } \omega = (1-1/a)/(2a).
+\]
+This satisfies definition \eqref{DHKM:EssentialOpt}.
 \end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tractability}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\FredNote{Next should come tractability}
-
-\PeterNote{It seems to me that we can handle this case by an analogy to tractability for the 
-average case setting. There, the complexity also depends on the truncated trace of the eigenvalues.}
-\FredNote{Agreed.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\FredNote{Fred should add about the necessary conditions.}
-Although we may not be able to guarantee that the particular $f$ of interest lies in the cone, $\calC$, we may derive necessary conditions for $f \in \calC$.
+We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC$, but we may derive necessary conditions for $f$ to lie in $\calC$.
 The following proposition follows from the definition of $\calC$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.
@@
 \begin{equation} \label{DHKM:PilotConeNecessary}
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n^*}} \le \frakC 
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n_1}}.
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n^*}} \le a 
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}.
 \end{equation}
@@
 
-If it is found in practice that condition \eqref{DHKM:PilotConeNecessary} is violated, then Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
-An alternative is to make the cone more inclusive by increasing $\frakC$ and/or $n_1$.
+If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
+The remedy is to make $\calC$ more inclusive by increasing the inflation factor, $a$, and/or the pilot sample size, $n_1$.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tracking the Decay Rate of the Fourier Coefficients} 
+\subsection{Tractability}\label{DHKM:SecPilotTract}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\FredNote{The \cite{DinHic20a} case with tractability}
+
+In this section, we write again $\calC_d$ instead of $\calC$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
+Recall that we assume that
+$\lambda_{d,\bsk_1}\ge \lambda_{d,\bsk_2}\ge \cdots >0$. From 
+Equations \eqref{DHKM:PilotConeAlg_cost} and \eqref{DHKM:PilotConeAlg_comp}, we obtain that 
+\[
+        \COMP(\calA(\calC_d),\varepsilon,R)  \asymp \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le \varepsilon\, D(a,R) \right \},
+\]
+where $D(a,R)$ is a positive constant that may depend on $a$ and $R$, but does not depend on $d$ and $\varepsilon$.
+We would like to study under which conditions we obtain the various tractability notions defined in Section \ref{DHKM:secTractability}.
+
+Since $\lambda_{\bsk_i}>0$, and since we are interested in the asymptotic behavior 
+of $\COMP(\calA(\calC_d),\varepsilon,R)$ when $d$ and/or $\varepsilon^{-1}$ tend to infinity, it is sufficient to consider the quantity 
+\[
+n(\varepsilon,d)=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le \varepsilon \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R) ,
+\]
+for $\varepsilon \in (0,1)$ and $d\in\NN$.
+To this end, we distinguish two cases, depending on whether $\rho'$ is infinite or not. This 
+distinction is useful because it allows us to relate the computational complexity of the algorithms 
+considered in this paper to the computational complexity of linear problems considered over the 
+unit ball of certain function spaces. Then, the case $\rho'=\infty$ corresponds to the so-called 
+worst-case setting, and the case $\rho<\infty$ corresponds to the so-called average-case setting. 
+For both of these settings there exist tractability results that we will make use of here.
+
+\paragraph*{CASE 1: $\rho'=\infty$:}
+
+If $\rho'=\infty$, we have due to the monotonicity of the $\lambda_{\bsk_i}$, 
+\[
+n(\varepsilon,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
+    \le \varepsilon \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R).
+\]
+We then have the following theorem.
+
+\begin{theorem} \label{DHKM:thmtract1}
+Using the same notation as above, the following statements hold for the case $\rho'=\infty$.
+ \begin{itemize}
+  \item[1.] 
+  We have strong polynomial tractability if and only if there exist $\eta>0$ and $i_0\in\NN$ such that
+ \begin{equation}\label{DHKM:eq:condspt}
+    \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^\eta < \infty.
+ \end{equation}
+ Furthermore, the exponent of strong polynomial tractability is then equal to the infimum of those $\eta>0$ for which \eqref{DHKM:eq:condspt} holds. 
+ \item[2.] 
+  We have polynomial tractability if and only if there exist $\eta_1, \eta_2 \ge 0$ and $\eta_3, K>0$ such that
+ \[
+    \sup_{d\in\NN} d^{-\eta_1}\, \sum_{i=\lceil K d^{\eta_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\eta_3} < \infty.
+ \]
+ \item[3.] 
+ We have weak tractability if and only if 
+ \begin{equation}\label{DHKM:eq:condwt}
+  \sup_{d\in\NN} \, \exp(-cd) \sum_{i=1}^\infty \exp\left(-c\left(\frac{1}{\lambda_{d,\bsk_i}}\right)\right) <\infty\quad \mbox{for all}\quad c>0.
+ \end{equation}
+\end{itemize}
+\end{theorem}
+
+\begin{proof}
+Letting $\widetilde{\varepsilon}:=\sqrt{\varepsilon}$, we see that 
+$n(\varepsilon,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
+The latter expression is well studied in the context of tractability of linear problems in the worst-case setting defined on unit balls of certain spaces, and if and only if conditions on the $\lambda_{d,\bsk_i}$ for various tractability notions are known.
+These conditions can be found in \cite[Chapter 5]{NovWoz08a} for (strong) polynomial tractability and  \cite{WerWoz17} for weak tractability.
+
+Since, in this paper, we consider $\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \varepsilon \right \}$, and \cite{NovWoz08a} and
+\cite{WerWoz17} study $\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$, 
+there are slight differences between the results here and those in the aforementioned references; to be more precise, the exponent of strong polynomial tractability is $\eta$ here, whereas corresponds to $2\eta$ in \cite{NovWoz08a}, and $1/\lambda_{d,\bsk_i}$ in \eqref{DHKM:eq:condwt} corresponds to $1/\sqrt{\lambda_{d,\bsk_i}}$ in \cite{WerWoz17}.
+\end{proof}
+
+\paragraph*{CASE 2: $\rho'<\infty$:}
+
+In this case, we have 
+\[
+n(\varepsilon,d)=\min \left \{n\ge 0\colon 
+\sum_{i=n+1}^\infty \lambda_{d,\bsk_i}^{\rho'}\,
+    \le \varepsilon^{\rho'} \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R).
+\]
+Let $\widetilde{\varepsilon}:=\varepsilon^{\rho'/2}$ and 
+$\widetilde{\lambda}_{d,i}:=\lambda_{d,\bsk_i}^{\rho'}$, then
+\begin{equation}\label{DHKM:eqaveragetract}
+n(\varepsilon,d)=\min \left \{n\ge 0\colon 
+\sum_{i=n+1}^\infty \widetilde{\lambda}_{d,i}\,
+    \le \widetilde{\varepsilon}^{\,2} \right \},
+\end{equation}
+However, the latter expression corresponds exactly to the 
+average-case tractability (with respect to the parameters 
+$\widetilde{\lambda}_{d,i}$ and $\widetilde{\varepsilon}$) defined 
+on unit balls of certain spaces as studied in, e.g., \cite{NovWoz08a}. 
+This leads us to the following theorem.
+\begin{theorem} \label{DHKM:thmtract2}
+Using the same notation as above, the following statements hold for the case $\rho'<\infty$.
+ \begin{itemize}
+  \item[1.] 
+  We have strong polynomial tractability if and only if there exist $\eta\in (0,1)$ and $i_0\in\NN$ such that
+ \begin{equation}\label{DHKM:eq:condspt1}
+    \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^{\rho'\,\eta} < \infty.
+ \end{equation}
+ Furthermore, the exponent of strong polynomial tractability is then 
+ \[
+ \inf\left\{\eta/(1-\eta)\colon \mbox{$\eta$ satisfies \eqref{DHKM:eq:condspt1}}\right\}.
+ \]
+ \item[2.] 
+  We have polynomial tractability if and only if there exist $\eta_1, \eta_2 \ge 0$ and $\eta_3\in (0,1), K>0$ such that
+ \[
+    \sup_{d\in\NN} d^{-\eta_1}\, \sum_{i=\lceil K d^{\eta_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\rho'\,\eta_3} < \infty.
+ \]
+ \item[3.] Let $t_{d,i}:=\sum_{k=i}^\infty \lambda_{d,\bsk_i}$.
+ We have weak tractability if and only if 
+ \[
+   \lim_{i\to\infty} t_{d,i}\, \log i^2=0\quad\mbox{for all $d$},
+ \]
+ and there exists a function $f:[0,1/2)\to \{1,2,3,\ldots\}$ such that
+\[
+  \sup_{\beta\in (0,1/2]}\, \beta^{-2} \,
+  \sup_{d\ge f(\beta)}\,\, \sup_{i\ge \lceil \exp (d\sqrt{b}) \rceil +1}\, \, \lim_{i\to\infty} t_{d,i}\, \log i^2
+  < \infty.
+\]
+ \end{itemize}
+\end{theorem}
+\begin{proof}
+  The proof of the theorem is similar to that of Theorem \ref{DHKM:thmtract1}, using \eqref{DHKM:eqaveragetract}.
+\end{proof}
+\begin{remark}
+  Results for further tractability notions, such as quasi-polynomial tractability or $(s,t)$-weak 
+  tractability, can be shown using similar arguments as above and results from \cite{KriWoz19}, \cite{NovWoz10a}, \cite{WerWoz17}, and the papers cited therein. 
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Tracking the Decay Rate of the Series Coefficients} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \end{equation}
-Thus, the faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
-A disadvantage of Algorithm \ref{DHKM:PilotConeAlg} is that it cannot adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
-In this section, we develop an algorithm that can do so.
+The faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
+Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
+It simply bounds $\norm[\calF]{f}$ based on a pilot sample.
+The algorithm presented in this section does track the rate of decay of the $\hf(\bsk_i)$ and terminate sooner if the $\hf(\bsk_i)$ decay more quickly.
 
@@
 This sequence may increase geometrically or algebraically.
-For any $f \in \calF$, define the partial sums of powers of series coefficients:
-\[
-\sigma_j (f):=\norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n_{j-1}-1}^{n_j}} \qquad \text{for}\ j \in \N,
-\]
-We now define the cone of input functions, $\calC$, by
+Define the sets of wavenumbers analogously to \eqref{DHKM:KOnedef}.
+\begin{equation}
+    \calK_0 : = \{\bsk_1, \ldots, \bsk_{n_0} \}, \qquad \calK_j := \{\bsk_{n_{j-1}+1}, \ldots, \bsk_{n_j}\} \quad \text{for } j \in \N.
+\end{equation}For any $f \in \calF$, define the partial sums of powers of series coefficients:
+\begin{equation} \label{DHKM:SigmaDef}
+\sigma_j (f):=\norm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \in \calK_j}} \qquad \text{for } j \in \N.
+\end{equation}
+For this section, we define the cone of input functions, $\calC$, by
 \begin{equation} \label{DHKM:TrackConeDef}
@@
 The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
-Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $S(f)$, to decay monotonically.
+Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
 However, we expect their partial sums to decay steadily.
+The series coefficients for  wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\calC$ and may be have erratically.
+If $n_0 = 0$, then $\calK_0$ is empty.
 
-From the expression for the error in \label{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, one can now derive a data-driven error bound for $j \in \bbN$:
+From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, one can now derive a data-driven error bound 
 \begin{align}
 \nonumber
-\norm[\calG]{\SOL(f)-\APP(f,n_j)} &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty} \\
+\norm[\calG]{\SOL(f)-\APP(f,n_j)} &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty} 
+= \norm[\tau]{\bigl(\sigma_l(f) \bigr)_{l = j+1}^\infty} \\
 \nonumber 
-& = \left\{\sum_{r=1}^\infty \sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \abs{\hf(\bsk_i) }^{\tau}  \right\}^{1/\tau} = \norm[\tau]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
-&\le \norm[\tau]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}}
- = \displaystyle a \left(\frac{b^\tau}{1 - b^\tau} \right)^{1/\tau} \sigma_{j}(f)
+& = \norm[\tau]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
+\nonumber
+&\le \norm[\tau]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}} \\
+& = \displaystyle \frac{ab  \sigma_{j}(f)}{(1 - b^\tau)^{1/\tau}} \quad \forall f \in \calC, \ j \in \bbN.
  \label{DHKM:algoineq}
@@
 
-\FredNote{Perhaps Yuhan can fill in here following our \cite{DinHic20a} paper.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The Adaptive Algorithm and Its
+ Computational Cost}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\FredNote{Pity, I do not see our cost upper bounds reflecting different rates of decay of the series coefficients.}
+The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\calC$ defined in \eqref{DHKM:TrackConeDef}.
+The following theorem establishes its viability and computational cost.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Adaptive Algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{algorithm}
-	\caption{Adaptive ALG for a Cone of Input Functions} 
+	\caption{Adaptive ALG for a Cone of Input Functions Tracking the Series Coefficient Decay Rate \label{DHKM:TrackConeAlg}}
 	\begin{algorithmic}
-	\PARAM a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0},$ where $j \in \N$ starts from 1;  $\APP$ satisfying \eqref{DHKM:algoineq}
+	\PARAM a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0},$ where $j \in \N$ starts from 1; an inflation factor, $a$; the general decay rate, $b$; $\APP$ satisfying \eqref{DHKM:APP_Err_Coef}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 
-\Ensure  Choose $j^* =  \min \left \{j \in \N : 
-\sigma_{j}(f) < \frac{\varepsilon}{a}\left(\frac{1 - b^\tau}{b^\tau} \right)^{1/\tau} 
-\right \}$
+\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:TrackConeDef}
 
-\RETURN $\ALG(f,\varepsilon) = \APP(f,j^*)$
+\State Let $j \leftarrow 0$
+\Repeat
+
+\State Let $j \leftarrow j + 1$
+
+\State Compute $\sigma_{j}(f)$ as defined in \eqref{DHKM:SigmaDef}
+
+\Until $\sigma_{j}(f) \le \varepsilon (1 - b^\tau)^{1/\tau}/ab$
+
+\RETURN $\ALG(f,\varepsilon) = \APP(f,n_{j})$
 \end{algorithmic}
@@
 
+\begin{theorem}\label{DHKM:TractConeCompCost}
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC)$ for $\calC$ defined in \eqref{DHKM:TrackConeDef}.
+The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
+\begin{equation} \label{DHKM:EqTractConejstar}
+j^* = \min\left \{ j \in \bbN : \sigma_{j}(f) \le \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{ab}   \right\}.
+\end{equation}
+Moreover, $\COST(\ALG,\calC,\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+\begin{equation} \label{DHKM:TractConejdagger}
+j^\dagger = \min \left \{j \in \bbN :  \norm[\rho]{\left(\frac{b^{1-j}}{a \Lambda_1}, \ldots, \frac{b^{-1}}{a \Lambda_{j-1}}, \frac{1}{ \Lambda_{j}} \right) } \ge \frac{Ra b}{\varepsilon (1 - b^\tau)^{1/\tau}}  \right\},
+\end{equation}
+where
+\begin{equation}
+    \label{DHKM:LambdaDef}
+ \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+This algorithm terminates for some $j = j^*$ because $\sigma_j(f) \le ab^{j-1} \sigma_{1}(f) \to 0$ as $j \to \infty$.
+The value of $j^*$ in \eqref{DHKM:EqTractConejstar} follows directly from the error criterion.
+The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
+
+For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
+To derive an upper bound on $\COST(\ALG,\calC,\varepsilon,R)$ we first note a key inequality involving the $\sigma_j(f)$ for all $f \in \calF$ and norms of subsequences of the $\lambda_{\bsk_i}$ for all $j \ge 1$.
+This inequality follows directly from H\"older's inequality:
+\begin{equation}\label{DHKM:SigmaInEq}
+ \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_j}} \ge 
+ \frac{ \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_j}}} {
+  \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}}
+ = \frac{\sigma_j(f) }{\Lambda_j}.
+\end{equation}
+
+For any $f \in  \calC \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
+\begin{align*}
+R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
+\ge \norm[\rho]{\left(\norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_j}} \right)_{j=1}^{j^\dagger}}
+\\
+& \ge \norm[\rho]{\left(\frac{\sigma_j(f)}{\Lambda_{j}} \right)_{j=1}^{j^\dagger}}  
+\qquad \text{by \eqref{DHKM:SigmaInEq} }\\
+& \ge \norm[\rho]{\left(\frac{b^{1-j^\dagger}\sigma_{j^\dagger}(f)}{a \Lambda_1}, \ldots, \frac{b^{-1}\sigma_{j^\dagger}(f)}{a \Lambda_{j^\dagger-1}}, \frac{\sigma_{j^\dagger}(f)}{ \Lambda_{j^\dagger}} \right) } \quad \text{by the definition of } \calC \text{ in \eqref{DHKM:TrackConeDef}}\\
+& = \sigma_{j^\dagger}(f)\norm[\rho]{\left(\frac{b^{1-j^\dagger}}{a \Lambda_1}, \ldots, \frac{b^{-1}}{a \Lambda_{j^\dagger-1}}, \frac{1}{ \Lambda_{j^\dagger}} \right) } \\
+& \ge \sigma_{j^\dagger}(f)\,\frac{Ra b }{\varepsilon (1 - b^\tau)^{1/\tau}}\qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}}
+\end{align*}
+From this last inequality, it follows that $j^\dagger \ge j^*$.
+\end{proof}
+
+\FredNote{Pity, I do not see our cost upper bounds reflecting different rates of decay of the series coefficients.  Perhaps a remark here is in order.}
+
+\PeterNote{Added a remark that may be useful for tractability results:}
+\begin{remark}
+A loose bound on $j^\dagger$ can be obtained in the following way. 
+%\begin{itemize}
+%    \item[(a)] For any $j<j^* \le j^\dagger$ we have, by \eqref{DHKM:SigmaInEq}
+%    \begin{align*}
+%        R &\ge \norm[\calF]{f}\ge\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=n_{j-1}+1}^{n_j}}\ge \frac{\sigma_j(f) }{\Lambda_j}> \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{ab}\, \frac{1}{\Lambda_j}.
+%    \end{align*}
+%    Hence, an upper bound on $j^\dagger$ is the first $j$ violating this inequality,
+%    \begin{align}\label{DHKM:jdaggerbound1}
+%        j^\dagger \le \min\left \{ j \in \bbN \colon \Lambda_j \le \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{abR} \right\}.
+%    \end{align}
+%    \item[(b)] A slightly looser bound can be obtained 
+%    by the following observation.
+
+    For
+    $j<j^* \le j^\dagger$ we have, again by \eqref{DHKM:SigmaInEq}
+    \begin{align*}
+        R &\ge\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=n_{j-1}+1}^{n_j}}\ge \frac{\sigma_j(f) }{\Lambda_j}> \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{ab}\, \frac{1}{\norm[\rho']{\left(\lambda_{\bsk_i} \right)_{i=n_{j-1}+1}^{\infty}}}.
+    \end{align*}
+    Hence, an upper bound on $j^\dagger$ is the first $j$ violating this inequality,
+    \begin{align}\label{DHKM:jdaggerbound2}
+        j^\dagger \le \min\left \{ j \in \bbN \colon \norm[\rho']{\left(\lambda_{\bsk_i} \right)_{i=n_{j-1}+1}^{\infty}} \le \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{abR} \right\}.
+    \end{align}
+%\end{itemize}
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Essential Optimality of the Algorithm and Tractability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The following theorem establishes a lower bound on the complexity of our problem for input functions in $\calC$. To obtain a result that can be compared with the cost of our algorithm, we assume that 
+\begin{equation} \label{DHKM:lambdaRatio}
+S = \sup_{l \in \bbN} \frac{\Lambda_l}{\lambda_{\bsk_{n_l}}} < \infty.
+\end{equation} The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TractConeCompCost} is essentially no worse than this lower bound.
+
+\begin{theorem} \label{DHKM:TractConeLowBdComp}
+A lower bound on the complexity of the linear problem is
+\begin{align*}
+ %\label{compbdA}
+&\COMP(\calA(\calC),\varepsilon,R) \ge n_{j^\ddagger}, 
+\intertext{where}
+%\label{compbdB}
+j^\ddagger & = \max \left \{ j \in \bbN : \left[\frac{(a+1)^{\rho}  }{(a-1)^\rho} + 1\right] \sum_{l=0}^j \frac{b^{\rho(l-j)}}{\lambda_{\bsk_{n_l}}^\rho}   <
+\frac{R^\rho}{\varepsilon^\rho}
+\right \}.
+\end{align*}
+\end{theorem}
+
+\begin{proof}
+\FredNote{Fred working on the part below}
+
+\FredNote{Now trying a proof technique more aligned with \cite{DinHic20a}.}
+
+As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
+We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC \cap \calB_{R}$, which yield the same approximate solution but different true solutions.
+This leads to a lower bound on $\COMP(\calA(\calC),\varepsilon,R)$.
+
+Let $j$ be the positive integer satisfying 
+\[
+n_{j-1} \le \COMP(\calA(\calC),\varepsilon,\rho) < n_j.
+\]  
+The first test function $f_1 \in \calC$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
+\begin{align}
+\nonumber
+f_1 &= f_{11} + \cdots + f_{1j}, \qquad
+\hf_{1l}(\bsk) := \begin{cases}
+\displaystyle
+\frac{c_1 b^{l-j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_l^{\rho'/\rho+1}},  & \bsk \in \calK_l,
+\\
+0, & \bsk \notin \calK_l,
+\end{cases}
+\\
+\nonumber
+c_1 &:=  \frac{R(a+1)}{2a} \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_j} \biggr)_{l=1}^j }^{-1}.
+\end{align}
+It can be verified that $f_1$ lies in both $\calB_{R}$ and $\calC$.  Note that 
+\begin{align}
+\nonumber
+\norm[\calF]{f_{1l}} &= \norm[\rho]{\biggl(\frac{\hf_{1l}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_l}} 
+= \frac{c_1 b^{l-j}}{\Lambda_l} \qquad l \in \N,\\
+\nonumber
+\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \norm[\calF]{f_{1l}} \bigr)_{l=1}^{j} } 
+=  c_1 \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^{j} } = \frac{R(a+1)}{2a} \le R,
+\end{align}
+so $f_1 \in \calB_R$.  Also,
+\begin{align}
+\nonumber
+\sigma_l(f_1) &= \begin{cases}
+c_1 b^{l-j}, & l=1, \ldots, j, \\
+0, & l=j+1, j+2, \ldots,
+\end{cases}
+\\
+\nonumber
+\sigma_{l+r}(f_1) &= 
+\begin{cases}
+c_1 b^{l+r - j}, & l=1, \ldots, \max(0,j-r), \\
+0, & l = \max(0,j-r)+1, \max(0,j-r) +2, \ldots, 
+\end{cases}
+\\
+\nonumber 
+& \le b^r \sigma_l(f_1), \qquad l,r \in \N,
+\end{align}
+so $f_1$ also lies in the cone $\calC$.
+
+Let $u$ be a linear combination of $u_1, \cdots, u_{n_j}$, expressed as
+\[
+u =  \sum_{k=0}^{j}\frac{b^{k-j}u^{(k)}}{\lambda_{n_k}},
+\]
+where $u^{(0)}$ is a linear combination of $u_{1}, \ldots, u_{n_0}$, and each $u^{(k)}$ is a linear combination of $u_{n_{k-1}+1}, \ldots, u_{n_k}$, for $k =1, \ldots, j$.
+We constrain $u$ to satisfy:
+\begin{equation}\label{uConstraint}
+L_1(u) = \cdots = L_n(u) = 0, \qquad \langle u,f \rangle_{\calF} = 0, \qquad 
+\max_{0\le k\le j} \DHJRbignorm[\calF]{u^{(k)}} = 1.
+\end{equation}
+Since $u$ is a linear combination of $n_j >n+1$ basis functions, these constraints can be satisfied.
+
+Let the other two test functions be constructed in terms of $u$ as 
+\begin{align}
+\nonumber
+f_\pm & := f \pm \eta u, \qquad \eta : =  \frac {(a-1)c}{(a+1)R}, \\
+\nonumber
+\DHJRnorm[\calF]{f_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
+& \nonumber 
+\le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \DHJRbignorm[\calF]{u^{(k)}}^2\right) + \eta^2 \DHJRbignorm[\calF]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
+\nonumber
+& \le  \left(c^2+ \eta^2 \right) \sum_{k=0}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}}  \qquad \text{by \eqref{uConstraint}}\\
+& \nonumber 
+\le \rho^2,
+\end{align} 
+so $f_{\pm} \in \calB_{\rho}$.  By design, $A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
+
+\FredNote{The approach below does not seem to work, but I do not want to erase it. I will try another approach above.}
+
+As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
+We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC \cap \calB_{R}$, which yield the same approximate solution but different true solutions.
+This leads to a lower bound on $\COMP(\calA(\calC),\varepsilon,R)$.
+
+The first test function $f_1 \in \calC$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
+\begin{align}
+\nonumber
+f_1 &= f_{11} + f_{12} +  \cdots, \qquad
+\hf_{1j}(\bsk) := \begin{cases}
+\displaystyle
+\frac{c_1 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_j^{\rho'/\rho+1}},  & \bsk \in \calK_j,
+\\
+0, & \bsk \notin \calK_j,
+\end{cases}
+\\
+\nonumber
+c_1 &:=  \frac{R(a+1)}{2a} \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_j} \biggr)_{j \in \N} }^{-1}.
+\end{align}
+It can be verified that the test function lies both in $\calB_{R}$ and in $\calC$:
+\begin{align}
+\nonumber
+\norm[\calF]{f_{1j}} &= \norm[\rho]{\biggl(\frac{\hf_1(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
+= \frac{c_1 b^j}{\Lambda_j} \qquad j \in \N,\\
+\nonumber
+\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \norm[\calF]{f_{1j}} \bigr)_{j \in \N} } 
+=  c_1 \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_l} \biggr)_{j \in \N} } = \frac{R(a+1)}{2a} \le R,
+\\
+\nonumber
+\sigma_j(f_1) &= \sigma_j(f_{1j}) = 
+c_1 b^{j}, \qquad j \in \N, 
+\\
+\nonumber
+\sigma_{j+r}(f_1) &= 
+b^{r} \sigma_j(f_1) \le a b^r \sigma_j(f_1), \qquad j,r \in \N.
+\end{align}
+
+Now suppose that $\ALG' \in \calA(\calC)$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$, where the cardinality of $\calJ$ is $n$.
+Let $\tcalK_j = \calK_j \setminus \calJ$ for all positive integer $j$.
+Construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
+\begin{align}
+\nonumber
+f_2 &= f_{21} + f_{22} +  \cdots, \qquad \hf_{2j}(\bsk_i) := \begin{cases}
+\displaystyle
+\frac{c_2 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\tLambda_j^{\rho'/\rho} \Lambda_j},  
+& \bsk \in \tcalK_j,
+\\
+0, & \text{otherwise},
+\end{cases}
+\\
+\nonumber
+c_2 &:= \frac{R(a-1)}{2a} \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_j} \biggr)_{j \in \N}}^{-1}, \qquad
+\tLambda_j := \norm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \tcalK_j}} \le \Lambda_j, \\
+\norm[\calF]{f_2} &= \norm[\rho]{\bigl( \norm[\calF]{f_{2j}} \bigr)_{j \in \N} } 
+\le  c_2 \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_l} \biggr)_{j \in \N} } \le R, \\
+\sigma_j(f_2) &= \sigma_j(f_{2j}) = 
+\frac{c_2 b^{j}\tLambda_j}{\Lambda_j} , \qquad j \in \N.
+\end{align}
+Furthermore, define $f_{\pm} = f_1 \pm f_2$.
+It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\calC$:
+\begin{align}
+\nonumber
+\norm[\calF]{f_\pm} &\le \norm[\calF]{f_1} + \norm[\calF]{f_2} \le (c_1 + c_2) \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_l} \biggr)_{j \in \N} } = R,
+\\
+\nonumber
+\sigma_j(f_\pm) & \ge \sigma_j(f_1) - \sigma_j(f_2) \ge
+\left(c_1 - c_2 \right) b^{j},  \qquad j \in \N,
+\\
+\nonumber
+\sigma_{j+r}(f_\pm) & \le \sigma_{j+r}(f_1) + \sigma_{j+r}(f_2) = 
+(c_1+c_2) b^{j+r}
+\\
+\nonumber
+& = (c_1 - c_2) a b^{j+r}
+\le a b^r \sigma_j(f_\pm),  \qquad j \in \N.
+\end{align}
+
+Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG'(f_1,\varepsilon) = \ALG'(f_\pm,\varepsilon)$.
+But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
+In particular,
+\begin{align*}
+\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - \ALG'(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - \ALG'(f_-,\varepsilon)} \bigr\} \\
+&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{S(f_-) - \ALG'(f_1,\varepsilon)}  \bigr] \\
+&\qquad \qquad \text{since } \ALG'(f_\pm,\varepsilon) = \ALG'(f_1,\varepsilon) \\
+&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
+&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $\SOL$ is linear}\\
+&= \norm[\calG]{\SOL(f_2)} = \norm[\tau]{\bigl( \sigma_j(f_2) \bigr)_{j \in N}} \\
+& = 
+\frac{R(a-1)}{2a} \norm[\tau]{ \biggl(\frac{b^{j}\tLambda_j}{\Lambda_j} \biggr)_{j \in \N}} \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_j} \biggr)_{j \in \N}}^{-1}.
+\end{align*}
+
+%%%%%%%%%%%%%% 
+\FredNote{Still playing around}
+
+Now suppose that $\ALG' \in \calA(\calC)$ is an optimal algorithm, i.e., \[\COST(\ALG,\calC,\varepsilon,R) =  \COMP(\calA(\calC),\varepsilon,R)\]
+for all $\varepsilon, R > 0$.
+For our particular input $f_1$ defined above, suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$, where the cardinality of $\calJ$ is $n$ with
+\[
+n + 1\le \COMP(\calA(\calC),\varepsilon,R) +1 < n_j.
+\]  
+Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
+\begin{align}
+\nonumber
+\hf_2(\bsk_i) &:= \begin{cases}
+\displaystyle
+\frac{c_2 b^{l-j} \lambda_{\bsk_i}^{\rho'/\rho+1}}{\Lambda_l^{\rho'/\rho+1}},  & \bsk_i \notin \calJ \text{ and } i =  1, \ldots, n_l, \ l = 1, \ldots, j,
+\\
+0, & \text{otherwise},
+\end{cases}
+\\
+\nonumber
+c_2 &:= \frac{R(1-a)}{2} \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^j }^{-1}, \\
+\norm[\calF]{f_2} &= \norm[\rho]{\Biggl( \norm[\rho]{\biggl(\frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \biggr)_{i = n_{l-1} + 1}^{n_l}} \Biggr)_{j=1}^l } 
+\le  c_2 \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^j } \le R, \\
+\sigma_l(f_2) & \le \begin{cases}
+\displaystyle
+c_2 b^{l-j}, & l =1, \ldots, j, \\
+0, & \text{otherwise},
+\end{cases}
+\end{align}
+Furthermore, define $f_{\pm} = f_1 \pm f_2$.
+It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\calC$:
+\begin{align}
+\nonumber
+\norm[\calF]{f_\pm} &\le \norm[\calF]{f_1} + \norm[\calF]{f_2} \le (c_1 + c_2) \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^j } = R,
+\\
+\nonumber
+\sigma_l(f_\pm) & \ge \sigma_l(f_1) - \sigma_2(f_2) = \begin{cases}
+\displaystyle
+(c_1 - c_2) b^{l-j}, & l =1, \ldots, j, \\
+0, & \text{otherwise},
+\end{cases}
+\\
+\nonumber
+\sigma_{l+r}(f_\pm) & \le \sigma_{l+r}(f_1) + \sigma_{l+r}(f_2) = \begin{cases}
+\displaystyle
+(c_1+c_2) b^{l+r-j}, & l =1, \ldots, j-r, \\
+0, & \text{otherwise},
+\end{cases}
+\\
+\nonumber
+& = \begin{cases}
+\displaystyle
+(c_1 - c_2) a b^{l+r-j}, & l =1, \ldots, j-r, \\
+0, & \text{otherwise},
+\end{cases}
+\\
+\nonumber
+& \le b^r \sigma_l(f_\pm), \qquad l =1, \ldots .
+\end{align}
+
+Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG(f_1,\varepsilon) = \ALG(f_\pm,\varepsilon)$.
+But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
+In particular,
+\begin{align*}
+\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - \ALG(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - \ALG(f_-,\varepsilon)} \bigr\} \\
+&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{S(f_-) - \ALG(f_1,\varepsilon)}  \bigr] \\
+&\qquad \qquad \text{since } \ALG(f_\pm,\varepsilon) = \ALG(f_1,\varepsilon) \\
+&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
+&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $\SOL$ is linear}\\
+&= \norm[\calG]{\SOL(f_2)}.
+\end{align*}
+\FredNote{Fred has got to here on 1/18/19}
+
+======
+
+Now suppose that $ALG \in \calA(\calC)$ is an optimal algorithm, i.e., \[\COST(ALG,\calC,\varepsilon,R) =  \textup{comp}(\calA(\calC),\varepsilon,R)\]
+for all $\varepsilon, R > 0$.  For our particular input $f$ defined above, suppose that $ALG(f,\varepsilon)$ samples $L_1(f), \ldots, L_n(f)$ where 
+\[
+n + 1\le \textup{comp}(\calA(\calC),\varepsilon,R) +1 < n_j.
+\]
+
+Let $u$ be a linear combination of $u_1,\ldots, u_{n_j}$, expressed as
+\[
+u =  \sum_{l=0}^{j}\frac{b^{l-j}u^{(l)}}{\lambda_{\bsk_{n_l}}},
+\]
+where $u^{(0)}$ is a linear combination of $u_{1}, \ldots, u_{n_0}$, and each $u^{(l)}$ is a linear combination of $u_{n_{l-1}+1}, \ldots, u_{n_l}$, for $l =1, \ldots, j$.
+We constrain $u$ to satisfy:
+\begin{equation}\label{DHKM:uConstraint}
+L_1(u) = \cdots = L_n(u) = 0, \qquad \langle u,f \rangle_{\calF} = 0, \qquad 
+\max_{0\le l\le j} \norm[\calF]{u^{(l)}} = 1.
+\end{equation}
+
+Since $u$ is a linear combination of $n_j >n+1$ basis functions, these constraints can be satisfied.
+
+Let the other two test functions be constructed in terms of $u$ as 
+\begin{align}
+\nonumber
+f_\pm & := f \pm \eta u, \qquad \eta : =  \frac {(a-1)c}{(a+1)S}, \\
+\nonumber
+\norm[\calF]{f_\pm}^\rho & \le \norm[\calF]{f}^\rho + \norm[\calF]{\eta u }^\rho \qquad \text{by \eqref{DHKM:uConstraint}} \\
+& \nonumber 
+\le \sum_{l=1}^j \frac{ b^{\rho(l-j)}}{\lambda^\rho_{\bsk_{n_l}}} \left(c^\rho+ \eta^\rho \norm[\calF]{u^{(l)}}^\rho\right) + \eta^\rho \norm[\calF]{u^{(0)}}^\rho \frac{b^{-\rho j}}{\lambda_{\bsk_{n_0}}^\rho}\\
+\nonumber
+& \le  \left(c^\rho+ \eta^\rho \right) \sum_{l=0}^j \frac{ b^{\rho(k-j)}}{\lambda^\rho_{\bsk_{n_l}}}  \qquad \text{by \eqref{DHKM:uConstraint}}\\
+& \nonumber 
+\le R^{\rho},
+\end{align} 
+so $f_{\pm} \in \calB_{B}$.  By design, $ALG(f_\pm,\varepsilon) = ALG(f,\varepsilon)$, which will be used below.
+
+Now we must check that $f_\pm \in \calC$. From the definition in \eqref{DHKM:SigmaDef} it follows that for $l = 1, \ldots, j$ and $r \ge 1$,
+\begin{equation*}
+\sigma_l(f_\pm)  \begin{cases} 
+\displaystyle
+\le \sigma_l(f) + \sigma_l(\eta u)\le 
+c b^{l-j} + \eta b^{l-j}\frac{\Lambda_l}{\lambda_{\bsk_{n_l}}}\norm[\calF]{u^{(l)} }
+\le b^{l-j}\left(c+ \eta S \right)
+\\[1ex]
+\displaystyle
+\ge \sigma_l(f) - \sigma_l(\eta u)\ge 
+c b^{l-j} - \eta b^{l-j} \frac{\Lambda_l}{\lambda_{\bsk_{n_l}}}\norm[\calF]{u^{(k)}  }
+\ge b^{l-j}\left(c-\eta S\right) , 
+\end{cases}
+\end{equation*}
+Therefore, 
+\begin{equation*}
+\sigma_{l+r}(f_\pm)
+\le b^{l+r-j}(c+\eta S) = ab^r b^{l-j}\frac{2c}{a+1}
+=ab^r b^{l-j}\left(c-\eta S \right) \le a b^r \sigma_{l}(f_\pm),
+\end{equation*}
+which establishes that $f_\pm \in \calC$.
+
+Although two test functions $f_\pm$ yield the same approximate solution, they have different true solutions.  In particular,
+\begin{align*}
+\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - ALG(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - ALG(f_-,\varepsilon)} \bigr\} \\
+&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - ALG(f,\varepsilon)} + \norm[\calG]{S(f_-) - ALG(f,\varepsilon)}  \bigr] \\
+&\qquad \qquad \text{since } ALG(f_\pm,\varepsilon) = ALG(f,\varepsilon) \\
+&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
+&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $S$ is linear}\\
+&= \eta \norm[\calG]{\SOL(u)}.
+\end{align*}
+Thus, we have
+\begin{align*}
+\varepsilon^2  & \ge \eta^2 \norm[\calG]{\SOL(u)}^2= 
+\eta^2 \sum_{l=0}^{j} \norm[\calG]{\SOL(u^{(l)})}^2  \frac{b^{2(l-j)}}{\lambda_{n_k}^2}\\
+& \ge \eta^2 
+\sum_{k=0}^{j} \norm[\calF]{u^{(k)}}^2 
+b^{2(k-j)}\\
+& \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \argmax_{0 \le k \le j} \norm[\calF]{u^{(k)}} \\
+& \ge \eta^2 = \frac{(a-1)^2c^2}{(a+1)^2} \\
+&
+=\frac{(a-1)^2 \rho^2}{(a+1)^2R^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
+& =  \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
+\end{align*}
+
+This lower bound must be satisfied by $j$ to be consistent with the assumption $\textup{comp}(\calA(\calC),\varepsilon,R) \le n_j - 1$.
+Thus, for any $j$ violating this inequality it follows that $\textup{comp}(\calA(\calC),\varepsilon,R) \ge n_j$.
+This implication provides a lower bound on $\textup{comp}(\calA(\calC),\varepsilon,R)$.
+\end{proof}
+
+\PeterNote{Working on tractability below
+
+\medskip
+
+We again would like to study tractability.
+To this end, we assume in the following that $n_0$ is some given positive integer, and that $(n_j)_{j\ge 1}=(g^j n_0)_{j\ge 1}$ for some real $g>1$.
+Like in Section~\ref{DHKM:SecPilotTract}, we distinguish whether $\rho'=\infty$ or not.
+
+\paragraph*{CASE 1: $\rho'=\infty$:}
+
+\begin{theorem} \label{DHKM:thmtract3}
+Using the same notation as above, strong polynomial, polynomial, and weak tractability for the case $\rho'=\infty$ hold under exactly the 
+same conditions as in Theorem \ref{DHKM:thmtract1}.
+\end{theorem}
+\begin{proof}
+Our starting point is \eqref{DHKM:jdaggerbound2}.
+ We define, for $d\in\NN$ and $\varepsilon\in (0,1)$,
+ \[
+  n^*(\varepsilon,d):=\min\left\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le \varepsilon\right\}\asymp
+  \min\left\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le \frac{\varepsilon (1-b^\tau)^{1/\tau}}{abR}\right\}.
+ \]
+ To show the sufficient condition for strong polynomial tractability, let now $\widetilde{\varepsilon}:=\sqrt{\varepsilon}$ such that $n^*(\varepsilon,d)=\min\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le (\widetilde{\varepsilon})^2 \}$.
+From \cite{NovWoz08a}, we know that if \eqref{DHKM:eq:condspt} holds for some real $\eta>0$ and some $i_0\in\NN$, then
+ \[
+  n^* (\varepsilon,d) \le C\,((\widetilde{\varepsilon})^{-1})^{2\eta}= C\, (\varepsilon^{-1})^\eta 
+ \]
+ with some $C>0$.
+
+ Suppose that $n^*(\varepsilon,d) /n_0 < 1/g$. Then, $n^*(\varepsilon,d) < n_0$, and it follows by the monotonicity of the $\lambda_{d,\bsk_i}$ that
+ $\lambda_{d,\bsk_{n_0+1}}\le \lambda_{d,\bsk_{n^*(\varepsilon,d)+1}}$, and hence $j^\dagger =1$, which yields $n_{j^\dagger}=g\,n_0$.
+
+ If $n^*(\varepsilon,d) /n_0 \ge 1/g$, let $j_0\in \NN$ be maximal such that $g^{j_0-2}\le n^*(\varepsilon,d) /n_0$. This means that 
+ \[
+ n^*(\varepsilon,d)  < g^{j_0-1} n_0=n_{j_0-1},
+ \] 
+ and hence, again by the monotonicity of the $\lambda_{d,i}$, that 
+ \[
+ \lambda_{d,\bsk_{n_{j_0-1}+1}}\le \lambda_{d,\bsk_{n^*(\varepsilon,d)+1}}.
+ \] 
+ Consequently, 
+ \[
+ n_{j^\dagger} \le n_{j_0}=g^{j_0} n_0 \le 
+ n^*(\varepsilon,d)\, g^2\,n_0.
+ \]
+ Hence, in any case we obtain
+ \[
+  \textup{comp} (\calA (\calC_d),\varepsilon,R) \le n_{j^\dagger} \le 
+  C\, (\varepsilon^{-1})^\eta g^2 n_0+ gn_0.
+ \]
+
+ This implies strong polynomial tractability, as claimed, and hence the sufficiency of Condition \eqref{DHKM:eq:condspt} for 
+ strong polynomial tractability is shown. Note that this also shows the upper bound of $\eta$ for the exponent 
+ of strong polynomial tractability. The proof of the sufficient condition for polynomial tractability is done analogously
+
+ Regarding the proof of the sufficient condition for weak tractability, let $\widetilde{\varepsilon}$ and $n^*(\varepsilon,d)$ be defined as above. Let
+ $\widetilde{n}^*(\widetilde{\varepsilon},d)=\min\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le (\widetilde{\varepsilon})^2 \}$. 
+ Note, as above, that we have $n^*(\varepsilon,d)=\widetilde{n}^*(\widetilde{\varepsilon},d)$. This yields
+ $$   
+\lim_{d+\varepsilon^{-1}\to\infty}\   
+\frac{\log\, n^*(\varepsilon,d)}   
+{d +(\varepsilon^{-1}) }\,=\, \lim_{d+\varepsilon^{-1}\to\infty}\   
+\frac{\log\, \widetilde{n}^*(\widetilde{\varepsilon},d)}   
+{d +(\widetilde{\varepsilon}^{-1})^{2}}  
+$$ 
+As shown in \cite{WerWoz17}, we have 
+\[
+ \lim_{d+\varepsilon^{-1}\to\infty}\   
+\frac{\log\, \widetilde{n}^*(\widetilde{\varepsilon},d)}   
+{d +(\widetilde{\varepsilon}^{-1})^{2}}=0
+\]
+if \eqref{DHKM:eq:condwt} holds.
+
+As above, we see that $n_{j^\dagger}\le n^*(\varepsilon,d)\, g^2 n_0+g\,n_0$, hence 
+$$ 
+  0\le\lim_{d+\varepsilon^{-1}\to\infty}\   
+ \frac{\log\, n_{j^\dagger}}   
+{d +(\varepsilon^{-1}) }
+ \, \le\, k\,
+\lim_{d+\varepsilon^{-1}\to\infty}\   
+\frac{\log\, n^*(\varepsilon,d)}   
+{d+(\varepsilon^{-1})}\,=\, k\,\lim_{d+\varepsilon^{-1}\to\infty}\   
+\frac{\log\, \widetilde{n}^*(\widetilde{\varepsilon},d)}   
+{d +(\widetilde{\varepsilon}^{-1})^{2}}  
+$$
+for some positive constant $k$.
+Hence, we conclude that we have weak tractability if \eqref{DHKM:eq:condwt} holds. 
+\end{proof}
+}
+
+%%%%%%%%%%%%
+\subsection{Numerical Example}
+%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Inferring Coordinate Importance and Smoothness} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\FredNote{The work with Simon}
+\section{Inferring Coordinate and Smoothness Importance} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In many problems, the input function $f$ has structure which can be learned for adaptive approximation.
+For example, certain input variables in $f$ may be more active than others, or certain effects in $f$ (e.g., smoother effects) may be more important than others (e.g., rough effects).
+The incorporation of such structure can be advantageous in two ways.
+First, it allows for a tighter, adaptive approximation error bound in \eqref{DHKM:pilot_errbd}.
+Second, this data-based bound can then be used to guide an adaptive sampling procedure on $f$.
+
+In the following, we present a framework which accounts for coordinate, order and smoothness importance on $f$, via the weights $(\lambda_\bsk)_{\mathbf{k} \in \mathbb{K}}$ from Section 1.1.
+We then show how such structure can be inferred from a pilot sample, and how the resulting inferred weights can be used for adaptive sampling on $f$.
+For simplicity, we assume the index set $\mathbb{K}$ to be $\mathbb{N}_0^d$ in this section.
+
+%We then investigate how different combinations of these importances affect tractability of approximation.
+
+\subsection{Product, Order and Smoothness Dependent (POSD) weights}
+Let us first define $\mathbf{w} = (w_l)_{l=1}^d$ as the so-called \textit{product} weights, $\boldsymbol{\Gamma} = (\Gamma_k)_{k=1}^d$ as the \textit{order} weights, and $\mathbf{s} = (s_j)_{j=1}^\infty$ as the \textit{smoothness} weights.
+The intuition behind these weights are as follows: product weights quantify variable importance for the $d$ input variables in $f$; order weights $(\Gamma_k)_{k=1}^d$ quantify the importance of effects with different orders (e.g., first-order, second-order); and smoothness weights $(s_j)_{j=1}^\infty$ quantify the importance of effects with different degrees (e.g., linear, quadratic).
+Our strategy is to use these product, order and smoothness dependent (POSD) weights to parametrize weights $(\lambda_{\bsk})_{\bsk \in \mathbb{N}_0^d}$, which reflect the importance of each Fourier coefficient in $f$.
+
+Consider next the following POSD parametrization of weights $(\lambda_{\bsk})_{\bsk \in \mathbb{N}_0^d}$:
+\begin{equation}
+\lambda_{\bsk} = \Gamma_{\|\bsk\|_0} \prod_{\substack{l=1\\ k_l>0}}^d w_l s_{k_l}, \quad \Gamma_0 = s_1 = 1, \quad \bsk = (k_1, \cdots, k_d).
+\label{eq:posd}
+\end{equation}
+\PeterNote{Is $\|\bsk\|_0$ equal to the number of non-zero components in $\bsk$?}
+This parametrization is motivated by several guiding principles from the experimental design literature (see \cite{WuHam2009}), which presumes certain structure on $f$ for effective inference with limited data.
+\begin{itemize}
+\item The first principle, called \textit{effect sparsity}, assumes only a small number of input variables are important in $f$.
+In \eqref{eq:posd}, this sparsity can be accounted for restricting (\PeterNote{allowing?}) only a small number of product weights $\mathbf{w}$ to be large.
+\item The second principle, called \textit{effect heredity}, states that lower-order effects are more important than higher-order effects.
+Here, this means that a first-order effect (e.g., $\bsk_1 = (1,0, 0,\ldots, 0)$) should be more important than a second-order effect (e.g., $\bsk_2 = (1, 1, 0, \ldots, 0)$), and so on.
+From \eqref{eq:posd}, this heredity can be enforced by letting the order weights $\boldsymbol{\Gamma}$ be decreasing in order $k$.
+\item The third principle, called \textit{effect hierarchy}, allows an effect to be active \textit{only} when all its component effects are active as well.
+For example, the second-order effect $\bsk = (1, 1, 0, \ldots, 0)$ is active (i.e., $\lambda_\bsk > 0$) only when its two first-order components $\bsk_1 = (1, 0, 0, \ldots, 0)$ and $\bsk_2 = (0, 1, 0, \ldots, 0)$ are also active as well.
+This hierarchy is implicitly enforced within the product structure of the POSD weights \eqref{eq:posd}.
+\item The last principle, which we call \textit{effect smoothness}, states that lower-degree effects are more important than higher-degree effects.
+For example, when the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are polynomials, this means linear effects are more important than quadratic effects, which are in turn more significant than cubic effects, and so on.
+Effect smoothness can be imposed by setting a decreasing sequence for smoothness weights $\mathbf{s}$.
+This decaying importance in smoothness \PeterNote{Something seems to be missing.}
+\end{itemize}
+
+From a quasi-Monte Carlo (QMC) perspective, the POSD weights in \eqref{eq:posd} generalize upon the product-and-order dependent (POD) weights in \cite{KuoEtal12a}, which were first introduced in the analysis of QMC methods for partial differential equations with random coefficients.
+In particular, these existing POD weights can be recovered by restricting indices to be in $\{0, 1\}^d$, and setting $\mathbf{s} \equiv 1$ (i.e., all smoothness effects are of equal importance).
+Our POSD weights are also different from the smoothness-driven product-and-order dependent (SPOD) weights in \cite{Dea2014}, which were recently used to analyze higher-order QMC methods for stochastic partial differential equations.
+These SPOD weights take the form:
+\begin{equation}
+\gamma_{\mathbf{u}} = \sum_{\bsk \in \{1:\alpha\}^{|\mathbf{u}|}} \|\bsk\|_1 !
+\prod_{l \in \mathbf{u}} \left( 2^{\delta(k_l,\alpha)} w_l^{k_l} \right), \quad \|\bsk\|_1 = \sum_{l=1}^d k_l, \quad \mathbf{u} \in \{0, 1\}^d.
+\label{eq:spod}
+\end{equation}
+Intuitively, SPOD weights quantify the importance of each \textit{subspace} (indexed by $\mathbf{u}$), under a common smoothness structure between subspaces.
+To contrast, the proposed POSD weights in \eqref{eq:posd} instead quantify the importance of each \textit{Fourier coefficient} in $f$ (indexed by $\bsk$), under a common smoothness structure between coefficients.
+
+%This can be seen as a generalization of the product-and-order (POD) weights, proposed by \cite{KuoEtal12a} for Quasi-Monte Carlo finite element methods.
+The original POD weights can be recovered by restricting $\bsk \in \{0, 1\}^d$ and $(s_j)_{j=1}^\infty \equiv 1$.
+
+\subsection{Inferring product and smoothness weights from pilot sample}
+
+As mentioned earlier, the key motivation for an adaptive algorithm is that it allows us to infer, from finite observations, information on what was not observed on $f$.
+In Section 2, this is used to bound the input function norm $\| f \|_{\mathcal{F}}$.
+A similar inference approach is introduced next for POSD weights: these weights are first inferred from a pilot sample, then used for adaptive error estimation and sampling.
+For simplicity, we assume in the following that order weights $\boldsymbol{\Gamma}$ are fixed (these can be preset a priori), and focus on the inference of product and order weights from data.
+
+Consider first the inference of product weights $\mathbf{w}$ from pilot sample $\{\hat{f}(\bsk_i)\}_{i=1}^n$, given fixed order weights $\boldsymbol{\Gamma}$ and smoothness weights $\mathbf{s}$.
+One intuitive strategy is to find weights $\mathbf{w}$ which minimize the pilot sample input norm $\|(\hat{f}(\bsk_i)/\lambda_{\bsk_i})_{i=1}^n\|_{\rho}$, since this is a key ingredient for reducing the approximation error \eqref{DHKM:pilot_errbd} for the cone of functions in \eqref{DHKM:pilot_cone}.
+Moreover, by the effect sparsity principle, product weights should also be set as small as possible, to reflect the belief that a small number of variables are active in $f$.
+This motivates the following inference procedure:
+\begin{equation}
+\mathbf{w} \leftarrow \text{InfProd}(\{\hat{f}(\bsk_i)\}_{i=1}^n, w^*, \boldsymbol{\Gamma}, \mathbf{s}) := \min \argmin_{w_l \leq w^*} \left\|\left( \frac{\hat{f}(\bsk_i)}{\lambda_{\bsk_i}(\mathbf{w},\boldsymbol{\Gamma},\mathbf{s})} \right)_{i=1}^n\right\|_{\rho}.
+\label{eq:infprod}
+\end{equation}
+Here, $w^*$ is the maximum product weight allowed, and $\lambda_{\bsk_i}(\mathbf{w},\boldsymbol{\Gamma},\mathbf{s})$ follows the POSD form \eqref{eq:posd} with weights $\mathbf{w}$, $\boldsymbol{\Gamma}$ and $\mathbf{s}$.
+In words, the problem in \eqref{eq:infprod} finds the smallest product weights which uniformly minimize the input norm $\| f \|_{\mathcal{F}}$ for functions $f$ within cone $\mathcal{C}$.
+
+Consider next the inference of smoothness weights $\mathbf{s}$, given fixed product weights $\mathbf{w}$ and order weights $\boldsymbol{\Gamma}$. Applying the same strategy as above, we get: 
+\begin{equation}
+\mathbf{s} \leftarrow \text{InfSmooth}(\{\hat{f}(\bsk_i)\}_{i=1}^n, s^*, \mathbf{w}, \boldsymbol{\Gamma}) := \min \argmin_{s_j \leq s^*} \left\|\left( \frac{\hat{f}(\bsk_i)}{\lambda_{\bsk_i}(\mathbf{w},\boldsymbol{\Gamma},\mathbf{s})} \right)_{i=1}^n\right\|_{\rho},
+\label{eq:infsmooth}
+\end{equation}
+where $s^*$ is the maximum smoothness weight allowed.
+In words, problem \eqref{eq:infsmooth} finds the smallest smoothness weights which uniformly minimize the input norm $\| f \|_{\mathcal{F}}$ for functions $f$ within cone $\mathcal{C}$.
+Alternatively, if one is willing to assume a parametric form for smoothness decay (e.g., $s_j = 1/j^{\nu}$), then the unknown decay parameters (e.g., $\nu$) can be similarly estimated by minimizing the sample input norm.
+
+The two procedures \eqref{eq:infprod} and \eqref{eq:infsmooth} can be performed iteratively for joint inference on both product weights $\mathbf{w}$ and smoothness weights $\mathbf{s}$.
+Beginning with an initial choice of $\mathbf{w} \equiv 1$ and $\mathbf{s} \equiv 1$, we first perform \eqref{eq:infprod} to update $\mathbf{w}$, then perform \eqref{eq:infsmooth} to update $\mathbf{s}$ (using updated $\mathbf{w}$).
+These two steps are repeated until both $\mathbf{w}$ and $\mathbf{s}$ converge.
+One nice feature of this iterative procedure is the so-called ``descent property'' -- one can show that the pilot sample input norm $\|(\hat{f}(\bsk_i)/\lambda_{\bsk_i})_{i=1}^n\|_{\rho}$ (the objective to minimize) indeed decreases within each iteration, which stabilizes the optimization algorithm.
+
+Of course, the quality of the inferred weights depends greatly on the design of the pilot sample, which we denote as $\mathcal{I}$.
+In our implementation, we take $\mathcal{I}$ to be $\{ (0, \ldots, 0, j, 0, \ldots, 0): j = 0, \ldots, s^*\}$, the set of all univariate indices with maximum smoothness $s^*$.
+The intuition here is that, by sampling all possible coefficient smoothness (\PeterNote{smoothness coefficients?}) over each variable ($\# \mathcal{I} = d s^* + 1$ coefficients in total), one can accurately infer from this pilot sample both variable importance weights $\mathbf{w}$ and smoothness weights $\mathbf{s}$.
+
+Algorithm \ref{DHKM:InfPilotConeAlg} summarizes the full adaptive approximation procedure with POSD weights.
+First, the Fourier coefficients are observed from the pilot sample $\mathcal{I}$.
+Next, the product and smoothness weights $(\mathbf{w},\mathbf{s})$ are iteratively inferred from this pilot sample.
+Finally, incorporating these inferred weights within $(\lambda_{\bsk})_{\bsk \in \mathbb{K}}$, the required sample size $n^*$ can then be computed via the data-based error bound \eqref{DHKM:pilot_errbd}.
+Note that the remaining $n^* - \# \mathcal{I}$ indices (after the initial pilot sample) should be the indices with largest data-inferred weights $(\lambda_{\bsk})_{\bsk \in \mathbb{K}}$, i.e., the indices with greatest estimated importance from the pilot sample.
+
+\begin{algorithm}
+	\caption{$\ALG$ Based on Adaptive POSD Weights \label{DHKM:InfPilotConeAlg}} 
+	\begin{algorithmic}
+	\PARAM maximum product and smoothness weights, $w^*$ and $s^*$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $\frakC$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}; 
+		\INPUT a black-box function, $f$; an absolute error tolerance,
+		$\varepsilon>0$
+
+\Ensure Error criterion \eqref{DHKM:err_crit} for the cone defined in \eqref{DHKM:pilot_cone}
+\State $\bullet$ Define pilot sample indices $\mathcal{I} := \{ (0, \ldots, 0, j, 0, \ldots, 0): j = 0, \ldots, s^*\}$
+\State $\bullet$ Evaluate pilot sample $\{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}$
+\State $\bullet$ Repeat until $(\mathbf{w},\mathbf{s})$ converges:
+\State \quad - $\mathbf{w} \leftarrow \text{InfProd}(\{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}, w^*, \boldsymbol{\Gamma}, \mathbf{s})$
+\State \quad - $\mathbf{s} \leftarrow \text{InfSmooth}(\{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}, s^*, \mathbf{w}, \boldsymbol{\Gamma})$
+\State $\bullet$ Choose $n^* =  \min \left \{n \ge \# \mathcal{I} : \text{ERR}\left( \{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}, \#\mathcal{I} \right) \le \varepsilon \right \}$, with $\ERR$ in \eqref{DHKM:pilot_errbd}
+
+\RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
+\end{algorithmic}
+\end{algorithm}
+
+%\subsection{POSD weights and tractability}
+%We now investigate how different settings of the POSD weights, which corresponds to different assumptions on function $f$, influence tractability for function approximation.
+For simplicity, assume $\rho = \infty$ and $\rho' = \tau = 1$.
+From the error bound in \eqref{DHKM:APP_errorBd} and the cone definition in \eqref{DHKM:pilot_cone}, we have:
+%\begin{equation}
+%   \norm[\calG]{\SOL(f) - \APP(f,n)}  \le  \frakC \norm[\infty]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, \bignorm[1]{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
+%   \label{DHKM:err}
+%\end{equation}
+%\SimonNote{Include POSD tractability here?}
+
+\subsection{Numerical examples}
+
+We now investigate the numerical performance of this adaptive algorithm with POSD weights.
+For simplicity, we consider only the case of $\rho = \infty$ and $\rho' = \tau = 1$ here.
+The simulation set-up is as follows.
+The Fourier coefficients for input function $f$, $\{\hat{f}(\bsk)\}_{\bsk \in \mathbb{N}_0^d}$, are randomly sampled as:
+\begin{equation}
+\hat{f}(\bsk) = Z_{\bsk} \left( \Gamma_{\|\bsk\|_0}^* \prod_{\substack{l=1\\ k_l>0}}^d w_l^* s_{k_l}^* \right), \quad Z_{\bsk} \overset{\mathrm{i.i.d.}}{\sim} \text{Unif}\{-1, 1\},
+\label{eq:foursim}
+\end{equation}
+where $w_l^* = 1/l^2$, $\Gamma_k^*= 1/k!$ and $s_j^* = 1/j^3$ are the true order, product and smoothness weights of $f$, and $Z_{\bsk}$ randomly sets the sign of each coefficient.
+Here, the product weights are also randomized in terms of order, to ensure that the order of the inputs in $f$ does not necessarily reflect the order of variable importance.
+We also assume that the order weights $\boldsymbol{\Gamma}$ in Algorithm \ref{DHKM:InfPilotConeAlg} are the true order weights $\boldsymbol{\Gamma}^*$.
+
+Figure \ref{fig:four} shows the
+
+%\begin{itemize}
+%\item Figure \ref{fig:four} shows the performance of this adaptive approximation method, with $f$ being a 4-d or 8-d function with random Fourier coefficients.
+%\item \SimonNote{Numerical results for function evaluations?}
+%\end{itemize}
+
+\begin{figure}
+\centering
+\begin{subfigure}{\textwidth}
+\centering
+\includegraphics[width=0.7\textwidth]{d4}
+\label{fig:four1}
+\caption{$f$ is a $d=4$-dim. function with random Fourier coefficients.}
+\end{subfigure}
+\begin{subfigure}{\textwidth}
+\centering
+\includegraphics[width=0.7\textwidth]{d8}
+\label{fig:four2}
+\caption{$f$ is a $d=8$-dim. function with random Fourier coefficients.}
+\end{subfigure}
+\caption{Adaptive sample size $n^*$ as a function of absolute error $\text{ERR}$, with points colored by absolute error tolerance $\epsilon$.}
+\label{fig:four}
+\end{figure}
 
@@
 
-\bibliography{FJH23.bib,FJHown23.bib}
+\bibliography{ExtraBib.bib,FJH23.bib,FJHown23.bib}
 

### 2019-01-26 DingHickKritzMakRICAMChap.tex
new edits

@@
 \usepackage{color,mathtools,bbm,xspace,natbib}
+\usepackage{algpseudocode}
 \usepackage{algorithm, algorithmicx}
-\usepackage{algpseudocode}
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
@@
 
-There are many situations in which adaptive algorithms cannot perform much better than non-adaptive algorithms.
+In many situations, adaptive algorithms can be rigorously shown to perform \emph{essentially no better} than non-adaptive algorithms.
 Yet, in practice adaptive algorithms are appreciated because they relieve the user from having to stipulate the computational effort required to achieve the desired accuracy.
 Adaptive algorithms infer the computational effort required based on the function data sampled.
+The key to resolving this seeming contradiction is to construct a theory based on assumptions that favor adaptive algorithms.
+That is what we do here.
 
@@
 \begin{algorithm}
-	\caption{Non-Adaptive $\ALG$ for a Ball of Input Functions} \label{DHKM:BallAlg}
+\caption{Non-Adaptive $\ALG$ for a Ball of Input Functions \label{DHKM:BallAlg}}
 	\begin{algorithmic}
@@
 Note that algorithms satisfying \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$.
-No matter how large a sample size is required by an algorithm, it is finite.
+Any algorithm must require a finite sample size, even if it is huge.
 Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.

### 2019-02-13 DingHickKritzMakRICAMChap.tex
Fixed Sect. 3 optimality proof I think

@@
 \usepackage{subcaption}
+\usepackage{bbm}
 \input{macros}
@@
 \newtheorem{remark}{Remark}
+\theoremstyle{definition}
+\newtheorem{exmp}{Example}
 
@@
 \newcommand{\dataN}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^n}
+\newcommand{\dataNj}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_j}}
+\newcommand{\dataNjd}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_{j^\dagger}}}
 \newcommand{\ERRN}{\ERR\bigl(\dataN,n\bigr)}
+\newcommand{\ERRNj}{\ERR\bigl(\dataNj,n_j\bigr)}
+\newcommand{\ERRNjd}{\ERR\bigl(\dataNjd,n_{j^\dagger}\bigr)}
 \DeclareMathOperator{\COST}{COST}
@@
 \newcommand{\tv}{\Tilde{v}}
+\newcommand{\tcalJ}{\widetilde{\calJ}}
 \newcommand{\tcalK}{\widetilde{\calK}}
@@
 \newcommand{\tbbK}{\widetilde{\bbK}}
+\newcommand{\lo}{\textup{lo}}
+\newcommand{\up}{\textup{up}}
+\newcommand{\E}{\textup{e}}
 \def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
@@
   Austrian Academy of Sciences, Altenbergerstr. 69, 4040 Linz, Austria}
-  \affil[4]{...}
+  \affil[4]{H. Milton Stewart School of Industrial and Systems Engineering, Georgia Institute of Technology, 755 Ferst Drive, Atlanta, GA 30332 USA}
   \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
@@
 In many situations, adaptive algorithms can be rigorously shown to perform \emph{essentially no better} than non-adaptive algorithms.
-Yet, in practice adaptive algorithms are appreciated because they relieve the user from having to stipulate the computational effort required to achieve the desired accuracy.
-Adaptive algorithms infer the computational effort required based on the function data sampled.
+Yet, in practice adaptive algorithms are appreciated because they relieve the user from stipulating the computational effort required to achieve the desired accuracy.
 The key to resolving this seeming contradiction is to construct a theory based on assumptions that favor adaptive algorithms.
-That is what we do here.
-
-Adaptive algorithms may perform better if the set of input functions is not convex, and that is the situation studied here.
-We propose adaptive algorithms for general multivariate linear problems where the input function lies in non-convex cones.
+We do that here.
+
+Adaptive algorithms infer the necessary computational effort based on the function data sampled.
+Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is not convex.
+We construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
 Our algorithms use series coefficients of the input function to construct an approximate solution that satisfies an absolute error tolerance.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{An Illustrative Example}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$ in this case
+	\begin{align*}
+	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f) \\
+    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , & \tu_{k}(x) & := \begin{cases} 1, & k =0 ,\\
+	x, & k=1,\\
+	2x \tu_{k-1}(x)-\tu_{k-2}(x), & k = 2, 3, \ldots.
+	\end{cases}
+	\end{align*}
+If one can observe the series coefficients, then $f$ can be approximated by a finite sum.  However, one should have some notion of which terms in the infinite series for $f$ are more important.  Let 
+\begin{equation*}
+    \lambda_\bsk := \prod_{\ell =1}^d \frac{1}{\max(1,k^r_\ell)}, \qquad \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}.
+\end{equation*}
+By this definition, an input function with modest sized norm must have series coefficients that decay quickly enough as the degree of the polynomial increases.
+The assumed decay is quicker for larger $r$, and this assumed decay governs the assumed smoothness of the input functions.
+
+The weights, $\lambda_{\bsk}$, can be ordered,
+\begin{equation} \label{DHKM:lambda_order}
+    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots >0,
+\end{equation}
+which then implies an ordering of the wavenumbers.  Given this ordering, it is natural to approximate the solution using the first $n$ series coefficients as follows:
+\begin{equation} \label{DHKM:Ex_APP_def}
+   \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \quad \forall n \in \N.
+\end{equation}
+The error of this approximation can be defined as 
+\begin{gather*}
+    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}, \\
+    \text{where}\qquad
+    \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
+\end{gather*}
+
+If one has a fixed data budget, $n$, then choosing approximation $\APP(f,n)$ is appropriate.
+However, often one has an error tolerance, $\varepsilon$, for which one desires an algorithm, $\ALG(f,\varepsilon)$, which satisfies
+\begin{equation*}
+    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon.
+\end{equation*}
+Such an algorithm must have a rule of choosing the correct $n$---depending on $f$ and $\varepsilon$---so that $\ALG(f,\varepsilon) = \APP(f,n)$.
+Choosing such a rule, choosing a set $\calC$ of input functions for which the rule is valid,  characterizing the information cost of $\ALG$, and determining whether $\ALG$ has optimal information cost, and understanding the dependence of this cost on the the number of input variables, $d$, as well as the error tolerance, $\varepsilon$, are all objectives of this chapter.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{General Linear Problem}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our general linear problem is defined by a solution operator that mapping an input function to an output, $\SOL:\calF \to \calG$.
-The Banach spaces of inputs and outputs are defined by series expansions:
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Our general linear problem is defined by a solution operator mapping an input function to an output, $\SOL:\calF \to \calG$.
+As in the illustrative example above, the Banach spaces of inputs and outputs are defined by series expansions:
 \begin{gather}
@@
 \end{equation}
-where $\mathbb{K}$ is a general index set. The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.
-
-Although this problem formulation is quite general in some aspects, condition \eqref{DHKM:basis_relate} may be somewhat restrictive.
-In theory, the choice of basis can be made via the singular value decomposition, but in practice, if $\calF$ and $\calG$ have common norms, bases satisfying \eqref{DHKM:basis_relate} may be difficult to identify explicitly.
-
-To facilitate our derivations below, we establish the following lemma:
+where $\mathbb{K}$ is a general index set.
+The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.
+The larger $\lambda_{\bsk}$ is, the more important $\hf(\bsk)$ is.
+
+Although this problem formulation is quite general in some aspects, condition \eqref{DHKM:basis_relate} is somewhat restrictive.
+In theory, the choice of basis can be made via the singular value decomposition, but in practice, if the norms of $\calF$ and $\calG$ are typical, the bases satisfying \eqref{DHKM:basis_relate} may be difficult to identify explicitly.
+
+To facilitate our derivations below, we establish the following lemma, which follows from H\"older's inequality:
 
@@
 \end{equation*}
-so $\tau \le \rho' < \infty$.  Let $\Lambda =  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$.  Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
-\begin{gather}
+so $\tau \le \rho' \le \infty$.  Let $\Lambda =  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$.  Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
+\begin{equation}
 \label{DHKM:SOL_ineq}
-    \norm[\calG]{\SOL(f)} \le \norm[\calF]{f} \, \Lambda,
-    \\
+    \norm[\calG]{\SOL(f)} = \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK}} \le \norm[\calF]{f} \, \Lambda,
+    \end{equation}
+    \begin{multline}
     \label{DHKM:SOL_tight_ineq}
-    \bigabs{\hf(\bsk)} = \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\Lambda^{\rho'/\rho}} \quad \forall \bsk \in \calK \ \ 
+    \bigabs{\hf(\bsk)} = \begin{cases}
+    \displaystyle 
+    \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\Lambda^{\rho'/\rho}}, & \forall \bsk \in \calK, \quad  \rho'<\infty \\
+    R \Lambda \delta_{\bsk,\bsk^*}, & \forall \bsk \in \calK, \ \bsk^* \in \calK \text{ satisfies } \lambda_{\bsk^*} = \Lambda, \quad \rho' = \infty,
+    \end{cases}
+   \\ 
     \implies  \ \ \norm[\calF]{f} = R \ \& \ \norm[\calG]{\SOL(f)} = R \Lambda.
-    \end{gather}
+    \end{multline}
+
+\PeterNote{Please excuse me for asking stupid questions all the time, but I was wondering: if $\rho'=\infty$, how would the formula for the $\hf (\bsk)$ in (7) look like?
+We would have $\infty$ in the exponents.}
+\FredNote{How does it look now?}
 Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} may be made tight.
@@
 \begin{proof}
+We give the proof for $\rho' < \infty$.  The proof for $\rho' = \infty$ follows similiarly. 
 The proof of inequality \eqref{DHKM:SOL_ineq} proceeds by applying H\"older's inequality:  
@@
     \norm[\calG]{\SOL(f)}  
-    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}} \\
-\nonumber
-    & = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
+    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
     \nonumber
@@
 This completes the proof.
-\end{proof}
-
-\hspace{\parindent} Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
+\end{proof} \
+
+%\hspace{\parindent} 
+Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
 \begin{equation} \label{DHKM:SOLNorm}
@@
 \end{equation}
-The $\lambda_{\bsk}$ define the smoothness of the input space and have a known order:
+The $\lambda_{\bsk}$ define the smoothness of the input space and are assumed to have a known order:
 \begin{equation} \label{DHKM:lambda_order}
@@
 \begin{equation} \label{DHKM:APP_def}
-    \APP : \calF \times \N_0 \to \calG, \qquad  \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i}, \quad \APP(f,0) = 0.
+    \APP : \calF \times \N_0 \to \calG, \quad  \APP(f,0) = 0, \ \ \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
 \end{equation}
@@
 
- Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.  Use Lemma \ref{DHKM:Key_Lem} to choose $f$ to satisfy the following conditions:
+ Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.
+Use Lemma \ref{DHKM:Key_Lem} with $\calK = \bbK \setminus \calJ$ to choose $f$ to satisfy the following conditions:
 \begin{gather*}
@@
     = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
-    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}
+    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.
 \end{gather*}
@@
 & \ge \norm[\calG]{\SOL(f)} 
-= \Bignorm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \notin \calJ}}
-    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
-    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \\
-    & = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.
+ = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOL_tight_ineq}}.
 \end{align*}
@@
 
-\hspace{\parindent} While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion
+\hspace{\parindent} The decay rate of the approximation error in \eqref{DHKM:APP_errorBd} depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
+This decay may be algebraic or exponential and will determine the complexity of the problem as a function of the error tolerance.
+
+While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion
 \begin{equation} \label{DHKM:err_crit}
@@
 The non-adaptive Algorithm \ref{DHKM:BallAlg} satisfies this error criterion for $\calC  = \calB_R$.
-However, in practice one cannot bound the norm of the input function a priori, so Algorithm \ref{DHKM:BallAlg} is impractical.
-
-In contrast to error bound \eqref{DHKM:APP_errorBd}, we will construct data-based error bounds for $\APP(f,n)$, which will lead to \emph{adaptive} algorithms $\ALG$ satisfying \eqref{DHKM:err_crit}.
-For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}.
 
@@
 \end{algorithm}
+
+After defining the information cost of an algorithm and the problem complexity in the next subsection, we demonstrate that this non-adaptive algorithm is optimal when the set of inputs is chosen to be $\calC = \calB_R$.
+However, typically one cannot bound the norm of the input function a priori, so Algorithm \ref{DHKM:BallAlg} is impractical.
+
+The key difficulty is that error bound \eqref{DHKM:APP_errorBd} depends on the norm of the input function.
+In contrast, we will construct  error bounds for $\APP(f,n)$ that only depend on function values.
+These will lead to \emph{adaptive} algorithms $\ALG$ satisfying error criterion \eqref{DHKM:err_crit}.
+For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball.
 
@@
 \end{equation}
-This means that the dependence of 
+If the complexity of the problem is $\calO(\varepsilon^{-p})$, the cost of an essentially optimal algorithm is also $\calO(\varepsilon^{-p})$.
+If the complexity of the problem is asymptotically $c \log(1 + \varepsilon^{-1})$, then  the cost of an essentially optimal algorithm is also asymptotically $c \log(1 + \varepsilon^{-1})$.
 We will show that our adaptive algorithms are essentially optimal.
+
+\begin{theorem}
+The non-adaptive Algorithm \ref{DHKM:BallAlg} is essentially optimal for our problem when the set of input functions is $\calC = \calB_R$, specifically
+\[
+\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R), \varepsilon R'/R,R') \qquad \forall \varepsilon > 0, \ 0 < R' \le R.
+\]
+\end{theorem}
+
+\begin{proof}  Fix positive $\varepsilon$, $R$ and $R' \le R$.  Let $\omega = R'/R$.  From the definition of the non-adaptive Algorithm  \ref{DHKM:BallAlg}, 
+\[
+\COST(\ALG, \calB_R, \varepsilon,R') = n^*(\varepsilon,R) = \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}.
+\]
+Construct an input function $f \in \calB_{R'}$ as in the proof of Theorem \ref{DHKM:APP_optimality_thm} with $\calJ = \{\bsk_1, \ldots, \bsk_{n^*(\omega \varepsilon,R')} \}$.
+By the argument in the proof of Theorem \ref{DHKM:APP_optimality_thm}, any algorithm in $\calA(\calB_{R'})$ that can approximate $\SOL(f)$ with an error no greater than $\omega \varepsilon$ must use at least $n^*(\omega \varepsilon,R')$ series coefficients.
+Thus,
+\begin{align*}
+\COST(\ALG, \calB_R, \varepsilon,R') & =  n^*(\varepsilon,R) 
+= n^*(\varepsilon R'/R,R') = n^*(\omega \varepsilon, R')
+\\
+& \le \COMP(\calA(\calB_{R'}),\omega \varepsilon, R') \le  \COMP(\calA(\calB_{R}),\omega \varepsilon, R').
+\end{align*}
+Thus, Algorithm \ref{DHKM:BallAlg} is essentially optimal. For $R'=R \ (\omega = 1)$, we have optimality.
+\end{proof}
+
+\hspace{\parindent} This theorem illustrates how an essentially optimal algorithm for solving a problem for a ball of input functions, $\calC = \calB_R$, can be non-adaptive.
+However, as alluded to above, we claim that it is impractical to know a priori which ball your input function lies in.
+On the other hand, in the situations described below where $\calC$ is a cone, we will show that $\calA(\calC)$ actually contains only adaptive algorithms via the lemma below.
+The proof of this lemma follows directly from the definition of non-adaptivity.
+
+\begin{lemma} \label{DHKM:NoNonAdpatLem}
+For a given set of input functions, $\calC$, if  $\calA(\calC)$ contains any non-adaptive algorithms, then for every $\varepsilon > 0$,
+\begin{equation*}
+    \sup_{R > 0} \COMP(\calA(\calC),\varepsilon, R) < \infty.
+\end{equation*}
+\end{lemma}
+
+Consider the example in Section 1.1, we obtain
+	\begin{align*}
+	\textup{COMP}(\calA(\calB_{R}),\varepsilon,R) &= \textup{COST}(ALG,\calB_{R},\varepsilon,R) 
+	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \} \\
+	& = \min \left\{ n \in \N_0: \prod_{\ell =1}^d \frac{1}{\max(1,k^r_{n+1,\ell})} \le \frac{\varepsilon}{R} \right\} 
+	% & \lambda_{n+1} = \frac{1}{\lceil (n+1)/2 \rceil^r}.
+	\end{align*}
+	\YuhanNote{I can't get an explicit bound of n}
+	Here, $\calG=L^2[-1,1]$.
+The larger the non-negative parameter $r$ is, the faster the $\lambda_{\bsk_i}$ tend to 0 as $ i \to 0$, the more exclusive $\calB_R$ is, and the smaller  $\textup{cost}(ALG,\calB_{R},\varepsilon,R)$ is.
+For $r = 0$, $\textup{cost}(ALG,\calB_{R},\varepsilon,R) = \infty$.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-The premise of an adaptive algorithm is that the finite information we observe about the input function that tells us something about what is not observed about the input function.
-Let $n_1$ denote the number of pilot samples to be observed, based on the wave numbers
+The premise of an adaptive algorithm is that the finite information we observe about the input function 
+tells us something about what is not observed about the input function.  Let $n_1$ denote the number of pilot samples to be observed, based on the wave numbers
 \begin{equation} \label{DHKM:KOnedef}
@@
 \begin{equation} \label{DHKM:pilot_cone}
-    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le a \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\},
-\end{equation}
-Define the data-based error bound,
-\begin{equation} \label{DHKM:pilot_errbd}
-    \ERRN : =  
-    a \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
-    \qquad n > n_1.
-\end{equation}
-Although the error bound does not actually depend on the series coefficients for $n> n_1$, we adopt this notation for the data-based error bound recognizing that other forms below do depend on all series coefficients observed.
-
-From the error bound on $\APP$ in \eqref{DHKM:APP_errorBd} and the definition of the cone in \eqref{DHKM:pilot_cone}, it follows that $ \norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN $ for all $f \in \calC$.
-For this cone of functions, Algorithm \ref{DHKM:PilotConeAlg} is successful:
+    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le a \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
+\end{equation}
+
+The error of $\APP(f,n)$ given in Theorem \ref{DHKM:APP_optimality_thm} can be refined by noting that the error only depends on the series coefficients numbered $n+1$ and more.  Specifically, 
+\begin{equation} \label{DHKM:Refined_APP_err}
+    \norm[\calG]{\SOL(f) - \APP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
+    \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
+\end{equation}
+Moreover, by the definitions of the $\calF$-norm and $\calC$,
+\begin{align*}
+     \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty} & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    \right]^{1/\rho} \qquad \forall f \in \calF \\
+    &  \le  \left[ a^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    \right]^{1/\rho} \quad \forall f \in \calC.
+\end{align*}
+This inequality together with \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
+\begin{subequations} \label{DHKM:pilot_errbd}
+\begin{equation}
+\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \calC,
+\end{equation}
+where 
+\begin{multline}
+\ERRN \\
+    : =  
+    \left[ a^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
+    \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
+    \\ n > n_1.
+\end{multline}
+\end{subequations}
+This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
+For this $\calC$ defined in \eqref{DHKM:pilot_cone}, Algorithm \ref{DHKM:PilotConeAlg} is successful:
 
@@
 
-\State Choose $n^* =  \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \}$, where $\ERR$ is defined in \eqref{DHKM:pilot_errbd}
-
-\RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
+\State Let $n \leftarrow 0$
+\Repeat
+
+\State Let $n \leftarrow n + 1$
+
+\State Compute $\ERRN$ as defined in \eqref{DHKM:pilot_errbd}
+
+\Until $\ERRN \le \varepsilon$
+
+\RETURN $\ALG(f,\varepsilon) = \APP(f,n)$
+
 \end{algorithmic}
@@
 The information cost is
-\begin{equation} \label{DHKM:PilotConeAlg_cost}
-    \COST(\ALG,\calC,\varepsilon,R) = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \varepsilon/(a R) \right \}.
-\end{equation}
+\begin{multline} \label{DHKM:PilotConeAlg_cost}
+    \COST(\ALG,\calC,\varepsilon,R) \\
+    = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le \varepsilon/[(a^\rho -1)^{1/\rho}R] \right \}.
+\end{multline}
 The computational complexity has the lower bound
@@
 \end{equation}
-Therefore, Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.
+Therefore, Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\calC)$ contains only adaptive algorithms.
 \end{theorem}
@@
     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
-     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
-     a \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
+     & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
+     (a^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}} \, 
      \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
@@
      & \le \min \left \{n \ge n_1 : 
-     a R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
+     (a^\rho -1)^{1/\rho} R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
     \le \varepsilon \right \},  
 \end{align*}
-since $\norm[\rho]{\left( \hf(\bsk_i)/\lambda_{\bsk_i} \right)_{i=1}^{n_1}} \le \norm[\calF]{f} \le R$ for all $f \in \calB_R$.
+since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
 Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
@@
 \end{align*}
-by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.  This inequality implies the lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
+by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.
+This inequality implies the lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
+Because $\lim_{R \to \infty} \COMP(\calA(\calC), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\calC)$ contains only adaptive algorithms.
 
@@
 \[
-\COST(\ALG,\calC,\varepsilon,R) \le \COMP(\calA(\calC),\omega \varepsilon,R) \qquad \text{for } \omega = (1-1/a)/(2a).
+\COST(\ALG,\calC,\varepsilon,R) \le \COMP(\calA(\calC),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/a}{2(a^\rho -1)^{1/\rho}}.
 \]
@@
 \begin{proposition}
-If $f \in \calC$ and $n^*$ is defined as in Algorithm \ref{DHKM:PilotConeAlg}, then 
+If $f \in \calC$, then 
 \begin{equation} \label{DHKM:PilotConeNecessary}
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n^*}} \le a 
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}.
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n}} \le a 
+    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \ge n_1.
 \end{equation}
@@
 distinction is useful because it allows us to relate the computational complexity of the algorithms 
-considered in this paper to the computational complexity of linear problems considered over the 
-unit ball of certain function spaces. Then, the case $\rho'=\infty$ corresponds to the so-called 
-worst-case setting, and the case $\rho<\infty$ corresponds to the so-called average-case setting. 
+considered in this paper to the computational complexity of linear problems on certain function spaces considered in the classical literature on information-based complexity, as for example \cite{NovWoz08a}.
+The case $\rho'=\infty$ corresponds to the so-called
+worst-case setting, where one studies the worst performance of an algorithm over the unit ball of 
+a space. The case $\rho<\infty$ corresponds to the so-called average-case setting, where one 
+considers the average performance over a function space equipped with a suitable measure. 
 For both of these settings there exist tractability results that we will make use of here.
@@
 
-If $\rho'=\infty$, we have due to the monotonicity of the $\lambda_{\bsk_i}$, 
+If $\rho'=\infty$, we have, due to the monotonicity of the $\lambda_{d,\bsk_i}$, 
 \[
@@
 \cite{WerWoz17} study $\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$, 
-there are slight differences between the results here and those in the aforementioned references; to be more precise, the exponent of strong polynomial tractability is $\eta$ here, whereas corresponds to $2\eta$ in \cite{NovWoz08a}, and $1/\lambda_{d,\bsk_i}$ in \eqref{DHKM:eq:condwt} corresponds to $1/\sqrt{\lambda_{d,\bsk_i}}$ in \cite{WerWoz17}.
+there are slight differences between the results here and those in the aforementioned references; to be more precise, the exponent of strong polynomial tractability is $\eta$ here, whereas it is $2\eta$ in \cite{NovWoz08a}, and $1/\lambda_{d,\bsk_i}$ in \eqref{DHKM:eq:condwt} corresponds to $1/\sqrt{\lambda_{d,\bsk_i}}$ in \cite{WerWoz17}.
 \end{proof}
@@
 \sum_{i=n+1}^\infty \widetilde{\lambda}_{d,i}\,
-    \le \widetilde{\varepsilon}^{\,2} \right \},
+    \le \widetilde{\varepsilon}^{\,2} \right \}.
 \end{equation}
@@
 $\widetilde{\lambda}_{d,i}$ and $\widetilde{\varepsilon}$) defined 
-on unit balls of certain spaces as studied in, e.g., \cite{NovWoz08a}. 
+on certain spaces as studied in, e.g., \cite{NovWoz08a}. 
 This leads us to the following theorem.
@@
  \[
-   \lim_{i\to\infty} t_{d,i}\, \log i^2=0\quad\mbox{for all $d$},
+   \lim_{i\to\infty} t_{d,i}\, (\log i)^2=0\quad\mbox{for all $d$},
  \]
@@
   \sup_{\beta\in (0,1/2]}\, \beta^{-2} \,
-  \sup_{d\ge f(\beta)}\,\, \sup_{i\ge \lceil \exp (d\sqrt{b}) \rceil +1}\, \, \lim_{i\to\infty} t_{d,i}\, \log i^2
+  \sup_{d\ge f(\beta)}\,\, \sup_{i\ge \lceil \exp (d\sqrt{b}) \rceil +1}\, \, \lim_{i\to\infty} t_{d,i}\, (\log i)^2
   < \infty.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tracking the Decay Rate of the Series Coefficients} 
+\section{Tracking the Decay Rate of the Series Coefficients \FredNote{of the Input Function}}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+From the argument leading to \eqref{DHKM:SOL_A} it follows that 
+\begin{equation} \label{DHKM:APP_Err_Coef}
+    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
+\end{equation}
+The faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
+Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
+It simply bounds $\norm[\calF]{f}$ based on a pilot sample.
+The algorithm presented in this section does track the rate of decay of the $\hf(\bsk_i)$ and terminate sooner if the $\hf(\bsk_i)$ decay more quickly.
+
+Let $(n_j)_{j\ge 0}$ be a strictly increasing sequence of non-negative integers.
+This sequence may increase geometrically or algebraically.
+Define the sets of wavenumbers analogously to \eqref{DHKM:KOnedef}.
+\begin{equation}
+   n_{-1}=0, \qquad \calK_j := \{\bsk_{n_{j-1}+1}, \ldots, \bsk_{n_j}\} \quad \text{for } j \in \N_0.
+\end{equation}
+If $n_0 = 0$, then $\calK_0$ is empty.  For any $f \in \calF$, define the norms of subsets of series coefficients:
+\begin{equation} \label{DHKM:SigmaDef}
+\sigma_j (f):=\norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} \qquad \text{for } j \in \N.
+\end{equation}
+For this section, we define the cone of input functions, $\calC$, by
+\begin{equation} \label{DHKM:TrackConeDef}
+  \calC : =\left\{f\in\calF \colon \sigma_{j+r} (f)\le ab^r \sigma_j (f)\ \forall j,r\in\NN\right\}.
+\end{equation}
+Here, $a$ and $b$ are positive reals with $b< 1 < a$.
+The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
+Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
+However, we expect their partial sums to decay steadily.
+The series coefficients for  wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\calC$ and may behave erratically.
+Lemma \ref{DHKM:Key_Lem} implies that 
+\begin{equation} \label{DHKM:LambdaDef}
+    \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_j}} \le \sigma_j(f) \Lambda_j, \qquad \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
+\end{equation}
+
+If $f$ belongs to the $\calC$ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
+\begin{align*}
+    \norm[\calF]{f} & = \norm[\rho]{\Biggl(\,\norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
+    & \le \bignorm[\rho]{\bigl(\sigma_1(f), ab \sigma_1(f), ab^2 \sigma_1(f), \ldots \bigr)} \\
+    & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
+\end{align*}
+Comparing this inequality to the definition of $\calC$ in the previous section, it can be seen that  $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone} with a different $a$.
+
+\FredNote{Hmm.  Should we use different $a$ to distinguish the two?}
+
+\PeterNote{Thanks, Fred, for adapting it such that we see the relation between the two kinds of cones. 
+A different $a$ would be good, if it does not too much trouble.
+Would you like me to change $a$ in Section 2 to $\widetilde{a}$?}
+\FredNote{$\widetilde{a}$ or $A$, not sure which is best.  Let's wait until we have finished the rest. }
+From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, one can now derive a data-driven error bound for all $f \in \calC$ and $j \in \bbN$:
+\begin{align}
+\nonumber
+\MoveEqLeft{\norm[\calG]{\SOL(f)-\APP(f,n_j)}} \\
+\nonumber &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty}
+= \norm[\tau]{ \left(\norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_l}} \right)_{l=j+1}^\infty}
+\\
+\nonumber
+& \le \norm[\tau]{ \bigl(\sigma_l(f) \Lambda_l \bigr)_{l=j+1}^\infty} \qquad \text{by \eqref{DHKM:LambdaDef}} \\
+\nonumber 
+&
+= \norm[\tau]{ \bigl(\sigma_{j+r}(f) \Lambda_{j+r} \bigr)_{r=1}^\infty}
+\\
+& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^r\Lambda_{j+r} \bigr)_{r=1}^\infty} =:\ERRNj
+ \qquad \text{by \eqref{DHKM:TrackConeDef}.}
+ \label{DHKM:algoineq}
+\end{align}
+
+This upper bound depends only on the function data and the parameters defining $\calC$.
+The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ and $\Lambda_j \to 0$.
+Moreover, the error bound for $\APP(f,n_j)$ depends on $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
+
+\FredNote{\emph{This part added to illustrate the sequence of $n_j$}
+
+These assumptions accommodate both the cases where the approximation converges algebraically and exponentially.
+To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \calO(i^{-r_\Delta})$ for some positive $r_\Delta > 1/\rho$.
+For this algebraic case one would normally define $\calC$ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
+\begin{align*}
+    \sigma_j(f) &= \left[ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
+    = \calO \left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
+    & = \calO \left(  2^{-j(r_\Delta-1/\rho)} \right)
+\end{align*}
+Reasonable functions would satisfy 
+\begin{equation*}
+    C_{\lo} 2^{-j(r_\Delta-1/\rho)} \le \sigma_j(f) \le C_{\up} 2^{-j(r_\Delta-1/\rho)} 
+\end{equation*}
+for some constants $C_{\lo}$ and $C_{\up}$.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\calC$ to include such functions.
+Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
+
+To illustrate the exponential case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \calO(\E^{-r_\Delta i})$.
+For this exponential case one would normally define $\calC$ in terms of an arithmetic sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 + j s$, where $s$ is a positive integer.
+This implies that
+\begin{align*}
+    \sigma_j(f) &= \left[ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
+    = \calO \left( \left [ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
+    & = \calO \left(  \E^{-j r_{\Delta} s} \right)
+\end{align*}
+Analogous to the algebraic case, reasonable functions would satisfy 
+    $C_{\lo} \E^{-j r_{\Delta} s} \le \sigma_j(f) \le C_{\up} \E^{-j r_{\Delta} s}$
+for some constants $C_{\lo}$ and $C_{\up}$.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} s}$ causes the cone $\calC$ to include such functions.
+Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The Adaptive Algorithm and Its
+ Computational Cost}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\calC$ defined in \eqref{DHKM:TrackConeDef}.
+The following theorem establishes its viability and computational cost.
+In deriving upper bounds on the computational cost and lower bounds on the complexity, we may sacrifice tightness for simplicity.
+
+\begin{algorithm}
+	\caption{Adaptive ALG for a Cone of Input Functions Tracking the Series Coefficient Decay Rate \label{DHKM:TrackConeAlg}}
+	\begin{algorithmic}
+	\PARAM a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0}$; an inflation factor, $a$; the general decay rate, $b$; $\APP$ satisfying \eqref{DHKM:APP_Err_Coef}
+		\INPUT a black-box function, $f$; an absolute error tolerance,
+		$\varepsilon>0$
+
+\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:TrackConeDef}
+
+\State Let $j \leftarrow 0$
+\Repeat
+
+\State Let $j \leftarrow j + 1$
+
+\State Compute $\ERRNj$ as defined in \eqref{DHKM:algoineq}
+
+\Until $\ERRNj \le \varepsilon$
+
+\RETURN $\ALG(f,\varepsilon) = \APP(f,n_{j})$
+\end{algorithmic}
+\end{algorithm}
+
+\begin{theorem}\label{DHKM:TractConeCompCost}
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC)$ for $\calC$ defined in \eqref{DHKM:TrackConeDef}.
+The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
+\begin{equation} \label{DHKM:EqTractConejstar}
+j^* = \min\left \{ j \in \bbN : \ERRNj \le \varepsilon  \right\}.
+\end{equation}
+Moreover, $\COST(\ALG,\calC,\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+\begin{equation} \label{DHKM:TractConejdagger}
+j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}
+\le  \frac{b\varepsilon}{Ra^2} \left( \frac{1 - b^{j\rho}}{1 - b^\rho} \right)^{1/\rho} \right\}.
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+The value of $j^*$ in \eqref{DHKM:EqTractConejstar} follows directly from the error criterion. The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
+
+For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.  For any $f \in  \calC \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
+\begin{align*}
+R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
+ \ge \norm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
+ \qquad \text{by \eqref{DHKM:SigmaDef} } \\
+& \ge \norm[\rho]{\left(a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f), \ldots, a^{-1} b^{-1}\sigma_{j^\dagger}(f), \sigma_{j^\dagger}(f) \right) } \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
+& \ge \frac {\sigma_{j^\dagger}(f)} a \norm[\rho]{\bigl(b^{1-j^\dagger}, \ldots, b^{-1}, 1 \bigr) } 
+= \frac {b\sigma_{j^\dagger}(f)} a \left( \frac{b^{-j^\dagger\rho} -1}{1 - b^\rho} \right)^{1/\rho}\\
+& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^r\Lambda_{j^\dagger+r} \bigr)_{r=1}^\infty}
+\qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
+& = \frac{R}{\varepsilon} \ERRNjd\, .
+\end{align*}
+From this last inequality, it follows that $j^\dagger \ge j^*$.
+\end{proof}
+
+\FredNote{Pity, I do not see our cost upper bounds reflecting different rates of decay of the series coefficients.  Perhaps a remark here is in order.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Essential Optimality of the Algorithm and Tractability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The following theorem establishes a lower bound on the complexity of our problem for input functions in $\calC$.
+The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TractConeCompCost} is essentially no worse than this lower bound.
+
+\begin{theorem} \label{DHKM:TractConeLowBdComp}
+A lower bound on the complexity of the linear problem is
+\begin{align*}
+ %\label{compbdA}
+&\COMP(\calA(\calC),\varepsilon,R) > n_{j^\ddagger}, 
+\intertext{where}
+%\label{compbdB}
+j^\ddagger & = \max \left \{ j \in \bbN :  b^{j+1} \Lambda_{j+1}    >
+ \frac{2a}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
+\right \}.
+\end{align*}
+\end{theorem}
+
+\begin{proof}
+
+As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
+We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC \cap \calB_{R}$, which yield the same approximate solution but different true solutions.
+This leads to a lower bound on $\COMP(\calA(\calC),\varepsilon,R)$.
+
+The first test function $f_1 \in \calC$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
+\begin{align}
+\nonumber
+f_1 &= f_{10} + f_{11} +  \cdots, \qquad
+\hf_{1j}(\bsk) := \begin{cases}
+\displaystyle
+\frac{c_1 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_j^{\rho'/\rho}},  & \bsk \in \calK_j,
+\\
+0, & \bsk \notin \calK_j,
+\end{cases}
+\\
+\nonumber
+c_1 &:=  \frac{R(a+1)(1 - b^\rho)^{1/\rho}}{2a}.
+\end{align}
+It can be verified that the test function lies both in $\calB_{R}$ and in $\calC$:
+\begin{align}
+\nonumber
+\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
+= c_1 b^j, \qquad j \in \N_0,\\
+\nonumber
+\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \sigma_j(f) \bigr)_{j \in \N_0} } 
+=  \frac{c_1}{(1 - b^\rho)^{1/\rho}} = \frac{R(a+1)}{2a} \le R,
+\\
+\nonumber
+\sigma_{j+r}(f_1) &= 
+b^{r} \sigma_j(f_1) \le a b^r \sigma_j(f_1), \qquad j,r \in \N_0.
+\end{align}
+
+Now let $\ALG'$ be an arbitrary algorithm in $\calA(\calC)$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$, where the cardinality of $\calJ$ is $n$.
+Let $\tcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
+Construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
+\begin{align}
+\nonumber
+f_2 &= f_{20} + f_{21} +  \cdots, \qquad \hf_{2j}(\bsk) := \begin{cases}
+\displaystyle
+\frac{c_2 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\tLambda_j^{\rho'/\rho}},  
+& \bsk \in \tcalK_j,
+\\
+0, & \text{otherwise},
+\end{cases}
+\\
+\nonumber
+c_2 &:= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}, \qquad
+\tLambda_j := \norm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \tcalK_j}} \le \Lambda_j, \\
+\nonumber
+\sigma_j(f_2) & = \norm[\rho]{\biggl(\frac{\hf_{2j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \tcalK_j}} 
+= \begin{cases} c_2 b^j, & \tcalK_j \ne \emptyset, \\
+0, & \tcalK_j = \emptyset, 
+\end{cases}
+\qquad j \in \N_0, \\
+\nonumber 
+\norm[\calF]{f_2} &= \norm[\rho]{\bigl( \sigma_j(f_{2}) \bigr)_{j \in \N_0} } 
+\le \frac{c_2}{(1 - b^\rho)^{1/\rho}} = \frac{R(a - 1)}{2a}\le R, \\
+\nonumber 
+\norm[\calG]{\SOL(f_{2j})} &= \sigma_j(f_{2j}) \tLambda_j = 
+c_2 b^{j} \tLambda_j, \qquad j \in \N_0, \\
+\norm[\calG]{\SOL(f_2)} & = \norm[\tau]{\bigl(c_2 b^{j} \tLambda_j \bigr)_{j \in \N_0}}
+= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}.
+\label{DHKM:SOLftwo}
+\end{align}
+
+Furthermore, define $f_{\pm} = f_1 \pm f_2$.
+It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\calC$:
+\begin{align}
+\nonumber
+\norm[\calF]{f_\pm} &\le \norm[\calF]{f_1} + \norm[\calF]{f_2} \le \frac{c_1 + c_2}{(1 - b^\rho)^{1/\rho}} = R,
+\\
+\nonumber
+\sigma_j(f_\pm) & \ge \sigma_j(f_1) - \sigma_j(f_2) \ge
+\left(c_1 - c_2 \right) b^{j} = \frac{R(1 - b^\rho)^{1/\rho}b^{j}}{a},  \qquad j \in \N_0,
+\\
+\nonumber
+\sigma_{j+r}(f_\pm) & \le \sigma_{j+r}(f_1) + \sigma_{j+r}(f_2) \le 
+(c_1+c_2) b^{j+r} 
+\\
+\nonumber
+& =  R(1 - b^\rho)^{1/\rho}b^{j+r}
+\le a b^r \sigma_j(f_\pm),  \qquad j \in \N_0.
+\end{align}
+
+Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG'(f_1,\varepsilon) = \ALG'(f_\pm,\varepsilon)$.
+But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
+In particular,
+\begin{align}
+\nonumber
+\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - \ALG'(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - \ALG'(f_-,\varepsilon)} \bigr\} \\
+\nonumber
+&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{S(f_-) - \ALG'(f_1,\varepsilon)}  \bigr] \\
+\nonumber
+&\qquad \qquad \text{since } \ALG'(f_\pm,\varepsilon) = \ALG'(f_1,\varepsilon) \\
+\nonumber
+&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
+\nonumber
+&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $\SOL$ is linear}\\
+&= \norm[\calG]{\SOL(f_2)} 
+= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}
+\qquad 
+\text{by \eqref{DHKM:SOLftwo}.}
+\label{DHKM:eps_LBA}
+\end{align}
+
+\FredNote{The next step is to derive a lower bound on the $\tau$-norm term above, which we can use to show optimality.
+
+I am writing this part informally to explain to the rest of you my thinking.  We need to tighten the writing later.
+
+We make some further assumptions, which I think are reasonable, but can be checked later.  First we assert that the $\Lambda_j$ decrease montonically:
+\begin{equation*}
+     \Lambda_1 \ge \Lambda_2 \ge \cdots.
+\end{equation*}
+We also assume that the ratio of the largest to smallest $\lambda_{\bsk}$ in a group is bounded above:
+\begin{equation*}
+    \sup_{j \in \N} \frac{\lambda_{\bsk_{n_{j-1}+1}}}{\lambda_{\bsk_{n_{j}}}} \le S_1 < \infty.
+\end{equation*}
+Finally, we assume that if $n\le n_j$, then at least some of the $\tcalK_l$ must have a cardinality that is not too small a proportion of the cardinality of the  $\calK_l$, i.e. 
+\begin{equation*}
+    \max_{1 \le l \le j+1} \frac{\bigabs{\tcalK_l}}{\abs{\calK_l}} \ge S_2 > 0.
+\end{equation*}
+
+Suppose that $n = \abs{\calJ} = \COST(\ALG',f_{\pm},\varepsilon) \le n_l$.
+Then by the above third condition, there exists an $l^*$ where $\normabs{\tcalK} \ge S_2 \abs{\calK}$.
+This implies a lower bound on $\tLambda_{l^*}$.
+Let $m = n_{l^*} - n_{l^*-1}$, $m_{\inc} = \lceil S_2 m \rceil$, and $m_{\out} = m - m_{\inc}$
+\begin{align*}
+    \Lambda_{l^*}^\rho & = \sum_{i \in \calK_{l^*}} \lambda_{\bsk_i}^{\rho} =  \tLambda_{l^*}^\rho + \sum_{i \in \calK_{l^*} \setminus \tcalK_{l^*}} \lambda_{\bsk_i}^{\rho}
+    \\
+    &\le  \tLambda_{l^*}^\rho + m_{\out} \lambda_{\bsk_{n_{l^* -1}+1}}^\rho \\
+    &\le  \tLambda_{l^*}^\rho + m_{\out} S_1^\rho \lambda_{\bsk_{n_{l^*}}}^\rho \\
+    & \le \tLambda_{l^*}^\rho + \frac{m_{\out}}{m_{\inc}} S_1^\rho \tLambda_{l^*}^\rho \\
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] \tLambda_{l^*}^\rho
+\end{align*}
+
+Thus, going back to \eqref{DHKM:eps_LBA} it follows that 
+\begin{align}
+\nonumber
+\varepsilon 
+& \ge \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} b^{l^*} \tLambda_l^* 
+\\
+\nonumber
+& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} b^{l^*} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} \Lambda_{l^*}
+\\
+\nonumber
+& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{l+1} \Lambda_{n_{l+1}}
+\end{align}
+Therefore, if this inequality is violated for any $l$, we must have $n>n_l$}
+
+\FredNote{The expression above has been corrected.  The hard work is still to bridge the gap.
+
+=====Begining of the gap}
+
+\PeterNote{To see whether the original proof method still works:
+
+\medskip
+
+Let $j_1<j_2$ (i.e., $n_{j_1} < n_{j_2}$), and assume furthermore 
+that $i_1\in \{n_{j_1-1}+1,\ldots,n_{j_1}\}$ and $i_2\in \{n_{j_2-1}+1,\ldots,n_{j_2}\}$. If we could 
+show that
+\begin{multline*}
+ \left(\sum_{i=n_{j_1-1}+1}^{n_{j_1}} b^{j_1} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'} +
+ \left(\sum_{\substack{i=n_{j_2-1}+1\\ i\neq i_2}}^{n_{j_2}} b^{j_2} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'}\ge\\
+  \left(\sum_{\substack{i=n_{j_1-1}+1\\ i \neq i_1}}^{n_{j_1}} b^{j_1} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'} +
+ \left(\sum_{i=n_{j_2-1}+1}^{n_{j_2}} b^{j_2} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'}
+\end{multline*}
+that should be enough.
+
+Or, more simply: Suppose $v\le 1$, and $a,b,\beta,\alpha$ are positive reals, with $\alpha>\beta$, 
+and $\alpha\le a$, $\beta\le b$. 
+Do we always have
+\[
+ a^v + (b-\beta)^v \ge (a-\alpha)^v + b^v\ ?
+\]
+Can we use the two-dimensional mean value theorem?
+
+Just tried numerically, no it does not work. There are counterexamples.
+}
+
+\FredNote{Peter suggeted Jensen's inequality.  But I could not figure out how to apply that.
+}
+
+\FredNote{End of gap ======}
+\PeterNote{I am afraid with Jensen's inequality we will not get the condition we want but a weaker one.
+Another thought: can we multiply the lower bound after the gap with a small quantity (depending on b, $\tau$, $\rho'$) such that the lower bound holds?}
+
+The smallest that this double sum can be is when the set of wavenumbers sampled corresponds to the first $n$, i.e., $\calJ = \{\bsk_1, \ldots, \bsk_n\}$.
+Therefore, for all $j \in \N$ satisfying $n_{j} \ge n$, it follows that
+\begin{align*}
+    \varepsilon & \ge \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \left(\sum_{r=1}^\infty b^{(j+r)\tau}  \, \left(\sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \lambda_{\bsk_i}^{\rho'} \right)^{\tau/\rho'} \right)^{1/\tau} \\
+    & = \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j+r} \Lambda_{j+r} \bigr)_{r \in \N}}.
+\end{align*}
+On the contrary, if $n > n_j$, then the above inequality must be violated \PeterNote{I am not good with such conclusions, but why does $n> n_j$ imply that the inequality must be violated?
+What am I missing?}.
+This implies the stated lower complexity bound.
+
+\end{proof}
+
+\medskip
+
+\PeterNote{Working on Tractability below:
+
+\bigskip
+
+We again would like to study tractability. Like in Section~\ref{DHKM:SecPilotTract}, we distinguish whether $\rho'=\infty$ or not.
+
+\paragraph*{CASE 1: $\rho'=\infty$:}
+
+\begin{theorem} \label{DHKM:thmtract3}
+Using the same notation as above, strong polynomial, polynomial, and weak tractability for the case $\rho'=\infty$ hold under exactly the 
+same conditions as in Theorem \ref{DHKM:thmtract1}.
+\end{theorem}
+\begin{proof}
+
+Regarding sufficiency of the conditions, as pointed out above, $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone}, with suitably adapted constants (\PeterNote{I will make this more precise once we have agreed on notation}).
+This means that the approximation problem on  $\calC$ defined in \eqref{DHKM:TrackConeDef} is essentially no harder than the same problem on $\calC$ defined in \eqref{DHKM:pilot_cone}.
+This, however, implies that all sufficient conditions in Theorem \ref{DHKM:thmtract1} are also sufficient in the case considered in Theorem \ref{DHKM:thmtract3}.
+
+\medskip
+
+Regarding necessity of the conditions \ldots (\PeterNote{To come once we have lower bounds}).
+
+\end{proof}
+
+\paragraph*{CASE 2: $\rho'<\infty$:}
+
+\begin{theorem} \label{DHKM:thmtract4}
+Using the same notation as above, strong polynomial, polynomial, and weak tractability for the case $\rho'<\infty$ hold under exactly the 
+same conditions as in Theorem \ref{DHKM:thmtract2}.
+\end{theorem}
+\begin{proof}
+Sufficiency of the conditions follows by the same argument as in the proof of Theorem \ref{DHKM:thmtract3}.
+
+\medskip
+
+Regarding necessity of the conditions \ldots (\PeterNote{To come once we have lower bounds}).
+
+\end{proof}
+
+}
+
+%%%%%%%%%%%%
+\subsection{Numerical Example}
+%%%%%%%%%%%%
+
+\iffalse
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Tracking the Decay Rate of the Series Coefficients \FredNote{of the Solution}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 If $n_0 = 0$, then $\calK_0$ is empty.
+
+If $f$ belongs to the $\calC$ defined in \eqref{DHKM:TrackConeDef}, then
+
+\PeterNote{Fred, in our last discussion we talked about the problem in Section 2 being ``easier" than that in Section 3.
+Intuitively, I agree; but how do we make this precise?
+It does not seem obvious to me.}
 
@@
 
+\fi
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In the following, we present a framework which accounts for coordinate, order and smoothness importance on $f$, via the weights $(\lambda_\bsk)_{\mathbf{k} \in \mathbb{K}}$ from Section 1.1.
-We then show how such structure can be inferred from a pilot sample, and how the resulting inferred weights can be used for adaptive sampling on $f$.
+We then show how such structure can be inferred from a pilot sample, and how the resulting inferred weights can be used for adaptive approximation on $f$.
 For simplicity, we assume the index set $\mathbb{K}$ to be $\mathbb{N}_0^d$ in this section.
@@
 
-Consider next the following POSD parametrization of weights $(\lambda_{\bsk})_{\bsk \in \mathbb{N}_0^d}$:
+We employ the following POSD parametrization of weights $(\lambda_{\bsk})_{\bsk \in \mathbb{N}_0^d}$:
 \begin{equation}
-\lambda_{\bsk} = \Gamma_{\|\bsk\|_0} \prod_{\substack{l=1\\ k_l>0}}^d w_l s_{k_l}, \quad \Gamma_0 = s_1 = 1, \quad \bsk = (k_1, \cdots, k_d).
+\lambda_{\bsk} = \Gamma_{\|\bsk\|_0} \prod_{\substack{l=1\\ k_l>0}}^d w_l s_{k_l}, \quad \Gamma_0 = s_1 = 1, \quad \bsk = (k_1, \cdots, k_d) \in \mathbb{N}_0^d,
 \label{eq:posd}
 \end{equation}
-\PeterNote{Is $\|\bsk\|_0$ equal to the number of non-zero components in $\bsk$?}
-This parametrization is motivated by several guiding principles from the experimental design literature (see \cite{WuHam2009}), which presumes certain structure on $f$ for effective inference with limited data.
+where $\|\bsk\|_0$ equals the number of non-zero components in $\bsk$.
+This parametrization is motivated by several guiding principles from the experimental design literature (see \cite{WuHam2009}), which are briefly described below:
 \begin{itemize}
 \item The first principle, called \textit{effect sparsity}, assumes only a small number of input variables are important in $f$.
-In \eqref{eq:posd}, this sparsity can be accounted for restricting (\PeterNote{allowing?}) only a small number of product weights $\mathbf{w}$ to be large.
+In \eqref{eq:posd}, this sparsity can be accounted for allowing only a small number of product weights $\mathbf{w}$ to be large.
 \item The second principle, called \textit{effect heredity}, states that lower-order effects are more important than higher-order effects.
@@
 Effect smoothness can be imposed by setting a decreasing sequence for smoothness weights $\mathbf{s}$.
-This decaying importance in smoothness \PeterNote{Something seems to be missing.}
 \end{itemize}
 
-From a quasi-Monte Carlo (QMC) perspective, the POSD weights in \eqref{eq:posd} generalize upon the product-and-order dependent (POD) weights in \cite{KuoEtal12a}, which were first introduced in the analysis of QMC methods for partial differential equations with random coefficients.
+From a Quasi-Monte Carlo (QMC) perspective, the POSD weights in \eqref{eq:posd} generalize upon the product-and-order dependent (POD) weights in \cite{KuoEtal12a}, which were first introduced in the analysis of QMC methods for partial differential equations with random coefficients.
 In particular, these existing POD weights can be recovered by restricting indices to be in $\{0, 1\}^d$, and setting $\mathbf{s} \equiv 1$ (i.e., all smoothness effects are of equal importance).
@@
 As mentioned earlier, the key motivation for an adaptive algorithm is that it allows us to infer, from finite observations, information on what was not observed on $f$.
-In Section 2, this is used to bound the input function norm $\| f \|_{\mathcal{F}}$.
-A similar inference approach is introduced next for POSD weights: these weights are first inferred from a pilot sample, then used for adaptive error estimation and sampling.
-For simplicity, we assume in the following that order weights $\boldsymbol{\Gamma}$ are fixed (these can be preset a priori), and focus on the inference of product and order weights from data.
+We introduce next such an adaptive algorithm using POSD weights: these weights are first inferred from a pilot sample, then used for adaptive error estimation and sampling.
+For simplicity, we assume that order weights $\boldsymbol{\Gamma}$ are fixed (these can be preset a priori), and focus on the inference of product and order weights from data.
+This algorithm should work well for approximating functions within the data-based cone $\mathcal{C}$ in \eqref{DHKM:pilot_cone}, where $(\lambda_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are now the inferred POSD weights from the pilot sample.
 
@@
 These two steps are repeated until both $\mathbf{w}$ and $\mathbf{s}$ converge.
-One nice feature of this iterative procedure is the so-called ``descent property'' -- one can show that the pilot sample input norm $\|(\hat{f}(\bsk_i)/\lambda_{\bsk_i})_{i=1}^n\|_{\rho}$ (the objective to minimize) indeed decreases within each iteration, which stabilizes the optimization algorithm.
+One nice feature of this iterative procedure is the so-called ``descent property'' -- one can show that the pilot sample input norm $\|(\hat{f}(\bsk_i)/\lambda_{\bsk_i})_{i=1}^n\|_{\rho}$ (the objective to minimize) indeed decreases with each iteration, which stabilizes the optimization algorithm.
 
@@
 In our implementation, we take $\mathcal{I}$ to be $\{ (0, \ldots, 0, j, 0, \ldots, 0): j = 0, \ldots, s^*\}$, the set of all univariate indices with maximum smoothness $s^*$.
-The intuition here is that, by sampling all possible coefficient smoothness (\PeterNote{smoothness coefficients?}) over each variable ($\# \mathcal{I} = d s^* + 1$ coefficients in total), one can accurately infer from this pilot sample both variable importance weights $\mathbf{w}$ and smoothness weights $\mathbf{s}$.
+The intuition here is that, by sampling all possible smoothness coefficients over each variable ($\# \mathcal{I} = d s^* + 1$ coefficients in total), one can accurately infer from this pilot sample both variable importance weights $\mathbf{w}$ and smoothness weights $\mathbf{s}$.
 
@@
 	\begin{algorithmic}
-	\PARAM maximum product and smoothness weights, $w^*$ and $s^*$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $\frakC$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}; 
+	\PARAM maximum product and smoothness weights, $w^*$ and $s^*$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $a > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}; 
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 We now investigate the numerical performance of this adaptive algorithm with POSD weights.
-For simplicity, we consider only the case of $\rho = \infty$ and $\rho' = \tau = 1$ here.
+For simplicity, only the case of $\rho = \infty$ and $\rho' = \tau = 1$ is considered here.
 The simulation set-up is as follows.
@@
 \begin{equation}
-\hat{f}(\bsk) = Z_{\bsk} \left( \Gamma_{\|\bsk\|_0}^* \prod_{\substack{l=1\\ k_l>0}}^d w_l^* s_{k_l}^* \right), \quad Z_{\bsk} \overset{\mathrm{i.i.d.}}{\sim} \text{Unif}\{-1, 1\},
+\hat{f}(\bsk) = Z_{\bsk} \left( \tilde{\Gamma}_{\|\bsk\|_0} \prod_{\substack{l=1\\ k_l>0}}^d \tilde{w_l} \tilde{s}_{k_l} \right), \quad Z_{\bsk} \overset{i.i.d.}{\sim} \text{Unif}\{-1, 1\}, \quad \mathbf{k} \in \mathbb{N}_0^d.
 \label{eq:foursim}
 \end{equation}
-where $w_l^* = 1/l^2$, $\Gamma_k^*= 1/k!$ and $s_j^* = 1/j^3$ are the true order, product and smoothness weights of $f$, and $Z_{\bsk}$ randomly sets the sign of each coefficient.
-Here, the product weights are also randomized in terms of order, to ensure that the order of the inputs in $f$ does not necessarily reflect the order of variable importance.
-We also assume that the order weights $\boldsymbol{\Gamma}$ in Algorithm \ref{DHKM:InfPilotConeAlg} are the true order weights $\boldsymbol{\Gamma}^*$.
-
-Figure \ref{fig:four} shows the
+Here, $\tilde{w_l} = 1/l^2$, $\tilde{\Gamma}_k= 1/k!$ and $\tilde{s_j} = \mathbbm{1}\{ j \leq 4 \}/j^3$ are the true order, product and smoothness weights of $f$, and $Z_{\bsk}$ randomly sets the sign of each coefficient.
+The product weights are also randomized in terms of variable order, to ensure that the order of input variables does not necessarily reflect the order of variable importance.
+For Algorithm \ref{DHKM:InfPilotConeAlg}, we set $\boldsymbol{\Gamma}$ as the true order weights $\tilde{\boldsymbol{\Gamma}}$, and use an inflation factor of $a = 1.1$.
+
+Figure \ref{fig:four} (a) and (b) plot the adaptive sample size $n^*$ (from Algorithm \ref{DHKM:InfPilotConeAlg}) as a function of the error ratio $\|f - \hat{f}\|_{\infty}/\epsilon$, for $f$ in $d=4$ and $d=8$ dimensions, respectively.
+Each data point corresponds to a different error tolerance $\epsilon$.
+Here, an error ratio $\|f - \hat{f}\|_{\infty}/\epsilon$ close to 1 (but not exceeding 1) is desired, since this shows our adaptive approach can achieve the desired error tolerance $\epsilon$ by inferring and incorporating POSD structure.
+For $d=4$ (Figure \ref{fig:four} (a)), the error ratios $\|f - \hat{f}\|_{\infty}/\epsilon$ fluctuate around 0.25 for all choices of $\epsilon$; for $d=8$ (Figure \ref{fig:four} (b)), these ratios begin at $\approx 0.2$ for $\epsilon = 0.1$, and decrease to $\approx 0.07$ for $\epsilon = 0.001$.
+This suggests that our adaptive algorithm works reasonably well, and appears to be slightly more effective in lower dimensions ($d=4$) than in higher dimensions ($d=8$).
+One reason for this is that the POSD structure is more easily inferred in lower dimensions from a small pilot sample, which then allows for a tighter data-based error bound.
 
@@
 \end{subfigure}
-\caption{Adaptive sample size $n^*$ as a function of absolute error $\text{ERR}$, with points colored by absolute error tolerance $\epsilon$.}
+\caption{Adaptive sample size $n^*$ as a function of error ratio $\|f - \hat{f}\|_{\infty}/\epsilon$, with points colored by the absolute error tolerance level $\epsilon$.}
 \label{fig:four}

### 2019-02-17 DingHickKritzMakRICAMChap.tex
Updates from Overleaf

@@
 \newcommand{\up}{\textup{up}}
+\newcommand{\inc}{\textup{in}}
+\newcommand{\out}{\textup{out}}
 \newcommand{\E}{\textup{e}}
@@
 Adaptive algorithms infer the necessary computational effort based on the function data sampled.
-Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is not convex.
+Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is non-convex.
 We construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
@@
 We show our algorithms to be essentially optimal.
-We derive conditions under which the problem is tractable.
+We derive conditions under which the problem is tractable, i.e., the information cost of constructing the approximate solution does not increase exponentially with the dimension of the input function domain.
 In the remainder of this section we define the problem and essential notation.
@@
 	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f) \\
-    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , & \tu_{k}(x) & := \begin{cases} 1, & k =0 ,\\
-	x, & k=1,\\
-	2x \tu_{k-1}(x)-\tu_{k-2}(x), & k = 2, 3, \ldots.
+    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , 
+    \qquad \tu_{k_\ell}(x) & := \begin{cases} 1, & k_\ell =0 ,\\
+	x, & k_\ell=1,\\
+	2x \tu_{k_\ell-1}(x)-\tu_{k_\ell-2}(x), & k_\ell = 2, 3, \ldots.
 	\end{cases}
 	\end{align*}
-If one can observe the series coefficients, then $f$ can be approximated by a finite sum.  However, one should have some notion of which terms in the infinite series for $f$ are more important.  Let 
+The function $f$ may be well approximated by a finite sum, however, this requires knowing which terms in the infinite series for $f$ are more important.  Let 
 \begin{equation*}
-    \lambda_\bsk := \prod_{\ell =1}^d \frac{1}{\max(1,k^r_\ell)}, \qquad \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}.
+    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\ell =1}^d \frac{1}{\max(1,k^r_\ell)}, \quad r > 0.
 \end{equation*}
-By this definition, an input function with modest sized norm must have series coefficients that decay quickly enough as the degree of the polynomial increases.
-The assumed decay is quicker for larger $r$, and this assumed decay governs the assumed smoothness of the input functions.
+This definition implies that an input function with modest sized norm must have series coefficients that decay quickly enough as the degree of the polynomial increases.
+This assumed decay governs the assumed smoothness of the input functions and is quicker for larger $r$.
 
@@
 
-If one has a fixed data budget, $n$, then choosing approximation $\APP(f,n)$ is appropriate.
-However, often one has an error tolerance, $\varepsilon$, for which one desires an algorithm, $\ALG(f,\varepsilon)$, which satisfies
+If one has a fixed data budget, $n$, then $\APP(f,n)$ is the correct answer.
+However, often one has an error tolerance, $\varepsilon$, for which one desires an algorithm, $\ALG(f,\varepsilon)$, that satisfies
 \begin{equation*}
@@
 \end{equation*}
-Such an algorithm must have a rule of choosing the correct $n$---depending on $f$ and $\varepsilon$---so that $\ALG(f,\varepsilon) = \APP(f,n)$.
-Choosing such a rule, choosing a set $\calC$ of input functions for which the rule is valid,  characterizing the information cost of $\ALG$, and determining whether $\ALG$ has optimal information cost, and understanding the dependence of this cost on the the number of input variables, $d$, as well as the error tolerance, $\varepsilon$, are all objectives of this chapter.
+Such an algorithm must have a rule for choosing $n$---depending on $f$ and $\varepsilon$---so that $\ALG(f,\varepsilon) = \APP(f,n)$.
+The objectives of this chapter are to construct such a rule, choose a set $\calC$ of input functions for which the rule is valid,  characterize the information cost of $\ALG$, determine whether $\ALG$ has optimal information cost, and understand the dependence of this cost on the the number of input variables, $d$, as well as the error tolerance, $\varepsilon$.
 
@@
 \end{gather}
-Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$.
+Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, and $\mathbb{K}$ is a countable index set.
 These bases are defined to match the solution operator:
 \begin{equation} \label{DHKM:basis_relate}
-    \SOL(u_{\bsk}) = v_{\bsk} \qquad \forall \bsk \in \mathbb{K},
-\end{equation}
-where $\mathbb{K}$ is a general index set.
-The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.
-The larger $\lambda_{\bsk}$ is, the more important $\hf(\bsk)$ is.
+    \SOL(u_{\bsk}) = v_{\bsk} \qquad \forall \bsk \in \mathbb{K}.
+\end{equation}
+The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.  The larger $\lambda_{\bsk}$ is, the more important $\hf(\bsk)$ is.
 
 Although this problem formulation is quite general in some aspects, condition \eqref{DHKM:basis_relate} is somewhat restrictive.
-In theory, the choice of basis can be made via the singular value decomposition, but in practice, if the norms of $\calF$ and $\calG$ are typical, the bases satisfying \eqref{DHKM:basis_relate} may be difficult to identify explicitly.
+In theory, the choice of basis can be made via the singular value decomposition, but in practice, if the norms of $\calF$ and $\calG$ are specified without reference to their respective bases, it may be difficult to identify bases satisfying \eqref{DHKM:basis_relate}.
 
@@
     \end{multline}
-
-\PeterNote{Please excuse me for asking stupid questions all the time, but I was wondering: if $\rho'=\infty$, how would the formula for the $\hf (\bsk)$ in (7) look like?
-We would have $\infty$ in the exponents.}
-\FredNote{How does it look now?}
 Equality \eqref{DHKM:SOL_tight_ineq} illustrates how inequality \eqref{DHKM:SOL_ineq} may be made tight.
@@
 
-%\hspace{\parindent} 
 Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
@@
 \end{equation}
-The $\lambda_{\bsk}$ define the smoothness of the input space and are assumed to have a known order:
-\begin{equation} \label{DHKM:lambda_order}
-    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots >0.
-\end{equation}
+We assume throughout that this norm is finite, namely,
+\begin{equation} \label{DHKM:SOLNormFinite}
+    \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \mathbb{K}}} < \infty.
+\end{equation}
+The $\lambda_{\bsk}$ are assumed to have a known order as was specified in \eqref{DHKM:lambda_order}.
 We assume that all $\lambda_{\bsk_i}$ are positive to avoid the trivial case where the problem can be solved by knowing a finite number of series coefficients.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{An Approximation and an Algorithm}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 An optimal approximation  based on $n$ series coefficients of the input function can be defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
@@
 \end{equation}
+From the argument leading to \eqref{DHKM:SOL_A} it follows that 
+\begin{equation} \label{DHKM:APP_Err_Coef}
+    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
+\end{equation}
+An upper bound on the approximation error follows from Lemma \ref{DHKM:Key_Lem}:
+\begin{equation} \label{DHKM:Refined_APP_err}
+    \norm[\calG]{\SOL(f) - \APP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
+    \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
+\end{equation}
+This leads to the following theorem.
 
@@
 \begin{proof}
-The proof of \eqref{DHKM:APP_errorBd} follows from an argument similar to that used to derive 
-\eqref{DHKM:SOLNorm}.  The optimality of $\APP$ follows by bounding the error of an arbitrary approximation, $\APP'$ applied to functions that mimic the zero function.
+The proof of \eqref{DHKM:APP_errorBd} follows immediately from \eqref{DHKM:Refined_APP_err} and  Lemma \ref{DHKM:Key_Lem}.
+The optimality of $\APP$ follows by bounding the error of an arbitrary approximation, $\APP'$, applied to functions that mimic the zero function.
 
@@
 This completes the proof.
-\end{proof}
-
-\hspace{\parindent} The decay rate of the approximation error in \eqref{DHKM:APP_errorBd} depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
-This decay may be algebraic or exponential and will determine the complexity of the problem as a function of the error tolerance.
+\end{proof} \
 
@@
 
-The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our case series coefficients---required by $\ALG(f,\varepsilon)$.
+The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our case, series coefficients---required by $\ALG(f,\varepsilon)$.
 For adaptive algorithms this cost varies with the input function $f$.
-We also define the information cost of the algorithm in general, recognizing that it will tend to depend on $\norm[\calF]{f}$
+We also define the information cost of the algorithm in general, recognizing that it will tend to depend on $\norm[\calF]{f}$:
 \begin{equation*}
@@
 Thus, Algorithm \ref{DHKM:BallAlg} is essentially optimal. For $R'=R \ (\omega = 1)$, we have optimality.
-\end{proof}
-
-\hspace{\parindent} This theorem illustrates how an essentially optimal algorithm for solving a problem for a ball of input functions, $\calC = \calB_R$, can be non-adaptive.
+\end{proof} \
+
+The decay rate of the approximation error in \eqref{DHKM:APP_errorBd} depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
+This decay may be algebraic or exponential and will determine the complexity of the problem as a function of the error tolerance.
+
+This theorem illustrates how an essentially optimal algorithm for solving a problem for a ball of input functions, $\calC = \calB_R$, can be non-adaptive.
 However, as alluded to above, we claim that it is impractical to know a priori which ball your input function lies in.
@@
 	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \} \\
-	& = \min \left\{ n \in \N_0: \prod_{\ell =1}^d \frac{1}{\max(1,k^r_{n+1,\ell})} \le \frac{\varepsilon}{R} \right\} 
+	& = \min \left\{ n \in \N_0: \prod_{\ell =1}^d \frac{1}{\max(1,k^r_{{ n+1}_\ell})} \le \frac{\varepsilon}{R} \right\} 
 	% & \lambda_{n+1} = \frac{1}{\lceil (n+1)/2 \rceil^r}.
@@
 The error of $\APP(f,n)$ given in Theorem \ref{DHKM:APP_optimality_thm} can be refined by noting that the error only depends on the series coefficients numbered $n+1$ and more.  Specifically, 
-\begin{equation} \label{DHKM:Refined_APP_err}
-    \norm[\calG]{\SOL(f) - \APP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
-    \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
-\end{equation}
+\eqref{DHKM:Refined_APP_err} \FredNote{Note to self:  FIX}
 Moreover, by the definitions of the $\calF$-norm and $\calC$,
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tracking the Decay Rate of the Series Coefficients \FredNote{of the Input Function}}
+\section{Tracking the Decay Rate of the Series Coefficients of the Input Function}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 It simply bounds $\norm[\calF]{f}$ based on a pilot sample.
-The algorithm presented in this section does track the rate of decay of the $\hf(\bsk_i)$ and terminate sooner if the $\hf(\bsk_i)$ decay more quickly.
+The algorithm presented in this section tracks the rate of decay of the $\hf(\bsk_i)$ and terminates sooner if the $\hf(\bsk_i)$ decay more quickly.
 
@@
 This sequence may increase geometrically or algebraically.
-Define the sets of wavenumbers analogously to \eqref{DHKM:KOnedef}.
+Define the sets of wavenumbers analogously to \eqref{DHKM:KOnedef},
 \begin{equation}
@@
     = \calO \left( \left [ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
-    & = \calO \left(  \E^{-j r_{\Delta} s} \right)
+    & = \calO \left(  \E^{-j r_{\Delta} s} \right).
 \end{align*}
@@
 %\label{compbdB}
-j^\ddagger & = \max \left \{ j \in \bbN :  b^{j+1} \Lambda_{j+1}    >
+j^\ddagger & = \max \left \{ j \in \bbN :  b^{j+1} \Lambda_{j+1}    > \varepsilon\,
  \frac{2a}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
@@
 \end{theorem}
+\PeterNote{added $\varepsilon$ in the right hand side of the bound in $j^\ddagger$}
 
@@
 \nonumber
-&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{S(f_-) - \ALG'(f_1,\varepsilon)}  \bigr] \\
+&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{\SOL(f_-) - \ALG'(f_1,\varepsilon)}  \bigr] \\
 \nonumber
@@
 \end{equation*}
+\PeterNote{I first thought this assumption is very strict but it seems it is not (e.g. it is okay if the $\lambda_{\bsk_i}$ decay like $i^{-2}$). However, looking at the proof below, can we weaken it 
+to $b^j \Lambda_j \ge b^{j+1}\Lambda_{j+1}$?}
+\FredNote{Yes, we probably can.  Let's leave it for now and return to it after the rest of the proof is in place.  I think that we want to bound 
+$\norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}$ in \eqref{DHKM:TractConejdagger} in terms of $\Lambda_{j+1}$ so we may need to keep a stronger decay than you suggest.}
+
 We also assume that the ratio of the largest to smallest $\lambda_{\bsk}$ in a group is bounded above:
@@
 
-Suppose that $n = \abs{\calJ} = \COST(\ALG',f_{\pm},\varepsilon) \le n_l$.
-Then by the above third condition, there exists an $l^*$ where $\normabs{\tcalK} \ge S_2 \abs{\calK}$.
+Suppose that $n = \abs{\calJ} = \COST(\ALG',f_{\pm},\varepsilon) \le n_l$.  Then by the above third condition, there exists an $l^* \le l+1$ where $\normabs{\tcalK_{l^*}} \ge S_2 \abs{\calK_{l^*}}$.
+
 This implies a lower bound on $\tLambda_{l^*}$.
-Let $m = n_{l^*} - n_{l^*-1}$, $m_{\inc} = \lceil S_2 m \rceil$, and $m_{\out} = m - m_{\inc}$
+Let $m = n_{l^*} - n_{l^*-1}$ denote the cardinality of $\calK_{l^*}$, which is the number of terms in the sum defining $\Lambda_{l^*}$.
+Then, $m_{\inc} = \lceil S_2 m \rceil$ is lower bound on the cardinality of $\tcalK_{l^*}$, and $m_{\out} = m - m_{\inc}$ is an upper bound on the cardinality of in $\calK_{l^*} \setminus \tcalK_{l^*}$.
+Then
+
 \begin{align*}
@@
 \end{align}
-Therefore, if this inequality is violated for any $l$, we must have $n>n_l$}
+Therefore, if this inequality is violated for any $l$, we must have $n>n_l$.}
 
@@
 
-\FredNote{Peter suggeted Jensen's inequality.  But I could not figure out how to apply that.
+\FredNote{Peter suggested Jensen's inequality.  But I could not figure out how to apply that.
 }
@@
 %%%%%%%%%%%%
-
-\iffalse
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Tracking the Decay Rate of the Series Coefficients \FredNote{of the Solution}}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-From the argument leading to \eqref{DHKM:SOL_A} it follows that 
-\begin{equation} \label{DHKM:APP_Err_Coef}
-    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
-\end{equation}
-The faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
-Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
-It simply bounds $\norm[\calF]{f}$ based on a pilot sample.
-The algorithm presented in this section does track the rate of decay of the $\hf(\bsk_i)$ and terminate sooner if the $\hf(\bsk_i)$ decay more quickly.
-
-Let $(n_j)_{j\ge 0}$ be a strictly increasing sequence of non-negative integers.
-This sequence may increase geometrically or algebraically.
-Define the sets of wavenumbers analogously to \eqref{DHKM:KOnedef}.
-\begin{equation}
-    \calK_0 : = \{\bsk_1, \ldots, \bsk_{n_0} \}, \qquad \calK_j := \{\bsk_{n_{j-1}+1}, \ldots, \bsk_{n_j}\} \quad \text{for } j \in \N.
-\end{equation}For any $f \in \calF$, define the partial sums of powers of series coefficients:
-\begin{equation} \label{DHKM:SigmaDef}
-\sigma_j (f):=\norm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \in \calK_j}} \qquad \text{for } j \in \N.
-\end{equation}
-For this section, we define the cone of input functions, $\calC$, by
-\begin{equation} \label{DHKM:TrackConeDef}
-  \calC : =\left\{f\in\calF \colon \sigma_{j+r} (f)\le ab^r \sigma_j (f)\ \forall j,r\in\NN\right\}.
-\end{equation}
-Here, $a$ and $b$ are positive reals with $b< 1 < a$.
-The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
-Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
-However, we expect their partial sums to decay steadily.
-The series coefficients for  wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\calC$ and may be have erratically.
-If $n_0 = 0$, then $\calK_0$ is empty.
-
-If $f$ belongs to the $\calC$ defined in \eqref{DHKM:TrackConeDef}, then
-
-\PeterNote{Fred, in our last discussion we talked about the problem in Section 2 being ``easier" than that in Section 3.
-Intuitively, I agree; but how do we make this precise?
-It does not seem obvious to me.}
-
-From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, one can now derive a data-driven error bound 
-\begin{align}
-\nonumber
-\norm[\calG]{\SOL(f)-\APP(f,n_j)} &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty} 
-= \norm[\tau]{\bigl(\sigma_l(f) \bigr)_{l = j+1}^\infty} \\
-\nonumber 
-& = \norm[\tau]{ \bigl(\sigma_{j+r}(f)\bigr)_{r=1}^{\infty}} \\
-\nonumber
-&\le \norm[\tau]{ \bigl(ab^r\sigma_{j}(f)\bigr)_{r=1}^{\infty}} \\
-& = \displaystyle \frac{ab  \sigma_{j}(f)}{(1 - b^\tau)^{1/\tau}} \quad \forall f \in \calC, \ j \in \bbN.
- \label{DHKM:algoineq}
-\end{align}
-This upper bound depends only on the function data and the parameters defining $\calC$.
-The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ as $j \to \infty$.
-Moreover, the error of $\APP(f,n_j)$ is asymptotically no worse than $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Adaptive Algorithm and Its
- Computational Cost}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\calC$ defined in \eqref{DHKM:TrackConeDef}.
-The following theorem establishes its viability and computational cost.
-
-\begin{algorithm}
-	\caption{Adaptive ALG for a Cone of Input Functions Tracking the Series Coefficient Decay Rate \label{DHKM:TrackConeAlg}}
-	\begin{algorithmic}
-	\PARAM a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0},$ where $j \in \N$ starts from 1; an inflation factor, $a$; the general decay rate, $b$; $\APP$ satisfying \eqref{DHKM:APP_Err_Coef}
-		\INPUT a black-box function, $f$; an absolute error tolerance,
-		$\varepsilon>0$
-
-\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:TrackConeDef}
-
-\State Let $j \leftarrow 0$
-\Repeat
-
-\State Let $j \leftarrow j + 1$
-
-\State Compute $\sigma_{j}(f)$ as defined in \eqref{DHKM:SigmaDef}
-
-\Until $\sigma_{j}(f) \le \varepsilon (1 - b^\tau)^{1/\tau}/ab$
-
-\RETURN $\ALG(f,\varepsilon) = \APP(f,n_{j})$
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}\label{DHKM:TractConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC)$ for $\calC$ defined in \eqref{DHKM:TrackConeDef}.
-The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
-\begin{equation} \label{DHKM:EqTractConejstar}
-j^* = \min\left \{ j \in \bbN : \sigma_{j}(f) \le \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{ab}   \right\}.
-\end{equation}
-Moreover, $\COST(\ALG,\calC,\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
-\begin{equation} \label{DHKM:TractConejdagger}
-j^\dagger = \min \left \{j \in \bbN :  \norm[\rho]{\left(\frac{b^{1-j}}{a \Lambda_1}, \ldots, \frac{b^{-1}}{a \Lambda_{j-1}}, \frac{1}{ \Lambda_{j}} \right) } \ge \frac{Ra b}{\varepsilon (1 - b^\tau)^{1/\tau}}  \right\},
-\end{equation}
-where
-\begin{equation}
-    \label{DHKM:LambdaDef}
- \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
-\end{equation}
-\end{theorem}
-
-\begin{proof}
-This algorithm terminates for some $j = j^*$ because $\sigma_j(f) \le ab^{j-1} \sigma_{1}(f) \to 0$ as $j \to \infty$.
-The value of $j^*$ in \eqref{DHKM:EqTractConejstar} follows directly from the error criterion.
-The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
-
-For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
-To derive an upper bound on $\COST(\ALG,\calC,\varepsilon,R)$ we first note a key inequality involving the $\sigma_j(f)$ for all $f \in \calF$ and norms of subsequences of the $\lambda_{\bsk_i}$ for all $j \ge 1$.
-This inequality follows directly from H\"older's inequality:
-\begin{equation}\label{DHKM:SigmaInEq}
- \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_j}} \ge 
- \frac{ \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_j}}} {
-  \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}}
- = \frac{\sigma_j(f) }{\Lambda_j}.
-\end{equation}
-
-For any $f \in  \calC \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
-\begin{align*}
-R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
-\ge \norm[\rho]{\left(\norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_j}} \right)_{j=1}^{j^\dagger}}
-\\
-& \ge \norm[\rho]{\left(\frac{\sigma_j(f)}{\Lambda_{j}} \right)_{j=1}^{j^\dagger}}  
-\qquad \text{by \eqref{DHKM:SigmaInEq} }\\
-& \ge \norm[\rho]{\left(\frac{b^{1-j^\dagger}\sigma_{j^\dagger}(f)}{a \Lambda_1}, \ldots, \frac{b^{-1}\sigma_{j^\dagger}(f)}{a \Lambda_{j^\dagger-1}}, \frac{\sigma_{j^\dagger}(f)}{ \Lambda_{j^\dagger}} \right) } \quad \text{by the definition of } \calC \text{ in \eqref{DHKM:TrackConeDef}}\\
-& = \sigma_{j^\dagger}(f)\norm[\rho]{\left(\frac{b^{1-j^\dagger}}{a \Lambda_1}, \ldots, \frac{b^{-1}}{a \Lambda_{j^\dagger-1}}, \frac{1}{ \Lambda_{j^\dagger}} \right) } \\
-& \ge \sigma_{j^\dagger}(f)\,\frac{Ra b }{\varepsilon (1 - b^\tau)^{1/\tau}}\qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}}
-\end{align*}
-From this last inequality, it follows that $j^\dagger \ge j^*$.
-\end{proof}
-
-\FredNote{Pity, I do not see our cost upper bounds reflecting different rates of decay of the series coefficients.  Perhaps a remark here is in order.}
-
-\PeterNote{Added a remark that may be useful for tractability results:}
-\begin{remark}
-A loose bound on $j^\dagger$ can be obtained in the following way. 
-%\begin{itemize}
-%    \item[(a)] For any $j<j^* \le j^\dagger$ we have, by \eqref{DHKM:SigmaInEq}
-%    \begin{align*}
-%        R &\ge \norm[\calF]{f}\ge\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=n_{j-1}+1}^{n_j}}\ge \frac{\sigma_j(f) }{\Lambda_j}> \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{ab}\, \frac{1}{\Lambda_j}.
-%    \end{align*}
-%    Hence, an upper bound on $j^\dagger$ is the first $j$ violating this inequality,
-%    \begin{align}\label{DHKM:jdaggerbound1}
-%        j^\dagger \le \min\left \{ j \in \bbN \colon \Lambda_j \le \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{abR} \right\}.
-%    \end{align}
-%    \item[(b)] A slightly looser bound can be obtained 
-%    by the following observation.
-
-    For
-    $j<j^* \le j^\dagger$ we have, again by \eqref{DHKM:SigmaInEq}
-    \begin{align*}
-        R &\ge\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=n_{j-1}+1}^{n_j}}\ge \frac{\sigma_j(f) }{\Lambda_j}> \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{ab}\, \frac{1}{\norm[\rho']{\left(\lambda_{\bsk_i} \right)_{i=n_{j-1}+1}^{\infty}}}.
-    \end{align*}
-    Hence, an upper bound on $j^\dagger$ is the first $j$ violating this inequality,
-    \begin{align}\label{DHKM:jdaggerbound2}
-        j^\dagger \le \min\left \{ j \in \bbN \colon \norm[\rho']{\left(\lambda_{\bsk_i} \right)_{i=n_{j-1}+1}^{\infty}} \le \frac{\varepsilon (1 - b^\tau)^{1/\tau}}{abR} \right\}.
-    \end{align}
-%\end{itemize}
-\end{remark}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Essential Optimality of the Algorithm and Tractability}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The following theorem establishes a lower bound on the complexity of our problem for input functions in $\calC$. To obtain a result that can be compared with the cost of our algorithm, we assume that 
-\begin{equation} \label{DHKM:lambdaRatio}
-S = \sup_{l \in \bbN} \frac{\Lambda_l}{\lambda_{\bsk_{n_l}}} < \infty.
-\end{equation} The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TractConeCompCost} is essentially no worse than this lower bound.
-
-\begin{theorem} \label{DHKM:TractConeLowBdComp}
-A lower bound on the complexity of the linear problem is
-\begin{align*}
- %\label{compbdA}
-&\COMP(\calA(\calC),\varepsilon,R) \ge n_{j^\ddagger}, 
-\intertext{where}
-%\label{compbdB}
-j^\ddagger & = \max \left \{ j \in \bbN : \left[\frac{(a+1)^{\rho}  }{(a-1)^\rho} + 1\right] \sum_{l=0}^j \frac{b^{\rho(l-j)}}{\lambda_{\bsk_{n_l}}^\rho}   <
-\frac{R^\rho}{\varepsilon^\rho}
-\right \}.
-\end{align*}
-\end{theorem}
-
-\begin{proof}
-\FredNote{Fred working on the part below}
-
-\FredNote{Now trying a proof technique more aligned with \cite{DinHic20a}.}
-
-As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
-We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC \cap \calB_{R}$, which yield the same approximate solution but different true solutions.
-This leads to a lower bound on $\COMP(\calA(\calC),\varepsilon,R)$.
-
-Let $j$ be the positive integer satisfying 
-\[
-n_{j-1} \le \COMP(\calA(\calC),\varepsilon,\rho) < n_j.
-\]  
-The first test function $f_1 \in \calC$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
-\begin{align}
-\nonumber
-f_1 &= f_{11} + \cdots + f_{1j}, \qquad
-\hf_{1l}(\bsk) := \begin{cases}
-\displaystyle
-\frac{c_1 b^{l-j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_l^{\rho'/\rho+1}},  & \bsk \in \calK_l,
-\\
-0, & \bsk \notin \calK_l,
-\end{cases}
-\\
-\nonumber
-c_1 &:=  \frac{R(a+1)}{2a} \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_j} \biggr)_{l=1}^j }^{-1}.
-\end{align}
-It can be verified that $f_1$ lies in both $\calB_{R}$ and $\calC$.  Note that 
-\begin{align}
-\nonumber
-\norm[\calF]{f_{1l}} &= \norm[\rho]{\biggl(\frac{\hf_{1l}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_l}} 
-= \frac{c_1 b^{l-j}}{\Lambda_l} \qquad l \in \N,\\
-\nonumber
-\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \norm[\calF]{f_{1l}} \bigr)_{l=1}^{j} } 
-=  c_1 \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^{j} } = \frac{R(a+1)}{2a} \le R,
-\end{align}
-so $f_1 \in \calB_R$.  Also,
-\begin{align}
-\nonumber
-\sigma_l(f_1) &= \begin{cases}
-c_1 b^{l-j}, & l=1, \ldots, j, \\
-0, & l=j+1, j+2, \ldots,
-\end{cases}
-\\
-\nonumber
-\sigma_{l+r}(f_1) &= 
-\begin{cases}
-c_1 b^{l+r - j}, & l=1, \ldots, \max(0,j-r), \\
-0, & l = \max(0,j-r)+1, \max(0,j-r) +2, \ldots, 
-\end{cases}
-\\
-\nonumber 
-& \le b^r \sigma_l(f_1), \qquad l,r \in \N,
-\end{align}
-so $f_1$ also lies in the cone $\calC$.
-
-Let $u$ be a linear combination of $u_1, \cdots, u_{n_j}$, expressed as
-\[
-u =  \sum_{k=0}^{j}\frac{b^{k-j}u^{(k)}}{\lambda_{n_k}},
-\]
-where $u^{(0)}$ is a linear combination of $u_{1}, \ldots, u_{n_0}$, and each $u^{(k)}$ is a linear combination of $u_{n_{k-1}+1}, \ldots, u_{n_k}$, for $k =1, \ldots, j$.
-We constrain $u$ to satisfy:
-\begin{equation}\label{uConstraint}
-L_1(u) = \cdots = L_n(u) = 0, \qquad \langle u,f \rangle_{\calF} = 0, \qquad 
-\max_{0\le k\le j} \DHJRbignorm[\calF]{u^{(k)}} = 1.
-\end{equation}
-Since $u$ is a linear combination of $n_j >n+1$ basis functions, these constraints can be satisfied.
-
-Let the other two test functions be constructed in terms of $u$ as 
-\begin{align}
-\nonumber
-f_\pm & := f \pm \eta u, \qquad \eta : =  \frac {(a-1)c}{(a+1)R}, \\
-\nonumber
-\DHJRnorm[\calF]{f_\pm}^2 & \le \DHJRnorm[\calF]{f}^2 + \DHJRnorm[\calF]{\eta u }^2 \qquad \text{by \eqref{uConstraint}} \\
-& \nonumber 
-\le \sum_{k=1}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}} \left(c^2+ \eta^2 \DHJRbignorm[\calF]{u^{(k)}}^2\right) + \eta^2 \DHJRbignorm[\calF]{u^{(0)}}^2 \frac{b^{-2j}}{\lambda_{n_0}^2}\\
-\nonumber
-& \le  \left(c^2+ \eta^2 \right) \sum_{k=0}^j \frac{ b^{2(k-j)}}{\lambda^2_{n_{k}}}  \qquad \text{by \eqref{uConstraint}}\\
-& \nonumber 
-\le \rho^2,
-\end{align} 
-so $f_{\pm} \in \calB_{\rho}$.  By design, $A^*(f_\pm,\varepsilon) = A^*(f,\varepsilon)$, which will be used below.
-
-\FredNote{The approach below does not seem to work, but I do not want to erase it. I will try another approach above.}
-
-As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
-We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC \cap \calB_{R}$, which yield the same approximate solution but different true solutions.
-This leads to a lower bound on $\COMP(\calA(\calC),\varepsilon,R)$.
-
-The first test function $f_1 \in \calC$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
-\begin{align}
-\nonumber
-f_1 &= f_{11} + f_{12} +  \cdots, \qquad
-\hf_{1j}(\bsk) := \begin{cases}
-\displaystyle
-\frac{c_1 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_j^{\rho'/\rho+1}},  & \bsk \in \calK_j,
-\\
-0, & \bsk \notin \calK_j,
-\end{cases}
-\\
-\nonumber
-c_1 &:=  \frac{R(a+1)}{2a} \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_j} \biggr)_{j \in \N} }^{-1}.
-\end{align}
-It can be verified that the test function lies both in $\calB_{R}$ and in $\calC$:
-\begin{align}
-\nonumber
-\norm[\calF]{f_{1j}} &= \norm[\rho]{\biggl(\frac{\hf_1(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
-= \frac{c_1 b^j}{\Lambda_j} \qquad j \in \N,\\
-\nonumber
-\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \norm[\calF]{f_{1j}} \bigr)_{j \in \N} } 
-=  c_1 \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_l} \biggr)_{j \in \N} } = \frac{R(a+1)}{2a} \le R,
-\\
-\nonumber
-\sigma_j(f_1) &= \sigma_j(f_{1j}) = 
-c_1 b^{j}, \qquad j \in \N, 
-\\
-\nonumber
-\sigma_{j+r}(f_1) &= 
-b^{r} \sigma_j(f_1) \le a b^r \sigma_j(f_1), \qquad j,r \in \N.
-\end{align}
-
-Now suppose that $\ALG' \in \calA(\calC)$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$, where the cardinality of $\calJ$ is $n$.
-Let $\tcalK_j = \calK_j \setminus \calJ$ for all positive integer $j$.
-Construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
-\begin{align}
-\nonumber
-f_2 &= f_{21} + f_{22} +  \cdots, \qquad \hf_{2j}(\bsk_i) := \begin{cases}
-\displaystyle
-\frac{c_2 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\tLambda_j^{\rho'/\rho} \Lambda_j},  
-& \bsk \in \tcalK_j,
-\\
-0, & \text{otherwise},
-\end{cases}
-\\
-\nonumber
-c_2 &:= \frac{R(a-1)}{2a} \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_j} \biggr)_{j \in \N}}^{-1}, \qquad
-\tLambda_j := \norm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \tcalK_j}} \le \Lambda_j, \\
-\norm[\calF]{f_2} &= \norm[\rho]{\bigl( \norm[\calF]{f_{2j}} \bigr)_{j \in \N} } 
-\le  c_2 \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_l} \biggr)_{j \in \N} } \le R, \\
-\sigma_j(f_2) &= \sigma_j(f_{2j}) = 
-\frac{c_2 b^{j}\tLambda_j}{\Lambda_j} , \qquad j \in \N.
-\end{align}
-Furthermore, define $f_{\pm} = f_1 \pm f_2$.
-It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\calC$:
-\begin{align}
-\nonumber
-\norm[\calF]{f_\pm} &\le \norm[\calF]{f_1} + \norm[\calF]{f_2} \le (c_1 + c_2) \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_l} \biggr)_{j \in \N} } = R,
-\\
-\nonumber
-\sigma_j(f_\pm) & \ge \sigma_j(f_1) - \sigma_j(f_2) \ge
-\left(c_1 - c_2 \right) b^{j},  \qquad j \in \N,
-\\
-\nonumber
-\sigma_{j+r}(f_\pm) & \le \sigma_{j+r}(f_1) + \sigma_{j+r}(f_2) = 
-(c_1+c_2) b^{j+r}
-\\
-\nonumber
-& = (c_1 - c_2) a b^{j+r}
-\le a b^r \sigma_j(f_\pm),  \qquad j \in \N.
-\end{align}
-
-Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG'(f_1,\varepsilon) = \ALG'(f_\pm,\varepsilon)$.
-But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
-In particular,
-\begin{align*}
-\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - \ALG'(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - \ALG'(f_-,\varepsilon)} \bigr\} \\
-&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{S(f_-) - \ALG'(f_1,\varepsilon)}  \bigr] \\
-&\qquad \qquad \text{since } \ALG'(f_\pm,\varepsilon) = \ALG'(f_1,\varepsilon) \\
-&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
-&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $\SOL$ is linear}\\
-&= \norm[\calG]{\SOL(f_2)} = \norm[\tau]{\bigl( \sigma_j(f_2) \bigr)_{j \in N}} \\
-& = 
-\frac{R(a-1)}{2a} \norm[\tau]{ \biggl(\frac{b^{j}\tLambda_j}{\Lambda_j} \biggr)_{j \in \N}} \norm[\rho]{ \biggl(\frac{b^{j}}{\Lambda_j} \biggr)_{j \in \N}}^{-1}.
-\end{align*}
-
-%%%%%%%%%%%%%% 
-\FredNote{Still playing around}
-
-Now suppose that $\ALG' \in \calA(\calC)$ is an optimal algorithm, i.e., \[\COST(\ALG,\calC,\varepsilon,R) =  \COMP(\calA(\calC),\varepsilon,R)\]
-for all $\varepsilon, R > 0$.
-For our particular input $f_1$ defined above, suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$, where the cardinality of $\calJ$ is $n$ with
-\[
-n + 1\le \COMP(\calA(\calC),\varepsilon,R) +1 < n_j.
-\]  
-Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
-\begin{align}
-\nonumber
-\hf_2(\bsk_i) &:= \begin{cases}
-\displaystyle
-\frac{c_2 b^{l-j} \lambda_{\bsk_i}^{\rho'/\rho+1}}{\Lambda_l^{\rho'/\rho+1}},  & \bsk_i \notin \calJ \text{ and } i =  1, \ldots, n_l, \ l = 1, \ldots, j,
-\\
-0, & \text{otherwise},
-\end{cases}
-\\
-\nonumber
-c_2 &:= \frac{R(1-a)}{2} \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^j }^{-1}, \\
-\norm[\calF]{f_2} &= \norm[\rho]{\Biggl( \norm[\rho]{\biggl(\frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \biggr)_{i = n_{l-1} + 1}^{n_l}} \Biggr)_{j=1}^l } 
-\le  c_2 \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^j } \le R, \\
-\sigma_l(f_2) & \le \begin{cases}
-\displaystyle
-c_2 b^{l-j}, & l =1, \ldots, j, \\
-0, & \text{otherwise},
-\end{cases}
-\end{align}
-Furthermore, define $f_{\pm} = f_1 \pm f_2$.
-It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\calC$:
-\begin{align}
-\nonumber
-\norm[\calF]{f_\pm} &\le \norm[\calF]{f_1} + \norm[\calF]{f_2} \le (c_1 + c_2) \norm[\rho]{ \biggl(\frac{b^{l-j}}{\Lambda_l} \biggr)_{l=1}^j } = R,
-\\
-\nonumber
-\sigma_l(f_\pm) & \ge \sigma_l(f_1) - \sigma_2(f_2) = \begin{cases}
-\displaystyle
-(c_1 - c_2) b^{l-j}, & l =1, \ldots, j, \\
-0, & \text{otherwise},
-\end{cases}
-\\
-\nonumber
-\sigma_{l+r}(f_\pm) & \le \sigma_{l+r}(f_1) + \sigma_{l+r}(f_2) = \begin{cases}
-\displaystyle
-(c_1+c_2) b^{l+r-j}, & l =1, \ldots, j-r, \\
-0, & \text{otherwise},
-\end{cases}
-\\
-\nonumber
-& = \begin{cases}
-\displaystyle
-(c_1 - c_2) a b^{l+r-j}, & l =1, \ldots, j-r, \\
-0, & \text{otherwise},
-\end{cases}
-\\
-\nonumber
-& \le b^r \sigma_l(f_\pm), \qquad l =1, \ldots .
-\end{align}
-
-Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG(f_1,\varepsilon) = \ALG(f_\pm,\varepsilon)$.
-But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
-In particular,
-\begin{align*}
-\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - \ALG(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - \ALG(f_-,\varepsilon)} \bigr\} \\
-&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{S(f_-) - \ALG(f_1,\varepsilon)}  \bigr] \\
-&\qquad \qquad \text{since } \ALG(f_\pm,\varepsilon) = \ALG(f_1,\varepsilon) \\
-&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
-&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $\SOL$ is linear}\\
-&= \norm[\calG]{\SOL(f_2)}.
-\end{align*}
-\FredNote{Fred has got to here on 1/18/19}
-
-======
-
-Now suppose that $ALG \in \calA(\calC)$ is an optimal algorithm, i.e., \[\COST(ALG,\calC,\varepsilon,R) =  \textup{comp}(\calA(\calC),\varepsilon,R)\]
-for all $\varepsilon, R > 0$.  For our particular input $f$ defined above, suppose that $ALG(f,\varepsilon)$ samples $L_1(f), \ldots, L_n(f)$ where 
-\[
-n + 1\le \textup{comp}(\calA(\calC),\varepsilon,R) +1 < n_j.
-\]
-
-Let $u$ be a linear combination of $u_1,\ldots, u_{n_j}$, expressed as
-\[
-u =  \sum_{l=0}^{j}\frac{b^{l-j}u^{(l)}}{\lambda_{\bsk_{n_l}}},
-\]
-where $u^{(0)}$ is a linear combination of $u_{1}, \ldots, u_{n_0}$, and each $u^{(l)}$ is a linear combination of $u_{n_{l-1}+1}, \ldots, u_{n_l}$, for $l =1, \ldots, j$.
-We constrain $u$ to satisfy:
-\begin{equation}\label{DHKM:uConstraint}
-L_1(u) = \cdots = L_n(u) = 0, \qquad \langle u,f \rangle_{\calF} = 0, \qquad 
-\max_{0\le l\le j} \norm[\calF]{u^{(l)}} = 1.
-\end{equation}
-
-Since $u$ is a linear combination of $n_j >n+1$ basis functions, these constraints can be satisfied.
-
-Let the other two test functions be constructed in terms of $u$ as 
-\begin{align}
-\nonumber
-f_\pm & := f \pm \eta u, \qquad \eta : =  \frac {(a-1)c}{(a+1)S}, \\
-\nonumber
-\norm[\calF]{f_\pm}^\rho & \le \norm[\calF]{f}^\rho + \norm[\calF]{\eta u }^\rho \qquad \text{by \eqref{DHKM:uConstraint}} \\
-& \nonumber 
-\le \sum_{l=1}^j \frac{ b^{\rho(l-j)}}{\lambda^\rho_{\bsk_{n_l}}} \left(c^\rho+ \eta^\rho \norm[\calF]{u^{(l)}}^\rho\right) + \eta^\rho \norm[\calF]{u^{(0)}}^\rho \frac{b^{-\rho j}}{\lambda_{\bsk_{n_0}}^\rho}\\
-\nonumber
-& \le  \left(c^\rho+ \eta^\rho \right) \sum_{l=0}^j \frac{ b^{\rho(k-j)}}{\lambda^\rho_{\bsk_{n_l}}}  \qquad \text{by \eqref{DHKM:uConstraint}}\\
-& \nonumber 
-\le R^{\rho},
-\end{align} 
-so $f_{\pm} \in \calB_{B}$.  By design, $ALG(f_\pm,\varepsilon) = ALG(f,\varepsilon)$, which will be used below.
-
-Now we must check that $f_\pm \in \calC$. From the definition in \eqref{DHKM:SigmaDef} it follows that for $l = 1, \ldots, j$ and $r \ge 1$,
-\begin{equation*}
-\sigma_l(f_\pm)  \begin{cases} 
-\displaystyle
-\le \sigma_l(f) + \sigma_l(\eta u)\le 
-c b^{l-j} + \eta b^{l-j}\frac{\Lambda_l}{\lambda_{\bsk_{n_l}}}\norm[\calF]{u^{(l)} }
-\le b^{l-j}\left(c+ \eta S \right)
-\\[1ex]
-\displaystyle
-\ge \sigma_l(f) - \sigma_l(\eta u)\ge 
-c b^{l-j} - \eta b^{l-j} \frac{\Lambda_l}{\lambda_{\bsk_{n_l}}}\norm[\calF]{u^{(k)}  }
-\ge b^{l-j}\left(c-\eta S\right) , 
-\end{cases}
-\end{equation*}
-Therefore, 
-\begin{equation*}
-\sigma_{l+r}(f_\pm)
-\le b^{l+r-j}(c+\eta S) = ab^r b^{l-j}\frac{2c}{a+1}
-=ab^r b^{l-j}\left(c-\eta S \right) \le a b^r \sigma_{l}(f_\pm),
-\end{equation*}
-which establishes that $f_\pm \in \calC$.
-
-Although two test functions $f_\pm$ yield the same approximate solution, they have different true solutions.  In particular,
-\begin{align*}
-\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - ALG(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - ALG(f_-,\varepsilon)} \bigr\} \\
-&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - ALG(f,\varepsilon)} + \norm[\calG]{S(f_-) - ALG(f,\varepsilon)}  \bigr] \\
-&\qquad \qquad \text{since } ALG(f_\pm,\varepsilon) = ALG(f,\varepsilon) \\
-&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
-&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $S$ is linear}\\
-&= \eta \norm[\calG]{\SOL(u)}.
-\end{align*}
-Thus, we have
-\begin{align*}
-\varepsilon^2  & \ge \eta^2 \norm[\calG]{\SOL(u)}^2= 
-\eta^2 \sum_{l=0}^{j} \norm[\calG]{\SOL(u^{(l)})}^2  \frac{b^{2(l-j)}}{\lambda_{n_k}^2}\\
-& \ge \eta^2 
-\sum_{k=0}^{j} \norm[\calF]{u^{(k)}}^2 
-b^{2(k-j)}\\
-& \ge  \eta^2 b^{2(k^{*}-j)} \qquad \text{ where } k^* = \argmax_{0 \le k \le j} \norm[\calF]{u^{(k)}} \\
-& \ge \eta^2 = \frac{(a-1)^2c^2}{(a+1)^2} \\
-&
-=\frac{(a-1)^2 \rho^2}{(a+1)^2R^2}\left[\left(1+\frac{(a-1)^2}{(a+1)^{2} R^2 }\right)\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} \\
-& =  \rho^2 \left[\left\{\frac{(a+1)^{2} R^2 }{(a-1)^2} + 1\right\}\sum_{k=0}^j \frac{b^{2(k-j)}}{\lambda_{n_{k}}^2}\right]^{-1} 
-\end{align*}
-
-This lower bound must be satisfied by $j$ to be consistent with the assumption $\textup{comp}(\calA(\calC),\varepsilon,R) \le n_j - 1$.
-Thus, for any $j$ violating this inequality it follows that $\textup{comp}(\calA(\calC),\varepsilon,R) \ge n_j$.
-This implication provides a lower bound on $\textup{comp}(\calA(\calC),\varepsilon,R)$.
-\end{proof}
-
-\PeterNote{Working on tractability below
-
-\medskip
-
-We again would like to study tractability.
-To this end, we assume in the following that $n_0$ is some given positive integer, and that $(n_j)_{j\ge 1}=(g^j n_0)_{j\ge 1}$ for some real $g>1$.
-Like in Section~\ref{DHKM:SecPilotTract}, we distinguish whether $\rho'=\infty$ or not.
-
-\paragraph*{CASE 1: $\rho'=\infty$:}
-
-\begin{theorem} \label{DHKM:thmtract3}
-Using the same notation as above, strong polynomial, polynomial, and weak tractability for the case $\rho'=\infty$ hold under exactly the 
-same conditions as in Theorem \ref{DHKM:thmtract1}.
-\end{theorem}
-\begin{proof}
-Our starting point is \eqref{DHKM:jdaggerbound2}.
- We define, for $d\in\NN$ and $\varepsilon\in (0,1)$,
- \[
-  n^*(\varepsilon,d):=\min\left\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le \varepsilon\right\}\asymp
-  \min\left\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le \frac{\varepsilon (1-b^\tau)^{1/\tau}}{abR}\right\}.
- \]
- To show the sufficient condition for strong polynomial tractability, let now $\widetilde{\varepsilon}:=\sqrt{\varepsilon}$ such that $n^*(\varepsilon,d)=\min\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le (\widetilde{\varepsilon})^2 \}$.
-From \cite{NovWoz08a}, we know that if \eqref{DHKM:eq:condspt} holds for some real $\eta>0$ and some $i_0\in\NN$, then
- \[
-  n^* (\varepsilon,d) \le C\,((\widetilde{\varepsilon})^{-1})^{2\eta}= C\, (\varepsilon^{-1})^\eta 
- \]
- with some $C>0$.
-
- Suppose that $n^*(\varepsilon,d) /n_0 < 1/g$. Then, $n^*(\varepsilon,d) < n_0$, and it follows by the monotonicity of the $\lambda_{d,\bsk_i}$ that
- $\lambda_{d,\bsk_{n_0+1}}\le \lambda_{d,\bsk_{n^*(\varepsilon,d)+1}}$, and hence $j^\dagger =1$, which yields $n_{j^\dagger}=g\,n_0$.
-
- If $n^*(\varepsilon,d) /n_0 \ge 1/g$, let $j_0\in \NN$ be maximal such that $g^{j_0-2}\le n^*(\varepsilon,d) /n_0$. This means that 
- \[
- n^*(\varepsilon,d)  < g^{j_0-1} n_0=n_{j_0-1},
- \] 
- and hence, again by the monotonicity of the $\lambda_{d,i}$, that 
- \[
- \lambda_{d,\bsk_{n_{j_0-1}+1}}\le \lambda_{d,\bsk_{n^*(\varepsilon,d)+1}}.
- \] 
- Consequently, 
- \[
- n_{j^\dagger} \le n_{j_0}=g^{j_0} n_0 \le 
- n^*(\varepsilon,d)\, g^2\,n_0.
- \]
- Hence, in any case we obtain
- \[
-  \textup{comp} (\calA (\calC_d),\varepsilon,R) \le n_{j^\dagger} \le 
-  C\, (\varepsilon^{-1})^\eta g^2 n_0+ gn_0.
- \]
-
- This implies strong polynomial tractability, as claimed, and hence the sufficiency of Condition \eqref{DHKM:eq:condspt} for 
- strong polynomial tractability is shown. Note that this also shows the upper bound of $\eta$ for the exponent 
- of strong polynomial tractability. The proof of the sufficient condition for polynomial tractability is done analogously
-
- Regarding the proof of the sufficient condition for weak tractability, let $\widetilde{\varepsilon}$ and $n^*(\varepsilon,d)$ be defined as above. Let
- $\widetilde{n}^*(\widetilde{\varepsilon},d)=\min\{n\in\NN\colon \lambda_{d,\bsk_{n+1}}\le (\widetilde{\varepsilon})^2 \}$. 
- Note, as above, that we have $n^*(\varepsilon,d)=\widetilde{n}^*(\widetilde{\varepsilon},d)$. This yields
- $$   
-\lim_{d+\varepsilon^{-1}\to\infty}\   
-\frac{\log\, n^*(\varepsilon,d)}   
-{d +(\varepsilon^{-1}) }\,=\, \lim_{d+\varepsilon^{-1}\to\infty}\   
-\frac{\log\, \widetilde{n}^*(\widetilde{\varepsilon},d)}   
-{d +(\widetilde{\varepsilon}^{-1})^{2}}  
-$$ 
-As shown in \cite{WerWoz17}, we have 
-\[
- \lim_{d+\varepsilon^{-1}\to\infty}\   
-\frac{\log\, \widetilde{n}^*(\widetilde{\varepsilon},d)}   
-{d +(\widetilde{\varepsilon}^{-1})^{2}}=0
-\]
-if \eqref{DHKM:eq:condwt} holds.
-
-As above, we see that $n_{j^\dagger}\le n^*(\varepsilon,d)\, g^2 n_0+g\,n_0$, hence 
-$$ 
-  0\le\lim_{d+\varepsilon^{-1}\to\infty}\   
- \frac{\log\, n_{j^\dagger}}   
-{d +(\varepsilon^{-1}) }
- \, \le\, k\,
-\lim_{d+\varepsilon^{-1}\to\infty}\   
-\frac{\log\, n^*(\varepsilon,d)}   
-{d+(\varepsilon^{-1})}\,=\, k\,\lim_{d+\varepsilon^{-1}\to\infty}\   
-\frac{\log\, \widetilde{n}^*(\widetilde{\varepsilon},d)}   
-{d +(\widetilde{\varepsilon}^{-1})^{2}}  
-$$
-for some positive constant $k$.
-Hence, we conclude that we have weak tractability if \eqref{DHKM:eq:condwt} holds. 
-\end{proof}
-}
-
-%%%%%%%%%%%%
-\subsection{Numerical Example}
-%%%%%%%%%%%%
-
-\fi
 

### 2019-02-17 DingHickKritzMakRICAMChap.tex
Closed loop on proofs in Section 3

@@
 \DeclareMathOperator{\ERR}{ERR}
+\DeclareMathOperator{\card}{card}
 \newcommand{\dataN}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^n}
@@
 Note that while the cost depends on $\norm[\calF]{f}$, $\ALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
-It is common for $\COST(\ALG, \calC, \varepsilon,R)$ to be bounded by a power of $\varepsilon^{-1}$.
+It is common for $\COST(\ALG, \calC, \varepsilon,R)$ to be $\calO(\varepsilon^{-p})$, or perhaps asymptotically $c\log(1 + \varepsilon^{-1})$.
 
@@
 \begin{theorem}
-The non-adaptive Algorithm \ref{DHKM:BallAlg} is essentially optimal for our problem when the set of input functions is $\calC = \calB_R$, specifically
+The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$, which is given by
+\[
+\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}.
+\]
+This algorithm is essentially optimal for the set of input functions $\calB_R$, namely,
 \[
@@
 
-\begin{proof}  Fix positive $\varepsilon$, $R$ and $R' \le R$.  Let $\omega = R'/R$.  From the definition of the non-adaptive Algorithm  \ref{DHKM:BallAlg}, 
+\begin{proof}  Fix positive $\varepsilon$, $R$ and $R' \le R$.  Let $\omega = R'/R$.  The information cost of non-adaptive Algorithm  \ref{DHKM:BallAlg} follows from its definition.  Let 
 \[
-\COST(\ALG, \calB_R, \varepsilon,R') = n^*(\varepsilon,R) = \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}.
+n^*(\varepsilon,R) : = \COST(\ALG, \calB_R, \varepsilon,R').
 \]
@@
 
-The decay rate of the approximation error in \eqref{DHKM:APP_errorBd} depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
-This decay may be algebraic or exponential and will determine the complexity of the problem as a function of the error tolerance.
+For Algorithm \ref{DHKM:BallAlg}, the information cost, $\COST(\ALG,\calB_R,\varepsilon, R)$, depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
+This decay may be algebraic or exponential and also determines the problem compleixty, $\COMP(\calA(\calB_R),\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tractability}\label{DHKM:secTractability}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Besides understanding the dependence of the computational complexity on $\varepsilon$, we also want to understand how this quantity depends on the dimension of the domain of the input function.
+Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
+Let the bases and $\lambda_{\bsk}$ be of product form:
+\begin{gather*}
+    u_{\bsk} = \tu_{1,k_1} \cdots \tu_{d,k_d}, \qquad  v_{\bsk} = \tv_{1,k_1} \cdots \tv_{d,k_d}, \\ 
+    \lambda_{\bsk} = \tlambda_{1,k_1} \cdots \tlambda_{d,k_d}, \quad \forall \bsk = (k_1, \ldots, k_d) \in \bbK = \tbbK^d.
+\end{gather*}
+The cone of functions for which our algorithms succeed, $\calC_d$, will also depend on the dimension.
+Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
+
+\bigskip
+
+We would like to study how $\COMP(\calA(\calC_d), \varepsilon,R)$ 
+depends on the dimension $d$ and the error threshold $\varepsilon$.
+This is described by defining various notions of tractability.
+Roughly speaking, the different tractability notions correspond to different
+ways of how the complexity $\COMP(\calA(\calC_d), \varepsilon,R)$ depends on $d$ and $\varepsilon$. Since 
+the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
+We define the following notions of tractability (for further information on tractability we refer to the trilogy 
+\cite{NovWoz08a}, \cite{NovWoz10a}, \cite{NovWoz12a}).
+
+\begin{itemize}   
+\item We say that the adaptive approximation problem is strongly polynomially tractable
+if and only if there are non-negative $C$ and $p$ such that   
+for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
+$$   
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,\varepsilon^{-p}.
+$$   
+The infimum of $p$ satisfying the bound above is denoted by $p^*$   
+and is called the exponent of strong polynomial tractability.    
+\newline \qquad
+
+\item    
+We say that the problem is polynomially tractable
+if and only if there are non-negative $C,p$, and $q$ such that   
+for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
+$$   
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,   
+\varepsilon^{-p}.   
+$$   
+\vskip 0.5pc
+
+\item   
+We say that the problem is weakly tractable iff    
+$$   
+\lim_{d+\varepsilon^{-1}\to\infty}\   
+\frac{\log\, \COMP(\calA(\calC_d), \varepsilon,R)}   
+{d+\varepsilon}\,=\,0.   
+$$    
+\end{itemize}
+
+Necessary and sufficient conditions on these tractability notions will be studied 
+for different types of algorithms in Sections \ref{DHKM:SecPilotTract} and \ldots .
+
+\subsection{The Illustrative Example Revisited}
+\FredNote{This part needs some work.}
 Consider the example in Section 1.1, we obtain
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tractability}\label{DHKM:secTractability}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Besides understanding the dependence of the computational complexity on $\varepsilon$, we also want to understand how this quantity depends on the dimension of the domain of the input function.
-Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
-Let the bases and $\lambda_{\bsk}$ be of product form:
-\begin{gather*}
-    u_{\bsk} = \tu_{1,k_1} \cdots \tu_{d,k_d}, \qquad  v_{\bsk} = \tv_{1,k_1} \cdots \tv_{d,k_d}, \\ 
-    \lambda_{\bsk} = \tlambda_{1,k_1} \cdots \tlambda_{d,k_d}, \quad \forall \bsk = (k_1, \ldots, k_d) \in \bbK = \tbbK^d.
-\end{gather*}
-The cone of functions for which our algorithms succeed, $\calC_d$, will also depend on the dimension.
-Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
-
-\bigskip
-
-We would like to study how $\COMP(\calA(\calC_d), \varepsilon,R)$ 
-depends on the dimension $d$ and the error threshold $\varepsilon$.
-This is described by defining various notions of tractability.
-Roughly speaking, the different tractability notions correspond to different
-ways of how the complexity $\COMP(\calA(\calC_d), \varepsilon,R)$ depends on $d$ and $\varepsilon$. Since 
-the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
-We define the following notions of tractability (for further information on tractability we refer to the trilogy 
-\cite{NovWoz08a}, \cite{NovWoz10a}, \cite{NovWoz12a}).
-
-\begin{itemize}   
-\item We say that the adaptive approximation problem is strongly polynomially tractable
-if and only if there are non-negative $C$ and $p$ such that   
-for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
-$$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,\varepsilon^{-p}.
-$$   
-The infimum of $p$ satisfying the bound above is denoted by $p^*$   
-and is called the exponent of strong polynomial tractability.    
-\newline \qquad
-
-\item    
-We say that the problem is polynomially tractable
-if and only if there are non-negative $C,p$, and $q$ such that   
-for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
-$$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,   
-\varepsilon^{-p}.   
-$$   
-\vskip 0.5pc
-
-\item   
-We say that the problem is weakly tractable iff    
-$$   
-\lim_{d+\varepsilon^{-1}\to\infty}\   
-\frac{\log\, \COMP(\calA(\calC_d), \varepsilon,R)}   
-{d+\varepsilon}\,=\,0.   
-$$    
-\end{itemize}
-
-Necessary and sufficient conditions on these tractability notions will be studied 
-for different types of algorithms in Sections \ref{DHKM:SecPilotTract} and \ldots .
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The premise of an adaptive algorithm is that the finite information we observe about the input function 
-tells us something about what is not observed about the input function.  Let $n_1$ denote the number of pilot samples to be observed, based on the wave numbers
+tells us something about what is not observed about the input function.  Let $n_1$ denote the number of pilot observations, based on the wave numbers
 \begin{equation} \label{DHKM:KOnedef}
@@
 
-The error of $\APP(f,n)$ given in Theorem \ref{DHKM:APP_optimality_thm} can be refined by noting that the error only depends on the series coefficients numbered $n+1$ and more.  Specifically, 
-\eqref{DHKM:Refined_APP_err} \FredNote{Note to self:  FIX}
-Moreover, by the definitions of the $\calF$-norm and $\calC$,
+Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.
+The definition of $\calC$ allows us to bound these as follows:
 \begin{align*}
@@
 \end{align*}
-This inequality together with \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
+This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
 \begin{subequations} \label{DHKM:pilot_errbd}
@@
 This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
-For this $\calC$ defined in \eqref{DHKM:pilot_cone}, Algorithm \ref{DHKM:PilotConeAlg} is successful:
+This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\calC$ defined in \eqref{DHKM:pilot_cone}:
 
@@
 This satisfies definition \eqref{DHKM:EssentialOpt}.  
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Necessary Condition for the Input Function to Lie in the Cone}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\end{proof} \
+
 We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC$, but we may derive necessary conditions for $f$ to lie in $\calC$.
@@
 
-From the argument leading to \eqref{DHKM:SOL_A} it follows that 
-\begin{equation} \label{DHKM:APP_Err_Coef}
-    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
-\end{equation}
-The faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
+From error bound \eqref{DHKM:APP_Err_Coef} it follows that the faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
 Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
@@
 \end{equation}
+Thus, $\norm[\calF]{f} = \norm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N_0}}$.
+
 For this section, we define the cone of input functions, $\calC$, by
@@
 \end{equation}
+From \eqref{DHKM:SOLNorm} and \eqref{DHKM:SOLNormFinite} it follows that norm of the solution operator is 
+\begin{equation} \label{DHKM:NormLambdaFinite}
+    \norm[\calF \to \calG]{\SOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty
+\end{equation}
 
@@
 \FredNote{$\widetilde{a}$ or $A$, not sure which is best.  Let's wait until we have finished the rest. }
-From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, one can now derive a data-driven error bound for all $f \in \calC$ and $j \in \bbN$:
+From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \calC$ and $j \in \bbN$:
 \begin{align}
@@
 Moreover, the error bound for $\APP(f,n_j)$ depends on $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
-
-\FredNote{\emph{This part added to illustrate the sequence of $n_j$}
 
@@
     = \calO \left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
-    & = \calO \left(  2^{-j(r_\Delta-1/\rho)} \right)
+    & = \calO \left(  2^{-j(r_\Delta-1/\rho)} \right).
 \end{align*}
@@
 Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\calC$ to include such functions.
-Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
+Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
 
@@
 Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} s}$ causes the cone $\calC$ to include such functions.
-Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
-}
+Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Adaptive Algorithm and Its
- Computational Cost}
+\subsection{The Adaptive Algorithm and Its Computational Cost} \label{DHKM:SecAdapAlgTrackDecay}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+To establish the essential optimality of Algorithm \ref{DHKM:TrackConeAlg} requires some additional assumptions on the sequences $(n_j)_{j \in \N_0}$ and $\bigl(\sigma_j(f) \bigr)_{j \in \N_0}$.
+Recall from \eqref{DHKM:NormLambdaFinite} that $\bigl(\sigma_j(f) \bigr)_{j \in \N_0}$ has a finite $\rho'$ norm.
+We require that the $\Lambda_j$ cannot increase too quickly with $j$:
+\begin{equation} \label{DHKM:LambdaDecayCond}
+     \Lambda_{j+r} \le b^r \Lambda_j  \quad \forall j,r \in \N_0.
+\end{equation}
+We also assume that the ratio of the largest to smallest $\lambda_{\bsk}$ in a group is bounded above:
+\begin{equation} \label{DHKM:MinMaxCond}
+    \sup_{j \in \N} \frac{\lambda_{\bsk_{n_{j-1}+1}}}{\lambda_{\bsk_{n_{j}}}} \le S_1 < \infty.
+\end{equation}
+For the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.
+Finally, let $\card(\cdot)$ denote the cardinality of a set.
+We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le n_{j+1}$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
+\begin{equation} \label{DHKM:PropCond}
+     \inf_{j \in \N} \ \min_{\calJ \subset \bbK \, : \, \card(\calJ) \le n_j} \ \max_{0 \le l \le j+1} \frac{\card(\calK_l \setminus \calJ)}{\card(\calK_l)} \ge S_2 > 0.
+\end{equation}
+Again, for the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.
+
 The following theorem establishes a lower bound on the complexity of our problem for input functions in $\calC$.
@@
 %\label{compbdB}
-j^\ddagger & = \max \left \{ j \in \bbN :  b^{j+1} \Lambda_{j+1}    > \varepsilon\,
- \frac{2a}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
+j^\ddagger & = \max \left \{ j \in \bbN :  b^{j+1} \Lambda_{j+1}    > 
+ \frac{2a\varepsilon}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
 \right \}.
@@
 \end{theorem}
-\PeterNote{added $\varepsilon$ in the right hand side of the bound in $j^\ddagger$}
 
@@
 This leads to a lower bound on $\COMP(\calA(\calC),\varepsilon,R)$.
+The proof is provided for $\rho' < \infty$.
+The proof for $\rho' = \infty$ is similar.
 
@@
 \displaystyle
-\frac{c_1 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_j^{\rho'/\rho}},  & \bsk \in \calK_j,
-\\
-0, & \bsk \notin \calK_j,
+\frac{c_1 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_l^{\rho'/\rho}},  & \bsk \in \calK_l,
+\\
+0, & \bsk \notin \calK_l,
 \end{cases}
@@
 \nonumber
-\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
-= c_1 b^j, \qquad j \in \N_0,\\
-\nonumber
-\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \sigma_j(f) \bigr)_{j \in \N_0} } 
+\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1l}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_l}} 
+= c_1 b^l, \qquad l \in \N_0,\\
+\nonumber
+\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \sigma_l(f) \bigr)_{l \in \N_0} } 
 =  \frac{c_1}{(1 - b^\rho)^{1/\rho}} = \frac{R(a+1)}{2a} \le R,
@@
 
-\FredNote{The next step is to derive a lower bound on the $\tau$-norm term above, which we can use to show optimality.
-
-I am writing this part informally to explain to the rest of you my thinking.  We need to tighten the writing later.
-
-We make some further assumptions, which I think are reasonable, but can be checked later.  First we assert that the $\Lambda_j$ decrease montonically:
-\begin{equation*}
-     \Lambda_1 \ge \Lambda_2 \ge \cdots.
-\end{equation*}
-\PeterNote{I first thought this assumption is very strict but it seems it is not (e.g. it is okay if the $\lambda_{\bsk_i}$ decay like $i^{-2}$). However, looking at the proof below, can we weaken it 
-to $b^j \Lambda_j \ge b^{j+1}\Lambda_{j+1}$?}
-\FredNote{Yes, we probably can.  Let's leave it for now and return to it after the rest of the proof is in place.  I think that we want to bound 
-$\norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}$ in \eqref{DHKM:TractConejdagger} in terms of $\Lambda_{j+1}$ so we may need to keep a stronger decay than you suggest.}
-
-We also assume that the ratio of the largest to smallest $\lambda_{\bsk}$ in a group is bounded above:
-\begin{equation*}
-    \sup_{j \in \N} \frac{\lambda_{\bsk_{n_{j-1}+1}}}{\lambda_{\bsk_{n_{j}}}} \le S_1 < \infty.
-\end{equation*}
-Finally, we assume that if $n\le n_j$, then at least some of the $\tcalK_l$ must have a cardinality that is not too small a proportion of the cardinality of the  $\calK_l$, i.e. 
-\begin{equation*}
-    \max_{1 \le l \le j+1} \frac{\bigabs{\tcalK_l}}{\abs{\calK_l}} \ge S_2 > 0.
-\end{equation*}
-
-Suppose that $n = \abs{\calJ} = \COST(\ALG',f_{\pm},\varepsilon) \le n_l$.  Then by the above third condition, there exists an $l^* \le l+1$ where $\normabs{\tcalK_{l^*}} \ge S_2 \abs{\calK_{l^*}}$.
-
-This implies a lower bound on $\tLambda_{l^*}$.
-Let $m = n_{l^*} - n_{l^*-1}$ denote the cardinality of $\calK_{l^*}$, which is the number of terms in the sum defining $\Lambda_{l^*}$.
-Then, $m_{\inc} = \lceil S_2 m \rceil$ is lower bound on the cardinality of $\tcalK_{l^*}$, and $m_{\out} = m - m_{\inc}$ is an upper bound on the cardinality of in $\calK_{l^*} \setminus \tcalK_{l^*}$.
-Then
+Suppose that $n = \abs{\calJ} = \COST(\ALG',f_{\pm},\varepsilon) \le n_{j^{\star}}$.
+Then by condition \eqref{DHKM:PropCond}, there exists an $l^\star \le j^\star+1$ where $\card(\tcalK_{l^\star}) \ge S_2 \card(\calK_{l^\star})$.
+This implies a lower bound on $\tLambda_{l^\star}$.
+Let $m = n_{l^\star} - n_{l^\star-1} = \card(\calK_{l^\star})$.
+Then, $m_{\inc} = \lceil S_2 m \rceil \ge S_2 m$ is lower bound on  $\card(\tcalK_{l^\star})$, and $m_{\out} = m - m_{\inc} \le (1 - S_2) m$ is an upper bound on $\card(\calK_{l^\star} \setminus \tcalK_{l^\star})$.
+Moreover,
 
 \begin{align*}
-    \Lambda_{l^*}^\rho & = \sum_{i \in \calK_{l^*}} \lambda_{\bsk_i}^{\rho} =  \tLambda_{l^*}^\rho + \sum_{i \in \calK_{l^*} \setminus \tcalK_{l^*}} \lambda_{\bsk_i}^{\rho}
-    \\
-    &\le  \tLambda_{l^*}^\rho + m_{\out} \lambda_{\bsk_{n_{l^* -1}+1}}^\rho \\
-    &\le  \tLambda_{l^*}^\rho + m_{\out} S_1^\rho \lambda_{\bsk_{n_{l^*}}}^\rho \\
-    & \le \tLambda_{l^*}^\rho + \frac{m_{\out}}{m_{\inc}} S_1^\rho \tLambda_{l^*}^\rho \\
-    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] \tLambda_{l^*}^\rho
+    \Lambda_{l^\star}^\rho & = \sum_{i \in \calK_{l^\star}} \lambda_{\bsk_i}^{\rho} =  \tLambda_{l^\star}^\rho + \sum_{i \in \calK_{l^\star} \setminus \tcalK_{l^\star}} \lambda_{\bsk_i}^{\rho}
+    \\
+    &\le  \tLambda_{l^\star}^\rho + m_{\out} \lambda_{\bsk_{n_{l^\star -1}+1}}^\rho \qquad \text{by the ordering of the } \lambda_{\bsk_i}\\
+    &\le  \tLambda_{l^\star}^\rho + m_{\out} S_1^\rho \lambda_{\bsk_{n_{l^\star}}}^\rho \qquad \text{by \eqref{DHKM:MinMaxCond}}\\
+    & \le \tLambda_{l^\star}^\rho + \frac{m_{\out}}{m_{\inc}} S_1^\rho \tLambda_{l^\star}^\rho \qquad \text{by the definition of } \tLambda_{l^\star}\\
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] \tLambda_{l^\star}^\rho \qquad \text{by the bounds on } m_{\inc} \text{ and } m_{\out} 
+    \\
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] b^{-\rho l^\star} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}^\rho
 \end{align*}
 
-Thus, going back to \eqref{DHKM:eps_LBA} it follows that 
+Returning to \eqref{DHKM:eps_LBA}, the above inequality and condition \eqref{DHKM:LambdaDecayCond} imply that
 \begin{align}
@@
 \varepsilon 
-& \ge \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} b^{l^*} \tLambda_l^* 
-\\
-\nonumber
-& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} b^{l^*} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} \Lambda_{l^*}
-\\
-\nonumber
-& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{l+1} \Lambda_{n_{l+1}}
+& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{l^\star} \Lambda_{l^\star}
+\\
+\nonumber
+& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{j^\star+1} \Lambda_{j^\star+1}.
 \end{align}
-Therefore, if this inequality is violated for any $l$, we must have $n>n_l$.}
-
-\FredNote{The expression above has been corrected.  The hard work is still to bridge the gap.
-
-=====Begining of the gap}
-
-\PeterNote{To see whether the original proof method still works:
-
-\medskip
-
-Let $j_1<j_2$ (i.e., $n_{j_1} < n_{j_2}$), and assume furthermore 
-that $i_1\in \{n_{j_1-1}+1,\ldots,n_{j_1}\}$ and $i_2\in \{n_{j_2-1}+1,\ldots,n_{j_2}\}$. If we could 
-show that
-\begin{multline*}
- \left(\sum_{i=n_{j_1-1}+1}^{n_{j_1}} b^{j_1} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'} +
- \left(\sum_{\substack{i=n_{j_2-1}+1\\ i\neq i_2}}^{n_{j_2}} b^{j_2} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'}\ge\\
-  \left(\sum_{\substack{i=n_{j_1-1}+1\\ i \neq i_1}}^{n_{j_1}} b^{j_1} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'} +
- \left(\sum_{i=n_{j_2-1}+1}^{n_{j_2}} b^{j_2} \lambda_{\bsk_i}^{\rho'}\right)^{\tau/\rho'}
-\end{multline*}
-that should be enough.
-
-Or, more simply: Suppose $v\le 1$, and $a,b,\beta,\alpha$ are positive reals, with $\alpha>\beta$, 
-and $\alpha\le a$, $\beta\le b$. 
-Do we always have
+Therefore, if this inequality is violated for any $j^\star$, we must have $n>n_{j^\star}$.
+\end{proof}
+
+\begin{theorem}
+\label{DHKM:TrackConeAlgOptThm}
+Adaptive Algorithm \ref{DHKM:TrackConeAlg} is essentially optimal for the cone of input functions defined in \eqref{DHKM:TrackConeDef}.
+\end{theorem}
+\begin{proof}
+Let $j^\dagger(\varepsilon)$ be defined as in \ref{DHKM:TractConejdagger}, with the $\varepsilon$ dependence made explicit.  This defintion implies that 
+\begin{align*}
+    b^{j^\dagger(\varepsilon) +1 } \Lambda_{j^\dagger(\varepsilon) +1 } 
+    & \le  \norm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)+r}\Lambda_{j^\dagger(\varepsilon)+r} \bigr)_{r=1}^\infty} 
+    \le  \frac{b\varepsilon}{Ra^2} \left( \frac{1 - b^{j^\dagger(\varepsilon)\rho}}{1 - b^\rho} \right)^{1/\rho} 
+    \\
+    &
+    \le \frac{b\varepsilon}{Ra^2 (1 - b^\rho)^{1/\rho}} \\
+    & =  \frac{2a \omega \varepsilon}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
+    \\
+    & \qquad \qquad \text{where } \omega = \frac{(a-1)b}{2a^3} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho}.
+\end{align*}
+Making the $\varepsilon$ dependence explicit in the definition of $j^\ddagger(\varepsilon)$ in Theorem \ref{DHKM:TractConeLowBdComp} it follows that $j^\dagger(\varepsilon) < j^\ddagger(\omega \varepsilon)$, and so
 \[
- a^v + (b-\beta)^v \ge (a-\alpha)^v + b^v\ ?
+\COST(\ALG,\calC,\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calA(\calC),\omega \varepsilon,R).
 \]
-Can we use the two-dimensional mean value theorem?
-
-Just tried numerically, no it does not work. There are counterexamples.
-}
-
-\FredNote{Peter suggested Jensen's inequality.  But I could not figure out how to apply that.
-}
-
-\FredNote{End of gap ======}
-\PeterNote{I am afraid with Jensen's inequality we will not get the condition we want but a weaker one.
-Another thought: can we multiply the lower bound after the gap with a small quantity (depending on b, $\tau$, $\rho'$) such that the lower bound holds?}
-
-The smallest that this double sum can be is when the set of wavenumbers sampled corresponds to the first $n$, i.e., $\calJ = \{\bsk_1, \ldots, \bsk_n\}$.
-Therefore, for all $j \in \N$ satisfying $n_{j} \ge n$, it follows that
-\begin{align*}
-    \varepsilon & \ge \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \left(\sum_{r=1}^\infty b^{(j+r)\tau}  \, \left(\sum_{i=n_{j+r-1}+1}^{n_{j+r}}  \lambda_{\bsk_i}^{\rho'} \right)^{\tau/\rho'} \right)^{1/\tau} \\
-    & = \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j+r} \Lambda_{j+r} \bigr)_{r \in \N}}.
-\end{align*}
-On the contrary, if $n > n_j$, then the above inequality must be violated \PeterNote{I am not good with such conclusions, but why does $n> n_j$ imply that the inequality must be violated?
-What am I missing?}.
-This implies the stated lower complexity bound.
-
+Thus,  Algorithm \ref{DHKM:TrackConeAlg} is essentially optimal.
 \end{proof}

### 2019-03-20 DingHickKritzMakRICAMChap.tex
polishing

@@
 \newcommand{\tLambda}{\widetilde{\Lambda}}
+\newcommand{\bcalK}{\bar{\calK}}
+\newcommand{\fapp}{f_{\text{app}}}
 %\newcommand{\HickernellFJ}{Hickernell}
@@
   \runningtitle{Adaptive Approximation}
-  \subtitle{...}
-  \abstract{...}
+  %\subtitle{...}
+  \abstract{We study adaptive approximation algorithms for multivariate linear 
+  problems where the input sets are non-convex cones. While it is known that adaptive algorithms perform 
+  essentially no better than non-adaptive algorithms for convex input sets, the 
+  situation may be different for non-convex sets. A typical example
+  considered here is function approximation based on series expansions. Given 
+  an error tolerance, we use series coefficients of the input to construct an 
+  approximate solution such that the error does not exceed this tolerance.
+We study the situation where we can bound the norm of the input based on a pilot sample, and the situation where we keep track of the decay rate of the series coefficients of the input.
+Moreover,
+  we consider situations where it makes sense to infer coordinate and smoothness importance.
+Besides performing an error analysis, we also study the information cost of our algorithms and the computational complexity
+  of our problems, and we identify conditions under which we can avoid a curse of 
+  dimensionality.}
   %\keywords{...}
@@
 Adaptive algorithms infer the necessary computational effort based on the function data sampled.
-Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is non-convex.
+Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex}.
 We construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
@@
 In the remainder of this section we define the problem and essential notation.
+But first, we present a helpful example.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{An Illustrative Example}
+\subsection{An Illustrative Example}\label{DHKM:secexamp}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$ in this case
+Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$.  In this case,
 	\begin{align*}
-	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f) \\
+	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f), 
+	\qquad \bsk = (k_1, \ldots, k_d),\\
     u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , 
-    \qquad \tu_{k_\ell}(x) & := \begin{cases} 1, & k_\ell =0 ,\\
-	x, & k_\ell=1,\\
-	2x \tu_{k_\ell-1}(x)-\tu_{k_\ell-2}(x), & k_\ell = 2, 3, \ldots.
+    \qquad \tu_{k}(x) := \begin{cases} 1, & k =0 ,\\
+	x, & k=1,\\
+	2x \tu_{k-1}(x)-\tu_{k-2}(x), & k = 2, 3, \ldots.
 	\end{cases}
 	\end{align*}
-The function $f$ may be well approximated by a finite sum, however, this requires knowing which terms in the infinite series for $f$ are more important.  Let 
+Approximating $f$ well by a finite sum requires knowing which terms in the infinite series for $f$ are more important.  Let 
 \begin{equation*}
-    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\ell =1}^d \frac{1}{\max(1,k^r_\ell)}, \quad r > 0.
+    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0,
 \end{equation*}
-This definition implies that an input function with modest sized norm must have series coefficients that decay quickly enough as the degree of the polynomial increases.
-This assumed decay governs the assumed smoothness of the input functions and is quicker for larger $r$.
+where the $w_\ell$ are \emph{coordinate weights}.
+The introduction of coordinate weights expresses the understanding that the $f$ may depend more strongly on some coordinates---those with larger coordinate weights---than others.
+The definition of the norm of $f$ implies that an input function with modest sized norm must have series coefficients that decay quickly enough as the degree of the polynomial increases.
+This decay of the series coefficients corresponds to the smoothness of the input functions.
+Larger $r$ corresponds to greater smoothness.
 
@@
 \end{equation}
-which then implies an ordering of the wavenumbers.  Given this ordering, it is natural to approximate the solution using the first $n$ series coefficients as follows:
-\begin{equation} \label{DHKM:Ex_APP_def}
-   \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \quad \forall n \in \N.
-\end{equation}
+which implies an ordering of the wavenumbers, $\bsk$.  Given this ordering, it is natural to approximate the solution using the first $n$ series coefficients as follows:
+\begin{equation*} %\label{DHKM:Ex_APP_def}
+   \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \qquad \forall n \in \N.
+\end{equation*}
+
+Here, we assume that it is possible to sample the series coefficients of the input function.
+This is a less restrictive assumption than being able to sample any linear functional, but it is more restrictive than only being able to sample function values.
+An important problem for future work is to extend the theory here to the case where the only function data available are function values.
+
 The error of this approximation can be defined as 
@@
 
-If one has a fixed data budget, $n$, then $\APP(f,n)$ is the correct answer.
-However, often one has an error tolerance, $\varepsilon$, for which one desires an algorithm, $\ALG(f,\varepsilon)$, that satisfies
-\begin{equation*}
-    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon.
-\end{equation*}
-Such an algorithm must have a rule for choosing $n$---depending on $f$ and $\varepsilon$---so that $\ALG(f,\varepsilon) = \APP(f,n)$.
-The objectives of this chapter are to construct such a rule, choose a set $\calC$ of input functions for which the rule is valid,  characterize the information cost of $\ALG$, determine whether $\ALG$ has optimal information cost, and understand the dependence of this cost on the the number of input variables, $d$, as well as the error tolerance, $\varepsilon$.
+If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer.  However, our goal is an algorithm, $\ALG(f,\varepsilon)$ that satisfies the error criterion
+\begin{equation} \label{DHKM:err_crit}
+    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon \qquad \forall \varepsilon > 0, \ f \in \calC,
+\end{equation}
+where  $\varepsilon$ is the error tolerance, and $\calC \subset \calF$ is the set of input functions for which $\ALG$ is successful.
+This algorithm contains a rule for choosing $n$---depending on $f$ and $\varepsilon$---so that $\ALG(f,\varepsilon) = \APP(f,n)$.
+The objectives of this chapter are to
+\begin{itemize}
+    \item construct such a rule, 
+    \item choose a set $\calC$ of input functions for which the rule is valid,  
+    \item characterize the information cost of $\ALG$, 
+    \item determine whether $\ALG$ has optimal information cost, and 
+    \item understand the dependence of this cost on the number of input variables, $d$, as well as the error tolerance, $\varepsilon$.
+\end{itemize}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Our general linear problem is defined by a solution operator mapping an input function to an output, $\SOL:\calF \to \calG$.
+Now, we define our problem more generally.
+A solution operator maps the input function to an output, $\SOL:\calF \to \calG$.
 As in the illustrative example above, the Banach spaces of inputs and outputs are defined by series expansions:
-\begin{gather}
+\begin{gather*}
     \calF = \left \{f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad 1 \le \rho \le \infty, \\
     \calG = \left \{g = \sum_{\bsk \in \mathbb{K}} \hg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \hg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad 1 \le \tau \le \rho.
-\end{gather}
-Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, and $\mathbb{K}$ is a countable index set.
+\end{gather*}
+Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, and $\mathbb{K}$ is a countable index set.
 These bases are defined to match the solution operator:
@@
 Although this problem formulation is quite general in some aspects, condition \eqref{DHKM:basis_relate} is somewhat restrictive.
-In theory, the choice of basis can be made via the singular value decomposition, but in practice, if the norms of $\calF$ and $\calG$ are specified without reference to their respective bases, it may be difficult to identify bases satisfying \eqref{DHKM:basis_relate}.
-
-To facilitate our derivations below, we establish the following lemma, which follows from H\"older's inequality:
+In principle, the choice of basis can be made via the singular value decomposition, but in practice, if the norms of $\calF$ and $\calG$ are specified without reference to their respective bases, it may be difficult to identify bases satisfying \eqref{DHKM:basis_relate}.
+
+To facilitate our derivations below, we establish the following lemma based on H\"older's inequality:
 
@@
    \\ 
-    \implies  \ \ \norm[\calF]{f} = R \ \& \ \norm[\calG]{\SOL(f)} = R \Lambda.
+    \implies  \ \ \norm[\calF]{f} = R \ \mbox{and} \ \norm[\calG]{\SOL(f)} = R \Lambda.
     \end{multline}
@@
 \begin{proof}
-We give the proof for $\rho' < \infty$.  The proof for $\rho' = \infty$ follows similiarly. 
+We give the proof for $\rho' < \infty$.  The proof for $\rho' = \infty$ follows similarly. 
 The proof of inequality \eqref{DHKM:SOL_ineq} proceeds by applying H\"older's inequality:  
@@
     \nonumber
-    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau \\
-    \nonumber
-    & = \norm[\calF]{f} \, \Lambda.
+    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \norm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
 \end{align}
@@
 \end{equation}
-The $\lambda_{\bsk}$ are assumed to have a known order as was specified in \eqref{DHKM:lambda_order}.
-We assume that all $\lambda_{\bsk_i}$ are positive to avoid the trivial case where the problem can be solved by knowing a finite number of series coefficients.
+
+As in Section \ref{DHKM:secexamp}, here in the general case the $\lambda_{\bsk}$ are assumed to have a known order as was specified in \eqref{DHKM:lambda_order}.
+Also, we assume that all $\lambda_{\bsk}$ are  positive to avoid the trivial case where $\SOL(f)$ can be expressed exactly as a finite sum.
 
@@
 \end{equation}
-From the argument leading to \eqref{DHKM:SOL_A} it follows that 
+By the argument leading to \eqref{DHKM:SOL_A} it follows that 
 \begin{equation} \label{DHKM:APP_Err_Coef}
@@
  Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.
-Use Lemma \ref{DHKM:Key_Lem} with $\calK = \bbK \setminus \calJ$ to choose $f$ to satisfy the following conditions:
-\begin{gather*}
-    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ \Bignorm[\tau]{\bigl(\hf(\bsk)\bigr)_{\bsk \notin \calJ}}
-    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \notin \calJ}} \,
-    \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.
-\end{gather*}
-Then $\APP'(\pm f,n) = \APP'(0,n)$, and
+Use Lemma \ref{DHKM:Key_Lem} with $\calK = \bbK \setminus \calJ$ to choose $f$ to mimic the zero function, have norm $R$, and have as large a solution as possible, i.e.,
+\begin{gather}
+\nonumber
+    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ 
+    \norm[\calG]{\SOL(f)} =  R \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad  \text{by \eqref{DHKM:SOL_tight_ineq}}.  \label{DHKM:FoolFun}
+\end{gather}
+Then $\APP'(\pm f,n) = \APP'(0,n)$ because $f$ mimics the zero function, and
 \begin{align*}
-\MoveEqLeft{\max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)} =  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)}} \\
+\MoveEqLeft{\sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}} \\
+& \ge \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)} =  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)} \\
 & \ge \frac 12 \left [ \norm[\calG]{\SOL(f) - \APP'(0,n)} 
@@
 & \ge \norm[\calG]{\SOL(f)} 
- = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOL_tight_ineq}}.
+ = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:FoolFun}}.
 \end{align*}
@@
 
-While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion
-\begin{equation} \label{DHKM:err_crit}
-    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon \qquad \forall f \in \calC.
-\end{equation}
+While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion \eqref{DHKM:err_crit}.
 The non-adaptive Algorithm \ref{DHKM:BallAlg} satisfies this error criterion for $\calC  = \calB_R$.
@@
 The key difficulty is that error bound \eqref{DHKM:APP_errorBd} depends on the norm of the input function.
-In contrast, we will construct  error bounds for $\APP(f,n)$ that only depend on function values.
+In contrast, we will construct  error bounds for $\APP(f,n)$ that only depend on function data.
 These will lead to \emph{adaptive} algorithms $\ALG$ satisfying error criterion \eqref{DHKM:err_crit}.
@@
 
-Note that algorithms satisfying \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$.
+Note that algorithms satisfying error criterion \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$.
 Any algorithm must require a finite sample size, even if it is huge.
 Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.
-Thus, algorithms satisfying the error criterion only exist for some strict subset of $\calF$, and choosing that subset well is both an art and a science.
+Thus, algorithms satisfying the error criterion  exist only for some strict subset of $\calF$, and choosing that subset well is both an art and a science.
 
@@
 
-The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our case, series coefficients---required by $\ALG(f,\varepsilon)$.
+The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$.
 For adaptive algorithms this cost varies with the input function $f$.
@@
 These definitions follow the information-based complexity literature \cite{TraWer98, TraWasWoz88}.
-We define an algorithm to be \emph{essentially optimal} if there exists some fixed positive $\omega$ for which
-\begin{equation} \label{DHKM:EssentialOpt}
-    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calA(\calC), \omega \varepsilon,R) \qquad \forall \varepsilon,R > 0.
-\end{equation}
+We define an algorithm to be \emph{essentially optimal} if there exists some fixed positive $\omega$, $\varepsilon_{\max}$, and $R_{\min}$ for which
+\begin{multline} \label{DHKM:EssentialOpt}
+    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calA(\calC), \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+\end{multline}
 If the complexity of the problem is $\calO(\varepsilon^{-p})$, the cost of an essentially optimal algorithm is also $\calO(\varepsilon^{-p})$.
 If the complexity of the problem is asymptotically $c \log(1 + \varepsilon^{-1})$, then  the cost of an essentially optimal algorithm is also asymptotically $c \log(1 + \varepsilon^{-1})$.
-We will show that our adaptive algorithms are essentially optimal.
-
-\begin{theorem}
+We will show that our adaptive algorithms presented in Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}  are essentially optimal.
+
+\begin{theorem}\label{DHKM:thm_cost_non_adapt}
 The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$, which is given by
@@
 This algorithm is essentially optimal for the set of input functions $\calB_R$, namely,
-\[
-\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R), \varepsilon R'/R,R') \qquad \forall \varepsilon > 0, \ 0 < R' \le R.
-\]
+\begin{multline*}
+\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R),\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
+\end{multline*}
+where $\varepsilon_{\max}$ and $R_{\min}$ are arbitrary and fixed, and $\omega = R_{\min}/R$.
 \end{theorem}
 
-\begin{proof}  Fix positive $\varepsilon$, $R$ and $R' \le R$.  Let $\omega = R'/R$.  The information cost of non-adaptive Algorithm  \ref{DHKM:BallAlg} follows from its definition.  Let 
+\begin{proof}  Fix positive $\varepsilon_{\max}$, $R_{\min}$, $R$, and $\omega$ as defined above.
+For $0 < \varepsilon \le \varepsilon_{\max}$ and $R_{\min} \le R' \le R$, the information cost of non-adaptive Algorithm  \ref{DHKM:BallAlg} follows from its definition.
+Let
 \[
@@
 \COST(\ALG, \calB_R, \varepsilon,R') & =  n^*(\varepsilon,R) 
-= n^*(\varepsilon R'/R,R') = n^*(\omega \varepsilon, R')
+= n^*(\varepsilon R'/R,R') \\
+& \le n^*(\omega \varepsilon, R') \qquad \text{since } R'/R \ge \omega
 \\
@@
 \end{align*}
-Thus, Algorithm \ref{DHKM:BallAlg} is essentially optimal. For $R'=R \ (\omega = 1)$, we have optimality.
+Thus, Algorithm \ref{DHKM:BallAlg} is essentially optimal.
 \end{proof} \
@@
 For Algorithm \ref{DHKM:BallAlg}, the information cost, $\COST(\ALG,\calB_R,\varepsilon, R)$, depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
-This decay may be algebraic or exponential and also determines the problem compleixty, $\COMP(\calA(\calB_R),\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
+This decay may be algebraic or exponential and also determines the problem complexity, $\COMP(\calA(\calB_R),\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
 
@@
 \begin{equation*}
-    \sup_{R > 0} \COMP(\calA(\calC),\varepsilon, R) < \infty.
+    \COMP(\calA(\calC),\varepsilon) : = \sup_{R > 0} \COMP(\calA(\calC),\varepsilon, R) < \infty.
 \end{equation*}
@@
 Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
-Let the bases and $\lambda_{\bsk}$ be of product form:
-\begin{gather*}
-    u_{\bsk} = \tu_{1,k_1} \cdots \tu_{d,k_d}, \qquad  v_{\bsk} = \tv_{1,k_1} \cdots \tv_{d,k_d}, \\ 
-    \lambda_{\bsk} = \tlambda_{1,k_1} \cdots \tlambda_{d,k_d}, \quad \forall \bsk = (k_1, \ldots, k_d) \in \bbK = \tbbK^d.
-\end{gather*}
-The cone of functions for which our algorithms succeed, $\calC_d$, will also depend on the dimension.
+The cone of functions for which our algorithms succeed, $\calC_d$, depends on the dimension too.
 Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
@@
 
-We would like to study how $\COMP(\calA(\calC_d), \varepsilon,R)$ 
-depends on the dimension $d$ and the error threshold $\varepsilon$.
-This is described by defining various notions of tractability.
-Roughly speaking, the different tractability notions correspond to different
-ways of how the complexity $\COMP(\calA(\calC_d), \varepsilon,R)$ depends on $d$ and $\varepsilon$. Since 
+Different dependencies of $\COMP(\calA(\calC_d), \varepsilon,R)$ on the dimension $d$ and the error tolerance $\varepsilon$ are formalized as different notions of tractability. Since 
 the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
 We define the following notions of tractability (for further information on tractability we refer to the trilogy 
-\cite{NovWoz08a}, \cite{NovWoz10a}, \cite{NovWoz12a}).
+\cite{NovWoz08a}, \cite{NovWoz10a}, \cite{NovWoz12a}). Note that in contrast to 
+these references we explicitly include the dependence on $R$ in our definitions. This 
+dependence is natural for cones $\calC$ and might be different if $\calC$ is not a cone.
 
@@
 \item We say that the adaptive approximation problem is strongly polynomially tractable
-if and only if there are non-negative $C$ and $p$ such that   
-for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
+if and only if there are non-negative $C$, $p$, $\varepsilon_{\max}$, and $R_{\min}$ such that   
 $$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,\varepsilon^{-p}.
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,R^p\,\varepsilon^{-p} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
 $$   
@@
 We say that the problem is polynomially tractable
-if and only if there are non-negative $C,p$, and $q$ such that   
-for all \ $d\in\NN,\ \varepsilon\in (0,1)$ we have   
+if and only if there are non-negative $C,p$, $q$,  $\varepsilon_{\max}$, and $R_{\min}$ such that   
 $$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,   
-\varepsilon^{-p}.   
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,R^p\,   
+\varepsilon^{-p}\qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).  
 $$   
@@
 $$   
-\lim_{d+\varepsilon^{-1}\to\infty}\   
+\lim_{d+R\,\varepsilon^{-1}\to\infty}\   
 \frac{\log\, \COMP(\calA(\calC_d), \varepsilon,R)}   
-{d+\varepsilon}\,=\,0.   
+{d+R\,\varepsilon^{-1}}\,=\,0.   
 $$    
@@
 Necessary and sufficient conditions on these tractability notions will be studied 
-for different types of algorithms in Sections \ref{DHKM:SecPilotTract} and \ldots .
-
-\subsection{The Illustrative Example Revisited}
-\FredNote{This part needs some work.}
-Consider the example in Section 1.1, we obtain
+for different types of algorithms in Sections \ref{DHKM:SecPilotTract} and \ref{DHKM:SecDecayTract}.
+
+We remark that, for the sake of brevity, we focus here on tractability notions that are summarized as 
+algebraic tractability in the recent literature 
+(see, e.g., \cite{KriWoz19}). Theoretically, one could also study exponential tractability, where 
+one would essentially replace $\varepsilon^{-1}$ 
+by $\log \varepsilon^{-1}$ in the previous tractability notions. A more detailed study of 
+tractability will be done in a future paper.
+
+\subsection{The Illustrative Example Revisited}\label{DHKM:revisexamp}
+The example in Section \ref{DHKM:secexamp} chooses $\rho = \tau = 2$ and $\rho' = \infty$.  Thus, we obtain by Theorem \ref{DHKM:thm_cost_non_adapt}:
 \begin{align*}
 	\textup{COMP}(\calA(\calB_{R}),\varepsilon,R) &= \textup{COST}(ALG,\calB_{R},\varepsilon,R) 
-	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \} \\
-	& = \min \left\{ n \in \N_0: \prod_{\ell =1}^d \frac{1}{\max(1,k^r_{{ n+1}_\ell})} \le \frac{\varepsilon}{R} \right\} 
-	% & \lambda_{n+1} = \frac{1}{\lceil (n+1)/2 \rceil^r}.
+	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \}.
 \end{align*}
-	\YuhanNote{I can't get an explicit bound of n}
-	Here, $\calG=L^2[-1,1]$.
-The larger the non-negative parameter $r$ is, the faster the $\lambda_{\bsk_i}$ tend to 0 as $ i \to 0$, the more exclusive $\calB_R$ is, and the smaller  $\textup{cost}(ALG,\calB_{R},\varepsilon,R)$ is.
-For $r = 0$, $\textup{cost}(ALG,\calB_{R},\varepsilon,R) = \infty$.
+Using the non-increasing ordering of the $\lambda_{\bsk_i}$, we employ a standard technique for bounding the $n+1^\text{st}$ largest $\lambda_{\bsk}$ in terms of the sum of the $1/p^\text{th}$ power of all the $\lambda_{\bsk}$.
+For $0 < p < r$,
+\begin{align*}
+(n+1)\lambda_{\bsk_{n+1}}^{1/p} &\le \sum_{i=1}^{n+1}\lambda_{\bsk_{i}}^{1/p} \le \sum_{\bsk \in \bbN_0^d}\lambda_{\bsk}^{1/p} = \prod_{\ell =1}^d \left[1 + w_\ell^{1/p}\sum_{k = 1}^\infty \frac {1}{k^{r/p}} \right ] \\
+& =  \prod_{\ell =1}^d \left[1 + w_\ell^{1/p}\zeta(r/p)\right ] 
+= \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{1/p}\zeta(r/p) \bigr) \right) \\
+& \le \exp\left(\zeta(r/p) \sum_{\ell = 1}^{\infty} w_\ell^{1/p} \right) \qquad \text{since }\log(1+x) \le x \ \forall x\ge 0.
+\end{align*}
+Hence, substituting the above upper bound on $\lambda_{\bsk_{n+1}}$ into the formula for the complexity of the problem, we obtain an upper bound on the complexity:
+\begin{align*}
+    \MoveEqLeft{\textup{COMP}(\calA(\calB_{R}),\varepsilon,R)} \\
+  &\le\min\left\{ n \in \N_0 : \frac{1}{n+1}\exp\left(\zeta(r/p) \sum_{\ell = 1}^\infty w_\ell^{1/p} \right)  \le \left( \frac{\varepsilon}{R} \right)^{1/p}  \right\} \\
+  &= \left \lceil \left( \frac{R}{\varepsilon} \right)^{1/p}  \exp\left(\zeta(r/p) \sum_{\ell = 1}^{\infty} w_\ell^{1/p} \right) \right \rceil - 1.
+\end{align*}
+
+If the $w_\ell$ decay quickly enough so that $\sum_{\ell = 1}^{\infty} w_\ell^{1/p}$ is finite, we obtain strong polynomial tractability and a complexity that is $\calO \bigl((R/\varepsilon)^{1/p} \bigr)$.
+On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.
 
@@
 \section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
+\label{DHKM:pilot_sec} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The premise of an adaptive algorithm is that the finite information we observe about the input function 
-tells us something about what is not observed about the input function.  Let $n_1$ denote the number of pilot observations, based on the wave numbers
+tells us something about what is not observed about the input function.  Let $n_1$ denote the number of pilot observations, based on the wavenumbers
 \begin{equation} \label{DHKM:KOnedef}
@@
 where the $\bsk_i$ are given by the ordering of the $\lambda_{\bsk}$ in \eqref{DHKM:lambda_order}.
-Let $a$ be some constant inflation factor greater than one.
-The cone of functions whose norm can be bounded well in terms of a pilot sample
+Let $A$ be some constant inflation factor greater than one.
+The cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$,
 is given by
 \begin{equation} \label{DHKM:pilot_cone}
-    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le a \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
+    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
 \end{equation}
@@
     \right]^{1/\rho} \qquad \forall f \in \calF \\
-    &  \le  \left[ a^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
     \right]^{1/\rho} \quad \forall f \in \calC.
@@
     : =  
-    \left[ a^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
+    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
     \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
@@
 	\begin{algorithmic}
-	\PARAM an initial sample size, $n_1 \in \N$; an inflation factor, $a > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
+	\PARAM an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
     = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \varepsilon/[(a^\rho -1)^{1/\rho}R] \right \}.
+    \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
 \end{multline}
-The computational complexity has the lower bound
-\begin{equation} \label{DHKM:PilotConeAlg_comp}
+There exist positive $\varepsilon_{\max}$ and $R_{\min}$ for which the computational complexity has the lower bound
+\begin{multline} \label{DHKM:PilotConeAlg_comp}
         \COMP(\calA(\calC),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le 2\varepsilon/[(1 - 1/a) R] \right \}.
-\end{equation}
-Therefore, Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\calC)$ contains only adaptive algorithms.
+    \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
+    \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+\end{multline}
+Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\calC)$ contains only adaptive algorithms.
 \end{theorem}
@@
      & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
-     (a^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}} \, 
+     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1 }} \, 
      \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
@@
      & \le \min \left \{n \ge n_1 : 
-     (a^\rho -1)^{1/\rho} R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
+     (A^\rho -1)^{1/\rho} R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
     \le \varepsilon \right \},  
 \end{align*}
-since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
+since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
 Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
@@
 
-To prove the lower complexity bound, let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.
-Fix $R$ and $\varepsilon$ arbitrarily.
+To prove the lower complexity bound, choose $\varepsilon_{\max}$ and $R_{\min}$ such that 
+\[
+\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n_1+1}^{\infty}} \,
+    > 2\varepsilon_{\max}/[(1 - 1/A) R_{\min}].
+    \]
+Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.
+Fix $R \in [R_{\min},\infty)$ and $\varepsilon \in (0,\varepsilon_{\max}]$ arbitrarily.
 Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.
@@
 \begin{equation*}
-    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/a) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
+    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
     0, & \bsk \notin \calK_1,
     \end{cases}
-   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/a)}{2}.
+   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/A)}{2}.
 \end{equation*}
@@
 \nonumber
-    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/a) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
+    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
     0, & \bsk \in \calJ, 
     \end{cases}
-    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/a)}{2}, \\
+    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/A)}{2}, \\
     \label{DHKM:SOLf2bd}
-    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/a)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
+    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
 \end{gather}
@@
     \nonumber
-    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{a} \\
-    & \ge \frac{\norm[\calF]{f_{\pm}}}{a}.
+    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{A} \\
+    & \ge \frac{\norm[\calF]{f_{\pm}}}{A}.
 \end{align}
@@
 & \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
-=\frac{R(1 - 1/a)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
-& \ge \frac{R(1 - 1/a)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
+=\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
+& \ge \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
 \end{align*}
 by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.
-This inequality implies the lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
+By the choice of $R_{\min}$ and $\varepsilon_{\max}$ above, it follows that $n > n_1$.
+This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
 Because $\lim_{R \to \infty} \COMP(\calA(\calC), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\calC)$ contains only adaptive algorithms.
@@
 \[
-\COST(\ALG,\calC,\varepsilon,R) \le \COMP(\calA(\calC),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/a}{2(a^\rho -1)^{1/\rho}}.
+\COST(\ALG,\calC,\varepsilon,R) \le \COMP(\calA(\calC),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
 \]
@@
 
+The above derivation assumes that $A > 1$.
+If $A =1$, then our cone consists of functions whose series coefficients vanish for wavenumbers outside $\calK_1$.
+The exact solution can be constructed using only the pilot sample.
+Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\calC$, which is an unbounded set.
+
 We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC$, but we may derive necessary conditions for $f$ to lie in $\calC$.
@@
 \begin{equation} \label{DHKM:PilotConeNecessary}
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n}} \le a 
-    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \ge n_1.
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n}} \le A
+    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
 \end{equation}
@@
 
-If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
-The remedy is to make $\calC$ more inclusive by increasing the inflation factor, $a$, and/or the pilot sample size, $n_1$.
+If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \calC$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
+The remedy is to make $\calC$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.
 
@@
 
-In this section, we write again $\calC_d$ instead of $\calC$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
+\FredNote{
+
+In this section, we write $\calC_d$ instead of $\calC$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
 Recall that we assume that
-$\lambda_{d,\bsk_1}\ge \lambda_{d,\bsk_2}\ge \cdots >0$. From 
+$\lambda_{d,\bsk_1}\ge \lambda_{d,\bsk_2}\ge \cdots >0$. Let 
+\[
+n(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le \delta \right \} \qquad \forall \delta > 0.
+\]
+From 
+Equations \eqref{DHKM:PilotConeAlg_cost} and \eqref{DHKM:PilotConeAlg_comp}, we obtain that 
+\begin{multline*}
+     \COMP(\calA(\calC_d),\omega_{\textup{lo}} \varepsilon,R) \le n(\varepsilon/R,d) \le 
+        \COMP(\calA(\calC_d),\omega_{\textup{hi}} \varepsilon,R)  \\
+        \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
+\end{multline*}
+where the positive constants $\omega_{\textup{lo}}$ and $\omega_{\textup{hi}}$  depend on $A$, but not depend on $d$, $\varepsilon$, or $R$.
+From the equation above, it is clear that tractability depends on the behavior of $n(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity.
+We would like to study under which conditions we obtain the various tractability notions defined in Section \ref{DHKM:secTractability}.
+
+To this end, we distinguish two cases, depending on whether $\rho'$ is infinite or not. This 
+distinction is useful because it allows us to relate the computational complexity of the algorithms 
+considered in this chapter to the computational complexity of linear problems on certain function spaces considered in the classical literature on information-based complexity, as for example \cite{NovWoz08a}.
+The case $\rho'=\infty$ corresponds to the
+worst-case setting, where one studies the worst performance of an algorithm over the unit ball of 
+a space. The results in Theorem \ref{DHKM:thmtract1} below are indeed very similar to the results 
+for the worst-case setting over balls of suitable function spaces. The case $\rho<\infty$ corresponds to the so-called average-case setting, where one 
+considers the average performance over a function space equipped with a suitable measure. 
+For both of these settings there exist tractability results that we will make use of here.
+
+}
+
+\iffalse
+
+From 
 Equations \eqref{DHKM:PilotConeAlg_cost} and \eqref{DHKM:PilotConeAlg_comp}, we obtain that 
@@
         \COMP(\calA(\calC_d),\varepsilon,R)  \asymp \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \varepsilon\, D(a,R) \right \},
+    \le D_A\,  \varepsilon/R\, \right \},
 \]
-where $D(a,R)$ is a positive constant that may depend on $a$ and $R$, but does not depend on $d$ and $\varepsilon$.
+where $D_A$ is a positive constant that may depend on $A$, but does not depend on $d$, $\varepsilon$, and $R$.
 We would like to study under which conditions we obtain the various tractability notions defined in Section \ref{DHKM:secTractability}.
 
-Since $\lambda_{\bsk_i}>0$, and since we are interested in the asymptotic behavior 
+Since $\lambda_{d,\bsk_i}>0$, and since we are interested in the asymptotic behavior 
 of $\COMP(\calA(\calC_d),\varepsilon,R)$ when $d$ and/or $\varepsilon^{-1}$ tend to infinity, it is sufficient to consider the quantity 
@@
 n(\varepsilon,d)=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \varepsilon \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R) ,
+    \le \varepsilon/R \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R) ,
 \]
-for $\varepsilon \in (0,1)$ and $d\in\NN$.
+for $\varepsilon \in (0,1)$ and $d\in\NN$, where the implied constant may depend on $a$.
 To this end, we distinguish two cases, depending on whether $\rho'$ is infinite or not. This 
 distinction is useful because it allows us to relate the computational complexity of the algorithms 
-considered in this paper to the computational complexity of linear problems on certain function spaces considered in the classical literature on information-based complexity, as for example \cite{NovWoz08a}.
-The case $\rho'=\infty$ corresponds to the so-called
+considered in this chapter to the computational complexity of linear problems on certain function spaces considered in the classical literature on information-based complexity, as for example \cite{NovWoz08a}.
+The case $\rho'=\infty$ corresponds to the
 worst-case setting, where one studies the worst performance of an algorithm over the unit ball of 
-a space. The case $\rho<\infty$ corresponds to the so-called average-case setting, where one 
+a space. The results in Theorem \ref{DHKM:thmtract1} below are indeed very similar to the results 
+for the worst-case setting over balls of suitable function spaces. The case $\rho<\infty$ corresponds to the so-called average-case setting, where one 
 considers the average performance over a function space equipped with a suitable measure. 
 For both of these settings there exist tractability results that we will make use of here.
+\fi
+
+\PeterNote{I added a sentence for $\rho'=\infty$ regarding similarities to the 
+case of balls in the worst-case setting. For $\rho'<\infty$ it does not make sense to speak of 
+balls, because this case is related to the average case setting, where one considers the average 
+over the whole space.}
 
@@
 \[
-n(\varepsilon,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
-    \le \varepsilon \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R).
+\FredNote{n(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
+    \le \varepsilon/R \right \}}.
 \]
@@
 \begin{proof}
-Letting $\widetilde{\varepsilon}:=\sqrt{\varepsilon}$, we see that 
-$n(\varepsilon,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
+Letting $\widetilde{\varepsilon}:=\sqrt{\varepsilon/R}$, we see that 
+$n(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
 The latter expression is well studied in the context of tractability of linear problems in the worst-case setting defined on unit balls of certain spaces, and if and only if conditions on the $\lambda_{d,\bsk_i}$ for various tractability notions are known.
@@
 
-Since, in this paper, we consider $\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \varepsilon \right \}$, and \cite{NovWoz08a} and
-\cite{WerWoz17} study $\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$, 
+Since, in this chapter, we consider $\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \varepsilon/R \right \}$, and in \cite{NovWoz08a} and \cite{WerWoz17} $\varepsilon /R$ is replaced by the square of the error tolerance,
 there are slight differences between the results here and those in the aforementioned references; to be more precise, the exponent of strong polynomial tractability is $\eta$ here, whereas it is $2\eta$ in \cite{NovWoz08a}, and $1/\lambda_{d,\bsk_i}$ in \eqref{DHKM:eq:condwt} corresponds to $1/\sqrt{\lambda_{d,\bsk_i}}$ in \cite{WerWoz17}.
@@
 
-In this case, we have 
-\[
-n(\varepsilon,d)=\min \left \{n\ge 0\colon 
+\FredNote{In this case, letting $\widetilde{\varepsilon}:=(\varepsilon/R)^{\rho'/2}$ and 
+$\widetilde{\lambda}_{d,i}:=\lambda_{d,\bsk_i}^{\rho'}$, we have 
+\begin{align}
+    \nonumber 
+    n(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
 \sum_{i=n+1}^\infty \lambda_{d,\bsk_i}^{\rho'}\,
-    \le \varepsilon^{\rho'} \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R).
-\]
-Let $\widetilde{\varepsilon}:=\varepsilon^{\rho'/2}$ and 
-$\widetilde{\lambda}_{d,i}:=\lambda_{d,\bsk_i}^{\rho'}$, then
-\begin{equation}\label{DHKM:eqaveragetract}
-n(\varepsilon,d)=\min \left \{n\ge 0\colon 
+    \le (\varepsilon/R)^{\rho'} \right \} \\
+    \label{DHKM:eqaveragetract}
+    & =\min \left \{n\ge 0\colon 
 \sum_{i=n+1}^\infty \widetilde{\lambda}_{d,i}\,
     \le \widetilde{\varepsilon}^{\,2} \right \}.
-\end{equation}
-However, the latter expression corresponds exactly to the 
+\end{align}
+}However, the latter expression corresponds exactly to the 
 average-case tractability (with respect to the parameters 
@@
  \[
- \inf\left\{\eta/(1-\eta)\colon \mbox{$\eta$ satisfies \eqref{DHKM:eq:condspt1}}\right\}.
+ \inf\left\{\rho'\eta/(1-\eta)\colon \mbox{$\eta$ satisfies \eqref{DHKM:eq:condspt1}}\right\}.
  \]
@@
 
+\YuhanNote{\FredNote{
+To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of \emph{coordinate weights}, $w_1, \ldots, w_d$, and \emph{smoothness weights}, $s_1, s_2, \ldots$:
+\begin{equation}
+    \label{DHKM:prodwts}
+\lambda_{d,\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \NN_0^d, \ d \in \NN.
+\end{equation}
+This is a generalization of what was considered in Section \ref{DHKM:secexamp}, where $s_{k} = k^{-r}$.
+This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance}.
+The same argument as in Section \ref{DHKM:revisexamp} implies that
+\[\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} \le \exp\left(\sum_{k=1}^\infty s_k^\eta \sum_{\ell = 1}^{d} w_\ell^{\eta} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^\eta \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right).
+\]
+Thus, we have
+\begin{corollary} \label{DHKM:sptexample_cor}
+For the $\lambda_{d,\bsk}$ of the form \eqref{DHKM:prodwts} we have strong polynomial tractability if there exists $\eta>0$ such that
+ \begin{equation}
+\label{DHKM:sptexample}
+    \sum_{k=1}^\infty s_{k}^\eta < \infty \text{ and } 
+    \sum_{\ell = 1}^{\infty} w_\ell^{\eta} < \infty.
+\end{equation}
+\end{corollary}
+\textbf{I don't know if we can get if and only if.  Yuhan and Peter please check.}}}
+
+\PeterNote{For $d=1$, we need $\sum_{i=1}^\infty \lambda_{1,k_i}^\eta$ to be finite. But is not 
+$\sum_{i=1}^\infty \lambda_{1,k_i}^\eta=w_1\sum_{k=1}^\infty s_k^\eta$ ? If I am right, this shows that 
+$\sum_{k=1}^\infty s_k^\eta<\infty$ is necessary. I am not sure if the second condition is necessary. 
+Need some time to think.}
+
+\FredNote{Yes, I think that you are correct.  If we assume that $s_1>1$, then we may be able to show that the condition on the coordinate weights is necessary.}
+
+\FredNote{
+
+\begin{remark}
+Note that in the setting of this example, the term 
+$\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta}$ will usually depend exponentially on $d$ unless the 
+coordinate weights decay to zero fast enough with increasing $\ell$. Hence, we can only hope for tractability under the presence of decaying $w_\ell$. For further details on weighted approximation
+problems and tractability, we refer to \cite{NovWoz08a}.
+\end{remark}
+
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \section{Tracking the Decay Rate of the Series Coefficients of the Input Function}
+\label{DHKM:tracking_sec} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{equation}
-From \eqref{DHKM:SOLNorm} and \eqref{DHKM:SOLNormFinite} it follows that norm of the solution operator is 
+From \eqref{DHKM:SOLNorm} and \eqref{DHKM:SOLNormFinite} it follows that the norm of the solution operator is 
 \begin{equation} \label{DHKM:NormLambdaFinite}
@@
 \end{align*}
-Comparing this inequality to the definition of $\calC$ in the previous section, it can be seen that  $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone} with a different $a$.
-
-\FredNote{Hmm.  Should we use different $a$ to distinguish the two?}
-
-\PeterNote{Thanks, Fred, for adapting it such that we see the relation between the two kinds of cones. 
-A different $a$ would be good, if it does not too much trouble.
-Would you like me to change $a$ in Section 2 to $\widetilde{a}$?}
-\FredNote{$\widetilde{a}$ or $A$, not sure which is best.  Let's wait until we have finished the rest. }
+Comparing this inequality to the definition of $\calC$ in the previous section, it can be seen that  $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone} if we choose
+$A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
+
 From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \calC$ and $j \in \bbN$:
@@
 From this last inequality, it follows that $j^\dagger \ge j^*$.
-\end{proof}
-
-\FredNote{Pity, I do not see our cost upper bounds reflecting different rates of decay of the series coefficients.  Perhaps a remark here is in order.}
+\end{proof} \
+
+Although Algorithm \ref{DHKM:TrackConeAlg} tracks the decay rate of the $\hf(\bsk_i)$, the information cost bound and complexity bound in the theorem above do not reflect different decay rates of the $\hf(\bsk_i)$.
+That is a subject for future investigation.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Essential Optimality of the Algorithm and Tractability}
+\subsection{Essential Optimality of the Algorithm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-To establish the essential optimality of Algorithm \ref{DHKM:TrackConeAlg} requires some additional assumptions on the sequences $(n_j)_{j \in \N_0}$ and $\bigl(\sigma_j(f) \bigr)_{j \in \N_0}$.
-Recall from \eqref{DHKM:NormLambdaFinite} that $\bigl(\sigma_j(f) \bigr)_{j \in \N_0}$ has a finite $\rho'$ norm.
-We require that the $\Lambda_j$ cannot increase too quickly with $j$:
+To establish the essential optimality of Algorithm \ref{DHKM:TrackConeAlg} requires some additional, reasonable assumptions on the sequences $(n_j)_{j \in \N_0}$ and $\bigl(\sigma_j(f) \bigr)_{j \in \N_0}$.
+Recall from \eqref{DHKM:NormLambdaFinite} that $\bigl(\Lambda_j \bigr)_{j \in \N_0}$ has a finite $\rho'$ norm.
+We require that the $\Lambda_j$ must decay steadily with $j$:
 \begin{equation} \label{DHKM:LambdaDecayCond}
-     \Lambda_{j+r} \le b^r \Lambda_j  \quad \forall j,r \in \N_0.
+    \alpha^{-1} \beta^r \Lambda_j \le \Lambda_{j+r} \le \alpha \gamma^r \Lambda_j  \quad \forall j,r \in \N_0, \qquad \text{for some } \beta, \gamma < 1 \le \alpha.
 \end{equation}
@@
 For the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.
-Finally, let $\card(\cdot)$ denote the cardinality of a set.
+Let $\card(\cdot)$ denote the cardinality of a set.
 We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le n_{j+1}$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
@@
 j^\ddagger & = \max \left \{ j \in \bbN :  b^{j+1} \Lambda_{j+1}    > 
- \frac{2a\varepsilon}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
+ \frac{2a\alpha \varepsilon}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
 \right \}.
@@
 \displaystyle
-\frac{c_1 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_l^{\rho'/\rho}},  & \bsk \in \calK_l,
-\\
-0, & \bsk \notin \calK_l,
+\frac{c_1 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\Lambda_j^{\rho'/\rho}},  & \bsk \in \calK_j,
+\\
+0, & \bsk \notin \calK_j,
 \end{cases}
@@
 \nonumber
-\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1l}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_l}} 
-= c_1 b^l, \qquad l \in \N_0,\\
-\nonumber
-\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \sigma_l(f) \bigr)_{l \in \N_0} } 
+\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_l}} 
+= c_1 b^j, \qquad j \in \N_0,\\
+\nonumber
+\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \sigma_j(f) \bigr)_{j \in \N_0} } 
 =  \frac{c_1}{(1 - b^\rho)^{1/\rho}} = \frac{R(a+1)}{2a} \le R,
@@
 
-Now let $\ALG'$ be an arbitrary algorithm in $\calA(\calC)$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$, where the cardinality of $\calJ$ is $n$.
+Now let $\ALG'$ be an arbitrary algorithm in $\calA(\calC)$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
 Let $\tcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
-Construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
+Construct the function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
 \begin{align}
@@
 
-Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG'(f_1,\varepsilon) = \ALG'(f_\pm,\varepsilon)$.
+Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG'(f_\pm,\varepsilon) = \ALG'(f_1,\varepsilon)$.
 But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
@@
 
-Suppose that $n = \abs{\calJ} = \COST(\ALG',f_{\pm},\varepsilon) \le n_{j^{\star}}$.
+Suppose that $\card(\calJ) = \COST(\ALG',f_{\pm},\varepsilon) \le n_{j^{\star}}$.
 Then by condition \eqref{DHKM:PropCond}, there exists an $l^\star \le j^\star+1$ where $\card(\tcalK_{l^\star}) \ge S_2 \card(\calK_{l^\star})$.
@@
 Let $m = n_{l^\star} - n_{l^\star-1} = \card(\calK_{l^\star})$.
-Then, $m_{\inc} = \lceil S_2 m \rceil \ge S_2 m$ is lower bound on  $\card(\tcalK_{l^\star})$, and $m_{\out} = m - m_{\inc} \le (1 - S_2) m$ is an upper bound on $\card(\calK_{l^\star} \setminus \tcalK_{l^\star})$.
+Then, $m_{\inc} = \lceil S_2 m \rceil \ge S_2 m$ is a lower bound on  $\card(\tcalK_{l^\star})$, and $m_{\out} = m - m_{\inc} \le (1 - S_2) m$ is an upper bound on $\card(\calK_{l^\star} \setminus \tcalK_{l^\star})$.
 Moreover,
@@
     \\
-    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] b^{-\rho l^\star} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}^\rho
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] b^{-\rho l^\star} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}^\rho\, .
 \end{align*}
 
-Returning to \eqref{DHKM:eps_LBA}, the above inequality and condition \eqref{DHKM:LambdaDecayCond} imply that
-\begin{align}
-\nonumber
+Returning to \eqref{DHKM:eps_LBA}, the above inequality  implies that
+\begin{equation*}
     \varepsilon 
-& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{l^\star} \Lambda_{l^\star}
-\\
-\nonumber
-& \ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{j^\star+1} \Lambda_{j^\star+1}.
-\end{align}
-Therefore, if this inequality is violated for any $j^\star$, we must have $n>n_{j^\star}$.
+\ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{l^\star} \Lambda_{l^\star}.
+\end{equation*}
+Since $l^\star \le j^{\star}+1$ it follows that $ b^{l^\star} \ge b^{j^\star+1}$ and from condition \eqref{DHKM:LambdaDecayCond} it follows that $\Lambda_{l^\star} \ge \Lambda_{j^\star+1}/\alpha$.
+Thus,
+\begin{equation*}
+    \varepsilon 
+\ge  \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a\alpha} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho} b^{j^\star+1} \Lambda_{j^\star+1}.
+\end{equation*}
+If any algorithm satisfies the error tolerance $\varepsilon$ for all input functions in $\calC \cap \calB_R$ and has information cost no greater than $n_{j^\star}$, then $j^\star$ must satisfy the above inequality.
+By contrast, if the above inequality is violated for any $j^\star$, then the information cost of the successful algorithm must be greater than $n_{j^\star}$.
+This completes the proof.
 \end{proof}
@@
 \begin{proof}
-Let $j^\dagger(\varepsilon)$ be defined as in \ref{DHKM:TractConejdagger}, with the $\varepsilon$ dependence made explicit.  This defintion implies that 
+Let $j^\dagger(\varepsilon)$ be defined as in \eqref{DHKM:TractConejdagger}, with the $\varepsilon$ dependence made explicit.
+\FredNote{Choose $\varepsilon_{\max}$ and $R_{\min}$ in \eqref{DHKM:EssentialOpt} such that $j^\dagger(\varepsilon) \ge 2$.}  This definition implies that
+
 \begin{align*}
-    b^{j^\dagger(\varepsilon) +1 } \Lambda_{j^\dagger(\varepsilon) +1 } 
-    & \le  \norm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)+r}\Lambda_{j^\dagger(\varepsilon)+r} \bigr)_{r=1}^\infty} 
-    \le  \frac{b\varepsilon}{Ra^2} \left( \frac{1 - b^{j^\dagger(\varepsilon)\rho}}{1 - b^\rho} \right)^{1/\rho} 
+    b^{j^\dagger(\varepsilon)} \Lambda_{j^\dagger(\varepsilon) } 
+   & = \frac{[1 - (\gamma b)^\tau]^{1/\tau}}{\alpha}
+   \norm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)-1+r} \alpha \gamma^{r-1} \Lambda_{j^\dagger(\varepsilon)} \bigr)_{r=1}^\infty}
+    \\
+    & \ge \frac{[1 - (\gamma b)^\tau]^{1/\tau}}{\alpha}  \norm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)-1+r}\Lambda_{j^\dagger(\varepsilon)-1+r} \bigr)_{r=1}^\infty} \qquad \text{by \eqref{DHKM:LambdaDecayCond}}
     \\
     &
-    \le \frac{b\varepsilon}{Ra^2 (1 - b^\rho)^{1/\rho}} \\
-    & =  \frac{2a \omega \varepsilon}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
-    \\
-    & \qquad \qquad \text{where } \omega = \frac{(a-1)b}{2a^3} \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho}.
+    > \frac{b [1 - (\gamma b)^\tau]^{1/\tau} \varepsilon}{Ra^2 \alpha} \left( \frac{1 - b^{\rho(j^\dagger(\varepsilon)-1)}}{1 - b^\rho} \right)^{1/\rho} \qquad \text{by \eqref{DHKM:TractConejdagger}}
+    \\
+    &
+    \ge \frac{b [1 - (\gamma b)^\tau]^{1/\tau} \varepsilon}{Ra^2 \alpha} \qquad \text{since } j^\dagger(\varepsilon) \ge 2
+    \\
+    & =   \frac{\alpha^2}{(b\beta)^2} \times \frac{2a \alpha \omega \varepsilon}{R(a-1)(1 - b^\rho)^{1/\rho}}  \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{1/\rho}
+    \\
+    \intertext{where }
+   \omega  & = \frac{(a-1)b^3 \beta^2 (1 - b^\rho)^{1/\rho} [1 - (\gamma b)^\tau]^{1/\tau}}{2a^3 \alpha^4 } \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right]^{-1/\rho}.
 \end{align*}
-Making the $\varepsilon$ dependence explicit in the definition of $j^\ddagger(\varepsilon)$ in Theorem \ref{DHKM:TractConeLowBdComp} it follows that $j^\dagger(\varepsilon) < j^\ddagger(\omega \varepsilon)$, and so
+
+Making the $\varepsilon$ dependence explicit in the definition of $j^\ddagger(\varepsilon)$ in Theorem \ref{DHKM:TractConeLowBdComp} it follows from the above inequality that
+\begin{equation*}
+    b^{j^\dagger(\varepsilon)} \Lambda_{j^\dagger(\varepsilon) } 
+     > \frac{\alpha^2}{(b\beta)^2} b^{j^\ddagger(\omega\varepsilon)+2} \Lambda_{j^\ddagger(\omega \varepsilon) + 2 } 
+    \ge \alpha b^{j^\ddagger(\omega\varepsilon)} \Lambda_{j^\ddagger(\omega \varepsilon)} \qquad \text{by \eqref{DHKM:LambdaDecayCond}}.
+\end{equation*}
+
+If $j^{\dagger}(\varepsilon) \ge j^{\ddagger}(\omega \varepsilon)$, then \eqref{DHKM:LambdaDecayCond} implies that 
+\[
+ b^{j^\dagger(\varepsilon)} \Lambda_{j^\dagger(\varepsilon) } \le \alpha (\gamma b)^{j^{\dagger}(\varepsilon) - j^{\ddagger}(\omega \varepsilon)} b^{j^{\ddagger}(\omega \varepsilon) } \Lambda_{j^\ddagger(\omega \varepsilon) } \le \alpha b^{j^{\ddagger}(\omega \varepsilon) } \Lambda_{j^\ddagger(\omega \varepsilon) }.
+\]
+But, this contradicts the above inequality.  Thus, $j^\dagger(\varepsilon) < j^\ddagger(\omega \varepsilon)$, and so
 \[
@@
 
-\medskip
-
-\PeterNote{Working on Tractability below:
-
-\bigskip
-
-We again would like to study tractability. Like in Section~\ref{DHKM:SecPilotTract}, we distinguish whether $\rho'=\infty$ or not.
-
-\paragraph*{CASE 1: $\rho'=\infty$:}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tractability}\label{DHKM:SecDecayTract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We again would like to study tractability. As it turns out, by using the relation 
+between the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:TrackConeDef}, respectively, we 
+easily obtain sufficient conditions for tractability.
 
 \begin{theorem} \label{DHKM:thmtract3}
-Using the same notation as above, strong polynomial, polynomial, and weak tractability for the case $\rho'=\infty$ hold under exactly the 
-same conditions as in Theorem \ref{DHKM:thmtract1}.
+The respective conditions presented in Theorem \ref{DHKM:thmtract1} for the case where $\rho'=\infty$ and 
+in Theorem \ref{DHKM:thmtract2} for the case where $\rho'<\infty$ are sufficient for strong polynomial, polynomial, and weak tractability of the approximation problem defined on cones as in \eqref{DHKM:TrackConeDef}.
 \end{theorem}
 \begin{proof}
-
-Regarding sufficiency of the conditions, as pointed out above, $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone}, with suitably adapted constants (\PeterNote{I will make this more precise once we have agreed on notation}).
-This means that the approximation problem on  $\calC$ defined in \eqref{DHKM:TrackConeDef} is essentially no harder than the same problem on $\calC$ defined in \eqref{DHKM:pilot_cone}.
+As pointed out above, $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
+This means that the approximation problem on  $\calC$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\calC$ defined in \eqref{DHKM:pilot_cone}.
 This, however, implies that all sufficient conditions in Theorem \ref{DHKM:thmtract1} are also sufficient in the case considered in Theorem \ref{DHKM:thmtract3}.
-
-\medskip
-
-Regarding necessity of the conditions \ldots (\PeterNote{To come once we have lower bounds}).
-
 \end{proof}
 
-\paragraph*{CASE 2: $\rho'<\infty$:}
-
-\begin{theorem} \label{DHKM:thmtract4}
-Using the same notation as above, strong polynomial, polynomial, and weak tractability for the case $\rho'<\infty$ hold under exactly the 
-same conditions as in Theorem \ref{DHKM:thmtract2}.
-\end{theorem}
-\begin{proof}
-Sufficiency of the conditions follows by the same argument as in the proof of Theorem \ref{DHKM:thmtract3}.
-
-\medskip
-
-Regarding necessity of the conditions \ldots (\PeterNote{To come once we have lower bounds}).
-
-\end{proof}
-
-}
-
-%%%%%%%%%%%%
-\subsection{Numerical Example}
-%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Inferring Coordinate and Smoothness Importance} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-In many problems, the input function $f$ has structure which can be learned for adaptive approximation.
-For example, certain input variables in $f$ may be more active than others, or certain effects in $f$ (e.g., smoother effects) may be more important than others (e.g., rough effects).
-The incorporation of such structure can be advantageous in two ways.
-First, it allows for a tighter, adaptive approximation error bound in \eqref{DHKM:pilot_errbd}.
-Second, this data-based bound can then be used to guide an adaptive sampling procedure on $f$.
-
-In the following, we present a framework which accounts for coordinate, order and smoothness importance on $f$, via the weights $(\lambda_\bsk)_{\mathbf{k} \in \mathbb{K}}$ from Section 1.1.
-We then show how such structure can be inferred from a pilot sample, and how the resulting inferred weights can be used for adaptive approximation on $f$.
-For simplicity, we assume the index set $\mathbb{K}$ to be $\mathbb{N}_0^d$ in this section.
-
-%We then investigate how different combinations of these importances affect tractability of approximation.
-
-\subsection{Product, Order and Smoothness Dependent (POSD) weights}
-Let us first define $\mathbf{w} = (w_l)_{l=1}^d$ as the so-called \textit{product} weights, $\boldsymbol{\Gamma} = (\Gamma_k)_{k=1}^d$ as the \textit{order} weights, and $\mathbf{s} = (s_j)_{j=1}^\infty$ as the \textit{smoothness} weights.
-The intuition behind these weights are as follows: product weights quantify variable importance for the $d$ input variables in $f$; order weights $(\Gamma_k)_{k=1}^d$ quantify the importance of effects with different orders (e.g., first-order, second-order); and smoothness weights $(s_j)_{j=1}^\infty$ quantify the importance of effects with different degrees (e.g., linear, quadratic).
-Our strategy is to use these product, order and smoothness dependent (POSD) weights to parametrize weights $(\lambda_{\bsk})_{\bsk \in \mathbb{N}_0^d}$, which reflect the importance of each Fourier coefficient in $f$.
-
-We employ the following POSD parametrization of weights $(\lambda_{\bsk})_{\bsk \in \mathbb{N}_0^d}$:
+Theorem \ref{DHKM:thmtract3} yields sufficient conditions for the tractability notions considered 
+here. A general result for necessary conditions seems to be more difficult to obtain and is left open for future research.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Inferring Coordinate and Smoothness Importance} \label{DHKM:smoothimportance}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec} the $\lambda_{\bsk}$, which appear in the definition of the cone of inputs, $\calC$ are taken as given.
+These may take the form suggested in \eqref{DHKM:prodwts}, which define the $\bsk$ in terms of coordinate weights and smoothness weights.
+However, practically speaking it may be difficulty to know a priori the values of these weights.
+This section explores a situation where the initial data collected for the input function data can be used to learn the $\lambda_{\bsk}$, inferring which input variables in $f$ may be more important and the smoothness of the function.
+
+The motivation for this section is situations where the relative importance of the $d$ input variables of the function is not known from physical considerations.
+We also envision the situation where the cost of function data is large, e.g., the result of an expensive computer simulation.
+Thus, we are not concerned with the cost of algorithm beyond the information cost, which we hope to limit to $\calO(d)$.
+
+\subsection{Product, Order and Smoothness Dependent (POSD) Weights}
+The $u_{\bsk}$ and the $\lambda_{\bsk}$ in this section are defined as 
 \begin{equation}
-\lambda_{\bsk} = \Gamma_{\|\bsk\|_0} \prod_{\substack{l=1\\ k_l>0}}^d w_l s_{k_l}, \quad \Gamma_0 = s_1 = 1, \quad \bsk = (k_1, \cdots, k_d) \in \mathbb{N}_0^d,
+u_\bsk = \prod_{\ell = 1}^d \tu_{k_\ell}, \quad 
+\lambda_{\bsk} = \Gamma_{\|\bsk\|_0} \prod_{\substack{\ell=1\\ k_\ell>0}}^d w_\ell s_{k_\ell}, \quad \Gamma_0 = s_1 = 1, \quad \bsk \in \mathbb{N}_0^d,
 \label{eq:posd}
 \end{equation}
-where $\|\bsk\|_0$ equals the number of non-zero components in $\bsk$.
-This parametrization is motivated by several guiding principles from the experimental design literature (see \cite{WuHam2009}), which are briefly described below:
+where $\bsw = (w_\ell)_{l=1}^d$ is the vector of coordinate weights, $\bss = (s_k)_{k=1}^\infty$ is the vector of smoothness weights,  $\boldsymbol{\Gamma} = (\Gamma_m)_{m=1}^d$ is the vector of \emph{order weights}, and $\norm[0]{\bsk}$ denotes the number of nonzero elements of $\bsk$.
+The intuition behind these weights is as follows:
 \begin{itemize}
-\item The first principle, called \textit{effect sparsity}, assumes only a small number of input variables are important in $f$.
-In \eqref{eq:posd}, this sparsity can be accounted for allowing only a small number of product weights $\mathbf{w}$ to be large.
-\item The second principle, called \textit{effect heredity}, states that lower-order effects are more important than higher-order effects.
-Here, this means that a first-order effect (e.g., $\bsk_1 = (1,0, 0,\ldots, 0)$) should be more important than a second-order effect (e.g., $\bsk_2 = (1, 1, 0, \ldots, 0)$), and so on.
-From \eqref{eq:posd}, this heredity can be enforced by letting the order weights $\boldsymbol{\Gamma}$ be decreasing in order $k$.
-\item The third principle, called \textit{effect hierarchy}, allows an effect to be active \textit{only} when all its component effects are active as well.
-For example, the second-order effect $\bsk = (1, 1, 0, \ldots, 0)$ is active (i.e., $\lambda_\bsk > 0$) only when its two first-order components $\bsk_1 = (1, 0, 0, \ldots, 0)$ and $\bsk_2 = (0, 1, 0, \ldots, 0)$ are also active as well.
-This hierarchy is implicitly enforced within the product structure of the POSD weights \eqref{eq:posd}.
-\item The last principle, which we call \textit{effect smoothness}, states that lower-degree effects are more important than higher-degree effects.
-For example, when the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are polynomials, this means linear effects are more important than quadratic effects, which are in turn more significant than cubic effects, and so on.
-Effect smoothness can be imposed by setting a decreasing sequence for smoothness weights $\mathbf{s}$.
+    \item Coordinate weights quantify the importance for the $d$ input variables in $f$.
+    \item Smoothness weights quantify the importance of the $\tu_k$.  E.g., if the $\tu_k$ is a polynomial  of degree $k$, then the faster the $s_k$ decay, the smoother $f$ is.  
+    \item Order weights quantify the importance of effects with different orders; $\bsk$ having one nonzero element corresponds to a first-order or main effect, $bsk$ having two nonzero elements corresponds to a second-order (interaction) effect.
+(e.g., first-order, second-order)
 \end{itemize}
 
-From a Quasi-Monte Carlo (QMC) perspective, the POSD weights in \eqref{eq:posd} generalize upon the product-and-order dependent (POD) weights in \cite{KuoEtal12a}, which were first introduced in the analysis of QMC methods for partial differential equations with random coefficients.
-In particular, these existing POD weights can be recovered by restricting indices to be in $\{0, 1\}^d$, and setting $\mathbf{s} \equiv 1$ (i.e., all smoothness effects are of equal importance).
-Our POSD weights are also different from the smoothness-driven product-and-order dependent (SPOD) weights in \cite{Dea2014}, which were recently used to analyze higher-order QMC methods for stochastic partial differential equations.
+This parametrization is motivated by several guiding principles from the experimental design literature \citep{WuHam2009}, which are briefly described below.
+In statistical parlance, the terms $\hf(\bsk) u_{\bsk}$ are effects.
+\begin{itemize}
+\item \emph{Effect sparsity} assumes that only a small number of inputs in $f$ are important.
+In \eqref{eq:posd}, this sparsity is accounted for by allowing only a small number of product weights $\bsw$ to be large.
+This principle arose in the sufficient condition for strong tractability in Corollary \ref{DHKM:sptexample_cor}.
+\item \emph{Effect heredity} assumes that lower-order effects are more important than higher-order effects.
+E.g., $\lambda_{(1,0, 0,\ldots, 0)}$ should be larger than $\lambda_{(1, 1, 0, \ldots, 0)}$.
+In \eqref{eq:posd}, this heredity can be enforced by letting order weights $\Gamma_{m}$ be decreasing in $m$.
+\item \emph{Effect hierarchy} assumes that an effect is active \emph{only} when all its component effects are active.
+For example, $\lambda_{(1, 1, 0, \ldots, 0)} > 0$ only when $\lambda_{(1, 0, 0, \ldots, 0)}$ and $\lambda_{(0, 1, 0, \ldots, 0)}$ are both nonzero.
+This hierarchy is implicitly enforced within the product structure of the weights in \eqref{eq:posd}.
+\item \emph{Effect smoothness} assumes that lower-degree effects are more important than higher-degree effects.
+For example, when the $(\tu_k)_{k \in \mathbb{N}_0}$ are polynomials, this means that linear effects are more important than quadratic effects, which are in turn more significant than cubic effects, and so on.
+Effect smoothness can be imposed by setting $\bss$ to be a decreasing sequence.
+\end{itemize}
+
+The $\lambda_{\bsk}$ defined in \eqref{eq:posd} are called product, order and smoothness dependent (POSD) weights.
+From a quasi-Monte Carlo (QMC) perspective, the POSD weights in \eqref{eq:posd} generalize upon the product-and-order dependent (POD) weights in \cite{KuoEtal12a}, which were introduced for analyzing QMC methods in partial differential equations with random coefficients.
+The latter POD weights can be recovered by ignoring the smoothness weights.
+Our POSD weights differ from the smoothness-driven product-and-order dependent (SPOD) weights in \cite{Dea2014}, which were recently used to analyze higher-order QMC methods for stochastic partial differential equations.
 These SPOD weights take the form:
 \begin{equation}
-\gamma_{\mathbf{u}} = \sum_{\bsk \in \{1:\alpha\}^{|\mathbf{u}|}} \|\bsk\|_1 !
-\prod_{l \in \mathbf{u}} \left( 2^{\delta(k_l,\alpha)} w_l^{k_l} \right), \quad \|\bsk\|_1 = \sum_{l=1}^d k_l, \quad \mathbf{u} \in \{0, 1\}^d.
+\gamma_{\fraku} = \sum_{\bsk \in \{1:\alpha\}^{|\fraku|}} \|\bsk\|_1 !
+\prod_{l \in \fraku} \left( 2^{\delta(k_\ell,\alpha)} w_\ell^{k_\ell} \right), \quad \|\bsk\|_1 = \sum_{l=1}^d k_\ell, \quad \fraku \in \{0, 1\}^d.
 \label{eq:spod}
 \end{equation}
-Intuitively, SPOD weights quantify the importance of each \textit{subspace} (indexed by $\mathbf{u}$), under a common smoothness structure between subspaces.
-To contrast, the proposed POSD weights in \eqref{eq:posd} instead quantify the importance of each \textit{Fourier coefficient} in $f$ (indexed by $\bsk$), under a common smoothness structure between coefficients.
-
-%This can be seen as a generalization of the product-and-order (POD) weights, proposed by \cite{KuoEtal12a} for Quasi-Monte Carlo finite element methods.
-The original POD weights can be recovered by restricting $\bsk \in \{0, 1\}^d$ and $(s_j)_{j=1}^\infty \equiv 1$.
-
-\subsection{Inferring product and smoothness weights from pilot sample}
-
-As mentioned earlier, the key motivation for an adaptive algorithm is that it allows us to infer, from finite observations, information on what was not observed on $f$.
-We introduce next such an adaptive algorithm using POSD weights: these weights are first inferred from a pilot sample, then used for adaptive error estimation and sampling.
-For simplicity, we assume that order weights $\boldsymbol{\Gamma}$ are fixed (these can be preset a priori), and focus on the inference of product and order weights from data.
-This algorithm should work well for approximating functions within the data-based cone $\mathcal{C}$ in \eqref{DHKM:pilot_cone}, where $(\lambda_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are now the inferred POSD weights from the pilot sample.
-
-Consider first the inference of product weights $\mathbf{w}$ from pilot sample $\{\hat{f}(\bsk_i)\}_{i=1}^n$, given fixed order weights $\boldsymbol{\Gamma}$ and smoothness weights $\mathbf{s}$.
-One intuitive strategy is to find weights $\mathbf{w}$ which minimize the pilot sample input norm $\|(\hat{f}(\bsk_i)/\lambda_{\bsk_i})_{i=1}^n\|_{\rho}$, since this is a key ingredient for reducing the approximation error \eqref{DHKM:pilot_errbd} for the cone of functions in \eqref{DHKM:pilot_cone}.
-Moreover, by the effect sparsity principle, product weights should also be set as small as possible, to reflect the belief that a small number of variables are active in $f$.
-This motivates the following inference procedure:
-\begin{equation}
-\mathbf{w} \leftarrow \text{InfProd}(\{\hat{f}(\bsk_i)\}_{i=1}^n, w^*, \boldsymbol{\Gamma}, \mathbf{s}) := \min \argmin_{w_l \leq w^*} \left\|\left( \frac{\hat{f}(\bsk_i)}{\lambda_{\bsk_i}(\mathbf{w},\boldsymbol{\Gamma},\mathbf{s})} \right)_{i=1}^n\right\|_{\rho}.
-\label{eq:infprod}
-\end{equation}
-Here, $w^*$ is the maximum product weight allowed, and $\lambda_{\bsk_i}(\mathbf{w},\boldsymbol{\Gamma},\mathbf{s})$ follows the POSD form \eqref{eq:posd} with weights $\mathbf{w}$, $\boldsymbol{\Gamma}$ and $\mathbf{s}$.
-In words, the problem in \eqref{eq:infprod} finds the smallest product weights which uniformly minimize the input norm $\| f \|_{\mathcal{F}}$ for functions $f$ within cone $\mathcal{C}$.
-
-Consider next the inference of smoothness weights $\mathbf{s}$, given fixed product weights $\mathbf{w}$ and order weights $\boldsymbol{\Gamma}$. Applying the same strategy as above, we get: 
-\begin{equation}
-\mathbf{s} \leftarrow \text{InfSmooth}(\{\hat{f}(\bsk_i)\}_{i=1}^n, s^*, \mathbf{w}, \boldsymbol{\Gamma}) := \min \argmin_{s_j \leq s^*} \left\|\left( \frac{\hat{f}(\bsk_i)}{\lambda_{\bsk_i}(\mathbf{w},\boldsymbol{\Gamma},\mathbf{s})} \right)_{i=1}^n\right\|_{\rho},
-\label{eq:infsmooth}
-\end{equation}
-where $s^*$ is the maximum smoothness weight allowed.
-In words, problem \eqref{eq:infsmooth} finds the smallest smoothness weights which uniformly minimize the input norm $\| f \|_{\mathcal{F}}$ for functions $f$ within cone $\mathcal{C}$.
-Alternatively, if one is willing to assume a parametric form for smoothness decay (e.g., $s_j = 1/j^{\nu}$), then the unknown decay parameters (e.g., $\nu$) can be similarly estimated by minimizing the sample input norm.
-
-The two procedures \eqref{eq:infprod} and \eqref{eq:infsmooth} can be performed iteratively for joint inference on both product weights $\mathbf{w}$ and smoothness weights $\mathbf{s}$.
-Beginning with an initial choice of $\mathbf{w} \equiv 1$ and $\mathbf{s} \equiv 1$, we first perform \eqref{eq:infprod} to update $\mathbf{w}$, then perform \eqref{eq:infsmooth} to update $\mathbf{s}$ (using updated $\mathbf{w}$).
-These two steps are repeated until both $\mathbf{w}$ and $\mathbf{s}$ converge.
-One nice feature of this iterative procedure is the so-called ``descent property'' -- one can show that the pilot sample input norm $\|(\hat{f}(\bsk_i)/\lambda_{\bsk_i})_{i=1}^n\|_{\rho}$ (the objective to minimize) indeed decreases with each iteration, which stabilizes the optimization algorithm.
-
-Of course, the quality of the inferred weights depends greatly on the design of the pilot sample, which we denote as $\mathcal{I}$.
-In our implementation, we take $\mathcal{I}$ to be $\{ (0, \ldots, 0, j, 0, \ldots, 0): j = 0, \ldots, s^*\}$, the set of all univariate indices with maximum smoothness $s^*$.
-The intuition here is that, by sampling all possible smoothness coefficients over each variable ($\# \mathcal{I} = d s^* + 1$ coefficients in total), one can accurately infer from this pilot sample both variable importance weights $\mathbf{w}$ and smoothness weights $\mathbf{s}$.
-
-Algorithm \ref{DHKM:InfPilotConeAlg} summarizes the full adaptive approximation procedure with POSD weights.
-First, the Fourier coefficients are observed from the pilot sample $\mathcal{I}$.
-Next, the product and smoothness weights $(\mathbf{w},\mathbf{s})$ are iteratively inferred from this pilot sample.
-Finally, incorporating these inferred weights within $(\lambda_{\bsk})_{\bsk \in \mathbb{K}}$, the required sample size $n^*$ can then be computed via the data-based error bound \eqref{DHKM:pilot_errbd}.
-Note that the remaining $n^* - \# \mathcal{I}$ indices (after the initial pilot sample) should be the indices with largest data-inferred weights $(\lambda_{\bsk})_{\bsk \in \mathbb{K}}$, i.e., the indices with greatest estimated importance from the pilot sample.
+Intuitively, the SPOD weights in \eqref{eq:spod} quantify the importance of each \textit{subspace} (indexed by $\fraku$), under a common smoothness structure between subspaces.
+In contrast, the proposed POSD weights in \eqref{eq:posd} instead quantify the importance of each \textit{Fourier coefficient} in $f$ (indexed by $\bsk$), under a common smoothness structure between coefficients.
+
+\subsection{Inferring POSD Weights from an Initial Sample}
+
+Let $\calC_{\bslambda}$ denote the cone of inputs defined in \eqref{DHKM:pilot_cone} by POSD weights $\bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}$.
+As mentioned above, our goal here is to infer $\bslambda$ from input function data.
+We start with an initial set of wavenumbers:
+\begin{equation} \label{DHKM:barKdef}
+    \bcalK= \{ (0, \ldots, 0, k, 0, \ldots, 0): k = 0, \ldots, k_{\max}\}.
+\end{equation}
+The approximation to $f$ based on sampling the series coefficients for these wavenumbers is
+\begin{equation*}
+    \fapp = \sum_{\bsk \in \bar{\calK}} \hf(\bsk) u_{\bsk}.
+\end{equation*}
+We choose the $\calC_{\bslambda}$ that best fits $f$ by selecting $\bslambda$ to make the norm of  $f_{\text{app}}$ small:
+\begin{multline}
+\bar{\bslambda} = \bslambda(\bar{\bsw}, \bar{\bss}, \bsGamma) \\
+\text{where } (\bar{\bsw}, \bar{\bss} ) = \min \left\{ \argmin_{(\bsw,\bss) \in \calW \times \calS} \left\|\left( \frac{\hf(\bsk)}{\lambda_{\bsk}(\bsw,\bss,\bsGamma)} \right)_{\bsk \in \bar{\calK}}\right\|_{\rho} \right \}.
+\label{DHKM:eq:inf}
+\end{multline}
+Here, $\calW$ is a candidate set for coordinate weights, e.g., $\calW = [0,w^*]^d$, and $\calS$ is a candidate set for the smoothness weights, e.g., $\calS = \{(1/k^r)_{k=1}^{\infty} \colon r > 0\}$.
+The inner minimization finds the $(\bsw,\bss)$ that minimize the approximate norm of the input function.
+This minimizer may be non-unique, so the outer minimization chooses the smallest such $(\bsw,\bss)$.
+Making the coordinate and smoothness weights as small as possible helps enforce the principles of effect sparsity.
+The optimum, $(\bar{\bsw}, \bar{\bss})$, then defines the \emph{data-inferred} POSD $\bslambda$, denoted $\bar{\bslambda}$.
+
+The candidate sets $\calW$ and $\calS$ should be constructed such that the coordinate and smoothness weights have a priori upper bounds.
+Otherwise the inner minimization would choose huge values for $\bsw$ and $\bss$ to maximize the $\lambda_{\bsk}(\bsw,\bss,\bsGamma)$ and minimize the norm of $\fapp$.
+The cardinality of the initial set of wavenumbers is $d k_{\max} + 1$.
+There is a trade-off between reducing cost by keeping $k_{\max}$ small enough and ensuring robustness by making $k_{\max}$ large enough.
+
+For simplicity, we assume that order weights, $\bsGamma$, are fixed a priori.
+If desired, they too could be inferred as the next step.
+However, since we want to limit the size of the initial sample to $\calO(d)$ we must sample judiciously the higher order interactions.
+
+The optimization in \eqref{DHKM:eq:inf} is nontrivial to solve numerically.
+In practice, we iteratively optimize over $\bsw$ and then $\bss$ until convergence is reached.
+At each step of the iteration $\|(\hat{f}(\bsk)/\lambda_{\bsk})_{\bsk \in \bcalK}\|_{\rho}$ decreases.
+
+Algorithm \ref{DHKM:InfPilotConeAlg} combines the construction of data-inferred POSD weights, $\bar{\bslambda}$ with Algorithm \ref{DHKM:PilotConeAlg}.
+This algorithm succeeds for input functions in the cone
+\begin{equation} \label{DHKM:pilot_cone2}
+    \bar{\calC} := \left \{ f \in \calF : f \in \calC_{\bar{\bslambda}} \text{ for } \bar{\bslambda} \text{ defined in \eqref{DHKM:eq:inf}} \right\}.
+\end{equation}
+The reason that $\bar{\calC}$ is a cone is that the data-inferred $\bar{\bslambda}$ for the input function $f$ is exactly the same as for the input function $cf$, where $c$ is any constant.
 
 \begin{algorithm}
-	\caption{$\ALG$ Based on Adaptive POSD Weights \label{DHKM:InfPilotConeAlg}} 
+	\caption{Adaptive $\ALG$ Based on Data-Inferred POSD Weights \label{DHKM:InfPilotConeAlg}} 
 	\begin{algorithmic}
-	\PARAM maximum product and smoothness weights, $w^*$ and $s^*$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $a > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}; 
+	\PARAM candidate sets $\calW$ and $\calC$; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}; 
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 
-\Ensure Error criterion \eqref{DHKM:err_crit} for the cone defined in \eqref{DHKM:pilot_cone}
-\State $\bullet$ Define pilot sample indices $\mathcal{I} := \{ (0, \ldots, 0, j, 0, \ldots, 0): j = 0, \ldots, s^*\}$
-\State $\bullet$ Evaluate pilot sample $\{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}$
-\State $\bullet$ Repeat until $(\mathbf{w},\mathbf{s})$ converges:
-\State \quad - $\mathbf{w} \leftarrow \text{InfProd}(\{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}, w^*, \boldsymbol{\Gamma}, \mathbf{s})$
-\State \quad - $\mathbf{s} \leftarrow \text{InfSmooth}(\{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}, s^*, \mathbf{w}, \boldsymbol{\Gamma})$
-\State $\bullet$ Choose $n^* =  \min \left \{n \ge \# \mathcal{I} : \text{ERR}\left( \{\hat{f}(\bsk_i)\}_{i \in \mathcal{I}}, \#\mathcal{I} \right) \le \varepsilon \right \}$, with $\ERR$ in \eqref{DHKM:pilot_errbd}
-
-\RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
+\Ensure Error criterion \eqref{DHKM:err_crit} for the cone defined in \eqref{DHKM:pilot_cone2}
+\State  Define the initial set of  wavenumbers $\bcalK$ defined in \eqref{DHKM:barKdef}
+\State Evaluate initial sample $\bigl\{\hf(\bsk)\bigr\}_{\bsk \in \bcalK}$
+\State Compute data-driven POSD weights, $\bar{\bslambda}$ according to \eqref{DHKM:eq:inf}
+\State Using these weights, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\ALG(f,\varepsilon)$
+\RETURN $\ALG(f,\varepsilon)$
 \end{algorithmic}
@@
 
-%\subsection{POSD weights and tractability}
-%We now investigate how different settings of the POSD weights, which corresponds to different assumptions on function $f$, influence tractability for function approximation.
-For simplicity, assume $\rho = \infty$ and $\rho' = \tau = 1$.
-From the error bound in \eqref{DHKM:APP_errorBd} and the cone definition in \eqref{DHKM:pilot_cone}, we have:
-%\begin{equation}
-%   \norm[\calG]{\SOL(f) - \APP(f,n)}  \le  \frakC \norm[\infty]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, \bignorm[1]{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
-%   \label{DHKM:err}
-%\end{equation}
-%\SimonNote{Include POSD tractability here?}
-
-\subsection{Numerical examples}
-
-We now investigate the numerical performance of this adaptive algorithm with POSD weights.
-For simplicity, only the case of $\rho = \infty$ and $\rho' = \tau = 1$ is considered here.
-The simulation set-up is as follows.
-The Fourier coefficients for input function $f$, $\{\hat{f}(\bsk)\}_{\bsk \in \mathbb{N}_0^d}$, are randomly sampled as:
+\FredNote{Fred is here}
+
+\subsection{Numerical Examples}
+
+We now investigate the numerical performance of this adaptive algorithm using data-inferred POSD weights.
+For simplicity, only the case of $\rho = \infty$ and $\rho' = \tau = 1$ is considered in the following examples.
+Here, the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d$ are Chebyshev polynomials, and the solution operator is $\SOL (f) = f$ (i.e., function approximation).
+We note that $\|f - \APP(f)\|_\infty$ is bounded above by $\|f - \APP(f)\|_\calG$, so the worst-case approximation error $\|f - \APP(f)\|_\infty$ should satisfy the desired error tolerance $\varepsilon$ by \eqref{DHKM:err_crit}.
+
+The simulation set-up is as follows. The Fourier coefficients for input function $f$, $\{\hat{f}(\bsk)\}_{\bsk \in \mathbb{N}_0^d}$, are randomly sampled as:
 \begin{equation}
-\hat{f}(\bsk) = Z_{\bsk} \left( \tilde{\Gamma}_{\|\bsk\|_0} \prod_{\substack{l=1\\ k_l>0}}^d \tilde{w_l} \tilde{s}_{k_l} \right), \quad Z_{\bsk} \overset{i.i.d.}{\sim} \text{Unif}\{-1, 1\}, \quad \mathbf{k} \in \mathbb{N}_0^d.
+\hat{f}(\bsk) = Z_{\bsk} \left( {\Gamma}_{\|\bsk\|_0}^{\rm tr} \prod_{\substack{l=1\\ k_\ell>0}}^d {w_\ell^{\rm tr}} {s}_{k_\ell}^{\rm tr} \right), \quad Z_{\bsk} \overset{i.i.d.}{\sim} \text{Unif}[-1, 1], \quad \bsk \in \mathbb{N}_0^d.
 \label{eq:foursim}
 \end{equation}
-Here, $\tilde{w_l} = 1/l^2$, $\tilde{\Gamma}_k= 1/k!$ and $\tilde{s_j} = \mathbbm{1}\{ j \leq 4 \}/j^3$ are the true order, product and smoothness weights of $f$, and $Z_{\bsk}$ randomly sets the sign of each coefficient.
-The product weights are also randomized in terms of variable order, to ensure that the order of input variables does not necessarily reflect the order of variable importance.
-For Algorithm \ref{DHKM:InfPilotConeAlg}, we set $\boldsymbol{\Gamma}$ as the true order weights $\tilde{\boldsymbol{\Gamma}}$, and use an inflation factor of $a = 1.1$.
-
-Figure \ref{fig:four} (a) and (b) plot the adaptive sample size $n^*$ (from Algorithm \ref{DHKM:InfPilotConeAlg}) as a function of the error ratio $\|f - \hat{f}\|_{\infty}/\epsilon$, for $f$ in $d=4$ and $d=8$ dimensions, respectively.
-Each data point corresponds to a different error tolerance $\epsilon$.
-Here, an error ratio $\|f - \hat{f}\|_{\infty}/\epsilon$ close to 1 (but not exceeding 1) is desired, since this shows our adaptive approach can achieve the desired error tolerance $\epsilon$ by inferring and incorporating POSD structure.
-For $d=4$ (Figure \ref{fig:four} (a)), the error ratios $\|f - \hat{f}\|_{\infty}/\epsilon$ fluctuate around 0.25 for all choices of $\epsilon$; for $d=8$ (Figure \ref{fig:four} (b)), these ratios begin at $\approx 0.2$ for $\epsilon = 0.1$, and decrease to $\approx 0.07$ for $\epsilon = 0.001$.
-This suggests that our adaptive algorithm works reasonably well, and appears to be slightly more effective in lower dimensions ($d=4$) than in higher dimensions ($d=8$).
-One reason for this is that the POSD structure is more easily inferred in lower dimensions from a small pilot sample, which then allows for a tighter data-based error bound.
+Here, $(w_\ell^{\rm tr})_{l=1}^d = (1/l^2)_{l=1}^d$, $({\Gamma_k^{\rm tr}})_{k=1}^\infty \equiv 1$ and $(s_j^{\rm tr})_{j=1}^{k_{\rm max}} = (1/j^4)_{j=1}^4$ are the true product, order and smoothness weights of $f$, and $Z_{\bsk}$ randomly sets the magnitude and sign of each coefficient.
+Product weights are also randomized in terms of variable order, to ensure that the order of input variables does not necessarily reflect the order of variable importance.
+We also set $\boldsymbol{\Gamma}$ in Algorithm \ref{DHKM:InfPilotConeAlg} as the true order weights $\boldsymbol{\Gamma}^{\rm tr}$, and use an inflation factor of $A = 1.1$.
+
+%\PeterNote{Below, we write $\epsilon instead of $\varepsilon$. Simon, is that on purpose?}
+
+Figures \ref{fig:four} (a) and (b) plot the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error ratio $\|f - \APP(f)\|_\infty/\varepsilon$, for $f$ in $d=4$ and $d=7$ dimensions, respectively.
+Each data point corresponds to a different error tolerance $\varepsilon$.
+Here, a ratio $\|f - \APP(f)\|_\infty / \varepsilon$ close to 1 (but not exceeding 1) is desired, since this shows our adaptive procedure can achieve the desired tolerance $\varepsilon$ by inferring and incorporating POSD structure.
+For $d=4$ (Figure \ref{fig:four} (a)), $\|f - \APP(f)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$ (Figure \ref{fig:four} (b)), this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decrease to $\approx 0.014$ for $\varepsilon = 0.001$.
+This shows that our adaptive approximation algorithm works reasonably well, and appears slightly more effective in lower dimensions ($d=4$) than in higher dimensions ($d=7$).
+A likely reason for this is that the underlying POSD structure can be more easily learned from a small pilot sample in lower dimensions than in higher dimensions; using this inferred structure then allows for a tighter data-based error bound.
 
@@
 \centering
-\includegraphics[width=0.7\textwidth]{d8}
+\includegraphics[width=0.7\textwidth]{d7}
 \label{fig:four2}
-\caption{$f$ is a $d=8$-dim. function with random Fourier coefficients.}
+\caption{$f$ is a $d=7$-dim. function with random Fourier coefficients.}
 \end{subfigure}
-\caption{Adaptive sample size $n^*$ as a function of error ratio $\|f - \hat{f}\|_{\infty}/\epsilon$, with points colored by the absolute error tolerance level $\epsilon$.}
+\caption{Total required sample size as a function of error ratio $\|f - \hat{f}\|_{\infty}/\varepsilon$, with points colored by the absolute error tolerance level $\varepsilon$.}
 \label{fig:four}
@@
 
-\section*{Appendix}
+%\section*{Appendix}
 

### 2019-06-16 DHKM_Response_to_Reviewers.tex
Updates from Overleaf

\documentclass[11pt]{article}
\usepackage{latexsym,amsfonts,amsmath,theorem,amssymb}

\newcommand{\il}{\left\langle}
\newcommand{\ir}{\right\rangle}
\newcommand{\bsb}{{\boldsymbol{b}}}
\newcommand{\bsc}{{\boldsymbol{c}}}
\newcommand{\bsgamma}{{\boldsymbol{\gamma}}}
\newcommand{\bseta}{{\boldsymbol{\eta}}}
\newcommand{\bstau}{{\boldsymbol{\tau}}}
\newcommand{\bsh}{{\boldsymbol{h}}}
\newcommand{\bsp}{{\boldsymbol{p}}}
\newcommand{\bsell}{{\boldsymbol{\ell}}}
\newcommand{\bst}{{\boldsymbol{t}}}
\newcommand{\bsr}{{\boldsymbol{r}}}
\newcommand{\bsu}{{\boldsymbol{u}}}
\newcommand{\bsv}{{\boldsymbol{v}}}
\newcommand{\bsx}{{\boldsymbol{x}}}
\newcommand{\bsq}{{\boldsymbol{q}}}
\newcommand{\bsy}{{\boldsymbol{y}}}
\newcommand{\bsz}{{\boldsymbol{z}}}
\newcommand{\bsw}{{\boldsymbol{w}}}
\newcommand{\bsS}{{\boldsymbol{S}}}
\newcommand{\bsW}{{\boldsymbol{W}}}
\newcommand{\bspitch}{{\boldsymbol{\,\pitchfork}}}
\newcommand{\bszero}{{\boldsymbol{0}}}
\newcommand{\bsone}{{\boldsymbol{1}}}
\newcommand{\rd}{\,\mathrm{d}}
\newcommand{\ri}{\mathrm{i}}
\newcommand{\re}{\mathrm{e}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\bbN}{\mathbb{N}}
\newcommand{\bbZ}{\mathbb{Z}}
\newcommand{\bbE}{\mathbb{E}}
\newcommand{\calA}{\mathcal{A}}
\newcommand{\calB}{\mathcal{B}}
\newcommand{\calC}{\mathcal{C}}
\newcommand{\calD}{\mathcal{D}}
\newcommand{\calJ}{\mathcal{J}}
\newcommand{\calK}{\mathcal{K}}
\newcommand{\calL}{\mathcal{L}}
\newcommand{\calZ}{\mathcal{Z}}
\newcommand{\calF}{\mathcal{F}}
\newcommand{\calG}{\mathcal{G}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\calI}{\mathcal{I}}
\newcommand{\calO}{\mathcal{O}}
\newcommand{\calQ}{\mathcal{Q}}
\newcommand{\calS}{\mathcal{S}}
\newcommand{\calW}{\mathcal{W}}
\newcommand{\tr}{{\tt T}}
\renewcommand{\pmod}[1]{\,(\bmod\,#1)}
\renewcommand{\mod}[1]{\,(\negthickspace\bmod #1)}
\newcommand{\ns}{\negthickspace\negthickspace}
\newcommand{\nns}{\negthickspace\negthickspace\negthickspace\negthickspace}
\newcommand{\mask}[1]{}
\newcommand{\esup}{\operatornamewithlimits{ess\,sup}}
\newcommand{\einf}{\operatornamewithlimits{ess\,inf}}
\newcommand{\e}{{\varepsilon}}
\newcommand{\setu}{{\mathfrak{u}}}
\newcommand{\setv}{{\mathfrak{v}}}
\newcommand{\setw}{{\mathfrak{w}}}
\newcommand{\setU}{{\mathfrak{U}}}
\newcommand{\sob}{{\rm Sob}}
\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\newcommand{\sset}{[s]}
\newcommand{\To}{\rightarrow}
\newcommand{\dimtr}{{\rm dim}^{\rm trnc}}
\newcommand{\dimtrint}{{\rm dim}^{\rm trnc-int}}

\begin{document}

\begin{center}

{\Large Response to the Reviewers of the Manuscript\\
``Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone''}
\end{center}

\medskip

\noindent We would like to thank you for your careful reviews of our manuscript and your helpful comments.

Following the suggestions of one of the reviewers, we have restructured the introductory parts of the paper. Thereby, we address several of the remarks 
made by both referees.

Below, we respond to the points made in your reports.

\subsection*{Referee Report 1 ``Summary. The authors study \ldots '' (2 pages):}

\begin{itemize}
\item Remarks (1)--(4): done. 
\item Remark (6): What we mean by "this example" is the example of functions defined over $[-1,1]^d$ with a Chebyshev polynomial basis. We reformulated this passage to make this point clearer. 
\item Remarks (7), (8): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
\item Remark (9): done. 
\item Remarks (11), (12): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
\item Remark (13): We put this definition into a separate paragraph. 
\item Remark (14): done. 
\item Remark (15): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
\item Remark (16): done. 
\item Remark (17): The motivation for defining this cone is stated in the beginning of the section, but we have reformulated this passage to make it clearer. 
\item Remark (18): Thanks, we have provided further details in Algorithm 4 for the step ``Compute data-driven POSD weights'', as well as for the sentence around (41). With this, the adaptive procedure is better defined, and we believe it should be called an algorithm.
\end{itemize}

\subsection*{Referee Report 2 ``The paper studies \ldots'' (4 pages):}

\begin{itemize}
\item Major issues 1.a)--1.d), 2.a), 2.b): Done. We have modified the introduction, and re-organized it into two sections. 
\item Remark (i): The ordering is not necessarily unique, as we might have weights 
that are equal. 
\item Remark (ii): the referee is correct. Thanks for pointing this out. 
\item Remark (iii): done. 
\item Remark (iv): The paper will be a chapter in a proceedings volume.
\item Remark (vii): We changed ``Choosing" to ``Identifying".
\item Remark (viii): Theoretically, we could simplify this as suggested by the reviewer; however, we would like to keep the influence of $\varepsilon$ and $R$ separate and explicit. 
\item Remark (ix): We have kept this result as a theorem, but due to the re-structuring of the paper, it is no longer part of the introduction. 
\item Remark (x): we have moved the contents of the previous Section 1.5 as suggested by the reviewer. 
\item Remark (xi): done. 
\item Remark (xix): Here, we mean a ``small number of coordinates in $f$ are important''. We have made this change in the paper.
\item Remark (xx): These guiding principles help guide the inference of weights $\boldsymbol{\lambda}$ (and its corresponding cone $\calC_{\boldsymbol{\lambda},A}$) from initial data. We have added a sentence on this on page 29. 
\item Remark (xxi): Thanks, the cone in equation (16) is now denoted as $\calC_{\boldsymbol{\lambda},A}$, and the data-inferred cone on page 30 is now denoted as $\bar{\calC}_A = \calC_{\bar{\boldsymbol{\lambda}},A}$.
\item Remark (xxii): Yes, this is correct. We have added a sentence after equation (40) clarifying this.
\item Remark (xxiii): The data-adaptive cone $\bar{\calC}$ is the earlier cone $\calC_{\boldsymbol{\lambda},A}$ in equation (16) with data-adaptive weights $\boldsymbol{\lambda} = \bar{\boldsymbol{\lambda}}$. We have clarified this in equation (42).

\end{itemize}

\bigskip

\bigskip

\noindent With kind regards,\\[0.25cm]
The authors,

\noindent Y. Ding, F.J. Hickernell, P. Kritzer, and S. Mak.

\end{document}

### 2019-06-25 DHKM_Response_to_Reviewers.tex
updates

@@
 \item Remark (ix): We have kept this result as a theorem, but due to the re-structuring of the paper, it is no longer part of the introduction. 
-\item Remark (x): we have moved the contents of the previous Section 1.5 as suggested by the reviewer. 
-\item Remark (xi): done. 
+\item Remark (x): We have moved the contents of the previous Section 1.5 as suggested by the reviewer. 
+\item Remark (xi): The cone in equation (16) is now denoted as $\calC_{\boldsymbol{\lambda},A}$. 
+\item Remark (xii): We have fixed the notation in Proposition 1.
+Thanks for pointing this out.
+We have also added a Proposition 2 to discuss the relationship between our cone $\mathcal{C}_{\boldsymbol{\lambda},A}$ and a new cone $\mathcal{C}'$.
+\item Remark (xiii): We have added the results with smoothness parameters $r$ in Corollary 1.
+\item Remark (xiv): Thanks for pointing this out.
+$\kappa_i$ should be $k_i$.
+$k_i$ and $l_i$ are the sub-indices of $\boldsymbol{s}$ and $\boldsymbol{w}$ after ordering respectively.
+We could obtain the left-hand side inequality via the right-hand side special case.
+\item Remark (xv): The cone in equation (28) is now denoted as $\calC_{\boldsymbol{\lambda},a,b}$. 
 \item Remark (xix): Here, we mean a ``small number of coordinates in $f$ are important''. We have made this change in the paper.

### 2019-06-25 DingHickKritzMakRICAMChapVerD.tex
updates

--- 2019-03-20 DingHickKritzMakRICAMChap.tex
@@
 \newcommand{\SimonNote}[1]{{\color{purple}Simon: #1}}
+\newcommand{\DHKMchange}[1]{{\color{red}{#1}}}
+
 \newcommand{\tLambda}{\widetilde{\Lambda}}
@@
   %\subtitle{...}
-  \abstract{We study adaptive approximation algorithms for multivariate linear 
-  problems where the input sets are non-convex cones. While it is known that adaptive algorithms perform 
-  essentially no better than non-adaptive algorithms for convex input sets, the 
+  \abstract{We study adaptive approximation algorithms for general multivariate linear 
+  problems where the sets of input functions are non-convex cones. While it is known that adaptive algorithms perform 
+  essentially no better than non-adaptive algorithms for \DHKMchange{convex and symmetric} input sets, the 
   situation may be different for non-convex sets. A typical example
@@
 
+\DHKMchange{
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Adaptive algorithms infer the necessary computational effort based on the function data sampled.
-Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex}.
-We construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
-Our algorithms use series coefficients of the input function to construct an approximate solution that satisfies an absolute error tolerance.
+Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex} \DHKMchange{or \emph{non-symmetric}}.
+\DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
+\DHKMchange{By a cone, we mean a set of functions satisfying that for each element also all its multiples lie in the set.
+We will study different variants of cone here, the precise definitions will be given below.}
+
+Our algorithms use a finite number of series coefficients of the input function to construct an approximate solution that satisfies an absolute error tolerance.
 We show our algorithms to be essentially optimal.
 We derive conditions under which the problem is tractable, i.e., the information cost of constructing the approximate solution does not increase exponentially with the dimension of the input function domain.
-In the remainder of this section we define the problem and essential notation.
-But first, we present a helpful example.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{An Illustrative Example}\label{DHKM:secexamp}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$.  In this case,
-	\begin{align*}
-	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f), 
-	\qquad \bsk = (k_1, \ldots, k_d),\\
-    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , 
-    \qquad \tu_{k}(x) := \begin{cases} 1, & k =0 ,\\
-	x, & k=1,\\
-	2x \tu_{k-1}(x)-\tu_{k-2}(x), & k = 2, 3, \ldots.
-	\end{cases}
-	\end{align*}
-Approximating $f$ well by a finite sum requires knowing which terms in the infinite series for $f$ are more important.  Let 
-\begin{equation*}
-    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0,
-\end{equation*}
-where the $w_\ell$ are \emph{coordinate weights}.
-The introduction of coordinate weights expresses the understanding that the $f$ may depend more strongly on some coordinates---those with larger coordinate weights---than others.
-The definition of the norm of $f$ implies that an input function with modest sized norm must have series coefficients that decay quickly enough as the degree of the polynomial increases.
-This decay of the series coefficients corresponds to the smoothness of the input functions.
-Larger $r$ corresponds to greater smoothness.
-
-The weights, $\lambda_{\bsk}$, can be ordered,
-\begin{equation} \label{DHKM:lambda_order}
-    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots >0,
-\end{equation}
-which implies an ordering of the wavenumbers, $\bsk$.  Given this ordering, it is natural to approximate the solution using the first $n$ series coefficients as follows:
-\begin{equation*} %\label{DHKM:Ex_APP_def}
-   \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \qquad \forall n \in \N.
-\end{equation*}
-
-Here, we assume that it is possible to sample the series coefficients of the input function.
-This is a less restrictive assumption than being able to sample any linear functional, but it is more restrictive than only being able to sample function values.
-An important problem for future work is to extend the theory here to the case where the only function data available are function values.
-
-The error of this approximation can be defined as 
-\begin{gather*}
-    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}, \\
-    \text{where}\qquad
-    \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
-\end{gather*}
-
-If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer.  However, our goal is an algorithm, $\ALG(f,\varepsilon)$ that satisfies the error criterion
+In the remainder of this section we outline the general idea of the paper.
+
+We study the approximation of a solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
+Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(f,\varepsilon)$ for $f\in\calC$ that satisfies the error criterion
 \begin{equation} \label{DHKM:err_crit}
@@
 \end{equation}
-where  $\varepsilon$ is the error tolerance, and $\calC \subset \calF$ is the set of input functions for which $\ALG$ is successful.
-This algorithm contains a rule for choosing $n$---depending on $f$ and $\varepsilon$---so that $\ALG(f,\varepsilon) = \APP(f,n)$.
-The objectives of this chapter are to
+where  $\varepsilon$ denotes the error tolerance. Such an algorithm will  contain a rule for choosing $n$---depending on $f$ and $\varepsilon$.  The objectives of this chapter are to 
 \begin{itemize}
@@
 
+We assume in this paper that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n=n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
+I.e.,
+we will study algorithms which have an output of the form 
+\begin{equation*} 
+  \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N,
+\end{equation*}
+where an oracle provides $\hf(\bsk_1),\ldots,\hf (\bsk_{n(f,\varepsilon)})$ 
+with $n(f,\varepsilon)$ being chosen based on a stopping rule. 
+I.e., we assume that it is possible to sample the series coefficients of the input function.
+This is a \DHKMchange{more} restrictive assumption than being able to sample any linear functional, but it is \DHKMchange{less} restrictive than only being able to sample function values.
+An important future problem is to extend the theory in this chapter to the case where the only function data available are function values.
+
+We call an algorithm \emph{non-adaptive} if it is such that $n(f,\varepsilon)=n(\varepsilon)$, independently of the particular choice of $f\in\calC$.
+
+The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$.
+For adaptive algorithms this cost varies with the input function $f$.
+
+In the following, let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
+
+We now define the information cost of the algorithm in general, recognizing that it will tend to depend on $\norm[\calF]{f}$:
+\begin{equation*}
+    \COST(\ALG, \calC, \varepsilon,R) : = \max_{f \in \calC \cap \calB_{R}} \COST(\ALG,f,\varepsilon).
+\end{equation*}
+Note that while the cost depends on $\norm[\calF]{f}$, $\ALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
+It is common for $\COST(\ALG, \calC, \varepsilon,R)$ to be $\calO(\varepsilon^{-p})$, or perhaps asymptotically $c\log(1 + \varepsilon^{-1})$.
+
+\medskip
+
+\DHKMchange{A crucial concept is the set of all possible algorithms that may be constructed using series coefficients and that \emph{satisfy error criterion \eqref{DHKM:err_crit}}.
+We denote this set by $\calA(\calC)$.
+}
+
+Furthermore, we define the \emph{computational complexity} of a problem as the information cost of the best algorithm:
+\begin{equation*}
+    \COMP(\calA(\calC), \varepsilon,R) := \min_{\ALG \in \calA(\calC)} \COST(\ALG, \calC, \varepsilon,R) .
+\end{equation*}
+These definitions follow the information-based complexity literature \cite{TraWer98, TraWasWoz88}.
+We define an algorithm to be \emph{essentially optimal} if there exist some fixed positive $\omega$, $\varepsilon_{\max}$, and $R_{\min}$ for which
+\begin{multline} \label{DHKM:EssentialOpt}
+    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calA(\calC), \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+\end{multline}
+If the complexity of the problem is $\calO(\varepsilon^{-p})$, the cost of an essentially optimal algorithm is also $\calO(\varepsilon^{-p})$.
+If the complexity of the problem is asymptotically $c \log(1 + \varepsilon^{-1})$, then  the cost of an essentially optimal algorithm is also asymptotically $c \log(1 + \varepsilon^{-1})$.
+We will show that our adaptive algorithms presented in Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}  are essentially optimal.
+
+We will demonstrate below that non-adaptive algorithms are optimal when the set of inputs is chosen to be $\calC = \calB_R$.
+However, typically one cannot bound the norm of the input function a priori, so non-adaptive algorithms may be impractical.
+  This will lead to \emph{adaptive} algorithms $\ALG$ satisfying error criterion \eqref{DHKM:err_crit}.
+For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball.
+By a cone, we mean a set of functions satisfying that for each element also all its multiples lie in the set.
+We will study different variants of cones in different sections of this paper.
+The first definition of a cone will be given in \eqref{DHKM:pilot_cone},
+where the idea is that the consists of $f\in\calF$ such that 
+$$
+  \norm[\calF]{f}\le h (\hf(\bsk_1),\ldots,\hf (\bsk_{n_1}))
+$$
+for a suitably chosen homogeneous function $h:\bbR\to [0,\infty)$. This means that the norm of $f$ can be bounded well in terms of 
+a \emph{pilot sample} of size $n_1\in\bbN$, see \eqref{DHKM:pilot_cone} for the precise definition.
+In Section \ref{DHKM:SecAdapAlgTrackDecay}, we will modify the definition of cones such that we can keep track of the decay rate of the series coefficients of the input function (see \eqref{DHKM:TrackConeDef}),
+and in Section \ref{DHKM:smoothimportance_sec} we allow a situation 
+where we infer coordinate and smoothness importance from some initial data, thus making the definition of the cone more practical (see  
+\eqref{DHKM:pilot_cone2}).
+
+Note that algorithms satisfying error criterion \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$.
+Any algorithm must require a finite sample size, even if it is huge.
+Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.
+Thus, algorithms satisfying the error criterion  exist only for some strict subset of $\calF$.
+Identifying that subset is both an art and a science.
+
+The rest of the paper is structured as follows.
+In the next section, we will formulate our problem more formally, and we point out some results for non-adaptive algorithms with inputs from balls.
+Furthermore, we illustrate our theory by
+a particular example, and mention some definitions regarding \emph{tractability}.
+
+In Section \ref{DHKM:pilot_sec}, we define a cone of input functions, $\calC$, in \eqref{DHKM:pilot_cone} whose norms can be bounded above in terms of the series coefficients obtained from a pilot sample.
+Adaptive Algorithm \ref{DHKM:PilotConeAlg} is shown to be optimal for this $\calC$.
+We also identify necessary and sufficient conditions for tractability.
+
+Section \ref{DHKM:tracking_sec} considers the situation where function data is relatively inexpensive, and we track the decay rate of the series coefficients.
+Adaptive Algorithm \ref{DHKM:TrackConeAlg} is shown to be optimal in this situation.
+
+Section \ref{DHKM:smoothimportance_sec} considers the case where the most suitable weights $\bslambda$ are not known a priori and are instead inferred from function data.
+Adaptive Algorithm \ref{DHKM:InfPilotConeAlg} combines this inference step with Algorithm \ref{DHKM:PilotConeAlg} to construct an approximation that satisfies the error criterion.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{General Linear Problem}
+
+\section{Problem Formulation and an Illustrative Example}\label{DHKM:secprobdef}
+
+\PeterNote{Can we find a better heading for this section?}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Now, we define our problem more generally.
-A solution operator maps the input function to an output, $\SOL:\calF \to \calG$.
-As in the illustrative example above, the Banach spaces of inputs and outputs are defined by series expansions:
+
+\subsection{General problem formulation}
+
+Now, we define our problem more formally.
+The solution operator $\SOL$ maps the input function to an output, $\SOL:\calF \to \calG$.
+The Banach spaces of inputs and outputs are defined by series expansions:
+\DHKMchange{
 \begin{gather*}
-    \calF = \left \{f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad 1 \le \rho \le \infty, \\
-    \calG = \left \{g = \sum_{\bsk \in \mathbb{K}} \hg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \hg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad 1 \le \tau \le \rho.
+    \calF := \left \{f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \rho \le \infty,
 \end{gather*}
-Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, and $\mathbb{K}$ is a countable index set.
+and
+\begin{gather*}
+    \calG := \left \{g = \sum_{\bsk \in \mathbb{K}} \hg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \hg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \tau \le \rho.
+\end{gather*}
+}
+Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, $\mathbb{K}$ is a countable index set, and $\bslambda = (\lambda_\bsk)_{\bsk \in \mathbb{K}}$ is the sequence of weights.
 These bases are defined to match the solution operator:
@@
 
-To facilitate our derivations below, we establish the following lemma based on H\"older's inequality:
+To facilitate our derivations below, we establish the following lemma via H\"older's inequality:
 
 \begin{lemma} \label{DHKM:Key_Lem}
-Let $\calK$ be some proper or improper subset of $\bbK$. Moreover, let $\rho'$ be defined by the relation
-\begin{equation*}
-    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau, \qquad \text{i.e., } \rho' = \frac{\rho \tau}{\rho - \tau},
-\end{equation*}
-so $\tau \le \rho' \le \infty$.  Let $\Lambda =  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$.  Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
+Let $\calK$ be some proper or improper subset of the index set $\bbK$. Moreover, let $\rho'$ be defined by the relation
+\begin{equation*}
+    \frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau, \qquad \text{i.e., } \rho' := \frac{\rho \tau}{\rho - \tau},
+\end{equation*}
+so $\tau \le \rho' \le \infty$.
+Let $\Lambda :=  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$ be the norm of a subset of the weights.
+Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
 \begin{equation}
@@
     \displaystyle 
-    \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\Lambda^{\rho'/\rho}}, & \forall \bsk \in \calK, \quad  \rho'<\infty \\
-    R \Lambda \delta_{\bsk,\bsk^*}, & \forall \bsk \in \calK, \ \bsk^* \in \calK \text{ satisfies } \lambda_{\bsk^*} = \Lambda, \quad \rho' = \infty,
+    \frac{R \lambda_{\bsk}^{\rho'/\rho + 1}}{\Lambda^{\rho'/\rho}}, & \forall \bsk \in \calK, \quad  \text{if}\ \rho'<\infty, \\
+    R \Lambda \delta_{\bsk,\bsk^*}, & \forall \bsk \in \calK, \ \bsk^* \in \calK \text{ satisfies } \lambda_{\bsk^*} = \Lambda, \quad\text{if}\ \rho' = \infty,
     \end{cases}
@@
 
-Based on this lemma and taking $\calK = \bbK$, the norm of the solution operator can be expressed in terms of the $\lambda_\bsk$ as follows:
+Taking $\calK = \bbK$ in the lemma above, the norm of the solution operator can be expressed in terms of the norm of $\bslambda$ as follows:
 \begin{equation} \label{DHKM:SOLNorm}
-    \norm[\calF \to \calG]{\SOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\SOL(f)} = \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \mathbb{K}}}.
-\end{equation}
-We assume throughout that this norm is finite, namely,
+    \norm[\calF \to \calG]{\SOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\SOL(f)} = \bignorm[\rho']{\bslambda}.
+\end{equation}
+We assume throughout this chapter that the weights are chosen to keep this norm finite, namely,
 \begin{equation} \label{DHKM:SOLNormFinite}
-    \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \mathbb{K}}} < \infty.
-\end{equation}
-
-As in Section \ref{DHKM:secexamp}, here in the general case the $\lambda_{\bsk}$ are assumed to have a known order as was specified in \eqref{DHKM:lambda_order}.
-Also, we assume that all $\lambda_{\bsk}$ are  positive to avoid the trivial case where $\SOL(f)$ can be expressed exactly as a finite sum.
+    \bignorm[\rho']{\bslambda} < \infty.
+\end{equation}
+
+The $\lambda_{\bsk}$ are assumed to have a known order, and
+we also assume that all $\lambda_{\bsk}$ are  positive to avoid the trivial case where $\SOL(f)$ can be expressed exactly as a finite sum for all $f \in \calF$.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{An Illustrative Example}\label{DHKM:secexamp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$.  In this case,
+	\begin{align*}
+	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f), 
+	\qquad \bsk = (k_1, \ldots, k_d) \in \N_0^d,\\
+    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , 
+    \qquad \tu_{k}(x) := \cos( k \cos^{-1}(x)) \quad \forall k \in \N_0.
+	\end{align*}
+For this example, let $\calF$ denote a Hilbert space of input functions where we choose $\bbK=\bbN_0^d$ and $\rho=2$,
+\begin{equation*}
+    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}, \quad \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
+\end{equation*}
+The $w_\ell$ are non-negative \emph{coordinate weights}, which embody the assumption that $f$ may depend more strongly on coordinates with larger $w_\ell$ than those with smaller $w_\ell$.
+The definition of the $\calF$-norm implies that an input function must have series coefficients that decay quickly enough as the degree of the polynomial increases.
+Larger $r$ implies smoother input functions.
+
+The ordering of the weights,
+\begin{equation} \label{DHKM:lambda_order}
+    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots >0,
+\end{equation}
+implies an ordering of the wavenumbers, $\bsk$.  It is natural to approximate the solution using the first $n$ series coefficients as follows:
+\begin{equation*} %\label{DHKM:Ex_APP_def}
+   \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N.
+\end{equation*}
+
+The error of this approximation in terms of the norm on the output space, $\calG$, can be expressed as
+\begin{gather*}
+    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}, \\
+    \text{where}\qquad
+    \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
+\end{gather*}
+If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer \DHKMchange{for certain classes of inputs in $\calF$ as for example balls, which 
+are among the most prominent examples studied in the literature}.
+
+\PeterNote{Should we keep the list of questions in this extensive form?}
+\YuhanNote{I moved it to introduction}
+
+We return \DHKMchange{to the example of functions on $[-1,1]^d$, using a Chebyshev polynomial basis}, in Section \ref{DHKM:SecPilotTract} to discuss the computational cost and complexity.
+We perform some numerical experiments for this example in Section \ref{DHKM:numexamp_sec}.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{An Approximation and an Algorithm}
+\subsection{Approximation with inputs lying in a ball}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-An optimal approximation  based on $n$ series coefficients of the input function can be defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
+The optimal approximation  based on $n$ series coefficients of the input function is defined in terms of the series coefficients of the input function corresponding to the largest $\lambda_{\bsk}$ as follows:
 \begin{equation} \label{DHKM:APP_def}
@@
 \end{equation}
-Moreover, the worst case error over $\calB_R$ of any approximation based on $n$ series coefficients of the input function, $\APP'(\cdot,n)$, can be no smaller.
+Moreover, the worst case error over $\calB_R$ of $\APP'(\cdot,n)$, for any approximation based on $n$ series coefficients of the input function, can be no smaller.
 \end{theorem}
@@
 
-While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \subset \calF \times [0,\infty)$, satisfying the absolute error criterion \eqref{DHKM:err_crit}.
+While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \times [0,\infty)$, satisfying the absolute error criterion \eqref{DHKM:err_crit}.
 The non-adaptive Algorithm \ref{DHKM:BallAlg} satisfies this error criterion for $\calC  = \calB_R$.
 
-\begin{algorithm}
+\begin{algorithm}[H]
 \caption{Non-Adaptive $\ALG$ for a Ball of Input Functions \label{DHKM:BallAlg}}
 	\begin{algorithmic}
-	\PARAM the ball radius, $R$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
+	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; the ball radius, $R$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
 	\INPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$
@@
 \end{algorithm}
-
-After defining the information cost of an algorithm and the problem complexity in the next subsection, we demonstrate that this non-adaptive algorithm is optimal when the set of inputs is chosen to be $\calC = \calB_R$.
-However, typically one cannot bound the norm of the input function a priori, so Algorithm \ref{DHKM:BallAlg} is impractical.
-
-The key difficulty is that error bound \eqref{DHKM:APP_errorBd} depends on the norm of the input function.
-In contrast, we will construct  error bounds for $\APP(f,n)$ that only depend on function data.
-These will lead to \emph{adaptive} algorithms $\ALG$ satisfying error criterion \eqref{DHKM:err_crit}.
-For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball.
-
-Note that algorithms satisfying error criterion \eqref{DHKM:err_crit} cannot exist for $\calC = \calF$.
-Any algorithm must require a finite sample size, even if it is huge.
-Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.
-Thus, algorithms satisfying the error criterion  exist only for some strict subset of $\calF$, and choosing that subset well is both an art and a science.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Information Cost and Problem Complexity}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$.
-For adaptive algorithms this cost varies with the input function $f$.
-We also define the information cost of the algorithm in general, recognizing that it will tend to depend on $\norm[\calF]{f}$:
-\begin{equation*}
-    \COST(\ALG, \calC, \varepsilon,R) : = \max_{f \in \calC \cap \calB_{R}} \COST(\ALG,f,\varepsilon).
-\end{equation*}
-Note that while the cost depends on $\norm[\calF]{f}$, $\ALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
-It is common for $\COST(\ALG, \calC, \varepsilon,R)$ to be $\calO(\varepsilon^{-p})$, or perhaps asymptotically $c\log(1 + \varepsilon^{-1})$.
-
-Let $\calA(\calC)$ denote the set of all possible algorithms that may be constructed using series coefficients and that \emph{satisfy error criterion \eqref{DHKM:err_crit}}.
-We define the \emph{computational complexity} of a problem as the information cost of the best algorithm:
-\begin{equation*}
-    \COMP(\calA(\calC), \varepsilon,R) := \min_{\ALG \in \calA(\calC)} \COST(\ALG, \calC, \varepsilon,R) .
-\end{equation*}
-These definitions follow the information-based complexity literature \cite{TraWer98, TraWasWoz88}.
-We define an algorithm to be \emph{essentially optimal} if there exists some fixed positive $\omega$, $\varepsilon_{\max}$, and $R_{\min}$ for which
-\begin{multline} \label{DHKM:EssentialOpt}
-    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calA(\calC), \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
-\end{multline}
-If the complexity of the problem is $\calO(\varepsilon^{-p})$, the cost of an essentially optimal algorithm is also $\calO(\varepsilon^{-p})$.
-If the complexity of the problem is asymptotically $c \log(1 + \varepsilon^{-1})$, then  the cost of an essentially optimal algorithm is also asymptotically $c \log(1 + \varepsilon^{-1})$.
-We will show that our adaptive algorithms presented in Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}  are essentially optimal.
-
+We now show that this algorithm is optimal if the input set is a ball.
 \begin{theorem}\label{DHKM:thm_cost_non_adapt}
-The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$, which is given by
+The non-adaptive Algorithm \ref{DHKM:BallAlg} has an information cost for the set of input functions $\calC = \calB_R$ that is given by
 \[
@@
 
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
+\label{DHKM:pilot_sec} 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tractability}\label{DHKM:secTractability}
+\subsection{The Cone and the Optimal Algorithm}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-Besides understanding the dependence of the computational complexity on $\varepsilon$, we also want to understand how this quantity depends on the dimension of the domain of the input function.
+The premise of an adaptive algorithm is that the finite information we observe about the input function 
+tells us something about what is not observed.  Let $n_1$ denote the number of pilot observations, based on the set of wavenumbers
+\begin{equation} \label{DHKM:KOnedef}
+    \calK_1 := \{\bsk_1, \ldots, \bsk_{n_1} \},
+\end{equation}
+where the $\bsk_i$ are defined by the ordering of the $\lambda_{\bsk}$ in \eqref{DHKM:lambda_order}.  Let $A$ be some constant inflation factor greater than one.
+
+\DHKMchange{Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by}
+\begin{equation} \label{DHKM:pilot_cone}
+    \DHKMchange{\calC_{\boldsymbol{\lambda},A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
+\end{equation}
+
+Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.
+The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ allows us to bound these as follows:
+\begin{align*}
+     \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty} & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    \right]^{1/\rho} \qquad \forall f \in \calF \\
+    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}}.
+\end{align*}
+This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
+\begin{subequations} \label{DHKM:pilot_errbd}
+\begin{equation}
+\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}},
+\end{equation}
+where 
+\begin{multline}
+\ERRN \\
+    : =  
+    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
+    \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
+    \\ n \ge n_1.
+\end{multline}
+\end{subequations}
+This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
+This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ defined in \eqref{DHKM:pilot_cone}:
+
+\begin{algorithm}
+	\caption{$\ALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
+	\begin{algorithmic}
+	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:Refined_APP_err}
+		\INPUT a black-box function, $f$; an absolute error tolerance,
+		$\varepsilon>0$
+
+\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:pilot_cone}
+
+\State Let $n \leftarrow n_1 -1$
+\Repeat
+
+\State Let $n \leftarrow n + 1$
+
+\State Compute $\ERRN$ as defined in \eqref{DHKM:pilot_errbd}
+
+\Until $\ERRN \le \varepsilon$
+
+\RETURN $\ALG(f,\varepsilon) = \APP(f,n)$
+
+\end{algorithmic}
+\end{algorithm}
+
+\begin{theorem} \label{DHKM:PilotCostThm}
+Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ defined in \eqref{DHKM:pilot_cone}.
+The information cost is
+\begin{multline} \label{DHKM:PilotConeAlg_cost}
+    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},A}},\varepsilon,R) \\
+    = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
+\end{multline}
+There exist positive $\varepsilon_{\max}$ and $R_{\min}$ for which the computational complexity has the lower bound
+\begin{multline} \label{DHKM:PilotConeAlg_comp}
+        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
+    \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+\end{multline}
+Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}})$ contains only adaptive algorithms.
+\end{theorem}
+
+\begin{proof} 
+The upper bound on the computational cost of this algorithm is obtained by noting that 
+\begin{align*}
+    \MoveEqLeft[1]{\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},A}},\varepsilon,R)} \\
+    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
+     & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
+     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1 }} \, 
+     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
+    \le \varepsilon \right \} \\   
+     & \le \min \left \{n \ge n_1 : 
+     (A^\rho -1)^{1/\rho} R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
+    \le \varepsilon \right \},  
+\end{align*}
+since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
+Moreover, this inequality is tight for some $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
+This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.
+
+To prove the lower complexity bound, choose $\varepsilon_{\max}$ and $R_{\min}$ such that 
+\[
+\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n_1+1}^{\infty}} \,
+    > 2\varepsilon_{\max}/[(1 - 1/A) R_{\min}].
+    \]
+Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ in \eqref{DHKM:pilot_cone}.
+Fix $R \in [R_{\min},\infty)$ and $\varepsilon \in (0,\varepsilon_{\max}]$ arbitrarily.
+Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.
+
+The input function $f_1$ is defined via its series coefficients as in Lemma \ref{DHKM:Key_Lem}, having nonzero coefficients only for $\bsk \in \calK_1$:
+\begin{equation*}
+    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
+    0, & \bsk \notin \calK_1,
+    \end{cases}
+   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/A)}{2}.
+\end{equation*}
+Suppose that $\ALG'(f_1,\varepsilon)$ samples the series coefficients $\hf_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
+
+Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$ and also as in Lemma \ref{DHKM:Key_Lem}:
+\begin{gather}
+\nonumber
+    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
+    0, & \bsk \in \calJ, 
+    \end{cases}
+    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/A)}{2}, \\
+    \label{DHKM:SOLf2bd}
+    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
+\end{gather}
+Let $f_{\pm} = f_1 \pm f_2$.  By the definitions above, it follows that
+\begin{align}
+\nonumber
+    \norm[\calF]{f_{\pm}} &= \norm[\calF]{ f_1 \pm f_2 } \le \norm[\calF]{ f_1} + \norm[\calF]{ f_2 } =  R, \\
+    \nonumber
+    \norm[\rho]{\left( \frac{\hf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
+    & = \norm[\rho]{\left( \frac{\hf_1(\bsk_i) \pm \hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \nonumber
+    & \ge \norm[\rho]{\left( \frac{\hf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \nonumber
+    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{A} \ge \frac{\norm[\calF]{f_{\pm}}}{A}.
+\end{align}
+Therefore, $f_\pm \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}} \cap \calB_R$.
+Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.
+Thus, $\SOL(f_{+})$ must be quite similar to $\SOL(f_{-})$.
+
+Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
+\begin{align*}
+\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
+=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
+& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
++ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
+& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
+=\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
+& \ge \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
+\end{align*}
+by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.
+By the choice of $R_{\min}$ and $\varepsilon_{\max}$ above, it follows that $n > n_1$.
+This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
+Because $\lim_{R \to \infty} \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}}), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}})$ contains only adaptive algorithms.
+
+The essential optimality of Algorithm \ref{DHKM:PilotConeAlg} follows by observing that 
+\[
+\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},A}},\varepsilon,R) \le \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}}),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
+\]
+This satisfies definition \eqref{DHKM:EssentialOpt}.  
+\end{proof} \
+
+The above derivation assumes that $A > 1$.
+If $A =1$, then our cone consists of functions whose series coefficients vanish for wavenumbers outside $\calK_1$.
+The exact solution can be constructed using only the pilot sample.
+Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, which is an unbounded set.
+
+We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, but we may derive necessary conditions for $f$ to lie in $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$.
+The following proposition follows from the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.
+
+\YuhanNote{Should we delete Proposition 1 just keep Propostion 2?}
+\begin{proposition}
+If $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, then 
+\begin{equation} \label{DHKM:PilotConeNecessary}
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\DHKMchange{i =1}}^{n}} \le A
+    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
+\end{equation}
+\end{proposition}
+
+If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
+The remedy is to make $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.
+
+\DHKMchange{Let's consider an alternative cone, i.e.,
+\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \cf : \norm[\calF]{f} \le A'\norm[\calF']{f}\},\]
+where
+$\norm[\calF']{f} =\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}}$ and $\omega_{\bsk}$ decreases. 
+\begin{proposition}
+If there exists $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ such that
+\[\omega_{n_1} A'' \ge A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and} \qquad  \omega_{n_1+1}A' < 1, \]
+then 
+\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
+\subseteq 
+\calC_{\boldsymbol{\lambda}, A}
+\subseteq
+\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.\]
+\end{proposition}
+
+\begin{proof}
+Let's prove $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
+\subseteq 
+\calC_{\boldsymbol{\lambda}, A}$ at first.
+Suppose $f \in \calC_{\boldsymbol{\lambda}, A}$, then by definition, we have
+\begin{align*}
+    \norm[\calF]{f} &\le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk = 1} ^{ n_1}}
+     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk =1} ^{n_1}}
+     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
+\end{align*}
+Thus, if $A'' \ge A\omega_{n_1}^{-1}$, i.e. $\omega_{n_1} A'' \ge A $,
+we obtain $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.
+
+Next, we show the rest part.
+Suppose, $f \in \calC'_{\boldsymbol{\lambda},\boldsymbol{\omega},  A'}$, we have
+\begin{align*}
+    \norm[\calF']{f}^\rho- \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho 
+	& = \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho 
+     \le \omega_{n_1+1}^\rho \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
+     & = \omega_{n_1+1}^\rho \left[ \norm[\cf]{f}^\rho - \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
+     & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \norm[\calF']{f}^\rho - \omega_1^{-\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].
+\end{align*}
+Rearrange the terms, we obtain
+\begin{align*}
+\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \\
+ \iff	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
+\end{align*}
+Hence, if $A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and } \omega_{n_1+1}A' < 1,$
+we obtain $\calC_{\boldsymbol{\lambda}, A}
+\subseteq
+\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.$
+\end{proof}
+}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Tractability}\label{DHKM:SecPilotTract}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\DHKMchange{
+Besides understanding the dependence of $\COMP(\calA(\calC), \varepsilon,R)$ on $\varepsilon$, we also want to understand how $\COMP(\calA(\calC), \varepsilon,R)$ depends on the dimension of the domain of the input function.
 Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
-The cone of functions for which our algorithms succeed, $\calC_d$, depends on the dimension too.
+The set of functions for which our algorithms succeed, $\calC_d$, depends on the dimension, too.
 Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
@@
 Different dependencies of $\COMP(\calA(\calC_d), \varepsilon,R)$ on the dimension $d$ and the error tolerance $\varepsilon$ are formalized as different notions of tractability. Since 
-the complexity is defined in terms of the best available algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
+the complexity is defined in terms of the best algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
 We define the following notions of tractability (for further information on tractability we refer to the trilogy 
@@
 one would essentially replace $\varepsilon^{-1}$ 
-by $\log \varepsilon^{-1}$ in the previous tractability notions. A more detailed study of 
+by $\log (1 + \varepsilon^{-1})$ in the previous tractability notions. A more detailed study of 
 tractability will be done in a future paper.
 
-\subsection{The Illustrative Example Revisited}\label{DHKM:revisexamp}
 The example in Section \ref{DHKM:secexamp} chooses $\rho = \tau = 2$ and $\rho' = \infty$.  Thus, we obtain by Theorem \ref{DHKM:thm_cost_non_adapt}:
 \begin{align*}
-	\textup{COMP}(\calA(\calB_{R}),\varepsilon,R) &= \textup{COST}(ALG,\calB_{R},\varepsilon,R) 
+	\COMP(\calA(\calB_{R}),\varepsilon,R) &= \COST(\ALG,\calB_{R},\varepsilon,R) 
 	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \}.
 \end{align*}
-Using the non-increasing ordering of the $\lambda_{\bsk_i}$, we employ a standard technique for bounding the $n+1^\text{st}$ largest $\lambda_{\bsk}$ in terms of the sum of the $1/p^\text{th}$ power of all the $\lambda_{\bsk}$.
-For $0 < p < r$,
-\begin{align*}
-(n+1)\lambda_{\bsk_{n+1}}^{1/p} &\le \sum_{i=1}^{n+1}\lambda_{\bsk_{i}}^{1/p} \le \sum_{\bsk \in \bbN_0^d}\lambda_{\bsk}^{1/p} = \prod_{\ell =1}^d \left[1 + w_\ell^{1/p}\sum_{k = 1}^\infty \frac {1}{k^{r/p}} \right ] \\
-& =  \prod_{\ell =1}^d \left[1 + w_\ell^{1/p}\zeta(r/p)\right ] 
-= \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{1/p}\zeta(r/p) \bigr) \right) \\
-& \le \exp\left(\zeta(r/p) \sum_{\ell = 1}^{\infty} w_\ell^{1/p} \right) \qquad \text{since }\log(1+x) \le x \ \forall x\ge 0.
+Using the non-increasing ordering of the $\lambda_{\bsk_i}$, we employ a standard technique for bounding the $n+1^\text{st}$ largest $\lambda_{\bsk}$ in terms of the sum of the $p^\text{th}$ power of all the $\lambda_{\bsk}$.
+For $0  < 1/r < p$,
+\begin{align*}
+(n+1)\lambda_{\bsk_{n+1}}^{p} &\le \sum_{i=1}^{n+1}\lambda_{\bsk_{i}}^{p} \le \sum_{\bsk \in \bbN_0^d}\lambda_{\bsk}^{p} = \prod_{\ell =1}^d \left[1 + w_\ell^{p}\sum_{k = 1}^\infty \frac {1}{k^{pr}} \right ] \\
+& =  \prod_{\ell =1}^d \left[1 + w_\ell^{p}\zeta(pr)\right ] 
+= \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\zeta(pr) \bigr) \right) \\
+& \le \exp\left(\zeta(pr) \sum_{\ell = 1}^{\infty} w_\ell^{p} \right) \qquad \text{since }\log(1+x) \le x \ \forall x\ge 0.
 \end{align*}
@@
 \begin{align*}
-    \MoveEqLeft{\textup{COMP}(\calA(\calB_{R}),\varepsilon,R)} \\
-  &\le\min\left\{ n \in \N_0 : \frac{1}{n+1}\exp\left(\zeta(r/p) \sum_{\ell = 1}^\infty w_\ell^{1/p} \right)  \le \left( \frac{\varepsilon}{R} \right)^{1/p}  \right\} \\
-  &= \left \lceil \left( \frac{R}{\varepsilon} \right)^{1/p}  \exp\left(\zeta(r/p) \sum_{\ell = 1}^{\infty} w_\ell^{1/p} \right) \right \rceil - 1.
-\end{align*}
-
-If the $w_\ell$ decay quickly enough so that $\sum_{\ell = 1}^{\infty} w_\ell^{1/p}$ is finite, we obtain strong polynomial tractability and a complexity that is $\calO \bigl((R/\varepsilon)^{1/p} \bigr)$.
+    \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} \\
+  &\le\min\left\{ n \in \N_0 : \frac{1}{n+1}\exp\left(\zeta(pr) \sum_{\ell = 1}^\infty w_\ell^{p} \right)  \le \left( \frac{\varepsilon}{R} \right)^{p}  \right\} \\
+  &= \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(pr) \sum_{\ell = 1}^{\infty} w_\ell^{p} \right) \right \rceil - 1.
+\end{align*}
+
+If $p^\dagger$ is the infimum of the $p$ for which $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $p^* = \max(1/r,p^\dagger)$.
 On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Bounding the Norm of the Input Function Based on a Pilot Sample} 
-\label{DHKM:pilot_sec} 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Cone and the Optimal Algorithm}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The premise of an adaptive algorithm is that the finite information we observe about the input function 
-tells us something about what is not observed about the input function.  Let $n_1$ denote the number of pilot observations, based on the wavenumbers
-\begin{equation} \label{DHKM:KOnedef}
-    \calK_1 := \{\bsk_1, \ldots, \bsk_{n_1} \},
-\end{equation}
-where the $\bsk_i$ are given by the ordering of the $\lambda_{\bsk}$ in \eqref{DHKM:lambda_order}.
-Let $A$ be some constant inflation factor greater than one.
-The cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$,
-is given by
-\begin{equation} \label{DHKM:pilot_cone}
-    \calC = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
-\end{equation}
-
-Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.
-The definition of $\calC$ allows us to bound these as follows:
-\begin{align*}
-     \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty} & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
-    \right]^{1/\rho} \qquad \forall f \in \calF \\
-    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
-    \right]^{1/\rho} \quad \forall f \in \calC.
-\end{align*}
-This inequality together with error bound \eqref{DHKM:Refined_APP_err} implies the data-based error bound 
-\begin{subequations} \label{DHKM:pilot_errbd}
-\begin{equation}
-\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \calC,
-\end{equation}
-where 
-\begin{multline}
-\ERRN \\
-    : =  
-    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
-    \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
-    \\ n > n_1.
-\end{multline}
-\end{subequations}
-This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
-This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\calC$ defined in \eqref{DHKM:pilot_cone}:
-
-\begin{algorithm}
-	\caption{$\ALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
-	\begin{algorithmic}
-	\PARAM an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
-		\INPUT a black-box function, $f$; an absolute error tolerance,
-		$\varepsilon>0$
-
-\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:pilot_cone}
-
-\State Let $n \leftarrow 0$
-\Repeat
-
-\State Let $n \leftarrow n + 1$
-
-\State Compute $\ERRN$ as defined in \eqref{DHKM:pilot_errbd}
-
-\Until $\ERRN \le \varepsilon$
-
-\RETURN $\ALG(f,\varepsilon) = \APP(f,n)$
-
-\end{algorithmic}
-\end{algorithm}
-
-\begin{theorem} \label{DHKM:PilotCostThm}
-Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC)$ for $\calC$ defined in \eqref{DHKM:pilot_cone}.
-The information cost is
-\begin{multline} \label{DHKM:PilotConeAlg_cost}
-    \COST(\ALG,\calC,\varepsilon,R) \\
-    = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
-\end{multline}
-There exist positive $\varepsilon_{\max}$ and $R_{\min}$ for which the computational complexity has the lower bound
-\begin{multline} \label{DHKM:PilotConeAlg_comp}
-        \COMP(\calA(\calC),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
-    \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
-\end{multline}
-Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\calC)$ contains only adaptive algorithms.
-\end{theorem}
-
-\begin{proof} 
-The upper bound on the computational cost of this algorithm is obtained by noting that 
-\begin{align*}
-    \MoveEqLeft{\COST(\ALG,\calC,\varepsilon,R)} \\
-    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
-     & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1 }} \, 
-     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
-    \le \varepsilon \right \} \\   
-     & \le \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
-    \le \varepsilon \right \},  
-\end{align*}
-since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
-Moreover, this inequality is tight for some $f \in \calC \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
-This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.
-
-To prove the lower complexity bound, choose $\varepsilon_{\max}$ and $R_{\min}$ such that 
-\[
-\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n_1+1}^{\infty}} \,
-    > 2\varepsilon_{\max}/[(1 - 1/A) R_{\min}].
-    \]
-Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC$ in \eqref{DHKM:pilot_cone}.
-Fix $R \in [R_{\min},\infty)$ and $\varepsilon \in (0,\varepsilon_{\max}]$ arbitrarily.
-Two fooling functions will be constructed of the form $f_\pm = f_1 \pm f_2$.
-
-The input function $f_1$ is defined via its series coefficients as in Lemma \ref{DHKM:Key_Lem}, having nonzero coefficients only for $\bsk \in \calK_1$:
-\begin{equation*}
-    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
-    0, & \bsk \notin \calK_1,
-    \end{cases}
-   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/A)}{2}.
-\end{equation*}
-Suppose that $\ALG'(f_1,\varepsilon)$ samples the series coefficients $\hf_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
-
-Now, construct the input function $f_2$, having zero coefficients for $\bsk \in \calJ$ and also as in Lemma \ref{DHKM:Key_Lem}:
-\begin{gather}
-\nonumber
-    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
-    0, & \bsk \in \calJ, 
-    \end{cases}
-    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/A)}{2}, \\
-    \label{DHKM:SOLf2bd}
-    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
-\end{gather}
-Let $f_{\pm} = f_1 \pm f_2$.  By the definitions above, it follows that
-\begin{align}
-    \norm[\calF]{f_{\pm}} &= \norm[\calF]{ f_1 \pm f_2 } \le \norm[\calF]{ f_1} + \norm[\calF]{ f_2 } =  R, \\
-    \nonumber
-    \norm[\rho]{\left( \frac{\hf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
-    & = \norm[\rho]{\left( \frac{\hf_1(\bsk_i) \pm \hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
-    \nonumber
-    & \ge \norm[\rho]{\left( \frac{\hf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
-    \nonumber
-    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{A} \\
-    & \ge \frac{\norm[\calF]{f_{\pm}}}{A}.
-\end{align}
-Therefore, $f_\pm \in \calC \cap \calB_R$.
-Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.
-Thus, $\SOL(f_{\pm})$ must be similar to each other.
-
-Using an argument like that in the proof of  Theorem \ref{DHKM:APP_optimality_thm}, it follows that 
-\begin{align*}
-\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
-=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
-& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
-+ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
-& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
-=\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
-& \ge \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
-\end{align*}
-by the ordering of the $\bsk$ in \eqref{DHKM:lambda_order}.
-By the choice of $R_{\min}$ and $\varepsilon_{\max}$ above, it follows that $n > n_1$.
-This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
-Because $\lim_{R \to \infty} \COMP(\calA(\calC), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\calC)$ contains only adaptive algorithms.
-
-The essential optimality of Algorithm \ref{DHKM:PilotConeAlg} follows by observing that 
-\[
-\COST(\ALG,\calC,\varepsilon,R) \le \COMP(\calA(\calC),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
-\]
-This satisfies definition \eqref{DHKM:EssentialOpt}.  
-\end{proof} \
-
-The above derivation assumes that $A > 1$.
-If $A =1$, then our cone consists of functions whose series coefficients vanish for wavenumbers outside $\calK_1$.
-The exact solution can be constructed using only the pilot sample.
-Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\calC$, which is an unbounded set.
-
-We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC$, but we may derive necessary conditions for $f$ to lie in $\calC$.
-The following proposition follows from the definition of $\calC$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.
-
-\begin{proposition}
-If $f \in \calC$, then 
-\begin{equation} \label{DHKM:PilotConeNecessary}
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\bsk_i =1}^{n}} \le A
-    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
-\end{equation}
-\end{proposition}
-
-If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \calC$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
-The remedy is to make $\calC$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Tractability}\label{DHKM:SecPilotTract}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\FredNote{
-
-In this section, we write $\calC_d$ instead of $\calC$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
+}
+
+In this section, we write $\calC_d$ instead of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
 Recall that we assume that
@@
 From the equation above, it is clear that tractability depends on the behavior of $n(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity.
-We would like to study under which conditions we obtain the various tractability notions defined in Section \ref{DHKM:secTractability}.
+We would like to study under which conditions we obtain the various tractability notions defined above
 
@@
 
-}
-
-\iffalse
-
-From 
-Equations \eqref{DHKM:PilotConeAlg_cost} and \eqref{DHKM:PilotConeAlg_comp}, we obtain that 
-\[
-        \COMP(\calA(\calC_d),\varepsilon,R)  \asymp \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le D_A\,  \varepsilon/R\, \right \},
-\]
-where $D_A$ is a positive constant that may depend on $A$, but does not depend on $d$, $\varepsilon$, and $R$.
-We would like to study under which conditions we obtain the various tractability notions defined in Section \ref{DHKM:secTractability}.
-
-Since $\lambda_{d,\bsk_i}>0$, and since we are interested in the asymptotic behavior 
-of $\COMP(\calA(\calC_d),\varepsilon,R)$ when $d$ and/or $\varepsilon^{-1}$ tend to infinity, it is sufficient to consider the quantity 
-\[
-n(\varepsilon,d)=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \varepsilon/R \right \}\,\asymp\,\COMP(\calA(\calC_d),\varepsilon,R) ,
-\]
-for $\varepsilon \in (0,1)$ and $d\in\NN$, where the implied constant may depend on $a$.
-To this end, we distinguish two cases, depending on whether $\rho'$ is infinite or not. This 
-distinction is useful because it allows us to relate the computational complexity of the algorithms 
-considered in this chapter to the computational complexity of linear problems on certain function spaces considered in the classical literature on information-based complexity, as for example \cite{NovWoz08a}.
-The case $\rho'=\infty$ corresponds to the
-worst-case setting, where one studies the worst performance of an algorithm over the unit ball of 
-a space. The results in Theorem \ref{DHKM:thmtract1} below are indeed very similar to the results 
-for the worst-case setting over balls of suitable function spaces. The case $\rho<\infty$ corresponds to the so-called average-case setting, where one 
-considers the average performance over a function space equipped with a suitable measure. 
-For both of these settings there exist tractability results that we will make use of here.
-\fi
-
-\PeterNote{I added a sentence for $\rho'=\infty$ regarding similarities to the 
-case of balls in the worst-case setting. For $\rho'<\infty$ it does not make sense to speak of 
-balls, because this case is related to the average case setting, where one considers the average 
-over the whole space.}
-
 \paragraph*{CASE 1: $\rho'=\infty$:}
@@
 \[
-\FredNote{n(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
-    \le \varepsilon/R \right \}}.
+n(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
+    \le \varepsilon/R \right \}.
 \]
@@
 
-\FredNote{In this case, letting $\widetilde{\varepsilon}:=(\varepsilon/R)^{\rho'/2}$ and 
+In this case, letting $\widetilde{\varepsilon}:=(\varepsilon/R)^{\rho'/2}$ and 
 $\widetilde{\lambda}_{d,i}:=\lambda_{d,\bsk_i}^{\rho'}$, we have 
@@
 \end{align}
-}However, the latter expression corresponds exactly to the 
+However, the latter expression corresponds exactly to the 
 average-case tractability (with respect to the parameters 
@@
 
-\YuhanNote{\FredNote{
-To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of \emph{coordinate weights}, $w_1, \ldots, w_d$, and \emph{smoothness weights}, $s_1, s_2, \ldots$:
+To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of positive \emph{coordinate weights}, $w_1, \ldots, w_d$, and positive \emph{smoothness weights}, $s_1, s_2, \ldots$:
 \begin{equation}
@@
 \end{equation}
-This is a generalization of what was considered in Section \ref{DHKM:secexamp}, where $s_{k} = k^{-r}$.
-This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance}.
-The same argument as in Section \ref{DHKM:revisexamp} implies that
-\[\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} \le \exp\left(\sum_{k=1}^\infty s_k^\eta \sum_{\ell = 1}^{d} w_\ell^{\eta} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^\eta \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right).
+This is a generalization of the example in Section \ref{DHKM:secexamp}, where $s_{k} = k^{-r}$.
+This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.
+The same argument as \DHKMchange{stated above} implies that the sum of the $\lambda_{d,\bsk_i}^\eta$ is bounded above as
+\[
+\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} \le \exp\left(\sum_{k=1}^\infty s_k^\eta \sum_{\ell = 1}^{d} w_\ell^{\eta} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^\eta \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right).
 \]
-Thus, we have
+Moreover, it also follows that for any fixed positive integer $i_0$, the sum of the $\lambda_{d,\bsk_i}^\eta$ is bounded below as
+\begin{align*}
+    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge w_1^\eta \sum_{\DHKMchange{i=i_0}}^{\infty}s_{\DHKMchange{k_i}}^{\eta} \qquad \parbox{8cm}{considering only $\bsk_i$ of the form $(k, 0, 0, \ldots, 0)$, \\
+    and ordering $\bss$ so that $\DHKMchange{s_{k_1} \ge s_{k_2} \ge \cdots}$,} \\
+    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge  s_{1}^{\eta} \sum_{i=i_0}^{\infty} w_{\ell_i}^\eta
+    %\qquad %\text{for } d \ge i_0 
+    %\\ &
+    \qquad \parbox{8cm}{considering only $\bsk_i$ of the form\\  $(0, \ldots, 0,1,0 , \ldots, 0)$,
+    where the non-zero\\ component is at the $\ell$-th   position with 
+    $i_0\le \ell \le d$,\\ and ordering $\bsw$  so that $w_{\ell_1} \ge w_{\ell_2} \ge \cdots$.}
+\end{align*}
+Thus, we have necessary and sufficient conditions for strong tractability.
 \begin{corollary} \label{DHKM:sptexample_cor}
-For the $\lambda_{d,\bsk}$ of the form \eqref{DHKM:prodwts} we have strong polynomial tractability if there exists $\eta>0$ such that
- \begin{equation}
-\label{DHKM:sptexample}
+For the $\lambda_{d,\bsk}$ of the form \eqref{DHKM:prodwts} we have strong polynomial tractability if and only if there exists $\eta>0$ such that
+ \begin{equation*}
+%\label{DHKM:sptexample}
     \sum_{k=1}^\infty s_{k}^\eta < \infty \text{ and } 
     \sum_{\ell = 1}^{\infty} w_\ell^{\eta} < \infty.
-\end{equation}
+\end{equation*}
+\DHKMchange{In particular, considering example in Section \ref{DHKM:secexamp}, where $s_{k} = k^{-r}$, we have strong polynomial tractability if and only if there exists $\eta> 0 $ such that
+\begin{equation*}
+%\label{DHKM:sptexample}
+   r \eta > 1 \text{ and } 
+    \sum_{\ell = 1}^{\infty} w_\ell^{\eta} < \infty.
+\end{equation*}}
 \end{corollary}
-\textbf{I don't know if we can get if and only if.  Yuhan and Peter please check.}}}
-
-\PeterNote{For $d=1$, we need $\sum_{i=1}^\infty \lambda_{1,k_i}^\eta$ to be finite. But is not 
-$\sum_{i=1}^\infty \lambda_{1,k_i}^\eta=w_1\sum_{k=1}^\infty s_k^\eta$ ? If I am right, this shows that 
-$\sum_{k=1}^\infty s_k^\eta<\infty$ is necessary. I am not sure if the second condition is necessary. 
-Need some time to think.}
-
-\FredNote{Yes, I think that you are correct.  If we assume that $s_1>1$, then we may be able to show that the condition on the coordinate weights is necessary.}
-
-\FredNote{
 
@@
 \end{remark}
-
-}
 
@@
 The algorithm presented in this section tracks the rate of decay of the $\hf(\bsk_i)$ and terminates sooner if the $\hf(\bsk_i)$ decay more quickly.
+Similar algorithms for quasi-Monte Carlo integration are developed in \cite{HicJim16a}, \cite{JimHic16a}, and \cite{HicEtal17a}.
+
+There is an implicit assumption in this section that function data are cheap and we can afford a large sample size.
+A large sample size is required to do meaningful tracking of the decay of the series coefficients.
+The previous section and the next section are more suited to the case when function data are expensive and the final sample size must be modest.
 
@@
 Define the sets of wavenumbers analogously to \eqref{DHKM:KOnedef},
-\begin{equation}
+\begin{equation*}
    n_{-1}=0, \qquad \calK_j := \{\bsk_{n_{j-1}+1}, \ldots, \bsk_{n_j}\} \quad \text{for } j \in \N_0.
-\end{equation}
+\end{equation*}
 If $n_0 = 0$, then $\calK_0$ is empty.  For any $f \in \calF$, define the norms of subsets of series coefficients:
@@
 
-For this section, we define the cone of input functions, $\calC$, by
+\DHKMchange{As stated above, we would like to keep track of the rate of decay of the $\hf(\bsk_i)$. Hence, for this section, we define the cone of input functions by}
 \begin{equation} \label{DHKM:TrackConeDef}
-  \calC : =\left\{f\in\calF \colon \sigma_{j+r} (f)\le ab^r \sigma_j (f)\ \forall j,r\in\NN\right\}.
+  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} : =\left\{f\in\calF \colon \sigma_{j+r} (f)\le ab^r \sigma_j (f)\ \forall j,r\in\NN\right\}.
 \end{equation}
 Here, $a$ and $b$ are positive reals with $b< 1 < a$.
-The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in \calC$.
+The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $.
 Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
 However, we expect their partial sums to decay steadily.
-The series coefficients for  wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\calC$ and may behave erratically.
+The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ and may behave erratically.
 Lemma \ref{DHKM:Key_Lem} implies that 
@@
 
-If $f$ belongs to the $\calC$ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
+If $f$ belongs to the $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
 \begin{align*}
@@
 \end{align*}
-Comparing this inequality to the definition of $\calC$ in the previous section, it can be seen that  $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone} if we choose
+Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},A}} $defined in \eqref{DHKM:pilot_cone} if we choose
 $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
 
-From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \calC$ and $j \in \bbN$:
+From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ and $j \in \bbN$:
 \begin{align}
@@
 These assumptions accommodate both the cases where the approximation converges algebraically and exponentially.
-To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \calO(i^{-r_\Delta})$ for some positive $r_\Delta > 1/\rho$.
-For this algebraic case one would normally define $\calC$ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
+To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \DHKMchange{\Theta(i^{-r_\Delta})}$ for some positive $r_\Delta > 1/\rho$.
+For this algebraic case one would normally define $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
 \begin{align*}
     \sigma_j(f) &= \left[ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
-    = \calO \left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
-    & = \calO \left(  2^{-j(r_\Delta-1/\rho)} \right).
+    = \DHKMchange{\Theta}\left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
+    & =\DHKMchange{\Theta}\left(  2^{-j(r_\Delta-1/\rho)} \right).
 \end{align*}
@@
 for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\calC$ to include such functions.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ to include such functions.
 Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
 
-To illustrate the exponential case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \calO(\E^{-r_\Delta i})$.
+To illustrate the exponential case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \DHKMchange{\Theta}(\E^{-r_\Delta i})$.
 For this exponential case one would normally define $\calC$ in terms of an arithmetic sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 + j s$, where $s$ is a positive integer.
@@
     \sigma_j(f) &= \left[ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
-    = \calO \left( \left [ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
-    & = \calO \left(  \E^{-j r_{\Delta} s} \right).
+    = \DHKMchange{\Theta} \left( \left [ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
+    & = \DHKMchange{\Theta} \left(  \E^{-j r_{\Delta} s} \right).
 \end{align*}
@@
 for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} s}$ causes the cone $\calC$ to include such functions.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} s}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ to include such functions.
 Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
@@
 
-The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\calC$ defined in \eqref{DHKM:TrackConeDef}.
+The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
 The following theorem establishes its viability and computational cost.
@@
 	\begin{algorithmic}
-	\PARAM a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0}$; an inflation factor, $a$; the general decay rate, $b$; $\APP$ satisfying \eqref{DHKM:APP_Err_Coef}
+	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0}$; an inflation factor, $a$; the general decay rate, $b$; $\APP$ satisfying \eqref{DHKM:APP_Err_Coef}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 \begin{theorem}\label{DHKM:TractConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC)$ for $\calC$ defined in \eqref{DHKM:TrackConeDef}.
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
 The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
@@
 \end{equation}
-Moreover, $\COST(\ALG,\calC,\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
 \begin{equation} \label{DHKM:TractConejdagger}
@@
 
-For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.  For any $f \in  \calC \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
+For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
+For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
 \begin{align*}
@@
 
-The following theorem establishes a lower bound on the complexity of our problem for input functions in $\calC$.
+The following theorem establishes a lower bound on the complexity of our problem for input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$.
 The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TractConeCompCost} is essentially no worse than this lower bound.
@@
  %\label{compbdA}
-&\COMP(\calA(\calC),\varepsilon,R) > n_{j^\ddagger}, 
+&\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}),\varepsilon,R) > n_{j^\ddagger}, 
 \intertext{where}
@@
 As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
-We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC \cap \calB_{R}$, which yield the same approximate solution but different true solutions.
-This leads to a lower bound on $\COMP(\calA(\calC),\varepsilon,R)$.
+We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}\cap \calB_{R}$, which yield the same approximate solution but different true solutions.
+This leads to a lower bound on $\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}),\varepsilon,R)$.
 The proof is provided for $\rho' < \infty$.
@@
 
-The first test function $f_1 \in \calC$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
+The first test function $f_1 \in \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
 \begin{align}
@@
 \end{align}
-It can be verified that the test function lies both in $\calB_{R}$ and in $\calC$:
+It can be verified that the test function lies both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$:
 \begin{align}
@@
 
-Now let $\ALG'$ be an arbitrary algorithm in $\calA(\calC)$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
+Now let $\ALG'$ be an arbitrary algorithm in $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}})$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
 Let $\tcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
@@
 Furthermore, define $f_{\pm} = f_1 \pm f_2$.
-It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\calC$:
+It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$:
 \begin{align}
@@
 \end{equation*}
-If any algorithm satisfies the error tolerance $\varepsilon$ for all input functions in $\calC \cap \calB_R$ and has information cost no greater than $n_{j^\star}$, then $j^\star$ must satisfy the above inequality.
+If any algorithm satisfies the error tolerance $\varepsilon$ for all input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} \cap \calB_R$ and has information cost no greater than $n_{j^\star}$, then $j^\star$ must satisfy the above inequality.
 By contrast, if the above inequality is violated for any $j^\star$, then the information cost of the successful algorithm must be greater than $n_{j^\star}$.
@@
 Let $j^\dagger(\varepsilon)$ be defined as in \eqref{DHKM:TractConejdagger}, with the $\varepsilon$ dependence made explicit.
-\FredNote{Choose $\varepsilon_{\max}$ and $R_{\min}$ in \eqref{DHKM:EssentialOpt} such that $j^\dagger(\varepsilon) \ge 2$.}  This definition implies that
+Choose $\varepsilon_{\max}$ and $R_{\min}$ in \eqref{DHKM:EssentialOpt} such that $j^\dagger(\varepsilon) \ge 2$.
+This definition implies that
 
@@
 \[
-\COST(\ALG,\calC,\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calA(\calC),\omega \varepsilon,R).
+\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}),\omega \varepsilon,R).
 \]
@@
 \begin{proof}
-As pointed out above, $\calC$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
-This means that the approximation problem on  $\calC$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\calC$ defined in \eqref{DHKM:pilot_cone}.
+As pointed out above, $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
+This means that the approximation problem on  $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:pilot_cone}.
 This, however, implies that all sufficient conditions in Theorem \ref{DHKM:thmtract1} are also sufficient in the case considered in Theorem \ref{DHKM:thmtract3}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Inferring Coordinate and Smoothness Importance} \label{DHKM:smoothimportance}
+\section{Inferring Coordinate and Smoothness Importance} \label{DHKM:smoothimportance_sec}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec} the $\lambda_{\bsk}$, which appear in the definition of the cone of inputs, $\calC$ are taken as given.
-These may take the form suggested in \eqref{DHKM:prodwts}, which define the $\bsk$ in terms of coordinate weights and smoothness weights.
-However, practically speaking it may be difficulty to know a priori the values of these weights.
-This section explores a situation where the initial data collected for the input function data can be used to learn the $\lambda_{\bsk}$, inferring which input variables in $f$ may be more important and the smoothness of the function.
+In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}, the weights $\bslambda = (\lambda_{\bsk})_{\bsk \in \bbK}$, which appear in the definition of the cone of inputs, $\calC_{\bslambda,A}$, are taken as given and fixed.
+One may assume the form suggested in \eqref{DHKM:prodwts}, which defines $\bslambda$ in terms of coordinate weights and smoothness weights.
+However, practically speaking it may be difficult to know a priori the values of these weights.
+This section explores a situation where the initial data collected for the input function data can be used to learn $\bslambda$, inferring which input variables in $f$ may be more important and the smoothness of the function.
 
 The motivation for this section is situations where the relative importance of the $d$ input variables of the function is not known from physical considerations.
-We also envision the situation where the cost of function data is large, e.g., the result of an expensive computer simulation.
-Thus, we are not concerned with the cost of algorithm beyond the information cost, which we hope to limit to $\calO(d)$.
+We also envision situations where the cost of function data is large, e.g., the result of an expensive computer simulation.
+Thus, we are not concerned with the cost of the algorithm beyond the information cost, which we hope to limit to $\calO(d)$.
 
@@
 \lambda_{\bsk} = \Gamma_{\|\bsk\|_0} \prod_{\substack{\ell=1\\ k_\ell>0}}^d w_\ell s_{k_\ell}, \quad \Gamma_0 = s_1 = 1, \quad \bsk \in \mathbb{N}_0^d,
-\label{eq:posd}
+\label{DHKM:posdeq}
 \end{equation}
@@
     \item Coordinate weights quantify the importance for the $d$ input variables in $f$.
-    \item Smoothness weights quantify the importance of the $\tu_k$.  E.g., if the $\tu_k$ is a polynomial  of degree $k$, then the faster the $s_k$ decay, the smoother $f$ is.  
-    \item Order weights quantify the importance of effects with different orders; $\bsk$ having one nonzero element corresponds to a first-order or main effect, $bsk$ having two nonzero elements corresponds to a second-order (interaction) effect.
-(e.g., first-order, second-order)
-\end{itemize}
+    \item Smoothness weights quantify the importance of the $\tu_k$.
+E.g., if the $\tu_k$ are polynomials of degree $k$ as in Section \ref{DHKM:secexamp}, then the faster the $s_k$ decay, the smoother $f$ is.
+    \item Order weights quantify the importance of effects with different orders; $\bsk$ having one nonzero element corresponds to a first-order or main effect, $\bsk$ having two nonzero elements corresponds to a second-order (interaction) effect.
+(e.g., first-order, second-order).
+\end{itemize} \ \vspace{-4ex}
 
@@
 \begin{itemize}
-\item \emph{Effect sparsity} assumes that only a small number of inputs in $f$ are important.
-In \eqref{eq:posd}, this sparsity is accounted for by allowing only a small number of product weights $\bsw$ to be large.
-This principle arose in the sufficient condition for strong tractability in Corollary \ref{DHKM:sptexample_cor}.
+\item \emph{Effect sparsity} assumes that only a small number of \DHKMchange{coordinates in} $f$ are important.
+In \eqref{DHKM:posdeq}, this sparsity means that only a small number of product weights $\bsw$ are large.
+This principle arises in the sufficient condition for strong tractability in Corollary \ref{DHKM:sptexample_cor}.
 \item \emph{Effect heredity} assumes that lower-order effects are more important than higher-order effects.
 E.g., $\lambda_{(1,0, 0,\ldots, 0)}$ should be larger than $\lambda_{(1, 1, 0, \ldots, 0)}$.
-In \eqref{eq:posd}, this heredity can be enforced by letting order weights $\Gamma_{m}$ be decreasing in $m$.
+In \eqref{DHKM:posdeq}, this heredity can be enforced by assuming that the order weights $\Gamma_{m}$ decrease with $m$.
 \item \emph{Effect hierarchy} assumes that an effect is active \emph{only} when all its component effects are active.
 For example, $\lambda_{(1, 1, 0, \ldots, 0)} > 0$ only when $\lambda_{(1, 0, 0, \ldots, 0)}$ and $\lambda_{(0, 1, 0, \ldots, 0)}$ are both nonzero.
-This hierarchy is implicitly enforced within the product structure of the weights in \eqref{eq:posd}.
+This hierarchy is implicitly enforced by the product structure of the weights in \eqref{DHKM:posdeq}.
 \item \emph{Effect smoothness} assumes that lower-degree effects are more important than higher-degree effects.
 For example, when the $(\tu_k)_{k \in \mathbb{N}_0}$ are polynomials, this means that linear effects are more important than quadratic effects, which are in turn more significant than cubic effects, and so on.
-Effect smoothness can be imposed by setting $\bss$ to be a decreasing sequence.
+Effect smoothness can be imposed by assuming $\bss$ to be a decreasing sequence.
 \end{itemize} 
-
-The $\lambda_{\bsk}$ defined in \eqref{eq:posd} are called product, order and smoothness dependent (POSD) weights.
-From a quasi-Monte Carlo (QMC) perspective, the POSD weights in \eqref{eq:posd} generalize upon the product-and-order dependent (POD) weights in \cite{KuoEtal12a}, which were introduced for analyzing QMC methods in partial differential equations with random coefficients.
+\vspace{-3ex}
+\DHKMchange{These principles will guide the inference of weights $\bslambda$ (and its corresponding cone of inputs $\calC_{\bslambda,A}$) from initial data.}
+
+\hspace{\parindent} The $\lambda_{\bsk}$ defined in \eqref{DHKM:posdeq} are called product, order and smoothness dependent (POSD) weights.
+From a quasi-Monte Carlo (QMC) perspective, the POSD weights in \eqref{DHKM:posdeq} generalize upon the product-and-order dependent (POD) weights in \cite{KuoEtal12a}, which were introduced for analyzing QMC methods in partial differential equations with random coefficients.
 The latter POD weights can be recovered by ignoring the smoothness weights.
+
 Our POSD weights differ from the smoothness-driven product-and-order dependent (SPOD) weights in \cite{Dea2014}, which were recently used to analyze higher-order QMC methods for stochastic partial differential equations.
 These SPOD weights take the form:
-\begin{equation}
-\gamma_{\fraku} = \sum_{\bsk \in \{1:\alpha\}^{|\fraku|}} \|\bsk\|_1 !
-\prod_{l \in \fraku} \left( 2^{\delta(k_\ell,\alpha)} w_\ell^{k_\ell} \right), \quad \|\bsk\|_1 = \sum_{l=1}^d k_\ell, \quad \fraku \in \{0, 1\}^d.
-\label{eq:spod}
-\end{equation}
-Intuitively, the SPOD weights in \eqref{eq:spod} quantify the importance of each \textit{subspace} (indexed by $\fraku$), under a common smoothness structure between subspaces.
-In contrast, the proposed POSD weights in \eqref{eq:posd} instead quantify the importance of each \textit{Fourier coefficient} in $f$ (indexed by $\bsk$), under a common smoothness structure between coefficients.
+\begin{equation*}
+\gamma_{\fraku} = \sum_{\bsk \in \{1, \ldots, \alpha\}^{|\fraku|}} \|\bsk\|_1 !
+\prod_{\ell \in \fraku} \left( 2^{\delta(k_\ell,\alpha)} w_\ell^{k_\ell} \right), \quad \|\bsk\|_1 = \sum_{l=1}^d k_\ell, \quad \fraku \subseteq \{1, \ldots, d\},
+%\label{eq:spod}
+\end{equation*}
+where $\delta (k_\ell,\alpha)$ is 1 if $k_\ell=\alpha$ and 0 otherwise. 
+Intuitively, the SPOD weights quantify the importance of each \textit{subspace} (indexed by $\fraku$), under a common smoothness structure among subspaces (for further details on SPOD weights, we refer the reader to \cite{Dea2014}).
+In contrast, the proposed POSD weights in \eqref{DHKM:posdeq} instead quantify the importance of each \textit{Fourier series coefficient} $\hf(\bsk)$ (indexed by $\bsk$), under a common smoothness structure among coefficients.
 
@@
 
-Let $\calC_{\bslambda}$ denote the cone of inputs defined in \eqref{DHKM:pilot_cone} by POSD weights $\bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}$.
-As mentioned above, our goal here is to infer $\bslambda$ from input function data.
-We start with an initial set of wavenumbers:
+%Let $\calC_{\bslambda}$ denote the cone of inputs defined in \eqref{DHKM:pilot_cone} by POSD weights $\bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}$.
+As mentioned above, our goal here is to infer $\bslambda$ from input function data.  We start with an initial set of wavenumbers:
 \begin{equation} \label{DHKM:barKdef}
-    \bcalK= \{ (0, \ldots, 0, k, 0, \ldots, 0): k = 0, \ldots, k_{\max}\}.
-\end{equation}
-The approximation to $f$ based on sampling the series coefficients for these wavenumbers is
+    \bcalK= \{ (0, \ldots, 0, k, 0, \ldots, 0): k = 0, \ldots, k_{\max}\},
+\end{equation}
+\DHKMchange{where the only non-zero entry $k$ may be at any position in the vector}. The approximation to $f$ based on sampling the series coefficients for these wavenumbers is
 \begin{equation*}
@@
 \end{equation*}
-We choose the $\calC_{\bslambda}$ that best fits $f$ by selecting $\bslambda$ to make the norm of  $f_{\text{app}}$ small:
+\DHKMchange{To choose the cone $\calC_{\bslambda,A}$ which best fits $f$, we select the POSD weights $\bslambda$ to make the norm of $f_{\text{app}}$ small. These weights can be written as:}
 \begin{multline}
-\bar{\bslambda} = \bslambda(\bar{\bsw}, \bar{\bss}, \bsGamma) \\
+\bar{\bslambda} = \bslambda(\bar{\bsw}, \bar{\bss}, \bsGamma), \\
 \text{where } (\bar{\bsw}, \bar{\bss} ) = \min \left\{ \argmin_{(\bsw,\bss) \in \calW \times \calS} \left\|\left( \frac{\hf(\bsk)}{\lambda_{\bsk}(\bsw,\bss,\bsGamma)} \right)_{\bsk \in \bar{\calK}}\right\|_{\rho} \right \}.
@@
 Here, $\calW$ is a candidate set for coordinate weights, e.g., $\calW = [0,w^*]^d$, and $\calS$ is a candidate set for the smoothness weights, e.g., $\calS = \{(1/k^r)_{k=1}^{\infty} \colon r > 0\}$.
-The inner minimization finds the $(\bsw,\bss)$ that minimize the approximate norm of the input function.
+The inner minimization finds the $(\bsw,\bss)$ that minimizes the approximate norm of the input function.
 This minimizer may be non-unique, so the outer minimization chooses the smallest such $(\bsw,\bss)$.
@@
 The cardinality of the initial set of wavenumbers is $d k_{\max} + 1$.
-There is a trade-off between reducing cost by keeping $k_{\max}$ small enough and ensuring robustness by making $k_{\max}$ large enough.
+There is a trade-off between keeping $k_{\max}$ small enough to reducing cost and making $k_{\max}$ large enough to ensuring robustness.
 
@@
 
-Algorithm \ref{DHKM:InfPilotConeAlg} combines the construction of data-inferred POSD weights, $\bar{\bslambda}$ with Algorithm \ref{DHKM:PilotConeAlg}.
+Algorithm \ref{DHKM:InfPilotConeAlg} combines the construction of data-inferred POSD weights, $\bar{\bslambda}$, with Algorithm \ref{DHKM:PilotConeAlg} of Section \ref{DHKM:pilot_sec}.
 This algorithm succeeds for input functions in the cone
 \begin{equation} \label{DHKM:pilot_cone2}
-    \bar{\calC} := \left \{ f \in \calF : f \in \calC_{\bar{\bslambda}} \text{ for } \bar{\bslambda} \text{ defined in \eqref{DHKM:eq:inf}} \right\}.
-\end{equation}
-The reason that $\bar{\calC}$ is a cone is that the data-inferred $\bar{\bslambda}$ for the input function $f$ is exactly the same as for the input function $cf$, where $c$ is any constant.
+     \DHKMchange{\bar{\calC}_{A}} := \left \{ f \in \calF : f \in \DHKMchange{\calC_{\bar{\bslambda},A}} \text{ for } \bar{\bslambda} \text{ defined in \eqref{DHKM:eq:inf}} \right\}.
+\end{equation}
+The reason that \DHKMchange{$\bar{\calC}_A$} is a cone is that the data-inferred $\bar{\bslambda}$ for the input function $f$ is exactly the same as for the input function $cf$, where $c$ is any constant.
 
@@
 	\begin{algorithmic}
-	\PARAM candidate sets $\calW$ and $\calC$; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}; 
+	\PARAM the bases $\{u_{\bsk}\}_{\bsk \in \N_0^d}$ and $\{v_{\bsk}\}_{\bsk \in \N_0^d}$; candidate sets $\calW$ and $\calS$ \DHKMchange{for product and smoothness weights}; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:Refined_APP_err}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 \State Evaluate initial sample $\bigl\{\hf(\bsk)\bigr\}_{\bsk \in \bcalK}$
-\State Compute data-driven POSD weights, $\bar{\bslambda}$ according to \eqref{DHKM:eq:inf}
-\State Using these weights, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\ALG(f,\varepsilon)$
+\State Compute data-driven POSD weight $\bar{\bslambda}$\DHKMchange{, by iteratively optimizing over $\bsw \in \calW$ and $\bss \in \calS$ in \eqref{DHKM:eq:inf} until convergence}
+\State Using these weights, $\bar{\bslambda}$, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\ALG(f,\varepsilon)$
 \RETURN $\ALG(f,\varepsilon)$
@@
 
-\FredNote{Fred is here}
-
-\subsection{Numerical Examples}
+\subsection{Numerical Examples} \label{DHKM:numexamp_sec}
 
@@
 For simplicity, only the case of $\rho = \infty$ and $\rho' = \tau = 1$ is considered in the following examples.
-Here, the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d$ are Chebyshev polynomials, and the solution operator is $\SOL (f) = f$ (i.e., function approximation).
-We note that $\|f - \APP(f)\|_\infty$ is bounded above by $\|f - \APP(f)\|_\calG$, so the worst-case approximation error $\|f - \APP(f)\|_\infty$ should satisfy the desired error tolerance $\varepsilon$ by \eqref{DHKM:err_crit}.
+Here, the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are Chebyshev polynomials in Section \ref{DHKM:secexamp}, and the solution operator is $\SOL (f) = f$ (i.e., function approximation).
+We note that $\|f - \ALG(f,\varepsilon)\|_\infty \le \|f - \ALG(f,\varepsilon)\|_\calG$, so our error criterion \eqref{DHKM:err_crit} implies that $\|f - \ALG(f,\varepsilon)\|_\infty \le \varepsilon$.
 
 The simulation set-up is as follows. The Fourier coefficients for input function $f$, $\{\hat{f}(\bsk)\}_{\bsk \in \mathbb{N}_0^d}$, are randomly sampled as:
-\begin{equation}
-\hat{f}(\bsk) = Z_{\bsk} \left( {\Gamma}_{\|\bsk\|_0}^{\rm tr} \prod_{\substack{l=1\\ k_\ell>0}}^d {w_\ell^{\rm tr}} {s}_{k_\ell}^{\rm tr} \right), \quad Z_{\bsk} \overset{i.i.d.}{\sim} \text{Unif}[-1, 1], \quad \bsk \in \mathbb{N}_0^d.
-\label{eq:foursim}
-\end{equation}
-Here, $(w_\ell^{\rm tr})_{l=1}^d = (1/l^2)_{l=1}^d$, $({\Gamma_k^{\rm tr}})_{k=1}^\infty \equiv 1$ and $(s_j^{\rm tr})_{j=1}^{k_{\rm max}} = (1/j^4)_{j=1}^4$ are the true product, order and smoothness weights of $f$, and $Z_{\bsk}$ randomly sets the magnitude and sign of each coefficient.
-Product weights are also randomized in terms of variable order, to ensure that the order of input variables does not necessarily reflect the order of variable importance.
-We also set $\boldsymbol{\Gamma}$ in Algorithm \ref{DHKM:InfPilotConeAlg} as the true order weights $\boldsymbol{\Gamma}^{\rm tr}$, and use an inflation factor of $A = 1.1$.
-
-%\PeterNote{Below, we write $\epsilon instead of $\varepsilon$. Simon, is that on purpose?}
-
-Figures \ref{fig:four} (a) and (b) plot the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error ratio $\|f - \APP(f)\|_\infty/\varepsilon$, for $f$ in $d=4$ and $d=7$ dimensions, respectively.
+\begin{equation*}
+\hat{f}(\bsk) = Z_{\bsk} \,  {\Gamma}_{\|\bsk\|_0}^{\rm tr} \prod_{\substack{\ell=1\\ k_\ell>0}}^d {w_\ell^{\rm tr}} {s}_{k_\ell}^{\rm tr}, \quad Z_{\bsk} \overset{i.i.d.}{\sim} \text{Unif}[-1, 1], \quad \bsk \in \mathbb{N}_0^d.
+%\label{eq:foursim}
+\end{equation*}
+Here, $(w_\ell^{\rm tr})_{\ell=1}^d = (1/L^2(\ell))_{l=1}^d$, $({\Gamma_k^{\rm tr}})_{k=1}^\infty \equiv 1$ and $(s_j^{\rm tr})_{j=1}^{k_{\rm max}} = (1/j^4)_{j=1}^4$ are the true coordinate, order, and smoothness weights, and $Z_{\bsk}$ randomly sets the magnitude and sign of each coefficient.
+Moreover, $\bigl(L(\ell)\bigr)_{\ell=1}^d$ is a random permutation of $1, \ldots, d$ to ensure that the order of input variables does not necessarily reflect their order of importance.
+We also set $\boldsymbol{\Gamma} = \boldsymbol{\Gamma}^{\rm tr}$ in Algorithm \ref{DHKM:InfPilotConeAlg} and use an inflation factor of $A = 1.1$.
+
+Figures \ref{fig:four} (a) and (b) display the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error to tolerance ratio, $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$, in $d=4$ and $d=7$ dimensions, respectively.
 Each data point corresponds to a different error tolerance $\varepsilon$.
-Here, a ratio $\|f - \APP(f)\|_\infty / \varepsilon$ close to 1 (but not exceeding 1) is desired, since this shows our adaptive procedure can achieve the desired tolerance $\varepsilon$ by inferring and incorporating POSD structure.
-For $d=4$ (Figure \ref{fig:four} (a)), $\|f - \APP(f)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$ (Figure \ref{fig:four} (b)), this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decrease to $\approx 0.014$ for $\varepsilon = 0.001$.
-This shows that our adaptive approximation algorithm works reasonably well, and appears slightly more effective in lower dimensions ($d=4$) than in higher dimensions ($d=7$).
-A likely reason for this is that the underlying POSD structure can be more easily learned from a small pilot sample in lower dimensions than in higher dimensions; using this inferred structure then allows for a tighter data-based error bound.
-
-%\begin{itemize}
-%\item Figure \ref{fig:four} shows the performance of this adaptive approximation method, with $f$ being a 4-d or 8-d function with random Fourier coefficients.
-%\item \SimonNote{Numerical results for function evaluations?}
-%\end{itemize}
+A ratio $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
+For $d=4$, $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$.
+This shows that our adaptive approximation algorithm works reasonably well.
+It appears slightly more effective in lower dimensions  than in higher dimensions.
+A likely reason is that the underlying POSD structure can be more easily learned from a small pilot sample in lower dimensions than in higher dimensions.
 
@@
 \end{subfigure}
-\caption{Total required sample size as a function of error ratio $\|f - \hat{f}\|_{\infty}/\varepsilon$, with points colored by the absolute error tolerance level $\varepsilon$.}
+\caption{Total required sample size as a function of error ratio $\|f - \ALG(f,\varepsilon)\|_{\infty}/\varepsilon$, with points colored by the absolute error tolerance level $\varepsilon$.}
 \label{fig:four}
@@
 \begin{acknowledgement}
- P.~Kritzer gratefully acknowledges support by the Austrian Science Fund (FWF) Project  F5506-N26, 
-which is part of the Special Research Program ``Quasi-Monte Carlo Methods: Theory and Applications''.
+\DHKMchange{The authors would like to thank two anonymous referees for their suggestions which helped to improve the presentation of the results.}
+
+F.~J.~Hickernell, P.~Kritzer, and S.~Mak gratefully acknowledge the support of the Statistical and Applied Mathematical Sciences Institute year-long ``Program on Quasi-Monte Carlo and High-Dimensional Sampling Methods for Applied Mathematics'' through NSF-DMS-1638521.
+F.~J.~Hickernell also acknowledges the support of NSF-DMS-1522687.
+F.~J.~Hickernell and P.~Kritzer thank the RICAM Special Semester Program 2018 for support.
+P.~Kritzer gratefully acknowledges support by the Austrian Science Fund (FWF) Project  F5506-N26, which is part of the Special Research Program ``Quasi-Monte Carlo Methods: Theory and Applications''.
 \end{acknowledgement}

### 2019-07-09 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 Let $\card(\cdot)$ denote the cardinality of a set.
-We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le n_{j+1}$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
+We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le \DHKMchange{j+1}$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
 \begin{equation} \label{DHKM:PropCond}

### 2019-08-02 DHKM_Response_to_Reviewers.tex
Updates from Overleaf

@@
 \item Remark (9): done. 
+\item Remark (10): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
 \item Remarks (11), (12): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
@@
 \begin{itemize}
-\item Major issues 1.a)--1.d), 2.a), 2.b): Done. We have modified the introduction, and re-organized it into two sections. 
+\item Major issues 1.a)--1.d), 2.a), 2.b): Done.
+We have modified the introduction, and re-organized it into two sections.
+We have added a statement after Corollary 1 regarding a result for the example with respect to the smoothness parameter $r$
 \item Remark (i): The ordering is not necessarily unique, as we might have weights 
@@
 \item Remark (iv): The paper will be a chapter in a proceedings volume.
+\item Remark (v): The re-structuring of the paper should have resolved this issue.
+\item Remark (vi): done. 
 \item Remark (vii): We changed ``Choosing" to ``Identifying".
@@
 \item Remark (xv): The cone in equation (28) is now denoted as $\calC_{\boldsymbol{\lambda},a,b}$.
+\item Remark (xvi): Done.
 \item Remark (xix): Here, we mean a ``small number of coordinates in $f$ are important''. We have made this change in the paper.

### 2019-08-02 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
   Austrian Academy of Sciences, Altenbergerstr. 69, 4040 Linz, Austria}
-  \affil[4]{H. Milton Stewart School of Industrial and Systems Engineering, Georgia Institute of Technology, 755 Ferst Drive, Atlanta, GA 30332 USA}
+  \affil[4]{Department of Statistical Science, Duke University, Durham, NC 27708-0251 USA}
   \title{Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone}
@@
 }
-Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, $\mathbb{K}$ is a countable index set, and $\bslambda = (\lambda_\bsk)_{\bsk \in \mathbb{K}}$ is the sequence of weights.
+Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, $\mathbb{K}$ is a countable index set, and $\bslambda = (\lambda_\bsk)_{\bsk \in \mathbb{K}}$ is the sequence of weights.
 These bases are defined to match the solution operator:
@@
 \begin{equation} \label{DHKM:pilot_cone}
-    \DHKMchange{\calC_{\boldsymbol{\lambda},A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
-\end{equation}
-
+    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
+\end{equation}
 Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.
-The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ allows us to bound these as follows:
+The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ allows us to bound these as follows:
 \begin{align*}
@@
     &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
-    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}}.
+    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}.
 \end{align*}
@@
 \begin{equation}
-\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}},
+\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},
 \end{equation}
@@
 This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
-This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ defined in \eqref{DHKM:pilot_cone}:
+This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}:
 
@@
 \begin{theorem} \label{DHKM:PilotCostThm}
-Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ defined in \eqref{DHKM:pilot_cone}.
+Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}.
 The information cost is
 \begin{multline} \label{DHKM:PilotConeAlg_cost}
-    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},A}},\varepsilon,R) \\
+    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) \\
     = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
@@
 \begin{multline} \label{DHKM:PilotConeAlg_comp}
-        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
     \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
@@
 \end{multline}
-Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}})$ contains only adaptive algorithms.
+Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.
 \end{theorem}
@@
 \begin{align*}
-    \MoveEqLeft[1]{\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},A}},\varepsilon,R)} \\
+    \MoveEqLeft[1]{\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R)} \\
     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
@@
 since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
-Moreover, this inequality is tight for some $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
+Moreover, this inequality is tight for some $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
 This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.
@@
     \]
-Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ in \eqref{DHKM:pilot_cone}.
+Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ in \eqref{DHKM:pilot_cone}.
 Fix $R \in [R_{\min},\infty)$ and $\varepsilon \in (0,\varepsilon_{\max}]$ arbitrarily.
@@
 \end{align}
-Therefore, $f_\pm \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}} \cap \calB_R$.
+Therefore, $f_\pm \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_R$.
 Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.
@@
 This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
-Because $\lim_{R \to \infty} \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}}), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}})$ contains only adaptive algorithms.
+Because $\lim_{R \to \infty} \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.
 
@@
 \[
-\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},A}},\varepsilon,R) \le \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},A}}),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
+\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) \le \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
 \]
@@
 The exact solution can be constructed using only the pilot sample.
-Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, which is an unbounded set.
-
-We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, but we may derive necessary conditions for $f$ to lie in $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$.
-The following proposition follows from the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.
+Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, which is an unbounded set.
+
+We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, but we may derive necessary conditions for $f$ to lie in $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$.
+The following proposition follows from the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.
 
@@
 \begin{proposition}
-If $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, then 
+If $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, then 
 \begin{equation} \label{DHKM:PilotConeNecessary}
@@
 
-If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
-The remedy is to make $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.
+If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
+The remedy is to make $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.
 
@@
 
-In this section, we write $\calC_d$ instead of $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
+In this section, we write $\calC_d$ instead of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
 Recall that we assume that
@@
 The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $.
+\DHKMchange{We remark that knowing $\sigma_1 (f)$ would already be sufficient to identify 
+a sample size that guarantees an error of at most $\varepsilon$. However, knowing $\sigma_j (f)$ for further values of $j$ will allow us to stop earlier.}
+
 Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
@@
 \end{align*}
-Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},A}} $defined in \eqref{DHKM:pilot_cone} if we choose
+Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $defined in \eqref{DHKM:pilot_cone} if we choose
 $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
@@
 \begin{proof}
-As pointed out above, $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},A}}$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
+As pointed out above, $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
 This means that the approximation problem on  $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:pilot_cone}.

### 2019-08-06 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 \DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
-\DHKMchange{By a cone, we mean a set of functions satisfying that for each element also all its multiples lie in the set.
-We will study different variants of cone here, the precise definitions will be given below.}
+\DHKMchange{By a cone, we mean a set of functions where constant multiples of every element in the set also lie in the set.
+We study different variants of cone here, the precise definitions are given below.}
 
@@
 We derive conditions under which the problem is tractable, i.e., the information cost of constructing the approximate solution does not increase exponentially with the dimension of the input function domain.
-In the remainder of this section we outline the general idea of the paper.
-
-We study the approximation of a solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
+In the remainder of this section we outline the general idea of this chapter.
+
+We study the approximation of a linear solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
 Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(f,\varepsilon)$ for $f\in\calC$ that satisfies the error criterion
@@
 
-We assume in this paper that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n=n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
-I.e.,
-we will study algorithms which have an output of the form 
+We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n=n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
+That is,
+we study algorithms that have an output of the form 
 \begin{equation*} 
@@
 with $n(f,\varepsilon)$ being chosen based on a stopping rule. 
-I.e., we assume that it is possible to sample the series coefficients of the input function.
+We assume that it is possible to sample the series coefficients of the input function.
 This is a \DHKMchange{more} restrictive assumption than being able to sample any linear functional, but it is \DHKMchange{less} restrictive than only being able to sample function values.
@@
 
-We call an algorithm \emph{non-adaptive} if it is such that $n(f,\varepsilon)=n(\varepsilon)$, independently of the particular choice of $f\in\calC$.
-
 The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$.
 For adaptive algorithms this cost varies with the input function $f$.
+We call an algorithm \emph{non-adaptive} if $n(f,\varepsilon)=n(\varepsilon)$, independently of the particular choice of $f\in\calC$.
 
 In the following, let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
-
 We now define the information cost of the algorithm in general, recognizing that it will tend to depend on $\norm[\calF]{f}$:
@@
 }
-
 Furthermore, we define the \emph{computational complexity} of a problem as the information cost of the best algorithm:
@@
 
-We will demonstrate below that non-adaptive algorithms are optimal when the set of inputs is chosen to be $\calC = \calB_R$.
+We demonstrate below that non-adaptive algorithms are optimal when the set of inputs is chosen to be $\calC = \calB_R$.
 However, typically one cannot bound the norm of the input function a priori, so non-adaptive algorithms may be impractical.
@@
 For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball.
-By a cone, we mean a set of functions satisfying that for each element also all its multiples lie in the set.
-We will study different variants of cones in different sections of this paper.
-The first definition of a cone will be given in \eqref{DHKM:pilot_cone},
+By a cone, we mean a set of functions where the constant multiples of each element of the set also lie in the set.
+We study different variants of cones in different sections of this chapter.
+The first definition of a cone is given in \eqref{DHKM:pilot_cone},
 where the idea is that the consists of $f\in\calF$ such that 
@@
 for a suitably chosen homogeneous function $h:\bbR\to [0,\infty)$. This means that the norm of $f$ can be bounded well in terms of 
-a \emph{pilot sample} of size $n_1\in\bbN$, see \eqref{DHKM:pilot_cone} for the precise definition.
+a \emph{pilot sample} of size $n_1\in\bbN$.
+See \eqref{DHKM:pilot_cone} for the precise definition.
 In Section \ref{DHKM:SecAdapAlgTrackDecay}, we will modify the definition of cones such that we can keep track of the decay rate of the series coefficients of the input function (see \eqref{DHKM:TrackConeDef}),
@@
 Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.
-Thus, algorithms satisfying the error criterion  exist only for some strict subset of $\calF$.
+Thus, algorithms satisfying the error criterion  exist only for some strict subset of $\calF$, such as a ball or a cone.
 Identifying that subset is both an art and a science.
 
-The rest of the paper is structured as follows.
-In the next section, we will formulate our problem more formally, and we point out some results for non-adaptive algorithms with inputs from balls.
+The rest of this chapter is structured as follows.
+In the next section, we formulate our problem more formally, and we point out some results for non-adaptive algorithms with inputs from balls.
 Furthermore, we illustrate our theory by
@@
 
-\section{Problem Formulation and an Illustrative Example}\label{DHKM:secprobdef}
+\section{General Setting}\label{DHKM:secprobdef}
 
 \PeterNote{Can we find a better heading for this section?}
+\FredNote{How about the above?}
 
@@
 
-\subsection{General problem formulation}
+\subsection{Problem formulation}
 
@@
 \end{gather*}
-}
+}%
 Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, $\mathbb{K}$ is a countable index set, and $\bslambda = (\lambda_\bsk)_{\bsk \in \mathbb{K}}$ is the sequence of weights.
@@
 
-\PeterNote{Should we keep the list of questions in this extensive form?}
-\YuhanNote{I moved it to introduction}
+%\PeterNote{Should we keep the list of questions in this extensive form?}
+%\YuhanNote{I moved it to introduction}
 
@@
 \DHKMchange{Let's consider an alternative cone, i.e.,
-\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \cf : \norm[\calF]{f} \le A'\norm[\calF']{f}\},\]
+\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\},\]
 where
@@
      \le \omega_{n_1+1}^\rho \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
-     & = \omega_{n_1+1}^\rho \left[ \norm[\cf]{f}^\rho - \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
+     & = \omega_{n_1+1}^\rho \left[ \norm[\calF]{f}^\rho - \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
      & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \norm[\calF']{f}^\rho - \omega_1^{-\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].

### 2019-08-17 DingHickKritzMakRICAMChapVerD.tex
Fix
Updates from Overleaf
testing

@@
   essentially no better than non-adaptive algorithms for \DHKMchange{convex and symmetric} input sets, the 
-  situation may be different for non-convex sets. A typical example
+  situation may be different for non-convex sets. \DHKMchange{The setting} 
   considered here is function approximation based on series expansions. Given 
@@
   we consider situations where it makes sense to infer coordinate and smoothness importance.
-Besides performing an error analysis, we also study the information cost of our algorithms and the computational complexity
+Besides performing an error analysis, we also \DHKMchange{derive upper bounds on} the information cost of our algorithms and \DHKMchange{lower bounds on} the computational complexity
   of our problems, and we identify conditions under which we can avoid a curse of 
@@
 \DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
-\DHKMchange{By a cone, we mean a set of functions where constant multiples of every element in the set also lie in the set.
-We study different variants of cone here, the precise definitions are given below.}
+\DHKMchange{By a cone, we mean a set of functions where constant multiples of every function in the set also lie in the set.
+The precise definitions of the cones that we study are given below.}
 
@@
 We study the approximation of a linear solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
-Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(f,\varepsilon)$ for $f\in\calC$ that satisfies the error criterion
+Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(\cdot,\cdot):\calC \times (0,\infty) \to \calG$ that satisfies the error criterion:
 \begin{equation} \label{DHKM:err_crit}
@@
 \end{equation}
-where  $\varepsilon$ denotes the error tolerance. Such an algorithm will  contain a rule for choosing $n$---depending on $f$ and $\varepsilon$.  The objectives of this chapter are to 
+where  $\varepsilon$ denotes the error tolerance.
+Such an algorithm will  contain a rule for choosing the number of series coefficients required, $n(f,\varepsilon)$, which depends on $f$ and $\varepsilon$.
+The objectives of this chapter are to
 \begin{itemize}
@@
 \begin{equation*} 
-  \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N,
+  \ALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N,
 \end{equation*}
@@
 
-The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$.
+The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$, i.e., $\COST(\ALG,f,\varepsilon) = n(f,\varepsilon)$.
 For adaptive algorithms this cost varies with the input function $f$.
@@
 For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball.
-By a cone, we mean a set of functions where the constant multiples of each element of the set also lie in the set.
 We study different variants of cones in different sections of this chapter.
 The first definition of a cone is given in \eqref{DHKM:pilot_cone},
-where the idea is that the consists of $f\in\calF$ such that 
+where the idea is that the cone consists of $f\in\calF$ such that 
 $$
@@
 
-Section \ref{DHKM:smoothimportance_sec} considers the case where the most suitable weights $\bslambda$ are not known a priori and are instead inferred from function data.
+Section \ref{DHKM:smoothimportance_sec} considers the case where the most suitable weights $\bslambda$, which are used to define the input space, are not known a priori and are instead inferred from function data.
 Adaptive Algorithm \ref{DHKM:InfPilotConeAlg} combines this inference step with Algorithm \ref{DHKM:PilotConeAlg} to construct an approximation that satisfies the error criterion.
@@
 
-\section{General Setting}\label{DHKM:secprobdef}
-
-\PeterNote{Can we find a better heading for this section?}
-\FredNote{How about the above?}
+\section{Formal Setting}\label{DHKM:secprobdef}
 
@@
 \end{gather*}
+Here we have chosen $\tau = 2$ so $\rho'=\infty$.
 If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer \DHKMchange{for certain classes of inputs in $\calF$ as for example balls, which
@@
 \end{lemma}
-
 }
@@
 \begin{align*}
-     \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty} & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+     \MoveEqLeft{\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
+     & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
     \right]^{1/\rho} \qquad \forall f \in \calF \\
@@
 where 
-\begin{multline}
+\begin{multline} \label{ErrNDef}
 \ERRN \\
@@
     \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
-    \\ n \ge n_1.
+    \\ \forall n \ge n_1.
 \end{multline}
@@
 \end{gather}
+
 Let $f_{\pm} = f_1 \pm f_2$.  By the definitions above, it follows that
@@
 
-We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, but we may derive necessary conditions for $f$ to lie in $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$.
-The following proposition follows from the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ in \eqref{DHKM:pilot_cone} and the fact that the term on the left below underestimates $\norm[\calF]{f}$.
-
-\YuhanNote{Should we delete Proposition 1 just keep Propostion 2?}
-\begin{proposition}
-If $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, then 
+\DHKMchange{We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\ERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
 \begin{equation} \label{DHKM:PilotConeNecessary}
@@
 \end{equation}
-\end{proposition}
+}
 
@@
 \DHKMchange{Let's consider an alternative cone, i.e.,
-\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\},\]
+\begin{equation} \label{DHKM:altconedef}
+    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\},
+\end{equation}
 where
 $\norm[\calF']{f} =\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}}$ and $\omega_{\bsk}$ decreases.
+The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is defined as the subset of $\calF$ for which the weaker norm of the function  provides an upper bound the stronger norm of the function.
+The following proposition describes the relationship between the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef}.
 \begin{proposition}
@@
 }
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{The Illustrative Example Revisited}\label{DHKM:revisexamp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\FredNote{Fred got to here}
+\YuhanNote{Create a new subsection and move the content related with the example here}
+\DHKMchange{
+Before we revisit the example in Section \ref{DHKM:secexamp}, we introduce several lemmas.
+
+\begin{lemma}\label{DHKM:lambdineq}
+Consider the ordering weights,
+$\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
+we have for $p>0$
+\[ \sum_{i=1}^\infty \lambda_{d,\bsk_{i}}^p \le \frac{1}{n^{1/p}}
+\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p\right)^{1/p}\]
+\end{lemma}
+\begin{proof}
+As $\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0$, we obtain for $p>0$
+\begin{align*}
+    n \lambda_{\bsk_{n+1}}^p & \le 
+    \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
+    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \\
+    \Longleftrightarrow 
+    \lambda_{\bsk_{n+1}}&  \le \frac{1}{n^{1/p}}
+\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \right)^{1/p}
+\end{align*}
+\end{proof}
+
+To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of positive \emph{coordinate weights}, $w_1, \ldots, w_d$, and positive \emph{smoothness weights}, $s_1, s_2, \ldots$:
+\begin{equation}
+    \label{DHKM:prodwts}
+\lambda_{d,\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \NN_0^d, \ d \in \NN.
+\end{equation}
+To stress the dependence on $d$, we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$
+  This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.
+
+\begin{lemma}\label{DHKM:prodwtsupperbound}
+Consider $\lambda_{d,\bsk}$ defined in \eqref{DHKM:prodwts},
+we have for $p>0$,
+\[\sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p \le \exp\left(\sum_{k=1}^\infty s_k^p \sum_{\ell = 1}^{d} w_\ell^{p} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^p \sum_{\ell = 1}^{\infty} w_\ell^{p} \right),\]
+if $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite.
+\end{lemma}
+\begin{proof}
+\begin{align*}
+   \sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p  & =
+   \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) \qquad \text{ by \eqref{DHKM:prodwts} }\\
+    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \bigr) \right)\\
+ &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \right)
+\qquad \text{since }\log(1+x) \le x \ \forall x\ge 0,\\
+&\le \exp\left(\sum_{\ell = 1}^\infty w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \right)
+\qquad \text{ since  } \sum_{\ell = 1}^{\infty} w_\ell^{p} \text{ converges}.\\
+\end{align*}
+\end{proof}
+
+The example in Section \ref{DHKM:secexamp} chooses $\rho = \tau = 2$, $\rho' = \infty$. Thus, we obtain by Theorem \ref{DHKM:thm_cost_non_adapt}:
+\begin{align*}
+	\COMP(\calA(\calB_{R}),\varepsilon,R) &= \COST(\ALG,\calB_{R},\varepsilon,R) 
+	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \}.
+\end{align*}
+Using the non-increasing ordering of the $\lambda_{\bsk_i}$, we employ a standard technique for bounding the $n+1^\text{st}$ largest $\lambda_{\bsk}$ in terms of the sum of the $p^\text{th}$ power of all the $\lambda_{\bsk}$.
+For $0  < 1/r < p$, by Lemma \ref{DHKM:lambdineq} and Lemma \ref{DHKM:prodwtsupperbound} with $s_k = k^{-r}$,
+\begin{align*}
+n\lambda_{\bsk_{n+1}}^{p} \le \sum_{\bsk \in \bbN_0^d}\lambda_{\bsk}^{p}  \le 
+\exp\left(\sum_{\ell = 1}^d  w_\ell^{p}\sum_{k=1}^{\infty}\frac{1}{k^{p r} }\right)
+ \le \exp\left(\zeta(pr) \sum_{\ell = 1}^{\infty} w_\ell^{p} \right).
+\end{align*}
+Hence, substituting the above upper bound on $\lambda_{\bsk_{n+1}}$ into the formula for the complexity of the problem, we obtain an upper bound on the complexity:
+\begin{align*}
+    \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} \\
+  &\le\min\left\{ n \in \N_0 : \frac{1}{n}\exp\left(\zeta(p r) \sum_{\ell = 1}^\infty w_\ell^{p} \right)  \le \left( \frac{\varepsilon}{R} \right)^{p}  \right\} \\
+  &= \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right) \right \rceil .
+\end{align*}
+
+If $p^\dagger$ is the infimum of the $p$ for which $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $p^* = \max(1/r,p^\dagger)$.
+On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.
+}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The example in Section \ref{DHKM:secexamp} chooses $\rho = \tau = 2$ and $\rho' = \infty$.  Thus, we obtain by Theorem \ref{DHKM:thm_cost_non_adapt}:
-\begin{align*}
-	\COMP(\calA(\calB_{R}),\varepsilon,R) &= \COST(\ALG,\calB_{R},\varepsilon,R) 
-	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \}.
-\end{align*}
-Using the non-increasing ordering of the $\lambda_{\bsk_i}$, we employ a standard technique for bounding the $n+1^\text{st}$ largest $\lambda_{\bsk}$ in terms of the sum of the $p^\text{th}$ power of all the $\lambda_{\bsk}$.
-For $0  < 1/r < p$,
-\begin{align*}
-(n+1)\lambda_{\bsk_{n+1}}^{p} &\le \sum_{i=1}^{n+1}\lambda_{\bsk_{i}}^{p} \le \sum_{\bsk \in \bbN_0^d}\lambda_{\bsk}^{p} = \prod_{\ell =1}^d \left[1 + w_\ell^{p}\sum_{k = 1}^\infty \frac {1}{k^{pr}} \right ] \\
-& =  \prod_{\ell =1}^d \left[1 + w_\ell^{p}\zeta(pr)\right ] 
-= \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\zeta(pr) \bigr) \right) \\
-& \le \exp\left(\zeta(pr) \sum_{\ell = 1}^{\infty} w_\ell^{p} \right) \qquad \text{since }\log(1+x) \le x \ \forall x\ge 0.
-\end{align*}
-Hence, substituting the above upper bound on $\lambda_{\bsk_{n+1}}$ into the formula for the complexity of the problem, we obtain an upper bound on the complexity:
-\begin{align*}
-    \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} \\
-  &\le\min\left\{ n \in \N_0 : \frac{1}{n+1}\exp\left(\zeta(pr) \sum_{\ell = 1}^\infty w_\ell^{p} \right)  \le \left( \frac{\varepsilon}{R} \right)^{p}  \right\} \\
-  &= \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(pr) \sum_{\ell = 1}^{\infty} w_\ell^{p} \right) \right \rceil - 1.
+Consider the example in Section \ref{DHKM:secexamp}, we have
+\begin{align*}
+    \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} 
+  \le \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right) \right \rceil .
 \end{align*}
@@
 If $p^\dagger$ is the infimum of the $p$ for which $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $p^* = \max(1/r,p^\dagger)$.
-On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.
+On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.\\
+
 }
 
-In this section, we write $\calC_d$ instead of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, to stress the dependence on $d$, and for the same reason we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$.
 Recall that we assume that 
@@
  \item[2.] 
-  We have polynomial tractability if and only if there exist $\eta_1, \eta_2 \ge 0$ and $\eta_3, K>0$ such that
+  We have polynomial tractability if and only if there exist $\eta_1, p_2 \ge 0$ and $\eta_3, K>0$ such that
  \[
@@
 
-To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of positive \emph{coordinate weights}, $w_1, \ldots, w_d$, and positive \emph{smoothness weights}, $s_1, s_2, \ldots$:
-\begin{equation}
-    \label{DHKM:prodwts}
-\lambda_{d,\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \NN_0^d, \ d \in \NN.
-\end{equation}
-This is a generalization of the example in Section \ref{DHKM:secexamp}, where $s_{k} = k^{-r}$.
-This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.
-The same argument as \DHKMchange{stated above} implies that the sum of the $\lambda_{d,\bsk_i}^\eta$ is bounded above as
+\DHKMchange{
+To be more concrete, we consider the situation 
+\[
+\lambda_{d,\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \NN_0^d, \ d \in \NN,
+\] one more time.
+By Lemma \ref{DHKM:prodwtsupperbound}, we have
+}
 \[
@@
 From this last inequality, it follows that $j^\dagger \ge j^*$.
-\end{proof} \
+\end{proof}
+
+\YuhanNote{Create a new version of Theorem 6, as $ \frac{1 - b^{j\rho}}{1 - b^\rho} \ge 1 \forall j$. And based on that, derive the explicit bound of the example. }
+\DHKMchange{
+
+\begin{theorem}\label{DHKM:TractConeCompCost}
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
+The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
+\begin{equation} \label{DHKM:EqTractConejstar}
+j^* = \min\left \{ j \in \bbN : \ERRNj \le \varepsilon  \right\}.
+\end{equation}
+Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+\begin{equation} \label{DHKM:TractConejdagger}
+j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}
+\le  \frac{b\varepsilon}{Ra^2}\right\}.
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+The value of $j^*$ in \eqref{DHKM:EqTractConejstar} follows directly from the error criterion. The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
+
+For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
+For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
+\begin{align*}
+R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
+ \ge \norm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
+ \qquad \text{by \eqref{DHKM:SigmaDef} } \\
+& \ge \sigma_1(f) \ge a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f) \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
+& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^r\Lambda_{j^\dagger+r} \bigr)_{r=1}^\infty}
+\qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
+& = \frac{R}{\varepsilon} \ERRNjd\, .
+\end{align*}
+From this last inequality, it follows that $j^\dagger \ge j^*$.
+\end{proof}
+
+Let's revisit the example in Section \ref{DHKM:secexamp}. For this example,
+we choose $n_j = n_02^j,$ thus
+\[\calK_j = \{\bsk_{n_0 2^{j-1}+1}, \ldots, \bsk_{n_02^j}\} \quad \text{for } j \in \N \qquad \text{ and } \calK_1 = \{\bsk_{1}, \ldots, \bsk_{n_0}\}.\]
+For example, we have $\rho = \tau = 2$, $\rho' = \infty$. Therefore
+\[\Lambda_j = \|(\lambda_\bsk)_\bsk \in \calK_j\|_{\rho'} = \lambda_{\bsk_{n_0 2^{j-1}+1}}.\]
+By Lemma \ref{DHKM:lambdineq} and Lemma \ref{DHKM:prodwtsupperbound}, we obtain
+\[\Lambda_j \le \frac{1}{ n_0^{1/p} 2^{(j-1)/p}} \exp\left(\frac{1}{p}
+\zeta(pr)\sum_{\ell=1}^\infty 
+w_\ell^p
+\right),\]
+where $0< 1/r< p$.
+\begin{align*}
+\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}^\tau
+ & =  \sum_{q=1}^\infty
+( b^{j+q}\Lambda_{j+q})^\tau \\
+& \le \sum_{q=1}^\infty b^{(j+q)\tau} 
+ \frac{1}{ n_0^{\tau/p} 2^{(j+q-1)\tau/p}} \exp\left(\frac{\tau}{p}
+\zeta(pr)\sum_{\ell=1}^\infty 
+w_\ell^p
+\right)\\
+& = 
+\frac{\exp\left(\frac{\tau}{p}
+\zeta(pr)\sum_{\ell=1}^\infty 
+w_\ell^p
+\right)}{ n_0^{\tau/p} } \sum_{q=1}^\infty 
+\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}\\
+\Leftrightarrow 
+\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}
+ & \le  \frac{\exp\left(\frac{1}{p}
+\zeta(pr)\sum_{\ell=1}^\infty 
+w_\ell^p
+\right)}{ n_0^{1/p} } 
+\left(\sum_{q=1}^\infty 
+\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
+\right)^{1/\tau}
+\end{align*}
+Therefore, the upper bound of the computation cost is $n_j^\dagger$, where
+\[j^\dagger = \min \left \{j \in \bbN : 
+\left(\sum_{q=1}^\infty 
+\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
+\right)^{1/\tau}
+\le  \frac{b\varepsilon n_0^{1/p}}{Ra^2}\exp\left(\frac{1}{p}
+\zeta(pr)\sum_{\ell=1}^\infty 
+w_\ell^p
+\right) \right\}.\]
+}
 

### 2019-08-17 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 
-We study the approximation of a linear solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
+We study the approximation of a linear solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
 Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(\cdot,\cdot):\calC \times (0,\infty) \to \calG$ that satisfies the error criterion:
@@
 
-\DHKMchange{Let's consider an alternative cone, i.e.,
+\DHKMchange{Let us consider an alternative cone, i.e.,
 \begin{equation} \label{DHKM:altconedef}
@@
 \begin{proposition}
-If there exists $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ such that
+If there exist $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ such that
 \[\omega_{n_1} A'' \ge A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and} \qquad  \omega_{n_1+1}A' < 1, \]
@@
 \begin{proof}
-Let's prove $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
+Let us prove $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
 \subseteq 
 \calC_{\boldsymbol{\lambda}, A}$ at first.
-Suppose $f \in \calC_{\boldsymbol{\lambda}, A}$, then by definition, we have
+Suppose $f \in \calC_{\boldsymbol{\lambda}, A}$, then by definition we have
 \begin{align*}
@@
 
-Next, we show the rest part.
-Suppose, $f \in \calC'_{\boldsymbol{\lambda},\boldsymbol{\omega},  A'}$, we have
+For the proof of the remaining part, 
+suppose $f \in \calC'_{\boldsymbol{\lambda},\boldsymbol{\omega},  A'}$. Then we have
 \begin{align*}
@@
 \end{align*}
-Rearrange the terms, we obtain
+Rearranging the terms, we obtain
 \begin{align*}
@@
 \begin{lemma}\label{DHKM:lambdineq}
-Consider the ordering weights,
+Consider the ordered weights,
 $\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
-we have for $p>0$
+then we have for $p>0$,
 \[ \sum_{i=1}^\infty \lambda_{d,\bsk_{i}}^p \le \frac{1}{n^{1/p}}
-\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p\right)^{1/p}\]
+\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p\right)^{1/p}\].
 \end{lemma}
+\PeterNote{It seems to me that on the left-hand side of the 
+above inequality we need $\lambda_{\bsk_{n+1}}^p$, right?}
 \begin{proof}
@@
     \lambda_{\bsk_{n+1}}&  \le \frac{1}{n^{1/p}}
-\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \right)^{1/p}
+\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \right)^{1/p}.
 \end{align*}

### 2019-08-18 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 
-\DHKMchange{Let us consider an alternative cone, i.e.,
-\begin{equation} \label{DHKM:altconedef}
-    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\},
-\end{equation}
-where
-$\norm[\calF']{f} =\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}}$ and $\omega_{\bsk}$ decreases.
-The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is defined as the subset of $\calF$ for which the weaker norm of the function  provides an upper bound the stronger norm of the function.
-The following proposition describes the relationship between the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef}.
+\DHKMchange{Our $\calC_{\boldsymbol{\lambda},n_1,A}$ is a cone for which a pilot sample of the input function allows you to bound its norm.
+An alternative might be to define a cone for which a weaker norm of the function provides an upper bound on the original norm.
+Here is such a cone:
+\begin{multline} \label{DHKM:altconedef}
+    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{i}}{\lambda_{\bsk}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
+\end{multline}
+The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is a strict subset of $\calF$.
+The following proposition describes how the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef} are related.
 \begin{proposition}
-If there exist $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ such that
-\[\omega_{n_1} A'' \ge A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and} \qquad  \omega_{n_1+1}A' < 1, \]
+If the parameters $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ satisfy
+\[ 
+\omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho}
+\le A \le \omega_{n_1} A'' \text{ and} \qquad  \omega_{n_1+1}A' < 1, 
+\]
 then 
-\[\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
+\[
+\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
 \subseteq 
-\calC_{\boldsymbol{\lambda}, A}
+\calC_{\boldsymbol{\lambda}, n_1, A}
 \subseteq
-\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.\]
+\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}.
+\]
 \end{proposition}
@@
 \begin{proof}
-Let us prove $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}
+Let us prove $
+\calC_{\boldsymbol{\lambda}, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$ first.
+Suppose $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$, then by the definition of $\calC_{\boldsymbol{\lambda}, n_1, A}$ we have
+\begin{equation*}
+    \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
+     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
+     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
+\end{equation*}
+Thus, if $A\omega_{n_1}^{-1} \le A''$, i.e. $A \le \omega_{n_1} A'' $, then
+we obtain $f \in \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.  So,
+
+For the proof that 
+$\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
 \subseteq 
-\calC_{\boldsymbol{\lambda}, A}$ at first.
-Suppose $f \in \calC_{\boldsymbol{\lambda}, A}$, then by definition we have
-\begin{align*}
-    \norm[\calF]{f} &\le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk = 1} ^{ n_1}}
-     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk}}{\lambda_{\bsk}} \right)_{\bsk =1} ^{n_1}}
-     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
-\end{align*}
-Thus, if $A'' \ge A\omega_{n_1}^{-1}$, i.e. $\omega_{n_1} A'' \ge A $,
-we obtain $\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.
-
-For the proof of the remaining part, 
+\calC_{\boldsymbol{\lambda}, n_1, A}$, 
 suppose $f \in \calC'_{\boldsymbol{\lambda},\boldsymbol{\omega},  A'}$. Then we have
@@
 \end{align*}
-Rearranging the terms, we obtain
+Assuming $\omega_{n_1+1}A' < 1$ and rearranging the above terms, we obtain
 \begin{align*}
 \norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \\
- \iff	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
-\end{align*}
-Hence, if $A \ge \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \text{ and } \omega_{n_1+1}A' < 1,$
-we obtain $\calC_{\boldsymbol{\lambda}, A}
+	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
+\end{align*}
+Hence, if $\omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \le A$, it follows that $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$ and so
+we obtain $
+\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}
 \subseteq
-\calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}.$
+\calC_{\boldsymbol{\lambda}, n_1, A}
+$.
 \end{proof}
@@
 The set of functions for which our algorithms succeed, $\calC_d$, depends on the dimension, too.
-Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
+Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on the dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
 
@@
 \item We say that the adaptive approximation problem is strongly polynomially tractable
-if and only if there are non-negative $C$, $p$, $\varepsilon_{\max}$, and $R_{\min}$ such that   
+if and only if there are non-negative $C$, $p$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
 $$   
@@
 We say that the problem is polynomially tractable
-if and only if there are non-negative $C,p$, $q$,  $\varepsilon_{\max}$, and $R_{\min}$ such that   
+if and only if there are non-negative $C,p$, $q$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
 $$   
@@
 Necessary and sufficient conditions on these tractability notions will be studied 
-for different types of algorithms in Sections \ref{DHKM:SecPilotTract} and \ref{DHKM:SecDecayTract}.
+for different types of algorithms in this section and Section \ref{DHKM:SecDecayTract}.
 
@@
 \end{multline*}
-where the positive constants $\omega_{\textup{lo}}$ and $\omega_{\textup{hi}}$  depend on $A$, but not depend on $d$, $\varepsilon$, or $R$.
+where the positive constants $\omega_{\textup{lo}}$ and $\omega_{\textup{hi}}$  depend on $A$, but do not depend on $d$, $\varepsilon$, or $R$.
 From the equation above, it is clear that tractability depends on the behavior of $n(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity.
-We would like to study under which conditions we obtain the various tractability notions defined above
+We would like to study under which conditions we obtain the various tractability notions defined above.
 
@@
  \item[2.] 
-  We have polynomial tractability if and only if there exist $\eta_1, p_2 \ge 0$ and $\eta_3, K>0$ such that
+  We have polynomial tractability if and only if there exist $\eta_1, \eta_2 \ge 0$ and $\eta_3, K>0$ such that
  \[
@@
 \begin{equation} \label{DHKM:NormLambdaFinite}
-    \norm[\calF \to \calG]{\SOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty
+    \norm[\calF \to \calG]{\SOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
 \end{equation}
@@
 \end{align*}
-Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $defined in \eqref{DHKM:pilot_cone} if we choose
+Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone} if we choose
 $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.

### 2019-08-19 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 For this example, let $\calF$ denote a Hilbert space of input functions where we choose $\bbK=\bbN_0^d$ and $\rho=2$,
-\begin{equation*}
-    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}, \quad \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
-\end{equation*}
+\begin{multline}
+\label{DHKM:IllExWts}
+    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \\ \text{where } \bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}, \quad \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
+\end{multline}
 The $w_\ell$ are non-negative \emph{coordinate weights}, which embody the assumption that $f$ may depend more strongly on coordinates with larger $w_\ell$ than those with smaller $w_\ell$.
@@
 \end{equation}
-}
-
+}%
 If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
@@
 \DHKMchange{Our $\calC_{\boldsymbol{\lambda},n_1,A}$ is a cone for which a pilot sample of the input function allows you to bound its norm.
-An alternative might be to define a cone for which a weaker norm of the function provides an upper bound on the original norm.
+An alternative is to define a cone for which a weaker norm of the function provides an upper bound on the original norm.
 Here is such a cone:
 \begin{multline} \label{DHKM:altconedef}
-    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\hf(\bsk)\omega_{i}}{\lambda_{\bsk}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
+    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\hf(\bsk_i)\omega_{i}}{\lambda_{\bsk_i}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
 \end{multline}
@@
 \begin{proposition}
-If the parameters $A,A',A'', n_1,$ and $\boldsymbol{\omega}$ satisfy
+If the parameters $A,A',A'', n_1,$ and $\boldsymbol{\omega} = (\omega_1, \omega_2, \ldots)$ satisfy
 \[ 
@@
 \]
-then 
+then the two types of cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef} include one another:
 \[
@@
 Let us prove $
-\calC_{\boldsymbol{\lambda}, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$ first.
-Suppose $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$, then by the definition of $\calC_{\boldsymbol{\lambda}, n_1, A}$ we have
+\calC_{\boldsymbol{\lambda}, n_1, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$ first.
+If $f \in \calC_{\boldsymbol{\lambda}, n_1, A}$, then by the definition of $\calC_{\boldsymbol{\lambda}, n_1, A}$ we have
 \begin{equation*}
@@
 Thus, if $A\omega_{n_1}^{-1} \le A''$, i.e. $A \le \omega_{n_1} A'' $, then
-we obtain $f \in \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.  So,
+we must have $f \in \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.  So, $
+\calC_{\boldsymbol{\lambda}, n_1, A} \subseteq \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A''}$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\FredNote{Fred got to here}
+
 \YuhanNote{Create a new subsection and move the content related with the example here}
 \DHKMchange{
-Before we revisit the example in Section \ref{DHKM:secexamp}, we introduce several lemmas.
+We now interpret the information cost upper bounds of Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} for the example introduced in Section \ref{DHKM:secexamp}, where $\rho = \tau = 2$ and $\rho' = \infty$.
+In this case, $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$.
+To facilitate this interpretation we establish a couple of commonly used lemmas.
 
@@
 $\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
-then we have for $p>0$,
-\[ \sum_{i=1}^\infty \lambda_{d,\bsk_{i}}^p \le \frac{1}{n^{1/p}}
-\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p\right)^{1/p}\].
+then we have
+\[ 
+\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \qquad \forall p >0,
+\]
+provided that $\norm[p]{\bslambda}$ is finite.
 \end{lemma}
-\PeterNote{It seems to me that on the left-hand side of the 
-above inequality we need $\lambda_{\bsk_{n+1}}^p$, right?}
 \begin{proof}
-As $\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0$, we obtain for $p>0$
-\begin{align*}
-    n \lambda_{\bsk_{n+1}}^p & \le 
+Since the $\lambda_{\bsk_i}$ are non-increasing it follows that 
+\begin{equation*}
+    n \lambda_{\bsk_{n+1}}^p \le 
     \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
-    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \\
-    \Longleftrightarrow 
-    \lambda_{\bsk_{n+1}}&  \le \frac{1}{n^{1/p}}
-\left(\sum_{\bsk \in \NN_0^d}^\infty \lambda_{\bsk}^p \right)^{1/p}.
-\end{align*}
+    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK}^\infty \lambda_{\bsk}^p = \norm[p]{\bslambda}^p \qquad \forall p > 0.
+\end{equation*}
+Dividing both sides by $n$ and taking the $p^{\text{th}}$ root completes the proof.
 \end{proof}
 
-To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of positive \emph{coordinate weights}, $w_1, \ldots, w_d$, and positive \emph{smoothness weights}, $s_1, s_2, \ldots$:
+\bigskip
+
+To be more concrete, we consider the situation where the $\lambda_{\bsk}$ are specified in terms of positive \emph{coordinate weights}, $\bsw = (w_1, \ldots, w_d)$, and positive \emph{smoothness weights}, $\bss = (s_1, s_2, \ldots)$:
 \begin{equation}
     \label{DHKM:prodwts}
-\lambda_{d,\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \NN_0^d, \ d \in \NN.
-\end{equation}
-To stress the dependence on $d$, we write $\lambda_{d,\bsk_i}$ instead of $\lambda_{\bsk_i}$
+\lambda_{\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \bbK :=\NN_0^d, \ d \in \NN.
+\end{equation}
+This is a generalization of our illustrative example, \eqref{DHKM:IllExWts}, in Section \ref{DHKM:secexamp} where $\bss = (1, 2^{-r}, 3^{-r}, \ldots )$.  
 This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.
@@
 \begin{lemma}\label{DHKM:prodwtsupperbound}
-Consider $\lambda_{d,\bsk}$ defined in \eqref{DHKM:prodwts},
-we have for $p>0$,
-\[\sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p \le \exp\left(\sum_{k=1}^\infty s_k^p \sum_{\ell = 1}^{d} w_\ell^{p} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^p \sum_{\ell = 1}^{\infty} w_\ell^{p} \right),\]
-if $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite.
+For $\bslambda = \bigl(\lambda_{\bsk} \bigr)_{\bsk \in \bbN_0^d}$ defined in \eqref{DHKM:prodwts}
+we have 
+\begin{align*}
+\norm[p]{\bslambda} &\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
+ \norm[p]{\bslambda} & \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
+\end{align*}
 \end{lemma}
 \begin{proof}
-\begin{align*}
-   \sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p  & =
-   \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) \qquad \text{ by \eqref{DHKM:prodwts} }\\
-    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \bigr) \right)\\
- &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \right)
-\qquad \text{since }\log(1+x) \le x \ \forall x\ge 0,\\
-&\le \exp\left(\sum_{\ell = 1}^\infty w_\ell^{p}\sum_{k=1}^{\infty}s_{k}^p \right)
-\qquad \text{ since  } \sum_{\ell = 1}^{\infty} w_\ell^{p} \text{ converges}.\\
-\end{align*}
+The proof proceeds by straightforward calculation under the assumption that $\norm[p]{\bss}$ is finite:
+\begin{align*}
+   \norm[p]{\bslambda}^ p & 
+   = \sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p  
+   = \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) 
+   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right) 
+   \qquad \text{ by \eqref{DHKM:prodwts} }\\
+    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\norm[p]{\bss}^p \bigr) \right)\\
+ &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p} \norm[p]{\bss}^p \right) = \exp\left(\norm[p]{\bsw}^p\norm[p]{\bss}^p \right)
+\quad \text{since }\log(1+x) \le x \ \forall x\ge 0.
+\end{align*}
+Taking the $p^{\text{th}}$ root completes the proof for the general case.
+For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
 \end{proof}
 
-The example in Section \ref{DHKM:secexamp} chooses $\rho = \tau = 2$, $\rho' = \infty$. Thus, we obtain by Theorem \ref{DHKM:thm_cost_non_adapt}:
-\begin{align*}
-	\COMP(\calA(\calB_{R}),\varepsilon,R) &= \COST(\ALG,\calB_{R},\varepsilon,R) 
-	=\min\{ n \in \N_0 : \lambda_{\bsk_{n+1}} \le \varepsilon/R \}.
-\end{align*}
-Using the non-increasing ordering of the $\lambda_{\bsk_i}$, we employ a standard technique for bounding the $n+1^\text{st}$ largest $\lambda_{\bsk}$ in terms of the sum of the $p^\text{th}$ power of all the $\lambda_{\bsk}$.
-For $0  < 1/r < p$, by Lemma \ref{DHKM:lambdineq} and Lemma \ref{DHKM:prodwtsupperbound} with $s_k = k^{-r}$,
-\begin{align*}
-n\lambda_{\bsk_{n+1}}^{p} \le \sum_{\bsk \in \bbN_0^d}\lambda_{\bsk}^{p}  \le 
-\exp\left(\sum_{\ell = 1}^d  w_\ell^{p}\sum_{k=1}^{\infty}\frac{1}{k^{p r} }\right)
- \le \exp\left(\zeta(pr) \sum_{\ell = 1}^{\infty} w_\ell^{p} \right).
-\end{align*}
-Hence, substituting the above upper bound on $\lambda_{\bsk_{n+1}}$ into the formula for the complexity of the problem, we obtain an upper bound on the complexity:
-\begin{align*}
-    \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} \\
-  &\le\min\left\{ n \in \N_0 : \frac{1}{n}\exp\left(\zeta(p r) \sum_{\ell = 1}^\infty w_\ell^{p} \right)  \le \left( \frac{\varepsilon}{R} \right)^{p}  \right\} \\
-  &= \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right) \right \rceil .
-\end{align*}
-
-If $p^\dagger$ is the infimum of the $p$ for which $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $p^* = \max(1/r,p^\dagger)$.
-On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.
+\bigskip
+
+Lemmas \ref{DHKM:lambdineq} and \ref{DHKM:prodwtsupperbound} imply upper bounds on $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$:
+\begin{align*}
+\lambda_{\bsk_{n+1}} &\le \frac{1}{n^{1/p}} \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
+\lambda_{\bsk_{n+1}} & \le \frac{1}{n^{1/p}} \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \  \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
+\end{align*}
+These upper bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply upper bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp} for all $p > 1/r$:
+\begin{equation*}
+    \text{Algorithm \ref{DHKM:BallAlg}:} \quad \COST(\ALG,\calB_R,\varepsilon, R') 
+    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil,
+    \end{equation*}
+    \begin{multline*}
+    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \\ \le \max \left( n_1, 
+    \left \lceil  \left(\frac{AR}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
+    \end{multline*}
+Note that these costs are $\calO(R^p \varepsilon^{-p})$ for all $p > 1/r$.
+A faster decay rate of the $\lambda_{\bsk}$ due to the faster decay rate of the smoothness coefficients implies smaller information cost.
 }
+
+\FredNote{Fred got to here}
+
+\FredNote{I think that we need a lower bound on $\lambda_{\bsk_{n+1}}$ to obatain lower bounds on the computational complexity. }
 
@@
 w_\ell^p
-\right) \right\}.\]
+\right) \right\}.
+\]
 }

### 2019-08-19 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 This is a generalization of our illustrative example, \eqref{DHKM:IllExWts}, in Section \ref{DHKM:secexamp} where $\bss = (1, 2^{-r}, 3^{-r}, \ldots )$.  
-This form of the $\lambda_{d,\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.
+This form of the $\lambda_{\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.
 
@@
 \norm[p]{\bslambda} &\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
- \norm[p]{\bslambda} & \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
-\end{align*}
+ \norm[p]{\bslambda} & \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1,
+\end{align*}
+where $\zeta$ is the Riemann zeta function.
 \end{lemma}
@@
 Note that these costs are $\calO(R^p \varepsilon^{-p})$ for all $p > 1/r$.
-A faster decay rate of the $\lambda_{\bsk}$ due to the faster decay rate of the smoothness coefficients implies smaller information cost.
+A faster decay rate of the $\lambda_{\bsk}$ due to the faster decay rate of the smoothness coefficients, $s_k$, implies asymptotically smaller information cost.
 }

### 2019-08-29 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 
-%\PeterNote{Should we keep the list of questions in this extensive form?}
-%\YuhanNote{I moved it to introduction}
-
 We return \DHKMchange{to the example of functions on $[-1,1]^d$, using a Chebyshev polynomial basis}, in Section \ref{DHKM:SecPilotTract} to discuss the computational cost and complexity.
@@
 An upper bound on the approximation error follows from Lemma \ref{DHKM:Key_Lem}:
-\begin{equation} \label{DHKM:Refined_APP_err}
+\begin{gather} \label{DHKM:Refined_APP_err}
     \norm[\calG]{\SOL(f) - \APP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
-    \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
-\end{equation}
+    \bignorm[\rho']{\bslambda^{(n+1)}}, \\
+    \intertext{where the tail of $\bslambda$ is defined by}
+    \label{DHKM:taillambds}
+     \bslambda^{(n)} : = \bigl(  \lambda_{\bsk_i}  \bigr)_{i = n}^{\infty}.
+\end{gather}
 This leads to the following theorem.
@@
 \begin{equation} \label{DHKM:APP_errorBd}
-    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}.
+    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
 \end{equation}
@@
 
-    \State Choose $n^* =  \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}$
+    \State Choose $n^* =  \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}$
 
@@
 \[
-\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \le \varepsilon /R \right \}.
+\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}.
 \]
@@
     \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
-    \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} , 
+    \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} , 
     \\ \forall n \ge n_1.
@@
     \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) \\
-    = \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+    = \min \left \{n \ge n_1 : \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} \,
     \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
@@
 \begin{multline} \label{DHKM:PilotConeAlg_comp}
-        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} \,
     \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
@@
      (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1 }} \, 
-     \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}}
+     \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}}
     \le \varepsilon \right \} \\   
      & \le \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} R \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} 
+     (A^\rho -1)^{1/\rho} R \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}}
     \le \varepsilon \right \},  
@@
 =\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
-& \ge \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^\infty},
+& \ge \frac{R(1 - 1/A)}{2} \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} ,
 \end{align*}
@@
 \[ 
-\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \qquad \forall p >0,
+\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \quad \forall p >0, 
+\qquad \sup_{n \in \bbN} \lambda_{\bsk_{n}} n^{\eta/p} \ge \frac{\norm[p]{\bslambda}}{\zeta(\eta)^{1/p}} \quad \forall \eta > 1, \ p>0.
 \]
-provided that $\norm[p]{\bslambda}$ is finite.
 \end{lemma}
@@
     \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
-    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK}^\infty \lambda_{\bsk}^p = \norm[p]{\bslambda}^p \qquad \forall p > 0.
+    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK} \lambda_{\bsk}^p = \norm[p]{\bslambda}^p \qquad \forall p > 0.
 \end{equation*}
@@
    \norm[p]{\bslambda}^ p & 
-   = \sum_{\bsk \in \NN_0^d}^\infty \lambda_{d,\bsk}^p  
+   = \sum_{\bsk \in \NN_0^d} \lambda_{\bsk}^p  
    = \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) 
@@
 These upper bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply upper bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp} for all $p > 1/r$:
-\begin{equation*}
-    \text{Algorithm \ref{DHKM:BallAlg}:} \quad \COST(\ALG,\calB_R,\varepsilon, R') 
-    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil,
-    \end{equation*}
-    \begin{multline*}
-    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
-    \\ \le \max \left( n_1, 
+\begin{align*}
+    \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \COST(\ALG,\calB_R,\varepsilon, R') 
+    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil, \\
+    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \\ & \qquad \qquad \le \max \left( n_1, 
     \left \lceil  \left(\frac{AR}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
-    \end{multline*}
+    \end{align*}
 Note that these costs are $\calO(R^p \varepsilon^{-p})$ for all $p > 1/r$.
@@
 
-\FredNote{I think that we need a lower bound on $\lambda_{\bsk_{n+1}}$ to obatain lower bounds on the computational complexity. }
+\FredNote{I think that we need a lower bound on $\lambda_{\bsk_{n+1}}$ to obtain lower bounds on the computational complexity. }
+
+\PeterNote{Do you mean a general estimate in terms of the other eigenvalues 
+or something specifically for this example?}
+
+\FredNote{Do we want to use $p$ as our exponent or $\eta$ as in the derivations below?}
+
+\PeterNote{As far as I can see, we could unify it, right? I do not mind which letter we use.}
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\FredNote{Here we use $n(\delta,d)$.  On the bottom of p.\ 2 we used $n(f,\varepsilon)$.  Will this cause confusion?  Would it make sense to use $N(\cdot,\cdot)$ for one of of these?}
+
+\PeterNote{I agree it might be confusing, but on the other hand it both is related 
+to $n$. How about taking an index $n_{\mathrm{COMP}}$ for $n(\delta,d)$?} \FredNote{Agreed}
+
 \DHKMchange{
@@
 
-Consider the example in Section \ref{DHKM:secexamp}, we have
+Considering the example in Section \ref{DHKM:secexamp}, we have
 \begin{align*}
@@
 
-Let's revisit the example in Section \ref{DHKM:secexamp}. For this example,
+Let us revisit the example in Section \ref{DHKM:secexamp}. For this example,
 we choose $n_j = n_02^j,$ thus
 \[\calK_j = \{\bsk_{n_0 2^{j-1}+1}, \ldots, \bsk_{n_02^j}\} \quad \text{for } j \in \N \qquad \text{ and } \calK_1 = \{\bsk_{1}, \ldots, \bsk_{n_0}\}.\]
-For example, we have $\rho = \tau = 2$, $\rho' = \infty$. Therefore
+For the example, we have $\rho = \tau = 2$, $\rho' = \infty$. Therefore
 \[\Lambda_j = \|(\lambda_\bsk)_\bsk \in \calK_j\|_{\rho'} = \lambda_{\bsk_{n_0 2^{j-1}+1}}.\]
@@
 \right),\]
-where $0< 1/r< p$.
+where $0< 1/r< p$. Then,
 \begin{align*}
@@
 \frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
-\right)^{1/\tau}
+\right)^{1/\tau}.
 \end{align*}

### 2019-09-01 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 \theoremstyle{dgthm}
-\newtheorem{lemma}{Lemma}
+\newtheorem{lemma}[theorem]{Lemma}
 \theoremstyle{dgthm}
-\newtheorem{corollary}{Corollary}
+\newtheorem{corollary}[theorem]{Corollary}
 \theoremstyle{dgthm}
-\newtheorem{proposition}{Proposition}
+\newtheorem{proposition}[theorem]{Proposition}
 \theoremstyle{dgdef}
@@
     \intertext{where the tail of $\bslambda$ is defined by}
-    \label{DHKM:taillambds}
+    \label{DHKM:taillambda}
      \bslambda^{(n)} : = \bigl(  \lambda_{\bsk_i}  \bigr)_{i = n}^{\infty}.
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Illustrative Example Revisited}\label{DHKM:revisexamp}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Bounds on the Information Cost for $\rho = \tau$, $\rho'=\infty$}\label{DHKM:revisexamp}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \DHKMchange{
-We now interpret the information cost upper bounds of Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} for the example introduced in Section \ref{DHKM:secexamp}, where $\rho = \tau = 2$ and $\rho' = \infty$.
-In this case, $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$.
-To facilitate this interpretation we establish a couple of commonly used lemmas.
+We now derive upper and lower bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the case  $\rho = \tau$ and $\rho' = \infty$, which includes the example introduced in Section \ref{DHKM:secexamp}.
+For $\rho'=\infty$, $\bignorm[\rho']{\bslambda^{(n+1)}} = \lambda_{\bsk_{n+1}}$.
+To facilitate these bounds we establish a couple of commonly used lemmas.
 
@@
 Consider the ordered weights,
-$\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$
-then we have
+$\lambda_{\bsk_{1}} \ge \lambda_{\bsk_{2}} \ge \cdots > 0,$ and recall from \eqref{DHKM:taillambda} that $\bslambda^{(n)} = (\lambda_{\bsk_n}, \lambda_{\bsk_{n+1}}, \ldots )$.  It follows that 
 \[ 
-\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \quad \forall p >0, 
-\qquad \sup_{n \in \bbN} \lambda_{\bsk_{n}} n^{\eta/p} \ge \frac{\norm[p]{\bslambda}}{\zeta(\eta)^{1/p}} \quad \forall \eta > 1, \ p>0.
+\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \ \ \text{and} \ \ 
+ \sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} \ge \frac{\bignorm[p\eta]{\bslambda^{(n_{\min})}}}{\zeta(\eta)^{1/(p\eta)}} \quad \forall p>0, \ \eta > 1, \ n_{\min} \in \bbN.
 \]
@@
 \end{equation*}
-Dividing both sides by $n$ and taking the $p^{\text{th}}$ root completes the proof.
+Dividing both sides by $n$ and taking the $p^{\text{th}}$ root completes the proof of the first inequality.
+
+To prove the second inequality, we employ H\"older's inequality to show that
+\begin{equation*}
+    \bignorm[p\eta]{\bslambda^{(n_{\min})}}^{p\eta} 
+    = \sum_{n=n_{\min}}^\infty \frac{\lambda_{\bsk_n}^{p\eta} n^\eta }{n^\eta} 
+    \le \sup_{n \ge n_{\min}}\lambda_{\bsk_n}^{p\eta} n^\eta \ \sum_{n=n_{\min}}^\infty \frac{1}{n^\eta} \le \sup_{n \ge n_{\min}}\lambda_{\bsk_n}^{p\eta} n^\eta  \zeta(\eta),
+\end{equation*}
+where $\zeta$ is the Riemann zeta function.  The proof is completed by taking the $p\eta^{\text{th}}$ root and rearranging the terms.
+\end{proof}
+
+\bigskip
+
+These upper and lower bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply relate the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} to the decay rate of the elements of $\bslambda$.
+
+\begin{theorem} \label{DHKM:thm:costbdspilot}
+If the elements of $\bslambda$ decay fast enough so that $\norm[p]{\bslambda} < \infty$, then the information cost of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are bounded above by
+\begin{align*}
+    \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \COST(\ALG,\calB_R,\varepsilon, R') 
+    \le \left \lceil  \left(\frac{R \norm[p]{\bslambda}}{\varepsilon}\right)^p     \right \rceil, \qquad \forall \varepsilon, R > 0, \\
+    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \\ & \qquad \qquad \le \max \left( n_1, 
+    \left \lceil  \left(\frac{AR \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil \right).
+    \end{align*}
+Conversely, for fixed $R', R$ with $0 < R' < R$, if either
+\begin{align*}
+    \COST(\ALG,\calB_R,\varepsilon, R') 
+    \le C \varepsilon^{-p} & \quad \forall \varepsilon \in (0,\varepsilon_{\max}] \quad  \text{for Algorithm \ref{DHKM:BallAlg}, or }  \\
+     \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \le C \varepsilon^{-p} & \quad \forall \varepsilon \in (0,\varepsilon_{\max}] \quad \text{for Algorithm \ref{DHKM:PilotConeAlg}},
+    \end{align*}
+then $\norm[p\eta]{\bslambda} < \infty$ for all $\eta > 1$.
+\end{theorem}
+\begin{proof}
+We give the proof for Algorithm \ref{DHKM:PilotConeAlg}, which is similar to the proof for Algorithm \ref{DHKM:BallAlg}.
+From \eqref{DHKM:PilotConeAlg_cost} it follows that the information cost for  Algorithm \ref{DHKM:PilotConeAlg} in the case of $\rho'=\infty$ is
+\begin{align*} 
+    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) 
+    & = \min \left \{n \ge n_1 : \lambda_{\bsk_{n+1}}
+    \le \frac{\varepsilon}{AR} \right \} \\
+  & \le  \min \left \{n \ge n_1 : \norm[p]{\bslambda}n^{-1/p}
+    \le \frac{\varepsilon}{AR} \right \} \quad  \text{by Lemma \ref{DHKM:lambdineq}} \\
+  & = \left \lceil  \left(\frac{AR \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil.
+\end{align*}
+Now suppose that $\COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \le C \varepsilon^{-p}$ for all $\varepsilon \in (0,\varepsilon_{\max}]$ and let $n_{\min} = \lfloor C \varepsilon_{\max}^{-p} \rfloor$. 
+    According to Lemma \ref{DHKM:lambdineq}, it follows that for all $\eta > 1$,
+    \begin{align*}
+       \bignorm[p\eta]{\bslambda^{(n_{\min})}}  
+       &\le  \zeta(\eta)^{1/(p\eta)} \sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} \\
+       &=  \zeta(\eta)^{1/(p\eta)} \sup_{0 < \varepsilon \le \varepsilon_{\max}} \lambda_{\bsk_{\lfloor C \varepsilon^{-p} \rfloor+1}} (\lfloor C \varepsilon^{-p} \rfloor+1)^{1/p} \\
+        & \hspace{3cm} \text{by the definition of } n_{\min} \\
+        & =  \zeta(\eta)^{1/(p\eta)} \sup_{0 < \varepsilon \le \varepsilon_{\max}} \frac{\varepsilon \, (\lfloor C \varepsilon^{-p} \rfloor+1)^{1/p}}{
+        AR} < \infty\\
+        & \hspace{3cm} \text{since } \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \le C \varepsilon^{-p}
+    \end{align*}
+    Since $\bignorm[p\eta]{\bslambda^{(n_{\min})}}$ is finite, it follows that $\bignorm[p\eta]{\bslambda}$ is finite.
 \end{proof}
@@
 For $\bslambda = \bigl(\lambda_{\bsk} \bigr)_{\bsk \in \bbN_0^d}$ defined in \eqref{DHKM:prodwts}
-we have 
-\begin{align*}
-\norm[p]{\bslambda} &\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
- \norm[p]{\bslambda} & \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1,
-\end{align*}
-where $\zeta$ is the Riemann zeta function.
+we have the following lower and upper bounds on $\norm[p]{\bslambda}$.  For general $\bss$ it follows that 
+\begin{gather*}
+\norm[p]{\bss} \norm[p]{\bsw} \le \norm[p]{\bslambda}\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \\
+[\zeta(pr)]^{1/p} \norm[p]{\bsw} \le \norm[p]{\bslambda} \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, \ldots ), \ pr > 1.
+\end{gather*}
 \end{lemma}
+
 \begin{proof}
-The proof proceeds by straightforward calculation under the assumption that $\norm[p]{\bss}$ is finite:
-\begin{align*}
-   \norm[p]{\bslambda}^ p & 
+The proof is constructed first for general $\bss$.  By straightforward calculation,
+\begin{equation} \label{DHKM:lambdaprodwts}
+   \norm[p]{\bslambda}^ p 
    = \sum_{\bsk \in \NN_0^d} \lambda_{\bsk}^p  
@@
    = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right) 
-   \qquad \text{ by \eqref{DHKM:prodwts} }\\
-    & = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\norm[p]{\bss}^p \bigr) \right)\\
+   \quad \text{ by \eqref{DHKM:prodwts} }
+\end{equation}
+A lower bound is obtained by noting from the equation above that 
+\begin{equation*}
+   \norm[p]{\bslambda}^ p 
+   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right)  
+   \ge  \norm[p]{\bss}^p \sum_{\ell =1}^d w_\ell^p = \norm[p]{\bss}^p \norm[p]{\bsw}^p
+\end{equation*}
+Taking the $p^{\text{th}}$ root completes the proof of the lower bound.  For the upper bound \eqref{DHKM:lambdaprodwts} implies that 
+\begin{align*}
+   \norm[p]{\bslambda}^ p
+   & = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right)
+   = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\norm[p]{\bss}^p \bigr) \right)\\
  &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p} \norm[p]{\bss}^p \right) = \exp\left(\norm[p]{\bsw}^p\norm[p]{\bss}^p \right)
@@
 \end{align*}
-Taking the $p^{\text{th}}$ root completes the proof for the general case.
+Again, taking the $p^{\text{th}}$ root completes the proof for general $\bss$.
 For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
@@
 
-Lemmas \ref{DHKM:lambdineq} and \ref{DHKM:prodwtsupperbound} imply upper bounds on $\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n+1}^{\infty}} = \lambda_{\bsk_{n+1}}$:
-\begin{align*}
-\lambda_{\bsk_{n+1}} &\le \frac{1}{n^{1/p}} \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \text{ provided that  $\norm[p]{\bss}$ is finite},\\
-\lambda_{\bsk_{n+1}} & \le \frac{1}{n^{1/p}} \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \  \text{for } \bss = (1, 2^{-r}, 3^{-r}, \ldots ), \text{ provided that } pr > 1.
-\end{align*}
-These upper bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply upper bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp} for all $p > 1/r$:
+Theorem \ref{DHKM:thm:costbdspilot} and Lemma \ref{DHKM:prodwtsupperbound} imply bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp}
+
+\begin{corollary} For the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp}, 
+for all $p > 1/r$:
 \begin{align*}
@@
     \end{align*}
-Note that these costs are $\calO(R^p \varepsilon^{-p})$ for all $p > 1/r$.
-A faster decay rate of the $\lambda_{\bsk}$ due to the faster decay rate of the smoothness coefficients, $s_k$, implies asymptotically smaller information cost.
+Furthermore, these information costs cannot grow any slower than $\calO(\varepsilon^{-1/r})$ for $\varepsilon \downarrow 0$.
+\end{corollary}
 }
@@
 \FredNote{Fred got to here}
-
-\FredNote{I think that we need a lower bound on $\lambda_{\bsk_{n+1}}$ to obtain lower bounds on the computational complexity. }
-
-\PeterNote{Do you mean a general estimate in terms of the other eigenvalues 
-or something specifically for this example?}
 

### 2019-09-04 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 $$
-for a suitably chosen homogeneous function $h:\bbR\to [0,\infty)$. This means that the norm of $f$ can be bounded well in terms of 
+for a suitably chosen homogeneous function $h:\bbR^{n_1}\to [0,\infty)$. This means that the norm of $f$ can be bounded well in terms of 
 a \emph{pilot sample} of size $n_1\in\bbN$.
@@
 \]
+If $\norm[p]{\bslambda} = \infty$ or $\sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} = \infty$, we consider these inequalities to be trivially true.
 \end{lemma}
@@
 
-These upper and lower bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} imply relate the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} to the decay rate of the elements of $\bslambda$.
+These upper and lower bounds together with Theorems \ref{DHKM:thm_cost_non_adapt} and \ref{DHKM:PilotCostThm} can be used to relate the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} to the decay rate of the elements of $\bslambda$.
 
 \begin{theorem} \label{DHKM:thm:costbdspilot}
-If the elements of $\bslambda$ decay fast enough so that $\norm[p]{\bslambda} < \infty$, then the information cost of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are bounded above by
+If the elements of $\bslambda$ decay fast enough so that $\norm[p]{\bslambda} < \infty$ and $\rho'=\infty$, then the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are bounded above by
 \begin{align*}
     \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \COST(\ALG,\calB_R,\varepsilon, R') 
-    \le \left \lceil  \left(\frac{R \norm[p]{\bslambda}}{\varepsilon}\right)^p     \right \rceil, \qquad \forall \varepsilon, R > 0, \\
+    \le \left \lceil  \left(\frac{R \norm[p]{\bslambda}}{\varepsilon}\right)^p     \right \rceil, \qquad \forall \varepsilon, \ 0 < R' < R, \\
     \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \\ & \qquad \qquad \le \max \left( n_1, 
-    \left \lceil  \left(\frac{AR \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil \right).
+    \left \lceil  \left(\frac{[(A^\rho -1)^{1/\rho}R] \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil \right).
     \end{align*}
@@
 then $\norm[p\eta]{\bslambda} < \infty$ for all $\eta > 1$.
+Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calA(\calB_R),\varepsilon,R')$ and $\COMP(\calA(\calC_{\bslambda,n_1,A}),\varepsilon,R)$.
 \end{theorem}
@@
 We give the proof for Algorithm \ref{DHKM:PilotConeAlg}, which is similar to the proof for Algorithm \ref{DHKM:BallAlg}.
-From \eqref{DHKM:PilotConeAlg_cost} it follows that the information cost for  Algorithm \ref{DHKM:PilotConeAlg} in the case of $\rho'=\infty$ is
+Recall that for $\rho'=\infty$, $\bignorm[\rho']{\bslambda^{(n+1)}} = \lambda_{\bsk_{n+1}}$.
+From \eqref{DHKM:PilotConeAlg_cost} it follows that the information cost for  Algorithm \ref{DHKM:PilotConeAlg} is
 \begin{align*} 
@@
     & = \min \left \{n \ge n_1 : \lambda_{\bsk_{n+1}}
-    \le \frac{\varepsilon}{AR} \right \} \\
+    \le \frac{\varepsilon}{[(A^\rho -1)^{1/\rho}R]} \right \} \\
   & \le  \min \left \{n \ge n_1 : \norm[p]{\bslambda}n^{-1/p}
-    \le \frac{\varepsilon}{AR} \right \} \quad  \text{by Lemma \ref{DHKM:lambdineq}} \\
-  & = \left \lceil  \left(\frac{AR \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil.
+    \le \frac{\varepsilon}{[(A^\rho -1)^{1/\rho}R]} \right \} \\
+    & \qquad \qquad \text{by Lemma \ref{DHKM:lambdineq} since } \lambda_{\bsk_{n+1}} \le \norm[p]{\bslambda}n^{-1/p}\\
+  & = \left \lceil  \left(\frac{[(A^\rho -1)^{1/\rho}R] \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil.
 \end{align*}
 Now suppose that $\COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
-    \le C \varepsilon^{-p}$ for all $\varepsilon \in (0,\varepsilon_{\max}]$ and let $n_{\min} = \lfloor C \varepsilon_{\max}^{-p} \rfloor$. 
+    \le C \varepsilon^{-p}$ for all $\varepsilon \in (0,\varepsilon_{\max}]$.  Since the information cost is an integer, this means that $\COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \le \lfloor C \varepsilon^{-p} \rfloor$  and let $n_{\min} = \lfloor C \varepsilon_{\max}^{-p} \rfloor +1$. 
     According to Lemma \ref{DHKM:lambdineq}, it follows that for all $\eta > 1$,
@@
         & \hspace{3cm} \text{by the definition of } n_{\min} \\
-        & =  \zeta(\eta)^{1/(p\eta)} \sup_{0 < \varepsilon \le \varepsilon_{\max}} \frac{\varepsilon \, (\lfloor C \varepsilon^{-p} \rfloor+1)^{1/p}}{
+        & \le  \zeta(\eta)^{1/(p\eta)} \sup_{0 < \varepsilon \le \varepsilon_{\max}} \frac{\varepsilon \, (\lfloor C \varepsilon^{-p} \rfloor+1)^{1/p}}{
         AR} < \infty\\
         & \hspace{3cm} \text{since } \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
-    \le C \varepsilon^{-p}
+    \le \lfloor C \varepsilon^{-p} \rfloor.
     \end{align*}
@@
 For $\bslambda = \bigl(\lambda_{\bsk} \bigr)_{\bsk \in \bbN_0^d}$ defined in \eqref{DHKM:prodwts}
-we have the following lower and upper bounds on $\norm[p]{\bslambda}$.  For general $\bss$ it follows that 
+we have the following lower and upper bounds on $\norm[p]{\bslambda}$.  It holds that
 \begin{gather*}
@@
    = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right) 
-   \quad \text{ by \eqref{DHKM:prodwts} }
+   \quad \text{ by \eqref{DHKM:prodwts} .}
 \end{equation}
@@
    = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right)  
-   \ge  \norm[p]{\bss}^p \sum_{\ell =1}^d w_\ell^p = \norm[p]{\bss}^p \norm[p]{\bsw}^p
+   \ge  \norm[p]{\bss}^p \sum_{\ell =1}^d w_\ell^p = \norm[p]{\bss}^p \norm[p]{\bsw}^p.
 \end{equation*}
@@
 
-Theorem \ref{DHKM:thm:costbdspilot} and Lemma \ref{DHKM:prodwtsupperbound} imply bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp}
-
-\begin{corollary} For the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp}, 
-for all $p > 1/r$:
+Theorem \ref{DHKM:thm:costbdspilot} and Lemma \ref{DHKM:prodwtsupperbound} imply bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp}.
+
+\begin{corollary}\label{DHKM:cor:illex} 
+For the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp}, for all $p > 1/r$:
 \begin{align*}
@@
     \\ & \qquad \qquad \le \max \left( n_1, 
-    \left \lceil  \left(\frac{AR}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
+    \left \lceil  \left(\frac{(A^\rho-1)^{1/\rho}R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
     \end{align*}
 Furthermore, these information costs cannot grow any slower than $\calO(\varepsilon^{-1/r})$ for $\varepsilon \downarrow 0$.
+Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calA(\calB_R),\varepsilon,R')$ and $\COMP(\calA(\calC_{\bslambda,n_1,A}),\varepsilon,R)$ for the illustrative example in Section \ref{DHKM:secexamp}.
 \end{corollary}
 }
-
-\FredNote{Fred got to here}
-
-\FredNote{Do we want to use $p$ as our exponent or $\eta$ as in the derivations below?}
-
-\PeterNote{As far as I can see, we could unify it, right? I do not mind which letter we use.}
 
@@
 
-\FredNote{Here we use $n(\delta,d)$.  On the bottom of p.\ 2 we used $n(f,\varepsilon)$.  Will this cause confusion?  Would it make sense to use $N(\cdot,\cdot)$ for one of of these?}
-
-\PeterNote{I agree it might be confusing, but on the other hand it both is related 
-to $n$. How about taking an index $n_{\mathrm{COMP}}$ for $n(\delta,d)$?} \FredNote{Agreed}
+\FredNote{As far as simplifications go,
+
+1) If we like the $\bslambda^{(n)}$ notation and even want to write $\bslambda^{(n)}_d$ to emphasize the $d$ dependence, then we can simplify some of the equations below.}
+
+\PeterNote{I am not sure. I have the impression that with the additional restriction 
+that many sums do not start with index 1, but with indices depending on $d$ and other parameters, it might make notation overly complicated... .
+I mostly left it as it is. But if you prefer, we can still change it!}
+
+\FredNote{I commented out where I thought we could introduce the notation.  Let me know what you think.}
+
+\PeterNote{I agree. Let us use your notation, it makes it more consistent.}
 
@@
 \item We say that the adaptive approximation problem is strongly polynomially tractable
-if and only if there are non-negative $C$, $p$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
+if and only if there are non-negative $C$, $\widetilde{p}$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
 $$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,R^p\,\varepsilon^{-p} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,R^{\widetilde{p}}\,\varepsilon^{-\widetilde{p}} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
 $$   
-The infimum of $p$ satisfying the bound above is denoted by $p^*$   
-and is called the exponent of strong polynomial tractability.    
+The infimum of $\widetilde{p}$ satisfying the bound above is denoted by $\widetilde{p}_*$  and is called the exponent of strong polynomial tractability.    
 \newline \qquad
@@
 We say that the problem is polynomially tractable
-if and only if there are non-negative $C,p$, $q$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
+if and only if there are non-negative $C,\widetilde{p}$, $q$, and positive $\varepsilon_{\max}$, and $R_{\min}$ such that   
 $$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,R^p\,   
-\varepsilon^{-p}\qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).  
+\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,R^{\widetilde{p}}\,   
+\varepsilon^{-{\widetilde{p}}}\qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).  
 $$   
@@
 \end{itemize}   
-
 Necessary and sufficient conditions on these tractability notions will be studied 
@@
 
-Considering the example in Section \ref{DHKM:secexamp}, we have
+Returning again to the example in Section \ref{DHKM:secexamp}, we have, by Corollary \ref{DHKM:cor:illex}
 \begin{align*}
     \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} 
-  \le \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right) \right \rceil .
-\end{align*}
-
-If $p^\dagger$ is the infimum of the $p$ for which $\sum_{\ell = 1}^{\infty} w_\ell^{p}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $p^* = \max(1/r,p^\dagger)$.
+  \le \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \norm[p]{\bsw}^p  \right) \right \rceil .
+\end{align*}
+If $p^\dagger$ is the infimum of the $p$ for which $\norm[p]{\bsw}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $\widetilde{p}_* = \max(1/r,p^\dagger)$.
 On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.\\
@@
 $\lambda_{d,\bsk_1}\ge \lambda_{d,\bsk_2}\ge \cdots >0$. Let 
+% \[
+% n_{\COMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+%     \le \delta \right \} \qquad \forall \delta > 0.
+% \]
 \[
-n(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
-    \le \delta \right \} \qquad \forall \delta > 0.
+n_{\COMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bslambda^{(n+1)}_d} \,
+    \le \delta \right \} \qquad \forall \delta > 0,
 \]
+where as in \eqref{DHKM:taillambda} $\bslambda_d^{(n)} := (\lambda_{d,\bsk_n}, \lambda_{d,\bsk_{n+1}}, \ldots )$
 From 
@@
 \begin{multline*}
-     \COMP(\calA(\calC_d),\omega_{\textup{lo}} \varepsilon,R) \le n(\varepsilon/R,d) \le 
+     \COMP(\calA(\calC_d),\omega_{\textup{lo}} \varepsilon,R) \le n_{\COMP}(\varepsilon/R,d) \le 
         \COMP(\calA(\calC_d),\omega_{\textup{hi}} \varepsilon,R)  \\
@@
 where the positive constants $\omega_{\textup{lo}}$ and $\omega_{\textup{hi}}$  depend on $A$, but do not depend on $d$, $\varepsilon$, or $R$.
-From the equation above, it is clear that tractability depends on the behavior of $n(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity.
+From the equation above, it is clear that tractability depends on the behavior of $n_{\COMP}(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity.
 We would like to study under which conditions we obtain the various tractability notions defined above.
@@
 \[
-n(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
+n_{\COMP}(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
     \le \varepsilon/R \right \}.
@@
   \item[1.] 
-  We have strong polynomial tractability if and only if there exist $\eta>0$ and $i_0\in\NN$ such that
+  We have strong polynomial tractability if and only if there exist $p>0$ and $i_0\in\NN$ such that
+%  \begin{equation}\label{DHKM:eq:condspt}
+%     \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^p < \infty.
+%  \end{equation}
  \begin{equation}\label{DHKM:eq:condspt}
-    \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^\eta < \infty.
- \end{equation}
- Furthermore, the exponent of strong polynomial tractability is then equal to the infimum of those $\eta>0$ for which \eqref{DHKM:eq:condspt} holds. 
+    \sup_{d\in\NN} \, \bignorm[p]{\bslambda_d^{(i_0)}} < \infty.
+ \end{equation}
+ Furthermore, the exponent of strong polynomial tractability is then equal to the infimum of those $p>0$ for which \eqref{DHKM:eq:condspt} holds. 
  \item[2.] 
-  We have polynomial tractability if and only if there exist $\eta_1, \eta_2 \ge 0$ and $\eta_3, K>0$ such that
+  We have polynomial tractability if and only if there exist $p_1, p_2 \ge 0$ and $p_3, K>0$ such that
+%  \[
+%     \sup_{d\in\NN} d^{-p_1}\, \sum_{i=\lceil K d^{p_2} \rceil}^\infty \lambda_{d,\bsk_i}^{p_3} < \infty.
+%  \]
  \[
-    \sup_{d\in\NN} d^{-\eta_1}\, \sum_{i=\lceil K d^{\eta_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\eta_3} < \infty.
+    \sup_{d\in\NN} d^{-p_1}\, \bignorm[p_3]{\bslambda_d^{(\lceil K d^{p_2} \rceil)}} < \infty.
  \]
@@
 Letting $\widetilde{\varepsilon}:=\sqrt{\varepsilon/R}$, we see that 
-$n(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
+$n_{\COMP}(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
 The latter expression is well studied in the context of tractability of linear problems in the worst-case setting defined on unit balls of certain spaces, and if and only if conditions on the $\lambda_{d,\bsk_i}$ for various tractability notions are known.
@@
 Since, in this chapter, we consider $\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \varepsilon/R \right \}$, and in \cite{NovWoz08a} and \cite{WerWoz17} $\varepsilon /R$ is replaced by the square of the error tolerance,
-there are slight differences between the results here and those in the aforementioned references; to be more precise, the exponent of strong polynomial tractability is $\eta$ here, whereas it is $2\eta$ in \cite{NovWoz08a}, and $1/\lambda_{d,\bsk_i}$ in \eqref{DHKM:eq:condwt} corresponds to $1/\sqrt{\lambda_{d,\bsk_i}}$ in \cite{WerWoz17}.
+there are slight differences between the results here and those in the aforementioned references; to be more precise, the exponent of strong polynomial tractability here is, formally speaking, half of the exponent in in \cite{NovWoz08a}, and $1/\lambda_{d,\bsk_i}$ in \eqref{DHKM:eq:condwt} corresponds to $1/\sqrt{\lambda_{d,\bsk_i}}$ in \cite{WerWoz17}.
 \end{proof}
@@
 $\widetilde{\lambda}_{d,i}:=\lambda_{d,\bsk_i}^{\rho'}$, we have 
+% \begin{align}
+%     \nonumber 
+%     n_{\COMP}(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
+% \sum_{i=n+1}^\infty \lambda_{d,\bsk_i}^{\rho'}\,
+%     \le (\varepsilon/R)^{\rho'} \right \} \\
+%     \label{DHKM:eqaveragetract}
+%     & =\min \left \{n\ge 0\colon 
+% \sum_{i=n+1}^\infty \widetilde{\lambda}_{d,i}\,
+%     \le \widetilde{\varepsilon}^{\,2} \right \}.
+% \end{align}
 \begin{align}
     \nonumber 
-    n(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
-\sum_{i=n+1}^\infty \lambda_{d,\bsk_i}^{\rho'}\,
+    n_{\COMP}(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
+\bignorm[\rho']{\bslambda_d^{(n+1)}}\,
     \le (\varepsilon/R)^{\rho'} \right \} \\
@@
     & =\min \left \{n\ge 0\colon 
-\sum_{i=n+1}^\infty \widetilde{\lambda}_{d,i}\,
+\bignorm[1]{\widetilde{\bslambda}_d^{(n+1)}}\,
     \le \widetilde{\varepsilon}^{\,2} \right \}.
@@
   \item[1.] 
-  We have strong polynomial tractability if and only if there exist $\eta\in (0,1)$ and $i_0\in\NN$ such that
+  We have strong polynomial tractability if and only if there exist $p\in (0,1)$ and $i_0\in\NN$ such that
+%  \begin{equation}\label{DHKM:eq:condspt1}
+%     \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^{\rho'\,p} < \infty.
+%  \end{equation}
  \begin{equation}\label{DHKM:eq:condspt1}
-    \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^{\rho'\,\eta} < \infty.
+    \sup_{d\in\NN} \bignorm[\rho, p]{\bslambda_d^{(i_0)}} < \infty.
  \end{equation}
@@
  \[
- \inf\left\{\rho'\eta/(1-\eta)\colon \mbox{$\eta$ satisfies \eqref{DHKM:eq:condspt1}}\right\}.
+ \inf\left\{\rho'p/(1-p)\colon \mbox{$p$ satisfies \eqref{DHKM:eq:condspt1}}\right\}.
  \]
  \item[2.] 
-  We have polynomial tractability if and only if there exist $\eta_1, \eta_2 \ge 0$ and $\eta_3\in (0,1), K>0$ such that
+  We have polynomial tractability if and only if there exist $p_1, p_2 \ge 0$ and $p_3\in (0,1), K>0$ such that
+%  \[
+%     \sup_{d\in\NN} d^{-p_1}\, \sum_{i=\lceil K d^{p_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\rho'\,p_3} < \infty.
+%  \]
   \[
-    \sup_{d\in\NN} d^{-\eta_1}\, \sum_{i=\lceil K d^{\eta_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\rho'\,\eta_3} < \infty.
+    \sup_{d\in\NN} d^{-p_1}\, \bignorm[\rho' p_3]{\bslambda_d^{(\lceil K d^{p_2} \rceil)}} < \infty.
  \]
- \item[3.] Let $t_{d,i}:=\sum_{k=i}^\infty \lambda_{d,\bsk_i}$.
+ \item[3.] Let $t_{d,i}:=\sum_{\ell=i}^\infty \lambda_{d,\bsk_{\ell}}$. \FredNote{Here we have a problem since $i$ is both a summation index and limit.} \PeterNote{I think it should be ok now (?).}
  We have weak tractability if and only if 
@@
 \DHKMchange{
-To be more concrete, we consider the situation 
+To be more concrete, we return to the situation where the $\lambda_{d,\bsk}$ are given 
+as in \eqref{DHKM:prodwts}  one more time. We note that
+% Below, we write $\bslambda_d$ for the 
+% sequence of the $\lambda_{d,\bsk}$
+% Considering Condition \eqref{DHKM:eq:condspt} in Theorem \ref{DHKM:thmtract1}, note that
+% \[
+% \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^p = \sup_{d\in\NN} \norm[p]{\bslambda_d^{(i_0)}}^p.
+% \]
+% Since we assumed that the $\lambda_{d,\bsk}$ are ordered, 
+$\bignorm[p]{\bslambda_d^{(i_0)}}^p<\infty$ holds if and only if  $\bignorm[p]{\bslambda_d}^p<\infty$.
+We denote the $d$-dependence of the vector of coordinate weights by writing $\bsw_d:=(w_1, \ldots, w_d)$ and $\bsw_\infty = (w_1, w_2, \ldots)$
+By Lemma \ref{DHKM:prodwtsupperbound}, we have
 \[
-\lambda_{d,\bsk}  := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d w_\ell s_{k_\ell}, \qquad \bsk \in \NN_0^d, \ d \in \NN,
-\] one more time.
-By Lemma \ref{DHKM:prodwtsupperbound}, we have
-}
-\[
-\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} \le \exp\left(\sum_{k=1}^\infty s_k^\eta \sum_{\ell = 1}^{d} w_\ell^{\eta} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^\eta \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right).
+\norm[p]{\bss} \norm[p]{\bsw_d} \le \norm[p]{\bslambda_d}\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw_d}^p  \right),
 \]
-Moreover, it also follows that for any fixed positive integer $i_0$, the sum of the $\lambda_{d,\bsk_i}^\eta$ is bounded below as
-\begin{align*}
-    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge w_1^\eta \sum_{\DHKMchange{i=i_0}}^{\infty}s_{\DHKMchange{k_i}}^{\eta} \qquad \parbox{8cm}{considering only $\bsk_i$ of the form $(k, 0, 0, \ldots, 0)$, \\
-    and ordering $\bss$ so that $\DHKMchange{s_{k_1} \ge s_{k_2} \ge \cdots}$,} \\
-    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge  s_{1}^{\eta} \sum_{i=i_0}^{\infty} w_{\ell_i}^\eta
+and this estimate holds for any $d\in\NN$.
+%\[
+%\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} \le \exp\left(\sum_{k=1}^\infty s_k^\eta %\sum_{\ell = 1}^{d} w_\ell^{\eta} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^\eta \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right).
+%\]
+%Moreover, it also follows that for any fixed positive integer $i_0$, the sum of the $\lambda_{d,\bsk_i}^\eta$ is bounded below as
+%\begin{align*}
+%    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge w_1^\eta \sum_{\DHKMchange{i=i_0}}^{\infty}s_{\DHKMchange{k_i}}^{\eta} \qquad \parbox{8cm}{considering only $\bsk_i$ of the form $(k, 0, 0, \ldots, 0)$, \\
+%    and ordering $\bss$ so that $\DHKMchange{s_{k_1} \ge s_{k_2} \ge \cdots}$,} \\
+%    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge  s_{1}^{\eta} \sum_{i=i_0}^{\infty} w_{\ell_i}^\eta
     %\qquad %\text{for } d \ge i_0 
     %\\ &
-    \qquad \parbox{8cm}{considering only $\bsk_i$ of the form\\  $(0, \ldots, 0,1,0 , \ldots, 0)$,
-    where the non-zero\\ component is at the $\ell$-th   position with 
-    $i_0\le \ell \le d$,\\ and ordering $\bsw$  so that $w_{\ell_1} \ge w_{\ell_2} \ge \cdots$.}
-\end{align*}
+%    \qquad \parbox{8cm}{considering only $\bsk_i$ of the form\\  $(0, \ldots, 0,1,0 , \ldots, 0)$,
+%    where the non-zero\\ component is at the $\ell$-th   position with 
+%    $i_0\le \ell \le d$,\\ and ordering $\bsw$  so that $w_{\ell_1} \ge w_{\ell_2} \ge \cdots$.}
+%\end{align*}
 Thus, we have necessary and sufficient conditions for strong tractability.
 \begin{corollary} \label{DHKM:sptexample_cor}
-For the $\lambda_{d,\bsk}$ of the form \eqref{DHKM:prodwts} we have strong polynomial tractability if and only if there exists $\eta>0$ such that
+For the $\lambda_{d,\bsk}$ of the form \eqref{DHKM:prodwts} we have strong polynomial tractability if and only if there exists $p>0$ such that
  \begin{equation*}
 %\label{DHKM:sptexample}
-    \sum_{k=1}^\infty s_{k}^\eta < \infty \text{ and } 
-    \sum_{\ell = 1}^{\infty} w_\ell^{\eta} < \infty.
-\end{equation*}
-\DHKMchange{In particular, considering example in Section \ref{DHKM:secexamp}, where $s_{k} = k^{-r}$, we have strong polynomial tractability if and only if there exists $\eta> 0 $ such that
+    \norm[p]{\bss} < \infty \text{ and } 
+    \norm[p]{\bsw_\infty} < \infty.
+\end{equation*}
+In particular, considering example in Section \ref{DHKM:secexamp}, where $s_{k} = k^{-r}$, we have strong polynomial tractability if and only if there exists $p> 0 $ such that
 \begin{equation*}
 %\label{DHKM:sptexample}
-   r \eta > 1 \text{ and } 
-    \sum_{\ell = 1}^{\infty} w_\ell^{\eta} < \infty.
-\end{equation*}}
+   r p > 1 \text{ and } 
+    \norm[p]{\bsw_\infty} < \infty.
+\end{equation*}
 \end{corollary}
@@
 Note that in the setting of this example, the term 
-$\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta}$ will usually depend exponentially on $d$ unless the 
-coordinate weights decay to zero fast enough with increasing $\ell$. Hence, we can only hope for tractability under the presence of decaying $w_\ell$. For further details on weighted approximation
+$\bignorm[p]{\bslambda_d}^p$
+%$\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta}$ 
+will usually depend exponentially on $d$ unless the 
+coordinate weights, $w_\ell$, decay to zero fast enough with increasing $\ell$.
+Hence, we can only hope for tractability under the presence of decaying $w_\ell$.
+For further details on weighted approximation
 problems and tractability, we refer to \cite{NovWoz08a}.
 \end{remark}
+}
 

### 2019-09-14 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 \[
-\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}.
+\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}, \qquad R’ \in (0, R].
 \]
@@
 \begin{multline*}
-\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R),\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
+\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R),\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
 \end{multline*}
@@
 
-\YuhanNote{Create a new subsection and move the content related with the example here}
 \DHKMchange{
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\FredNote{As far as simplifications go,
-
-1) If we like the $\bslambda^{(n)}$ notation and even want to write $\bslambda^{(n)}_d$ to emphasize the $d$ dependence, then we can simplify some of the equations below.}
-
-\PeterNote{I am not sure. I have the impression that with the additional restriction 
-that many sums do not start with index 1, but with indices depending on $d$ and other parameters, it might make notation overly complicated... .
-I mostly left it as it is. But if you prefer, we can still change it!}
-
-\FredNote{I commented out where I thought we could introduce the notation.  Let me know what you think.}
-
-\PeterNote{I agree. Let us use your notation, it makes it more consistent.}
 
@@
 
-\begin{theorem} \label{DHKM:thmtract1}
+\DHKMchange{\begin{theorem} \label{DHKM:thmtract1}
 Using the same notation as above, the following statements hold for the case $\rho'=\infty$.
@@
   We have strong polynomial tractability if and only if there exist $p>0$ and $i_0\in\NN$ such that
-%  \begin{equation}\label{DHKM:eq:condspt}
-%     \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^p < \infty.
-%  \end{equation}
  \begin{equation}\label{DHKM:eq:condspt}
@@
   We have polynomial tractability if and only if there exist $p_1, p_2 \ge 0$ and $p_3, K>0$ such that
-%  \[
-%     \sup_{d\in\NN} d^{-p_1}\, \sum_{i=\lceil K d^{p_2} \rceil}^\infty \lambda_{d,\bsk_i}^{p_3} < \infty.
-%  \]
  \[
@@
 \end{theorem}
+}
 
 \begin{proof}
-Letting $\widetilde{\varepsilon}:=\sqrt{\varepsilon/R}$, we see that 
+If $\widetilde{\varepsilon}:=\sqrt{\varepsilon/R}$, then
 $n_{\COMP}(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
@@
 
-In this case, letting $\widetilde{\varepsilon}:=(\varepsilon/R)^{\rho'/2}$ and 
+\DHKMchange{In this case, letting $\widetilde{\varepsilon}:=(\varepsilon/R)^{\rho'/2}$ and 
 $\widetilde{\lambda}_{d,i}:=\lambda_{d,\bsk_i}^{\rho'}$, we have 
-% \begin{align}
-%     \nonumber 
-%     n_{\COMP}(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
-% \sum_{i=n+1}^\infty \lambda_{d,\bsk_i}^{\rho'}\,
-%     \le (\varepsilon/R)^{\rho'} \right \} \\
-%     \label{DHKM:eqaveragetract}
-%     & =\min \left \{n\ge 0\colon 
-% \sum_{i=n+1}^\infty \widetilde{\lambda}_{d,i}\,
-%     \le \widetilde{\varepsilon}^{\,2} \right \}.
-% \end{align}
 \begin{align}
@@
   We have strong polynomial tractability if and only if there exist $p\in (0,1)$ and $i_0\in\NN$ such that
-%  \begin{equation}\label{DHKM:eq:condspt1}
-%     \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^{\rho'\,p} < \infty.
-%  \end{equation}
  \begin{equation}\label{DHKM:eq:condspt1}
@@
   We have polynomial tractability if and only if there exist $p_1, p_2 \ge 0$ and $p_3\in (0,1), K>0$ such that
-%  \[
-%     \sup_{d\in\NN} d^{-p_1}\, \sum_{i=\lceil K d^{p_2} \rceil}^\infty \lambda_{d,\bsk_i}^{\rho'\,p_3} < \infty.
-%  \]
   \[
@@
  \]
- \item[3.] Let $t_{d,i}:=\sum_{\ell=i}^\infty \lambda_{d,\bsk_{\ell}}$. \FredNote{Here we have a problem since $i$ is both a summation index and limit.} \PeterNote{I think it should be ok now (?).}
+ \item[3.] 
  We have weak tractability if and only if 
  \[
-   \lim_{i\to\infty} t_{d,i}\, (\log i)^2=0\quad\mbox{for all $d$},
+   \lim_{n\to\infty} (\log n)^2  \, \bignorm[1]{\bslambda_d^{(n)}} =0\quad\mbox{for all $d$},
  \]
@@
   \sup_{\beta\in (0,1/2]}\, \beta^{-2} \,
-  \sup_{d\ge f(\beta)}\,\, \sup_{i\ge \lceil \exp (d\sqrt{b}) \rceil +1}\, \, \lim_{i\to\infty} t_{d,i}\, (\log i)^2
+  \sup_{d\ge f(\beta)}\,\, \sup_{n \ge \lceil \exp (d\sqrt{b}) \rceil +1}\, \, (\log n)^2  \, \bignorm[1]{\bslambda_d^{(n)}} 
   < \infty.
@@
 \end{theorem}
+}
 \begin{proof}
@@
 as in \eqref{DHKM:prodwts}  one more time. We note that
-% Below, we write $\bslambda_d$ for the 
-% sequence of the $\lambda_{d,\bsk}$
-% Considering Condition \eqref{DHKM:eq:condspt} in Theorem \ref{DHKM:thmtract1}, note that
-% \[
-% \sup_{d\in\NN} \sum_{i=i_0}^\infty \lambda_{d,\bsk_i}^p = \sup_{d\in\NN} \norm[p]{\bslambda_d^{(i_0)}}^p.
-% \]
-% Since we assumed that the $\lambda_{d,\bsk}$ are ordered, 
 $\bignorm[p]{\bslambda_d^{(i_0)}}^p<\infty$ holds if and only if  $\bignorm[p]{\bslambda_d}^p<\infty$.
@@
 and this estimate holds for any $d\in\NN$.
-%\[
-%\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} \le \exp\left(\sum_{k=1}^\infty s_k^\eta %\sum_{\ell = 1}^{d} w_\ell^{\eta} \right)\le \exp\left(\sum_{k =1 }^{\infty} s_k^\eta \sum_{\ell = 1}^{\infty} w_\ell^{\eta} \right).
-%\]
-%Moreover, it also follows that for any fixed positive integer $i_0$, the sum of the $\lambda_{d,\bsk_i}^\eta$ is bounded below as
-%\begin{align*}
-%    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge w_1^\eta \sum_{\DHKMchange{i=i_0}}^{\infty}s_{\DHKMchange{k_i}}^{\eta} \qquad \parbox{8cm}{considering only $\bsk_i$ of the form $(k, 0, 0, \ldots, 0)$, \\
-%    and ordering $\bss$ so that $\DHKMchange{s_{k_1} \ge s_{k_2} \ge \cdots}$,} \\
-%    \sup_{d \in \N} \, \sum_{i=i_0}^{\infty}\lambda_{d, \bsk_{i}}^{\eta} & \ge  s_{1}^{\eta} \sum_{i=i_0}^{\infty} w_{\ell_i}^\eta
-    %\qquad %\text{for } d \ge i_0 
-    %\\ &
-%    \qquad \parbox{8cm}{considering only $\bsk_i$ of the form\\  $(0, \ldots, 0,1,0 , \ldots, 0)$,
-%    where the non-zero\\ component is at the $\ell$-th   position with 
-%    $i_0\le \ell \le d$,\\ and ordering $\bsw$  so that $w_{\ell_1} \ge w_{\ell_2} \ge \cdots$.}
-%\end{align*}
 Thus, we have necessary and sufficient conditions for strong tractability.
@@
 
-Let $(n_j)_{j\ge 0}$ be a strictly increasing sequence of non-negative integers.
+Let $\DHKMchange{\bsn = (n_j)_{j\ge 0}}$ be a strictly increasing sequence of non-negative integers.
 This sequence may increase geometrically or algebraically.
@@
 \begin{equation} \label{DHKM:TrackConeDef}
-  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} : =\left\{f\in\calF \colon \sigma_{j+r} (f)\le ab^r \sigma_j (f)\ \forall j,r\in\NN\right\}.
+  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} : =\left\{f\in\calF \colon \sigma_{j+s} (f)\le ab^s \sigma_j (f)\ \forall j,s\in\NN\right\}.
 \end{equation}
 Here, $a$ and $b$ are positive reals with $b< 1 < a$.
-The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $.
+The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $.
 \DHKMchange{We remark that knowing $\sigma_1 (f)$ would already be sufficient to identify 
@@
 
-Because $ab^r$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
+Because $ab^s$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
 However, we expect their partial sums to decay steadily.
-The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ and may behave erratically.
+The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ and may behave erratically.
 Lemma \ref{DHKM:Key_Lem} implies that 
@@
 
-If $f$ belongs to the $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
+If $f$ belongs to the $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
 \begin{align*}
@@
 \end{align*}
-Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone} if we choose
-$A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
-
-From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ and $j \in \bbN$:
+Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone} if we choose
+$A=\left[1 + a^\rho b^\rho/(1 - b^\rho) \right]^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
+
+From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ and $j \in \bbN$:
 \begin{align}
@@
 &
-= \norm[\tau]{ \bigl(\sigma_{j+r}(f) \Lambda_{j+r} \bigr)_{r=1}^\infty}
+= \norm[\tau]{ \bigl(\sigma_{j+s}(f) \Lambda_{j+s} \bigr)_{s=1}^\infty}
 \\
-& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^r\Lambda_{j+r} \bigr)_{r=1}^\infty} =:\ERRNj
+& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^s\Lambda_{j+s} \bigr)_{s=1}^\infty} =:\ERRNj
  \qquad \text{by \eqref{DHKM:TrackConeDef}.}
@@
 To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \DHKMchange{\Theta(i^{-r_\Delta})}$ for some positive $r_\Delta > 1/\rho$.
-For this algebraic case one would normally define $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} $ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
+For this algebraic case one would normally define $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
 \begin{align*}
@@
 for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ to include such functions.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
 Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
@@
 for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} s}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ to include such functions.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} s}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
 Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
@@
 
-The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
+The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
 The following theorem establishes its viability and computational cost.
@@
 
+\iffalse 
 \begin{theorem}\label{DHKM:TractConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
 The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
@@
 \end{equation}
-Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
 \begin{equation} \label{DHKM:TractConejdagger}
@@
 For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
-For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
+For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
 \begin{align*}
@@
 \end{proof} 
-
-\YuhanNote{Create a new version of Theorem 6, as $ \frac{1 - b^{j\rho}}{1 - b^\rho} \ge 1 \forall j$. And based on that, derive the explicit bound of the example. }
+\fi
+
+\YuhanNote{Create a new version of Theorem \ref{DHKM:TractConeCompCost}, as $ \frac{1 - b^{j\rho}}{1 - b^\rho} \ge 1 \forall j$. And based on that, derive the explicit bound of the example. }
 \DHKMchange{
@@
 \begin{theorem}\label{DHKM:TractConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
 The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
@@
 \end{equation}
-Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
 \begin{equation} \label{DHKM:TractConejdagger}
-j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}
+j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{s}\Lambda_{j+s} \bigr)_{s=1}^\infty}
 \le  \frac{b\varepsilon}{Ra^2}\right\}.
@@
 & \ge \sigma_1(f) \ge a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f) \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
-& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^r\Lambda_{j^\dagger+r} \bigr)_{r=1}^\infty}
+& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^s\Lambda_{j^\dagger+s} \bigr)_{r=1}^\infty}
 \qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
@@
 
-Let us revisit the example in Section \ref{DHKM:secexamp}. For this example,
-we choose $n_j = n_02^j,$ thus
-\[\calK_j = \{\bsk_{n_0 2^{j-1}+1}, \ldots, \bsk_{n_02^j}\} \quad \text{for } j \in \N \qquad \text{ and } \calK_1 = \{\bsk_{1}, \ldots, \bsk_{n_0}\}.\]
-For the example, we have $\rho = \tau = 2$, $\rho' = \infty$. Therefore
-\[\Lambda_j = \|(\lambda_\bsk)_\bsk \in \calK_j\|_{\rho'} = \lambda_{\bsk_{n_0 2^{j-1}+1}}.\]
-By Lemma \ref{DHKM:lambdineq} and Lemma \ref{DHKM:prodwtsupperbound}, we obtain
-\[\Lambda_j \le \frac{1}{ n_0^{1/p} 2^{(j-1)/p}} \exp\left(\frac{1}{p}
-\zeta(pr)\sum_{\ell=1}^\infty 
-w_\ell^p
-\right),\]
-where $0< 1/r< p$. Then,
-\begin{align*}
-\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}^\tau
- & =  \sum_{q=1}^\infty
-( b^{j+q}\Lambda_{j+q})^\tau \\
-& \le \sum_{q=1}^\infty b^{(j+q)\tau} 
- \frac{1}{ n_0^{\tau/p} 2^{(j+q-1)\tau/p}} \exp\left(\frac{\tau}{p}
-\zeta(pr)\sum_{\ell=1}^\infty 
-w_\ell^p
-\right)\\
-& = 
-\frac{\exp\left(\frac{\tau}{p}
-\zeta(pr)\sum_{\ell=1}^\infty 
-w_\ell^p
-\right)}{ n_0^{\tau/p} } \sum_{q=1}^\infty 
-\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}\\
-\Leftrightarrow 
-\norm[\tau]{ \bigl(b^{j+q}\Lambda_{j+q} \bigr)_{q=1}^\infty}
- & \le  \frac{\exp\left(\frac{1}{p}
-\zeta(pr)\sum_{\ell=1}^\infty 
-w_\ell^p
-\right)}{ n_0^{1/p} } 
-\left(\sum_{q=1}^\infty 
-\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
-\right)^{1/\tau}.
-\end{align*}
-Therefore, the upper bound of the computation cost is $n_j^\dagger$, where
-\[j^\dagger = \min \left \{j \in \bbN : 
-\left(\sum_{q=1}^\infty 
-\frac{b^{(j+q)\tau}}{2^{(j+q-1)\tau/p}}
-\right)^{1/\tau}
-\le  \frac{b\varepsilon n_0^{1/p}}{Ra^2}\exp\left(\frac{1}{p}
-\zeta(pr)\sum_{\ell=1}^\infty 
-w_\ell^p
-\right) \right\}.
-\]
-}
-
 Although Algorithm \ref{DHKM:TrackConeAlg} tracks the decay rate of the $\hf(\bsk_i)$, the information cost bound and complexity bound in the theorem above do not reflect different decay rates of the $\hf(\bsk_i)$.
 That is a subject for future investigation.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Bounds on the Information Cost for $\rho = \tau$, $\rho' = \infty$}\label{DHKM:SecDecayRhoEqTau}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+We again turn to the special case considered in Section \ref{DHKM:revisexamp}, where $\rho = \tau$ and $\rho' = \infty$.
+Furthermore, we consider a geometric progression of the $n_j$, namely, $\bsn = \bigl (n_02^j \bigr)_{j \in \bbN_0}$, so that
+\[
+\calK_0 = \{\bsk_{1}, \ldots, \bsk_{n_0}\}, \qquad \calK_j = \{\bsk_{n_0 2^{j-1}+1}, \ldots, \bsk_{n_02^j}\} \quad \text{for } j \in \N.
+\]
+Our goal, as in Section \ref{DHKM:revisexamp}, is to derive upper and lower bounds on the information cost of Algorithm \ref{DHKM:TrackConeAlg}.
+
+From Lemma \ref{DHKM:lambdineq} it follows that 
+\begin{equation*}
+    \Lambda_j = \norm[\infty]{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}} = \lambda_{\bsk_{n_02^{j-1}+1}}\le \frac{\norm[p]{\bslambda}}{n_0^{1/p} 2^{(j-1)/p}} \qquad \forall j \in \bbN.
+\end{equation*}
+The key term in the upper bound on the information cost in \eqref{DHKM:TractConejdagger} is
+\begin{align*}
+\norm[\rho]{ \bigl(b^{s}\Lambda_{j+s} \bigr)_{s=1}^\infty}^\rho
+ & =  \sum_{s=1}^\infty
+( b^{j+s}\Lambda_{j+s})^\rho \\
+& \le \sum_{s=1}^\infty  
+ \frac{b^{s\rho} \norm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{(j+s-1)\rho/p}} 
+=  
+ \frac{b^{\rho} \norm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{j\rho/p} (1 - b^{\rho}/2^{\rho/p})}, \\
+\norm[\rho]{ \bigl(b^{s}\Lambda_{j+s} \bigr)_{s=1}^\infty}
+ & \le  
+ \frac{b \norm[p]{\bslambda} }{ n_0^{1/p} 2^{j/p} (1 - b^{\rho}/2^{\rho/p})^{1/\rho}}.
+\end{align*}
+From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TractConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,a,b},\varepsilon,R) \le n_j = n_0 2^j$ for any $j$ satisfying
+\begin{align*}
+    \frac{b \norm[p]{\bslambda} }{ n_0^{1/p} 2^{j/p} (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} &\le \frac{b\varepsilon}{R a^2}, \\
+   \left(\frac{ R a^{2} \norm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p & \le n_0 2^{j},
+\end{align*}
+This argument leads to the following upper bound on the information cost, which is similar to Theorem \ref{DHKM:thm:costbdspilot}.
+Applying Lemma \ref{DHKM:prodwtsupperbound} yields a result analogous to Corollary \ref{DHKM:cor:illex}.
+
+\begin{theorem}
+\label{DHKM:thm:TrackConeExUpBd}
+If the elements of $\bslambda$ decay fast enough so that $\norm[p]{\bslambda} < \infty$ and $\rho'=\infty$, then the information cost of Algorithm \ref{DHKM:TrackConeAlg} is bounded above by
+\begin{multline*}
+\COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon, R) \\
+    \le 
+    \min \left \{n_0 2^j , \ j \in \N_0 : 
+    n_0 2^j \ge \left(\frac{ R a^{2} \norm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p
+    \right\}.
+    \end{multline*}
+For the function spaces defined in the illustrative example in Section \ref{DHKM:secexamp}, for all $p > 1/r$:
+\begin{multline*}
+ \COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon, R) \\
+   \le \min \left \{n_0 2^j , \ j \in \N_0 : 
+    n_0 2^j \ge \left(\frac{ R a^{2}\exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)  }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p \right \}.
+    \end{multline*}
+Thus, the information cost in this case is nearly $\calO(\bigl(R/\varepsilon\bigr)^{1/r})$, with a larger $r$ yielding a lower asymptotic information cost.
+\end{theorem}
+}
 
@@
 
-The following theorem establishes a lower bound on the complexity of our problem for input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$.
+The following theorem establishes a lower bound on the complexity of our problem for input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$.
 The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TractConeCompCost} is essentially no worse than this lower bound.
@@
  %\label{compbdA}
-&\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}),\varepsilon,R) > n_{j^\ddagger}, 
+&\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}),\varepsilon,R) > n_{j^\ddagger}, 
 \intertext{where}
@@
 As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
-We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}\cap \calB_{R}$, which yield the same approximate solution but different true solutions.
-This leads to a lower bound on $\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}),\varepsilon,R)$.
+We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}\cap \calB_{R}$, which yield the same approximate solution but different true solutions.
+This leads to a lower bound on $\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}),\varepsilon,R)$.
 The proof is provided for $\rho' < \infty$.
@@
 
-The first test function $f_1 \in \DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
+The first test function $f_1 \in \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
 \begin{align}
@@
 \end{align}
-It can be verified that the test function lies both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$:
+It can be verified that the test function lies both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$:
 \begin{align}
@@
 
-Now let $\ALG'$ be an arbitrary algorithm in $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}})$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
+Now let $\ALG'$ be an arbitrary algorithm in $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
 Let $\tcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
@@
 Furthermore, define $f_{\pm} = f_1 \pm f_2$.
-It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$:
+It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$:
 \begin{align}
@@
 \end{equation*}
-If any algorithm satisfies the error tolerance $\varepsilon$ for all input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}} \cap \calB_R$ and has information cost no greater than $n_{j^\star}$, then $j^\star$ must satisfy the above inequality.
+If any algorithm satisfies the error tolerance $\varepsilon$ for all input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} \cap \calB_R$ and has information cost no greater than $n_{j^\star}$, then $j^\star$ must satisfy the above inequality.
 By contrast, if the above inequality is violated for any $j^\star$, then the information cost of the successful algorithm must be greater than $n_{j^\star}$.
@@
 \[
-\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}),\omega \varepsilon,R).
+\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}),\omega \varepsilon,R).
 \]
@@
 \begin{proof}
-As pointed out above, $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
-This means that the approximation problem on  $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\DHKMchange{\calC_{\boldsymbol{\lambda},a,b}}$ defined in \eqref{DHKM:pilot_cone}.
+As pointed out above, $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
+This means that the approximation problem on  $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:pilot_cone}.
 This, however, implies that all sufficient conditions in Theorem \ref{DHKM:thmtract1} are also sufficient in the case considered in Theorem \ref{DHKM:thmtract3}.

### 2019-09-14 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 \documentclass[USenglish]{article}
+
+% Some common notation, to help us be consistent
+% \bsk = wavenumber
+% \ell = coordinate index
+% w_\ell = coordinate weight
+% s_k = smoothness weight
+% r = decay rate of wavenumbers
+% \bslambda = weights used to define
 
@@
 Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex} \DHKMchange{or \emph{non-symmetric}}.
-\DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones.
+\DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones, $\calC$.
 \DHKMchange{By a cone, we mean a set of functions where constant multiples of every function in the set also lie in the set.
@@
 
-We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n=n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
+We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
 That is,
@@
 \begin{equation*} 
-  \ALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N,
+  \ALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n(f,\varepsilon) \in \N,
 \end{equation*}
@@
 We study different variants of cones in different sections of this chapter.
+
 The first definition of a cone is given in \eqref{DHKM:pilot_cone}, 
@@
 The rest of this chapter is structured as follows.
-In the next section, we formulate our problem more formally, and we point out some results for non-adaptive algorithms with inputs from balls.
+In the next section, we formulate our problem more formally, including the price definition of the input space, $\calF$, in terms of a weights, $\bslambda$, which reflect the assumed smoothness of the input functions.
+We point out some results for non-adaptive algorithms with inputs from balls.
 Furthermore, we illustrate our theory by
@@
 
-We return \DHKMchange{to the example of functions on $[-1,1]^d$, using a Chebyshev polynomial basis}, in Section \ref{DHKM:SecPilotTract} to discuss the computational cost and complexity.
+We return \DHKMchange{to the example of functions on $[-1,1]^d$, using a Chebyshev polynomial basis}, in Section \ref{DHKM:SecPilotTract} to discuss the information cost and computational complexity.
 We perform some numerical experiments for this example in Section \ref{DHKM:numexamp_sec}.
@@
 \begin{proof} 
-The upper bound on the computational cost of this algorithm is obtained by noting that 
+The upper bound on the information cost of this algorithm is obtained by noting that 
 \begin{align*}
@@
 Because $ab^s$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
-However, we expect their partial sums to decay steadily.
+However, we expect their partial sums to decay \emph{steadily}.
 The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ and may behave erratically.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Adaptive Algorithm and Its Computational Cost} \label{DHKM:SecAdapAlgTrackDecay}
+\subsection{The Adaptive Algorithm and Its Information Cost} \label{DHKM:SecAdapAlgTrackDecay}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
-The following theorem establishes its viability and computational cost.
-In deriving upper bounds on the computational cost and lower bounds on the complexity, we may sacrifice tightness for simplicity.
+The following theorem establishes its viability and information cost.
+In deriving upper bounds on the information cost and lower bounds on the complexity, we may sacrifice tightness for simplicity.
 
@@
 
-\YuhanNote{Create a new version of Theorem \ref{DHKM:TractConeCompCost}, as $ \frac{1 - b^{j\rho}}{1 - b^\rho} \ge 1 \forall j$. And based on that, derive the explicit bound of the example. }
 \DHKMchange{

### 2019-09-15 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 The rest of this chapter is structured as follows.
-In the next section, we formulate our problem more formally, including the price definition of the input space, $\calF$, in terms of a weights, $\bslambda$, which reflect the assumed smoothness of the input functions.
+In the next section, we formulate our problem more formally, including the price definition of the input space, $\calF$, in terms of a sequence of weights, $\bslambda$, which reflect the assumed smoothness of the input functions.
 We point out some results for non-adaptive algorithms with inputs from balls.
@@
 
-Section \ref{DHKM:smoothimportance_sec} considers the case where the most suitable weights $\bslambda$, which are used to define the input space, are not known a priori and are instead inferred from function data.
+Section \ref{DHKM:smoothimportance_sec} considers the case where the most suitable weights $\bslambda$, which are used to define the input space, $\calF$, are not known a priori and are instead themselves inferred from function data.
 Adaptive Algorithm \ref{DHKM:InfPilotConeAlg} combines this inference step with Algorithm \ref{DHKM:PilotConeAlg} to construct an approximation that satisfies the error criterion.
@@
 The Banach spaces of inputs and outputs are defined by series expansions:
-\DHKMchange{
 \begin{gather*}
@@
 \end{gather*}
-}%
-Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, and $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, $\mathbb{K}$ is a countable index set, and $\bslambda = (\lambda_\bsk)_{\bsk \in \mathbb{K}}$ is the sequence of weights.
+
+Here, $\{u_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the input Banach space $\calF$, $\{v_{\bsk}\}_{\bsk \in \mathbb{K}}$ is a basis for the output Banach space $\calG$, and $\mathbb{K}$ is a countable index set.
 These bases are defined to match the solution operator:
@@
 \end{equation}
-The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.  The larger $\lambda_{\bsk}$ is, the more important $\hf(\bsk)$ is.
+
+The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.
+The larger $\lambda_{\bsk}$ is, the more important $\hf(\bsk)$ is.
+The $\lambda_{\bsk}$ are assumed to have a known order:
+\begin{equation} \label{DHKM:lambda_order}
+    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots >0,
+\end{equation}
+implies an ordering of the wavenumbers, $\bsk$.
+We also assume that all $\lambda_{\bsk}$ are  positive to avoid the trivial case where $\SOL(f)$ can be expressed exactly as a finite sum for all $f \in \calF$.
+We denote the sequence of weights  $\bigl(\lambda_{\bsk_i}\bigr)_{i=1}^\infty$ by $\bslambda$.
 
@@
 
-The $\lambda_{\bsk}$ are assumed to have a known order, and
-we also assume that all $\lambda_{\bsk}$ are  positive to avoid the trivial case where $\SOL(f)$ can be expressed exactly as a finite sum for all $f \in \calF$.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 For this example, let $\calF$ denote a Hilbert space of input functions where we choose $\bbK=\bbN_0^d$ and $\rho=2$,
-\begin{multline}
+\begin{equation}
 \label{DHKM:IllExWts}
-    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \\ \text{where } \bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}, \quad \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
-\end{multline}
+    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
+\end{equation}
 The $w_\ell$ are non-negative \emph{coordinate weights}, which embody the assumption that $f$ may depend more strongly on coordinates with larger $w_\ell$ than those with smaller $w_\ell$.
@@
 
-The ordering of the weights,
-\begin{equation} \label{DHKM:lambda_order}
-    \lambda_{\bsk_1} \ge \lambda_{\bsk_2} \ge \cdots >0,
-\end{equation}
-implies an ordering of the wavenumbers, $\bsk$.  It is natural to approximate the solution using the first $n$ series coefficients as follows:
+Due to the ordering of the weights in \eqref{DHKM:lambda_order}, it is natural to approximate the solution using the first $n$ series coefficients as follows:
 \begin{equation*} %\label{DHKM:Ex_APP_def}
@@
 \end{equation*}
-
 The error of this approximation in terms of the norm on the output space, $\calG$, can be expressed as
@@
 Let
-\[
+$
 n^*(\varepsilon,R) : = \COST(\ALG, \calB_R, \varepsilon,R').
-\]
+$
 Construct an input function $f \in \calB_{R'}$ as in the proof of Theorem \ref{DHKM:APP_optimality_thm} with $\calJ = \{\bsk_1, \ldots, \bsk_{n^*(\omega \varepsilon,R')} \}$.
@@
 \begin{equation} \label{DHKM:pilot_cone}
-    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \right\}.
+    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
 \end{equation}
@@
     \right]^{1/\rho} \qquad \forall f \in \calF \\
-    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
     \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}.
@@
     : =  
-    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
+    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
     \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} , 
@@
 This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
-This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}:
+This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for the cone of input functions, $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, defined in \eqref{DHKM:pilot_cone}:
 
@@
      & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1 }} \, 
+     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
      \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}}
@@
 \end{align*}
-since $\bignorm[\rho]{\bigl( \hf(\bsk)/\lambda_{\bsk} \bigr)_{\bsk \in \calK_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
+since $\bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
 Moreover, this inequality is tight for some $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
@@
 
-The input function $f_1$ is defined via its series coefficients as in Lemma \ref{DHKM:Key_Lem}, having nonzero coefficients only for $\bsk \in \calK_1$:
+The input function $f_1$ is defined via its series coefficients as in Lemma \ref{DHKM:Key_Lem}, having nonzero coefficients only for $\bsk \in \calK_1=\{\bsk_1, \ldots, \bsk_{n_1}\}$:
 \begin{equation*}
@@
 The above derivation assumes that $A > 1$.
-If $A =1$, then our cone consists of functions whose series coefficients vanish for wavenumbers outside $\calK_1$.
-The exact solution can be constructed using only the pilot sample.
+\DHKMchange{If $A =1$, then our cone consists of functions whose only nonzero series coefficients are for wavenumbers in the set $\{\bsk_1, \ldots, \bsk_{n_1}\}$.}  The exact solution can be constructed using only the pilot sample.
 Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, which is an unbounded set.
@@
 For $\rho'=\infty$, $\bignorm[\rho']{\bslambda^{(n+1)}} = \lambda_{\bsk_{n+1}}$.
-To facilitate these bounds we establish a couple of commonly used lemmas.
+To facilitate these bounds we establish a couple of common lemmas.
 
@@
 \end{align*}
+
 Now suppose that $\COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
@@
 This is a generalization of our illustrative example, \eqref{DHKM:IllExWts}, in Section \ref{DHKM:secexamp} where $\bss = (1, 2^{-r}, 3^{-r}, \ldots )$.  
-This form of the $\lambda_{\bsk}$ is considered in greater detail in Section \ref{DHKM:smoothimportance_sec}.
+This form of the $\lambda_{\bsk}$ is also considered in Sections \ref{DHKM:tracking_sec} and  \ref{DHKM:smoothimportance_sec}.
 
@@
 \begin{proof}
-The proof is constructed first for general $\bss$.  By straightforward calculation,
+The proof is constructed first for general $\bss$.  For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
+
+By straightforward calculation,
 \begin{equation} \label{DHKM:lambdaprodwts}
@@
 \end{equation*}
-Taking the $p^{\text{th}}$ root completes the proof of the lower bound.  For the upper bound \eqref{DHKM:lambdaprodwts} implies that 
+Taking the $p^{\text{th}}$ root completes the proof of the lower bound.
+
+For the upper bound \eqref{DHKM:lambdaprodwts} implies that 
 \begin{align*}
@@
 Again, taking the $p^{\text{th}}$ root completes the proof for general $\bss$.  
-For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
 \end{proof}
@@
 
+\FredNote{Do we drop the other subscripts on $\calC$, and just use $d$?}
 \DHKMchange{
@@
 \begin{equation} \label{DHKM:TrackConeDef}
-  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} : =\left\{f\in\calF \colon \sigma_{j+s} (f)\le ab^s \sigma_j (f)\ \forall j,s\in\NN\right\}.
+  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} : =\left\{f\in\calF \colon \sigma_{j+l} (f)\le ab^l \sigma_j (f)\ \forall j,l\in\NN\right\}.
 \end{equation}
@@
 
-Because $ab^s$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
+Because $ab^l$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
 However, we expect their partial sums to decay \emph{steadily}.
@@
 &
-= \norm[\tau]{ \bigl(\sigma_{j+s}(f) \Lambda_{j+s} \bigr)_{s=1}^\infty}
+= \norm[\tau]{ \bigl(\sigma_{j+l}(f) \Lambda_{j+l} \bigr)_{l=1}^\infty}
 \\
-& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^s\Lambda_{j+s} \bigr)_{s=1}^\infty} =:\ERRNj
+& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^l\Lambda_{j+l} \bigr)_{l=1}^\infty} =:\ERRNj
  \qquad \text{by \eqref{DHKM:TrackConeDef}.}
@@
 To illustrate the exponential case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \DHKMchange{\Theta}(\E^{-r_\Delta i})$.
-For this exponential case one would normally define $\calC$ in terms of an arithmetic sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 + j s$, where $s$ is a positive integer.
+For this exponential case one would normally define $\calC$ in terms of an arithmetic sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 + j q$, where $q$ is a positive integer.
 This implies that
 \begin{align*}
-    \sigma_j(f) &= \left[ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
-    = \DHKMchange{\Theta} \left( \left [ \sum_{i=n_0 + j s -s + 1}^{n_0 + j s} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
-    & = \DHKMchange{\Theta} \left(  \E^{-j r_{\Delta} s} \right).
+    \sigma_j(f) &= \left[ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
+    = \DHKMchange{\Theta} \left( \left [ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
+    & = \DHKMchange{\Theta} \left(  \E^{-j r_{\Delta} q} \right).
 \end{align*}
 Analogous to the algebraic case, reasonable functions would satisfy 
-    $C_{\lo} \E^{-j r_{\Delta} s} \le \sigma_j(f) \le C_{\up} \E^{-j r_{\Delta} s}$
+    $C_{\lo} \E^{-j r_{\Delta} q} \le \sigma_j(f) \le C_{\up} \E^{-j r_{\Delta} q}$
 for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} s}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} q}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
 Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
@@
 
-\iffalse 
-\begin{theorem}\label{DHKM:TractConeCompCost}
+\DHKMchange{
+
+\begin{theorem}\label{DHKM:TrackConeCompCost}
 Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
 The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
-\begin{equation} \label{DHKM:EqTractConejstar}
+\begin{equation} \label{DHKM:EqTrackConejstar}
 j^* = \min\left \{ j \in \bbN : \ERRNj \le \varepsilon  \right\}.
@@
 \begin{equation} \label{DHKM:TractConejdagger}
-j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}
-\le  \frac{b\varepsilon}{Ra^2} \left( \frac{1 - b^{j\rho}}{1 - b^\rho} \right)^{1/\rho} \right\}.
+j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{s}\Lambda_{j+l} \bigr)_{l=1}^\infty}
+\le  \frac{b\varepsilon}{Ra^2}\right\}.
 \end{equation}
@@
 \begin{proof}
-The value of $j^*$ in \eqref{DHKM:EqTractConejstar} follows directly from the error criterion. The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
-
-For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
-For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
-\begin{align*}
-R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
- \ge \norm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
- \qquad \text{by \eqref{DHKM:SigmaDef} } \\
-& \ge \norm[\rho]{\left(a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f), \ldots, a^{-1} b^{-1}\sigma_{j^\dagger}(f), \sigma_{j^\dagger}(f) \right) } \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
-& \ge \frac {\sigma_{j^\dagger}(f)} a \norm[\rho]{\bigl(b^{1-j^\dagger}, \ldots, b^{-1}, 1 \bigr) } 
-= \frac {b\sigma_{j^\dagger}(f)} a \left( \frac{b^{-j^\dagger\rho} -1}{1 - b^\rho} \right)^{1/\rho}\\
-& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^r\Lambda_{j^\dagger+r} \bigr)_{r=1}^\infty}
-\qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
-& = \frac{R}{\varepsilon} \ERRNjd\, .
-\end{align*}
-From this last inequality, it follows that $j^\dagger \ge j^*$.
-\end{proof} 
-\fi
-
-\DHKMchange{
-
-\begin{theorem}\label{DHKM:TractConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
-The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
-\begin{equation} \label{DHKM:EqTractConejstar}
-j^* = \min\left \{ j \in \bbN : \ERRNj \le \varepsilon  \right\}.
-\end{equation}
-Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
-\begin{equation} \label{DHKM:TractConejdagger}
-j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{s}\Lambda_{j+s} \bigr)_{s=1}^\infty}
-\le  \frac{b\varepsilon}{Ra^2}\right\}.
-\end{equation}
-\end{theorem}
-
-\begin{proof}
-The value of $j^*$ in \eqref{DHKM:EqTractConejstar} follows directly from the error criterion. The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
+The value of $j^*$ in \eqref{DHKM:EqTrackConejstar} follows directly from the error criterion. The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
 
@@
 & \ge \sigma_1(f) \ge a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f) \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
-& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^s\Lambda_{j^\dagger+s} \bigr)_{r=1}^\infty}
+& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^l \Lambda_{j^\dagger+l} \bigr)_{l=1}^\infty}
 \qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
@@
 \begin{align*}
-\norm[\rho]{ \bigl(b^{s}\Lambda_{j+s} \bigr)_{s=1}^\infty}^\rho
- & =  \sum_{s=1}^\infty
-( b^{j+s}\Lambda_{j+s})^\rho \\
-& \le \sum_{s=1}^\infty  
- \frac{b^{s\rho} \norm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{(j+s-1)\rho/p}} 
+\norm[\rho]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}^\rho
+ & =  \sum_{l=1}^\infty
+( b^{j+l}\Lambda_{j+l})^\rho \\
+& \le \sum_{l=1}^\infty  
+ \frac{b^{l\rho} \norm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{(j+l-1)\rho/p}} 
 =  
  \frac{b^{\rho} \norm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{j\rho/p} (1 - b^{\rho}/2^{\rho/p})}, \\
-\norm[\rho]{ \bigl(b^{s}\Lambda_{j+s} \bigr)_{s=1}^\infty}
+\norm[\rho]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}
  & \le  
@@
 \end{align*}
-From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TractConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,a,b},\varepsilon,R) \le n_j = n_0 2^j$ for any $j$ satisfying
+From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TrackConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,a,b},\varepsilon,R) \le n_j = n_0 2^j$ for any $j$ satisfying
 \begin{align*}
@@
 The following theorem establishes a lower bound on the complexity of our problem for input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$.
-The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TractConeCompCost} is essentially no worse than this lower bound.
+The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TrackConeCompCost} is essentially no worse than this lower bound.
 
@@
 \sigma_{j+r}(f_1) &= 
-b^{r} \sigma_j(f_1) \le a b^r \sigma_j(f_1), \qquad j,r \in \N_0.
+b^{l} \sigma_j(f_1) \le a b^l \sigma_j(f_1), \qquad j,l \in \N_0.
 \end{align}
@@
 \nonumber
-\sigma_{j+r}(f_\pm) & \le \sigma_{j+r}(f_1) + \sigma_{j+r}(f_2) \le 
-(c_1+c_2) b^{j+r} 
+\sigma_{j+l}(f_\pm) & \le \sigma_{j+l}(f_1) + \sigma_{j+l}(f_2) \le 
+(c_1+c_2) b^{j+l} 
 \\
 \nonumber
-& =  R(1 - b^\rho)^{1/\rho}b^{j+r}
-\le a b^r \sigma_j(f_\pm),  \qquad j \in \N_0.
+& =  R(1 - b^\rho)^{1/\rho}b^{j+l}
+\le a b^l \sigma_j(f_\pm),  \qquad j, l \in \N_0.
 \end{align}
@@
 
-In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}, the weights $\bslambda = (\lambda_{\bsk})_{\bsk \in \bbK}$, which appear in the definition of the cone of inputs, $\calC_{\bslambda,A}$, are taken as given and fixed.
-One may assume the form suggested in \eqref{DHKM:prodwts}, which defines $\bslambda$ in terms of coordinate weights and smoothness weights.
-However, practically speaking it may be difficult to know a priori the values of these weights.
-This section explores a situation where the initial data collected for the input function data can be used to learn $\bslambda$, inferring which input variables in $f$ may be more important and the smoothness of the function.
+In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}, the weights $\bslambda = (\lambda_{\bsk_1}, \lambda_{\bsk_2}, \ldots )$, which appear in the definition of the cone of inputs, $\calC_{\bslambda,n_1,A}$ and $\calC_{\bslambda,\bsn,a,b}$, are taken as given and fixed.
+One may assume the form suggested in \eqref{DHKM:prodwts}, which defines $\bslambda$ in terms of coordinate weights, $\bsw$, and smoothness weights, $\bss$.
+However, practically speaking it may be difficult to know a priori suitable values for these weights.
+This section explores a situation where the initial data collected for the input function data can be used to learn $\bsw$ and $\bss$, inferring which input variables in $f$ may be more important and the smoothness of the function.
 
@@
 \end{document}
+
+\iffalse 
+\begin{theorem}\label{DHKM:TractConeCompCost}
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
+The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
+\begin{equation} \label{DHKM:EqTrackConejstar}
+j^* = \min\left \{ j \in \bbN : \ERRNj \le \varepsilon  \right\}.
+\end{equation}
+Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+\begin{equation} \label{DHKM:TractConejdagger}
+j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}
+\le  \frac{b\varepsilon}{Ra^2} \left( \frac{1 - b^{j\rho}}{1 - b^\rho} \right)^{1/\rho} \right\}.
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+The value of $j^*$ in \eqref{DHKM:EqTrackConejstar} follows directly from the error criterion. The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
+
+For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
+For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
+\begin{align*}
+R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
+ \ge \norm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
+ \qquad \text{by \eqref{DHKM:SigmaDef} } \\
+& \ge \norm[\rho]{\left(a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f), \ldots, a^{-1} b^{-1}\sigma_{j^\dagger}(f), \sigma_{j^\dagger}(f) \right) } \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
+& \ge \frac {\sigma_{j^\dagger}(f)} a \norm[\rho]{\bigl(b^{1-j^\dagger}, \ldots, b^{-1}, 1 \bigr) } 
+= \frac {b\sigma_{j^\dagger}(f)} a \left( \frac{b^{-j^\dagger\rho} -1}{1 - b^\rho} \right)^{1/\rho}\\
+& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^r\Lambda_{j^\dagger+r} \bigr)_{r=1}^\infty}
+\qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
+& = \frac{R}{\varepsilon} \ERRNjd\, .
+\end{align*}
+From this last inequality, it follows that $j^\dagger \ge j^*$.
+\end{proof} 
+\fi

### 2019-09-16 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 
-In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}, the weights $\bslambda = (\lambda_{\bsk_1}, \lambda_{\bsk_2}, \ldots )$, which appear in the definition of the cone of inputs, $\calC_{\bslambda,n_1,A}$ and $\calC_{\bslambda,\bsn,a,b}$, are taken as given and fixed.
+In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}, the weights \DHKMchange{$\bslambda = (\lambda_{\bsk_1}, \lambda_{\bsk_2}, \ldots )$}, which appear in the definition of the cone of inputs, \DHKMchange{$\calC_{\bslambda,n_1,A}$ and $\calC_{\bslambda,\bsn,a,b}$, are taken as given and fixed.
 One may assume the form suggested in \eqref{DHKM:prodwts}, which defines $\bslambda$ in terms of coordinate weights, $\bsw$, and smoothness weights, $\bss$.
@@
 This section explores a situation where the initial data collected for the input function data can be used to learn $\bsw$ and $\bss$, inferring which input variables in $f$ may be more important and the smoothness of the function.
+We focus on inferring the $\bslambda$ defining the cone $\calC_{\bslambda,n_1,A}$ in Section \ref{DHKM:pilot_sec}.}
 
@@
 where $\bsw = (w_\ell)_{l=1}^d$ is the vector of coordinate weights, $\bss = (s_k)_{k=1}^\infty$ is the vector of smoothness weights,  $\boldsymbol{\Gamma} = (\Gamma_m)_{m=1}^d$ is the vector of \emph{order weights}, and $\norm[0]{\bsk}$ denotes the number of nonzero elements of $\bsk$.
-The intuition behind these weights is as follows:
+\DHKMchange{This is a generalization of the form for $\bslambda$ given by \eqref{DHKM:prodwts}.} The intuition behind these weights is as follows:
 \begin{itemize}
@@
 \vspace{-3ex}
-\DHKMchange{These principles will guide the inference of weights $\bslambda$ (and its corresponding cone of inputs $\calC_{\bslambda,A}$) from initial data.}
+\DHKMchange{These principles will guide the inference of weights $\bslambda$ (and its corresponding cone of inputs $\calC_{\bslambda,n_1,A}$ from initial data.}
 
@@
 %Let $\calC_{\bslambda}$ denote the cone of inputs defined in \eqref{DHKM:pilot_cone} by POSD weights $\bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}$.
-As mentioned above, our goal here is to infer $\bslambda$ from input function data.  We start with an initial set of wavenumbers:
+As mentioned above, our goal here is to infer $\bslambda$ from input function data.  We start with an initial set of \DHKMchange{$d k_{\max} + 1$} wavenumbers:
 \begin{equation} \label{DHKM:barKdef}
@@
 \end{equation}
-\DHKMchange{where the only non-zero entry $k$ may be at any position in the vector}. The approximation to $f$ based on sampling the series coefficients for these wavenumbers is
+\DHKMchange{where the possible non-zero entry $k$ may be at any one position in the vector}. The approximation to $f$ based on sampling the series coefficients for these wavenumbers is
 \begin{equation*}
@@
 \end{equation*}
-\DHKMchange{To choose the cone $\calC_{\bslambda,A}$ which best fits $f$, we select the POSD weights $\bslambda$ to make the norm of $f_{\text{app}}$ small. These weights can be written as:}
+\DHKMchange{To choose the cone $\calC_{\bslambda,n_1,A}$ which best fits $f$, we select the POSD weights $\bslambda$ to make the norm of $f_{\text{app}}$ small. These weights can be written as:}
 \begin{multline}
@@
 \begin{equation} \label{DHKM:pilot_cone2}
-     \DHKMchange{\bar{\calC}_{A}} := \left \{ f \in \calF : f \in \DHKMchange{\calC_{\bar{\bslambda},A}} \text{ for } \bar{\bslambda} \text{ defined in \eqref{DHKM:eq:inf}} \right\}.
-\end{equation}
-The reason that \DHKMchange{$\bar{\calC}_A$} is a cone is that the data-inferred $\bar{\bslambda}$ for the input function $f$ is exactly the same as for the input function $cf$, where $c$ is any constant.
+     \DHKMchange{\bar{\calC}_{n_1,A}} := \left \{ f \in \calF : f \in \DHKMchange{\calC_{\bar{\bslambda},n_1,A}} \text{ for } \bar{\bslambda} \text{ defined in \eqref{DHKM:eq:inf}} \right\}.
+\end{equation}
+The reason that \DHKMchange{$\bar{\calC}_{n_1,A}$} is a cone is that the data-inferred $\bar{\bslambda}$ for the input function $f$ is exactly the same as for the input function $cf$, where $c$ is any constant.
 
@@
 \State Evaluate initial sample $\bigl\{\hf(\bsk)\bigr\}_{\bsk \in \bcalK}$
-\State Compute data-driven POSD weight $\bar{\bslambda}$\DHKMchange{, by iteratively optimizing over $\bsw \in \calW$ and $\bss \in \calS$ in \eqref{DHKM:eq:inf} until convergence}
+\State Compute data-driven POSD weight $\bar{\bslambda}$\DHKMchange{, by iteratively optimizing over $(\bsw, \bss) \in \calW \times \calS$ in \eqref{DHKM:eq:inf} until convergence}
 \State Using these weights, $\bar{\bslambda}$, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\ALG(f,\varepsilon)$

### 2019-09-18 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
 \end{equation*}
-These definitions follow the information-based complexity literature \cite{TraWer98, TraWasWoz88}.
+These definitions follow the information-based complexity literature \citep{TraWer98, TraWasWoz88}.
 We define an algorithm to be \emph{essentially optimal} if there exist some fixed positive $\omega$, $\varepsilon_{\max}$, and $R_{\min}$ for which
@@
 
-\subsection{Problem formulation}
+\subsection{Problem Formulation}
 
@@
     \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
-     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
+     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk_i)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
      \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
@@
 \begin{align*}
-\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \\
+\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho, \\
 	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
@@
 
-\FredNote{Do we drop the other subscripts on $\calC$, and just use $d$?}
 \DHKMchange{
@@
 Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
-The set of functions for which our algorithms succeed, $\calC_d$, depends on the dimension, too.
+The set of functions for which our algorithms succeed, depends on the dimension, too.
+Thus, for the sake of brevity, we write $\calC_d$ instead of $\calC_{\bslambda,n_1,A}$ in this section.
 Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on the dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
@@
     n_{\COMP}(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
-\bignorm[\rho']{\bslambda_d^{(n+1)}}\,
+\bignorm[\rho']{\bslambda_d^{(n+1)}}^{\rho'}\,
     \le (\varepsilon/R)^{\rho'} \right \} \\
@@
 $\bignorm[p]{\bslambda_d^{(i_0)}}^p<\infty$ holds if and only if  $\bignorm[p]{\bslambda_d}^p<\infty$.
-We denote the $d$-dependence of the vector of coordinate weights by writing $\bsw_d:=(w_1, \ldots, w_d)$ and $\bsw_\infty = (w_1, w_2, \ldots)$
+We denote the $d$-dependence of the vector of coordinate weights by writing $\bsw_d:=(w_1, \ldots, w_d)$ and $\bsw_\infty = (w_1, w_2, \ldots)$.
 By Lemma \ref{DHKM:prodwtsupperbound}, we have
@@
     \frac{b \norm[p]{\bslambda} }{ n_0^{1/p} 2^{j/p} (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} &\le \frac{b\varepsilon}{R a^2}, \\
-   \left(\frac{ R a^{2} \norm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p & \le n_0 2^{j},
+   \left(\frac{ R a^{2} \norm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p & \le n_0 2^{j}.
 \end{align*}
@@
 \nonumber
-\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_l}} 
+\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
 = c_1 b^j, \qquad j \in \N_0,\\
@@
 
-The motivation for this section is situations where the relative importance of the $d$ input variables of the function is not known from physical considerations.
+This section is motivated by situations where the relative importance of the $d$ input variables of the function is not known from physical considerations.
 We also envision situations where the cost of function data is large, e.g., the result of an expensive computer simulation.
@@
 \end{equation}
-where $\bsw = (w_\ell)_{l=1}^d$ is the vector of coordinate weights, $\bss = (s_k)_{k=1}^\infty$ is the vector of smoothness weights,  $\boldsymbol{\Gamma} = (\Gamma_m)_{m=1}^d$ is the vector of \emph{order weights}, and $\norm[0]{\bsk}$ denotes the number of nonzero elements of $\bsk$.
+where $\bsw = (w_\ell)_{\ell=1}^d$ is the vector of coordinate weights, $\bss = (s_k)_{k=1}^\infty$ is the vector of smoothness weights,  $\boldsymbol{\Gamma} = (\Gamma_m)_{m=1}^d$ is the vector of \emph{order weights}, and $\norm[0]{\bsk}$ denotes the number of nonzero elements of $\bsk$.
 \DHKMchange{This is a generalization of the form for $\bslambda$ given by \eqref{DHKM:prodwts}.} The intuition behind these weights is as follows:
@@
 E.g., if the $\tu_k$ are polynomials of degree $k$ as in Section \ref{DHKM:secexamp}, then the faster the $s_k$ decay, the smoother $f$ is.
-    \item Order weights quantify the importance of effects with different orders; $\bsk$ having one nonzero element corresponds to a first-order or main effect, $\bsk$ having two nonzero elements corresponds to a second-order (interaction) effect.
-(e.g., first-order, second-order).
+    \item Order weights quantify the importance of effects with different orders; $\bsk$ having one nonzero element corresponds to a first-order or main effect, $\bsk$ having two nonzero elements corresponds to a second-order (interaction) effect (e.g., first-order, second-order).
 \end{itemize} \ \vspace{-4ex}
@@
 \vspace{-3ex}
-\DHKMchange{These principles will guide the inference of weights $\bslambda$ (and its corresponding cone of inputs $\calC_{\bslambda,n_1,A}$ from initial data.}
+\DHKMchange{These principles will guide the inference of weights $\bslambda$ (and its corresponding cone of inputs $\calC_{\bslambda,n_1,A}$) from initial data.}
 
@@
 \gamma_{\fraku} = \sum_{\bsk \in \{1, \ldots, \alpha\}^{|\fraku|}} \|\bsk\|_1 !
-\prod_{\ell \in \fraku} \left( 2^{\delta(k_\ell,\alpha)} w_\ell^{k_\ell} \right), \quad \|\bsk\|_1 = \sum_{l=1}^d k_\ell, \quad \fraku \subseteq \{1, \ldots, d\},
+\prod_{\ell \in \fraku} \left( 2^{\delta(k_\ell,\alpha)} w_\ell^{k_\ell} \right), \quad \|\bsk\|_1 = \sum_{\ell=1}^d k_\ell, \quad \fraku \subseteq \{1, \ldots, d\},
 %\label{eq:spod}
@@
 \end{equation*}
-Here, $(w_\ell^{\rm tr})_{\ell=1}^d = (1/L^2(\ell))_{l=1}^d$, $({\Gamma_k^{\rm tr}})_{k=1}^\infty \equiv 1$ and $(s_j^{\rm tr})_{j=1}^{k_{\rm max}} = (1/j^4)_{j=1}^4$ are the true coordinate, order, and smoothness weights, and $Z_{\bsk}$ randomly sets the magnitude and sign of each coefficient.
+Here, $(w_\ell^{\rm tr})_{\ell=1}^d = (1/L^2(\ell))_{\ell=1}^d$, $({\Gamma_m^{\rm tr}})_{m=1}^\infty \equiv 1$ and $(s_k^{\rm tr})_{k=1}^{k_{\rm max}} = (1/k^4)_{k=1}^4$ are the true coordinate, order, and smoothness weights, and $Z_{\bsk}$ randomly sets the magnitude and sign of each coefficient.
 Moreover, $\bigl(L(\ell)\bigr)_{\ell=1}^d$ is a random permutation of $1, \ldots, d$ to ensure that the order of input variables does not necessarily reflect their order of importance.

### 2019-09-23 DHKM_Response_to_Reviewers.tex
Updates from Overleaf

--- 2019-06-16 DHKM_Response_to_Reviewers.tex
@@
 \item Remarks (1)--(4): done. 
+\item Remark (5) We have rewritten the first and second sections extensively.
 \item Remark (6): What we mean by "this example" is the example of functions defined over $[-1,1]^d$ with a Chebyshev polynomial basis. We reformulated this passage to make this point clearer. 
@@
 \item Remark (ix): We have kept this result as a theorem, but due to the re-structuring of the paper, it is no longer part of the introduction. 
-\item Remark (x): we have moved the contents of the previous Section 1.5 as suggested by the reviewer. 
-\item Remark (xi): done. 
+\item Remark (x): We have moved the contents of the previous Section 1.5 as suggested by the reviewer. 
+\item Remark (xi): The cone in equation (16) is now denoted as $\calC_{\boldsymbol{\lambda},n_1,A}$. 
+\item Remark (xii): We have fixed the notation in old Proposition 1, which is no longer a proposition.
+Thanks for pointing this out.
+We have also added a new proposition  to discuss the relationship between our cone $\mathcal{C}_{\boldsymbol{\lambda},n_1,A}$ and a new cone $\mathcal{C}'_{\boldsymbol{\lambda},\boldsymbol{\omega},A'}$.
+\item Remark (xiii): We have added the results with smoothness parameters $r$ in the new Corollary 10.
+\item Remark (xiv): This portion has been re-written. 
+\item Remark (xv): The cone in equation (28) is now denoted as $\calC_{\boldsymbol{\lambda},\boldsymbol{n},a,b}$.
+Also, we have added extensive discussion in Section 4.2 related to the illustrative example.
+See Theorem 15.
+\item Remark (xvi): Done.
+\item Remark (xvii): Some wording has been added.
+\item Remark (xviii): We have added more elaboration in the new Sections 3 and 4 to apply our results to the illustrative example.
 \item Remark (xix): Here, we mean a ``small number of coordinates in $f$ are important''. We have made this change in the paper.
-\item Remark (xx): These guiding principles help guide the inference of weights $\boldsymbol{\lambda}$ (and its corresponding cone $\calC_{\boldsymbol{\lambda},A}$) from initial data.
+\item Remark (xx): These guiding principles help guide the inference of weights $\boldsymbol{\lambda}$ (and its corresponding cone $\calC_{\boldsymbol{\lambda},n_1,A}$) from initial data.
 We have added a sentence on this on page 29.
-\item Remark (xxi): Thanks, the cone in equation (16) is now denoted as $\calC_{\boldsymbol{\lambda},A}$, and the data-inferred cone on page 30 is now denoted as $\bar{\calC}_A = \calC_{\bar{\boldsymbol{\lambda}},A}$.
+\item Remark (xxi): Thanks, the cone in equation (16) is now denoted as $\calC_{\boldsymbol{\lambda},n_1,A}$, and the data-inferred cone on page 30 is now denoted as $\bar{\calC}_{n_1,A} = \calC_{\bar{\boldsymbol{\lambda}},n_1,A}$.
 \item Remark (xxii): Yes, this is correct. We have added a sentence after equation (40) clarifying this.
-\item Remark (xxiii): The data-adaptive cone $\bar{\calC}$ is the earlier cone $\calC_{\boldsymbol{\lambda},A}$ in equation (16) with data-adaptive weights $\boldsymbol{\lambda} = \bar{\boldsymbol{\lambda}}$.
+\item Remark (xxiii): The data-adaptive cone $\bar{\calC}_{n_1,A}$ is the earlier cone $\calC_{\boldsymbol{\lambda},n_1,A}$ in equation (16) with data-adaptive weights $\boldsymbol{\lambda} = \bar{\boldsymbol{\lambda}}$.
 We have clarified this in equation (42).

### 2019-09-23 DingHickKritzMakRICAMChapVerD.tex
Updates from Overleaf

@@
   \runningauthor{Y. Ding, F. J. Hickernell, P. Kritzer, and S. Mak}
-  \affil[1]{Department of Mathematics, 
-  Misericorida University, 301 Lake Street, Dallas, PA 18704 USA}
+  \affil[1]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
   \affil[2]{Department of Applied Mathematics, Illinois Institute of Technology, RE 220, 10 W.\ 32${}\text{nd}$ Street, Chicago, IL 60616 USA}
@@
 To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \DHKMchange{\Theta(i^{-r_\Delta})}$ for some positive $r_\Delta > 1/\rho$.
-For this algebraic case one would normally define $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
+\DHKMchange{Here $r_\Delta$ reflects the smoothness of the input function.}  For this algebraic case one would normally define $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
 \begin{align*}
@@
 for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
+\DHKMchange{By reasonable we mean that the values of $\sigma_j(f)$ would not drop precipitously and then rise again as $j$ increases.} Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
 Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
@@
 \begin{equation} \label{DHKM:TractConejdagger}
-j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{s}\Lambda_{j+l} \bigr)_{l=1}^\infty}
+j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}
 \le  \frac{b\varepsilon}{Ra^2}\right\}.
@@
 \end{align*}
-From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TrackConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,a,b},\varepsilon,R) \le n_j = n_0 2^j$ for any $j$ satisfying
+From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TrackConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,a,b},\varepsilon,R) \le n_j = n_0 2^j$ \SimonNote{Should this be $\COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon,R)$?} for any $j$ satisfying
 \begin{align*}

### 2019-10-31 DHKM_Response_to_Reviews_R1.tex
Updates from Overleaf

--- 2019-06-25 DHKM_Response_to_Reviewers.tex
@@
 \documentclass[11pt]{article}
-\usepackage{latexsym,amsfonts,amsmath,theorem,amssymb}
+\usepackage{latexsym,amsfonts,amsmath,theorem,color,amssymb}
 
@@
 \newcommand{\dimtrint}{{\rm dim}^{\rm trnc-int}}
+\newcommand{\Response}[1]{{\color{blue}#1}}
+\thispagestyle{empty}
+
+\textwidth 6.5in
+\hoffset -0.75in
 
@@
 {\Large Response to the Reviewers of the Manuscript\\
-``Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone''}
+``Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone''\quad
+Revision 1}
 \end{center}
@@
 
-\noindent We would like to thank you for your careful reviews of our manuscript and your helpful comments.
+\noindent Thank you for your careful reviews and comments on our revised manuscript. We have revised our manuscript in light of these remarks.
 
-Following the suggestions of one of the reviewers, we have restructured the introductory parts of the paper. Thereby, we address several of the remarks 
-made by both referees.
-
-Below, we respond to the points made in your reports.
-
-\subsection*{Referee Report 1 ``Summary. The authors study \ldots '' (2 pages):}
+\subsection*{Referee Report ``The manuscript is improved \ldots}
 
 \begin{itemize}
-\item Remarks (1)--(4): done. 
-\item Remark (6): What we mean by "this example" is the example of functions defined over $[-1,1]^d$ with a Chebyshev polynomial basis. We reformulated this passage to make this point clearer. 
-\item Remarks (7), (8): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
-\item Remark (9): done. 
-\item Remarks (11), (12): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
-\item Remark (13): We put this definition into a separate paragraph. 
-\item Remark (14): done. 
-\item Remark (15): Due to the new structure of the paper, we hope to have addressed these issues accordingly. 
-\item Remark (16): done. 
-\item Remark (17): The motivation for defining this cone is stated in the beginning of the section, but we have reformulated this passage to make it clearer. 
-\item Remark (18): Thanks, we have provided further details in Algorithm 4 for the step ``Compute data-driven POSD weights'', as well as for the sentence around (41).
-With this, the adaptive procedure is better defined, and we believe it should be called an algorithm.
+
+\item page 3, line 2: ``it is less restrictive than only being able to
+sample function values". \ldots  \Response{Change has been made.}
+
+\item page 3, ``We call an algorithm non-adaptive if". \ldots \Response{Clarification has been added.}
+
+\item Formula (26):  It seems to me that 11by (25)" should not be part
+of formula (26) \ldots  \Response{This has been changed in some places, but has been left as is for those multi-line equations where we wanted to refer to precisely to what equation was supporting what part of the argument.}
 \end{itemize}
 
-\subsection*{Referee Report 2 ``The paper studies \ldots'' (4 pages):}
+\subsection*{Referee Report ``The paper has significantly improved.  \ldots'':}
 
-\begin{itemize}
-\item Major issues 1.a)--1.d), 2.a), 2.b): Done. We have modified the introduction, and re-organized it into two sections. 
-\item Remark (i): The ordering is not necessarily unique, as we might have weights 
-that are equal. 
-\item Remark (ii): the referee is correct. Thanks for pointing this out. 
-\item Remark (iii): done. 
-\item Remark (iv): The paper will be a chapter in a proceedings volume.
-\item Remark (vii): We changed ``Choosing" to ``Identifying".
-\item Remark (viii): Theoretically, we could simplify this as suggested by the reviewer; however, we would like to keep the influence of $\varepsilon$ and $R$ separate and explicit. 
-\item Remark (ix): We have kept this result as a theorem, but due to the re-structuring of the paper, it is no longer part of the introduction. 
-\item Remark (x): We have moved the contents of the previous Section 1.5 as suggested by the reviewer. 
-\item Remark (xi): The cone in equation (16) is now denoted as $\calC_{\boldsymbol{\lambda},A}$. 
-\item Remark (xii): We have fixed the notation in Proposition 1.
-Thanks for pointing this out.
-We have also added a Proposition 2 to discuss the relationship between our cone $\mathcal{C}_{\boldsymbol{\lambda},A}$ and a new cone $\mathcal{C}'$.
-\item Remark (xiii): We have added the results with smoothness parameters $r$ in Corollary 1.
-\item Remark (xiv): Thanks for pointing this out.
-$\kappa_i$ should be $k_i$.
-$k_i$ and $l_i$ are the sub-indices of $\boldsymbol{s}$ and $\boldsymbol{w}$ after ordering respectively.
-We could obtain the left-hand side inequality via the right-hand side special case.
-\item Remark (xv): The cone in equation (28) is now denoted as $\calC_{\boldsymbol{\lambda},a,b}$. 
-\item Remark (xix): Here, we mean a ``small number of coordinates in $f$ are important''. We have made this change in the paper.
-\item Remark (xx): These guiding principles help guide the inference of weights $\boldsymbol{\lambda}$ (and its corresponding cone $\calC_{\boldsymbol{\lambda},A}$) from initial data.
-We have added a sentence on this on page 29.
-\item Remark (xxi): Thanks, the cone in equation (16) is now denoted as $\calC_{\boldsymbol{\lambda},A}$, and the data-inferred cone on page 30 is now denoted as $\bar{\calC}_A = \calC_{\bar{\boldsymbol{\lambda}},A}$.
-\item Remark (xxii): Yes, this is correct. We have added a sentence after equation (40) clarifying this.
-\item Remark (xxiii): The data-adaptive cone $\bar{\calC}$ is the earlier cone $\calC_{\boldsymbol{\lambda},A}$ in equation (16) with data-adaptive weights $\boldsymbol{\lambda} = \bar{\boldsymbol{\lambda}}$.
-We have clarified this in equation (42).
+\begin{enumerate}
 
-\end{itemize}
+\renewcommand{\labelenumi}{\alph{enumi})} 
+\item Page 2, line -3, in the formula it should be \ldots \Response{Done.}
+
+\item  Page 3, line 21, the notation for the computational complexity \ldots  \Response{Done.}
+
+\item  Page 4, line 21, it should be “precise definition” \ldots \Response{Yes!  Corrected.}
+
+\item Section 2: After my remark in the first report that the setting is actually a problem of diagonal operators between sequence spaces \ldots \Response{Pietsch 1978 is now referred to before Lemma 1 and again at the beginning of Section 3.2.}
+
+\item Page 7: The norm $||\cdot ||_{\mathcal{G}}$ should be given earlier \ldots \Response{Done.}
+
+\item Page 22: In formula (30) \ldots \Response{Yes, thank you.  Corrected.}
+
+\item  Page 27, to me the shape of the blocks \ldots \Response{You are correct for the illustrative example.  A sentence stating this has been added.}
+
+\end{enumerate}
 
@@
 
-\noindent Y. Ding, F.J. Hickernell, P. Kritzer, and S. Mak.
+\noindent Y. Ding, F.J. Hickernell, P. Kritzer, and S. Mak
 

### 2019-10-31 DingHickKritzMakRICAMChapVerE.tex
Updates from Overleaf

--- 2019-09-23 DingHickKritzMakRICAMChapVerD.tex
@@
 \documentclass[USenglish]{article}
+%Second Revision
 
@@
 
-\usepackage[notref,notcite]{showkeys}
+%\usepackage[notref,notcite]{showkeys}
 
@@
   problems where the sets of input functions are non-convex cones. While it is known that adaptive algorithms perform 
-  essentially no better than non-adaptive algorithms for \DHKMchange{convex and symmetric} input sets, the 
-  situation may be different for non-convex sets. \DHKMchange{The setting} 
+  essentially no better than non-adaptive algorithms for convex and symmetric input sets, the 
+  situation may be different for non-convex sets. The setting 
   considered here is function approximation based on series expansions. Given 
@@
   we consider situations where it makes sense to infer coordinate and smoothness importance.
-Besides performing an error analysis, we also \DHKMchange{derive upper bounds on} the information cost of our algorithms and \DHKMchange{lower bounds on} the computational complexity
+Besides performing an error analysis, we also derive upper bounds on the information cost of our algorithms and lower bounds on the computational complexity
   of our problems, and we identify conditions under which we can avoid a curse of 
@@
 
-\DHKMchange{
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Adaptive algorithms infer the necessary computational effort based on the function data sampled.
-Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex} \DHKMchange{or \emph{non-symmetric}}.
-\DHKMchange{Here we focus on the former situation and} construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones, $\calC$.
-\DHKMchange{By a cone, we mean a set of functions where constant multiples of every function in the set also lie in the set.
-The precise definitions of the cones that we study are given below.}
+Adaptive algorithms may perform better than non-adaptive algorithms if the set of input functions is \emph{non-convex} or \emph{non-symmetric}.
+Here we focus on the former situation and construct adaptive algorithms for general multivariate linear problems where the input functions lie in non-convex cones, $\calC$.
+By a cone, we mean a set of functions where constant multiples of every function in the set also lie in the set.
+The precise definitions of the cones that we study are given below.
 
@@
 we study algorithms that have an output of the form 
-\begin{equation*} 
-  \ALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n(f,\varepsilon) \in \N,
+\begin{equation*} %\label{DHKM:algform}
+  \ALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) v_{\bsk_i} \qquad \forall f \in \calF, \ n(f,\varepsilon) \in \N,
 \end{equation*}
@@
 We assume that it is possible to sample the series coefficients of the input function.
-This is a \DHKMchange{more} restrictive assumption than being able to sample any linear functional, but it is \DHKMchange{less} restrictive than only being able to sample function values.
+This is a more restrictive assumption than being able to sample any linear functional, but it is different than only being able to sample function values.
 An important future problem is to extend the theory in this chapter to the case where the only function data available are function values.
@@
 For adaptive algorithms this cost varies with the input function $f$.
-We call an algorithm \emph{non-adaptive} if $n(f,\varepsilon)=n(\varepsilon)$, independently of the particular choice of $f\in\calC$.
+We call an algorithm \emph{non-adaptive} if $n(f,\varepsilon)=n(\varepsilon)$, independently of the particular choice of $f\in\calC$, and also the sequence $\bsk_1, \bsk_2, \ldots$ is independent of the choice of $f\in\calC$.
 
@@
 
-\DHKMchange{A crucial concept is the set of all possible algorithms that may be constructed using series coefficients and that \emph{satisfy error criterion \eqref{DHKM:err_crit}}.
+A crucial concept is the set of all possible algorithms that may be constructed using series coefficients and that \emph{satisfy error criterion \eqref{DHKM:err_crit}}.
 We denote this set by $\calA(\calC)$.
-}
 Furthermore, we define the \emph{computational complexity} of a problem as the information cost of the best algorithm:
 \begin{equation*}
-    \COMP(\calA(\calC), \varepsilon,R) := \min_{\ALG \in \calA(\calC)} \COST(\ALG, \calC, \varepsilon,R) .
+    \COMP(\calC, \varepsilon,R) := \min_{\ALG \in \calA(\calC)} \COST(\ALG, \calC, \varepsilon,R) .
 \end{equation*}
@@
 \begin{multline} \label{DHKM:EssentialOpt}
-    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calA(\calC), \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calC, \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
 \end{multline}
@@
 The rest of this chapter is structured as follows.
-In the next section, we formulate our problem more formally, including the price definition of the input space, $\calF$, in terms of a sequence of weights, $\bslambda$, which reflect the assumed smoothness of the input functions.
+In the next section, we formulate our problem more formally, including the precise definition of the input space, $\calF$, in terms of a sequence of weights, $\bslambda$, which reflect the assumed smoothness of the input functions.
 We point out some results for non-adaptive algorithms with inputs from balls.
@@
 
+Some of the results on balls in this chapter can be found elsewhere, e.g., \cite[Section 11.11]{Pie78a}  and \cite[Chap.\ VI, Sect.\ 2]{Pin85a}, but we provide proofs for the sake of completeness.
 To facilitate our derivations below, we establish the following lemma via H\"older's inequality:
@@
 
+Define the norm of the Hilbert space of outputs as
+\begin{equation*}
+      \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
+\end{equation*}
 Due to the ordering of the weights in \eqref{DHKM:lambda_order}, it is natural to approximate the solution using the first $n$ series coefficients as follows:
@@
 The error of this approximation in terms of the norm on the output space, $\calG$, can be expressed as
-\begin{gather*}
-    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}, \\
-    \text{where}\qquad
-    \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
-\end{gather*}
+\begin{equation*}
+    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}.
+\end{equation*}
 Here we have chosen $\tau = 2$ so $\rho'=\infty$.
-If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer \DHKMchange{for certain classes of inputs in $\calF$ as for example balls, which
-are among the most prominent examples studied in the literature}.
-
-We return \DHKMchange{to the example of functions on $[-1,1]^d$, using a Chebyshev polynomial basis}, in Section \ref{DHKM:SecPilotTract} to discuss the information cost and computational complexity.
+If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer for certain classes of inputs in $\calF$ as for example balls, which are among the most prominent examples studied in the literature.
+
+We return to the example of functions on $[-1,1]^d$, using a Chebyshev polynomial basis, in Section \ref{DHKM:SecPilotTract} to discuss the information cost and computational complexity.
 We perform some numerical experiments for this example in Section \ref{DHKM:numexamp_sec}.
@@
 \end{gather}
-This leads to the following theorem.
+This leads to the theorem below.
 
@@
 Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.
-Use Lemma \ref{DHKM:Key_Lem} with $\calK = \bbK \setminus \calJ$ to choose $f$ to mimic the zero function, have norm $R$, and have as large a solution as possible, i.e.,
+Use Lemma \ref{DHKM:Key_Lem} with $\calK = \bbK \setminus \calJ$ to choose $f$ to mimic the zero function, have norm $R$, and have as large a solution as possible by \eqref{DHKM:SOL_tight_ineq}, i.e.,
 \begin{gather}
@@
     \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ 
-    \norm[\calG]{\SOL(f)} =  R \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad  \text{by \eqref{DHKM:SOL_tight_ineq}}.  \label{DHKM:FoolFun}
+    \norm[\calG]{\SOL(f)} =  R \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.  \label{DHKM:FoolFun}
 \end{gather}
@@
 \begin{multline*}
-\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calA(\calB_R),\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
+\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calB_R,\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
 \end{multline*}
@@
 \\
-& \le \COMP(\calA(\calB_{R'}),\omega \varepsilon, R') \le  \COMP(\calA(\calB_{R}),\omega \varepsilon, R').
+& \le \COMP(\calB_{R'},\omega \varepsilon, R') \le  \COMP(\calB_{R},\omega \varepsilon, R').
 \end{align*}
@@
 For Algorithm \ref{DHKM:BallAlg}, the information cost, $\COST(\ALG,\calB_R,\varepsilon, R)$, depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
-This decay may be algebraic or exponential and also determines the problem complexity, $\COMP(\calA(\calB_R),\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
+This decay may be algebraic or exponential and also determines the problem complexity, $\COMP(\calB_R,\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
 
@@
 \begin{equation*}
-    \COMP(\calA(\calC),\varepsilon) : = \sup_{R > 0} \COMP(\calA(\calC),\varepsilon, R) < \infty.
+    \COMP(\calC,\varepsilon) : = \sup_{R > 0} \COMP(\calC,\varepsilon, R) < \infty.
 \end{equation*}
 \end{lemma}
-}
 
@@
 
-\DHKMchange{Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by}
+Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by
 \begin{equation} \label{DHKM:pilot_cone}
-    \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
+    \calC_{\boldsymbol{\lambda},n_1,A} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
 \end{equation}
 Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.
-The definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ allows us to bound these as follows:
+The definition of $\calC_{\boldsymbol{\lambda},n_1,A}$ allows us to bound these as follows:
 \begin{align*}
@@
     &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
-    \right]^{1/\rho} \quad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}.
+    \right]^{1/\rho} \quad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A}.
 \end{align*}
@@
 \begin{equation}
-\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},
+\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A},
 \end{equation}
@@
     \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
-    \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} , 
+    \, \bignorm[\rho']{\bslambda^{(n+1)}} , 
     \\ \forall n \ge n_1.
@@
 This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
-This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for the cone of input functions, $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, defined in \eqref{DHKM:pilot_cone}:
+This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for the cone of input functions, $\calC_{\boldsymbol{\lambda},n_1,A}$, defined in \eqref{DHKM:pilot_cone}:
 
@@
 \begin{theorem} \label{DHKM:PilotCostThm}
-Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}.
+Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC_{\boldsymbol{\lambda},n_1,A})$ for $\calC_{\boldsymbol{\lambda},n_1,A}$ defined in \eqref{DHKM:pilot_cone}.
 The information cost is
 \begin{multline} \label{DHKM:PilotConeAlg_cost}
-    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) \\
-    = \min \left \{n \ge n_1 : \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} \,
+    \COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \\
+    = \min \left \{n \ge n_1 : \bignorm[\rho']{\bslambda^{(n+1)}} \,
     \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
@@
 \begin{multline} \label{DHKM:PilotConeAlg_comp}
-        \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\varepsilon,R) \ge \min \left \{n \ge n_1 : \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} \,
+        \COMP(\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bslambda^{(n+1)}} \,
     \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
@@
 \end{multline}
-Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.
+Algorithm \ref{DHKM:PilotConeAlg} is essentially optimal.  Moreover, $\calA(\calC_{\boldsymbol{\lambda},n_1,A})$ contains only adaptive algorithms.
 \end{theorem}
@@
 \begin{align*}
-    \MoveEqLeft[1]{\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R)} \\
+    \MoveEqLeft[1]{\COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R)} \\
     & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
@@
      (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
-     \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}}
+     \bignorm[\rho']{\bslambda^{(n+1)}}
     \le \varepsilon \right \} \\   
      & \le \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} R \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}}
+     (A^\rho -1)^{1/\rho} R \,\bignorm[\rho']{\bslambda^{(n+1)}}
     \le \varepsilon \right \},  
@@
 since $\bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
-Moreover, this inequality is tight for some $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
+Moreover, this inequality is tight for some $f \in \calC_{\boldsymbol{\lambda},n_1,A} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
 This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.
@@
     \]
-Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ in \eqref{DHKM:pilot_cone}.
+Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC_{\boldsymbol{\lambda},n_1,A}$ in \eqref{DHKM:pilot_cone}.
 Fix $R \in [R_{\min},\infty)$ and $\varepsilon \in (0,\varepsilon_{\max}]$ arbitrarily.
@@
 \end{align}
-Therefore, $f_\pm \in \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} \cap \calB_R$.
+Therefore, $f_\pm \in \calC_{\boldsymbol{\lambda},n_1,A} \cap \calB_R$.
 Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.
@@
 =\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
-& \ge \frac{R(1 - 1/A)}{2} \, \DHKMchange{\bignorm[\rho']{\bslambda^{(n+1)}}} ,
+& \ge \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bslambda^{(n+1)}} ,
 \end{align*}
@@
 This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
-Because $\lim_{R \to \infty} \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}), \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}})$ contains only adaptive algorithms.
+Because $\lim_{R \to \infty} \COMP(\calC_{\boldsymbol{\lambda},n_1,A}, \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\calC_{\boldsymbol{\lambda},n_1,A})$ contains only adaptive algorithms.
 
@@
 \[
-\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R) \le \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}),\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
+\COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \le \COMP(\calC_{\boldsymbol{\lambda},n_1,A},\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
 \]
@@
 The above derivation assumes that $A > 1$.
-\DHKMchange{If $A =1$, then our cone consists of functions whose only nonzero series coefficients are for wavenumbers in the set $\{\bsk_1, \ldots, \bsk_{n_1}\}$.}  The exact solution can be constructed using only the pilot sample.
-Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, which is an unbounded set.
-
-\DHKMchange{We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\ERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
+If $A =1$, then our cone consists of functions whose only nonzero series coefficients are for wavenumbers in the set $\{\bsk_1, \ldots, \bsk_{n_1}\}$.
+The exact solution can be constructed using only the pilot sample.
+Our algorithm is then non-adaptive, but succeeds for input functions in the cone $\calC_{\boldsymbol{\lambda},n_1,A}$, which is an unbounded set.
+
+We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\ERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
 \begin{equation} \label{DHKM:PilotConeNecessary}
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{\DHKMchange{i =1}}^{n}} \le A
+    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i =1}^{n}} \le A
     \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
 \end{equation}
-}%
-If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
-The remedy is to make $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.
-
-\DHKMchange{Our $\calC_{\boldsymbol{\lambda},n_1,A}$ is a cone for which a pilot sample of the input function allows you to bound its norm.
+If condition \eqref{DHKM:PilotConeNecessary} is violated in practice, then $f \notin \calC_{\boldsymbol{\lambda},n_1,A}$, and Algorithm \ref{DHKM:PilotConeAlg} may output an incorrect answer.
+The remedy is to make $\calC_{\boldsymbol{\lambda},n_1,A}$ more inclusive by increasing the inflation factor, $A$, and/or the pilot sample size, $n_1$.
+
+Our $\calC_{\boldsymbol{\lambda},n_1,A}$ is a cone for which a pilot sample of the input function allows you to bound its norm.
 An alternative is to define a cone for which a weaker norm of the function provides an upper bound on the original norm.
@@
 \end{proof}
-}
 
@@
 
-\DHKMchange{
 We now derive upper and lower bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the case  $\rho = \tau$ and $\rho' = \infty$, which includes the example introduced in Section \ref{DHKM:secexamp}.
@@
 To facilitate these bounds we establish a couple of common lemmas.
+Again we refer the reader to  \cite[Section 11.11]{Pie78a}.
 
@@
 then $\norm[p\eta]{\bslambda} < \infty$ for all $\eta > 1$.
-Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calA(\calB_R),\varepsilon,R')$ and $\COMP(\calA(\calC_{\bslambda,n_1,A}),\varepsilon,R)$.
+Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calB_R,\varepsilon,R')$ and $\COMP(\calC_{\bslambda,n_1,A},\varepsilon,R)$.
 \end{theorem}
@@
 \begin{align*} 
-    \COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}},\varepsilon,R)
+    \COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R)
     & = \min \left \{n \ge n_1 : \lambda_{\bsk_{n+1}}
@@
 
-By straightforward calculation,
+By straightforward calculation and \eqref{DHKM:prodwts},
 \begin{equation} \label{DHKM:lambdaprodwts}
@@
    = \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) 
-   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right) 
-   \quad \text{ by \eqref{DHKM:prodwts} .}
+   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right).
 \end{equation}
@@
 Furthermore, these information costs cannot grow any slower than $\calO(\varepsilon^{-1/r})$ for $\varepsilon \downarrow 0$.
-Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calA(\calB_R),\varepsilon,R')$ and $\COMP(\calA(\calC_{\bslambda,n_1,A}),\varepsilon,R)$ for the illustrative example in Section \ref{DHKM:secexamp}.
+Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calB_R,\varepsilon,R')$ and $\COMP(\calC_{\bslambda,n_1,A},\varepsilon,R)$ for the illustrative example in Section \ref{DHKM:secexamp}.
 \end{corollary}
-}
 
@@
 
-\DHKMchange{
-Besides understanding the dependence of $\COMP(\calA(\calC), \varepsilon,R)$ on $\varepsilon$, we also want to understand how $\COMP(\calA(\calC), \varepsilon,R)$ depends on the dimension of the domain of the input function.
+Besides understanding the dependence of $\COMP(\calC, \varepsilon,R)$ on $\varepsilon$, we also want to understand how $\COMP(\calC, \varepsilon,R)$ depends on the dimension of the domain of the input function.
 Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
@@
 
-Different dependencies of $\COMP(\calA(\calC_d), \varepsilon,R)$ on the dimension $d$ and the error tolerance $\varepsilon$ are formalized as different notions of tractability. Since 
+Different dependencies of $\COMP(\calC_d, \varepsilon,R)$ on the dimension $d$ and the error tolerance $\varepsilon$ are formalized as different notions of tractability. Since 
 the complexity is defined in terms of the best algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
@@
 $$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,R^{\widetilde{p}}\,\varepsilon^{-\widetilde{p}} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+\COMP(\calC_d, \varepsilon,R)\le C\,R^{\widetilde{p}}\,\varepsilon^{-\widetilde{p}} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
 $$   
@@
 $$   
-\COMP(\calA(\calC_d), \varepsilon,R)\le C\,d^{\,q}\,R^{\widetilde{p}}\,   
+\COMP(\calC_d, \varepsilon,R)\le C\,d^{\,q}\,R^{\widetilde{p}}\,   
 \varepsilon^{-{\widetilde{p}}}\qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).  
@@
 \lim_{d+R\,\varepsilon^{-1}\to\infty}\   
-\frac{\log\, \COMP(\calA(\calC_d), \varepsilon,R)}   
+\frac{\log\, \COMP(\calC_d, \varepsilon,R)}   
 {d+R\,\varepsilon^{-1}}\,=\,0.   
@@
 \begin{align*}
-    \MoveEqLeft{\COMP(\calA(\calB_{R}),\varepsilon,R)} 
+    \MoveEqLeft{\COMP(\calB_{R},\varepsilon,R)} 
   \le \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \norm[p]{\bsw}^p  \right) \right \rceil .
@@
 If $p^\dagger$ is the infimum of the $p$ for which $\norm[p]{\bsw}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $\widetilde{p}_* = \max(1/r,p^\dagger)$.
-On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calA(\calB_{R}),\varepsilon,R) \ge 2^d$, and the problem is not tractable.\\
-
-}
+On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calB_{R},\varepsilon,R) \ge 2^d$, and the problem is not tractable.\\
 
@@
 \begin{multline*}
-     \COMP(\calA(\calC_d),\omega_{\textup{lo}} \varepsilon,R) \le n_{\COMP}(\varepsilon/R,d) \le 
-        \COMP(\calA(\calC_d),\omega_{\textup{hi}} \varepsilon,R)  \\
+     \COMP(\calC_d,\omega_{\textup{lo}} \varepsilon,R) \le n_{\COMP}(\varepsilon/R,d) \le 
+        \COMP(\calC_d,\omega_{\textup{hi}} \varepsilon,R)  \\
         \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
@@
 
-\DHKMchange{\begin{theorem} \label{DHKM:thmtract1}
+\begin{theorem} \label{DHKM:thmtract1}
 Using the same notation as above, the following statements hold for the case $\rho'=\infty$.
@@
 \end{theorem}
-}
 
@@
 
-\DHKMchange{In this case, letting $\widetilde{\varepsilon}:=(\varepsilon/R)^{\rho'/2}$ and 
+In this case, letting $\widetilde{\varepsilon}:=(\varepsilon/R)^{\rho'/2}$ and 
 $\widetilde{\lambda}_{d,i}:=\lambda_{d,\bsk_i}^{\rho'}$, we have 
@@
  \begin{equation}\label{DHKM:eq:condspt1}
-    \sup_{d\in\NN} \bignorm[\rho, p]{\bslambda_d^{(i_0)}} < \infty.
+    \sup_{d\in\NN} \bignorm[\rho' p]{\bslambda_d^{(i_0)}} < \infty.
  \end{equation}
@@
 \end{theorem}
-}
+
 \begin{proof}
@@
 
-\DHKMchange{
 To be more concrete, we return to the situation where the $\lambda_{d,\bsk}$ are given 
@@
 \end{remark}
-}
 
@@
 
-Let $\DHKMchange{\bsn = (n_j)_{j\ge 0}}$ be a strictly increasing sequence of non-negative integers.
+Let $\bsn = (n_j)_{j\ge 0}$ be a strictly increasing sequence of non-negative integers.
 This sequence may increase geometrically or algebraically.
@@
 
-\DHKMchange{As stated above, we would like to keep track of the rate of decay of the $\hf(\bsk_i)$. Hence, for this section, we define the cone of input functions by}
+As stated above, we would like to keep track of the rate of decay of the $\hf(\bsk_i)$. Hence, for this section, we define the cone of input functions by
 \begin{equation} \label{DHKM:TrackConeDef}
-  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} : =\left\{f\in\calF \colon \sigma_{j+l} (f)\le ab^l \sigma_j (f)\ \forall j,l\in\NN\right\}.
+  \calC_{\boldsymbol{\lambda},\bsn,a,b} : =\left\{f\in\calF \colon \sigma_{j+l} (f)\le ab^l \sigma_j (f)\ \forall j,l\in\NN\right\}.
 \end{equation}
 Here, $a$ and $b$ are positive reals with $b< 1 < a$.
-The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $.
-\DHKMchange{We remark that knowing $\sigma_1 (f)$ would already be sufficient to identify 
-a sample size that guarantees an error of at most $\varepsilon$. However, knowing $\sigma_j (f)$ for further values of $j$ will allow us to stop earlier.}
+The constant $a$ is an inflation factor, and the constant $b$ defines the general rate of decay of the $\sigma_j(f)$ for $f \in  \calC_{\boldsymbol{\lambda},\bsn,a,b} $.
+We remark that knowing $\sigma_1 (f)$ would already be sufficient to identify 
+a sample size that guarantees an error of at most $\varepsilon$. However, knowing $\sigma_j (f)$ for further values of $j$ will allow us to stop earlier.
 
@@
 However, we expect their partial sums to decay \emph{steadily}.
-The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ and may behave erratically.
+The series coefficients for wavenumbers $\bsk \in \calK_0$ do not affect the definition of $\calC_{\boldsymbol{\lambda},\bsn,a,b} $ and may behave erratically.
 Lemma \ref{DHKM:Key_Lem} implies that 
@@
 
-If $f$ belongs to the $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
+If $f$ belongs to the $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:TrackConeDef} and $n_0 = 0$, then 
 \begin{align*}
@@
 \end{align*}
-Comparing this inequality to the definition of $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}} $ in the previous section, it can be seen that $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone} if we choose
+Comparing this inequality to the definition of $\calC_{\boldsymbol{\lambda},n_1,A}$ in the previous section, it can be seen that $\calC_{\boldsymbol{\lambda},\bsn,a,b}$  defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC_{\boldsymbol{\lambda},n_1,A}$ defined in \eqref{DHKM:pilot_cone} if we choose
 $A=\left[1 + a^\rho b^\rho/(1 - b^\rho) \right]^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
 
-From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ and $j \in \bbN$:
+From the expression for the error in \eqref{DHKM:APP_Err_Coef} and the definition of the cone in  \eqref{DHKM:TrackConeDef}, we can now derive a data-driven error bound for all $f \in \calC_{\boldsymbol{\lambda},\bsn,a,b} $ and $j \in \bbN$:
 \begin{align}
@@
 These assumptions accommodate both the cases where the approximation converges algebraically and exponentially.
-To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \DHKMchange{\Theta(i^{-r_\Delta})}$ for some positive $r_\Delta > 1/\rho$.
-\DHKMchange{Here $r_\Delta$ reflects the smoothness of the input function.}  For this algebraic case one would normally define $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} $ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
+To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \Theta(i^{-r_\Delta})$ for some positive $r_\Delta > 1/\rho$.
+Here $r_\Delta$ reflects the smoothness of the input function.
+For this algebraic case one would normally define $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ in terms of an exponentially increasing sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 2^j$, which implies that
 \begin{align*}
     \sigma_j(f) &= \left[ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
-    = \DHKMchange{\Theta}\left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
-    & =\DHKMchange{\Theta}\left(  2^{-j(r_\Delta-1/\rho)} \right).
+    = \Theta\left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
+    & =\Theta\left(  2^{-j(r_\Delta-1/\rho)} \right).
 \end{align*}
@@
 for some constants $C_{\lo}$ and $C_{\up}$.
-\DHKMchange{By reasonable we mean that the values of $\sigma_j(f)$ would not drop precipitously and then rise again as $j$ increases.} Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
+By reasonable we mean that the values of $\sigma_j(f)$ would not drop precipitously and then rise again as $j$ increases.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ to include such functions.
 Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
 
-To illustrate the exponential case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \DHKMchange{\Theta}(\E^{-r_\Delta i})$.
+To illustrate the exponential case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \Theta(\E^{-r_\Delta i})$.
 For this exponential case one would normally define $\calC$ in terms of an arithmetic sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 + j q$, where $q$ is a positive integer.
@@
     \sigma_j(f) &= \left[ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
-    = \DHKMchange{\Theta} \left( \left [ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
-    & = \DHKMchange{\Theta} \left(  \E^{-j r_{\Delta} q} \right).
+    = \Theta \left( \left [ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
+    & = \Theta \left(  \E^{-j r_{\Delta} q} \right).
 \end{align*}
@@
 for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} q}$ causes the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ to include such functions.
+Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} q}$ causes the cone $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ to include such functions.
 Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
@@
 
-The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
+The data-driven error bound in \eqref{DHKM:algoineq} forms the basis for an adaptive Algorithm \ref{DHKM:TrackConeAlg}, which solves our problem for input functions in the cone $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:TrackConeDef}.
 The following theorem establishes its viability and information cost.
@@
 
-\DHKMchange{
-
 \begin{theorem}\label{DHKM:TrackConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC_{\boldsymbol{\lambda},\bsn,a,b})$ for $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:TrackConeDef}.
 The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
@@
 \end{equation}
-Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+Moreover, $\COST(\ALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
 \begin{equation} \label{DHKM:TractConejdagger}
@@
 For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
-For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
+For any $f \in  \calC_{\boldsymbol{\lambda},\bsn,a,b} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
 \begin{align*}
@@
 Our goal, as in Section \ref{DHKM:revisexamp}, is to derive upper and lower bounds on the information cost of Algorithm \ref{DHKM:TrackConeAlg}.
+For the illustrative example in Section \ref{DHKM:secexamp} with weights defined in \eqref{DHKM:IllExWts}, the sets $\calK_j$ look roughly like hyperbolic slices of $\N_0^d$.
 
@@
  & =  \sum_{l=1}^\infty
-( b^{j+l}\Lambda_{j+l})^\rho \\
+( b^{l}\Lambda_{j+l})^\rho \\
 & \le \sum_{l=1}^\infty  
@@
 \end{align*}
-From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TrackConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,a,b},\varepsilon,R) \le n_j = n_0 2^j$ \SimonNote{Should this be $\COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon,R)$?} for any $j$ satisfying
+From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TrackConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon,R) \le n_j = n_0 2^j$ for any $j$ satisfying
 \begin{align*}
@@
 Let $\card(\cdot)$ denote the cardinality of a set.
-We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le \DHKMchange{j+1}$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
+We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le j+1$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
 \begin{equation} \label{DHKM:PropCond}
@@
 
-The following theorem establishes a lower bound on the complexity of our problem for input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$.
+The following theorem establishes a lower bound on the complexity of our problem for input functions in $\calC_{\boldsymbol{\lambda},\bsn,a,b}$.
 The theorem after that shows that the cost of our algorithm as given in Theorem \ref{DHKM:TrackConeCompCost} is essentially no worse than this lower bound.
@@
  %\label{compbdA}
-&\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}),\varepsilon,R) > n_{j^\ddagger}, 
+&\COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) > n_{j^\ddagger}, 
 \intertext{where}
@@
 As in the proof of Theorem \ref{DHKM:PilotCostThm} we consider fixed and arbitrary R and $\varepsilon$.
-We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}\cap \calB_{R}$, which yield the same approximate solution but different true solutions.
-This leads to a lower bound on $\COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}),\varepsilon,R)$.
+We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC_{\boldsymbol{\lambda},\bsn,a,b}\cap \calB_{R}$, which yield the same approximate solution but different true solutions.
+This leads to a lower bound on $\COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R)$.
 The proof is provided for $\rho' < \infty$.
@@
 
-The first test function $f_1 \in \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
+The first test function $f_1 \in \calC_{\boldsymbol{\lambda},\bsn,a,b}$ is defined in terms of its series coefficients---inspired by Lemma \ref{DHKM:Key_Lem}---as
 \begin{align}
@@
 \end{align}
-It can be verified that the test function lies both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$:
+It can be verified that the test function lies both in $\calB_{R}$ and in $\calC_{\boldsymbol{\lambda},\bsn,a,b}$:
 \begin{align}
@@
 
-Now let $\ALG'$ be an arbitrary algorithm in $\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
+Now let $\ALG'$ be an arbitrary algorithm in $\calA(\calC_{\boldsymbol{\lambda},\bsn,a,b})$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
 Let $\tcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
@@
 Furthermore, define $f_{\pm} = f_1 \pm f_2$.
-It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$:
+It can be verified that $f_{\pm}$ also lie both in $\calB_{R}$ and in $\calC_{\boldsymbol{\lambda},\bsn,a,b}$:
 \begin{align}
@@
 \end{equation*}
-If any algorithm satisfies the error tolerance $\varepsilon$ for all input functions in $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} \cap \calB_R$ and has information cost no greater than $n_{j^\star}$, then $j^\star$ must satisfy the above inequality.
+If any algorithm satisfies the error tolerance $\varepsilon$ for all input functions in $\calC_{\boldsymbol{\lambda},\bsn,a,b} \cap \calB_R$ and has information cost no greater than $n_{j^\star}$, then $j^\star$ must satisfy the above inequality.
 By contrast, if the above inequality is violated for any $j^\star$, then the information cost of the successful algorithm must be greater than $n_{j^\star}$.
@@
 
-Making the $\varepsilon$ dependence explicit in the definition of $j^\ddagger(\varepsilon)$ in Theorem \ref{DHKM:TractConeLowBdComp} it follows from the above inequality that
+Making the $\varepsilon$ dependence explicit in the definition of $j^\ddagger(\varepsilon)$ in Theorem \ref{DHKM:TractConeLowBdComp} it follows from the above inequality and \eqref{DHKM:LambdaDecayCond} that
 \begin{equation*}
@@
      > \frac{\alpha^2}{(b\beta)^2} b^{j^\ddagger(\omega\varepsilon)+2} \Lambda_{j^\ddagger(\omega \varepsilon) + 2 } 
-    \ge \alpha b^{j^\ddagger(\omega\varepsilon)} \Lambda_{j^\ddagger(\omega \varepsilon)} \qquad \text{by \eqref{DHKM:LambdaDecayCond}}.
-\end{equation*}
-
+    \ge \alpha b^{j^\ddagger(\omega\varepsilon)} \Lambda_{j^\ddagger(\omega \varepsilon)}.
+\end{equation*}
 If $j^{\dagger}(\varepsilon) \ge j^{\ddagger}(\omega \varepsilon)$, then \eqref{DHKM:LambdaDecayCond} implies that 
@@
 \[
-\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}),\omega \varepsilon,R).
+\COST(\ALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\omega \varepsilon,R).
 \]
@@
 \begin{proof}
-As pointed out above, $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\DHKMchange{\calC_{\boldsymbol{\lambda},n_1,A}}$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
-This means that the approximation problem on  $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:pilot_cone}.
+As pointed out above, $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:TrackConeDef} is a subset of  $\calC_{\boldsymbol{\lambda},n_1,A}$ defined in \eqref{DHKM:pilot_cone}, by choosing $A=\left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}$ in \eqref{DHKM:pilot_cone}.
+This means that the approximation problem on  $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:TrackConeDef} is essentially (i.e., up to constants depending on $A,a,b$ and $\rho$) no harder than the same problem on $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:pilot_cone}.
 This, however, implies that all sufficient conditions in Theorem \ref{DHKM:thmtract1} are also sufficient in the case considered in Theorem \ref{DHKM:thmtract3}.
@@
 
-In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}, the weights \DHKMchange{$\bslambda = (\lambda_{\bsk_1}, \lambda_{\bsk_2}, \ldots )$}, which appear in the definition of the cone of inputs, \DHKMchange{$\calC_{\bslambda,n_1,A}$ and $\calC_{\bslambda,\bsn,a,b}$, are taken as given and fixed.
+In Sections \ref{DHKM:pilot_sec} and \ref{DHKM:tracking_sec}, the weights $\bslambda = (\lambda_{\bsk_1}, \lambda_{\bsk_2}, \ldots )$, which appear in the definition of the cone of inputs, $\calC_{\bslambda,n_1,A}$ and $\calC_{\bslambda,\bsn,a,b}$, are taken as given and fixed.
 One may assume the form suggested in \eqref{DHKM:prodwts}, which defines $\bslambda$ in terms of coordinate weights, $\bsw$, and smoothness weights, $\bss$.
@@
 This section explores a situation where the initial data collected for the input function data can be used to learn $\bsw$ and $\bss$, inferring which input variables in $f$ may be more important and the smoothness of the function.
-We focus on inferring the $\bslambda$ defining the cone $\calC_{\bslambda,n_1,A}$ in Section \ref{DHKM:pilot_sec}.}
+We focus on inferring the $\bslambda$ defining the cone $\calC_{\bslambda,n_1,A}$ in Section \ref{DHKM:pilot_sec}.
 
@@
 where $\bsw = (w_\ell)_{\ell=1}^d$ is the vector of coordinate weights, $\bss = (s_k)_{k=1}^\infty$ is the vector of smoothness weights,  $\boldsymbol{\Gamma} = (\Gamma_m)_{m=1}^d$ is the vector of \emph{order weights}, and $\norm[0]{\bsk}$ denotes the number of nonzero elements of $\bsk$.
-\DHKMchange{This is a generalization of the form for $\bslambda$ given by \eqref{DHKM:prodwts}.} The intuition behind these weights is as follows:
+This is a generalization of the form for $\bslambda$ given by \eqref{DHKM:prodwts}.
+The intuition behind these weights is as follows:
 \begin{itemize}
@@
 \begin{itemize}
-\item \emph{Effect sparsity} assumes that only a small number of \DHKMchange{coordinates in} $f$ are important.
+\item \emph{Effect sparsity} assumes that only a small number of coordinates in $f$ are important.
 In \eqref{DHKM:posdeq}, this sparsity means that only a small number of product weights $\bsw$ are large.
@@
 \vspace{-3ex}
-\DHKMchange{These principles will guide the inference of weights $\bslambda$ (and its corresponding cone of inputs $\calC_{\bslambda,n_1,A}$) from initial data.}
+These principles will guide the inference of weights $\bslambda$ (and its corresponding cone of inputs $\calC_{\bslambda,n_1,A}$) from initial data.
 
@@
 %Let $\calC_{\bslambda}$ denote the cone of inputs defined in \eqref{DHKM:pilot_cone} by POSD weights $\bslambda = \bigl( \lambda_{\bsk} \bigr)_{\bsk \in \N_0^d}$.
-As mentioned above, our goal here is to infer $\bslambda$ from input function data.  We start with an initial set of \DHKMchange{$d k_{\max} + 1$} wavenumbers:
+As mentioned above, our goal here is to infer $\bslambda$ from input function data.  We start with an initial set of $d k_{\max} + 1$ wavenumbers:
 \begin{equation} \label{DHKM:barKdef}
@@
 \end{equation}
-\DHKMchange{where the possible non-zero entry $k$ may be at any one position in the vector}. The approximation to $f$ based on sampling the series coefficients for these wavenumbers is
+where the possible non-zero entry $k$ may be at any one position in the vector. The approximation to $f$ based on sampling the series coefficients for these wavenumbers is
 \begin{equation*}
@@
 \end{equation*}
-\DHKMchange{To choose the cone $\calC_{\bslambda,n_1,A}$ which best fits $f$, we select the POSD weights $\bslambda$ to make the norm of $f_{\text{app}}$ small. These weights can be written as:}
+To choose the cone $\calC_{\bslambda,n_1,A}$ which best fits $f$, we select the POSD weights $\bslambda$ to make the norm of $f_{\text{app}}$ small. These weights can be written as:
 \begin{multline}
@@
 The cardinality of the initial set of wavenumbers is $d k_{\max} + 1$.
-There is a trade-off between keeping $k_{\max}$ small enough to reducing cost and making $k_{\max}$ large enough to ensuring robustness.
+There is a trade-off between keeping $k_{\max}$ small enough to reduce cost and making $k_{\max}$ large enough to ensure robustness.
 
@@
 \begin{equation} \label{DHKM:pilot_cone2}
-     \DHKMchange{\bar{\calC}_{n_1,A}} := \left \{ f \in \calF : f \in \DHKMchange{\calC_{\bar{\bslambda},n_1,A}} \text{ for } \bar{\bslambda} \text{ defined in \eqref{DHKM:eq:inf}} \right\}.
-\end{equation}
-The reason that \DHKMchange{$\bar{\calC}_{n_1,A}$} is a cone is that the data-inferred $\bar{\bslambda}$ for the input function $f$ is exactly the same as for the input function $cf$, where $c$ is any constant.
+    \bar{\calC}_{n_1,A} := \left \{ f \in \calF : f \in \calC_{\bar{\bslambda},n_1,A} \text{ for } \bar{\bslambda} \text{ defined in \eqref{DHKM:eq:inf}} \right\}.
+\end{equation}
+The reason that $\bar{\calC}_{n_1,A}$ is a cone is that the data-inferred $\bar{\bslambda}$ for the input function $f$ is exactly the same as for the input function $cf$, where $c$ is any constant.
 
@@
 	\begin{algorithmic}
-	\PARAM the bases $\{u_{\bsk}\}_{\bsk \in \N_0^d}$ and $\{v_{\bsk}\}_{\bsk \in \N_0^d}$; candidate sets $\calW$ and $\calS$ \DHKMchange{for product and smoothness weights}; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:Refined_APP_err}
+	\PARAM the bases $\{u_{\bsk}\}_{\bsk \in \N_0^d}$ and $\{v_{\bsk}\}_{\bsk \in \N_0^d}$; candidate sets $\calW$ and $\calS$ for product and smoothness weights; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:Refined_APP_err}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 \State Evaluate initial sample $\bigl\{\hf(\bsk)\bigr\}_{\bsk \in \bcalK}$
-\State Compute data-driven POSD weight $\bar{\bslambda}$\DHKMchange{, by iteratively optimizing over $(\bsw, \bss) \in \calW \times \calS$ in \eqref{DHKM:eq:inf} until convergence}
+\State Compute data-driven POSD weight $\bar{\bslambda}$, by iteratively optimizing over $(\bsw, \bss) \in \calW \times \calS$ in \eqref{DHKM:eq:inf} until convergence
 \State Using these weights, $\bar{\bslambda}$, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\ALG(f,\varepsilon)$
@@
 For simplicity, only the case of $\rho = \infty$ and $\rho' = \tau = 1$ is considered in the following examples.
-Here, the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are Chebyshev polynomials in Section \ref{DHKM:secexamp}, and the solution operator is $\SOL (f) = f$ (i.e., function approximation).
+Here, the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are the Chebyshev polynomials in Section \ref{DHKM:secexamp}, and the solution operator is $\SOL (f) = f$ (i.e., function approximation).
 We note that $\|f - \ALG(f,\varepsilon)\|_\infty \le \|f - \ALG(f,\varepsilon)\|_\calG$, so our error criterion \eqref{DHKM:err_crit} implies that $\|f - \ALG(f,\varepsilon)\|_\infty \le \varepsilon$.
@@
 \begin{acknowledgement}
-\DHKMchange{The authors would like to thank two anonymous referees for their suggestions which helped to improve the presentation of the results.}
+The authors would like to thank two anonymous referees for their suggestions which helped to improve the presentation of the results. Furthermore, the authors thank 
+Stefan Heinrich and Aicke Hinrichs for helpful comments.
 
@@
 \end{document}
-
-\iffalse 
-\begin{theorem}\label{DHKM:TractConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}})$ for $\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}}$ defined in \eqref{DHKM:TrackConeDef}.
-The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
-\begin{equation} \label{DHKM:EqTrackConejstar}
-j^* = \min\left \{ j \in \bbN : \ERRNj \le \varepsilon  \right\}.
-\end{equation}
-Moreover, $\COST(\ALG,\DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
-\begin{equation} \label{DHKM:TractConejdagger}
-j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{j+r}\Lambda_{j+r} \bigr)_{r=1}^\infty}
-\le  \frac{b\varepsilon}{Ra^2} \left( \frac{1 - b^{j\rho}}{1 - b^\rho} \right)^{1/\rho} \right\}.
-\end{equation}
-\end{theorem}
-
-\begin{proof}
-The value of $j^*$ in \eqref{DHKM:EqTrackConejstar} follows directly from the error criterion. The success of the algorithm follows from the error bound in \eqref{DHKM:algoineq}.
-
-For the remainder of the proof consider $R$ and $\varepsilon$ to be fixed.
-For any $f \in  \DHKMchange{\calC_{\boldsymbol{\lambda},\bsn,a,b}} \cap \calB_R$ and for any $j^\dagger$ defined  as in \eqref{DHKM:TractConejdagger}, it follows that
-\begin{align*}
-R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
- \ge \norm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
- \qquad \text{by \eqref{DHKM:SigmaDef} } \\
-& \ge \norm[\rho]{\left(a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f), \ldots, a^{-1} b^{-1}\sigma_{j^\dagger}(f), \sigma_{j^\dagger}(f) \right) } \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
-& \ge \frac {\sigma_{j^\dagger}(f)} a \norm[\rho]{\bigl(b^{1-j^\dagger}, \ldots, b^{-1}, 1 \bigr) } 
-= \frac {b\sigma_{j^\dagger}(f)} a \left( \frac{b^{-j^\dagger\rho} -1}{1 - b^\rho} \right)^{1/\rho}\\
-& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^r\Lambda_{j^\dagger+r} \bigr)_{r=1}^\infty}
-\qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
-& = \frac{R}{\varepsilon} \ERRNjd\, .
-\end{align*}
-From this last inequality, it follows that $j^\dagger \ge j^*$.
-\end{proof} 
-\fi

### 2019-10-31 DingHickKritzMakRICAMChapVerF.tex
Updates from Overleaf

--- 2019-10-31 DingHickKritzMakRICAMChapVerE.tex
@@
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\algnewcommand\algorithmicparam{\textbf{Parameters:}}
-\algnewcommand\PARAM{\item[\algorithmicparam]}
-\algnewcommand\algorithmicinput{\textbf{Input:}}
-\algnewcommand\INPUT{\item[\algorithmicinput]}
-%\algnewcommand\STATE{\item}
-\algnewcommand\RETURN{\State \textbf{Return }}
+\DHKMALGnewcommand\DHKMALGorithmicparam{\textbf{Parameters:}}
+\DHKMALGnewcommand\PARAM{\item[\DHKMALGorithmicparam]}
+\DHKMALGnewcommand\DHKMALGorithmicinput{\textbf{Input:}}
+\DHKMALGnewcommand\INPUT{\item[\DHKMALGorithmicinput]}
+%\DHKMALGnewcommand\STATE{\item}
+\DHKMALGnewcommand\RETURN{\State \textbf{Return }}
 
@@
 
-\DeclareMathOperator{\SOL}{SOL}
-\DeclareMathOperator{\APP}{APP}
-\DeclareMathOperator{\ALG}{ALG}
-\DeclareMathOperator{\ERR}{ERR}
-\DeclareMathOperator{\card}{card}
-\newcommand{\dataN}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^n}
-\newcommand{\dataNj}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_j}}
-\newcommand{\dataNjd}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_{j^\dagger}}}
-\newcommand{\ERRN}{\ERR\bigl(\dataN,n\bigr)}
-\newcommand{\ERRNj}{\ERR\bigl(\dataNj,n_j\bigr)}
-\newcommand{\ERRNjd}{\ERR\bigl(\dataNjd,n_{j^\dagger}\bigr)}
-\DeclareMathOperator{\COST}{COST}
+\DeclareMathOperator{\DHKMSOL}{SOL}
+\DeclareMathOperator{\DHKMAPP}{APP}
+\DeclareMathOperator{\DHKMALG}{ALG}
+\DeclareMathOperator{\DHKMERR}{ERR}
+\DeclareMathOperator{\DHKMcard}{card}
+\newcommand{\DHKMdataN}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^n}
+\newcommand{\DHKMdataNj}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_j}}
+\newcommand{\DHKMdataNjd}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_{j^\dagger}}}
+\newcommand{\DHKMERRN}{\DHKMERR\bigl(\DHKMdataN,n\bigr)}
+\newcommand{\DHKMERRNj}{\DHKMERR\bigl(\DHKMdataNj,n_j\bigr)}
+\newcommand{\DHKMERRNjd}{\DHKMERR\bigl(\DHKMdataNjd,n_{j^\dagger}\bigr)}
+\DeclareMathOperator{\DHKMCOST}{COST}
 \DeclareMathOperator{\COMP}{COMP}
@@
 
-We study the approximation of a linear solution operator $\SOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
-Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\ALG(\cdot,\cdot):\calC \times (0,\infty) \to \calG$ that satisfies the error criterion:
+We study the approximation of a linear solution operator $\DHKMSOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
+Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\DHKMALG(\cdot,\cdot):\calC \times (0,\infty) \to \calG$ that satisfies the error criterion:
 \begin{equation} \label{DHKM:err_crit}
-    \norm[\calG]{\SOL(f) - \ALG(f,\varepsilon)} \le \varepsilon \qquad \forall \varepsilon > 0, \ f \in \calC,
+    \norm[\calG]{\DHKMSOL(f) - \DHKMALG(f,\varepsilon)} \le \varepsilon \qquad \forall \varepsilon > 0, \ f \in \calC,
 \end{equation}
@@
     \item choose a set $\calC$ of input functions for which the rule is valid,  
-    \item characterize the information cost of $\ALG$, 
-    \item determine whether $\ALG$ has optimal information cost, and 
+    \item characterize the information cost of $\DHKMALG$, 
+    \item determine whether $\DHKMALG$ has optimal information cost, and 
     \item understand the dependence of this cost on the number of input variables, $d$, as well as the error tolerance, $\varepsilon$.
@@
 
-We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\ALG (f,\varepsilon)$ to use $n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
+We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\DHKMALG (f,\varepsilon)$ to use $n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
 That is,
@@
 \begin{equation*} %\label{DHKM:algform}
-  \ALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) v_{\bsk_i} \qquad \forall f \in \calF, \ n(f,\varepsilon) \in \N,
+  \DHKMALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) v_{\bsk_i} \qquad \forall f \in \calF, \ n(f,\varepsilon) \in \N,
 \end{equation*}
@@
 
-The information cost of $\ALG(f,\varepsilon)$ is denoted $\COST(\ALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\ALG(f,\varepsilon)$, i.e., $\COST(\ALG,f,\varepsilon) = n(f,\varepsilon)$.
+The information cost of $\DHKMALG(f,\varepsilon)$ is denoted $\DHKMCOST(\DHKMALG,f,\varepsilon)$ and defined as the number of function data---in our situation, series coefficients---required by $\DHKMALG(f,\varepsilon)$, i.e., $\DHKMCOST(\DHKMALG,f,\varepsilon) = n(f,\varepsilon)$.
 For adaptive algorithms this cost varies with the input function $f$.
@@
 \begin{equation*}
-    \COST(\ALG, \calC, \varepsilon,R) : = \max_{f \in \calC \cap \calB_{R}} \COST(\ALG,f,\varepsilon).
-\end{equation*}
-Note that while the cost depends on $\norm[\calF]{f}$, $\ALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
-It is common for $\COST(\ALG, \calC, \varepsilon,R)$ to be $\calO(\varepsilon^{-p})$, or perhaps asymptotically $c\log(1 + \varepsilon^{-1})$.
+    \DHKMCOST(\DHKMALG, \calC, \varepsilon,R) : = \max_{f \in \calC \cap \calB_{R}} \DHKMCOST(\DHKMALG,f,\varepsilon).
+\end{equation*}
+Note that while the cost depends on $\norm[\calF]{f}$, $\DHKMALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
+It is common for $\DHKMCOST(\DHKMALG, \calC, \varepsilon,R)$ to be $\calO(\varepsilon^{-p})$, or perhaps asymptotically $c\log(1 + \varepsilon^{-1})$.
 
@@
 \begin{equation*}
-    \COMP(\calC, \varepsilon,R) := \min_{\ALG \in \calA(\calC)} \COST(\ALG, \calC, \varepsilon,R) .
+    \COMP(\calC, \varepsilon,R) := \min_{\DHKMALG \in \calA(\calC)} \DHKMCOST(\DHKMALG, \calC, \varepsilon,R) .
 \end{equation*}
@@
 \begin{multline} \label{DHKM:EssentialOpt}
-    \COST(\ALG, \calC, \varepsilon,R) \le \COMP(\calC, \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+    \DHKMCOST(\DHKMALG, \calC, \varepsilon,R) \le \COMP(\calC, \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
 \end{multline}
@@
 However, typically one cannot bound the norm of the input function a priori, so non-adaptive algorithms may be impractical.
-This will lead to \emph{adaptive} algorithms $\ALG$ satisfying error criterion \eqref{DHKM:err_crit}.
+This will lead to \emph{adaptive} algorithms $\DHKMALG$ satisfying error criterion \eqref{DHKM:err_crit}.
 For such algorithms, the set of allowable input functions, $\calC$, will be a \emph{cone}, not a ball.
@@
 Any algorithm must require a finite sample size, even if it is huge.
-Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\SOL(f)}$ is arbitrarily large.
+Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\DHKMSOL(f)}$ is arbitrarily large.
 Thus, algorithms satisfying the error criterion  exist only for some strict subset of $\calF$, such as a ball or a cone.
@@
 Now, we define our problem more formally.
-The solution operator $\SOL$ maps the input function to an output, $\SOL:\calF \to \calG$.
+The solution operator $\DHKMSOL$ maps the input function to an output, $\DHKMSOL:\calF \to \calG$.
 The Banach spaces of inputs and outputs are defined by series expansions:
@@
 \begin{equation} \label{DHKM:basis_relate}
-    \SOL(u_{\bsk}) = v_{\bsk} \qquad \forall \bsk \in \mathbb{K}.
+    \DHKMSOL(u_{\bsk}) = v_{\bsk} \qquad \forall \bsk \in \mathbb{K}.
 \end{equation}
@@
 implies an ordering of the wavenumbers, $\bsk$.
-We also assume that all $\lambda_{\bsk}$ are  positive to avoid the trivial case where $\SOL(f)$ can be expressed exactly as a finite sum for all $f \in \calF$.
+We also assume that all $\lambda_{\bsk}$ are  positive to avoid the trivial case where $\DHKMSOL(f)$ can be expressed exactly as a finite sum for all $f \in \calF$.
 We denote the sequence of weights  $\bigl(\lambda_{\bsk_i}\bigr)_{i=1}^\infty$ by $\bslambda$.
@@
 \label{DHKM:SOL_ineq}
-    \norm[\calG]{\SOL(f)} = \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK}} \le \norm[\calF]{f} \, \Lambda,
+    \norm[\calG]{\DHKMSOL(f)} = \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK}} \le \norm[\calF]{f} \, \Lambda,
     \end{equation}
@@
    \\ 
-    \implies  \ \ \norm[\calF]{f} = R \ \mbox{and} \ \norm[\calG]{\SOL(f)} = R \Lambda.
+    \implies  \ \ \norm[\calF]{f} = R \ \mbox{and} \ \norm[\calG]{\DHKMSOL(f)} = R \Lambda.
     \end{multline}
@@
     \label{DHKM:SOL_A}
-    \norm[\calG]{\SOL(f)}  
+    \norm[\calG]{\DHKMSOL(f)}  
     & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
@@
 \begin{equation*}
-       \norm[\calG]{\SOL(f)}  
+       \norm[\calG]{\DHKMSOL(f)}  
     =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\Lambda^{\rho'/\rho}} 
@@
 \begin{equation} \label{DHKM:SOLNorm}
-    \norm[\calF \to \calG]{\SOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\SOL(f)} = \bignorm[\rho']{\bslambda}.
+    \norm[\calF \to \calG]{\DHKMSOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\DHKMSOL(f)} = \bignorm[\rho']{\bslambda}.
 \end{equation}
@@
 
-Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\SOL(f) = f$.  In this case,
-	\begin{align*}
-	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \SOL(f), 
+Consider the case of approximating functions defined over $[-1,1]^d$, using a Chebyshev polynomial basis.  The input function is denoted $f$, and the solution is $\DHKMSOL(f) = f$.  In this case,
+	\begin{align*}
+	f &  = \sum_{\bsk \in \bbN_0^d} \widehat{f}(\bsk) u_\bsk =: \DHKMSOL(f), 
 	\qquad \bsk = (k_1, \ldots, k_d) \in \N_0^d,\\
@@
 \begin{equation*} %\label{DHKM:Ex_APP_def}
-   \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N.
+   \DHKMAPP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N.
 \end{equation*}
@@
 \begin{equation*}
-    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}.
+    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}.
 \end{equation*}
 Here we have chosen $\tau = 2$ so $\rho'=\infty$.
-If one has a fixed data budget, $n$, then $\APP(f,n)$ is the best answer for certain classes of inputs in $\calF$ as for example balls, which are among the most prominent examples studied in the literature.
+If one has a fixed data budget, $n$, then $\DHKMAPP(f,n)$ is the best answer for certain classes of inputs in $\calF$ as for example balls, which are among the most prominent examples studied in the literature.
 
@@
 \begin{equation} \label{DHKM:APP_def}
-    \APP : \calF \times \N_0 \to \calG, \quad  \APP(f,0) = 0, \ \ \APP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
+    \DHKMAPP : \calF \times \N_0 \to \calG, \quad  \DHKMAPP(f,0) = 0, \ \ \DHKMAPP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
 \end{equation}
@@
 \begin{equation} \label{DHKM:APP_Err_Coef}
-    \norm[\calG]{\SOL(f) - \APP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
+    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
 \end{equation}
@@
 \begin{gather} \label{DHKM:Refined_APP_err}
-    \norm[\calG]{\SOL(f) - \APP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
+    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
     \bignorm[\rho']{\bslambda^{(n+1)}}, \\
@@
 \begin{equation} \label{DHKM:APP_errorBd}
-    \sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
-\end{equation}
-Moreover, the worst case error over $\calB_R$ of $\APP'(\cdot,n)$, for any approximation based on $n$ series coefficients of the input function, can be no smaller.
+    \sup_{f \in \calB_R} \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
+\end{equation}
+Moreover, the worst case error over $\calB_R$ of $\DHKMAPP'(\cdot,n)$, for any approximation based on $n$ series coefficients of the input function, can be no smaller.
 \end{theorem}
@@
 The proof of \eqref{DHKM:APP_errorBd} follows immediately from \eqref{DHKM:Refined_APP_err} and  Lemma \ref{DHKM:Key_Lem}.
-The optimality of $\APP$ follows by bounding the error of an arbitrary approximation, $\APP'$, applied to functions that mimic the zero function.
-
-Let $\APP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.
+The optimality of $\DHKMAPP$ follows by bounding the error of an arbitrary approximation, $\DHKMAPP'$, applied to functions that mimic the zero function.
+
+Let $\DHKMAPP'(0,n)$ depend on the series coefficients indexed by $\calJ  = \{\bsk'_1, \ldots, \bsk'_n\}$.
 Use Lemma \ref{DHKM:Key_Lem} with $\calK = \bbK \setminus \calJ$ to choose $f$ to mimic the zero function, have norm $R$, and have as large a solution as possible by \eqref{DHKM:SOL_tight_ineq}, i.e.,
@@
     \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ 
-    \norm[\calG]{\SOL(f)} =  R \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.  \label{DHKM:FoolFun}
+    \norm[\calG]{\DHKMSOL(f)} =  R \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.  \label{DHKM:FoolFun}
 \end{gather}
-Then $\APP'(\pm f,n) = \APP'(0,n)$ because $f$ mimics the zero function, and
-\begin{align*}
-\MoveEqLeft{\sup_{f \in \calB_R} \norm[\calG]{\SOL(f) - \APP(f,n)}} \\
-& \ge \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(\pm f,n)} =  \max_{\pm} \norm[\calG]{\SOL(\pm f) - \APP'(0,n)} \\
-& \ge \frac 12 \left [ \norm[\calG]{\SOL(f) - \APP'(0,n)} 
-+ \norm[\calG]{- \SOL(f) - \APP'(0,n)}\right] \\
-& \ge \norm[\calG]{\SOL(f)} 
+Then $\DHKMAPP'(\pm f,n) = \DHKMAPP'(0,n)$ because $f$ mimics the zero function, and
+\begin{align*}
+\MoveEqLeft{\sup_{f \in \calB_R} \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}} \\
+& \ge \max_{\pm} \norm[\calG]{\DHKMSOL(\pm f) - \DHKMAPP'(\pm f,n)} =  \max_{\pm} \norm[\calG]{\DHKMSOL(\pm f) - \DHKMAPP'(0,n)} \\
+& \ge \frac 12 \left [ \norm[\calG]{\DHKMSOL(f) - \DHKMAPP'(0,n)} 
++ \norm[\calG]{- \DHKMSOL(f) - \DHKMAPP'(0,n)}\right] \\
+& \ge \norm[\calG]{\DHKMSOL(f)} 
  = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:FoolFun}}.
@@
 
-While approximation $\APP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\ALG : \calC \times [0,\infty)$, satisfying the absolute error criterion \eqref{DHKM:err_crit}.
+While approximation $\DHKMAPP$ is a key piece of the puzzle, our ultimate goal is an algorithm, $\DHKMALG : \calC \times [0,\infty)$, satisfying the absolute error criterion \eqref{DHKM:err_crit}.
 The non-adaptive Algorithm \ref{DHKM:BallAlg} satisfies this error criterion for $\calC  = \calB_R$.
@@
 \begin{algorithm}[H]
-\caption{Non-Adaptive $\ALG$ for a Ball of Input Functions \label{DHKM:BallAlg}}
+\caption{Non-Adaptive $\DHKMALG$ for a Ball of Input Functions \label{DHKM:BallAlg}}
 	\begin{algorithmic}
-	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; the ball radius, $R$; $\APP$ satisfying \eqref{DHKM:APP_errorBd}
+	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; the ball radius, $R$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_errorBd}
 	\INPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$
@@
 
-    \RETURN $\ALG(f,\varepsilon) = \APP(f,n^*)$
+    \RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n^*)$
 \end{algorithmic}
@@
 \[
-\COST(\ALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}, \qquad R’ \in (0, R].
+\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}, \qquad R’ \in (0, R].
 \]
@@
 \begin{multline*}
-\COST(\ALG, \calB_R, \varepsilon,R') \le \COMP(\calB_R,\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
+\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') \le \COMP(\calB_R,\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
 \end{multline*}
@@
 $
-n^*(\varepsilon,R) : = \COST(\ALG, \calB_R, \varepsilon,R').
+n^*(\varepsilon,R) : = \DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R').
 $
 Construct an input function $f \in \calB_{R'}$ as in the proof of Theorem \ref{DHKM:APP_optimality_thm} with $\calJ = \{\bsk_1, \ldots, \bsk_{n^*(\omega \varepsilon,R')} \}$.
-By the argument in the proof of Theorem \ref{DHKM:APP_optimality_thm}, any algorithm in $\calA(\calB_{R'})$ that can approximate $\SOL(f)$ with an error no greater than $\omega \varepsilon$ must use at least $n^*(\omega \varepsilon,R')$ series coefficients.
+By the argument in the proof of Theorem \ref{DHKM:APP_optimality_thm}, any algorithm in $\calA(\calB_{R'})$ that can approximate $\DHKMSOL(f)$ with an error no greater than $\omega \varepsilon$ must use at least $n^*(\omega \varepsilon,R')$ series coefficients.
 Thus,
 \begin{align*}
-\COST(\ALG, \calB_R, \varepsilon,R') & =  n^*(\varepsilon,R) 
+\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') & =  n^*(\varepsilon,R) 
 = n^*(\varepsilon R'/R,R') \\
@@
 
-For Algorithm \ref{DHKM:BallAlg}, the information cost, $\COST(\ALG,\calB_R,\varepsilon, R)$, depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
+For Algorithm \ref{DHKM:BallAlg}, the information cost, $\DHKMCOST(\DHKMALG,\calB_R,\varepsilon, R)$, depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
 This decay may be algebraic or exponential and also determines the problem complexity, $\COMP(\calB_R,\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
@@
 \end{equation}
-Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\APP(f,n)$ depends on the series coefficients not sampled.
+Referring to error bound \eqref{DHKM:Refined_APP_err}, we see that the error of $\DHKMAPP(f,n)$ depends on the series coefficients not sampled.
 The definition of $\calC_{\boldsymbol{\lambda},n_1,A}$ allows us to bound these as follows:
@@
 \begin{equation}
-\norm[\calG]{\SOL(f) - \APP(f,n)}  \le \ERRN  \qquad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A},
+\norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le \DHKMERRN  \qquad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A},
 \end{equation}
@@
 \begin{multline} \label{ErrNDef}
-\ERRN \\
+\DHKMERRN \\
     : =  
@@
 \begin{algorithm}
-	\caption{$\ALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
+	\caption{$\DHKMALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
 	\begin{algorithmic}
-	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:Refined_APP_err}
+	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 
-\State Compute $\ERRN$ as defined in \eqref{DHKM:pilot_errbd}
-
-\Until $\ERRN \le \varepsilon$
-
-\RETURN $\ALG(f,\varepsilon) = \APP(f,n)$
+\State Compute $\DHKMERRN$ as defined in \eqref{DHKM:pilot_errbd}
+
+\Until $\DHKMERRN \le \varepsilon$
+
+\RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n)$
 
@@
 \begin{theorem} \label{DHKM:PilotCostThm}
-Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC_{\boldsymbol{\lambda},n_1,A})$ for $\calC_{\boldsymbol{\lambda},n_1,A}$ defined in \eqref{DHKM:pilot_cone}.
+Algorithm \ref{DHKM:PilotConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\DHKMALG \in \calA(\calC_{\boldsymbol{\lambda},n_1,A})$ for $\calC_{\boldsymbol{\lambda},n_1,A}$ defined in \eqref{DHKM:pilot_cone}.
 The information cost is
 \begin{multline} \label{DHKM:PilotConeAlg_cost}
-    \COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \\
+    \DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \\
     = \min \left \{n \ge n_1 : \bignorm[\rho']{\bslambda^{(n+1)}} \,
@@
 \begin{align*}
-    \MoveEqLeft[1]{\COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R)} \\
-    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \ERRN \le \varepsilon \right \} \\
+    \MoveEqLeft[1]{\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R)} \\
+    & = \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : \DHKMERRN \le \varepsilon \right \} \\
      & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
@@
     \]
-Let $\ALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC_{\boldsymbol{\lambda},n_1,A}$ in \eqref{DHKM:pilot_cone}.
+Let $\DHKMALG'$ be any algorithm that satisfies the error criterion, \eqref{DHKM:err_crit}, for this choice of $\calC_{\boldsymbol{\lambda},n_1,A}$ in \eqref{DHKM:pilot_cone}.
 Fix $R \in [R_{\min},\infty)$ and $\varepsilon \in (0,\varepsilon_{\max}]$ arbitrarily.
@@
 \end{equation*}
-Suppose that $\ALG'(f_1,\varepsilon)$ samples the series coefficients $\hf_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
+Suppose that $\DHKMALG'(f_1,\varepsilon)$ samples the series coefficients $\hf_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
 
@@
     \label{DHKM:SOLf2bd}
-    \norm[\calG]{\SOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
+    \norm[\calG]{\DHKMSOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
 \end{gather}
@@
 Therefore, $f_\pm \in \calC_{\boldsymbol{\lambda},n_1,A} \cap \calB_R$.
-Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\ALG'(f_+,\varepsilon) = \ALG'(f_-,\varepsilon)$.
-Thus, $\SOL(f_{+})$ must be quite similar to $\SOL(f_{-})$.
+Moreover, since the series coefficients for $f_\pm$ are the same for $\bsk \in \calJ$, it follows that $\DHKMALG'(f_+,\varepsilon) = \DHKMALG'(f_-,\varepsilon)$.
+Thus, $\DHKMSOL(f_{+})$ must be quite similar to $\DHKMSOL(f_{-})$.
 
@@
 \begin{align*}
-\varepsilon & \ge \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{\pm},\varepsilon)} 
-=  \max_{\pm} \norm[\calG]{\SOL(f_{\pm}) - \ALG'(f_{+},\varepsilon)} \\
-& \ge \frac 12 \left [ \norm[\calG]{\SOL(f_{+}) - \ALG'(f_{+},\varepsilon)} 
-+ \norm[\calG]{\SOL(f_{-}) - \ALG'(f_{+},\varepsilon)}  \right] \\
-& \ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} = \norm[\calG]{\SOL(f_2)} 
+\varepsilon & \ge \max_{\pm} \norm[\calG]{\DHKMSOL(f_{\pm}) - \DHKMALG'(f_{\pm},\varepsilon)} 
+=  \max_{\pm} \norm[\calG]{\DHKMSOL(f_{\pm}) - \DHKMALG'(f_{+},\varepsilon)} \\
+& \ge \frac 12 \left [ \norm[\calG]{\DHKMSOL(f_{+}) - \DHKMALG'(f_{+},\varepsilon)} 
++ \norm[\calG]{\DHKMSOL(f_{-}) - \DHKMALG'(f_{+},\varepsilon)}  \right] \\
+& \ge \frac 12 \norm[\calG]{\DHKMSOL(f_+ - f_-)} = \norm[\calG]{\DHKMSOL(f_2)} 
 =\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
@@
 \[
-\COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \le \COMP(\calC_{\boldsymbol{\lambda},n_1,A},\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
+\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \le \COMP(\calC_{\boldsymbol{\lambda},n_1,A},\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
 \]
@@
 
-We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\ERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
+We may not be able to guarantee that a particular $f$ of interest lies in our cone, $\calC_{\boldsymbol{\lambda},n_1,A}$, but the definition of $\DHKMERRN$ in \eqref{ErrNDef} provides a necessary condition for  $f$ to lie in $\calC_{\boldsymbol{\lambda},n_1,A}$, namely,
 \begin{equation} \label{DHKM:PilotConeNecessary}
@@
 \begin{align*}
-    \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \COST(\ALG,\calB_R,\varepsilon, R') 
+    \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \DHKMCOST(\DHKMALG,\calB_R,\varepsilon, R') 
     \le \left \lceil  \left(\frac{R \norm[p]{\bslambda}}{\varepsilon}\right)^p     \right \rceil, \qquad \forall \varepsilon, \ 0 < R' < R, \\
-    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \\ & \qquad \qquad \le \max \left( n_1, 
@@
 \begin{align*}
-    \COST(\ALG,\calB_R,\varepsilon, R') 
+    \DHKMCOST(\DHKMALG,\calB_R,\varepsilon, R') 
     \le C \varepsilon^{-p} & \quad \forall \varepsilon \in (0,\varepsilon_{\max}] \quad  \text{for Algorithm \ref{DHKM:BallAlg}, or }  \\
-     \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+     \DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \le C \varepsilon^{-p} & \quad \forall \varepsilon \in (0,\varepsilon_{\max}] \quad \text{for Algorithm \ref{DHKM:PilotConeAlg}},
@@
 \begin{align*} 
-    \COST(\ALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R)
+    \DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R)
     & = \min \left \{n \ge n_1 : \lambda_{\bsk_{n+1}}
@@
 
-Now suppose that $\COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
-    \le C \varepsilon^{-p}$ for all $\varepsilon \in (0,\varepsilon_{\max}]$.  Since the information cost is an integer, this means that $\COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+Now suppose that $\DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \le C \varepsilon^{-p}$ for all $\varepsilon \in (0,\varepsilon_{\max}]$.  Since the information cost is an integer, this means that $\DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \le \lfloor C \varepsilon^{-p} \rfloor$  and let $n_{\min} = \lfloor C \varepsilon_{\max}^{-p} \rfloor +1$. 
@@
         AR} < \infty\\
-        & \hspace{3cm} \text{since } \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+        & \hspace{3cm} \text{since } \DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \le \lfloor C \varepsilon^{-p} \rfloor.
@@
 \begin{align*}
-    \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \COST(\ALG,\calB_R,\varepsilon, R') 
+    \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \DHKMCOST(\DHKMALG,\calB_R,\varepsilon, R') 
     \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil, \\
-    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \COST(\ALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
+    \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \\ & \qquad \qquad \le \max \left( n_1, 
@@
 Thus, for the sake of brevity, we write $\calC_d$ instead of $\calC_{\bslambda,n_1,A}$ in this section.
-Also, $\SOL$, $\APP$, $\COST$, and $\COMP$ depend implicitly on the dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
+Also, $\DHKMSOL$, $\DHKMAPP$, $\DHKMCOST$, and $\COMP$ depend implicitly on the dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
 
@@
 
-From error bound \eqref{DHKM:APP_Err_Coef} it follows that the faster the $\hf(\bsk_i)$ decay, the faster $\APP(f,n)$ converges to the solution.
+From error bound \eqref{DHKM:APP_Err_Coef} it follows that the faster the $\hf(\bsk_i)$ decay, the faster $\DHKMAPP(f,n)$ converges to the solution.
 Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
@@
 
-Because $ab^l$ may be greater than one, we do not require the series coefficients of the solution, $\SOL(f)$, to decay monotonically.
+Because $ab^l$ may be greater than one, we do not require the series coefficients of the solution, $\DHKMSOL(f)$, to decay monotonically.
 However, we expect their partial sums to decay \emph{steadily}.
@@
 \begin{equation} \label{DHKM:NormLambdaFinite}
-    \norm[\calF \to \calG]{\SOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
+    \norm[\calF \to \calG]{\DHKMSOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
 \end{equation}
@@
 \nonumber
-\MoveEqLeft{\norm[\calG]{\SOL(f)-\APP(f,n_j)}} \\
+\MoveEqLeft{\norm[\calG]{\DHKMSOL(f)-\DHKMAPP(f,n_j)}} \\
 \nonumber &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty}
@@
 \\
-& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^l\Lambda_{j+l} \bigr)_{l=1}^\infty} =:\ERRNj
+& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^l\Lambda_{j+l} \bigr)_{l=1}^\infty} =:\DHKMERRNj
  \qquad \text{by \eqref{DHKM:TrackConeDef}.}
@@
 The error vanishes as $j \to \infty$ because $\sigma_j(f) \le ab^{j-1} \sigma_1(f) \to 0$ and $\Lambda_j \to 0$.
-Moreover, the error bound for $\APP(f,n_j)$ depends on $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
+Moreover, the error bound for $\DHKMAPP(f,n_j)$ depends on $\sigma_j(f)$, whose rate of decay need not be postulated in advance.
 
@@
 	\begin{algorithmic}
-	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0}$; an inflation factor, $a$; the general decay rate, $b$; $\APP$ satisfying \eqref{DHKM:APP_Err_Coef}
+	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0}$; an inflation factor, $a$; the general decay rate, $b$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_Err_Coef}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 
-\State Compute $\ERRNj$ as defined in \eqref{DHKM:algoineq}
-
-\Until $\ERRNj \le \varepsilon$
-
-\RETURN $\ALG(f,\varepsilon) = \APP(f,n_{j})$
+\State Compute $\DHKMERRNj$ as defined in \eqref{DHKM:algoineq}
+
+\Until $\DHKMERRNj \le \varepsilon$
+
+\RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n_{j})$
 \end{algorithmic}
@@
 \begin{theorem}\label{DHKM:TrackConeCompCost}
-Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\ALG \in \calA(\calC_{\boldsymbol{\lambda},\bsn,a,b})$ for $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:TrackConeDef}.
-The information cost is $\COST(\ALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
+Algorithm \ref{DHKM:TrackConeAlg} yields an answer satisfying absolute error criterion \eqref{DHKM:err_crit}, i.e., $\DHKMALG \in \calA(\calC_{\boldsymbol{\lambda},\bsn,a,b})$ for $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ defined in \eqref{DHKM:TrackConeDef}.
+The information cost is $\DHKMCOST(\DHKMALG,f,\varepsilon)=n_{j^*}$, where $j^*$ is defined implicitly as
 \begin{equation} \label{DHKM:EqTrackConejstar}
-j^* = \min\left \{ j \in \bbN : \ERRNj \le \varepsilon  \right\}.
-\end{equation}
-Moreover, $\COST(\ALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
+j^* = \min\left \{ j \in \bbN : \DHKMERRNj \le \varepsilon  \right\}.
+\end{equation}
+Moreover, $\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger}$, where $j^\dagger$ is defined as follows:
 \begin{equation} \label{DHKM:TractConejdagger}
@@
 \qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
-& = \frac{R}{\varepsilon} \ERRNjd\, .
+& = \frac{R}{\varepsilon} \DHKMERRNjd\, .
 \end{align*}
@@
 \end{align*}
-From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TrackConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon,R) \le n_j = n_0 2^j$ for any $j$ satisfying
+From \eqref{DHKM:TractConejdagger} in Theorem \ref{DHKM:TrackConeCompCost} it follows that the cost of Algorithm \ref{DHKM:TrackConeAlg} has an upper bound of $\DHKMCOST(\DHKMALG,\calC_{\bslambda,\bsn,a,b},\varepsilon,R) \le n_j = n_0 2^j$ for any $j$ satisfying
 \begin{align*}
@@
 \begin{multline*}
-\COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon, R) \\
+\DHKMCOST(\DHKMALG,\calC_{\bslambda,\bsn,a,b},\varepsilon, R) \\
     \le 
@@
 \begin{multline*}
- \COST(\ALG,\calC_{\bslambda,\bsn,a,b},\varepsilon, R) \\
+ \DHKMCOST(\DHKMALG,\calC_{\bslambda,\bsn,a,b},\varepsilon, R) \\
    \le \min \left \{n_0 2^j , \ j \in \N_0 : 
@@
 For the illustrative choices of $(n_j)_{j \in \N_0}$ and $\bigl(\bsk_i \bigr)_{i \in \N}$ preceding Section \ref{DHKM:SecAdapAlgTrackDecay} this assumption holds.
-Let $\card(\cdot)$ denote the cardinality of a set.
-We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\card(\calJ) \le n_j$, then there exists some $l \le j+1$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
+Let $\DHKMcard(\cdot)$ denote the cardinality of a set.
+We assume that if $\calJ$ is an arbitrary set of wavenumbers with $\DHKMcard(\calJ) \le n_j$, then there exists some $l \le j+1$ for which $\calK_l \setminus \calJ$ retains some significant fraction of the original $\calK_l$ elements:
 \begin{equation} \label{DHKM:PropCond}
-     \inf_{j \in \N} \ \min_{\calJ \subset \bbK \, : \, \card(\calJ) \le n_j} \ \max_{0 \le l \le j+1} \frac{\card(\calK_l \setminus \calJ)}{\card(\calK_l)} \ge S_2 > 0.
+     \inf_{j \in \N} \ \min_{\calJ \subset \bbK \, : \, \DHKMcard(\calJ) \le n_j} \ \max_{0 \le l \le j+1} \frac{\DHKMcard(\calK_l \setminus \calJ)}{\DHKMcard(\calK_l)} \ge S_2 > 0.
 \end{equation}
@@
 
-Now let $\ALG'$ be an arbitrary algorithm in $\calA(\calC_{\boldsymbol{\lambda},\bsn,a,b})$, and suppose that $\ALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
+Now let $\DHKMALG'$ be an arbitrary algorithm in $\calA(\calC_{\boldsymbol{\lambda},\bsn,a,b})$, and suppose that $\DHKMALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
 Let $\tcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
@@
 \nonumber 
-\norm[\calG]{\SOL(f_{2j})} &= \sigma_j(f_{2j}) \tLambda_j = 
+\norm[\calG]{\DHKMSOL(f_{2j})} &= \sigma_j(f_{2j}) \tLambda_j = 
 c_2 b^{j} \tLambda_j, \qquad j \in \N_0, \\
-\norm[\calG]{\SOL(f_2)} & = \norm[\tau]{\bigl(c_2 b^{j} \tLambda_j \bigr)_{j \in \N_0}}
+\norm[\calG]{\DHKMSOL(f_2)} & = \norm[\tau]{\bigl(c_2 b^{j} \tLambda_j \bigr)_{j \in \N_0}}
 = \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}.
@@
 
-Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\ALG'(f_\pm,\varepsilon) = \ALG'(f_1,\varepsilon)$.
+Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\DHKMALG'(f_\pm,\varepsilon) = \DHKMALG'(f_1,\varepsilon)$.
 But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
@@
 \nonumber
-\varepsilon &\ge \max \bigl\{\norm[\calG]{\SOL(f_+) - \ALG'(f_+,\varepsilon)}, \norm[\calG]{\SOL(f_-) - \ALG'(f_-,\varepsilon)} \bigr\} \\
-\nonumber
-&\ge \frac 12 \bigl[\norm[\calG]{\SOL(f_+) - \ALG(f_1,\varepsilon)} + \norm[\calG]{\SOL(f_-) - \ALG'(f_1,\varepsilon)}  \bigr] \\
-\nonumber
-&\qquad \qquad \text{since } \ALG'(f_\pm,\varepsilon) = \ALG'(f_1,\varepsilon) \\
-\nonumber
-&\ge \frac 12 \norm[\calG]{\SOL(f_+) - \SOL(f_-)} \quad \text{by the triangle inequality}\\
-\nonumber
-&\ge \frac 12 \norm[\calG]{\SOL(f_+ - f_-)} \quad \text{since $\SOL$ is linear}\\
-&= \norm[\calG]{\SOL(f_2)} 
+\varepsilon &\ge \max \bigl\{\norm[\calG]{\DHKMSOL(f_+) - \DHKMALG'(f_+,\varepsilon)}, \norm[\calG]{\DHKMSOL(f_-) - \DHKMALG'(f_-,\varepsilon)} \bigr\} \\
+\nonumber
+&\ge \frac 12 \bigl[\norm[\calG]{\DHKMSOL(f_+) - \DHKMALG(f_1,\varepsilon)} + \norm[\calG]{\DHKMSOL(f_-) - \DHKMALG'(f_1,\varepsilon)}  \bigr] \\
+\nonumber
+&\qquad \qquad \text{since } \DHKMALG'(f_\pm,\varepsilon) = \DHKMALG'(f_1,\varepsilon) \\
+\nonumber
+&\ge \frac 12 \norm[\calG]{\DHKMSOL(f_+) - \DHKMSOL(f_-)} \quad \text{by the triangle inequality}\\
+\nonumber
+&\ge \frac 12 \norm[\calG]{\DHKMSOL(f_+ - f_-)} \quad \text{since $\DHKMSOL$ is linear}\\
+&= \norm[\calG]{\DHKMSOL(f_2)} 
 = \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}
@@
 
-Suppose that $\card(\calJ) = \COST(\ALG',f_{\pm},\varepsilon) \le n_{j^{\star}}$.
-Then by condition \eqref{DHKM:PropCond}, there exists an $l^\star \le j^\star+1$ where $\card(\tcalK_{l^\star}) \ge S_2 \card(\calK_{l^\star})$.
+Suppose that $\DHKMcard(\calJ) = \DHKMCOST(\DHKMALG',f_{\pm},\varepsilon) \le n_{j^{\star}}$.
+Then by condition \eqref{DHKM:PropCond}, there exists an $l^\star \le j^\star+1$ where $\DHKMcard(\tcalK_{l^\star}) \ge S_2 \DHKMcard(\calK_{l^\star})$.
 This implies a lower bound on $\tLambda_{l^\star}$.
-Let $m = n_{l^\star} - n_{l^\star-1} = \card(\calK_{l^\star})$.
-Then, $m_{\inc} = \lceil S_2 m \rceil \ge S_2 m$ is a lower bound on  $\card(\tcalK_{l^\star})$, and $m_{\out} = m - m_{\inc} \le (1 - S_2) m$ is an upper bound on $\card(\calK_{l^\star} \setminus \tcalK_{l^\star})$.
+Let $m = n_{l^\star} - n_{l^\star-1} = \DHKMcard(\calK_{l^\star})$.
+Then, $m_{\inc} = \lceil S_2 m \rceil \ge S_2 m$ is a lower bound on  $\DHKMcard(\tcalK_{l^\star})$, and $m_{\out} = m - m_{\inc} \le (1 - S_2) m$ is an upper bound on $\DHKMcard(\calK_{l^\star} \setminus \tcalK_{l^\star})$.
 Moreover,
@@
 \[
-\COST(\ALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\omega \varepsilon,R).
+\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\omega \varepsilon,R).
 \]
@@
 \begin{algorithm}
-	\caption{Adaptive $\ALG$ Based on Data-Inferred POSD Weights \label{DHKM:InfPilotConeAlg}} 
+	\caption{Adaptive $\DHKMALG$ Based on Data-Inferred POSD Weights \label{DHKM:InfPilotConeAlg}} 
 	\begin{algorithmic}
-	\PARAM the bases $\{u_{\bsk}\}_{\bsk \in \N_0^d}$ and $\{v_{\bsk}\}_{\bsk \in \N_0^d}$; candidate sets $\calW$ and $\calS$ for product and smoothness weights; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\APP$ satisfying \eqref{DHKM:Refined_APP_err}
+	\PARAM the bases $\{u_{\bsk}\}_{\bsk \in \N_0^d}$ and $\{v_{\bsk}\}_{\bsk \in \N_0^d}$; candidate sets $\calW$ and $\calS$ for product and smoothness weights; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
 		\INPUT a black-box function, $f$; an absolute error tolerance,
@@
 \State Compute data-driven POSD weight $\bar{\bslambda}$, by iteratively optimizing over $(\bsw, \bss) \in \calW \times \calS$ in \eqref{DHKM:eq:inf} until convergence
-\State Using these weights, $\bar{\bslambda}$, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\ALG(f,\varepsilon)$
-\RETURN $\ALG(f,\varepsilon)$
+\State Using these weights, $\bar{\bslambda}$, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\DHKMALG(f,\varepsilon)$
+\RETURN $\DHKMALG(f,\varepsilon)$
 \end{algorithmic}
@@
 For simplicity, only the case of $\rho = \infty$ and $\rho' = \tau = 1$ is considered in the following examples.
-Here, the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are the Chebyshev polynomials in Section \ref{DHKM:secexamp}, and the solution operator is $\SOL (f) = f$ (i.e., function approximation).
-We note that $\|f - \ALG(f,\varepsilon)\|_\infty \le \|f - \ALG(f,\varepsilon)\|_\calG$, so our error criterion \eqref{DHKM:err_crit} implies that $\|f - \ALG(f,\varepsilon)\|_\infty \le \varepsilon$.
+Here, the basis functions $(u_\bsk)_{\bsk \in \mathbb{N}_0^d}$ are the Chebyshev polynomials in Section \ref{DHKM:secexamp}, and the solution operator is $\DHKMSOL (f) = f$ (i.e., function approximation).
+We note that $\|f - \DHKMALG(f,\varepsilon)\|_\infty \le \|f - \DHKMALG(f,\varepsilon)\|_\calG$, so our error criterion \eqref{DHKM:err_crit} implies that $\|f - \DHKMALG(f,\varepsilon)\|_\infty \le \varepsilon$.
 
@@
 
-Figures \ref{fig:four} (a) and (b) display the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error to tolerance ratio, $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$, in $d=4$ and $d=7$ dimensions, respectively.
+Figures \ref{fig:four} (a) and (b) display the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error to tolerance ratio, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$, in $d=4$ and $d=7$ dimensions, respectively.
 Each data point corresponds to a different error tolerance $\varepsilon$.
-A ratio $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
-For $d=4$, $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$.
+A ratio $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
+For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\DHKMAPProx 0.1$ for $\varepsilon = 0.1$, then decreases to $\DHKMAPProx 0.014$ for $\varepsilon = 0.001$.
 This shows that our adaptive approximation algorithm works reasonably well.
@@
 \end{subfigure}
-\caption{Total required sample size as a function of error ratio $\|f - \ALG(f,\varepsilon)\|_{\infty}/\varepsilon$, with points colored by the absolute error tolerance level $\varepsilon$.}
+\caption{Total required sample size as a function of error ratio $\|f - \DHKMALG(f,\varepsilon)\|_{\infty}/\varepsilon$, with points colored by the absolute error tolerance level $\varepsilon$.}
 \label{fig:four}

### 2019-10-31 DingHickKritzMakRICAMChapVerF.tex
Updates from Overleaf

@@
 \DeclareMathOperator{\DHKMcard}{card}
-\newcommand{\DHKMdataN}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^n}
-\newcommand{\DHKMdataNj}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_j}}
-\newcommand{\DHKMdataNjd}{\bigl(\hf(\bsk_i)\bigr)_{i=1}^{n_{j^\dagger}}}
+\newcommand{\DHKMdataN}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^n}
+\newcommand{\DHKMdataNj}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^{n_j}}
+\newcommand{\DHKMdataNjd}{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=1}^{n_{j^\dagger}}}
 \newcommand{\DHKMERRN}{\DHKMERR\bigl(\DHKMdataN,n\bigr)}
@@
 \DeclareMathOperator{\DHKMCOST}{COST}
-\DeclareMathOperator{\COMP}{COMP}
-\newcommand{\hf}{\widehat{f}}
+\DeclareMathOperator{\DHKMCOMP}{COMP}
+\newcommand{\DHKMhf}{\widehat{f}}
 \newcommand{\hg}{\widehat{g}}
@@
 
-We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk}$, and we allow algorithms $\DHKMALG (f,\varepsilon)$ to use $n(f,\varepsilon)$ coefficients $\hf (\bsk)$ of this representation.
+We assume in this chapter that the functions $f\in\calF$ can be represented in terms of a basis representation as $f = \sum_{\bsk \in \mathbb{K}} \DHKMhf(\bsk) u_{\bsk}$, and we allow algorithms $\DHKMALG (f,\varepsilon)$ to use $n(f,\varepsilon)$ coefficients $\DHKMhf (\bsk)$ of this representation.
 That is,
@@
 \begin{equation*} %\label{DHKM:algform}
-  \DHKMALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\hf(\bsk_i) v_{\bsk_i} \qquad \forall f \in \calF, \ n(f,\varepsilon) \in \N,
-\end{equation*}
-where an oracle provides $\hf(\bsk_1),\ldots,\hf (\bsk_{n(f,\varepsilon)})$ 
+  \DHKMALG(f,\varepsilon) = \sum_{i=1}^{n(f,\varepsilon)}\DHKMhf(\bsk_i) v_{\bsk_i} \qquad \forall f \in \calF, \ n(f,\varepsilon) \in \N,
+\end{equation*}
+where an oracle provides $\DHKMhf(\bsk_1),\ldots,\DHKMhf (\bsk_{n(f,\varepsilon)})$ 
 with $n(f,\varepsilon)$ being chosen based on a stopping rule. 
@@
 \begin{equation*}
-    \COMP(\calC, \varepsilon,R) := \min_{\DHKMALG \in \calA(\calC)} \DHKMCOST(\DHKMALG, \calC, \varepsilon,R) .
+    \DHKMCOMP(\calC, \varepsilon,R) := \min_{\DHKMALG \in \calA(\calC)} \DHKMCOST(\DHKMALG, \calC, \varepsilon,R) .
 \end{equation*}
@@
 \begin{multline} \label{DHKM:EssentialOpt}
-    \DHKMCOST(\DHKMALG, \calC, \varepsilon,R) \le \COMP(\calC, \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+    \DHKMCOST(\DHKMALG, \calC, \varepsilon,R) \le \DHKMCOMP(\calC, \omega \varepsilon,R) \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
 \end{multline}
@@
 $$
-  \norm[\calF]{f}\le h (\hf(\bsk_1),\ldots,\hf (\bsk_{n_1}))
+  \norm[\calF]{f}\le h (\DHKMhf(\bsk_1),\ldots,\DHKMhf (\bsk_{n_1}))
 $$
@@
 \begin{gather*}
-    \calF := \left \{f = \sum_{\bsk \in \mathbb{K}} \hf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \rho \le \infty,
+    \calF := \left \{f = \sum_{\bsk \in \mathbb{K}} \DHKMhf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \rho \le \infty,
 \end{gather*}
@@
 The $\lambda_{\bsk}$ represent the importance of the series coefficients of the input function.
-The larger $\lambda_{\bsk}$ is, the more important $\hf(\bsk)$ is.
+The larger $\lambda_{\bsk}$ is, the more important $\DHKMhf(\bsk)$ is.
 The $\lambda_{\bsk}$ are assumed to have a known order:
@@
 Let $\Lambda :=  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$ be the norm of a subset of the weights.
-Then the following are true for $f = \sum_{\bsk \in \calK} \hf(\bsk) u_{\bsk}$:
+Then the following are true for $f = \sum_{\bsk \in \calK} \DHKMhf(\bsk) u_{\bsk}$:
 \begin{equation}
 \label{DHKM:SOL_ineq}
-    \norm[\calG]{\DHKMSOL(f)} = \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK}} \le \norm[\calF]{f} \, \Lambda,
+    \norm[\calG]{\DHKMSOL(f)} = \norm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK}} \le \norm[\calF]{f} \, \Lambda,
     \end{equation}
@@
     \label{DHKM:SOL_tight_ineq}
-    \bigabs{\hf(\bsk)} = \begin{cases}
+    \bigabs{\DHKMhf(\bsk)} = \begin{cases}
     \displaystyle 
@@
     \norm[\calG]{\DHKMSOL(f)}  
-    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \hf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \hf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\hf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
-    \nonumber
-    & \le \biggnorm[\rho]{\biggl(  \frac{\hf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \norm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
+    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \DHKMhf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \DHKMhf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
+    \nonumber
+    & \le \biggnorm[\rho]{\biggl(  \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \norm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
 \end{align}
-Substituting the formula for $\bigabs{\hf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into equation \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
+Substituting the formula for $\bigabs{\DHKMhf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into equation \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
 \begin{equation*}
@@
     \norm[\calF]{f}  
-    = \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
+    = \norm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
     = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\Lambda^{\rho'/\rho}} 
@@
 \label{DHKM:IllExWts}
-    \norm[\calF]{f} := \norm[2]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
+    \norm[\calF]{f} := \norm[2]{\left(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
 \end{equation}
@@
 \begin{equation*} %\label{DHKM:Ex_APP_def}
-   \DHKMAPP(f,n) := \sum_{i=1}^n \hf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N.
+   \DHKMAPP(f,n) := \sum_{i=1}^n \DHKMhf(\bsk_i) u_{\bsk_i} \qquad \forall f \in \calF, \ n \in \N.
 \end{equation*}
@@
 \begin{equation*}
-    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[2]{\bigl(\hf(\bsk_i) \bigr)_{i=n+1}^{\infty}}.
+    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[2]{\bigl(\DHKMhf(\bsk_i) \bigr)_{i=n+1}^{\infty}}.
 \end{equation*}
@@
 \begin{equation} \label{DHKM:APP_def}
-    \DHKMAPP : \calF \times \N_0 \to \calG, \quad  \DHKMAPP(f,0) = 0, \ \ \DHKMAPP(f,n) := \sum_{i=1}^n \hf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
+    \DHKMAPP : \calF \times \N_0 \to \calG, \quad  \DHKMAPP(f,0) = 0, \ \ \DHKMAPP(f,n) := \sum_{i=1}^n \DHKMhf(\bsk_i) v_{\bsk_i} \ \forall n \in \N.
 \end{equation}
@@
 \begin{equation} \label{DHKM:APP_Err_Coef}
-    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[\tau]{\bigl(\hf(\bsk_i)\bigr)_{i=n+1}^\infty}.
+    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[\tau]{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=n+1}^\infty}.
 \end{equation}
@@
 \begin{gather} \label{DHKM:Refined_APP_err}
-    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
+    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
     \bignorm[\rho']{\bslambda^{(n+1)}}, \\
@@
 \nonumber
-    \hf(\bsk'_1) = \cdots = \hf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ 
+    \DHKMhf(\bsk'_1) = \cdots = \DHKMhf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ 
     \norm[\calG]{\DHKMSOL(f)} =  R \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.  \label{DHKM:FoolFun}
@@
 \begin{multline*}
-\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') \le \COMP(\calB_R,\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty), 
+\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') \le \DHKMCOMP(\calB_R,\omega \varepsilon ,R') \\ \forall \, \varepsilon \in (0, \varepsilon_{\max}], \ R’ \in  [ R_{\min} , R], \ R \in [R_{\min}, \infty),
 \end{multline*}
@@
 \\
-& \le \COMP(\calB_{R'},\omega \varepsilon, R') \le  \COMP(\calB_{R},\omega \varepsilon, R').
+& \le \DHKMCOMP(\calB_{R'},\omega \varepsilon, R') \le  \DHKMCOMP(\calB_{R},\omega \varepsilon, R').
 \end{align*}
@@
 For Algorithm \ref{DHKM:BallAlg}, the information cost, $\DHKMCOST(\DHKMALG,\calB_R,\varepsilon, R)$, depends on the decay rate of the tail norm of the $\lambda_{\bsk_i}$.
-This decay may be algebraic or exponential and also determines the problem complexity, $\COMP(\calB_R,\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
+This decay may be algebraic or exponential and also determines the problem complexity, $\DHKMCOMP(\calB_R,\varepsilon, R)$, as a function of the error tolerance, $\varepsilon$.
 
@@
 \begin{equation*}
-    \COMP(\calC,\varepsilon) : = \sup_{R > 0} \COMP(\calC,\varepsilon, R) < \infty.
+    \DHKMCOMP(\calC,\varepsilon) : = \sup_{R > 0} \DHKMCOMP(\calC,\varepsilon, R) < \infty.
 \end{equation*}
@@
 
-Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\hf(\bsk_1), \ldots, \hf(\bsk_{n_1})\}$. It is given by
+Accordingly, we now define the cone of functions whose norm can be bounded well in terms of a pilot sample, $\{\DHKMhf(\bsk_1), \ldots, \DHKMhf(\bsk_{n_1})\}$. It is given by
 \begin{equation} \label{DHKM:pilot_cone}
-    \calC_{\boldsymbol{\lambda},n_1,A} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
+    \calC_{\boldsymbol{\lambda},n_1,A} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
 \end{equation}
@@
 \begin{align*}
-     \MoveEqLeft{\norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
-     & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+     \MoveEqLeft{\norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
+     & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
     \right]^{1/\rho} \qquad \forall f \in \calF \\
-    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
     \right]^{1/\rho} \quad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A}.
@@
     : =  
-    \left[ A^\rho \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho} 
+    \left[ A^\rho \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho}
     \, \bignorm[\rho']{\bslambda^{(n+1)}} , 
@@
 \begin{multline} \label{DHKM:PilotConeAlg_comp}
-        \COMP(\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bslambda^{(n+1)}} \,
+        \DHKMCOMP(\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bslambda^{(n+1)}} \,
     \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
@@
      & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
+     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
      \bignorm[\rho']{\bslambda^{(n+1)}}
@@
 \end{align*}
-since $\bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \bignorm[\rho]{\bigl( \hf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
-Moreover, this inequality is tight for some $f \in \calC_{\boldsymbol{\lambda},n_1,A} \cap \calB_{R}$, namely, those certain $f$ for which $\hf(\bsk_i) = 0$ for $i > n_1$.
+since $\bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
+Moreover, this inequality is tight for some $f \in \calC_{\boldsymbol{\lambda},n_1,A} \cap \calB_{R}$, namely, those certain $f$ for which $\DHKMhf(\bsk_i) = 0$ for $i > n_1$.
 This completes the proof of \eqref{DHKM:PilotConeAlg_cost}.
@@
 \begin{equation*}
-    \bigabs{\hf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
+    \bigabs{\DHKMhf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
     0, & \bsk \notin \calK_1,
@@
 \end{equation*}
-Suppose that $\DHKMALG'(f_1,\varepsilon)$ samples the series coefficients $\hf_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
+Suppose that $\DHKMALG'(f_1,\varepsilon)$ samples the series coefficients $\DHKMhf_1(\bsk)$ for $\bsk \in \calJ$, and let $n$ denote the cardinality of $\calJ$.
 
@@
 \nonumber
-    \bigabs{\hf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
+    \bigabs{\DHKMhf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
     0, & \bsk \in \calJ, 
@@
     \nonumber
-    \norm[\rho]{\left( \frac{\hf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
-    & = \norm[\rho]{\left( \frac{\hf_1(\bsk_i) \pm \hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
-    \nonumber
-    & \ge \norm[\rho]{\left( \frac{\hf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\hf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \norm[\rho]{\left( \frac{\DHKMhf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
+    & = \norm[\rho]{\left( \frac{\DHKMhf_1(\bsk_i) \pm \DHKMhf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \nonumber
+    & \ge \norm[\rho]{\left( \frac{\DHKMhf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\DHKMhf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
     \nonumber
@@
 This inequality then implies lower complexity bound \eqref{DHKM:PilotConeAlg_comp}.
-Because $\lim_{R \to \infty} \COMP(\calC_{\boldsymbol{\lambda},n_1,A}, \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\calC_{\boldsymbol{\lambda},n_1,A})$ contains only adaptive algorithms.
+Because $\lim_{R \to \infty} \DHKMCOMP(\calC_{\boldsymbol{\lambda},n_1,A}, \varepsilon,R) = \infty$  it follows from Lemma \ref{DHKM:NoNonAdpatLem} that $\calA(\calC_{\boldsymbol{\lambda},n_1,A})$ contains only adaptive algorithms.
 
@@
 \[
-\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \le \COMP(\calC_{\boldsymbol{\lambda},n_1,A},\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
+\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \le \DHKMCOMP(\calC_{\boldsymbol{\lambda},n_1,A},\omega \varepsilon,R) \qquad \text{for } \omega = \frac{1-1/A}{2(A^\rho -1)^{1/\rho}}.
 \]
@@
 \begin{equation} \label{DHKM:PilotConeNecessary}
-    \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i =1}^{n}} \le A
-    \norm[\rho]{\left( \frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
+    \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i =1}^{n}} \le A
+    \norm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
 \end{equation}
@@
 \begin{multline} \label{DHKM:altconedef}
-    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\hf(\bsk_i)\omega_{i}}{\lambda_{\bsk_i}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
+    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)\omega_{i}}{\lambda_{\bsk_i}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
 \end{multline}
@@
 \begin{equation*}
-    \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
-     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\hf(\bsk_i)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
+    \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
+     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
      \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
@@
 \begin{align*}
-    \norm[\calF']{f}^\rho- \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho 
-	& = \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho 
-     \le \omega_{n_1+1}^\rho \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
-     & = \omega_{n_1+1}^\rho \left[ \norm[\calF]{f}^\rho - \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
-     & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \norm[\calF']{f}^\rho - \omega_1^{-\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].
+    \norm[\calF']{f}^\rho- \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho 
+	& = \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho 
+     \le \omega_{n_1+1}^\rho \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
+     & = \omega_{n_1+1}^\rho \left[ \norm[\calF]{f}^\rho - \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
+     & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \norm[\calF']{f}^\rho - \omega_1^{-\rho} \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].
 \end{align*}
@@
 \begin{align*}
-\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho, \\
-	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\hf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
+\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho, \\
+	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
 \end{align*}
@@
 then $\norm[p\eta]{\bslambda} < \infty$ for all $\eta > 1$.
-Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calB_R,\varepsilon,R')$ and $\COMP(\calC_{\bslambda,n_1,A},\varepsilon,R)$.
+Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\DHKMCOMP(\calB_R,\varepsilon,R')$ and $\DHKMCOMP(\calC_{\bslambda,n_1,A},\varepsilon,R)$.
 \end{theorem}
@@
 Furthermore, these information costs cannot grow any slower than $\calO(\varepsilon^{-1/r})$ for $\varepsilon \downarrow 0$.
-Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\COMP(\calB_R,\varepsilon,R')$ and $\COMP(\calC_{\bslambda,n_1,A},\varepsilon,R)$ for the illustrative example in Section \ref{DHKM:secexamp}.
+Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\DHKMCOMP(\calB_R,\varepsilon,R')$ and $\DHKMCOMP(\calC_{\bslambda,n_1,A},\varepsilon,R)$ for the illustrative example in Section \ref{DHKM:secexamp}.
 \end{corollary}
@@
 
-Besides understanding the dependence of $\COMP(\calC, \varepsilon,R)$ on $\varepsilon$, we also want to understand how $\COMP(\calC, \varepsilon,R)$ depends on the dimension of the domain of the input function.
+Besides understanding the dependence of $\DHKMCOMP(\calC, \varepsilon,R)$ on $\varepsilon$, we also want to understand how $\DHKMCOMP(\calC, \varepsilon,R)$ depends on the dimension of the domain of the input function.
 Suppose that $f: \Omega^d \to \R$, for some $\Omega \subseteq \R$, and let $\calF_d$ denote the dependence of the input space on the dimension $d$.
@@
 Thus, for the sake of brevity, we write $\calC_d$ instead of $\calC_{\bslambda,n_1,A}$ in this section.
-Also, $\DHKMSOL$, $\DHKMAPP$, $\DHKMCOST$, and $\COMP$ depend implicitly on the dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
+Also, $\DHKMSOL$, $\DHKMAPP$, $\DHKMCOST$, and $\DHKMCOMP$ depend implicitly on the dimension, and this dependence is sometimes indicated explicitly by the subscript $d$.
 
@@
 
-Different dependencies of $\COMP(\calC_d, \varepsilon,R)$ on the dimension $d$ and the error tolerance $\varepsilon$ are formalized as different notions of tractability. Since 
+Different dependencies of $\DHKMCOMP(\calC_d, \varepsilon,R)$ on the dimension $d$ and the error tolerance $\varepsilon$ are formalized as different notions of tractability. Since 
 the complexity is defined in terms of the best algorithm, tractability is a property that is inherent to the problem, not to a particular algorithm. 
@@
 $$   
-\COMP(\calC_d, \varepsilon,R)\le C\,R^{\widetilde{p}}\,\varepsilon^{-\widetilde{p}} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
+\DHKMCOMP(\calC_d, \varepsilon,R)\le C\,R^{\widetilde{p}}\,\varepsilon^{-\widetilde{p}} \qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).
 $$   
@@
 $$   
-\COMP(\calC_d, \varepsilon,R)\le C\,d^{\,q}\,R^{\widetilde{p}}\,   
+\DHKMCOMP(\calC_d, \varepsilon,R)\le C\,d^{\,q}\,R^{\widetilde{p}}\,   
 \varepsilon^{-{\widetilde{p}}}\qquad \forall d\in\NN,\ \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty).  
@@
 \lim_{d+R\,\varepsilon^{-1}\to\infty}\   
-\frac{\log\, \COMP(\calC_d, \varepsilon,R)}   
+\frac{\log\, \DHKMCOMP(\calC_d, \varepsilon,R)}   
 {d+R\,\varepsilon^{-1}}\,=\,0.   
@@
 \begin{align*}
-    \MoveEqLeft{\COMP(\calB_{R},\varepsilon,R)} 
+    \MoveEqLeft{\DHKMCOMP(\calB_{R},\varepsilon,R)} 
   \le \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \norm[p]{\bsw}^p  \right) \right \rceil .
@@
 If $p^\dagger$ is the infimum of the $p$ for which $\norm[p]{\bsw}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $\widetilde{p}_* = \max(1/r,p^\dagger)$.
-On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\COMP(\calB_{R},\varepsilon,R) \ge 2^d$, and the problem is not tractable.\\
+On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\DHKMCOMP(\calB_{R},\varepsilon,R) \ge 2^d$, and the problem is not tractable.\\
 
@@
 % \[
-% n_{\COMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+% n_{\DHKMCOMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
 %     \le \delta \right \} \qquad \forall \delta > 0.
@@
 \[
-n_{\COMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bslambda^{(n+1)}_d} \,
+n_{\DHKMCOMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bslambda^{(n+1)}_d} \,
     \le \delta \right \} \qquad \forall \delta > 0,
@@
 \begin{multline*}
-     \COMP(\calC_d,\omega_{\textup{lo}} \varepsilon,R) \le n_{\COMP}(\varepsilon/R,d) \le 
-        \COMP(\calC_d,\omega_{\textup{hi}} \varepsilon,R)  \\
+     \DHKMCOMP(\calC_d,\omega_{\textup{lo}} \varepsilon,R) \le n_{\DHKMCOMP}(\varepsilon/R,d) \le 
+        \DHKMCOMP(\calC_d,\omega_{\textup{hi}} \varepsilon,R)  \\
         \forall \varepsilon \in (0, \varepsilon_{\max}], \ R \in [R_{\min}, \infty),
@@
 where the positive constants $\omega_{\textup{lo}}$ and $\omega_{\textup{hi}}$  depend on $A$, but do not depend on $d$, $\varepsilon$, or $R$.
-From the equation above, it is clear that tractability depends on the behavior of $n_{\COMP}(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity.
+From the equation above, it is clear that tractability depends on the behavior of $n_{\DHKMCOMP}(\varepsilon/R,d)$ as $R/\varepsilon$ and $d$ tend to infinity.
 We would like to study under which conditions we obtain the various tractability notions defined above.
@@
 \[
-n_{\COMP}(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
+n_{\DHKMCOMP}(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,
     \le \varepsilon/R \right \}.
@@
 If $\widetilde{\varepsilon}:=\sqrt{\varepsilon/R}$, then
-$n_{\COMP}(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
+$n_{\DHKMCOMP}(\varepsilon/R,d)=\min \left \{n\ge 0\colon \lambda_{d,\bsk_{n+1}} \,\le \widetilde{\varepsilon}^{\,2} \right \}$.
 The latter expression is well studied in the context of tractability of linear problems in the worst-case setting defined on unit balls of certain spaces, and if and only if conditions on the $\lambda_{d,\bsk_i}$ for various tractability notions are known.
@@
     \nonumber 
-    n_{\COMP}(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
+    n_{\DHKMCOMP}(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
 \bignorm[\rho']{\bslambda_d^{(n+1)}}^{\rho'}\,
@@
 
-From error bound \eqref{DHKM:APP_Err_Coef} it follows that the faster the $\hf(\bsk_i)$ decay, the faster $\DHKMAPP(f,n)$ converges to the solution.
-Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\hf(\bsk_i)$ as $i \to \infty$.
+From error bound \eqref{DHKM:APP_Err_Coef} it follows that the faster the $\DHKMhf(\bsk_i)$ decay, the faster $\DHKMAPP(f,n)$ converges to the solution.
+Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\DHKMhf(\bsk_i)$ as $i \to \infty$.
 It simply bounds $\norm[\calF]{f}$ based on a pilot sample.
-The algorithm presented in this section tracks the rate of decay of the $\hf(\bsk_i)$ and terminates sooner if the $\hf(\bsk_i)$ decay more quickly.
+The algorithm presented in this section tracks the rate of decay of the $\DHKMhf(\bsk_i)$ and terminates sooner if the $\DHKMhf(\bsk_i)$ decay more quickly.
 Similar algorithms for quasi-Monte Carlo integration are developed in \cite{HicJim16a}, \cite{JimHic16a}, and \cite{HicEtal17a}.
@@
 \begin{equation} \label{DHKM:SigmaDef}
-\sigma_j (f):=\norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} \qquad \text{for } j \in \N.
+\sigma_j (f):=\norm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} \qquad \text{for } j \in \N.
 \end{equation}
@@
 
-As stated above, we would like to keep track of the rate of decay of the $\hf(\bsk_i)$. Hence, for this section, we define the cone of input functions by
+As stated above, we would like to keep track of the rate of decay of the $\DHKMhf(\bsk_i)$. Hence, for this section, we define the cone of input functions by
 \begin{equation} \label{DHKM:TrackConeDef}
@@
 \begin{equation} \label{DHKM:LambdaDef}
-    \norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_j}} \le \sigma_j(f) \Lambda_j, \qquad \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
+    \norm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK_j}} \le \sigma_j(f) \Lambda_j, \qquad \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
 \end{equation}
@@
 \begin{align*}
-    \norm[\calF]{f} & = \norm[\rho]{\Biggl(\,\norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
+    \norm[\calF]{f} & = \norm[\rho]{\Biggl(\,\norm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
     & \le \bignorm[\rho]{\bigl(\sigma_1(f), ab \sigma_1(f), ab^2 \sigma_1(f), \ldots \bigr)} \\
-    & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \norm[\rho]{\biggl(\frac{\hf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
+    & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \norm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
 \end{align*}
@@
 \MoveEqLeft{\norm[\calG]{\DHKMSOL(f)-\DHKMAPP(f,n_j)}} \\
-\nonumber &= \norm[\tau]{\left(\hf(\bsk_i) \right)_{i = n_j+1}^\infty}
-= \norm[\tau]{ \left(\norm[\tau]{\bigl(\hf(\bsk) \bigr)_{\bsk \in \calK_l}} \right)_{l=j+1}^\infty}
+\nonumber &= \norm[\tau]{\left(\DHKMhf(\bsk_i) \right)_{i = n_j+1}^\infty}
+= \norm[\tau]{ \left(\norm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK_l}} \right)_{l=j+1}^\infty}
 \\
@@
 These assumptions accommodate both the cases where the approximation converges algebraically and exponentially.
-To illustrate the algebraic case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \Theta(i^{-r_\Delta})$ for some positive $r_\Delta > 1/\rho$.
+To illustrate the algebraic case, suppose that $\DHKMhf(\bsk_i)/\lambda_{\bsk_i} = \Theta(i^{-r_\Delta})$ for some positive $r_\Delta > 1/\rho$.
 Here $r_\Delta$ reflects the smoothness of the input function.
@@
 \begin{align*}
-    \sigma_j(f) &= \left[ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
+    \sigma_j(f) &= \left[ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} \biggabs{\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
     = \Theta\left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
@@
 
-To illustrate the exponential case, suppose that $\hf(\bsk_i)/\lambda_{\bsk_i} = \Theta(\E^{-r_\Delta i})$.
+To illustrate the exponential case, suppose that $\DHKMhf(\bsk_i)/\lambda_{\bsk_i} = \Theta(\E^{-r_\Delta i})$.
 For this exponential case one would normally define $\calC$ in terms of an arithmetic sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 + j q$, where $q$ is a positive integer.
@@
 \begin{align*}
-    \sigma_j(f) &= \left[ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \biggabs{\frac{\hf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
+    \sigma_j(f) &= \left[ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \biggabs{\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
     = \Theta \left( \left [ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
@@
 \begin{align*}
-R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\hf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
+R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
  \ge \norm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
@@
 
-Although Algorithm \ref{DHKM:TrackConeAlg} tracks the decay rate of the $\hf(\bsk_i)$, the information cost bound and complexity bound in the theorem above do not reflect different decay rates of the $\hf(\bsk_i)$.
+Although Algorithm \ref{DHKM:TrackConeAlg} tracks the decay rate of the $\DHKMhf(\bsk_i)$, the information cost bound and complexity bound in the theorem above do not reflect different decay rates of the $\DHKMhf(\bsk_i)$.
 That is a subject for future investigation.
@@
  %\label{compbdA}
-&\COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) > n_{j^\ddagger}, 
+&\DHKMCOMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) > n_{j^\ddagger}, 
 \intertext{where}
@@
 We proceed by carefully constructing the test input functions, $f_1$ and $f_{\pm} = f_1 \pm f_2$, lying in $\calC_{\boldsymbol{\lambda},\bsn,a,b}\cap \calB_{R}$, which yield the same approximate solution but different true solutions.
-This leads to a lower bound on $\COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R)$.
+This leads to a lower bound on $\DHKMCOMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R)$.
 The proof is provided for $\rho' < \infty$.
@@
 f_1 &= f_{10} + f_{11} +  \cdots, \qquad
-\hf_{1j}(\bsk) := \begin{cases}
+\DHKMhf_{1j}(\bsk) := \begin{cases}
 \displaystyle
@@
 \nonumber
-\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\hf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
+\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\DHKMhf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
 = c_1 b^j, \qquad j \in \N_0,\\
@@
 \nonumber
-f_2 &= f_{20} + f_{21} +  \cdots, \qquad \hf_{2j}(\bsk) := \begin{cases}
+f_2 &= f_{20} + f_{21} +  \cdots, \qquad \DHKMhf_{2j}(\bsk) := \begin{cases}
 \displaystyle
@@
 \nonumber
-\sigma_j(f_2) & = \norm[\rho]{\biggl(\frac{\hf_{2j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \tcalK_j}} 
+\sigma_j(f_2) & = \norm[\rho]{\biggl(\frac{\DHKMhf_{2j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \tcalK_j}} 
 = \begin{cases} c_2 b^j, & \tcalK_j \ne \emptyset, \\
@@
 
-Since $\hf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\DHKMALG'(f_\pm,\varepsilon) = \DHKMALG'(f_1,\varepsilon)$.
+Since $\DHKMhf_2(\bsk) = 0$ for $\bsk \in \calJ$, it follows that $\DHKMALG'(f_\pm,\varepsilon) = \DHKMALG'(f_1,\varepsilon)$.
 But, even though the two test functions $f_\pm$ lead to the same approximate solution, they have different true solutions.
@@
 \[
-\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \COMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\omega \varepsilon,R).
+\DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},\bsn,a,b},\varepsilon,R) \le n_{j^\dagger(\varepsilon)} < n_{j^\ddagger(\omega \varepsilon)} < \DHKMCOMP(\calC_{\boldsymbol{\lambda},\bsn,a,b},\omega \varepsilon,R).
 \]
@@
 This parametrization is motivated by several guiding principles from the experimental design literature \citep{WuHam2009}, which are briefly described below.
-In statistical parlance, the terms $\hf(\bsk) u_{\bsk}$ are effects.
+In statistical parlance, the terms $\DHKMhf(\bsk) u_{\bsk}$ are effects.
 \begin{itemize}
@@
 Intuitively, the SPOD weights quantify the importance of each \textit{subspace} (indexed by $\fraku$), under a common smoothness structure among subspaces (for further details on SPOD weights, we refer the reader to \cite{Dea2014}).
-In contrast, the proposed POSD weights in \eqref{DHKM:posdeq} instead quantify the importance of each \textit{Fourier series coefficient} $\hf(\bsk)$ (indexed by $\bsk$), under a common smoothness structure among coefficients.
+In contrast, the proposed POSD weights in \eqref{DHKM:posdeq} instead quantify the importance of each \textit{Fourier series coefficient} $\DHKMhf(\bsk)$ (indexed by $\bsk$), under a common smoothness structure among coefficients.
 
@@
 \begin{equation*}
-    \fapp = \sum_{\bsk \in \bar{\calK}} \hf(\bsk) u_{\bsk}.
+    \fapp = \sum_{\bsk \in \bar{\calK}} \DHKMhf(\bsk) u_{\bsk}.
 \end{equation*}
@@
 \bar{\bslambda} = \bslambda(\bar{\bsw}, \bar{\bss}, \bsGamma), \\
-\text{where } (\bar{\bsw}, \bar{\bss} ) = \min \left\{ \argmin_{(\bsw,\bss) \in \calW \times \calS} \left\|\left( \frac{\hf(\bsk)}{\lambda_{\bsk}(\bsw,\bss,\bsGamma)} \right)_{\bsk \in \bar{\calK}}\right\|_{\rho} \right \}.
+\text{where } (\bar{\bsw}, \bar{\bss} ) = \min \left\{ \argmin_{(\bsw,\bss) \in \calW \times \calS} \left\|\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}(\bsw,\bss,\bsGamma)} \right)_{\bsk \in \bar{\calK}}\right\|_{\rho} \right \}.
 \label{DHKM:eq:inf}
@@
 \State  Define the initial set of wavenumbers $\bcalK$ defined in \eqref{DHKM:barKdef}
-\State Evaluate initial sample $\bigl\{\hf(\bsk)\bigr\}_{\bsk \in \bcalK}$
+\State Evaluate initial sample $\bigl\{\DHKMhf(\bsk)\bigr\}_{\bsk \in \bcalK}$
 \State Compute data-driven POSD weight $\bar{\bslambda}$, by iteratively optimizing over $(\bsw, \bss) \in \calW \times \calS$ in \eqref{DHKM:eq:inf} until convergence

### 2019-10-31 DingHickKritzMakRICAMChapVerF.tex
Updates from Overleaf

@@
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\DHKMALGnewcommand\DHKMALGorithmicparam{\textbf{Parameters:}}
-\DHKMALGnewcommand\PARAM{\item[\DHKMALGorithmicparam]}
-\DHKMALGnewcommand\DHKMALGorithmicinput{\textbf{Input:}}
-\DHKMALGnewcommand\INPUT{\item[\DHKMALGorithmicinput]}
-%\DHKMALGnewcommand\STATE{\item}
-\DHKMALGnewcommand\RETURN{\State \textbf{Return }}
+\algnewcommand\algorithmicparam{\textbf{Parameters:}}
+\algnewcommand\PARAM{\item[\algorithmicparam]}
+\algnewcommand\algorithmicinput{\textbf{Input:}}
+\algnewcommand\INPUT{\item[\algorithmicinput]}
+%\algnewcommand\STATE{\item}
+\algnewcommand\RETURN{\State \textbf{Return }}
 
@@
 \newcommand{\DHKMhf}{\widehat{f}}
-\newcommand{\hg}{\widehat{g}}
-\newcommand{\tu}{\Tilde{u}}
-\newcommand{\tv}{\Tilde{v}}
-\newcommand{\tcalJ}{\widetilde{\calJ}}
-\newcommand{\tcalK}{\widetilde{\calK}}
-\newcommand{\tlambda}{\Tilde{\lambda}}
-\newcommand{\tbbK}{\widetilde{\bbK}}
-\newcommand{\lo}{\textup{lo}}
-\newcommand{\up}{\textup{up}}
-\newcommand{\inc}{\textup{in}}
-\newcommand{\out}{\textup{out}}
-\newcommand{\E}{\textup{e}}
-\def\abs#1{\ensuremath{\left \lvert #1 \right \rvert}}
-\newcommand{\normabs}[1]{\ensuremath{\lvert #1 \rvert}}
-\newcommand{\bigabs}[1]{\ensuremath{\bigl \lvert #1 \bigr \rvert}}
-\newcommand{\Bigabs}[1]{\ensuremath{\Bigl \lvert #1 \Bigr \rvert}}
-\newcommand{\biggabs}[1]{\ensuremath{\biggl \lvert #1 \biggr \rvert}}
-\newcommand{\Biggabs}[1]{\ensuremath{\Biggl \lvert #1 \Biggr \rvert}}
+\newcommand{\DHKMhg}{\widehat{g}}
+\newcommand{\DHKMtu}{\Tilde{u}}
+\newcommand{\DHKMtcalK}{\widetilde{\calK}}
+\newcommand{\DHKMlo}{\textup{lo}}
+\newcommand{\DHKMup}{\textup{up}}
+\newcommand{\DHKMinc}{\textup{in}}
+\newcommand{\DHKMout}{\textup{out}}
+\newcommand{\DHKME}{\textup{e}}
+\newcommand{\DHKMbigabs}[1]{\ensuremath{\bigl \lvert #1 \bigr \rvert}}
+\newcommand{\DHKMbiggabs}[1]{\ensuremath{\biggl \lvert #1 \biggr \rvert}}
 \newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
@@
 \begin{gather*}
-    \calG := \left \{g = \sum_{\bsk \in \mathbb{K}} \hg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \hg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \tau \le \rho.
+    \calG := \left \{g = \sum_{\bsk \in \mathbb{K}} \DHKMhg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \DHKMhg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \tau \le \rho.
 \end{gather*}
@@
     \label{DHKM:SOL_tight_ineq}
-    \bigabs{\DHKMhf(\bsk)} = \begin{cases}
+    \DHKMbigabs{\DHKMhf(\bsk)} = \begin{cases}
     \displaystyle 
@@
 \end{align}
-Substituting the formula for $\bigabs{\DHKMhf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into equation \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
+Substituting the formula for $\DHKMbigabs{\DHKMhf(\bsk)}$ in \eqref{DHKM:SOL_tight_ineq} into equation \eqref{DHKM:SOL_A} and applying the relationship between $\rho$, $\rho'$, and $\tau$ yields
 \begin{equation*}
@@
 	\qquad \bsk = (k_1, \ldots, k_d) \in \N_0^d,\\
-    u_\bsk & := \prod_{\ell =1}^d \tu_{k_\ell} , 
-    \qquad \tu_{k}(x) := \cos( k \cos^{-1}(x)) \quad \forall k \in \N_0.
+    u_\bsk & := \prod_{\ell =1}^d \DHKMtu_{k_\ell} , 
+    \qquad \DHKMtu_{k}(x) := \cos( k \cos^{-1}(x)) \quad \forall k \in \N_0.
 	\end{align*}
@@
 \begin{equation*}
-      \norm[\calG]{\sum_{\bsk \in \N_0^d} \hg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\hg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
+      \norm[\calG]{\sum_{\bsk \in \N_0^d} \DHKMhg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\DHKMhg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
 \end{equation*}
@@
 \begin{equation*}
-    \bigabs{\DHKMhf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
+    \DHKMbigabs{\DHKMhf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
     0, & \bsk \notin \calK_1,
@@
 \nonumber
-    \bigabs{\DHKMhf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
+    \DHKMbigabs{\DHKMhf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
     0, & \bsk \in \calJ, 
@@
 \begin{align*}
-    \sigma_j(f) &= \left[ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} \biggabs{\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
+    \sigma_j(f) &= \left[ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} \DHKMbiggabs{\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
     = \Theta\left( \left [ \sum_{i=n_0 2^{j-1} + 1}^{n_0 2^j} i^{-\rho r_\Delta} \right]^{1/\rho} \right) \\
@@
 \begin{equation*}
-    C_{\lo} 2^{-j(r_\Delta-1/\rho)} \le \sigma_j(f) \le C_{\up} 2^{-j(r_\Delta-1/\rho)} 
-\end{equation*}
-for some constants $C_{\lo}$ and $C_{\up}$.
+    C_{\DHKMlo} 2^{-j(r_\Delta-1/\rho)} \le \sigma_j(f) \le C_{\DHKMup} 2^{-j(r_\Delta-1/\rho)} 
+\end{equation*}
+for some constants $C_{\DHKMlo}$ and $C_{\DHKMup}$.
 By reasonable we mean that the values of $\sigma_j(f)$ would not drop precipitously and then rise again as $j$ increases.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ to include such functions.
-Note that only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
-
-To illustrate the exponential case, suppose that $\DHKMhf(\bsk_i)/\lambda_{\bsk_i} = \Theta(\E^{-r_\Delta i})$.
+Choosing $a \ge C_{\DHKMup}/C_{\DHKMlo} $  and $b \ge  2^{-(r_\Delta-1/\rho)}$ causes the cone $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ to include such functions.
+Note that only the ratio of $C_{\DHKMup}$ to $C_{\DHKMlo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
+
+To illustrate the exponential case, suppose that $\DHKMhf(\bsk_i)/\lambda_{\bsk_i} = \Theta(\DHKME^{-r_\Delta i})$.
 For this exponential case one would normally define $\calC$ in terms of an arithmetic sequence, $(n_j)_{j\ge 0}$, e.g., $n_j = n_0 + j q$, where $q$ is a positive integer.
@@
 \begin{align*}
-    \sigma_j(f) &= \left[ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \biggabs{\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
-    = \Theta \left( \left [ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \E^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
-    & = \Theta \left(  \E^{-j r_{\Delta} q} \right).
+    \sigma_j(f) &= \left[ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \DHKMbiggabs{\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}}^\rho \right]^{1/\rho}
+    = \Theta \left( \left [ \sum_{i=n_0 + j q -q + 1}^{n_0 + j q} \DHKME^{- \rho r_\Delta i} \right]^{1/\rho} \right) \\
+    & = \Theta \left(  \DHKME^{-j r_{\Delta} q} \right).
 \end{align*}
 Analogous to the algebraic case, reasonable functions would satisfy 
-    $C_{\lo} \E^{-j r_{\Delta} q} \le \sigma_j(f) \le C_{\up} \E^{-j r_{\Delta} q}$
-for some constants $C_{\lo}$ and $C_{\up}$.
-Choosing $a \ge C_{\up}/C_{\lo} $  and $b \ge \E^{- r_{\Delta} q}$ causes the cone $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ to include such functions.
-Again, only the ratio of $C_{\up}$ to $C_{\lo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
+    $C_{\DHKMlo} \DHKME^{-j r_{\Delta} q} \le \sigma_j(f) \le C_{\DHKMup} \DHKME^{-j r_{\Delta} q}$
+for some constants $C_{\DHKMlo}$ and $C_{\DHKMup}$.
+Choosing $a \ge C_{\DHKMup}/C_{\DHKMlo} $  and $b \ge \DHKME^{- r_{\Delta} q}$ causes the cone $\calC_{\boldsymbol{\lambda},\bsn,a,b}$ to include such functions.
+Again, only the ratio of $C_{\DHKMup}$ to $C_{\DHKMlo}$ need be assumed to determine $a$, and choosing $b$ larger than necessary does not affect the order of the decay of the error bound.
 
@@
 Now let $\DHKMALG'$ be an arbitrary algorithm in $\calA(\calC_{\boldsymbol{\lambda},\bsn,a,b})$, and suppose that $\DHKMALG'(f_1,\varepsilon)$ samples $f_1(\bsk)$ for $\bsk \in \calJ$.
-Let $\tcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
+Let $\DHKMtcalK_j = \calK_j \setminus \calJ$ for all non-negative integers $j$.
 Construct the function $f_2$, having zero coefficients for $\bsk \in \calJ$, but otherwise looking like $f_1$:
@@
 \frac{c_2 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\tLambda_j^{\rho'/\rho}},  
-& \bsk \in \tcalK_j,
+& \bsk \in \DHKMtcalK_j,
 \\
@@
 c_2 &:= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}, \qquad
-\tLambda_j := \norm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \tcalK_j}} \le \Lambda_j, \\
-\nonumber
-\sigma_j(f_2) & = \norm[\rho]{\biggl(\frac{\DHKMhf_{2j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \tcalK_j}} 
-= \begin{cases} c_2 b^j, & \tcalK_j \ne \emptyset, \\
-0, & \tcalK_j = \emptyset, 
+\tLambda_j := \norm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \DHKMtcalK_j}} \le \Lambda_j, \\
+\nonumber
+\sigma_j(f_2) & = \norm[\rho]{\biggl(\frac{\DHKMhf_{2j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \DHKMtcalK_j}} 
+= \begin{cases} c_2 b^j, & \DHKMtcalK_j \ne \emptyset, \\
+0, & \DHKMtcalK_j = \emptyset, 
 \end{cases}
@@
 Suppose that $\DHKMcard(\calJ) = \DHKMCOST(\DHKMALG',f_{\pm},\varepsilon) \le n_{j^{\star}}$.
-Then by condition \eqref{DHKM:PropCond}, there exists an $l^\star \le j^\star+1$ where $\DHKMcard(\tcalK_{l^\star}) \ge S_2 \DHKMcard(\calK_{l^\star})$.
+Then by condition \eqref{DHKM:PropCond}, there exists an $l^\star \le j^\star+1$ where $\DHKMcard(\DHKMtcalK_{l^\star}) \ge S_2 \DHKMcard(\calK_{l^\star})$.
 This implies a lower bound on $\tLambda_{l^\star}$.
 Let $m = n_{l^\star} - n_{l^\star-1} = \DHKMcard(\calK_{l^\star})$.
-Then, $m_{\inc} = \lceil S_2 m \rceil \ge S_2 m$ is a lower bound on  $\DHKMcard(\tcalK_{l^\star})$, and $m_{\out} = m - m_{\inc} \le (1 - S_2) m$ is an upper bound on $\DHKMcard(\calK_{l^\star} \setminus \tcalK_{l^\star})$.
+Then, $m_{\DHKMinc} = \lceil S_2 m \rceil \ge S_2 m$ is a lower bound on  $\DHKMcard(\DHKMtcalK_{l^\star})$, and $m_{\DHKMout} = m - m_{\DHKMinc} \le (1 - S_2) m$ is an upper bound on $\DHKMcard(\calK_{l^\star} \setminus \DHKMtcalK_{l^\star})$.
 Moreover,
@@
 \begin{align*}
-    \Lambda_{l^\star}^\rho & = \sum_{i \in \calK_{l^\star}} \lambda_{\bsk_i}^{\rho} =  \tLambda_{l^\star}^\rho + \sum_{i \in \calK_{l^\star} \setminus \tcalK_{l^\star}} \lambda_{\bsk_i}^{\rho}
+    \Lambda_{l^\star}^\rho & = \sum_{i \in \calK_{l^\star}} \lambda_{\bsk_i}^{\rho} =  \tLambda_{l^\star}^\rho + \sum_{i \in \calK_{l^\star} \setminus \DHKMtcalK_{l^\star}} \lambda_{\bsk_i}^{\rho}
     \\
-    &\le  \tLambda_{l^\star}^\rho + m_{\out} \lambda_{\bsk_{n_{l^\star -1}+1}}^\rho \qquad \text{by the ordering of the } \lambda_{\bsk_i}\\
-    &\le  \tLambda_{l^\star}^\rho + m_{\out} S_1^\rho \lambda_{\bsk_{n_{l^\star}}}^\rho \qquad \text{by \eqref{DHKM:MinMaxCond}}\\
-    & \le \tLambda_{l^\star}^\rho + \frac{m_{\out}}{m_{\inc}} S_1^\rho \tLambda_{l^\star}^\rho \qquad \text{by the definition of } \tLambda_{l^\star}\\
-    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] \tLambda_{l^\star}^\rho \qquad \text{by the bounds on } m_{\inc} \text{ and } m_{\out} 
+    &\le  \tLambda_{l^\star}^\rho + m_{\DHKMout} \lambda_{\bsk_{n_{l^\star -1}+1}}^\rho \qquad \text{by the ordering of the } \lambda_{\bsk_i}\\
+    &\le  \tLambda_{l^\star}^\rho + m_{\DHKMout} S_1^\rho \lambda_{\bsk_{n_{l^\star}}}^\rho \qquad \text{by \eqref{DHKM:MinMaxCond}}\\
+    & \le \tLambda_{l^\star}^\rho + \frac{m_{\DHKMout}}{m_{\DHKMinc}} S_1^\rho \tLambda_{l^\star}^\rho \qquad \text{by the definition of } \tLambda_{l^\star}\\
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] \tLambda_{l^\star}^\rho \qquad \text{by the bounds on } m_{\DHKMinc} \text{ and } m_{\DHKMout} 
     \\
@@
 \begin{equation}
-u_\bsk = \prod_{\ell = 1}^d \tu_{k_\ell}, \quad 
+u_\bsk = \prod_{\ell = 1}^d \DHKMtu_{k_\ell}, \quad 
 \lambda_{\bsk} = \Gamma_{\|\bsk\|_0} \prod_{\substack{\ell=1\\ k_\ell>0}}^d w_\ell s_{k_\ell}, \quad \Gamma_0 = s_1 = 1, \quad \bsk \in \mathbb{N}_0^d,
@@
     \item Coordinate weights quantify the importance for the $d$ input variables in $f$.
-    \item Smoothness weights quantify the importance of the $\tu_k$.
-E.g., if the $\tu_k$ are polynomials of degree $k$ as in Section \ref{DHKM:secexamp}, then the faster the $s_k$ decay, the smoother $f$ is.
+    \item Smoothness weights quantify the importance of the $\DHKMtu_k$.
+E.g., if the $\DHKMtu_k$ are polynomials of degree $k$ as in Section \ref{DHKM:secexamp}, then the faster the $s_k$ decay, the smoother $f$ is.
     \item Order weights quantify the importance of effects with different orders; $\bsk$ having one nonzero element corresponds to a first-order or main effect, $\bsk$ having two nonzero elements corresponds to a second-order (interaction) effect (e.g., first-order, second-order).
@@
 \item \emph{Effect smoothness} assumes that lower-degree effects are more important than higher-degree effects.
-For example, when the $(\tu_k)_{k \in \mathbb{N}_0}$ are polynomials, this means that linear effects are more important than quadratic effects, which are in turn more significant than cubic effects, and so on.
+For example, when the $(\DHKMtu_k)_{k \in \mathbb{N}_0}$ are polynomials, this means that linear effects are more important than quadratic effects, which are in turn more significant than cubic effects, and so on.
 Effect smoothness can be imposed by assuming $\bss$ to be a decreasing sequence.
@@
 A ratio $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
-For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\DHKMAPProx 0.1$ for $\varepsilon = 0.1$, then decreases to $\DHKMAPProx 0.014$ for $\varepsilon = 0.001$.
+For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$.
 This shows that our adaptive approximation algorithm works reasonably well.

### 2019-10-31 DingHickKritzMakRICAMChapVerF.tex
Updates from Overleaf

@@
 \newcommand{\DHKMbiggabs}[1]{\ensuremath{\biggl \lvert #1 \biggr \rvert}}
-\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
-\newcommand{\normnorm}[2][{}]{\ensuremath{\lVert #2 \rVert}_{#1}}
+\newcommand{\DHKMnorm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
+%\newcommand{\normnorm}[2][{}]{\ensuremath{\lVert #2 \rVert}_{#1}}
 \newcommand{\bignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
@@
 
-We study the approximation of a linear solution operator $\DHKMSOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and $\calG$ are Banach spaces with norms $\norm[\calF]{\cdot}$ and $\norm[\calG]{\cdot}$, respectively.
+We study the approximation of a linear solution operator $\DHKMSOL:\calF \to \calG$, which maps $f\in\calF$ to some $g\in\calG$, where we assume that $\calF$ and $\calG$ are Banach spaces with norms $\DHKMnorm[\calF]{\cdot}$ and $\DHKMnorm[\calG]{\cdot}$, respectively.
 Our goal is to define a suitable set of input functions $\calC$, and an algorithm $\DHKMALG(\cdot,\cdot):\calC \times (0,\infty) \to \calG$ that satisfies the error criterion:
 \begin{equation} \label{DHKM:err_crit}
-    \norm[\calG]{\DHKMSOL(f) - \DHKMALG(f,\varepsilon)} \le \varepsilon \qquad \forall \varepsilon > 0, \ f \in \calC,
+    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMALG(f,\varepsilon)} \le \varepsilon \qquad \forall \varepsilon > 0, \ f \in \calC,
 \end{equation}
@@
 
-In the following, let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
-We now define the information cost of the algorithm in general, recognizing that it will tend to depend on $\norm[\calF]{f}$:
+In the following, let $\calB_{R} : = \{ f \in \calF : \DHKMnorm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
+We now define the information cost of the algorithm in general, recognizing that it will tend to depend on $\DHKMnorm[\calF]{f}$:
 \begin{equation*}
@@
 \end{equation*}
-Note that while the cost depends on $\norm[\calF]{f}$, $\DHKMALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
+Note that while the cost depends on $\DHKMnorm[\calF]{f}$, $\DHKMALG(f,\varepsilon)$ has no knowledge of $f$ beyond the fact that it lies in $\calC$.
 It is common for $\DHKMCOST(\DHKMALG, \calC, \varepsilon,R)$ to be $\calO(\varepsilon^{-p})$, or perhaps asymptotically $c\log(1 + \varepsilon^{-1})$.
@@
 $$
-  \norm[\calF]{f}\le h (\DHKMhf(\bsk_1),\ldots,\DHKMhf (\bsk_{n_1}))
+  \DHKMnorm[\calF]{f}\le h (\DHKMhf(\bsk_1),\ldots,\DHKMhf (\bsk_{n_1}))
 $$
@@
 Any algorithm must require a finite sample size, even if it is huge.
-Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\norm[\calG]{\DHKMSOL(f)}$ is arbitrarily large.
+Then, there must exist some $f \in \calF$ that looks exactly like the zero function to the algorithm but for which $\DHKMnorm[\calG]{\DHKMSOL(f)}$ is arbitrarily large.
 Thus, algorithms satisfying the error criterion  exist only for some strict subset of $\calF$, such as a ball or a cone.
@@
 \begin{gather*}
-    \calF := \left \{f = \sum_{\bsk \in \mathbb{K}} \DHKMhf(\bsk) u_{\bsk} : \norm[\calF]{f} : = \norm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \rho \le \infty,
+    \calF := \left \{f = \sum_{\bsk \in \mathbb{K}} \DHKMhf(\bsk) u_{\bsk} : \DHKMnorm[\calF]{f} : = \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \rho \le \infty,
 \end{gather*}
@@
 \begin{gather*}
-    \calG := \left \{g = \sum_{\bsk \in \mathbb{K}} \DHKMhg(\bsk) v_{\bsk} : \norm[\calG]{g} : = \norm[\tau]{\bigl(  \DHKMhg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \tau \le \rho.
+    \calG := \left \{g = \sum_{\bsk \in \mathbb{K}} \DHKMhg(\bsk) v_{\bsk} : \DHKMnorm[\calG]{g} : = \DHKMnorm[\tau]{\bigl(  \DHKMhg(\bsk)  \bigr)_{\bsk \in \mathbb{K}}} < \infty \right\}, \quad\mbox{with}\quad 1 \le \tau \le \rho.
 \end{gather*}
@@
 \label{DHKM:SOL_ineq}
-    \norm[\calG]{\DHKMSOL(f)} = \norm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK}} \le \norm[\calF]{f} \, \Lambda,
+    \DHKMnorm[\calG]{\DHKMSOL(f)} = \DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK}} \le \DHKMnorm[\calF]{f} \, \Lambda,
     \end{equation}
@@
    \\ 
-    \implies  \ \ \norm[\calF]{f} = R \ \mbox{and} \ \norm[\calG]{\DHKMSOL(f)} = R \Lambda.
+    \implies  \ \ \DHKMnorm[\calF]{f} = R \ \mbox{and} \ \DHKMnorm[\calG]{\DHKMSOL(f)} = R \Lambda.
     \end{multline}
@@
     \label{DHKM:SOL_A}
-    \norm[\calG]{\DHKMSOL(f)}  
-    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \DHKMhf(\bsk) v_{\bsk}} = \norm[\tau]{\bigl(  \DHKMhf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
-    \nonumber
-    & \le \biggnorm[\rho]{\biggl(  \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \norm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
+    \DHKMnorm[\calG]{\DHKMSOL(f)}  
+    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \DHKMhf(\bsk) v_{\bsk}} = \DHKMnorm[\tau]{\bigl(  \DHKMhf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
+    \nonumber
+    & \le \biggnorm[\rho]{\biggl(  \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \DHKMnorm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
 \end{align}
@@
 \begin{equation*}
-       \norm[\calG]{\DHKMSOL(f)}  
+       \DHKMnorm[\calG]{\DHKMSOL(f)}  
     =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\Lambda^{\rho'/\rho}} 
@@
 \begin{equation*}
-    \norm[\calF]{f}  
-    = \norm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
+    \DHKMnorm[\calF]{f}  
+    = \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
     = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\Lambda^{\rho'/\rho}} 
@@
 \begin{equation} \label{DHKM:SOLNorm}
-    \norm[\calF \to \calG]{\DHKMSOL}  = \sup_{\norm[\calF]{f} \le 1} \norm[\calG]{\DHKMSOL(f)} = \bignorm[\rho']{\bslambda}.
+    \DHKMnorm[\calF \to \calG]{\DHKMSOL}  = \sup_{\DHKMnorm[\calF]{f} \le 1} \DHKMnorm[\calG]{\DHKMSOL(f)} = \bignorm[\rho']{\bslambda}.
 \end{equation}
@@
 \label{DHKM:IllExWts}
-    \norm[\calF]{f} := \norm[2]{\left(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
+    \DHKMnorm[\calF]{f} := \DHKMnorm[2]{\left(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}\right)_{\bsk \in \N_0^d}}, \qquad \text{where } \lambda_\bsk := \prod_{\substack{\ell =1\\ k_\ell > 0}}^d \frac{w_\ell}{k^r_\ell}, \quad r > 0.
 \end{equation}
@@
 \begin{equation*}
-      \norm[\calG]{\sum_{\bsk \in \N_0^d} \DHKMhg(\bsk) u_{\bsk}} : = \norm[2]{\bigl(\DHKMhg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
+      \DHKMnorm[\calG]{\sum_{\bsk \in \N_0^d} \DHKMhg(\bsk) u_{\bsk}} : = \DHKMnorm[2]{\bigl(\DHKMhg(\bsk) \bigr)_{\bsk \in \N_0^d}}.
 \end{equation*}
@@
 \begin{equation*}
-    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[2]{\bigl(\DHKMhf(\bsk_i) \bigr)_{i=n+1}^{\infty}}.
+    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \DHKMnorm[2]{\bigl(\DHKMhf(\bsk_i) \bigr)_{i=n+1}^{\infty}}.
 \end{equation*}
@@
 \begin{equation} \label{DHKM:APP_Err_Coef}
-    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \norm[\tau]{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=n+1}^\infty}.
+    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)} = \DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk_i)\bigr)_{i=n+1}^\infty}.
 \end{equation}
@@
 \begin{gather} \label{DHKM:Refined_APP_err}
-    \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
+    \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
     \bignorm[\rho']{\bslambda^{(n+1)}}, \\
@@
 
-\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \norm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
+\begin{theorem} \label{DHKM:APP_optimality_thm} Let $\calB_{R} : = \{ f \in \calF : \DHKMnorm[\calF]{f} \le R \}$ denote the ball of radius $R$ in the space of input functions.
 The error of the approximation defined in \eqref{DHKM:APP_def} is bounded tightly above as
 \begin{equation} \label{DHKM:APP_errorBd}
-    \sup_{f \in \calB_R} \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
+    \sup_{f \in \calB_R} \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
 \end{equation}
@@
 \nonumber
-    \DHKMhf(\bsk'_1) = \cdots = \DHKMhf(\bsk'_n) = 0, \qquad \norm[\calF]{f} = R, \\ 
-    \norm[\calG]{\DHKMSOL(f)} =  R \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.  \label{DHKM:FoolFun}
+    \DHKMhf(\bsk'_1) = \cdots = \DHKMhf(\bsk'_n) = 0, \qquad \DHKMnorm[\calF]{f} = R, \\ 
+    \DHKMnorm[\calG]{\DHKMSOL(f)} =  R \DHKMnorm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}.  \label{DHKM:FoolFun}
 \end{gather}
@@
 \begin{align*}
-\MoveEqLeft{\sup_{f \in \calB_R} \norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}} \\
-& \ge \max_{\pm} \norm[\calG]{\DHKMSOL(\pm f) - \DHKMAPP'(\pm f,n)} =  \max_{\pm} \norm[\calG]{\DHKMSOL(\pm f) - \DHKMAPP'(0,n)} \\
-& \ge \frac 12 \left [ \norm[\calG]{\DHKMSOL(f) - \DHKMAPP'(0,n)} 
-+ \norm[\calG]{- \DHKMSOL(f) - \DHKMAPP'(0,n)}\right] \\
-& \ge \norm[\calG]{\DHKMSOL(f)} 
- = R  \norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:FoolFun}}.
-\end{align*}
-The ordering of the $\lambda_{\bsk}$ implies that $\norm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}$ for arbitrary $\calJ$ can be no smaller than the case $\calJ = \{\bsk_1, \ldots, \bsk_n\}$.
+\MoveEqLeft{\sup_{f \in \calB_R} \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}} \\
+& \ge \max_{\pm} \DHKMnorm[\calG]{\DHKMSOL(\pm f) - \DHKMAPP'(\pm f,n)} =  \max_{\pm} \DHKMnorm[\calG]{\DHKMSOL(\pm f) - \DHKMAPP'(0,n)} \\
+& \ge \frac 12 \left [ \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP'(0,n)} 
++ \DHKMnorm[\calG]{- \DHKMSOL(f) - \DHKMAPP'(0,n)}\right] \\
+& \ge \DHKMnorm[\calG]{\DHKMSOL(f)} 
+ = R  \DHKMnorm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:FoolFun}}.
+\end{align*}
+The ordering of the $\lambda_{\bsk}$ implies that $\DHKMnorm[\rho']{\left( \lambda_{\bsk} \right)_{\bsk \notin \calJ}}$ for arbitrary $\calJ$ can be no smaller than the case $\calJ = \{\bsk_1, \ldots, \bsk_n\}$.
 This completes the proof.
@@
 \begin{equation} \label{DHKM:pilot_cone}
-    \calC_{\boldsymbol{\lambda},n_1,A} = \left \{ f \in \calF : \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
+    \calC_{\boldsymbol{\lambda},n_1,A} = \left \{ f \in \calF : \DHKMnorm[\calF]{f} \le A \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \right\}.
 \end{equation}
@@
 \begin{align*}
-     \MoveEqLeft{\norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
-     & =  \left[ \norm[\calF]{f}^\rho -  \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+     \MoveEqLeft{\DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}} \\
+     & =  \left[ \DHKMnorm[\calF]{f}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
     \right]^{1/\rho} \qquad \forall f \in \calF \\
-    &  \le  \left[ A^\rho \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
+    &  \le  \left[ A^\rho \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho
     \right]^{1/\rho} \quad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A}.
@@
 \begin{equation}
-\norm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le \DHKMERRN  \qquad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A},
+\DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le \DHKMERRN  \qquad \forall f \in \calC_{\boldsymbol{\lambda},n_1,A},
 \end{equation}
@@
     : =  
-    \left[ A^\rho \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \norm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho}
+    \left[ A^\rho \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho}
     \, \bignorm[\rho']{\bslambda^{(n+1)}} , 
@@
      & \le \max_{f \in \calC \cap \calB_{R}} \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
+     (A^\rho -1)^{1/\rho} \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
      \bignorm[\rho']{\bslambda^{(n+1)}}
@@
 \end{align*}
-since $\bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \norm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
+since $\bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \DHKMnorm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
 Moreover, this inequality is tight for some $f \in \calC_{\boldsymbol{\lambda},n_1,A} \cap \calB_{R}$, namely, those certain $f$ for which $\DHKMhf(\bsk_i) = 0$ for $i > n_1$.
@@
     \end{cases}
-   \qquad \norm[\calF]{f_1} = \frac{R(1 + 1/A)}{2}.
+   \qquad \DHKMnorm[\calF]{f_1} = \frac{R(1 + 1/A)}{2}.
 \end{equation*}
@@
     \end{cases}
-    \qquad \norm[\calF]{f_2} = \frac{R(1 - 1/A)}{2}, \\
+    \qquad \DHKMnorm[\calF]{f_2} = \frac{R(1 - 1/A)}{2}, \\
     \label{DHKM:SOLf2bd}
-    \norm[\calG]{\DHKMSOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
+    \DHKMnorm[\calG]{\DHKMSOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
 \end{gather}
@@
 \nonumber
-    \norm[\calF]{f_{\pm}} &= \norm[\calF]{ f_1 \pm f_2 } \le \norm[\calF]{ f_1} + \norm[\calF]{ f_2 } =  R, \\
-    \nonumber
-    \norm[\rho]{\left( \frac{\DHKMhf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
-    & = \norm[\rho]{\left( \frac{\DHKMhf_1(\bsk_i) \pm \DHKMhf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
-    \nonumber
-    & \ge \norm[\rho]{\left( \frac{\DHKMhf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \norm[\rho]{\left( \frac{\DHKMhf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
-    \nonumber
-    & \ge \norm[\calF]{ f_1} - \norm[\calF]{ f_2 } =  \frac{R}{A} \ge \frac{\norm[\calF]{f_{\pm}}}{A}.
+    \DHKMnorm[\calF]{f_{\pm}} &= \DHKMnorm[\calF]{ f_1 \pm f_2 } \le \DHKMnorm[\calF]{ f_1} + \DHKMnorm[\calF]{ f_2 } =  R, \\
+    \nonumber
+    \DHKMnorm[\rho]{\left( \frac{\DHKMhf_\pm(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} 
+    & = \DHKMnorm[\rho]{\left( \frac{\DHKMhf_1(\bsk_i) \pm \DHKMhf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \nonumber
+    & \ge \DHKMnorm[\rho]{\left( \frac{\DHKMhf_1(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} - \DHKMnorm[\rho]{\left( \frac{\DHKMhf_2(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \\
+    \nonumber
+    & \ge \DHKMnorm[\calF]{ f_1} - \DHKMnorm[\calF]{ f_2 } =  \frac{R}{A} \ge \frac{\DHKMnorm[\calF]{f_{\pm}}}{A}.
 \end{align}
@@
 \begin{align*}
-\varepsilon & \ge \max_{\pm} \norm[\calG]{\DHKMSOL(f_{\pm}) - \DHKMALG'(f_{\pm},\varepsilon)} 
-=  \max_{\pm} \norm[\calG]{\DHKMSOL(f_{\pm}) - \DHKMALG'(f_{+},\varepsilon)} \\
-& \ge \frac 12 \left [ \norm[\calG]{\DHKMSOL(f_{+}) - \DHKMALG'(f_{+},\varepsilon)} 
-+ \norm[\calG]{\DHKMSOL(f_{-}) - \DHKMALG'(f_{+},\varepsilon)}  \right] \\
-& \ge \frac 12 \norm[\calG]{\DHKMSOL(f_+ - f_-)} = \norm[\calG]{\DHKMSOL(f_2)} 
+\varepsilon & \ge \max_{\pm} \DHKMnorm[\calG]{\DHKMSOL(f_{\pm}) - \DHKMALG'(f_{\pm},\varepsilon)} 
+=  \max_{\pm} \DHKMnorm[\calG]{\DHKMSOL(f_{\pm}) - \DHKMALG'(f_{+},\varepsilon)} \\
+& \ge \frac 12 \left [ \DHKMnorm[\calG]{\DHKMSOL(f_{+}) - \DHKMALG'(f_{+},\varepsilon)} 
++ \DHKMnorm[\calG]{\DHKMSOL(f_{-}) - \DHKMALG'(f_{+},\varepsilon)}  \right] \\
+& \ge \frac 12 \DHKMnorm[\calG]{\DHKMSOL(f_+ - f_-)} = \DHKMnorm[\calG]{\DHKMSOL(f_2)} 
 =\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
@@
 \begin{equation} \label{DHKM:PilotConeNecessary}
-    \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i =1}^{n}} \le A
-    \norm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
+    \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i =1}^{n}} \le A
+    \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK_1}} \qquad \forall n \in \NN.
 \end{equation}
@@
 \begin{multline} \label{DHKM:altconedef}
-    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \norm[\calF]{f} \le A'\norm[\calF']{f}\}, \\ \text{where } \norm[\calF']{f} :=\norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)\omega_{i}}{\lambda_{\bsk_i}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
+    \calC'_{\boldsymbol{\lambda}, \boldsymbol{\omega}, A'}:=\{ f \in \calF : \DHKMnorm[\calF]{f} \le A'\DHKMnorm[\calF']{f}\}, \\ \text{where } \DHKMnorm[\calF']{f} :=\DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)\omega_{i}}{\lambda_{\bsk_i}} \right)_{i =  1}^n} \text{ and } \omega_1 \ge \omega_2 \ge \cdots.
 \end{multline}
-The norm $\norm[\calF']{\cdot}$ is weaker than the norm $\norm[\calF]{\cdot}$, so this cone is a strict subset of $\calF$.
+The norm $\DHKMnorm[\calF']{\cdot}$ is weaker than the norm $\DHKMnorm[\calF]{\cdot}$, so this cone is a strict subset of $\calF$.
 The following proposition describes how the cones defined in \eqref{DHKM:pilot_cone} and \eqref{DHKM:altconedef} are related.
@@
 \begin{equation*}
-    \norm[\calF]{f} \le A \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
-     \le A \omega_{n_1}^{-1} \norm[\rho]{\left( \frac{\DHKMhf(\bsk_i)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
-     \le A \omega_{n_1}^{-1} \norm[\calF']{f}.
+    \DHKMnorm[\calF]{f} \le A \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i = 1} ^{ n_1}}
+     \le A \omega_{n_1}^{-1} \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)\omega_{\bsk_i}}{\lambda_{\bsk_i}} \right)_{i =1} ^{n_1}}
+     \le A \omega_{n_1}^{-1} \DHKMnorm[\calF']{f}.
 \end{equation*}
@@
 \begin{align*}
-    \norm[\calF']{f}^\rho- \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho 
-	& = \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho 
-     \le \omega_{n_1+1}^\rho \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
-     & = \omega_{n_1+1}^\rho \left[ \norm[\calF]{f}^\rho - \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
-     & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \norm[\calF']{f}^\rho - \omega_1^{-\rho} \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].
+    \DHKMnorm[\calF']{f}^\rho- \DHKMnorm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho 
+	& = \DHKMnorm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho 
+     \le \omega_{n_1+1}^\rho \DHKMnorm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=n_1 + 1}^{\infty}}^\rho \\
+     & = \omega_{n_1+1}^\rho \left[ \DHKMnorm[\calF]{f}^\rho - \DHKMnorm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ]\\	
+     & \le \omega_{n_1+1}^\rho \left[ A'{}^\rho \DHKMnorm[\calF']{f}^\rho - \omega_1^{-\rho} \DHKMnorm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho \right ].
 \end{align*}
@@
 \begin{align*}
-\norm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho, \\
-	\norm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \norm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
+\DHKMnorm[\calF']{f}^\rho & \le \frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho} \DHKMnorm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i) \omega_i }{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}^\rho, \\
+	\DHKMnorm[\calF]{f} & \le \omega_1A'\left[\frac{1 + (\omega_{n_1+1}/\omega_1)^\rho}{1 - (\omega_{n_1+1}A')^\rho}\right]^{1/\rho} \DHKMnorm[\rho]{\biggl ( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \biggr) _{i=1}^{n_1}}.
 \end{align*}
@@
 \[ 
-\lambda_{\bsk_{n+1}} \le \frac{\norm[p]{\bslambda}}{n^{1/p}} \ \ \text{and} \ \ 
+\lambda_{\bsk_{n+1}} \le \frac{\DHKMnorm[p]{\bslambda}}{n^{1/p}} \ \ \text{and} \ \ 
  \sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} \ge \frac{\bignorm[p\eta]{\bslambda^{(n_{\min})}}}{\zeta(\eta)^{1/(p\eta)}} \quad \forall p>0, \ \eta > 1, \ n_{\min} \in \bbN.
 \]
-If $\norm[p]{\bslambda} = \infty$ or $\sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} = \infty$, we consider these inequalities to be trivially true.
+If $\DHKMnorm[p]{\bslambda} = \infty$ or $\sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} = \infty$, we consider these inequalities to be trivially true.
 \end{lemma}
@@
     \lambda_{\bsk_{1}}^p + \lambda_{\bsk_{2}}^p + \cdots 
-    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK} \lambda_{\bsk}^p = \norm[p]{\bslambda}^p \qquad \forall p > 0.
+    + \lambda_{\bsk_{n}}^p  \le \sum_{\bsk \in \bbK} \lambda_{\bsk}^p = \DHKMnorm[p]{\bslambda}^p \qquad \forall p > 0.
 \end{equation*}
@@
 \begin{theorem} \label{DHKM:thm:costbdspilot}
-If the elements of $\bslambda$ decay fast enough so that $\norm[p]{\bslambda} < \infty$ and $\rho'=\infty$, then the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are bounded above by
+If the elements of $\bslambda$ decay fast enough so that $\DHKMnorm[p]{\bslambda} < \infty$ and $\rho'=\infty$, then the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are bounded above by
 \begin{align*}
     \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \DHKMCOST(\DHKMALG,\calB_R,\varepsilon, R') 
-    \le \left \lceil  \left(\frac{R \norm[p]{\bslambda}}{\varepsilon}\right)^p     \right \rceil, \qquad \forall \varepsilon, \ 0 < R' < R, \\
+    \le \left \lceil  \left(\frac{R \DHKMnorm[p]{\bslambda}}{\varepsilon}\right)^p     \right \rceil, \qquad \forall \varepsilon, \ 0 < R' < R, \\
     \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \\ & \qquad \qquad \le \max \left( n_1, 
-    \left \lceil  \left(\frac{[(A^\rho -1)^{1/\rho}R] \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil \right).
+    \left \lceil  \left(\frac{[(A^\rho -1)^{1/\rho}R] \DHKMnorm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil \right).
     \end{align*}
@@
     \end{align*}
-then $\norm[p\eta]{\bslambda} < \infty$ for all $\eta > 1$.
+then $\DHKMnorm[p\eta]{\bslambda} < \infty$ for all $\eta > 1$.
 Since Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} are essentially optimal, the above inequalities provide upper and lower asymptotic bounds on  $\DHKMCOMP(\calB_R,\varepsilon,R')$ and $\DHKMCOMP(\calC_{\bslambda,n_1,A},\varepsilon,R)$.
@@
     \le \frac{\varepsilon}{[(A^\rho -1)^{1/\rho}R]} \right \} \\
-  & \le  \min \left \{n \ge n_1 : \norm[p]{\bslambda}n^{-1/p}
+  & \le  \min \left \{n \ge n_1 : \DHKMnorm[p]{\bslambda}n^{-1/p}
     \le \frac{\varepsilon}{[(A^\rho -1)^{1/\rho}R]} \right \} \\
-    & \qquad \qquad \text{by Lemma \ref{DHKM:lambdineq} since } \lambda_{\bsk_{n+1}} \le \norm[p]{\bslambda}n^{-1/p}\\
-  & = \left \lceil  \left(\frac{[(A^\rho -1)^{1/\rho}R] \norm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil.
+    & \qquad \qquad \text{by Lemma \ref{DHKM:lambdineq} since } \lambda_{\bsk_{n+1}} \le \DHKMnorm[p]{\bslambda}n^{-1/p}\\
+  & = \left \lceil  \left(\frac{[(A^\rho -1)^{1/\rho}R] \DHKMnorm[p]{\bslambda}}{\varepsilon}\right)^p \right \rceil.
 \end{align*}
@@
 For $\bslambda = \bigl(\lambda_{\bsk} \bigr)_{\bsk \in \bbN_0^d}$ defined in \eqref{DHKM:prodwts}
-we have the following lower and upper bounds on $\norm[p]{\bslambda}$.  It holds that
+we have the following lower and upper bounds on $\DHKMnorm[p]{\bslambda}$.  It holds that
 \begin{gather*}
-\norm[p]{\bss} \norm[p]{\bsw} \le \norm[p]{\bslambda}\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \\
-[\zeta(pr)]^{1/p} \norm[p]{\bsw} \le \norm[p]{\bslambda} \le \exp\left(\frac {\zeta(pr)}p \norm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, \ldots ), \ pr > 1.
+\DHKMnorm[p]{\bss} \DHKMnorm[p]{\bsw} \le \DHKMnorm[p]{\bslambda}\le \exp\left(\frac 1p \DHKMnorm[p]{\bss}^p \DHKMnorm[p]{\bsw}^p  \right) \qquad \text{for general } \bss, \\
+[\zeta(pr)]^{1/p} \DHKMnorm[p]{\bsw} \le \DHKMnorm[p]{\bslambda} \le \exp\left(\frac {\zeta(pr)}p \DHKMnorm[p]{\bsw}^p  \right) \qquad \text{for } \bss = (1, 2^{-r}, \ldots ), \ pr > 1.
 \end{gather*}
@@
 \begin{proof}
-The proof is constructed first for general $\bss$.  For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\norm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
+The proof is constructed first for general $\bss$.  For the particular form of $\bss$ introduced in \eqref{DHKM:IllExWts} it follows that $\DHKMnorm[p]{\bss}^p = \zeta(pr)$ for $pr > 1$.
 
@@
 \begin{equation} \label{DHKM:lambdaprodwts}
-   \norm[p]{\bslambda}^ p 
+   \DHKMnorm[p]{\bslambda}^ p 
    = \sum_{\bsk \in \NN_0^d} \lambda_{\bsk}^p  
    = \prod_{\ell =1}^d\left(1+ w_\ell^p \sum_{k=1}^{\infty}s_{k}^p\right) 
-   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right).
+   = \prod_{\ell =1}^d\left(1+ w_\ell^p \DHKMnorm[p]{\bss}^p \right).
 \end{equation}
@@
 \begin{equation*}
-   \norm[p]{\bslambda}^ p 
-   = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right)  
-   \ge  \norm[p]{\bss}^p \sum_{\ell =1}^d w_\ell^p = \norm[p]{\bss}^p \norm[p]{\bsw}^p.
+   \DHKMnorm[p]{\bslambda}^ p 
+   = \prod_{\ell =1}^d\left(1+ w_\ell^p \DHKMnorm[p]{\bss}^p \right)  
+   \ge  \DHKMnorm[p]{\bss}^p \sum_{\ell =1}^d w_\ell^p = \DHKMnorm[p]{\bss}^p \DHKMnorm[p]{\bsw}^p.
 \end{equation*}
@@
 \begin{align*}
-   \norm[p]{\bslambda}^ p
-   & = \prod_{\ell =1}^d\left(1+ w_\ell^p \norm[p]{\bss}^p \right)
-   = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\norm[p]{\bss}^p \bigr) \right)\\
- &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p} \norm[p]{\bss}^p \right) = \exp\left(\norm[p]{\bsw}^p\norm[p]{\bss}^p \right)
+   \DHKMnorm[p]{\bslambda}^ p
+   & = \prod_{\ell =1}^d\left(1+ w_\ell^p \DHKMnorm[p]{\bss}^p \right)
+   = \exp\left(\sum_{\ell = 1}^d \log\bigl(1 + w_\ell^{p}\DHKMnorm[p]{\bss}^p \bigr) \right)\\
+ &  \le \exp\left(\sum_{\ell = 1}^d  w_\ell^{p} \DHKMnorm[p]{\bss}^p \right) = \exp\left(\DHKMnorm[p]{\bsw}^p\DHKMnorm[p]{\bss}^p \right)
 \quad \text{since }\log(1+x) \le x \ \forall x\ge 0.
@@
     \text{Algorithm \ref{DHKM:BallAlg}:} \quad& \DHKMCOST(\DHKMALG,\calB_R,\varepsilon, R') 
-    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil, \\
+    \le \left \lceil  \left(\frac{R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \DHKMnorm[p]{\bsw}^p  \right)    \right \rceil, \\
     \text{Algorithm \ref{DHKM:PilotConeAlg}:} \quad& \DHKMCOST(\DHKMALG,\calC_{\bslambda,n_1,A},\varepsilon, R) 
     \\ & \qquad \qquad \le \max \left( n_1, 
-    \left \lceil  \left(\frac{(A^\rho-1)^{1/\rho}R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)    \right \rceil \right).
+    \left \lceil  \left(\frac{(A^\rho-1)^{1/\rho}R}{\varepsilon}\right)^p  \exp\left( \zeta(pr) \DHKMnorm[p]{\bsw}^p  \right)    \right \rceil \right).
     \end{align*}
@@
     \MoveEqLeft{\DHKMCOMP(\calB_{R},\varepsilon,R)} 
-  \le \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \norm[p]{\bsw}^p  \right) \right \rceil .
-\end{align*}
-If $p^\dagger$ is the infimum of the $p$ for which $\norm[p]{\bsw}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $\widetilde{p}_* = \max(1/r,p^\dagger)$.
+  \le \left \lceil \left( \frac{R}{\varepsilon} \right)^{p}  \exp\left(\zeta(p r) \DHKMnorm[p]{\bsw}^p  \right) \right \rceil .
+\end{align*}
+If $p^\dagger$ is the infimum of the $p$ for which $\DHKMnorm[p]{\bsw}$ is finite, and $p^\dagger$ is finite, then we obtain strong polynomial tractability and an exponent of strong tractability that is $\widetilde{p}_* = \max(1/r,p^\dagger)$.
 On the other hand, if the coordinate weights are all unity,  $w_1 = w_2 = \cdots = 1$, then there are $2^d$ different $\lambda_{\bsk}$ with a value of $1$, and so $\DHKMCOMP(\calB_{R},\varepsilon,R) \ge 2^d$, and the problem is not tractable.\\
@@
 \[
-\norm[p]{\bss} \norm[p]{\bsw_d} \le \norm[p]{\bslambda_d}\le \exp\left(\frac 1p \norm[p]{\bss}^p \norm[p]{\bsw_d}^p  \right),
+\DHKMnorm[p]{\bss} \DHKMnorm[p]{\bsw_d} \le \DHKMnorm[p]{\bslambda_d}\le \exp\left(\frac 1p \DHKMnorm[p]{\bss}^p \DHKMnorm[p]{\bsw_d}^p  \right),
 \]
@@
 %\label{DHKM:sptexample}
-    \norm[p]{\bss} < \infty \text{ and } 
-    \norm[p]{\bsw_\infty} < \infty.
+    \DHKMnorm[p]{\bss} < \infty \text{ and } 
+    \DHKMnorm[p]{\bsw_\infty} < \infty.
 \end{equation*}
@@
    r p > 1 \text{ and } 
-    \norm[p]{\bsw_\infty} < \infty.
+    \DHKMnorm[p]{\bsw_\infty} < \infty.
 \end{equation*}
@@
 Unfortunately, adaptive Algorithm \ref{DHKM:PilotConeAlg} does not adapt to the decay rate of the $\DHKMhf(\bsk_i)$ as $i \to \infty$.
-It simply bounds $\norm[\calF]{f}$ based on a pilot sample.
+It simply bounds $\DHKMnorm[\calF]{f}$ based on a pilot sample.
 The algorithm presented in this section tracks the rate of decay of the $\DHKMhf(\bsk_i)$ and terminates sooner if the $\DHKMhf(\bsk_i)$ decay more quickly.
@@
 \begin{equation} \label{DHKM:SigmaDef}
-\sigma_j (f):=\norm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} \qquad \text{for } j \in \N.
-\end{equation}
-Thus, $\norm[\calF]{f} = \norm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N_0}}$.
+\sigma_j (f):=\DHKMnorm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} \qquad \text{for } j \in \N.
+\end{equation}
+Thus, $\DHKMnorm[\calF]{f} = \DHKMnorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N_0}}$.
 
@@
 \begin{equation} \label{DHKM:LambdaDef}
-    \norm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK_j}} \le \sigma_j(f) \Lambda_j, \qquad \text{where } \Lambda_j : = \norm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
+    \DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK_j}} \le \sigma_j(f) \Lambda_j, \qquad \text{where } \Lambda_j : = \DHKMnorm[\rho']{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}}.
 \end{equation}
@@
 \begin{equation} \label{DHKM:NormLambdaFinite}
-    \norm[\calF \to \calG]{\DHKMSOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
+    \DHKMnorm[\calF \to \calG]{\DHKMSOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
 \end{equation}
@@
 \begin{align*}
-    \norm[\calF]{f} & = \norm[\rho]{\Biggl(\,\norm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
+    \DHKMnorm[\calF]{f} & = \DHKMnorm[\rho]{\Biggl(\,\DHKMnorm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
     & \le \bignorm[\rho]{\bigl(\sigma_1(f), ab \sigma_1(f), ab^2 \sigma_1(f), \ldots \bigr)} \\
-    & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \norm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
+    & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \DHKMnorm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
 \end{align*}
@@
 \nonumber
-\MoveEqLeft{\norm[\calG]{\DHKMSOL(f)-\DHKMAPP(f,n_j)}} \\
-\nonumber &= \norm[\tau]{\left(\DHKMhf(\bsk_i) \right)_{i = n_j+1}^\infty}
-= \norm[\tau]{ \left(\norm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK_l}} \right)_{l=j+1}^\infty}
+\MoveEqLeft{\DHKMnorm[\calG]{\DHKMSOL(f)-\DHKMAPP(f,n_j)}} \\
+\nonumber &= \DHKMnorm[\tau]{\left(\DHKMhf(\bsk_i) \right)_{i = n_j+1}^\infty}
+= \DHKMnorm[\tau]{ \left(\DHKMnorm[\tau]{\bigl(\DHKMhf(\bsk) \bigr)_{\bsk \in \calK_l}} \right)_{l=j+1}^\infty}
 \\
 \nonumber
-& \le \norm[\tau]{ \bigl(\sigma_l(f) \Lambda_l \bigr)_{l=j+1}^\infty} \qquad \text{by \eqref{DHKM:LambdaDef}} \\
+& \le \DHKMnorm[\tau]{ \bigl(\sigma_l(f) \Lambda_l \bigr)_{l=j+1}^\infty} \qquad \text{by \eqref{DHKM:LambdaDef}} \\
 \nonumber 
 &
-= \norm[\tau]{ \bigl(\sigma_{j+l}(f) \Lambda_{j+l} \bigr)_{l=1}^\infty}
+= \DHKMnorm[\tau]{ \bigl(\sigma_{j+l}(f) \Lambda_{j+l} \bigr)_{l=1}^\infty}
 \\
-& \le a \sigma_j(f) \norm[\tau]{ \bigl(b^l\Lambda_{j+l} \bigr)_{l=1}^\infty} =:\DHKMERRNj
+& \le a \sigma_j(f) \DHKMnorm[\tau]{ \bigl(b^l\Lambda_{j+l} \bigr)_{l=1}^\infty} =:\DHKMERRNj
  \qquad \text{by \eqref{DHKM:TrackConeDef}.}
@@
 \begin{equation} \label{DHKM:TractConejdagger}
-j^\dagger = \min \left \{j \in \bbN :   \norm[\tau]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}
+j^\dagger = \min \left \{j \in \bbN :   \DHKMnorm[\tau]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}
 \le  \frac{b\varepsilon}{Ra^2}\right\}.
@@
 \begin{align*}
-R &\ge \norm[\calF]{f} = \norm[\rho]{\left(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
- \ge \norm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
+R &\ge \DHKMnorm[\calF]{f} = \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \bbK}}
+ \ge \DHKMnorm[\rho]{\left(\sigma_j(f)\right)_{j=1}^{j^\dagger}}  
  \qquad \text{by \eqref{DHKM:SigmaDef} } \\
 & \ge \sigma_1(f) \ge a^{-1}b^{1-j^\dagger}\sigma_{j^\dagger}(f) \quad \text{by  \eqref{DHKM:TrackConeDef}}\\
-& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \norm[\tau]{ \bigl(b^l \Lambda_{j^\dagger+l} \bigr)_{l=1}^\infty}
+& \ge \sigma_{j^\dagger}(f)\,\frac{Ra}{\varepsilon} \DHKMnorm[\tau]{ \bigl(b^l \Lambda_{j^\dagger+l} \bigr)_{l=1}^\infty}
 \qquad \text{by the definition of } j^\dagger \text{ in \eqref{DHKM:TractConejdagger}} \\
@@
 \begin{equation*}
-    \Lambda_j = \norm[\infty]{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}} = \lambda_{\bsk_{n_02^{j-1}+1}}\le \frac{\norm[p]{\bslambda}}{n_0^{1/p} 2^{(j-1)/p}} \qquad \forall j \in \bbN.
+    \Lambda_j = \DHKMnorm[\infty]{\bigl(\lambda_{\bsk} \bigr)_{\bsk \in \calK_j}} = \lambda_{\bsk_{n_02^{j-1}+1}}\le \frac{\DHKMnorm[p]{\bslambda}}{n_0^{1/p} 2^{(j-1)/p}} \qquad \forall j \in \bbN.
 \end{equation*}
@@
 \begin{align*}
-\norm[\rho]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}^\rho
+\DHKMnorm[\rho]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}^\rho
  & =  \sum_{l=1}^\infty
@@
 & \le \sum_{l=1}^\infty  
- \frac{b^{l\rho} \norm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{(j+l-1)\rho/p}} 
+ \frac{b^{l\rho} \DHKMnorm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{(j+l-1)\rho/p}} 
 =  
- \frac{b^{\rho} \norm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{j\rho/p} (1 - b^{\rho}/2^{\rho/p})}, \\
-\norm[\rho]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}
+ \frac{b^{\rho} \DHKMnorm[p]{\bslambda}^\rho }{ n_0^{\rho/p} 2^{j\rho/p} (1 - b^{\rho}/2^{\rho/p})}, \\
+\DHKMnorm[\rho]{ \bigl(b^{l}\Lambda_{j+l} \bigr)_{l=1}^\infty}
  & \le  
- \frac{b \norm[p]{\bslambda} }{ n_0^{1/p} 2^{j/p} (1 - b^{\rho}/2^{\rho/p})^{1/\rho}}.
+ \frac{b \DHKMnorm[p]{\bslambda} }{ n_0^{1/p} 2^{j/p} (1 - b^{\rho}/2^{\rho/p})^{1/\rho}}.
 \end{align*}
@@
 \begin{align*}
-    \frac{b \norm[p]{\bslambda} }{ n_0^{1/p} 2^{j/p} (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} &\le \frac{b\varepsilon}{R a^2}, \\
-   \left(\frac{ R a^{2} \norm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p & \le n_0 2^{j}.
+    \frac{b \DHKMnorm[p]{\bslambda} }{ n_0^{1/p} 2^{j/p} (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} &\le \frac{b\varepsilon}{R a^2}, \\
+   \left(\frac{ R a^{2} \DHKMnorm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p & \le n_0 2^{j}.
 \end{align*}
@@
 \label{DHKM:thm:TrackConeExUpBd}
-If the elements of $\bslambda$ decay fast enough so that $\norm[p]{\bslambda} < \infty$ and $\rho'=\infty$, then the information cost of Algorithm \ref{DHKM:TrackConeAlg} is bounded above by
+If the elements of $\bslambda$ decay fast enough so that $\DHKMnorm[p]{\bslambda} < \infty$ and $\rho'=\infty$, then the information cost of Algorithm \ref{DHKM:TrackConeAlg} is bounded above by
 \begin{multline*}
@@
     \min \left \{n_0 2^j , \ j \in \N_0 : 
-    n_0 2^j \ge \left(\frac{ R a^{2} \norm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p
+    n_0 2^j \ge \left(\frac{ R a^{2} \DHKMnorm[p]{\bslambda} }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p
     \right\}.
@@
    \le \min \left \{n_0 2^j , \ j \in \N_0 : 
-    n_0 2^j \ge \left(\frac{ R a^{2}\exp\left( \zeta(pr) \norm[p]{\bsw}^p  \right)  }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p \right \}.
+    n_0 2^j \ge \left(\frac{ R a^{2}\exp\left( \zeta(pr) \DHKMnorm[p]{\bsw}^p  \right)  }{\varepsilon (1 - b^{\rho}/2^{\rho/p})^{1/\rho}} \right)^p \right \}.
     \end{multline*}
@@
 \nonumber
-\sigma_j(f_1) & = \norm[\rho]{\biggl(\frac{\DHKMhf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
+\sigma_j(f_1) & = \DHKMnorm[\rho]{\biggl(\frac{\DHKMhf_{1j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}} 
 = c_1 b^j, \qquad j \in \N_0,\\
 \nonumber
-\norm[\calF]{f_1} &= \norm[\rho]{\bigl( \sigma_j(f) \bigr)_{j \in \N_0} } 
+\DHKMnorm[\calF]{f_1} &= \DHKMnorm[\rho]{\bigl( \sigma_j(f) \bigr)_{j \in \N_0} } 
 =  \frac{c_1}{(1 - b^\rho)^{1/\rho}} = \frac{R(a+1)}{2a} \le R,
@@
 c_2 &:= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}, \qquad
-\tLambda_j := \norm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \DHKMtcalK_j}} \le \Lambda_j, \\
-\nonumber
-\sigma_j(f_2) & = \norm[\rho]{\biggl(\frac{\DHKMhf_{2j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \DHKMtcalK_j}} 
+\tLambda_j := \DHKMnorm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \DHKMtcalK_j}} \le \Lambda_j, \\
+\nonumber
+\sigma_j(f_2) & = \DHKMnorm[\rho]{\biggl(\frac{\DHKMhf_{2j}(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \DHKMtcalK_j}} 
 = \begin{cases} c_2 b^j, & \DHKMtcalK_j \ne \emptyset, \\
@@
 \nonumber 
-\norm[\calF]{f_2} &= \norm[\rho]{\bigl( \sigma_j(f_{2}) \bigr)_{j \in \N_0} } 
+\DHKMnorm[\calF]{f_2} &= \DHKMnorm[\rho]{\bigl( \sigma_j(f_{2}) \bigr)_{j \in \N_0} } 
 \le \frac{c_2}{(1 - b^\rho)^{1/\rho}} = \frac{R(a - 1)}{2a}\le R, \\
 \nonumber 
-\norm[\calG]{\DHKMSOL(f_{2j})} &= \sigma_j(f_{2j}) \tLambda_j = 
+\DHKMnorm[\calG]{\DHKMSOL(f_{2j})} &= \sigma_j(f_{2j}) \tLambda_j = 
 c_2 b^{j} \tLambda_j, \qquad j \in \N_0, \\
-\norm[\calG]{\DHKMSOL(f_2)} & = \norm[\tau]{\bigl(c_2 b^{j} \tLambda_j \bigr)_{j \in \N_0}}
-= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}.
+\DHKMnorm[\calG]{\DHKMSOL(f_2)} & = \DHKMnorm[\tau]{\bigl(c_2 b^{j} \tLambda_j \bigr)_{j \in \N_0}}
+= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \DHKMnorm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}.
 \label{DHKM:SOLftwo}
@@
 \nonumber
-\norm[\calF]{f_\pm} &\le \norm[\calF]{f_1} + \norm[\calF]{f_2} \le \frac{c_1 + c_2}{(1 - b^\rho)^{1/\rho}} = R,
+\DHKMnorm[\calF]{f_\pm} &\le \DHKMnorm[\calF]{f_1} + \DHKMnorm[\calF]{f_2} \le \frac{c_1 + c_2}{(1 - b^\rho)^{1/\rho}} = R,
 \\
@@
 \nonumber
-\varepsilon &\ge \max \bigl\{\norm[\calG]{\DHKMSOL(f_+) - \DHKMALG'(f_+,\varepsilon)}, \norm[\calG]{\DHKMSOL(f_-) - \DHKMALG'(f_-,\varepsilon)} \bigr\} \\
-\nonumber
-&\ge \frac 12 \bigl[\norm[\calG]{\DHKMSOL(f_+) - \DHKMALG(f_1,\varepsilon)} + \norm[\calG]{\DHKMSOL(f_-) - \DHKMALG'(f_1,\varepsilon)}  \bigr] \\
+\varepsilon &\ge \max \bigl\{\DHKMnorm[\calG]{\DHKMSOL(f_+) - \DHKMALG'(f_+,\varepsilon)}, \DHKMnorm[\calG]{\DHKMSOL(f_-) - \DHKMALG'(f_-,\varepsilon)} \bigr\} \\
+\nonumber
+&\ge \frac 12 \bigl[\DHKMnorm[\calG]{\DHKMSOL(f_+) - \DHKMALG(f_1,\varepsilon)} + \DHKMnorm[\calG]{\DHKMSOL(f_-) - \DHKMALG'(f_1,\varepsilon)}  \bigr] \\
 \nonumber
@@
 \nonumber
-&\ge \frac 12 \norm[\calG]{\DHKMSOL(f_+) - \DHKMSOL(f_-)} \quad \text{by the triangle inequality}\\
-\nonumber
-&\ge \frac 12 \norm[\calG]{\DHKMSOL(f_+ - f_-)} \quad \text{since $\DHKMSOL$ is linear}\\
-&= \norm[\calG]{\DHKMSOL(f_2)} 
-= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}
+&\ge \frac 12 \DHKMnorm[\calG]{\DHKMSOL(f_+) - \DHKMSOL(f_-)} \quad \text{by the triangle inequality}\\
+\nonumber
+&\ge \frac 12 \DHKMnorm[\calG]{\DHKMSOL(f_+ - f_-)} \quad \text{since $\DHKMSOL$ is linear}\\
+&= \DHKMnorm[\calG]{\DHKMSOL(f_2)} 
+= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \DHKMnorm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}
 \qquad 
@@
     \\
-    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] b^{-\rho l^\star} \norm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}^\rho\, .
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] b^{-\rho l^\star} \DHKMnorm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}^\rho\, .
 \end{align*}
@@
    & = \frac{[1 - (\gamma b)^\tau]^{1/\tau}}{\alpha}
-   \norm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)-1+r} \alpha \gamma^{r-1} \Lambda_{j^\dagger(\varepsilon)} \bigr)_{r=1}^\infty}
+   \DHKMnorm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)-1+r} \alpha \gamma^{r-1} \Lambda_{j^\dagger(\varepsilon)} \bigr)_{r=1}^\infty}
     \\
-    & \ge \frac{[1 - (\gamma b)^\tau]^{1/\tau}}{\alpha}  \norm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)-1+r}\Lambda_{j^\dagger(\varepsilon)-1+r} \bigr)_{r=1}^\infty} \qquad \text{by \eqref{DHKM:LambdaDecayCond}}
+    & \ge \frac{[1 - (\gamma b)^\tau]^{1/\tau}}{\alpha}  \DHKMnorm[\tau]{ \bigl(b^{j^\dagger(\varepsilon)-1+r}\Lambda_{j^\dagger(\varepsilon)-1+r} \bigr)_{r=1}^\infty} \qquad \text{by \eqref{DHKM:LambdaDecayCond}}
     \\
@@
 \end{equation}
-where $\bsw = (w_\ell)_{\ell=1}^d$ is the vector of coordinate weights, $\bss = (s_k)_{k=1}^\infty$ is the vector of smoothness weights,  $\boldsymbol{\Gamma} = (\Gamma_m)_{m=1}^d$ is the vector of \emph{order weights}, and $\norm[0]{\bsk}$ denotes the number of nonzero elements of $\bsk$.
+where $\bsw = (w_\ell)_{\ell=1}^d$ is the vector of coordinate weights, $\bss = (s_k)_{k=1}^\infty$ is the vector of smoothness weights,  $\boldsymbol{\Gamma} = (\Gamma_m)_{m=1}^d$ is the vector of \emph{order weights}, and $\DHKMnorm[0]{\bsk}$ denotes the number of nonzero elements of $\bsk$.
 This is a generalization of the form for $\bslambda$ given by \eqref{DHKM:prodwts}.

### 2019-11-05 DingHickKritzMakRICAMChapVerF.tex
Updates from Overleaf

@@
 \usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
-\algnewcommand\algorithmicparam{\textbf{Parameters:}}
-\algnewcommand\PARAM{\item[\algorithmicparam]}
-\algnewcommand\algorithmicinput{\textbf{Input:}}
-\algnewcommand\INPUT{\item[\algorithmicinput]}
-%\algnewcommand\STATE{\item}
-\algnewcommand\RETURN{\State \textbf{Return }}
+\algnewcommand\DHKMalgorithmicparam{\textbf{Parameters:}}
+\algnewcommand\DHKMPARAM{\item[\DHKMalgorithmicparam]}
+\algnewcommand\DHKMalgorithmicinput{\textbf{Input:}}
+\algnewcommand\DHKMINPUT{\item[\DHKMalgorithmicinput]}
+\algnewcommand\DHKMRETURN{\State \textbf{Return }}
 
@@
 \newcommand{\DHKMnorm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
-%\newcommand{\normnorm}[2][{}]{\ensuremath{\lVert #2 \rVert}_{#1}}
-\newcommand{\bignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
-\newcommand{\Bignorm}[2][{}]{\ensuremath{\Bigl \lVert #2 \Bigr \rVert}_{#1}}
-\newcommand{\biggnorm}[2][{}]{\ensuremath{\biggl \lVert #2 \biggr \rVert}_{#1}}
-\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
-\newcommand{\FredNote}[1]{{\color{blue}Fred: #1}}
-\newcommand{\YuhanNote}[1]{{\color{magenta}Yuhan: #1}}
-\newcommand{\PeterNote}[1]{{\color{orange}Peter: #1}}
-\newcommand{\SimonNote}[1]{{\color{purple}Simon: #1}}
-\newcommand{\DHKMchange}[1]{{\color{red}{#1}}}
-
-\newcommand{\tLambda}{\widetilde{\Lambda}}
-\newcommand{\bcalK}{\bar{\calK}}
-\newcommand{\fapp}{f_{\text{app}}}
+\newcommand{\DHKMbignorm}[2][{}]{\ensuremath{\bigl \lVert #2 \bigr \rVert}_{#1}}
+\newcommand{\DHKMbiggnorm}[2][{}]{\ensuremath{\biggl \lVert #2 \biggr \rVert}_{#1}}
+\newcommand{\DHKMbcalK}{\bar{\calK}}
+\newcommand{\DHKMfapp}{f_{\text{app}}}
+\newcommand{\DHKMtLambda}{\Tilde{\Lambda}}
+%\newcommand{\FredNote}[1]{{\color{blue}Fred: #1}}
+%\newcommand{\YuhanNote}[1]{{\color{magenta}Yuhan: #1}}
+%\newcommand{\PeterNote}[1]{{\color{orange}Peter: #1}}
+%\newcommand{\SimonNote}[1]{{\color{purple}Simon: #1}}
+%\newcommand{\DHKMchange}[1]{{\color{red}{#1}}}
 %\newcommand{\HickernellFJ}{Hickernell}
@@
 so $\tau \le \rho' \le \infty$.
-Let $\Lambda :=  \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$ be the norm of a subset of the weights.
+Let $\Lambda :=  \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}$ be the norm of a subset of the weights.
 Then the following are true for $f = \sum_{\bsk \in \calK} \DHKMhf(\bsk) u_{\bsk}$:
@@
     \DHKMnorm[\calG]{\DHKMSOL(f)}  
-    & = \biggnorm[\calG]{\sum_{\bsk \in \calK} \DHKMhf(\bsk) v_{\bsk}} = \DHKMnorm[\tau]{\bigl(  \DHKMhf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
-    \nonumber
-    & \le \biggnorm[\rho]{\biggl(  \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \DHKMnorm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
+    & = \DHKMbiggnorm[\calG]{\sum_{\bsk \in \calK} \DHKMhf(\bsk) v_{\bsk}} = \DHKMnorm[\tau]{\bigl(  \DHKMhf(\bsk)  \bigr)_{\bsk \in \calK}}  = \left [\sum_{\bsk \in \calK}  \left\lvert\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right\rvert^{\tau} \lambda_{\bsk}^{\tau} \right]^{1/\tau} \\
+    \nonumber
+    & \le \DHKMbiggnorm[\rho]{\biggl(  \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}}  \biggr)_{\bsk \in \calK}} \, \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}} = \DHKMnorm[\calF]{f} \, \Lambda \qquad \text{since }\frac 1\rho + \frac 1 {\rho'} = \frac 1 \tau.
 \end{align}
@@
        \DHKMnorm[\calG]{\DHKMSOL(f)}  
-    =  \frac{R \bignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\Lambda^{\rho'/\rho}} 
-    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
+    =  \frac{R \DHKMbignorm[\tau]{\bigl(  \lambda_{\bsk}^{\rho'/\rho + 1}  \bigr)_{\bsk \in \calK}}} {\Lambda^{\rho'/\rho}} 
+    = \frac{R \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho + 1}}
     {\Lambda^{\rho'/\rho}} = R \Lambda.
@@
     = \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \right)_{\bsk \in \calK}}
-    = \frac{R \bignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\Lambda^{\rho'/\rho}} 
-    = \frac{R \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
+    = \frac{R \DHKMbignorm[\rho]{\bigl(  \lambda_{\bsk}^{\rho'/\rho}  \bigr)_{\bsk \in \calK}}}{\Lambda^{\rho'/\rho}} 
+    = \frac{R \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK}}^{\rho'/\rho}}
     {\Lambda^{\rho'/\rho}} = R.
@@
 \begin{equation} \label{DHKM:SOLNorm}
-    \DHKMnorm[\calF \to \calG]{\DHKMSOL}  = \sup_{\DHKMnorm[\calF]{f} \le 1} \DHKMnorm[\calG]{\DHKMSOL(f)} = \bignorm[\rho']{\bslambda}.
+    \DHKMnorm[\calF \to \calG]{\DHKMSOL}  = \sup_{\DHKMnorm[\calF]{f} \le 1} \DHKMnorm[\calG]{\DHKMSOL(f)} = \DHKMbignorm[\rho']{\bslambda}.
 \end{equation}
@@
 \begin{equation} \label{DHKM:SOLNormFinite}
-    \bignorm[\rho']{\bslambda} < \infty.
+    \DHKMbignorm[\rho']{\bslambda} < \infty.
 \end{equation}
@@
     \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n) } \le \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=n+1}^\infty}
-    \bignorm[\rho']{\bslambda^{(n+1)}}, \\
+    \DHKMbignorm[\rho']{\bslambda^{(n+1)}}, \\
     \intertext{where the tail of $\bslambda$ is defined by}
@@
 \begin{equation} \label{DHKM:APP_errorBd}
-    \sup_{f \in \calB_R} \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le R \, \bignorm[\rho']{\bslambda^{(n+1)}}.
+    \sup_{f \in \calB_R} \DHKMnorm[\calG]{\DHKMSOL(f) - \DHKMAPP(f,n)}  \le R \, \DHKMbignorm[\rho']{\bslambda^{(n+1)}}.
 \end{equation}
@@
 	\begin{algorithmic}
-	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; the ball radius, $R$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_errorBd}
-	\INPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$
+	\DHKMPARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; the ball radius, $R$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_errorBd}
+	\DHKMINPUT a black-box function, $f$; an absolute error tolerance, $\varepsilon>0$
 
@@
 
-    \State Choose $n^* =  \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}$
-
-    \RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n^*)$
+    \State Choose $n^* =  \min \left \{n \in \N_0 : \DHKMbignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}$
+
+    \DHKMRETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n^*)$
 \end{algorithmic}
@@
 \[
-\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \bignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}, \qquad R’ \in (0, R].
+\DHKMCOST(\DHKMALG, \calB_R, \varepsilon,R') = \min \left \{n \in \N_0 : \DHKMbignorm[\rho']{\bslambda^{(n+1)}} \le \varepsilon /R \right \}, \qquad R’ \in (0, R].
 \]
@@
     \left[ A^\rho \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}}^\rho -  \DHKMnorm[\rho]{\left(\frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}}\right)_{i=1}^n}^\rho \right]^{1/\rho}
-    \, \bignorm[\rho']{\bslambda^{(n+1)}} , 
+    \, \DHKMbignorm[\rho']{\bslambda^{(n+1)}} , 
     \\ \forall n \ge n_1.
@@
 \end{subequations}
-This error bound decays as $\bignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
+This error bound decays as $\DHKMbignorm[\rho]{\bigl( f(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^n}$ increases and as the tail norm of the $\lambda_{\bsk_i}$ decreases.
 This data-driven error bound underlies  Algorithm \ref{DHKM:PilotConeAlg}, which is successful for the cone of input functions, $\calC_{\boldsymbol{\lambda},n_1,A}$, defined in \eqref{DHKM:pilot_cone}:
 
-\begin{algorithm}
+\begin{algorithm}[H]
 	\caption{$\DHKMALG$ Based on a Pilot Sample\label{DHKM:PilotConeAlg}} 
 	\begin{algorithmic}
-	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
-		\INPUT a black-box function, $f$; an absolute error tolerance,
+	\DHKMPARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; an initial sample size, $n_1 \in \N$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
+		\DHKMINPUT a black-box function, $f$; an absolute error tolerance,
 		$\varepsilon>0$
@@
 
-\RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n)$
+\DHKMRETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n)$
 
@@
     \DHKMCOST(\DHKMALG,\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \\
-    = \min \left \{n \ge n_1 : \bignorm[\rho']{\bslambda^{(n+1)}} \,
+    = \min \left \{n \ge n_1 : \DHKMbignorm[\rho']{\bslambda^{(n+1)}} \,
     \le \varepsilon/[(A^\rho -1)^{1/\rho}R] \right \}.
@@
 \begin{multline} \label{DHKM:PilotConeAlg_comp}
-        \DHKMCOMP(\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \ge \min \left \{n \ge n_1 : \bignorm[\rho']{\bslambda^{(n+1)}} \,
+        \DHKMCOMP(\calC_{\boldsymbol{\lambda},n_1,A},\varepsilon,R) \ge \min \left \{n \ge n_1 : \DHKMbignorm[\rho']{\bslambda^{(n+1)}} \,
     \le 2\varepsilon/[(1 - 1/A) R] \right \} \\
@@
      (A^\rho -1)^{1/\rho} \DHKMnorm[\rho]{\left( \frac{\DHKMhf(\bsk_i)}{\lambda_{\bsk_i}} \right)_{i=1}^{n_1}} \, 
-     \bignorm[\rho']{\bslambda^{(n+1)}}
+     \DHKMbignorm[\rho']{\bslambda^{(n+1)}}
     \le \varepsilon \right \} \\   
      & \le \min \left \{n \ge n_1 : 
-     (A^\rho -1)^{1/\rho} R \,\bignorm[\rho']{\bslambda^{(n+1)}}
+     (A^\rho -1)^{1/\rho} R \,\DHKMbignorm[\rho']{\bslambda^{(n+1)}}
     \le \varepsilon \right \},  
 \end{align*}
-since $\bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \bignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \DHKMnorm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
+since $\DHKMbignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n_1}} \le \DHKMbignorm[\rho]{\bigl( \DHKMhf(\bsk_i)/\lambda_{\bsk_i} \bigr)_{i=1}^{n}} \le  \DHKMnorm[\calF]{f} \le R$ for all $f \in \calB_R$, $n \ge n_1$.
 Moreover, this inequality is tight for some $f \in \calC_{\boldsymbol{\lambda},n_1,A} \cap \calB_{R}$, namely, those certain $f$ for which $\DHKMhf(\bsk_i) = 0$ for $i > n_1$.
@@
 \[
-\bignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n_1+1}^{\infty}} \,
+\DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk_i}  \bigr)_{i = n_1+1}^{\infty}} \,
     > 2\varepsilon_{\max}/[(1 - 1/A) R_{\min}].
@@
 \begin{equation*}
-    \DHKMbigabs{\DHKMhf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
+    \DHKMbigabs{\DHKMhf_1(\bsk)} = \begin{cases} \displaystyle \frac{R (1+1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \in \calK_1}}^{\rho'/\rho}}, &  \bsk \in \calK_1, \\
     0, & \bsk \notin \calK_1,
@@
 \nonumber
-    \DHKMbigabs{\DHKMhf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
+    \DHKMbigabs{\DHKMhf_2(\bsk)} = \begin{cases} \displaystyle \frac{R (1-1/A) \lambda_{\bsk}^{\rho'/\rho + 1}}{2\DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}^{\rho'/\rho}}, &  \bsk \notin \calJ, \\
     0, & \bsk \in \calJ, 
@@
     \label{DHKM:SOLf2bd}
-    \DHKMnorm[\calG]{\DHKMSOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
+    \DHKMnorm[\calG]{\DHKMSOL(f_2)} = \frac{R(1 - 1/A)}{2} \, \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}}.
 \end{gather}
@@
 & \ge \frac 12 \DHKMnorm[\calG]{\DHKMSOL(f_+ - f_-)} = \DHKMnorm[\calG]{\DHKMSOL(f_2)} 
-=\frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
-& \ge \frac{R(1 - 1/A)}{2} \, \bignorm[\rho']{\bslambda^{(n+1)}} ,
+=\frac{R(1 - 1/A)}{2} \, \DHKMbignorm[\rho']{\bigl(  \lambda_{\bsk}  \bigr)_{\bsk \notin \calJ}} \qquad \text{by \eqref{DHKM:SOLf2bd}} \\
+& \ge \frac{R(1 - 1/A)}{2} \, \DHKMbignorm[\rho']{\bslambda^{(n+1)}} ,
 \end{align*}
@@
 We now derive upper and lower bounds on the information costs of Algorithms \ref{DHKM:BallAlg} and \ref{DHKM:PilotConeAlg} for the case  $\rho = \tau$ and $\rho' = \infty$, which includes the example introduced in Section \ref{DHKM:secexamp}.
-For $\rho'=\infty$, $\bignorm[\rho']{\bslambda^{(n+1)}} = \lambda_{\bsk_{n+1}}$.
+For $\rho'=\infty$, $\DHKMbignorm[\rho']{\bslambda^{(n+1)}} = \lambda_{\bsk_{n+1}}$.
 To facilitate these bounds we establish a couple of common lemmas.
@@
 \lambda_{\bsk_{n+1}} \le \frac{\DHKMnorm[p]{\bslambda}}{n^{1/p}} \ \ \text{and} \ \ 
- \sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} \ge \frac{\bignorm[p\eta]{\bslambda^{(n_{\min})}}}{\zeta(\eta)^{1/(p\eta)}} \quad \forall p>0, \ \eta > 1, \ n_{\min} \in \bbN.
+ \sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} \ge \frac{\DHKMbignorm[p\eta]{\bslambda^{(n_{\min})}}}{\zeta(\eta)^{1/(p\eta)}} \quad \forall p>0, \ \eta > 1, \ n_{\min} \in \bbN.
 \]
@@
 \begin{equation*}
-    \bignorm[p\eta]{\bslambda^{(n_{\min})}}^{p\eta} 
+    \DHKMbignorm[p\eta]{\bslambda^{(n_{\min})}}^{p\eta} 
     = \sum_{n=n_{\min}}^\infty \frac{\lambda_{\bsk_n}^{p\eta} n^\eta }{n^\eta} 
@@
 where $\zeta$ is the Riemann zeta function.  The proof is completed by taking the $p\eta^{\text{th}}$ root and rearranging the terms.
-\end{proof}
-
-\bigskip
+\end{proof} \
 
@@
 We give the proof for Algorithm \ref{DHKM:PilotConeAlg}, which is similar to the proof for Algorithm \ref{DHKM:BallAlg}.
-Recall that for $\rho'=\infty$, $\bignorm[\rho']{\bslambda^{(n+1)}} = \lambda_{\bsk_{n+1}}$.
+Recall that for $\rho'=\infty$, $\DHKMbignorm[\rho']{\bslambda^{(n+1)}} = \lambda_{\bsk_{n+1}}$.
 From \eqref{DHKM:PilotConeAlg_cost} it follows that the information cost for  Algorithm \ref{DHKM:PilotConeAlg} is
@@
     \begin{align*}
-       \bignorm[p\eta]{\bslambda^{(n_{\min})}}  
+       \DHKMbignorm[p\eta]{\bslambda^{(n_{\min})}}  
        &\le  \zeta(\eta)^{1/(p\eta)} \sup_{n \ge n_{\min}} \lambda_{\bsk_{n}} n^{1/p} \\
@@
     \end{align*}
-    Since $\bignorm[p\eta]{\bslambda^{(n_{\min})}}$ is finite, it follows that $\bignorm[p\eta]{\bslambda}$ is finite.
-\end{proof}
-
-\bigskip
+    Since $\DHKMbignorm[p\eta]{\bslambda^{(n_{\min})}}$ is finite, it follows that $\DHKMbignorm[p\eta]{\bslambda}$ is finite.
+\end{proof} \
 
@@
 Again, taking the $p^{\text{th}}$ root completes the proof for general $\bss$.  
-\end{proof}
-
-\bigskip
+\end{proof} \
 
@@
 % \[
-% n_{\DHKMCOMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
+% n_{\DHKMCOMP}(\delta,d) :=\min \left \{n\ge 0: \DHKMbignorm[\rho']{\bigl(  \lambda_{d,\bsk_i}  \bigr)_{i = n+1}^{\infty}} \,
 %     \le \delta \right \} \qquad \forall \delta > 0.
@@
 \[
-n_{\DHKMCOMP}(\delta,d) :=\min \left \{n\ge 0: \bignorm[\rho']{\bslambda^{(n+1)}_d} \,
+n_{\DHKMCOMP}(\delta,d) :=\min \left \{n\ge 0: \DHKMbignorm[\rho']{\bslambda^{(n+1)}_d} \,
     \le \delta \right \} \qquad \forall \delta > 0,
@@
  \begin{equation}\label{DHKM:eq:condspt}
-    \sup_{d\in\NN} \, \bignorm[p]{\bslambda_d^{(i_0)}} < \infty.
+    \sup_{d\in\NN} \, \DHKMbignorm[p]{\bslambda_d^{(i_0)}} < \infty.
  \end{equation}
@@
  \[
-    \sup_{d\in\NN} d^{-p_1}\, \bignorm[p_3]{\bslambda_d^{(\lceil K d^{p_2} \rceil)}} < \infty.
+    \sup_{d\in\NN} d^{-p_1}\, \DHKMbignorm[p_3]{\bslambda_d^{(\lceil K d^{p_2} \rceil)}} < \infty.
  \]
@@
     n_{\DHKMCOMP}(\varepsilon/R,d) &=\min \left \{n\ge 0\colon 
-\bignorm[\rho']{\bslambda_d^{(n+1)}}^{\rho'}\,
+\DHKMbignorm[\rho']{\bslambda_d^{(n+1)}}^{\rho'}\,
     \le (\varepsilon/R)^{\rho'} \right \} \\
@@
     & =\min \left \{n\ge 0\colon 
-\bignorm[1]{\widetilde{\bslambda}_d^{(n+1)}}\,
+\DHKMbignorm[1]{\widetilde{\bslambda}_d^{(n+1)}}\,
     \le \widetilde{\varepsilon}^{\,2} \right \}.
@@
  \begin{equation}\label{DHKM:eq:condspt1}
-    \sup_{d\in\NN} \bignorm[\rho' p]{\bslambda_d^{(i_0)}} < \infty.
+    \sup_{d\in\NN} \DHKMbignorm[\rho' p]{\bslambda_d^{(i_0)}} < \infty.
  \end{equation}
@@
   \[
-    \sup_{d\in\NN} d^{-p_1}\, \bignorm[\rho' p_3]{\bslambda_d^{(\lceil K d^{p_2} \rceil)}} < \infty.
+    \sup_{d\in\NN} d^{-p_1}\, \DHKMbignorm[\rho' p_3]{\bslambda_d^{(\lceil K d^{p_2} \rceil)}} < \infty.
  \]
@@
  \[
-   \lim_{n\to\infty} (\log n)^2  \, \bignorm[1]{\bslambda_d^{(n)}} =0\quad\mbox{for all $d$},
+   \lim_{n\to\infty} (\log n)^2  \, \DHKMbignorm[1]{\bslambda_d^{(n)}} =0\quad\mbox{for all $d$},
  \]
@@
   \sup_{\beta\in (0,1/2]}\, \beta^{-2} \,
-  \sup_{d\ge f(\beta)}\,\, \sup_{n \ge \lceil \exp (d\sqrt{b}) \rceil +1}\, \, (\log n)^2  \, \bignorm[1]{\bslambda_d^{(n)}} 
+  \sup_{d\ge f(\beta)}\,\, \sup_{n \ge \lceil \exp (d\sqrt{b}) \rceil +1}\, \, (\log n)^2  \, \DHKMbignorm[1]{\bslambda_d^{(n)}} 
   < \infty.
@@
   The proof of the theorem is similar to that of Theorem \ref{DHKM:thmtract1}, using \eqref{DHKM:eqaveragetract}.
-\end{proof}
+\end{proof} \ 
 \begin{remark}
@@
 as in \eqref{DHKM:prodwts}  one more time. We note that
-$\bignorm[p]{\bslambda_d^{(i_0)}}^p<\infty$ holds if and only if  $\bignorm[p]{\bslambda_d}^p<\infty$.
+$\DHKMbignorm[p]{\bslambda_d^{(i_0)}}^p<\infty$ holds if and only if  $\DHKMbignorm[p]{\bslambda_d}^p<\infty$.
 We denote the $d$-dependence of the vector of coordinate weights by writing $\bsw_d:=(w_1, \ldots, w_d)$ and $\bsw_\infty = (w_1, w_2, \ldots)$.
@@
 Note that in the setting of this example, the term 
-$\bignorm[p]{\bslambda_d}^p$
+$\DHKMbignorm[p]{\bslambda_d}^p$
 %$\sum_{i=1}^{\infty}\lambda_{d, \bsk_{i}}^{\eta}$ 
@@
 \begin{equation} \label{DHKM:NormLambdaFinite}
-    \DHKMnorm[\calF \to \calG]{\DHKMSOL} = \bignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
+    \DHKMnorm[\calF \to \calG]{\DHKMSOL} = \DHKMbignorm[\rho']{\bigl(\Lambda_j \bigr)_{j \in \N_0}} < \infty.
 \end{equation}
@@
 \begin{align*}
-    \DHKMnorm[\calF]{f} & = \DHKMnorm[\rho]{\Biggl(\,\DHKMnorm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \bignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
-    & \le \bignorm[\rho]{\bigl(\sigma_1(f), ab \sigma_1(f), ab^2 \sigma_1(f), \ldots \bigr)} \\
+    \DHKMnorm[\calF]{f} & = \DHKMnorm[\rho]{\Biggl(\,\DHKMnorm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_j}}\,\Biggr)_{j \in \N}} = \DHKMbignorm[\rho]{\bigl(\sigma_j(f) \bigr)_{j \in \N}} \\
+    & \le \DHKMbignorm[\rho]{\bigl(\sigma_1(f), ab \sigma_1(f), ab^2 \sigma_1(f), \ldots \bigr)} \\
     & = \left(1 + \frac{a^\rho b^\rho}{1 - b^\rho} \right)^{1/\rho}  \DHKMnorm[\rho]{\biggl(\frac{\DHKMhf(\bsk)}{\lambda_{\bsk}} \biggr)_{\bsk \in \calK_1}}.
@@
 
-\begin{algorithm}
-	\caption{Adaptive ALG for a Cone of Input Functions Tracking the Series Coefficient Decay Rate \label{DHKM:TrackConeAlg}}
-	\begin{algorithmic}
-	\PARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0}$; an inflation factor, $a$; the general decay rate, $b$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_Err_Coef}
-		\INPUT a black-box function, $f$; an absolute error tolerance,
-		$\varepsilon>0$
-
-\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:TrackConeDef}
-
-\State Let $j \leftarrow 0$
-\Repeat
-
-\State Let $j \leftarrow j + 1$
-
-\State Compute $\DHKMERRNj$ as defined in \eqref{DHKM:algoineq}
-
-\Until $\DHKMERRNj \le \varepsilon$
-
-\RETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n_{j})$
-\end{algorithmic}
-\end{algorithm}
-
 \begin{theorem}\label{DHKM:TrackConeCompCost}
@@
 \end{theorem}
+
+\begin{algorithm}[H]
+	\caption{Adaptive ALG for a Cone of Input Functions Tracking the Series Coefficient Decay Rate \label{DHKM:TrackConeAlg}}
+	\begin{algorithmic}
+	\DHKMPARAM the Banach spaces $\calF$ and $\calG$, including the weights $\bslambda$; a strictly increasing sequence of non-negative integers, $(n_j)_{j\ge 0}$; an inflation factor, $a$; the general decay rate, $b$; $\DHKMAPP$ satisfying \eqref{DHKM:APP_Err_Coef}
+		\DHKMINPUT a black-box function, $f$; an absolute error tolerance,
+		$\varepsilon>0$
+
+\Ensure Error criterion \eqref{DHKM:err_crit} for  the cone defined in \eqref{DHKM:TrackConeDef}
+
+\State Let $j \leftarrow 0$
+\Repeat
+
+\State Let $j \leftarrow j + 1$
+
+\State Compute $\DHKMERRNj$ as defined in \eqref{DHKM:algoineq}
+
+\Until $\DHKMERRNj \le \varepsilon$
+
+\DHKMRETURN $\DHKMALG(f,\varepsilon) = \DHKMAPP(f,n_{j})$
+\end{algorithmic}
+\end{algorithm}
 
@@
 From this last inequality, it follows that $j^\dagger \ge j^*$.
-\end{proof}
+\end{proof} \
 
@@
 \displaystyle
-\frac{c_2 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\tLambda_j^{\rho'/\rho}},  
+\frac{c_2 b^{j} \lambda_{\bsk}^{\rho'/\rho+1}}{\DHKMtLambda_j^{\rho'/\rho}},  
 & \bsk \in \DHKMtcalK_j,
@@
 c_2 &:= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a}, \qquad
-\tLambda_j := \DHKMnorm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \DHKMtcalK_j}} \le \Lambda_j, \\
+\DHKMtLambda_j := \DHKMnorm[\rho']{\bigl(\lambda_\bsk \bigr)_{\bsk \in \DHKMtcalK_j}} \le \Lambda_j, \\
 \nonumber
@@
 \nonumber 
-\DHKMnorm[\calG]{\DHKMSOL(f_{2j})} &= \sigma_j(f_{2j}) \tLambda_j = 
-c_2 b^{j} \tLambda_j, \qquad j \in \N_0, \\
-\DHKMnorm[\calG]{\DHKMSOL(f_2)} & = \DHKMnorm[\tau]{\bigl(c_2 b^{j} \tLambda_j \bigr)_{j \in \N_0}}
-= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \DHKMnorm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}.
+\DHKMnorm[\calG]{\DHKMSOL(f_{2j})} &= \sigma_j(f_{2j}) \DHKMtLambda_j = 
+c_2 b^{j} \DHKMtLambda_j, \qquad j \in \N_0, \\
+\DHKMnorm[\calG]{\DHKMSOL(f_2)} & = \DHKMnorm[\tau]{\bigl(c_2 b^{j} \DHKMtLambda_j \bigr)_{j \in \N_0}}
+= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \DHKMnorm[\tau]{\bigl(b^{j} \DHKMtLambda_j \bigr)_{j \in \N_0}}.
 \label{DHKM:SOLftwo}
@@
 &= \DHKMnorm[\calG]{\DHKMSOL(f_2)} 
-= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \DHKMnorm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}
+= \frac{R(a-1)(1 - b^\rho)^{1/\rho}}{2a} \DHKMnorm[\tau]{\bigl(b^{j} \DHKMtLambda_j \bigr)_{j \in \N_0}}
 \qquad 
@@
 Then by condition \eqref{DHKM:PropCond}, there exists an $l^\star \le j^\star+1$ where $\DHKMcard(\DHKMtcalK_{l^\star}) \ge S_2 \DHKMcard(\calK_{l^\star})$.
-This implies a lower bound on $\tLambda_{l^\star}$.
+This implies a lower bound on $\DHKMtLambda_{l^\star}$.
 Let $m = n_{l^\star} - n_{l^\star-1} = \DHKMcard(\calK_{l^\star})$.
@@
 \begin{align*}
-    \Lambda_{l^\star}^\rho & = \sum_{i \in \calK_{l^\star}} \lambda_{\bsk_i}^{\rho} =  \tLambda_{l^\star}^\rho + \sum_{i \in \calK_{l^\star} \setminus \DHKMtcalK_{l^\star}} \lambda_{\bsk_i}^{\rho}
+    \Lambda_{l^\star}^\rho & = \sum_{i \in \calK_{l^\star}} \lambda_{\bsk_i}^{\rho} =  \DHKMtLambda_{l^\star}^\rho + \sum_{i \in \calK_{l^\star} \setminus \DHKMtcalK_{l^\star}} \lambda_{\bsk_i}^{\rho}
     \\
-    &\le  \tLambda_{l^\star}^\rho + m_{\DHKMout} \lambda_{\bsk_{n_{l^\star -1}+1}}^\rho \qquad \text{by the ordering of the } \lambda_{\bsk_i}\\
-    &\le  \tLambda_{l^\star}^\rho + m_{\DHKMout} S_1^\rho \lambda_{\bsk_{n_{l^\star}}}^\rho \qquad \text{by \eqref{DHKM:MinMaxCond}}\\
-    & \le \tLambda_{l^\star}^\rho + \frac{m_{\DHKMout}}{m_{\DHKMinc}} S_1^\rho \tLambda_{l^\star}^\rho \qquad \text{by the definition of } \tLambda_{l^\star}\\
-    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] \tLambda_{l^\star}^\rho \qquad \text{by the bounds on } m_{\DHKMinc} \text{ and } m_{\DHKMout} 
+    &\le  \DHKMtLambda_{l^\star}^\rho + m_{\DHKMout} \lambda_{\bsk_{n_{l^\star -1}+1}}^\rho \qquad \text{by the ordering of the } \lambda_{\bsk_i}\\
+    &\le  \DHKMtLambda_{l^\star}^\rho + m_{\DHKMout} S_1^\rho \lambda_{\bsk_{n_{l^\star}}}^\rho \qquad \text{by \eqref{DHKM:MinMaxCond}}\\
+    & \le \DHKMtLambda_{l^\star}^\rho + \frac{m_{\DHKMout}}{m_{\DHKMinc}} S_1^\rho \DHKMtLambda_{l^\star}^\rho \qquad \text{by the definition of } \DHKMtLambda_{l^\star}\\
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] \DHKMtLambda_{l^\star}^\rho \qquad \text{by the bounds on } m_{\DHKMinc} \text{ and } m_{\DHKMout} 
     \\
-    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] b^{-\rho l^\star} \DHKMnorm[\tau]{\bigl(b^{j} \tLambda_j \bigr)_{j \in \N_0}}^\rho\, .
+    & \le \left[1 + \left(\frac 1 {S_2} -1 \right) S_1^\rho \right] b^{-\rho l^\star} \DHKMnorm[\tau]{\bigl(b^{j} \DHKMtLambda_j \bigr)_{j \in \N_0}}^\rho\, .
 \end{align*}
@@
 This completes the proof.
-\end{proof}
+\end{proof} \
 
@@
 This, however, implies that all sufficient conditions in Theorem \ref{DHKM:thmtract1} are also sufficient in the case considered in Theorem \ref{DHKM:thmtract3}.
-\end{proof}
+\end{proof} \
 
@@
 \begin{equation} \label{DHKM:barKdef}
-    \bcalK= \{ (0, \ldots, 0, k, 0, \ldots, 0): k = 0, \ldots, k_{\max}\},
+    \DHKMbcalK= \{ (0, \ldots, 0, k, 0, \ldots, 0): k = 0, \ldots, k_{\max}\},
 \end{equation}
@@
 \begin{equation*}
-    \fapp = \sum_{\bsk \in \bar{\calK}} \DHKMhf(\bsk) u_{\bsk}.
+    \DHKMfapp = \sum_{\bsk \in \bar{\calK}} \DHKMhf(\bsk) u_{\bsk}.
 \end{equation*}
@@
 The candidate sets $\calW$ and $\calS$ should be constructed such that the coordinate and smoothness weights have a priori upper bounds.
-Otherwise the inner minimization would choose huge values for $\bsw$ and $\bss$ to maximize the $\lambda_{\bsk}(\bsw,\bss,\bsGamma)$ and minimize the norm of $\fapp$.
+Otherwise the inner minimization would choose huge values for $\bsw$ and $\bss$ to maximize the $\lambda_{\bsk}(\bsw,\bss,\bsGamma)$ and minimize the norm of $\DHKMfapp$.
 The cardinality of the initial set of wavenumbers is $d k_{\max} + 1$.
@@
 In practice, we iteratively optimize over $\bsw$ and then $\bss$ until convergence is reached.
-At each step of the iteration $\|(\hat{f}(\bsk)/\lambda_{\bsk})_{\bsk \in \bcalK}\|_{\rho}$ decreases.
+At each step of the iteration $\|(\hat{f}(\bsk)/\lambda_{\bsk})_{\bsk \in \DHKMbcalK}\|_{\rho}$ decreases.
 
@@
 	\begin{algorithmic}
-	\PARAM the bases $\{u_{\bsk}\}_{\bsk \in \N_0^d}$ and $\{v_{\bsk}\}_{\bsk \in \N_0^d}$; candidate sets $\calW$ and $\calS$ for product and smoothness weights; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
-		\INPUT a black-box function, $f$; an absolute error tolerance,
+	\DHKMPARAM the bases $\{u_{\bsk}\}_{\bsk \in \N_0^d}$ and $\{v_{\bsk}\}_{\bsk \in \N_0^d}$; candidate sets $\calW$ and $\calS$ for product and smoothness weights; maximum smoothness degree, $k_{\max}$; order weights, $\boldsymbol{\Gamma}$; an inflation factor, $A > 1$; $\DHKMAPP$ satisfying \eqref{DHKM:Refined_APP_err}
+		\DHKMINPUT a black-box function, $f$; an absolute error tolerance,
 		$\varepsilon>0$
@@
 \Ensure Error criterion \eqref{DHKM:err_crit} for the cone defined in \eqref{DHKM:pilot_cone2}
-\State  Define the initial set of wavenumbers $\bcalK$ defined in \eqref{DHKM:barKdef}
-\State Evaluate initial sample $\bigl\{\DHKMhf(\bsk)\bigr\}_{\bsk \in \bcalK}$
+\State  Define the initial set of wavenumbers $\DHKMbcalK$ defined in \eqref{DHKM:barKdef}
+\State Evaluate initial sample $\bigl\{\DHKMhf(\bsk)\bigr\}_{\bsk \in \DHKMbcalK}$
 \State Compute data-driven POSD weight $\bar{\bslambda}$, by iteratively optimizing over $(\bsw, \bss) \in \calW \times \calS$ in \eqref{DHKM:eq:inf} until convergence
 \State Using these weights, $\bar{\bslambda}$, perform Algorithm \ref{DHKM:PilotConeAlg} to obtain $\DHKMALG(f,\varepsilon)$
-\RETURN $\DHKMALG(f,\varepsilon)$
+\DHKMRETURN $\DHKMALG(f,\varepsilon)$
 \end{algorithmic}
@@
 
-Figures \ref{fig:four} (a) and (b) display the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error to tolerance ratio, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$, in $d=4$ and $d=7$ dimensions, respectively.
-Each data point corresponds to a different error tolerance $\varepsilon$.
-A ratio $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
-For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$.
-This shows that our adaptive approximation algorithm works reasonably well.
-It appears slightly more effective in lower dimensions  than in higher dimensions.
-A likely reason is that the underlying POSD structure can be more easily learned from a small pilot sample in lower dimensions than in higher dimensions.
-
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 
+Figures \ref{fig:four} (a) and (b) display the total required sample size from Algorithm \ref{DHKM:InfPilotConeAlg}, as a function of the error to tolerance ratio, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$, in $d=4$ and $d=7$ dimensions, respectively.
+Each data point corresponds to a different error tolerance $\varepsilon$.
+A ratio $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
+For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$.
+This shows that our adaptive approximation algorithm works reasonably well.
+It appears slightly more effective in lower dimensions  than in higher dimensions.
+A likely reason is that the underlying POSD structure can be more easily learned from a small pilot sample in lower dimensions than in higher dimensions.
+
 \begin{acknowledgement}

### 2020-01-25 Intro_Radon_Series_IBC_200102.tex
Add Intro

\documentclass[11pt,a4paper]{article}
\usepackage{latexsym,amsfonts,amsmath,graphics}
\usepackage{epsfig}
\usepackage[notref,notcite]{showkeys}
%\usepackage[active]{srcltx}
\usepackage{enumitem}
\usepackage{mathrsfs}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

\setlength{\textheight}{24cm} \setlength{\textwidth}{16cm}
\setlength{\hoffset}{-1.3cm} \setlength{\voffset}{-1.8cm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{proposition}{Proposition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{definition}{Definition}
\newtheorem{algorithm}{Algorithm}
\newtheorem{remark}{Remark}
\newenvironment{proof}{\begin{trivlist}
\item[\hskip\labelsep{\it Proof.}]}{$\hfill\Box$\end{trivlist}}

\newcommand{\norm}[1]{\left\Vert#1\right\Vert}
\newcommand{\To}{\rightarrow}
\newcommand{\Ref}[1] {\textup{(\ref{#1})}}
\newcommand{\satop}[2]{\stackrel{\scriptstyle{#1}}{\scriptstyle{#2}}}
\newcommand{\sump}{\mathop{{\sum}'}}
\newcommand{\bsDelta}{\boldsymbol{\Delta}}
\newcommand{\bsa}{\boldsymbol{a}}
\newcommand{\bsbeta}{\boldsymbol{\beta}}
\newcommand{\bsgamma}{\boldsymbol{\gamma}}
\newcommand{\bseta}{\boldsymbol{\eta}}
\newcommand{\bsalpha}{\boldsymbol{\alpha}}
\newcommand{\bslambda}{\boldsymbol{\lambda}}
\newcommand{\bsnu}{\boldsymbol{\nu}}
\newcommand{\bsmu}{\boldsymbol{\mu}}
\newcommand{\bsk}{\boldsymbol{k}}
\newcommand{\bsl}{\boldsymbol{l}}
\newcommand{\bsv}{\boldsymbol{v}}
\newcommand{\bsw}{\boldsymbol{w}}
\newcommand{\bsb}{\boldsymbol{b}}
\newcommand{\bsx}{\boldsymbol{x}}
\newcommand{\bsh}{\boldsymbol{h}}
\newcommand{\bsg}{\boldsymbol{g}}
\newcommand{\bst}{\boldsymbol{t}}
\newcommand{\bsz}{\boldsymbol{z}}
\newcommand{\bsell}{\boldsymbol{\ell}}
\newcommand{\bsu}{\boldsymbol{u}}
\newcommand{\bsone}{\boldsymbol{1}}
\newcommand{\tru}{{\rm tr}}
\newcommand{\maxp}{\operatornamewithlimits{max\phantom{p}}}
\newcommand{\infp}{\operatornamewithlimits{inf\phantom{p}}}
\newcommand{\bsy}{\boldsymbol{y}}
\newcommand{\bssigma}{\boldsymbol{\sigma}}
\newcommand{\D}{{\cal D}}
\newcommand{\E}{{\cal E}}
\newcommand{\calK}{{\cal K}}
\newcommand{\cP}{{\cal P}}
\newcommand{\cG}{{\cal G}}
\newcommand{\cQ}{{\cal Q}}
\newcommand{\e}{{\varepsilon}}
\newcommand{\wal}{{\rm wal}}
\newcommand{\sob}{{\rm sob}}
\newcommand{\cost}{{\rm cost}}
\newcommand{\comp}{{\rm comp}}
\newcommand{\dsh}{{\rm dsh}}
\newcommand\setu{{\mathfrak{u}}}
\newcommand{\uu}{\mathfrak{u}}
\newcommand{\de}{{\rm e}}
\newcommand{\swal}{{\rm wal}}
\newcommand{\landau}{{\cal O}}
\newcommand{\mc}{{\rm mc}}
\newcommand{\icomp}{\mathtt{i}}
\newcommand{\bszero}{\boldsymbol{0}}
\newcommand{\rd}{\,\mathrm{d}}
\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\integer}{\ZZ}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\calH}{\mathcal{H}}
\newcommand{\LL}{\mathcal{L}_{\bsg}}
\newcommand{\LLu}{\mathcal{L}_{\setu,\bsg}}
\newcommand{\qed} {\hfill \Box \vspace{0.5cm}}
\renewcommand{\pmod}[1]{\,(\bmod\,#1)}
\newcommand{\ns}{\negthickspace\negthickspace}
\newcommand{\nns}{\negthickspace\negthickspace\negthickspace\negthickspace}
\newcommand{\MC}{{\rm MC}_{n,s}}
\newcommand{\EE}{\mathbb{E}}
\newcommand{\il}{\left<}
\newcommand{\ir}{\right>}
\def\qed{\hfill$\Box$}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\def\calV{{\cal V}}

\DeclareMathOperator*{\esssup}{ess\,sup}

\allowdisplaybreaks

\definecolor{darkmagenta}{RGB}{139,0,139}
\definecolor{darkorange}{RGB}{180,60,0}

\newcommand{\fred}[1]{{\color{darkorange}{#1}}}
\newcommand{\peter}[1]{{\color{darkmagenta}{#1}}}

\begin{document}

 \title{Preface: Multivariate Algorithms and Information-Based Complexity}
% 
% \author{\ }
% 
 \maketitle
% 
% 
% 
% \begin{abstract}
% Abstract. 
% \end{abstract}

This book comprises several articles authored or co-authored by invited speakers in the workshop ``Multivariate Algorithms 
and Information-Based Complexity'' which was part of the 
RICAM Special Semester on ``Multivariate Algorithms and their Foundations in Number Theory'' in the fall of 2018. 
The Special Semester consisted of four larger and two smaller workshops on various topics ranging from 
Pseudo-Randomness and Discrepancy Theory to Information-Based Complexity and Uncertainty Quantification. The present book 
corresponds to the second workshop of the program, which
took place at the Johann Radon Institute for Computational and Applied Mathematics (RICAM) of the Austrian Academy 
of Sciences in Linz, Austria, on November 5--9, 2018.

The workshop and the papers contained in this book focus on 
multivariate continuous problems occurring in a multitude of practical applications, such as physics,
finance, computer graphics, and chemistry. In many cases, the number of variables in the problem
can be in the hundreds or thousands. The information complexity of a given problem is the minimal
number of information operations that is needed to solve the problem within a certain error
threshold. Typical examples of information operations are, e.g., function values or linear functionals.
The field of Information-Based Complexity (IBC), founded by Traub and Wozniakowski in the 1980s,
deals with the analysis of the information complexity for multivariate problems, and, in particular,
with the question how it depends on the number of variables and the error threshold. A crucial
question is, for instance, under which circumstances one can avoid a curse of dimensionality. This
book addresses the analysis of multivariate (continuous) problems, and in particular this shall be
done from the viewpoint of IBC.

The chapter ``The Control Variate Integration Algorithm for Multivariate Functions
Defined at Scattered Data Points'' studies a method of approximating the integral 
of a multivariate function in which one uses the exact integral of a control variate based on 
a least-squares multivariate quasi-interpolant. Numerical examples demonstrate that 
such an algorithm can help to deal with the curse of dimensionality for multivariate least-squares 
fits. The second chapter, titled ``An Adaptive Random Bit Multilevel
Algorithm for SDEs'', considers the approximations of expectations for functionals applied 
to the solutions of stochastic differential equations, by employing Monte Carlo methods 
based on random bits instead of random numbers; an adaptive random bit multilevel algorithm is provided 
and compared numerically to other methods. The chapter ``RBF-Based Penalized Least-Squares
Approximation of Noisy Scattered Data on the Sphere'' deals with the approximation of 
noisy scattered data on the 2-dimensional unit sphere, in particular global and local  
penalized least-squares approximation based on radial basis functions (RBFs). 
The authors of the fourth chapter in the book, ``On the Power of Random Information'', 
consider a problem from the core of IBC theory, namely the quality of random information 
in approximation and integration problems. Random information is compared to optimal 
information for such problems, and it is shown that in some cases random information 
can be almost optimal, whereas in other cases it may perform yield much worse 
results than optimal information. The chapter ``Optimality Criteria for Probabilistic Numerical Methods'' 
is in the field of Bayesian decision theory; to be more precise, the authors study 
an optimality criterion from Bayesian experimental design and considers its implied 
optimal information in the numerical context. Furthermore, the chapter compares this information 
to information commonly used in average-case-optimal numerical methods. The sixth chapter of the 
book, ``$\varepsilon$-Superposition and Truncation Dimensions, and Multivariate Decomposition Method
for $\infty$-Variate Linear Problems'' deals with linear problems on weighted normed function spaces, 
the elements of which depend on infinitely many variables. The author on so-called $\varepsilon$-truncation 
and $\varepsilon$-superposition dimension, as well as multivariate decomposition methods, which 
are means to reduce the number of variables in the problem to a relatively small finite number; 
anchored decomposition and also other types of decomposition (like, e.g., ANOVA decomposition) are used. 
The chapter ``Adaptive Approximation for Multivariate Linear Problems with Inputs Lying in a Cone'' is 
the final chapter of the book, and considers adaptive approximation algorithms for functions lying in particular subsets 
of certain function spaces. Contrary to many papers on IBC it is not assumed that the functions to be 
approximated do not lie in a ball of a certain radius, but instead in a cone. It is shown that for such problems 
it is an advantage to use adaptive instead of non-adaptive algorithms for function approximation.

All chapters were reviewed by internationally renowoned experts in this field. We wish to thank the anonymous referees 
for their precious help.

We would like to express our gratitude towards all speakers of the 
workshop for giving excellent talks on their respective fields of expertise and for contributing to the success of 
the meeting: 
\begin{itemize}
\item Paul Constantine (University of Colorado), 
\item Martin Ehler (University of Vienna), 
\item Mario Hefter (TU Kaiserslautern), 
\item Stefan Heinrich (TU Kaiserslautern), 
\item Kerstin Hesse (University of Paderborn),
\item Fred J.~Hickernell (Illinois Institute of Technology), 
\item James (Mac) Hyman (Tulane University),
\item Thomas M\"{u}ller-Gronbach (University of Passau), 
\item Erich Novak (University of Jena), 
\item Chris Oates (Newcastle University and Alan Turing Institute), 
\item Houman Owhadi (California Institute of Technology),
\item Sergei Pereverzyev (RICAM), Leszek Plaskota (University of Warsaw), 
\item Pawe\l{} Przyby\l{}owicz (AGH University of Science and Technology Krak\'{o}w),
\item Klaus Ritter (TU Kaiserslautern), 
\item Ingo Steinwart (University of Stuttgart),
\item Michaela Sz\"{o}lgyenyi (University of Klagenfurt), 
\item Greg W.~Wasilkowski (University of Kentucky), 
\item Henryk Wo\'{z}niakowski (Columbia University and University of Warsaw),
\item Henry Wynn (London School of Economics), 
\item Larisa Yaroslavtseva (University of Passau).
\end{itemize}

We also would like to thank all participants attending the workshop, 
and Annette Weihs and Wolfgang Forsthuber for administrative and technical support. Further information 
on the RICAM Special Semester ``Multivariate Algorithms and their Foundations in Number Theory'' can 
be found at
\begin{center}
 https://www.ricam.oeaw.ac.at/specsem/specsem2018/ 
\end{center}

The financial support of the Johann Radon Institute for Computational and Applied Mathematics (RICAM) 
of the Austrian Academy of Sciences is gratefully acknowledged.

\bigskip

Fred J.~Hickernell and Peter Kritzer,

Chicago and Linz, January 2020.

\end{document}

### 2020-01-25 DingHickKritzMakRICAMChapVerE.tex
Updates from Overleaf

@@
 A ratio $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
-For $d=4$, $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$.
+For $d=4$, $\|f - \ALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.3 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.01$ for $\varepsilon = 0.001$.
 This shows that our adaptive approximation algorithm works reasonably well.

### 2020-01-25 DingHickKritzMakRICAMChapVerF.tex

@@
 A ratio $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ close to, but not exceeding, one is desired, since this shows that our adaptive algorithm is successful.
-For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.4 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.014$ for $\varepsilon = 0.001$.
+For $d=4$, $\|f - \DHKMALG(f,\varepsilon)\|_\infty/\varepsilon$ fluctuates around 0.3 for all choices of $\varepsilon$; for $d=7$, this ratio begins at $\approx 0.1$ for $\varepsilon = 0.1$, then decreases to $\approx 0.01$ for $\varepsilon = 0.001$.
 This shows that our adaptive approximation algorithm works reasonably well.
